### 2020-03-10 scripts/00_data_wrangling.Rmd
moving raw data back over

---
output:
  html_document: default

title: "SubsidyExplorer - Step 0: Data Wrangling"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
---

```{r setup, include=FALSE}
library(knitr) 
library(countrycode) # country name matching
library(WDI) # World Bank GDP and population numbers by country
library(janitor) # cleaning column names
library(tidyverse)
library(readxl)
```

```{r}
# Code options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, message = FALSE, warning = F)

# Directories for the output files generated by this script
data_dir <- here::here("data", "edited/")
if (dir.exists(data_dir) == F) {
  dir.create(data_dir, recursive = T)
}

app_data_dir <- here::here("app", "data/")
if (dir.exists(app_data_dir) == F) {
  dir.create(app_data_dir, recursive = T)
}

results_dir <- here::here("results", "00-data-wrangling/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}

```

## Introduction

This script handles the preliminary data wrangling for the raw datasets underlying the SubsidyExplorer toolkit. It outputs tidyed data files to `r data_dir`.

It also creates and outputs four aggregated CSV files that are used as input data by the SubsidyExplorer toolkit (saved to `r app_data_dir`): 
- subsidies-2009-2018-tidy.csv
- demographic-2000-2018-tidy.csv
- fisheries-2000-2017.csv
- fao-landings-group-2000-2017.csv

Summary figures are exported to `r results_dir`.

```{r}
# Paths to subsidies data files
sumaila_subsidies_path <- here::here("data", "raw", "Sumaila-et-al-2019-subsidies", "Subsidies_PEW_Final.xlsx")
oecd_fse_path <- here::here("data", "raw", "OECD-2019-fse", "FISH_FSE_10032020183349581.csv")

# Paths to demographic data files
fao_fishers_path <- here::here("data", "raw", "FAO-2019-yearbook", "fao_fishers_yearbook_070619.csv")
teh_fte_path <- here::here("data", "raw", "Teh-and-Sumaila-2013-fte", "Fisher employment FTE.xlsx")

# Paths to fisheries data files
fao_production_path <- here::here("data", "raw", "FAO-2019-capture-production", "TS_FI_CAPTURE.csv")
#fao_value_path
melnychuk_price_path <- here::here("data", "raw", "Melnychuk-et-al-2013-price", "Melnychuk_Exvessel_Price_Database.csv")

# Paths to misc data files 
costello_upsides_path <- here::here("data", "raw", "Costello-et-al-2016-upsides", "ProjectionData_2012.csv")
iuu_vessel_path <- here::here("data", "raw", "IUU-Vessel-List-2019", "IUUList-20190430.csv")
ram_sadb_path <- here::here("data", "raw", "RAM-2018-stock-assessment-database", "RLSADB v4.40", "DB Files With Assessment Data", "RLSADB v4.40 (assessment data only).xlsx")
```

The following data sources are included in this analysis:

Estimates of annual fisheries subsidies provision by state from Sumaila et al. (2019) in 2018 US\$. These data were provided to us directly by the authors as a .xlsx file and are stored at `r sumaila_subsidies_path`.
> Sumaila, U. R., Ebrahim, N., Schuhbauer, A., Skerritt, D., Li, Y., Kim, H. S., … Pauly, D. (2019). Updated estimates and analysis of global fisheries subsidies. Marine Policy, 109, 103695. https://doi.org/10.1016/j.marpol.2019.103695

Estimates of fisheries support provision by state from the OECD (2008 - 2018). These data were last downloaded from the OECD iLibrary portal as a CSV file on March 10, 2019 and are stored as `r oecd_fse_path`.
> OECD (2019), "Fisheries: Fisheries support estimates", OECD Agriculture Statistics (database), https://doi.org/10.1787/ade64fdc-en (accessed on 10 March 2019).

Total GDP and population by state from the World Bank's World Development Indicators Database (2000 - 2018). These data were accessed through the `WDI` package. The code used to pull the data is below. 
> The World Bank (2019). "World Development Indicators", https://datacatalog.worldbank.org/dataset/world-development-indicators (accessed on 24 October 2019).

Total number of fishers by state from the FAO Yearbook of Fishery and Aquaculture Statistics (misc. years between 1995 and 2017). These data were manually transcribed from PDF (`./data/raw/fleet_&_employment.pdf`) to CSV format on July 6, 2019 and are stored as `r fao_fishers_path`. 
> FAO (2019). FAO yearbook. Fishery and Aquaculture Statistics 2017, http://www.fao.org/fishery/statistics/global-fishers/en (accessed on 24 October 2019).

Estimated number of full-time jobs in fisheries from Teh and Sumaila (2013) in 2003. These data were provided to us directly by the authors as a .xlsx file and are stored as `r teh_fte_path`. 
> Teh, L. C. L., & Sumaila, U. R. (2011). Contribution of marine fisheries to worldwide employment. Fish and Fisheries, 14(1), 77–88. https://doi.org/10.1111/j.1467-2979.2011.00450.x

Fisheries landings  in 2017 from the FAO Global Capture Production database (2019) and estimates of landed value generated using the ex-vessel price database created by Melnychuk et al. (2017). These data were were wrangled in the previous script, and the edited data are stored as `r catch_dat_path`. 
> FAO (2019). FAO yearbook. Fishery and Aquaculture Statistics 2017, http://www.fao.org/fishery/statistics/global-capture-production/en (accessed on 24 October 2019). 
> Melnychuk, M. C., Clavelle, T., Owashi, B., & Strauss, K. (2017). Reconstruction of global ex-vessel prices of fished species. ICES Journal of Marine Science, 74(1), 121–133. https://doi.org/10.1093/icesjms/fsw169

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2020-03-10 scripts/01_vessel_list.Rmd
moving raw data back over

---
output:
  html_document: default

title: "SubsidyExplorer - Step 1: Create Vessel List"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
bibliography: "../pew-subsidies.bib"

---

# Introduction

This script creates the global vessel list used in the SubsidyExplorer toolkit. It requires access to the raw Global Fishing Watch (GFW) data stored on BigQuery (not-publically available), as well as a valid Google Cloud Console billing account. It outputs a single data file to `r here::here("results", "01-vessel-list")`:

- vessel_list_2018_raw.csv

```{r}
# Load packages
library(knitr) 
library(countrycode) # country name matching
library(bigrquery) # access Bigquery from R
#devtools::install_github("r-dbi/bigrquery")
library(tidyverse)

# Path to cleaned subsidies data file
subsidy_dat_path <- here::here("data", "edited", "sumaila-subsidies-2018-tidy.csv")

# Path to cleaned landings data file
catch_dat_path <- here::here("data", "edited", "fisheries-area-2000-2017-tidy.csv")

# Bigquery project
bq_project <-  "ucsb-gfw"

# Do you want to make summary figures?
make_figures <- F
```

```{r}
# Code options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, message = FALSE, warning = F)

# Directories for the output files generated by this script
results_dir <- here::here("results", "1-vessel-list/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}

```

# Extract good fishing vessels from existing vessel info table

This section describes the process of linking to the most recent version of the GFW vessel information table, and pulling information on all likely fishing vessels represented in that dataset. This process was last performed on `r format(Sys.time(), '%B %d, %Y')`.

The vessel info table we're using (`world-fishing-827.gfw_research.vi_ssvid_byyear_v20190430`) has all sorts of stuff in it, so there are some basic filters we need to apply.

First, we remove all transmissions from objects that are likely fishing gear (buoys, nets, etc.), rather than vessels.

Second, we apply a number of filters to remove ids associated with non-fishing, inactive, and spoofing vessels:
- MMSI must be on the best fishing vessel list
- MMSI cannot be used by 2+ vessels with different names simultaneously
- MMSI cannot be used by multiple vessels simultaneously for more than 3 days
- MMSI has not been found to be offsetting its position
- MMSI vessel class can be inferred by the neural net (i.e. it is an active vessel)
- MMSI was active for at least 1 day and fished for at least 1 hour in a year
- MMSI is associated with fewer than five shipnames

Finally, GFW has manually compiled a list of vessel IDs that are bad, so we exclude those.

```{r}
sql <- "WITH
  # This query identifies fishing vessels that meet annual quality criteria
  # e.g. not spoofing/offsetting/too many identities/etc.
  good_fishing_vessels AS (
  SELECT
      ssvid,
      year,
      best.best_vessel_class geartype,
      best.best_flag flag
    FROM
      `world-fishing-827.gfw_research.vi_ssvid_byyear_v20190430`
    WHERE
      on_fishing_list_best # MMSI must be on best fishing list
      AND (activity.overlap_hours_multinames = 0 OR activity.overlap_hours_multinames IS NULL) # MMSI cannot be used by 2+ vessels with different names simultaneously
      AND activity.overlap_hours < 24*3 # MMSI cannot be used by multiple vessels simultaneously for more than 3 days
      AND activity.offsetting IS FALSE # MMSI not offsetting position
      AND inferred.inferred_vessel_class_byyear IS NOT NULL # MMSI vessel class can be inferred by the neural net (active)
      # MMSI active for at least 1 days and fished for at least 1 hours in the year.
      AND activity.fishing_hours > 1
      AND activity.active_hours > 24*1
      AND 5 >= ( # MMSI associated with fewer than five shipnames
        SELECT
          COUNT(*)
        FROM (
          SELECT
            value,
            SUM(count) AS count
          FROM
            UNNEST(ais_identity.n_shipname)
          WHERE
            value IS NOT NULL
          GROUP BY
            value)
        WHERE
          count >= 10)
      AND ssvid NOT IN (
        SELECT
          ssvid
        FROM
          `ucsb-gfw.SubsidyExplorer.likely_gear`)),

  # This subquery identifies MMSI that offsett a lot
  nast_ssvid AS (
  SELECT
    ssvid,
    SUM( positions) positions
  FROM `world-fishing-827.gfw_research.pipe_v20190502_segs`
  WHERE
    (dist_avg_pos_sat_vessel_km > 3000 AND sat_positions_known > 5)
    AND first_timestamp < timestamp('2018-12-31')
    AND last_timestamp > timestamp('2018-01-01')
  GROUP BY ssvid)

# Filter so manually determined bad mmsi and those ofsetting a lot are excluded and return
SELECT
  ssvid,
  year,
  geartype,
  flag
FROM
  good_fishing_vessels
WHERE
  CAST(ssvid AS int64) NOT IN (
    SELECT
      ssvid
    FROM
      `world-fishing-827.gfw_research.bad_mmsi`
    CROSS JOIN
      UNNEST(ssvid) AS ssvid)
  AND ssvid NOT IN (SELECT ssvid FROM nast_ssvid)"

fv_table <- bq_table(project = bq_project, 
                     table = "all_good_fishing_vessels",
                     dataset = "SubsidyExplorer")

if(bq_table_exists(fv_table)){

  bq_table_delete(fv_table)
  bq_project_query(bq_project, 
                   sql, 
                   destination_table = fv_table, 
                   use_legacy_sql = FALSE, 
                   allowLargeResults = TRUE)

}else {
  bq_table_create(fv_table)
  bq_project_query(bq_project, 
                   query = sql, 
                   destination_table = fv_table,
                   use_legacy_sql = FALSE, 
                   allowLargeResults = TRUE)
}
```

# Extract fishing effort for good fishing vessels

We then extract the number of hours spent fishing by each of our good fishing vessels in different EEZs and/or FAO regions from the raw fishing effort table (`world-fishing-827.gfw_research.pipe_v20190502_fishing`).

To identify valid fishing effort, we apply the following filters:
- The fishing activity must have occured during a valid segment as identified by GFW.
- The fishing activity must have occured during a segment with more than 10 positions that was not concurrently overlapping with another, longer, segment for the same MMSI.  
- The vessel performing the fishing activity must appear on the list of good fishing vessels created above

We then extract a vessel table with the the following attributes: 
- year (int): Year. Matches our data year specified above.
- eez_id (chr): EEZ identifier. 
- fao_region (int): Major FAO statistical region
- fishing_hours_eez_fao: Total annual fishing hours in the specified eez and/or fao region by a single vessel
- ssvid (chr): Unique vessel identification number given by GFW (MMSI number for most vessels)
- flag (chr): Best flag state of the vessel. 
- vessel_class (chr): Best vessel type. 
- length_m (dbl): Best vessel length in meters.
- tonnage_gt (dbl): Best vessel tonnage in gross tons. 
- engine_power_kw (dbl): Best engine power in killowatt hours. 
- broadcast_shipname (chr): Most common ship name broadcast by the vessel.
- broadcast_callsign (chr): Most common ship callsign broadcast by the vessel.
- broadcast_imo (chr): Most common imo number broadcast by the vessel.
- territory1_iso3 (chr) : Three letter code cooresponding to the administering territory of the EEZ
- territory2_iso3 (chr) : Three letter code cooresponding to the second administering territory of the EEZ (disputed areas only)
- territory3_iso3 (chr) : Three letter code cooresponding to the third administering territory of the EEZ (disputed areas only)
- sovereign1_iso3 (chr) : Three letter code cooresponding to the sovereign state of the EEZ
- sovereign2_iso3 (chr) : Three letter code cooresponding to the second sovereign state of the EEZ (disputed areas only)
- sovereign3_iso3 (chr) : Three letter code cooresponding to the third sovereign state of the EEZ (disputed areas only)

```{r}
sql2 <- '
WITH
  # This subquery identifies good segments
  good_segments AS (
  SELECT
    seg_id
  FROM
    `world-fishing-827.gfw_research.pipe_v20190502_segs`
  WHERE
    good_seg
    AND positions > 10
    AND NOT overlapping_and_short),

  # This subquery identifies good fishing vessels from our previous query
  good_vessels AS (
  SELECT
    *
  FROM
    `ucsb-gfw.SubsidyExplorer.all_good_fishing_vessels`),

  # This subquery identifies vessel information that we want to keep
  vessel_info AS (
  SELECT
    ssvid,
    year,
    best.best_flag as flag,
    best.best_vessel_class as vessel_class,
    best.best_length_m as length_m,
    best.best_tonnage_gt as tonnage_gt,
    best.best_engine_power_kw as engine_power_kw,
    ais_identity.n_shipname_mostcommon.value as broadcast_shipname,
    ais_identity.n_callsign_mostcommon.value as broadcast_callsign,
    ais_identity.n_imo_mostcommon.value as broadcast_imo
  FROM
    `world-fishing-827.gfw_research.vi_ssvid_byyear_v20190430`
  WHERE
    year = 2018),

  # This subquery identifies eez information that we want to keep
  eez_info AS (
  SELECT
    CAST(eez_id as string) as eez_id,
    territory1_iso3,
    territory2_iso3,
    territory3_iso3,
    sovereign1_iso3,
    sovereign2_iso3,
    sovereign3_iso3
  FROM
    `world-fishing-827.gfw_research.eez_info`),

  # This subquery gets all fishing effort by ssvid, eez, and fao region in 2018 cooresponding to good segments and good vessels
  fishing_by_eez_and_fao AS (
    SELECT
      EXTRACT(year FROM date) AS year,
      ssvid,
      if(ARRAY_LENGTH(regions.eez)=0, "0000", regions.eez[ordinal(1)]) AS eez_id,
      if(ARRAY_LENGTH(regions.major_fao)=0, "0", regions.major_fao[ordinal(1)]) AS fao_region,
      sum(hours) AS fishing_hours_eez_fao
    FROM
      `world-fishing-827.gfw_research.pipe_v20190502_fishing`
    WHERE
      date > timestamp("2018-01-01")
      AND date < timestamp("2018-12-31")
      AND ARRAY_LENGTH(regions.major_fao) > 0 # removes fishing inland
      AND nnet_score2 > .5
      AND seg_id IN (
        SELECT
          seg_id
        FROM
          good_segments)
      AND ssvid IN (
        SELECT
          ssvid
        FROM
          good_vessels
        WHERE
          year = 2018)
    GROUP BY
      year,
      ssvid,
      eez_id,
      fao_region
    ORDER BY
      year,
      ssvid,
      fishing_hours_eez_fao DESC)

SELECT
  *,
  fishing_hours_eez_fao*engine_power_kw as fishing_KWh_eez_fao
FROM
  fishing_by_eez_and_fao
LEFT JOIN
  vessel_info
USING
  (ssvid,
  year)
LEFT JOIN
  eez_info
USING
  (eez_id)
'

effort_table <- bq_table(project = bq_project, 
                     table = "effort_good_fishing_vessels_2018_raw",
                     dataset = "SubsidyExplorer")

if(bq_table_exists(effort_table)){

  bq_table_delete(effort_table)
  effort_good_fishing_vessels_2018 <- 
    bq_project_query(bq_project, 
                    sql2, 
                    destination_table = effort_table, 
                    use_legacy_sql = FALSE, 
                    allowLargeResults = TRUE) %>%
     bq_table_download()

}else {
  bq_table_create(effort_table)
  effort_good_fishing_vessels_2018 <- 
    bq_project_query("world-fishing-827", 
                   query = sql2, 
                   destination_table = effort_table,
                   use_legacy_sql = FALSE, 
                   allowLargeResults = TRUE) %>%
    bq_table_download()
}

# Save
write_csv(effort_good_fishing_vessels_2018, paste0(results_dir, "effort_good_fishing_vessels_2018_raw.csv"))

# If BigQuery connection isn't working, or you don't have access, impuort from local file
effort_good_fishing_vessels_2018 <- read_csv(paste0(results_dir, "effort_good_fishing_vessels_2018_raw.csv"), col_types = "nnnnnccnnnccnccccccn")
```

# Correct outdated flag codes and Identify EU and USA dependent vessels

Before allocating catches and subsidies across vessels, we need to do some manual corrections for incorrect flag codes and we need to identify vessels flagged to states that are overseas dependencies of the EU or USA. We assume that these vessels recieve subsidies from their sovereign states.

```{r}
# EU countries
#Belgium, Bulgaria, Croatia, Cyprus, Denmark, Estonia, Finland, France, Germany, Greece, Ireland, Italy, Latvia, Lithuania, Malta, Netherlands, Poland, Portugal, Romania, Slovenia, Spain, Sweden, United Kingdom
eu_countries <- c("BEL", "BGR", "HRV", "CYP", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "IRL", "ITA", "LVA", "LTU", "MLT", "NLD", "POL", "PRT", "ROU", "SVN", "ESP", "SWE", "GBR")

# EU overseas territories: 
# Dutch overseas territories: Aruba, Bonaire/St. Eustatius/Saba, Curacao, Sint Maarten
dutch_territories <- c("ABW", "BES", "CUW", "SXM")

# French overseas territories: French Guiana, French Polynesia, French Southern and Antarctic Territories, Guadeloupe, Martinique, Mayotte, New Caledonia, Reunion, Saint Barthelemy, Saint Martin, St. Pierre and Miquelon, Wallis and Futuna Islands
french_territories <- c("GUF", "PYF", "ATF", "GLP", "MTQ", "MYT", "NCL", "REU", "BLM", "MAF", "SPM", "WLF")

# Danish overseas territories: Faroe Islands, Greenland
danish_territories <- c("FRO", "GRL")

# British overseas territories: Anguilla, Ascension island, Bermuda, Cayman Islands, Falkland Islands, Guernsey, Gibraltar, British Indian Ocean Territories, Jersey, Monserratt, Pitcairn Island, South Georgia and the South Sandwich Islands, Saint Helena/Ascension/Tristan da Cunha, Tristan da Cunha, Turks and Caicos Islands, British Virgin Islands
uk_territories <- c("AIA","ASC","BMU","CYM","FLK","GGY","GIB","IOT","JEY","MSR","PCN","SGS","SHN","TAA","TCA","VGB")

# Combine
eu_territories <- c(dutch_territories, french_territories, danish_territories, uk_territories)

# Norwegian overseas territories: Bouvet Islands, Svalbard and Jan Mayen Islands
norwegian_territories <- c("BVT", "SJM")

# US overseas territories:  American Samoa, Guam, Northern Marianas Islands, Puerto Rico, US Virgin Islands
us_territories <- c("ASM", "GUM", "MNP", "PRI", "VIR")
```

```{r}
# Get table of all flag states in the GFW data
gfw_flags <- effort_good_fishing_vessels_2018 %>%
  distinct(flag) %>%
  mutate(flag_name = countrycode(flag, "iso3c", "country.name"))

```

```{r}
# Only three we need to fix: GCA (outdated code for Guatemala), ROM (outdated code for Romania), and UNK (unknown, for some reason not just NA)
vessel_list <- effort_good_fishing_vessels_2018
vessel_list$flag[vessel_list$flag == "GCA"] <- "GTM"
vessel_list$flag[vessel_list$flag == "ROM"] <- "ROU"
vessel_list$flag[vessel_list$flag == "UNK"] <- NA
```

# Allocating Catches and Subsidies

Before we allocate catches and subsidies, we need to get total fishing kWh by flag and FAO region, as well as by flag.

```{r}
# Effort by flag and fao
effort_flag_fao <- vessel_list %>%
  group_by(flag, fao_region) %>%
  summarize(fishing_KWh = sum(fishing_KWh_eez_fao, na.rm = T)) %>%
  ungroup()

# Effort by flag
effort_flag <- effort_flag_fao %>%
  group_by(flag) %>%
  summarize(fishing_KWh = sum(fishing_KWh, na.rm = T)) %>%
  ungroup()
```

We then need to get total catches and revenues per fishing KWh by flag and FAO region, as well as by flag. We first will assign catch rates for FAO region/flag combinations that appear in both the GFW and FAO data. For FAO region/flag combinations that don't appear in the FAO data, we will allocate the remainder?

```{r}
# Load catch and revenue data
catch_flag_fao <- read_csv(catch_dat_path) %>%
  dplyr::filter(year == 2017) %>%
  dplyr::filter(!(iso3 %in% c("EU", "USA-T", "UNK"))) %>%
  group_by(iso3, area, variable) %>%
  summarize(value = sum(value, na.rm = T)) %>%
  ungroup() %>%
  spread(variable, value) %>%
  dplyr::filter(landings > 0)

catch_flag <- catch_flag_fao %>%
  group_by(iso3) %>%
  summarize(landings = sum(landings, na.rm = T),
            revenue = sum(revenue, na.rm = T)) %>%
  ungroup()
```

First, we identify flag states in the GFW data that do not have reported catches.

```{r}
# effort_flag
effort_no_matching_catches <- effort_flag %>%
  dplyr::filter(!(flag %in% catch_flag$iso3))

# There are 3 flag states for which we don't have reported catch data at all: CXR (Christmas Island), LIE (Liechtenstein) and NA (no flag). We're going to try assigning them based on the EEZ in which they spend the most time fishing instead. 
vessels_new_flag <- vessel_list %>%
  dplyr::filter(flag %in% effort_no_matching_catches$flag) %>% # 773 entries 
  dplyr::filter(eez_id != 0) %>% # remove high seas entries
  group_by(ssvid) %>%
  top_n(1, fishing_KWh_eez_fao) %>%
  summarize(new_flag = unique(territory1_iso3))  #486 vessels

# So  there are 75 vessels that have no flag and that only fish on the high seas... We'll be excluding those vessels
vessel_info_new_flag <- vessel_list %>%
  dplyr::filter(ssvid %in% vessels_new_flag$ssvid) %>%
  left_join(vessels_new_flag, by = "ssvid") %>%
  mutate(flag = new_flag) %>%
  dplyr::select(-new_flag) # 688 entries

# Fix vessel list 
vessel_list <- vessel_list %>%
  dplyr::filter(!(flag %in% effort_no_matching_catches$flag)) %>%
  bind_rows(vessel_info_new_flag) %>%
  dplyr::filter(!is.na(flag))
vessel_list$flag[vessel_list$flag == "ESH"] <- "MAR"
vessel_list$flag[vessel_list$flag == "CPT"] <- "FRA"
```

Turns out they all do!

```{r}
# And we redo one last time
effort_flag_fao <- vessel_list %>%
  group_by(flag, fao_region) %>%
  summarize(fishing_KWh = sum(fishing_KWh_eez_fao, na.rm = T)) %>%
  ungroup()

# Effort by flag
effort_flag <- effort_flag_fao %>%
  group_by(flag) %>%
  summarize(fishing_KWh = sum(fishing_KWh, na.rm = T)) %>%
  ungroup()

# effort_flag
effort_no_matching_catches <- effort_flag %>%
  dplyr::filter(!(flag %in% catch_flag$iso3))
```

Now that we don't have any flags with no associated catch, we can start calculating catch rates by flag and FAO statistical area.

```{r}
# Let's get region specific catch rates we can use for when we don't have matching flag/fao pairs
catch_region_no_match <- catch_flag_fao %>%
  anti_join(effort_flag_fao, by = c("iso3" = "flag", "area" = "fao_region")) %>%
  mutate(join_region = case_when(area == 88 ~ 58,
                                      TRUE ~ area)) %>%
  group_by(join_region) %>%
  summarize(tot_landings = sum(landings, na.rm = T),
            tot_revenue = sum(revenue, na.rm = T))

# Get matching catch/effort flag and fao region pairings
match_effort_catch <- effort_flag_fao %>%
  left_join(catch_flag_fao, by = c("flag" = "iso3", "fao_region" = "area")) %>%
  arrange(flag, fao_region) %>%
  mutate(is_match = ifelse(!is.na(fishing_KWh) & !is.na(landings), T, F))

# # Extract those flag/fao pairings for which we have matching entries to calculate catch rates
match <- match_effort_catch %>%
  dplyr::filter(is_match) %>%
  mutate(catch_per_fishing_KWh = landings/fishing_KWh,
         revenue_per_fishing_KWh = revenue/fishing_KWh) %>%
  dplyr::select(flag, fao_region, catch_per_fishing_KWh, revenue_per_fishing_KWh)

# # Extract those flag/fao pairings for which we have matching entries to calculate catch rates
no_match <- match_effort_catch %>%
  dplyr::filter(is_match == F)

# Get leftover rates
rates_no_match <- no_match %>%
  mutate(join_region = case_when(fao_region == 18 ~ 21,
                                 fao_region == 67 ~ 77,
                                 fao_region == 47 ~ 41,
                                 TRUE ~ fao_region)) %>%
  full_join(catch_region_no_match, by = c("join_region")) %>%
  group_by(join_region) %>%
  mutate(tot_fishing_KWh = sum(fishing_KWh, na.rm = T),
         catch_per_fishing_KWh = tot_landings/tot_fishing_KWh,
         revenue_per_fishing_KWh = tot_revenue/tot_fishing_KWh) %>%
  ungroup() %>%
  group_by(fao_region) %>%
  summarize(catch_per_fishing_KWh = unique(catch_per_fishing_KWh),
            revenue_per_fishing_KWh = unique(revenue_per_fishing_KWh))

# Add back in to our flag/fao pairings
no_match <- no_match %>%
  left_join(rates_no_match, by = c("fao_region")) %>%
  dplyr::select(flag, fao_region, catch_per_fishing_KWh, revenue_per_fishing_KWh)

# Combine
catch_rates_flag_fao_all <- match %>%
  bind_rows(no_match)
```

And now we can apply those catch rates to our vessel list.

```{r}
vessel_list <- vessel_list %>%
  left_join(catch_rates_flag_fao_all, by = c("flag", "fao_region"))
```

The process for allocating subsidies is slightly more straightforard as we only have data by flag

```{r}
# Load subsidy data
subsidies_dat <- read_csv(subsidy_dat_path) %>%
  dplyr::filter(year == 2018)

# Summarize total subsidies by type and flag
subsidies_flag <- subsidies_dat %>%
  group_by(iso3, type) %>%
  summarize(value = sum(value, na.rm = T)) %>%
  spread(type, value)

subsidy_types <- unique(subsidies_dat$type)
good_subsidy_types <- c("A1", "A2", "A3")
ugly_subsidy_types <- c("C1", "C2", "C3")
bad_subsidy_types <- c("B1", "B2", "B3", "B4", "B5", "B6", "B7")

# Resummarize effort including overseas territories with their sovereign
effort_flag_revised <- effort_flag %>%
  mutate(flag_for_matching = case_when(flag %in% c("USA", us_territories) ~ "USA",
                              flag %in% c("FRA", french_territories) ~ "FRA",
                              flag %in% c("GBR", uk_territories) ~ "GBR",
                              flag %in% c("NOR", norwegian_territories) ~ "NOR",
                              flag %in% c("DNK", danish_territories) ~ "DNK",
                              flag %in% c("NLD", dutch_territories) ~ "NLD",
                              TRUE ~ flag)) %>%
  group_by(flag_for_matching) %>%
  mutate(tot_fishing_KWh = sum(fishing_KWh, na.rm = T))

# Calculate subsidy rates by flag
subsidy_rates_flag <- effort_flag_revised %>%
  left_join(subsidies_flag, by = c("flag_for_matching" = "iso3")) %>%
  group_by(flag) %>%
  summarize_at(subsidy_types, list(per_fishing_KWh = ~./tot_fishing_KWh))
subsidy_rates_flag[is.na(subsidy_rates_flag)] <- 0

# Join back to vessel_list
vessel_list <- vessel_list %>%
  left_join(subsidy_rates_flag, by = c("flag"))

```

Now we can calculate total catches, revenues, and subsidies by type for each vessel

```{r}
rename_me <- function(x){
  str_replace(x, "_per_fishing_KWh", "")
}

vessel_list <- vessel_list %>%
  mutate(catch = fishing_KWh_eez_fao*catch_per_fishing_KWh,
         revenue = fishing_KWh_eez_fao*revenue_per_fishing_KWh) %>%
  mutate_at(paste0(subsidy_types, "_per_fishing_KWh"), list(subs = ~.*fishing_KWh_eez_fao)) %>%
  rename_at(paste0(subsidy_types, "_per_fishing_KWh_subs"), rename_me) %>%
  dplyr::select_at(vars(-contains("_per_fishing_KWh"))) %>%
  mutate(good_subs = rowSums(select(., one_of(paste0(good_subsidy_types, "_subs")))),
         bad_subs = rowSums(select(., one_of(paste0(bad_subsidy_types, "_subs")))),
         ugly_subs = rowSums(select(., one_of(paste0(ugly_subsidy_types, "_subs")))))

write_csv(vessel_list, paste0(results_dir, "vessel-list-2018-raw.csv"))
```

# Vessel list summary figures

Quick summary of our global vessel list by gear type:

```{r}
if(make_figures){
# Summary by gear type
vessels_by_gear <- vessel_list %>%
  group_by(vessel_class) %>%
  summarize(count = n_distinct(ssvid),
            flag_states = n_distinct(flag),
            fao_regions = n_distinct(fao_region),
            length_avg = mean(length_m, na.rm = T),
            tonnage_avg = mean(tonnage_gt, na.rm = T),
            engine_power_avg = mean(engine_power_kw, na.rm = T),
            fishing_hours = sum(fishing_hours_eez_fao, na.rm = T))

normal_theme <- theme_linedraw()+
  theme(
    panel.grid=element_blank(),
    plot.title=element_text(size=14, face="bold")
  )

pie_theme <- normal_theme +
  theme(
    axis.line = element_blank(),
    axis.title.x = element_blank(),
    axis.text = element_blank(),
    axis.title.y = element_blank(),
    panel.border = element_blank(),
    axis.ticks = element_blank()  )

# Total number of vessels
ggplot(vessels_by_gear)+
  aes(x = "", y = count, fill = vessel_class)+
  geom_bar(stat = "identity", width = 1, color = "grey4", size = 0.2)+
  coord_polar("y")+
  #scale_fill_tableau(name = "Flag State", palette = "Tableau 20")+
  pie_theme+
  labs(title = paste0("Number of vessels by vessel class | Total vessels: ", format(sum(vessels_by_gear$count), big.mark = ",")))

# Flags using each gear types
ggplot(vessels_by_gear)+
  aes(x = fct_reorder(vessel_class, flag_states, .desc = TRUE), y = flag_states, fill = vessel_class)+
  geom_bar(stat = "identity", width = 1, color = "grey4", size = 0.2)+
  scale_y_continuous(expand = c(0,0))+
  scale_fill_discrete(guide = "none")+
  normal_theme +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  labs(title = paste0("Number of flag states using each vessel class | Total vessels: ", format(sum(vessels_by_gear$count), big.mark = ",")),
       x = "Vessel Class",
       y = "Number of Flag States")
}
```

### 2020-03-11 scripts/00_data_wrangling.Rmd
subsidy map back up

@@
 
-## Introduction
+# Introduction
 
@@
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+# Note: Political entities, dependencies, and naming
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+The naming of flag and coastal states varies widely across our data sources and we recognize that this can be a politially sensitive matter.
+For the purposes of merging multiple data sources, we therefore translate all state names from the raw data sources to ISO-3 character codes.
+Country names are only used for display purposes, and the use of any particular name is not meant to convey any options regarding sovereignty on behalf of the authors.
 
-```{r cars}
-summary(cars)
+```{r}
+# Load country dependencies helper file
+country_dependencies <- read_csv(here::here("data", "helper-files", "country_dependencies.csv"))
+
+# EU countries
+eu_countries <- country_dependencies$country_iso3[country_dependencies$is_EU]
+eu_country_names <- sort(countrycode(eu_countries, "iso3c", "country.name"))
+
+# EU overseas territories
+eu_territories <- country_dependencies$country_iso3[country_dependencies$sovereign_iso3 %in% eu_countries & !country_dependencies$is_EU]
+eu_territory_names <- sort(c(countrycode(eu_territories, "iso3c", "country.name"), "Ascension Island", "Tristan da Cunha"))
+
+# US overseas territories:  American Samoa, Guam, Northern Marianas Islands, Puerto Rico, US Virgin Islands
+us_territories <- country_dependencies$country_iso3[country_dependencies$sovereign_iso3 == "USA"]
+us_territory_names <- sort(countrycode(us_territories, "iso3c", "country.name"))
 ```
 
-## Including Plots
+Additionally, it is important to note that the European Union as a political entity is a Member of the World Trade Organization, rather then the individual states that make up the European Union.
+We therefore need to create a profile for the European Union as a whole.
+The following `r length(eu_country_names)` states are considered to be part of the European Union for the purposes of this analysis: `r paste(eu_country_names, collapse = ", ")`.
 
-You can also embed plots, for example:
+The Netherlands, France, Denmark, and the United Kingdom also have overseas dependencies that should be considered to be a part of the European Union for statistical purposes.
+The following overseas dependencies are also considered to be a part of the European Union for the purpose of aggregating data in this analysis: `r paste(eu_territory_names, collapse = ", ")`.
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+Outside of the EU, the only other dependencies we need to worry about are those that relate to the United States.
+The following overseas dependencies are considered to be a part of the United States for the purpose of aggregating data in this analysis: `r paste(us_territory_names, collapse = ", ")`.
+
+# Section 1 - Subsidies Data
+
+## Updated estimates and analysis of global fisheries subsidies from Sumaila et al. (2019)
+
+```{r}
+### Data Wrangling
+# Load and wrangle 2019 data
+sumaila_2019_dat <- read_xlsx(sumaila_subsidies_path) %>%
+  clean_names(case = "snake") %>%
+  mutate(iso3 = case_when(country == "Dominican Rp" ~ "DOM",
+                          country == "Micronesia" ~ "FSM",
+                          country == "Untd Arab Em" ~ "ARE",
+                          TRUE ~ countrycode(country, "country.name", "iso3c"))) %>%
+  dplyr::select(iso3, type = class, data_type, value = constant_2018_usd) %>%
+  mutate(year = 2018,
+         units = "2018 US$",
+         source = "Sumaila et al. (2019)") %>%
+  arrange(iso3)
+
+# Load lookup table for classification scheme
+sumaila_lookup <- read_csv(here::here("data", "helper-files", "sumaila_subsidies_classification.csv"))
+
+# Clean up the naming/spelling of the classification scheme as well as data type
+sumaila_2019_dat_edit <- sumaila_2019_dat %>%
+  left_join(sumaila_lookup, by = "type") %>%
+  dplyr::select(iso3, year, category, type, type_name = subtype, value, data_type, units, source)
+
+sumaila_2019_dat_edit$data_type[sumaila_2019_dat_edit$data_type == "not found evidence of subsidy"] <- "Found no evidience of subsidy"
+
+# Deal with the EU
+sumaila_2019_dat_eu <- sumaila_2019_dat_edit %>%
+  dplyr::filter(iso3 %in% c(eu_countries, eu_territories)) %>%
+  mutate(entity = "EU",
+         data_type = "Aggregate") %>%
+  group_by(entity, year, category, type, type_name, data_type, units, source) %>%
+  summarize(value = sum(value, na.rm = T)) %>%
+  rename(iso3 = entity)
+
+# Add the EU back in
+sumaila_2019_dat_edit <- sumaila_2019_dat_edit %>%
+  bind_rows(sumaila_2019_dat_eu)
+
+# Save
+write_csv(sumaila_2019_dat_edit, paste0(data_dir, "sumaila_et_al_2019_subsidies_tidy.csv"))
+write_csv(sumaila_2019_dat_edit, paste0(app_data_dir, "sumaila_et_al_2019_subsidies_tidy.csv"))
+
+### Summary Plots
+
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+## Estimates of fisheries support provision by state from the OECD (2008 - 2018)
+
+```{r}
+# Load and wrangle OECD data (2009 - 2017)
+oecd_fse_dat <- read_csv(oecd_fse_path) %>%
+  clean_names(case = "snake") %>%
+  dplyr::select(iso3 = country, country = country_2, code = variable, name = variable_2, measure, year, units = unit_code, value) %>%
+  dplyr::filter(measure == "USD", # only pull estimates in USD for consistancy
+                iso3 != "OECD") # remove totals
+
+# Annoying, but the OECD classification scheme is a little more complicated and the type codes don't tell us anything about the classification scheme just by looking at them so we are going to manually assign more meaningful ones to make sure we're not double counting.
+oecd_types_table <- oecd_dat %>%
+  distinct(code, name)
+
+# Create blank lookup table
+oecd_lookup <- tibble(category = character(0),
+                                  category_name = character(0))
+
+# Categories
+categories <- enframe(
+  c("0" = "TRANSFERS TO INDIVIDUAL FISHERS - Non Budgetary",
+    "1" = "TRANSFERS TO INDIVIDUAL FISHERS - Budgetary",
+    "2" = "GENERAL SERVICE SUPPORT ESTIMATE",
+    "3" = "COST RECOVERY CHARGES"), name = "category", value = "category_name")
+
+oecd_lookup <- oecd_lookup %>%
+  bind_rows(categories)
+
+# Non budgetary transfers to individual fishers
+types <- enframe(
+  c("0A" = "Market price support",
+    "0B" = "Fuel tax concessions",
+    "1A" = "Transfers based on input use",
+    "1B" = "Transfers based on fishers income",
+    "1C" = "Transfers based on the reduction of productive capacity",
+    "1D" = "Miscellaneous transfers to fishers",
+    "2A" = "Access to other countries’ waters",
+    "2B" = "Provision of infrastructure",
+    "2C" = "Marketing and promotion",
+    "2D" = "Support to fishing communities",
+    "2E" = "Education and training",
+    "2F" = "Research and development",
+    "2G" = "Management of resources",
+    "2H" = "Miscellaneous transfers to general services",
+    "3A" = "Cost Recovery Charges, for resource access rights",
+    "3B" = "Cost Recovery Charges, for infrastructure access",
+    "3C" = "Cost Recovery Charges, for management, research and enforcement",
+    #"3-D" = "Resource rent taxes and charges", #doesn't appear in this data set?
+    "3E" = "Cost Recovery Charges, other"), name = "type", value = "type_name") %>%
+  mutate(category = str_replace(type, "[A-Z]", ""))
+
+oecd_lookup <- oecd_lookup %>%
+  left_join(types, by = "category")
+
+# Subtypes
+subtypes <- enframe(
+  c("1A-1" = "Transfers based on variable input use",
+    "1A-2" = "Transfers based on fixed capital formation",
+    "1B-1" = "Income support",
+    "1B-2" = "Special insurance system for fishers",
+    "2B-1" = "Capital expenditures",
+    "2B-2" = "Subsidized access to infrastructure",
+    "2G-1" = "Management expenditures",
+    "2G-2" = "Stock enhancement programs",
+    "2G-3" = "Enforcement expenditures"), name = "subtype", value = "subtype_name") %>%
+  mutate(type = str_replace(subtype, "-[^-]*$", ""))
+
+oecd_lookup <- oecd_lookup %>%
+  left_join(subtypes, by = "type")
+
+# Sub-subtypes
+ssubtypes <- enframe(
+  c("1A-2a" = "Support to vessel construction/purchase",
+    "1A-2b" = "Support to modernisation",
+    "1A-2c" = "Support to other fixed costs"), name = "ssubtype", "ssubtype_name") %>%
+  mutate(subtype = str_replace(ssubtype, "[a-z]$", ""))
+
+oecd_lookup <- oecd_lookup %>%
+  left_join(ssubtypes, by = "subtype")
+
+# Now rejoin to get a better sense of organization
+oecd_lookup <- oecd_lookup %>%
+  left_join(oecd_types_table, by = c("category_name" = "name")) %>%
+  rename(category_code = code) %>%
+  left_join(oecd_types_table, by = c("type_name" = "name")) %>%
+  rename(type_code = code) %>%
+  left_join(oecd_types_table, by = c("subtype_name" = "name")) %>%
+  rename(subtype_code = code) %>%
+  left_join(oecd_types_table, by = c("ssubtype_name" = "name")) %>%
+  rename(ssubtype_code = code) %>%
+  dplyr::select(category, category_code, category_name, type, type_code, type_name, subtype, subtype_code, subtype_name, ssubtype, ssubtype_code, ssubtype_name)
+
+write_csv(oecd_lookup, paste0(data_dir, "oecd-subsidies-classification.csv"))
+
+# Create variable for matching 
+oecd_matching <- oecd_lookup %>%
+  mutate(code_for_matching = case_when(!is.na(ssubtype_code) ~ ssubtype_code,
+                                       !is.na(subtype_code) ~ subtype_code,
+                                       !is.na(type_code) ~ type_code))
+
+# Add better descriptors back into data set
+oecd_dat_edit <- oecd_dat %>%
+  dplyr::select(-name) %>%
+  inner_join(oecd_matching, by = c("code" = "code_for_matching")) %>%
+  mutate(category_keep = case_when(category == "0" ~ "Non Budgetary Transfers",
+                                   category == "1" ~ "Budgetary Transfers",
+                                   category == "2" ~ "General Service Support",
+                                   category == "3" ~ "Cost Recovery Charges"),
+         type_keep = case_when(!is.na(ssubtype_code) ~ ssubtype,
+                               !is.na(subtype_code) ~ subtype,
+                               TRUE ~ type),
+         subtype_keep = case_when(!is.na(ssubtype_code) ~ ssubtype_name,
+                               !is.na(subtype_code) ~ subtype_name,
+                               TRUE ~ type_name)) %>%
+  dplyr::select(iso3, year, category = category_keep, type = type_keep, subtype = subtype_keep, value) %>%
+  mutate(units = paste0(year, " US$"),
+         source = "OECD")
+
+# Deal with the EU
+oecd_dat_eu <- oecd_dat_edit %>%
+  dplyr::filter(iso3 %in% c(eu_countries, eu_territories)) %>%
+  mutate(entity = "EU") %>%
+  group_by(entity, year, category, type, subtype, units, source) %>%
+  summarize(value = sum(value, na.rm = T)) %>%
+  rename(iso3 = entity) %>%
+  arrange(iso3, year, type)
+
+# Add EU back in 
+oecd_dat_edit <- oecd_dat_edit %>%
+  bind_rows(oecd_dat_eu)
+
+write_csv(oecd_dat_edit, paste0(data_dir, "oecd-subsidies-2009-2017-tidy.csv"))
+
+```

### 2020-03-11 app/00_initialize_app.R

@@ -23,65 +23,40 @@ widget_text <- read_csv("./text/00_widget_text.csv")
 ### Country/Territory Naming ---------
 ### ----------------------------------
 
-# Country ISO3 codes and English names for use throuhout
-country_names <- countrycode::codelist %>%
-  dplyr::select(country_iso3 = iso3c,
-                country_name = country.name.en,
-                eu = eu28) %>%
-  mutate(is_eu = case_when(eu == "EU" ~ T,
-                           TRUE ~ F)) %>%
-  dplyr::filter(!is.na(country_iso3)) %>%
-  dplyr::select(-eu)
+# Load list of WTO Member states and their dependencies with chosen display names
+country_lookup <- read_csv("./data/country_lookup.csv") %>%
+  mutate(display_name = case_when(!is.na(WTO_name) ~ WTO_name,
+                                  TRUE ~ countrycode(iso3, "iso3c", "country.name"))) %>%
+  arrange(sovereign_iso3) 
 
-# Add EU aggregate
-country_names <- tibble(country_iso3 = "EU", country_name = "European Union", is_eu = T) %>%
-  bind_rows(country_names)
-
-# Manual corrections to some names to comply with WTO standards
-country_names$country_name[country_names$country_iso3 == "TWN"] <- "Chinese Taipei"
-
-# Vector of all countries for use in the app
-country_choices <- country_names$country_iso3
-names(country_choices) <- country_names$country_name
-
-# Get data frame with all relevant country dependancies
-country_dependencies <- read_csv("./data/country_dependencies.csv") %>%
-  mutate(states = str_split(states, pattern = ", "))
+# Vector of all WTO Members and Observers for use in the app
+wto_members_and_observers <- country_lookup$iso3[country_lookup$WTO_member_status %in% c("Member", "Observer")]
+names(wto_members_and_observers) <- country_lookup$display_name[country_lookup$WTO_member_status %in% c("Member", "Observer")]
 
 # EU states
-eu_countries <- unlist(country_dependencies$states[country_dependencies$entity == "eu_countries"])
+eu_countries <- country_lookup$iso3[country_lookup$iso3 != "EU" & country_lookup$is_EU]
 
 # List of all EU overseas territories - vessels flagged here should be considered WTO Members
[…]

### 2020-03-11 app/server.R

@@ -145,7 +145,6 @@ shinyServer(function(input, output, session) {
     }
   )
   
-  
   ### -------------------------
   ### 04a. global-subsidies ---
   ### -------------------------
@@ -162,9 +161,129 @@ shinyServer(function(input, output, session) {
     updateTabItems(session, "menu_items", "introduction")
   })
   
-  ### Leaflet map: Global map of fisheries subsidies with hover boxes ---------------------
+  ### Update selectInput: Only allow for selection of subsidy types from selected category ---------------------
+  observe({
+    
+    # Only allow types from the selected category to be chosen
+    new_choices <- subsidy_classification_sumaila$type[subsidy_classification_sumaila$category == input$w_global_subsidies_category]
+    names(new_choices) <- subsidy_classification_sumaila$type_name[subsidy_classification_sumaila$category == input$w_global_subsidies_category]
+    
+    # Update input
+    updateSelectizeInput(session, 
+                         "w_global_subsidies_types",
+                         choices = new_choices,
+                         selected = new_choices[1])
+  })
   
-  # output$global_subsidies_map <- renderLeaflet({})
+  
+  ### Leaflet map: Global map of fisheries subsidies with hover boxes ---------------------
+
+  output$global_subsidies_map <- renderLeaflet({
+    
+    req(input$w_global_subsidies_category)
+    req(input$w_global_subsidies_types)
+    
+    # Color palette to use based off selected input
+    global_subsidies_map_color <- switch(input$w_global_subsidies_category,
+                                         "Beneficial" = list("Blues", 1, 7.3e9),
+                                         "Capacity-enhancing" = list("Reds", 1, 7.3e9),
+                                         "Ambiguous" = list("Purples", 1, 7.3e9))
+    
+    global_subsidies_map_pal <- colorNumeric(palette = global_subsidies_map_color[[1]],
+                                             log10(c(global_subsidies_map_color[[2]], global_subsidies_map_color[[3]])))
+    
+    # Filter data
+    global_subsidies_map_dat <- subsidy_dat_sumaila %>%
+      dplyr::filter(type %in% c(input$w_global_subsidies_types)) %>%
+      group_by(display_name, iso3, category, type, type_name, units, source) %>%
+      summarize(value = sum(value, na.rm = T)) %>%
+      dplyr::filter(!is.na(value) & value > 0) %>%
+      group_by(iso3, display_name) %>%
[…]

### 2020-03-11 app/ui.R

@@ -29,6 +29,12 @@ library(sf) # shapefiles
 library(DT) # interactive data tables
 library(tidyverse) # workhorse data manipulation
 
+# Plotting
+library(leaflet) # interactive maps 
+library(plotly) # interactive charts
+library(viridis) # colorblind color scales
+library(RColorBrewer) # other color scales
+
 # The content for each tab is stored in a separate file. Source all .R files in the current directory that start with "ui_":  
 sapply(list.files(
     pattern = "^ui_.*\\.R$",
@@ -199,12 +205,12 @@ shinyUI(
                 ### About fisheries subsidies ---
                 # About fisheries subsidies - Item #1 - Global subsidy map
                 tabItem(tabName = "global-subsidies",
-                        GlobalSubsidies()
+                        GlobalSubsidies(subsidy_categories_sorted_sumaila, subsidy_types_sorted_sumaila)
                 ),
                 
                 # About fisheries subsidies - Item #2 - Fishery statistics by state
                 tabItem(tabName = "country-fishery-stats",
-                        CountryFisheryStats(country_choices)
+                        CountryFisheryStats(wto_members_and_observers)
                 ),
                 
                 # About fisheries subsidies - Item #3 - Compare fishery statistics

### 2020-03-11 app/ui_02b_edit_policies.R

@@ -304,7 +304,9 @@ column(12,
                                                   
                                                 ) # /fluidRow - IUU
                                                 
-                                         ), # /column - IUU manual options
+                                         ) # /box - IUU manual options
+                                         
+                                         ), # /column 12 - IUU manual options
                                          
                                          # # Collapsable box with more info
                                          # column(12, style = "padding: 0px 25px 15px; align: 'center';",

### 2020-03-11 app/ui_04a_global_subsidies.R

@@ -5,7 +5,7 @@
 ### This script contains the content for the global-subsidies tab
 ### --------------------------------------------------------------------
 
-GlobalSubsidies = function() 
+GlobalSubsidies = function(subsidy_categories_sorted_sumaila, subsidy_types_sorted_sumaila) 
   fluidPage(
     
     # Page style
@@ -35,31 +35,43 @@ GlobalSubsidies = function()
            # Text
            includeHTML("./text/04a_global_subsidies_intro.html"),
            
-           # Select subsidy type(s) to plot (change choices back to "subsidy_types_all")
-           selectizeInput("w_global_subsidies_included_subsidy_types",
-                          label = tagList(tags$b(" Subsidy type(s) to include:    "),
-                                          # Info button
-                                          tags$button(id = "info_subsidy_type_to_plot",
-                                                      class = "btn action-button info-button",
-                                                      icon("info"))),
-                          
-                          choices = c("choice1" = "B1", "choice2" = "B2", "etc" = "B3"),
-                          selected = 'B1',
-                          width = "100%",
-                          multiple = T)
-           
+           fluidRow(
+             
+             # Select category of subsidies to plot
+             column(6, style = "padding: 0 12.5px 0 0;",
+                    
+                    selectInput("w_global_subsidies_category",
+                                label = tags$b("Subsidy category: "),
+                                choices = subsidy_categories_sorted_sumaila,
+                                selected = "Capacity-enhancing",
+                                width = "100%")
+             ),
+             
+             # Select subsidy type(s) within selected category to plot
+             column(6, style = "padding: 0 0 0 12.5px;",
+                    
+                    selectizeInput("w_global_subsidies_types",
+                                   label = tagList(tags$b(" Subsidy type(s) to include:    "),
+                                                   # Info button
+                                                   tags$button(id = "info_subsidy_type_to_plot",
+                                                               class = "btn action-button info-button",
+                                                               icon("info"))),
+                                   
+                                   choices = subsidy_types_sorted_sumaila,
+                                   width = "100%",
+                                   multiple = T)
+             )
+           )
            
     ),
     
-    ### Global subsidies map (PLACEHOLDER - change back to leaflet object)
+    ### Global subsidies map
     column(12, style = "padding: 10px 0;",
            
            
            # Leaflet map
-           #leafletOutput('global_subsidies_map', width = "auto", height = "70vh")
-           
-           # Temp image
[…]

### 2020-03-11 app/ui_04b_country_fishery_stats.R

@@ -5,7 +5,7 @@
 ### This script contains the content for the country-fishery-stats tab
 ### --------------------------------------------------------------------
 
-CountryFisheryStats = function(country_choices) 
+CountryFisheryStats = function(wto_members_and_observers) 
   fluidPage(
     
     # Page style
@@ -53,7 +53,7 @@ CountryFisheryStats = function(country_choices)
                                                       icon("info")
                                           )
                           ), 
-                          choices = country_choices,
+                          choices = wto_members_and_observers,
                           selected = NULL,
                           width = "50%",
                           options = list(placeholder = 'Select...')

### 2020-03-11 app/server.R
fixing map quirks

@@ -185,9 +185,9 @@ shinyServer(function(input, output, session) {
     
     # Color palette to use based off selected input
     global_subsidies_map_color <- switch(input$w_global_subsidies_category,
-                                         "Beneficial" = list("Blues", 1, 7.3e9),
-                                         "Capacity-enhancing" = list("Reds", 1, 7.3e9),
-                                         "Ambiguous" = list("Purples", 1, 7.3e9))
+                                         "Beneficial" = list("Blues", 1, 2.2e9),
+                                         "Capacity-enhancing" = list("Reds", 1, 6e9),
+                                         "Ambiguous" = list("Purples", 1, 1e9))
     
     global_subsidies_map_pal <- colorNumeric(palette = global_subsidies_map_color[[1]],
                                              log10(c(global_subsidies_map_color[[2]], global_subsidies_map_color[[3]])))
@@ -195,12 +195,14 @@ shinyServer(function(input, output, session) {
     # Filter data
     global_subsidies_map_dat <- subsidy_dat_sumaila %>%
       dplyr::filter(type %in% c(input$w_global_subsidies_types)) %>%
-      group_by(display_name, iso3, category, type, type_name, units, source) %>%
-      summarize(value = sum(value, na.rm = T)) %>%
       dplyr::filter(!is.na(value) & value > 0) %>%
+      group_by(iso3, display_name, category, type, type_name) %>%
+      summarize(value = sum(value, na.rm = T)) %>%
       group_by(iso3, display_name) %>%
       mutate(included_types = paste0(type_name[type_name != "Total"], collapse = ";</br>")) %>%
-      ungroup()
+      ungroup() %>%
+      group_by(iso3, display_name, category, included_types) %>%
+      summarize(value = sum(value, na.rm = T))
       
     # Join to world polygons
     global_subsidies_map_dat_shp <- world %>%

### 2020-03-11 scripts/00_data_wrangling.Rmd
oecd data update

--- 2020-03-10 scripts/00_data_wrangling.Rmd
@@
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+# Note: Political entities, dependencies, and naming
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+The naming of flag and coastal states varies widely across our data sources and we recognize that this can be a politially sensitive matter.
+For the purposes of merging multiple data sources, we therefore translate all state names from the raw data sources to ISO-3 character codes.
+Country names are only used for display purposes, and the use of any particular name is not meant to convey any options regarding sovereignty on behalf of the authors.
 
-```{r cars}
-summary(cars)
+```{r}
+# Load country dependencies helper file
+country_dependencies <- read_csv(here::here("data", "lookup-tables", "country_dependencies.csv"))
+
+# EU countries
+eu_countries <- country_dependencies$iso3[country_dependencies$is_EU]
+eu_country_names <- sort(countrycode(eu_countries, "iso3c", "country.name"))
+
+# EU overseas territories
+eu_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 %in% eu_countries]
+eu_territory_names <- sort(c(countrycode(eu_territories, "iso3c", "country.name"), "Ascension Island", "Tristan da Cunha"))
+
+# US overseas territories:  American Samoa, Guam, Northern Marianas Islands, Puerto Rico, US Virgin Islands
+us_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "USA"]
+us_territory_names <- sort(countrycode(us_territories, "iso3c", "country.name"))
 ```
 
-## Including Plots
+Additionally, it is important to note that the European Union as a political entity is a Member of the World Trade Organization, rather then the individual states that make up the European Union.
+We therefore need to create a profile for the European Union as a whole.
+The following `r length(eu_country_names)` states are considered to be part of the European Union for the purposes of this analysis: `r paste(eu_country_names, collapse = ", ")`.
 
-You can also embed plots, for example:
+The Netherlands, France, Denmark, and the United Kingdom also have overseas dependencies that should be considered to be a part of the European Union for statistical purposes.
+The following overseas dependencies are also considered to be a part of the European Union for the purpose of aggregating data in this analysis: `r paste(eu_territory_names, collapse = ", ")`.
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+Outside of the EU, the only other dependencies we need to worry about are those that relate to the United States.
+The following overseas dependencies are considered to be a part of the United States for the purpose of aggregating data in this analysis: `r paste(us_territory_names, collapse = ", ")`.
+
+# Section 1 - Subsidies Data
+
+## Updated estimates and analysis of global fisheries subsidies from Sumaila et al. (2019)
+
+```{r}
+### Data Wrangling
+# Load and wrangle 2019 data
+sumaila_2019_dat <- read_xlsx(sumaila_subsidies_path) %>%
+  clean_names(case = "snake") %>%
+  mutate(iso3 = case_when(country == "Dominican Rp" ~ "DOM",
+                          country == "Micronesia" ~ "FSM",
+                          country == "Untd Arab Em" ~ "ARE",
+                          TRUE ~ countrycode(country, "country.name", "iso3c"))) %>%
+  dplyr::select(iso3, type = class, data_type, value = constant_2018_usd) %>%
+  mutate(year = 2018,
+         units = "2018 US$",
+         source = "Sumaila et al. (2019)") %>%
+  arrange(iso3)
+
+# Load lookup table for classification scheme
+sumaila_lookup <- read_csv(here::here("data", "lookup-tables", "sumaila_subsidies_classification_lookup_table.csv"))
+
+# Clean up the naming/spelling of the classification scheme as well as data type
+sumaila_2019_dat_edit <- sumaila_2019_dat %>%
+  left_join(sumaila_lookup, by = "type") %>%
+  dplyr::select(iso3, year, category, category_name, type, type_name, value, data_type, units, source)
+
+sumaila_2019_dat_edit$data_type[sumaila_2019_dat_edit$data_type == "not found evidence of subsidy"] <- "Found no evidence of subsidy"
+
+# Deal with the EU
+sumaila_2019_dat_eu <- sumaila_2019_dat_edit %>%
+  dplyr::filter(iso3 %in% c(eu_countries, eu_territories)) %>%
+  mutate(entity = "EU",
+         data_type = "Aggregate") %>%
+  group_by(entity, year, category, category_name, type, type_name, data_type, units, source) %>%
+  summarize(value = sum(value, na.rm = T)) %>%
+  rename(iso3 = entity)
+
+# Add the EU back in
+sumaila_2019_dat_edit <- sumaila_2019_dat_edit %>%
+  bind_rows(sumaila_2019_dat_eu)
+
+# Save
+write_csv(sumaila_2019_dat_edit, paste0(data_dir, "sumaila_et_al_2019_subsidies_tidy.csv"))
+write_csv(sumaila_2019_dat_edit, paste0(app_data_dir, "sumaila_et_al_2019_subsidies_tidy.csv"))
+
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+## Estimates of fisheries support provision by state from the OECD (2008 - 2018)
+
+```{r}
+# Load and wrangle OECD data (2009 - 2017)
+oecd_fse_dat <- read_csv(oecd_fse_path) %>%
+  clean_names(case = "snake") %>%
+  dplyr::filter(measure == "USD", # only pull estimates in USD for consistancy
+                country != "OECD") %>% # remove totals
+  dplyr::select(iso3 = country, code = variable, year, value)
+
+# Load OECD lookup table
+oecd_fse_lookup <- read_csv(here::here("data", "lookup-tables", "oecd_fse_classification_lookup_table.csv")) %>%
+  distinct(category, category_name, type, type_code, type_name)
+
+# # Create variable for matching 
+# oecd_matching <- oecd_lookup %>%
+#   mutate(code_for_matching = case_when(!is.na(ssubtype_code) ~ ssubtype_code,
+#                                        !is.na(subtype_code) ~ subtype_code,
+#                                        !is.na(type_code) ~ type_code))
+
+# Match based on type - that should be plenty for the figure on SubsidyExplorer
+oecd_fse_dat_edit <- oecd_fse_dat %>%
+  inner_join(oecd_fse_lookup, by = c("code" = "type_code")) %>%
+  mutate(data_type = "Reported",
+         units = paste0(year, " US$"),
+         source = "OECD FSE database") %>%
+  dplyr::select(iso3, year, category, category_name, type, type_name, data_type, units, source, value)
+
+# Deal with the EU
+oecd_fse_dat_eu <- oecd_fse_dat_edit %>%
+  dplyr::filter(iso3 %in% c(eu_countries, eu_territories)) %>%
+  mutate(entity = "EU",
+         data_type = "Aggregate") %>%
+  group_by(entity, year, category, category_name, type, type_name, data_type, units, source) %>%
+  summarize(value = sum(value, na.rm = T)) %>%
+  rename(iso3 = entity) %>%
+  arrange(iso3, year, type)
+
+# Add EU back in 
+oecd_fse_dat_edit <- oecd_fse_dat_edit %>%
+  bind_rows(oecd_fse_dat_eu)
+
+# Save
+write_csv(oecd_fse_dat_edit, paste0(data_dir, "oecd_2019_fse_tidy.csv"))
+write_csv(oecd_fse_dat_edit, paste0(app_data_dir, "oecd_2019_fse_tidy.csv"))
+
+```

### 2020-03-11 data/lookup-tables/oecd_fse_classification_lookup_table.R

@@ -1,0 +1,119 @@
+########################################################
+#
+# Create a lookup table for the OECD FSE data
+# The heiarchy of support types is somewhat complicated and not logical, therefore we need a lookup table
+#
+########################################################
+
+library(janitor)
+library(here)
+library(stringr)
+library(tidyverse)
+
+# Directories for the output file
+output_dir <- here::here("data", "lookup-tables/")
+if (dir.exists(output_dir) == F) {
+  dir.create(output_dir, recursive = T)
+}
+
+# Where is the raw OECD FSE data stored? 
+oecd_fse_path <- here::here("data", "raw", "OECD-2019-fse", "FISH_FSE_10032020183349581.csv")
+
+# Load and wrangle OECD data (2009 - 2017)
+oecd_fse_dat <- read_csv(oecd_fse_path) %>%
+  clean_names(case = "snake") %>%
+  dplyr::select(iso3 = country, country = country_2, code = variable, name = variable_2, measure, year, units = unit_code, value) %>%
+  dplyr::filter(measure == "USD", # only pull estimates in USD for consistancy
+                iso3 != "OECD") # remove totals
+
+# Annoying, but the OECD classification scheme is a little more complicated and the type codes don't tell us anything about the classification scheme just by looking at them so we are going to manually assign more meaningful ones to make sure we're not double counting. 
+oecd_types_table <- oecd_fse_dat %>%
+  distinct(code, name) 
+
+# Create blank lookup table
+oecd_lookup <- tibble(category = character(0),
+                      category_name = character(0))
+
+# Categories
+categories <- enframe(
+  c("0" = "TRANSFERS TO INDIVIDUAL FISHERS - Non Budgetary",
+    "1" = "TRANSFERS TO INDIVIDUAL FISHERS - Budgetary",
+    "2" = "GENERAL SERVICE SUPPORT ESTIMATE",
+    "3" = "COST RECOVERY CHARGES"), name = "category", value = "category_name")
+
+oecd_lookup <- oecd_lookup %>%
+  bind_rows(categories)
+
+# Non budgetary transfers to individual fishers
+types <- enframe(
+  c("0A" = "Market price support",
+    "0B" = "Fuel tax concessions",
+    "1A" = "Transfers based on input use",
+    "1B" = "Transfers based on fishers income",
[…]

### 2020-03-11 data/lookup-tables/sumaila_subsidies_classification_lookup_table.R

@@ -1,0 +1,53 @@
+########################################################
+#
+# Create a lookup table for the Sumaila et al. (2019) data
+# The heiarchy is pretty simple, but we generate this to clean up some of the names
+#
+########################################################
+
+library(janitor)
+library(here)
+library(stringr)
+library(readxl)
+library(tidyverse)
+
+# Directories for the output file
+output_dir <- here::here("data", "lookup-tables/")
+if (dir.exists(output_dir) == F) {
+  dir.create(output_dir, recursive = T)
+}
+
+# Where is the raw OECD FSE data stored? 
+sumaila_subsidies_path <- here::here("data", "raw", "Sumaila-et-al-2019-subsidies", "Subsidies_PEW_Final.xlsx")
+
+# Load and wrangle 2019 data
+sumaila_2019_dat <- read_xlsx(sumaila_subsidies_path) %>%
+  clean_names(case = "snake") %>%
+  rename(type = class, type_name = type, category_name = category) %>%
+  mutate(category = str_replace(type, "[0-9]", ""))
+
+# Annoying, but we want to clean up some of the spelling of Sumaila's subsidy types
+sumaila_types_table <- sumaila_2019_dat %>%
+  distinct(category, category_name, type, type_name) 
+
+# Lookup table
+sumaila_lookup <- sumaila_types_table
+
+# New spellings
+sumaila_lookup$type_name[sumaila_lookup$type == "A1"] <- "Fisheries management"
+sumaila_lookup$type_name[sumaila_lookup$type == "A2"] <- "Fishery research and development"
+sumaila_lookup$type_name[sumaila_lookup$type == "A3"] <- "Marine protected areas"
+sumaila_lookup$type_name[sumaila_lookup$type == "B1"] <- "Boat construction and renovation"
+sumaila_lookup$type_name[sumaila_lookup$type == "B2"] <- "Fisheries development projects"
+sumaila_lookup$type_name[sumaila_lookup$type == "B3"] <- "Fishing port development"
+sumaila_lookup$type_name[sumaila_lookup$type == "B4"] <- "Marketing and storage infrastructure"
+sumaila_lookup$type_name[sumaila_lookup$type == "B5"] <- "Non-fuel tax exemption"
+sumaila_lookup$type_name[sumaila_lookup$type == "B6"] <- "Fishing access agreements"
[…]

### 2020-03-13 scripts/01_data_wrangling.Rmd
moving all data and analysis over to this repo

--- 2020-03-11 scripts/00_data_wrangling.Rmd
@@
 
-```{r setup, include=FALSE}
+```{r}
+# Packages
 library(knitr) 
 library(countrycode) # country name matching
+library(here)
 library(WDI) # World Bank GDP and population numbers by country
@@
 library(readxl)
-```
 
-```{r}
-# Code options
-knitr::opts_chunk$set(echo = FALSE, error = FALSE, message = FALSE, warning = F)
+# Code chunk defaults
+knitr::opts_chunk$set(echo = FALSE, error = FALSE, message = FALSE, warning = FALSE, include = FALSE)
+
+# Source helper file
+source(here::here("scripts", "00_helpers.R"))
 
@@
 
-results_dir <- here::here("results", "00-data-wrangling/")
+results_dir <- here::here("results", "01-data-wrangling/")
 if (dir.exists(results_dir) == F) {
@@
 }
-
 ```
 
-# Introduction
+# Description
 
-This script handles the preliminary data wrangling for the raw datasets underlying the SubsidyExplorer toolkit. It outputs tidyed data files to `r data_dir`.
-
-It also creates and outputs four aggregated CSV files that are used as input data by the SubsidyExplorer toolkit (saved to `r app_data_dir`): 
-- subsidies-2009-2018-tidy.csv
-- demographic-2000-2018-tidy.csv
-- fisheries-2000-2017.csv
-- fao-landings-group-2000-2017.csv
-
-Summary figures are exported to `r results_dir`.
+This script handles the preliminary data wrangling for the raw datasets underlying the SubsidyExplorer analysis.
+It outputs tidyed data files to `r data_dir`.
+Some of these tidied data files are used directly as input data by the SubsidyExplorer toolkit (saved to `r app_data_dir`).
 
@@
 
-# Paths to misc data files 
+# Paths to fisheries mgmt files 
 costello_upsides_path <- here::here("data", "raw", "Costello-et-al-2016-upsides", "ProjectionData_2012.csv")
+melnychuk_fmi_path <- here::here("data", "raw", "Melnychuk-et-al-2017-fmi", )
+ram_sadb_path <- here::here("data", "raw", "RAM-2018-stock-assessment-database", "RLSADB v4.40", "DB Files With Assessment Data", "RLSADB v4.40 (assessment data only).xlsx")
+anderson_fpi_path <- here::here("data", "raw", "Anderson-et-al-")
+
+# Paths to other files
 iuu_vessel_path <- here::here("data", "raw", "IUU-Vessel-List-2019", "IUUList-20190430.csv")
-ram_sadb_path <- here::here("data", "raw", "RAM-2018-stock-assessment-database", "RLSADB v4.40", "DB Files With Assessment Data", "RLSADB v4.40 (assessment data only).xlsx")
 ```
@@
 
-# # Create variable for matching 
-# oecd_matching <- oecd_lookup %>%
-#   mutate(code_for_matching = case_when(!is.na(ssubtype_code) ~ ssubtype_code,
-#                                        !is.na(subtype_code) ~ subtype_code,
-#                                        !is.na(type_code) ~ type_code))
-
 # Match based on type - that should be plenty for the figure on SubsidyExplorer

### 2020-03-13 scripts/00_helpers.R

@@ -1,0 +1,6 @@
+
+### -----------------------------------------------------------------
+### This script contains helpers for the SubsidyExplorer analysis  
+### Last updated on January 23, 2020
+### -----------------------------------------------------------------
+

### 2020-03-13 scripts/01_data_wrangling.Rmd
demographic data done

@@
 costello_upsides_path <- here::here("data", "raw", "Costello-et-al-2016-upsides", "ProjectionData_2012.csv")
-melnychuk_fmi_path <- here::here("data", "raw", "Melnychuk-et-al-2017-fmi", )
+melnychuk_fmi_path <- here::here("data", "raw", "Melnychuk-et-al-2017-fmi", "fmi_values_country.csv")
 ram_sadb_path <- here::here("data", "raw", "RAM-2018-stock-assessment-database", "RLSADB v4.40", "DB Files With Assessment Data", "RLSADB v4.40 (assessment data only).xlsx")
-anderson_fpi_path <- here::here("data", "raw", "Anderson-et-al-")
+anderson_fpi_path <- here::here("data", "raw", "Anderson-et-al-2015-fpi", "fpi_values_fishery.csv")
 
@@
 
+**Subsidy Data**
 Estimates of annual fisheries subsidies provision by state from Sumaila et al.
@@
 
-Total GDP and population by state from the World Bank's World Development Indicators Database (2000 - 2018).
+**Demographic Data**
+Total GDP, GDP from fisheries, forestry, and agriculture, and population by state from the World Bank's World Development Indicators Database (2000 - 2018).
 These data were accessed through the `WDI` package.
@@
 
+**Fisheries Data**
 Fisheries landings in 2017 from the FAO Global Capture Production database (2019) and estimates of landed value generated using the ex-vessel price database created by Melnychuk et al.
@@
 > FAO (2019). FAO yearbook. Fishery and Aquaculture Statistics 2017, http://www.fao.org/fishery/statistics/global-capture-production/en (accessed on 24 October 2019).
+
+Estimated landed price 
 > Melnychuk, M.
@@
 https://doi.org/10.1093/icesjms/fsw169
+
+Stock status database
+> Costello, C., Ovando, D., Clavelle, T., Strauss, C.
+K., Hilborn, R., Melnychuk, M.
+C., Branch, T.
+A., Gaines, S.
+D., Szuwalski, C.
+S., Cabral, R.
+B., Rader, D.
+N., & Leland, A.
+(2016).
+Global fishery prospects under contrasting management regimes.
+Proceedings of the National Academy of Sciences, 113(18), 5125–5129.
+https://doi.org/10.1073/pnas.1520420113
+
+Fisheries management indicators
+> Melnychuk, M.
+C., Peterson, E., Elliott, M., & Hilborn, R.
+(2017).
+Fisheries management impacts on target species status.
+Proceedings of the National Academy of Sciences, 114(1), 178–183.
+https://doi.org/10.1073/pnas.1609915114
+
+RAM Stock assessment database
+> RAM Legacy Stock Assessment Database. (2018). Version 4.44-assessment-only. Released 2018-12-22. DOI:10.5281/zenodo.2542919
+
+Fisheries performance indicators
+> Anderson, J.
+L., Anderson, C.
+M., Chu, J., Meredith, J., Asche, F., Sylvia, G., Smith, M.
+D., Anggraeni, D., Arthur, R., Guttormsen, A., McCluney, J.
+K., Ward, T., Akpalu, W., Eggert, H., Flores, J., Freeman, M.
+A., Holland, D.
+S., Knapp, G., Kobayashi, M., … Valderrama, D.
+(2015).
+The Fishery Performance Indicators: A Management Tool for Triple Bottom Line Outcomes.
+PLOS ONE, 10(5), e0122809.
+https://doi.org/10.1371/journal.pone.0122809
+
+IUU Consolidated vessel list
+> NEED
 
@@
 # Section 1 - Subsidies Data
+
+For the two datasets in this section, we'll export tidied versions individually for use in SubsidyExplorer.
 
@@
 sumaila_2019_dat_edit <- sumaila_2019_dat_edit %>%
-  bind_rows(sumaila_2019_dat_eu)
+  bind_rows(sumaila_2019_dat_eu) %>%
+  mutate(variable = "subsidies_Sumaila")
 
@@
 oecd_fse_dat_edit <- oecd_fse_dat_edit %>%
-  bind_rows(oecd_fse_dat_eu)
+  bind_rows(oecd_fse_dat_eu) %>%
+  mutate(variable = "subsidies_OECD")
 
@@
 ```
+
+# Section 2 - Demographic Data
+
+For the four datasets in this section, we'll export a single aggregated demographic dataset for use in SubsidyExplorer.
+
+## Demographic statistics by state from the World Bank's World Development Indicators Database (2000 - 2018)
+
+```{r}
+# Load data using WDI package
+wb_demo_dat <- WDI(country = "all",
+                   indicator = c("gdp" = "NY.GDP.MKTP.CD",
+                                 "gdp_ffa" = "NV.AGR.TOTL.CD",
+                                 "population" = "SP.POP.TOTL"),
+                                  start = 2000,
+                                  end = 2018,
+                                  extra = TRUE) %>%
+  dplyr::filter(region != "Aggregates") %>%
+  dplyr::select(iso3 = iso3c,
+                year,
+                gdp,
+                gdp_ffa,
+                population) %>%
+  mutate(iso3 = as.character(iso3)) %>%
+  arrange(iso3, year) %>%
+  gather(variable, value, c("gdp", "gdp_ffa", "population")) %>%
+  dplyr::filter(!is.na(value)) %>%
+  mutate(units = case_when(variable == "population" ~ "individuals",
+                           TRUE ~ paste0(year, " US$")),
+         source = "World Bank WDI database")
+
+# Deal with the EU + territories
+wb_dat_eu <- wb_demo_dat %>%
+  dplyr::filter(iso3 %in% c(eu_countries, eu_territories)) %>%
+  mutate(entity = "EU") %>%
+  group_by(entity, year, variable, units, source) %>%
+  summarize(value = sum(value, na.rm = T)) %>%
+  rename(iso3 = entity) %>%
+  arrange(iso3, year, variable)
+
+# Deal with the US + territories
+wb_dat_us <- wb_demo_dat %>%
+  dplyr::filter(iso3 %in% c(us_territories, "USA")) %>%
+  mutate(entity = "USA") %>%
+  group_by(entity, year, variable, units, source) %>%
+  summarize(value = sum(value, na.rm = T)) %>%
+  rename(iso3 = entity) %>%
+  arrange(iso3, year, variable)
+
+# Add back in
+wb_dat_edit <- wb_demo_dat %>%
+  dplyr::filter(iso3 != "USA") %>%
+  bind_rows(wb_dat_eu) %>%
+  bind_rows(wb_dat_us)
+
+# Export clean
+write_csv(wb_dat_edit, paste0(data_dir, "world_bank_2020_wdi_tidy.csv"))
+write_csv(wb_dat_edit, paste0(app_data_dir, "world_bank_2020_wdi_tidy.csv"))
+```
+
+## Total number of fishers by state from the FAO Yearbook of Fishery and Aquaculture Statistics (misc. years between 1995 and 2016)
+
+```{r}
+# Pull data and wrangle
+fao_fishers_dat <- read_csv(fao_fishers_path) %>%
+  mutate(iso3 = countrycode(country, "country.name", "iso3c")) %>%
+  dplyr::select(-country) %>%
+  gather(year, value, c('1995', '2000', '2005', '2010', '2011', '2012', '2013', '2014', '2015', '2016')) %>%
+  mutate(year = as.numeric(year)) %>%
+  dplyr::filter(!is.na(value)) %>%
+  mutate(variable = "fishers",
+         units = "individuals",
+         source = "FAO Yearbook of Fishery and Aquaculture Statistics (2017)")
+
+# Deal with EU
+fao_fishers_dat_eu <- fao_fishers_dat %>%
+  dplyr::filter(iso3 %in% c(eu_countries, eu_territories)) %>%
+  mutate(entity = "EU") %>%
+  group_by(entity, year, variable, units, source) %>%
+  summarize(value = sum(value, na.rm = T)) %>%
+  rename(iso3 = entity) %>%
+  arrange(iso3, year, variable)
+
+# Add EU back in 
+fao_fishers_dat_edit <- fao_fishers_dat %>%
+  bind_rows(fao_fishers_dat_eu) %>%
+  arrange(year, iso3)
+
+# Export clean
+write_csv(fao_fishers_dat_edit, paste0(data_dir, "fao_2017_yearbook_fishers_tidy.csv"))
+write_csv(fao_fishers_dat_edit, paste0(app_data_dir, "fao_2017_yearbook_fishers_tidy.csv"))
+```
+
+## Estimated number of full-time jobs in fisheries from Teh and Sumaila (2013) in 2003
+
+```{r}
+# Pull data and wrangle
+teh_fte_dat <- read_xlsx(teh_fte_path) %>%
+  clean_names(case = "snake") %>%
+  mutate(iso3 = case_when(country == "Dominican Rp" ~ "DOM",
+                          country == "Micronesia" ~ "FSM",
+                          country == "Untd Arab Em" ~ "ARE",
+                          TRUE ~ countrycode(country, "country.name", "iso3c"))) %>%
+  dplyr::select(-country) %>%
+  mutate(variable = "fishers_fte",
+         year = 2003,
+         units = "full-time equivalent jobs",
+         source = "Teh and Sumaila (2013)") %>%
+  dplyr::select(iso3, year, variable, value = total_fte, units, source)
+
+# Deal with EU
+teh_fte_dat_eu <- teh_fte_dat %>%
+  dplyr::filter(iso3 %in% c(eu_countries, eu_territories)) %>%
+  mutate(entity = "EU") %>%
+  group_by(entity, year, variable, units, source) %>%
+  summarize(value = sum(value, na.rm = T)) %>%
+  rename(iso3 = entity) %>%
+  arrange(iso3, year, variable)
+
+# Add EU back in 
+teh_fte_dat_edit <- teh_fte_dat %>%
+  bind_rows(teh_fte_dat_eu)
+
+# Export clean
+write_csv(teh_fte_dat_edit, paste0(data_dir, "teh_and_sumaila_2013_fte_tidy.csv"))
+write_csv(teh_fte_dat_edit, paste0(app_data_dir, "teh_and_sumaila_2013_fte_tidy.csv"))
+```

### 2020-03-13 app/00_initialize_app.R

@@ -65,17 +65,15 @@ world_small_countries <- world  %>%
 # ### Data ---------------
 # ### --------------------
 
-### SUBSIDIES -----------------------------------------------------------------------------------
+### SUBSIDY DATA -----------------------------------------------------------------------------------
 
 # 1) Subsidy estimates (Sumaila et al. 2019) ---
 subsidy_dat_sumaila_raw <- read_csv("./data/sumaila_et_al_2019_subsidies_tidy.csv") %>%
-  arrange(iso3) %>%
-  mutate(variable = "subsidies_Sumaila")
+  arrange(iso3)
 
 # 2) Subsidy estimates (OECD 2019) ---
 subsidy_dat_oecd_raw <- read_csv("./data/oecd_2019_fse_tidy.csv") %>%
   arrange(iso3) %>%
-  mutate(variable = "subsidies_OECD") %>%
   mutate(category = as.character(category)) %>%
   group_by(iso3, type) %>%
   dplyr::filter(year == max(year)) %>%
@@ -133,6 +131,25 @@ myColors <- c(goodColors, badColors, ambigColors, totColor, oecdColors)
 
 categoryColors <- c(goodColors[1], badColors[1], ambigColors[1])
 names(categoryColors) <- names(subsidy_categories_sorted_sumaila)
+
+### DEMOGRAPHIC DATA -----------------------------------------------------------------------------------
+
+# 1) GDP and Population (World Bank WDI database 2020) ---
+demo_dat_world_bank <- read_csv("./data/world_bank_2020_wdi_tidy.csv") %>%
+  arrange(iso3)
+
+# 2) Number of fishers (FAO Yearbook 2017) ---
+fisher_dat_fao <- read_csv("./data/fao_2017_yearbook_fishers_tidy.csv") %>%
+  arrange(iso3)
+
+# 3) Full-time fisheries employment (Teh and Sumaila 2013) ---
+fisher_dat_teh_and_sumaila <- read_csv("./data/teh_and_sumaila_2013_fte_tidy.csv") %>%
+  arrange(iso3)
+
+# Aggregate
+demographic_dat <- demo_dat_world_bank %>%
+  bind_rows(fisher_dat_fao) %>%
+  bind_rows(fisher_dat_teh_and_sumaila)
 
 # # 2) Country profiles ---
 # profile_dat_raw <- read.csv("./data/country-profiles-tidy.csv", stringsAsFactors = F)

### 2020-03-13 app/server.R

@@ -319,6 +319,8 @@ shinyServer(function(input, output, session) {
       dplyr::filter(iso3 == input$w_country_fishery_stats_selected_country)
     country_fishery_stats_subsidies_plot_dat$value[is.na(country_fishery_stats_subsidies_plot_dat$value)] <- 0
     
+    req(nrow(country_fishery_stats_subsidies_plot_dat) > 0)
+    
     # Make plot  
     country_fishery_stats_subsidies_plot <- ggplot()+
       geom_col(data = country_fishery_stats_subsidies_plot_dat, aes(x = source, y = value, fill = type_name, 
@@ -360,9 +362,208 @@ shinyServer(function(input, output, session) {
     
   })
   
-  
   ### Plotly figure: FAO Marine Capture Production ---------------------
   #[NEED]
+  
+  ### Plotly figure: World Bank Population ---------------------
+  output$country_fishery_stats_pop_plot <- renderPlotly({
+
+    req(input$w_country_fishery_stats_selected_country)
+
+    # Filter data
+    country_fishery_stats_pop_plot_dat <- demographic_dat %>%
+      dplyr::filter(iso3 == input$w_country_fishery_stats_selected_country) %>%
+      dplyr::filter(variable %in% c("population"))
+    
+    req(nrow(country_fishery_stats_pop_plot_dat) > 0)
+    req(all(is.na(country_fishery_stats_pop_plot_dat$value)) == F)
+
+    # Make plot
+    country_fishery_stats_pop_plot <- ggplot(country_fishery_stats_pop_plot_dat)+
+      aes(x = year, y = value/1e6)+
+      geom_line(color = '#3c8dbc')+
+      geom_point(aes(text = paste0("<b>","Year: ","</b>", year,
+                                          "<br>",
+                                          "<b>", "Population: ", "</b>", format(round(value,0), big.mark = ",", scientific = F))),
+                 alpha = 0, color = '#3c8dbc')+
+      scale_y_continuous(name = "Population (persons, millions)",
+                         labels = function(x) format(x, big.mark = ",", decimal.mark = ".", scientific = FALSE))+
+      scale_x_continuous(expand = c(0,0))+
+      theme_bw()+
+      labs(x = "Year")+
+      theme(legend.title = element_blank(),
+            legend.position = "none")
+
+    # Convert to plotly
+    gg <- ggplotly(country_fishery_stats_pop_plot, tooltip="text") %>%
+      style(
+        traces = 2,
[…]

### 2020-03-13 app/ui_04b_country_fishery_stats.R

@@ -70,9 +70,6 @@ CountryFisheryStats = function(wto_members_and_observers)
            #Fishery subsidies bar plot
            plotlyOutput("country_fishery_stats_subsidies_plot")
            
-           # # Temp image
-           # img(src = "/sample-images/04b_subsidy_plot_image.png", width = "100%")
-           
     ),
     
     ### Section 2: Capture fisheries production                                                     
@@ -87,6 +84,37 @@ CountryFisheryStats = function(wto_members_and_observers)
            # Temp image
            img(src = "/sample-images/04b_capture_production_plot_image.png", width = "100%")
            
+    ),
+    
+    ### Section 3: Demographics                                                  
+    column(12, style = "padding: 10px 25px;",
+           
+           # Header and text
+           includeHTML("./text/04b_country_fishery_stats_section3.html"),
+           
+           # Top row of demographic plots
+           fluidRow(
+             
+             column(6,
+                    # Population plot
+                    plotlyOutput("country_fishery_stats_pop_plot")
+             ),
+             
+             column(6,
+                    # Fishers plot
+                    plotlyOutput("country_fishery_stats_fisher_plot")
+                    
+             )
+           ),
+           
+           # Bottom row of demographic plots
+           fluidRow(
+             
+             column(12,
+                    # GDP plot
+                    plotlyOutput("country_fishery_stats_gdp_plot")
+             )
+           )
     ),
     
     ### Bottom navigation buttons

### 2020-03-13 app/00_initialize_app.R
text and widget cleaning

@@ -13,11 +13,13 @@
 ### Text ---------
 ### --------------
 
-button_text <- read_csv("./text/00_button_text.csv")
-
-tab_text <- read_csv("./text/00_tab_text.csv")
-
-widget_text <- read_csv("./text/00_widget_text.csv")
+text <- read_csv("./text/00_button_and_widget_text.csv")
+# 
+# button_text <- read_csv("./text/00_button_text.csv")
+# 
+# tab_text <- read_csv("./text/00_tab_text.csv")
+# 
+# widget_text <- read_csv("./text/00_widget_text.csv")
 
 ### ----------------------------------
 ### Country/Territory Naming ---------

### 2020-03-13 app/server.R

@@ -165,14 +165,23 @@ shinyServer(function(input, output, session) {
   observe({
     
     # Only allow types from the selected category to be chosen
+    if(input$w_global_subsidies_category == "All"){
+      
+    new_choices <- subsidy_classification_sumaila$type
+    names(new_choices) <- subsidy_classification_sumaila$type_name
+      
+    }else{
+      
     new_choices <- subsidy_classification_sumaila$type[subsidy_classification_sumaila$category == input$w_global_subsidies_category]
     names(new_choices) <- subsidy_classification_sumaila$type_name[subsidy_classification_sumaila$category == input$w_global_subsidies_category]
+    
+    }
     
     # Update input
     updateSelectizeInput(session, 
                          "w_global_subsidies_types",
                          choices = new_choices,
-                         selected = new_choices[1])
+                         selected = new_choices)
   })
   
   
@@ -185,6 +194,7 @@ shinyServer(function(input, output, session) {
     
     # Color palette to use based off selected input
     global_subsidies_map_color <- switch(input$w_global_subsidies_category,
+                                         "All" = list("YlOrRd", 1, 9.2e9),
                                          "A" = list("Blues", 1, 2.2e9),
                                          "B" = list("Reds", 1, 6e9),
                                          "C" = list("Purples", 1, 1e9))

### 2020-03-13 app/ui.R

@@ -77,7 +77,7 @@ shinyUI(
             tags$li(
                 class = "dropdown",
                 a(href = 'http://sfg.msi.ucsb.edu/',
-                  img(src = 'sfg-logo-white.png', title = "The Sustainable Fisheries Group", height = "40px"), 
+                  img(src = 'sfg-logo-white.png', title = text$item_label[text$item_id == "sfg_logo"], height = "40px"), 
                   style = "padding-top:10px; padding-bottom:10px;"
                   ) # /a
             ), # /tags$li
@@ -86,7 +86,7 @@ shinyUI(
             tags$li(
                 class = "dropdown",
                 a(href = 'http://emlab.msi.ucsb.edu/',
-                  img(src = 'emlab_logo_horizontal_w.png', title = "The Environmental Market Solutions Lab", height = "40px"), 
+                  img(src = 'emlab_logo_horizontal_w.png', title = text$item_label[text$item_id == "emlab_logo"], height = "40px"), 
                   style = "padding-top:10px; padding-bottom:10px;"
                 ) # /a
             ) # /tags$li
@@ -112,62 +112,62 @@ shinyUI(
                 id = "menu_items",
                 
                 ### Introduction ---
-                menuItem(tab_text$tab[tab_text$id == "introduction"], 
+                menuItem(text$item_label[text$item_id == "introduction"], 
                          tabName = "introduction", 
                          icon = NULL,
                          selected = TRUE),
                 
                 ### Explore results ---
-                menuItem(tab_text$tab[tab_text$id == "explore-results"],
+                menuItem("",
                          icon = NULL,
                          
                          # Explore results - Item #1 - Selected results
-                         menuSubItem(tab_text$tab[tab_text$id == "selected-results"],
+                         menuSubItem(text$item_label[text$item_id == "selected-results"],
                                      tabName = 'selected-results',
                                      icon = NULL),
                                   
                          # Explore results - Item #2 - Edit policies and view those results
-                         menuSubItem(tab_text$tab[tab_text$id == "edit-policies"],
+                         menuSubItem(text$item_label[text$item_id == "edit-policies"],
                                      tabName = 'edit-policies',
                                      icon = NULL)
                          
                 ), 
                 
                 ### About methods and process ---
-                menuItem(tab_text$tab[tab_text$id == "methods-process"], 
+                menuItem(text$item_label[text$item_id == "methods-process"], 
                          icon = NULL,
                          tabName = "methods-process"
                          
                 ),
                 
                 ### About fisheries subsidies ---
[…]

### 2020-03-13 app/ui_01_introduction.R

@@ -33,14 +33,6 @@ Introduction = function()
                                
                                includeHTML("./text/01_introduction_intro.html")
                                
-                               # tags$h3("An ambitious agreement on fisheries subsidy reform at the WTO could result in increases of up to"),
-                               # tags$h1("XX% in global fish biomass"),
-                               # tags$h4("and"),
-                               # tags$h1("XX% in global fish catch"),
-                               # 
-                               # tags$h3("Subsidy reform represents one of the most beneficial actions we can take to restore our world’s oceans.")
-                               
-                               
                       ),
                       
                       # Buttons
@@ -50,21 +42,21 @@ Introduction = function()
                              tags$div(class = "picture-overlay-button-wrapper-l",
                                       
                                       actionButton("ab_introduction_to_selected_results",
-                                                   tags$h4(button_text$text[button_text$id == "ab_introduction_to_selected_results"]))
+                                                   tags$h4(text$item_label[text$item_id == "ab_introduction_to_selected_results"]))
 
                              ),
                              
                              tags$div(class = "picture-overlay-button-wrapper-c",
                                       
                                       actionButton("ab_introduction_to_methods_process",
-                                                   tags$h4(button_text$text[button_text$id == "ab_introduction_to_methods_process"]))
+                                                   tags$h4(text$item_label[text$item_id == "ab_introduction_to_methods_process"]))
                                       
                              ),
                              
                              tags$div(class = "picture-overlay-button-wrapper-r",
                                       
                                       actionButton("ab_introduction_to_global_subsidies",
-                                                   tags$h4(button_text$text[button_text$id == "ab_introduction_to_global_subsidies"]))
+                                                   tags$h4(text$item_label[text$item_id == "ab_introduction_to_global_subsidies"]))
                                       
                              )
 
@@ -76,7 +68,7 @@ Introduction = function()
                                tags$div(class = "picture-overlay-footer-wrapper",
 
                                         actionLink("al_introduction_to_need_help",
-                                                   tags$h4(button_text$text[button_text$id == "al_introduction_to_need_help"]))
+                                                   tags$h4(text$item_label[text$item_id == "al_introduction_to_need_help"]))
 
[…]

### 2020-03-13 app/ui_02a_selected_results.R

@@ -11,15 +11,15 @@ SelectedResults = function()
     # Page style
     style = "background-color: #ffffff; color: #000000;",
     
-    ### Navigation buttons
+    ### Top navigation button
     column(12,
            fluidRow(style = "padding: 5px 5px; background-color: #3c8dbc;",
                     
-                    # Next to edit-policies
-                    column(3, offset = 9,
-                           tags$button(id = "ab_selected_results_to_edit_policies",
-                                       class = "btn action-button nav-button-r",
-                                       button_text$text[button_text$id == "ab_selected_results_to_edit_policies"], icon("chevron-right")
+                    # Return to main menu
+                    column(3,
+                           tags$button(id = "ab_selected_results_to_introduction",
+                                       class = "btn action-button nav-button-l",
+                                       icon("undo"), text$item_label[text$item_id == "ab_selected_results_to_introduction"]
                            )
                     )
                     
@@ -30,7 +30,7 @@ SelectedResults = function()
     column(12, style = "padding: 25px 25px;",
            
            # Title
-           tags$h3(style = "padding: 0; margin: 0 0 10px;", tab_text$tab[tab_text$id == "selected-results"]),
+           tags$h3(style = "text-align: left; padding: 0; margin: 0 0 10px;", text$item_label[text$item_id == "selected-results"]),
            
            # Text
            includeHTML("./text/02a_selected_results_intro.html"),
@@ -39,16 +39,17 @@ SelectedResults = function()
            fluidRow(
              column(6, align = "center",
                     
-                    selectizeInput("timeseries_variable", label = tags$b("Plot... "),
+                    selectizeInput("w_selected_results_timeseries_plot_variable", 
+                                   label = tags$b(text$item_label[text$item_id == "w_selected_results_timeseries_plot_variable"]),
                                    choices = list("Biomass" = "biomass", "Catches" = "catches_total", "Revenue" = "revenue_total"),
-                                   selected = "biomass")
+                                   selected = text$selected[text$item_id == "w_selected_results_timeseries_plot_variable"])
                     
              ),
              column(6, align = "center",
-                    radioButtons("timeseries_resolution", label = tags$b("Resolution: "),
+                    radioButtons("w_selected_results_timeseries_plot_resolution", 
+                                 label = tags$b("Resolution: "),
                                  choices = list("Global" = 1, "Regional" = 2), 
-                                 selected = 1,
-                                 inline = T)
+                                 selected = text$selected[text$item_id == "w_selected_results_timeseries_plot_resolution"])
[…]

### 2020-03-13 app/ui_03_methods_process.R

@@ -11,12 +11,17 @@ MethodsProcess = function()
     # Page style
     style = "background-color: #262626; color: #ffffff;",
     
-    ### Top navigation buttons
+    ### Top navigation button
     column(12,
            fluidRow(style = "padding: 5px 5px; background-color: #3c8dbc;",
                     
-                    # Back to main menu button
-                    column(12, style = "height: 30px;")
+                    # Return to main menu
+                    column(3,
+                           tags$button(id = "ab_methods_process_to_introduction",
+                                       class = "btn action-button nav-button-l",
+                                       icon("undo"), text$item_label[text$item_id == "ab_methods_process_to_introduction"]
+                           )
+                    )
                     
            )
     ),
@@ -25,7 +30,7 @@ MethodsProcess = function()
     column(12, style = "padding: 25px 25px;",
            
            # Title
-           tags$h3(style = "padding: 0; margin: 0 0 10px;", tab_text$tab[tab_text$id == "methods-process"]),
+           tags$h3(style = "text-align: left; padding: 0; margin: 0 0 10px; color: #ffffff;", text$item_label[text$item_id == "methods-process"]),
            
            # Text
            includeHTML("./text/03_methods_process_intro.html"),
@@ -35,7 +40,7 @@ MethodsProcess = function()
                   
                   downloadButton("db_download_methods", 
                                  style = "padding: 10px; width: auto;", 
-                                 button_text$text[button_text$id == "db_download_methods"])
+                                 text$item_label[text$item_id == "db_download_methods"])
                   
            )
            
@@ -45,18 +50,11 @@ MethodsProcess = function()
     column(12,
            fluidRow(style = "padding: 5px 5px; background-color: #3c8dbc;",
                     
-                    # Return to main menu
-                    column(3,
-                           tags$button(id = "ab_methods_process_to_introduction",
-                                       class = "btn action-button nav-button-l",
-                                       icon("undo"), button_text$text[button_text$id == "ab_methods_process_to_introduction"]
-                           )
-                    )
+                    # Empty
+                    column(12, style = "height: 30px;")
                     
            )
     )
-            
-    
     
   ) # /fluidPage
   

### 2020-03-13 app/ui_04a_global_subsidies.R

@@ -11,15 +11,15 @@ GlobalSubsidies = function(subsidy_categories_sorted_sumaila, subsidy_types_sort
     # Page style
     style = "background-color: #262626; color: #ffffff;",
     
-    ### Top navigation buttons
+    ### Top navigation button
     column(12,
            fluidRow(style = "padding: 5px 5px; background-color: #3c8dbc;",
                     
-                    # Next to country-fishery-stats
-                    column(3, offset = 9,
-                           tags$button(id = "ab_global_subsidies_to_country_fishery_stats",
-                                       class = "btn action-button nav-button-r",
-                                       button_text$text[button_text$id == "ab_global_subsidies_to_country_fishery_stats"], icon("chevron-right")
+                    # Return to main menu
+                    column(3,
+                           tags$button(id = "ab_global_subsidies_to_introduction",
+                                       class = "btn action-button nav-button-l",
+                                       icon("undo"), text$item_label[text$item_id == "ab_global_subsidies_to_introduction"]
                            )
                     )
                     
@@ -30,7 +30,7 @@ GlobalSubsidies = function(subsidy_categories_sorted_sumaila, subsidy_types_sort
     column(12, style = "padding: 25px 25px;",
            
            # Title
-           tags$h3(style = "padding: 0; margin: 0 0 10px;", tab_text$tab[tab_text$id == "global-subsidies"]),
+           tags$h3(style = "text-align: left; padding: 0; margin: 0 0 10px; color: #ffffff;", text$item_label[text$item_id == "global-subsidies"]),
            
            # Text
            includeHTML("./text/04a_global_subsidies_intro.html"),
@@ -41,8 +41,11 @@ GlobalSubsidies = function(subsidy_categories_sorted_sumaila, subsidy_types_sort
              column(6, style = "padding: 0 12.5px 0 0;",
                     
                     selectInput("w_global_subsidies_category",
-                                label = tags$b("Subsidy category: "),
-                                choices = subsidy_categories_sorted_sumaila,
+                                label = tags$b(text$item_label[text$item_id == "w_global_subsidies_category"]),
+                                choices = setNames(c("All", subsidy_categories_sorted_sumaila), c("All subsidies", 
+                                                                                                  "Beneficial subsidies only", 
+                                                                                                  "Capacity-enhancing subsidies only",
+                                                                                                  "Ambiguous subsidies only")),
                                 selected = "Capacity-enhancing",
                                 width = "100%")
              ),
[…]

### 2020-03-13 app/ui_02b_edit_policies.R
two out of three policy selection sections done with widget text input

@@ -107,7 +107,7 @@ column(12,
                                                 # Provide policy description
                                                 textInput("w_run_name",
                                                           label = text$item_label[text$item_id == "w_run_name"],
-                                                          value = text$item_value[text$item_id == "w_run_name"]),
+                                                          value = text$value[text$item_id == "w_run_name"]),
                                          ),
                                          
                                          # Next tab button
@@ -164,7 +164,7 @@ column(12,
                                                     fluidRow( 
                                                       
                                                       ### Left column: Definitions
-                                                      column(6, style = "padding: 0 10px;",
+                                                      column(5, style = "padding: 0 10px;",
                                                          
                                                              # Input: IUU definitions
                                                              checkboxGroupInput("w_iuu_definitions", 
@@ -219,7 +219,7 @@ column(12,
                                                   
                                                   
                                                   ### Middle column: scope
-                                                  column(3, style = "padding: 0 10px;",
+                                                  column(4, style = "padding: 0 10px;",
                                                          
                                                          conditionalPanel('input.w_iuu_definitions.length > 0',
                                                                           
@@ -260,6 +260,7 @@ column(12,
                                                          
                                                          conditionalPanel("(input.w_iuu_allow_sdt == 'Yes' && input.w_iuu_definitions.length > 0)",
                                                                           
+                                                                          # S&DT - Who?
                                                                           radioButtons("w_iuu_sdt_who",
                                                                                        label = tagList(tags$b(text$item_label[text$item_id == "w_iuu_sdt_who"]),
                                                                                                        # Info button
@@ -271,24 +272,29 @@ column(12,
                                                                                        width = "100%",
                                                                                        inline = FALSE),
                                                                           
+                                                                          # S&DT - What? 
                                                                           checkboxGroupInput("w_iuu_sdt_what",
                                                                                              label = tags$b(text$item_label[text$item_id == "w_iuu_sdt_what"]),
-                                                                                             choices = c("A", "B"),
+                                                                                             choices = c("all", "domestic", "time"),
                                                                                              selected = "",
                                                                                              width = "100%",
                                                                                              inline = FALSE),
                                                                           
-                                                                          # conditionalPanel("input.iuu_sdt_what.includes('time')",
-                                                                          #                  
-                                                                          #                  sliderInput("iuu_sdt_time_delay", 
-                                                                          #                              label = tags$b("Time delay (years):"), 
-                                                                          #                              min = 0, 
-                                                                          #                              max = 5, 
-                                                                          #                              value = 1,
[…]

### 2020-03-13 app/ui_04a_global_subsidies.R

@@ -83,9 +83,10 @@ GlobalSubsidies = function(subsidy_categories_sorted_sumaila, subsidy_types_sort
     ),
     
     ### Map disclaimer
-    column(12, style = "padding: 10px 25px; color: #ffffff;",
+    column(12, style = "padding: 25px 25px; color: #ffffff;",
            
-           includeHTML("./text/00_map_disclaimer.html")
+           tags$i(text$item_label[text$item_id == "map_disclaimer"])
+           
     ),
     
     ### Bottom navigation buttons

### 2020-03-13 app/ui_04d_global_fishing_footprint.R

@@ -52,9 +52,9 @@ GlobalFishingFootprint = function()
     ),
     
     ### Map disclaimer
-    column(12, style = "padding: 10px 25px; color: #ffffff;",
+    column(12, style = "padding: 25px 25px; color: #ffffff;",
            
-           includeHTML("./text/00_map_disclaimer.html")
+           tags$i(text$item_label[text$item_id == "map_disclaimer"])
     ),
     
     ### Bottom navigation buttons

### 2020-03-13 scripts/01_data_wrangling.Rmd
end of day

@@
 
-For the two datasets in this section, we'll export tidied versions individually for use in SubsidyExplorer.
-
 ## Updated estimates and analysis of global fisheries subsidies from Sumaila et al. (2019)
@@
 # Section 2 - Demographic Data
-
-For the four datasets in this section, we'll export a single aggregated demographic dataset for use in SubsidyExplorer.
 
@@
 ```
+
+# Section 3 - Fisheries Data
+
+## Fisheries landings for 2000-2017 from the FAO Global Capture Production database (2019)

### 2020-03-13 app/server.R

@@ -104,8 +104,8 @@ shinyServer(function(input, output, session) {
   })
   
   # Navigation button from tab 3 to tab 4
-  observeEvent(input$ab_edit_policies_tabs_overcap_to_preview, {
-    updateTabsetPanel(session, "policy_tabs", "preview") 
+  observeEvent(input$ab_edit_policies_tabs_overcap_to_other, {
+    updateTabsetPanel(session, "policy_tabs", "other") 
   })
   
   ### Text Output: IUU data warning -------------------
@@ -117,8 +117,6 @@ shinyServer(function(input, output, session) {
       ""
     }
   })
-  
-  
   
   ### Reactive data frame: All select policy inputs -------------
   

### 2020-03-13 app/ui_02b_edit_policies.R

@@ -702,11 +702,9 @@ column(12,
                                          # Manual Overcap discipline selection
                                          column(12, style = "padding: 0px 25px 15px;", 
                                                 
-                                                h4("Manually select overcapacity and overfishing disciplines"),
-                                                
                                                 fluidRow(
                                                   ### Overcapacity definitions: left column
-                                                  column(6, style = "padding: 0 10px;",
+                                                  column(5, style = "padding: 0 10px;",
                                                          
                                                          checkboxGroupInput("w_overcap_definitions",
                                                                             label = tagList(tags$b("The following types of subsidies are considered to \ncontribute to overcapacity and overfishing and are prohibited..."),
@@ -722,7 +720,7 @@ column(12,
                                                   ), # /column - Overcapcity definitions
                                                   
                                                   ### Overcapacity scope: middle column
-                                                  column(3, style = "padding: 0 10px;",
+                                                  column(4, style = "padding: 0 10px;",
                                                          
                                                          conditionalPanel('input.w_overcap_definitions.length > 0',
                                                                           

### 2020-03-15 papers/pnas_figures.Rmd
good start on figure paper redo

---
output:
  html_document: default

title: "Paper # 1 - Figures"
author: "Kat Millage"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
---

# Description

```{r setup, include=FALSE}
# Load packages
library(knitr) 
library(countrycode) # country name matching
library(sf)
library(rworldmap)
library(tidyverse)

# Path to cleaned subsidies data file
subsidy_dat_sumaila_path <- here::here("data", "edited", "sumaila_et_al_2019_subsidies_tidy.csv")

# Path to binned effort data file
effort_dat_binned_path <- here::here("results", "01-vessel-list", "effort_binned_good_fishing_vessels_2018_raw.csv")

# Path to upsides data file 
#upsides_dat_path <- here::here("results", )

knitr::opts_chunk$set(echo = TRUE)

# Directories for the output files generated by this script
results_dir <- here::here("papers", "paper-1/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}
```

# Version 1: Binned effort and median F/Fmsy by FAO region

```{r}
effort_binned_good_fishing_vessels_2018 <- read_csv(effort_dat_binned_path)
```

# Correct outdated flag codes and Identify EU and USA dependent vessels

Before allocating catches and subsidies across vessels, we need to identify vessels flagged to states that are overseas dependencies of the EU or USA. We assume that these vessels recieve subsidies from their sovereign states and therefore their fishing efforts should be included in the totals.

```{r}
# Load country dependencies helper file
country_dependencies <- read_csv(here::here("data", "lookup-tables", "country_dependencies.csv"))

# EU countries
eu_countries <- country_dependencies$iso3[country_dependencies$is_EU]

# EU overseas territories
eu_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 %in% eu_countries]

# US overseas territories:  American Samoa, Guam, Northern Marianas Islands, Puerto Rico, US Virgin Islands
us_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "USA"]
```

We apply these to our binned fishing effort

```{r}
effort_binned <- effort_binned_good_fishing_vessels_2018 %>%
  mutate(is_eu = case_when(flag %in% c(eu_countries, eu_territories) ~ TRUE,
                           TRUE ~ FALSE),
         is_usa = case_when(flag %in% c(us_territories, "USA") ~ TRUE,
                            TRUE ~ FALSE),
         new_flag = case_when(is_eu ~ "EU", 
                              is_usa ~ "USA", 
                              TRUE ~ flag))

effort_binned$new_flag[effort_binned$new_flag == "GCA"] <- "GTM"
effort_binned$new_flag[effort_binned$new_flag == "ROM"] <- "ROU"
effort_binned$new_flag[effort_binned$new_flag == "UNK"] <- NA
```

Now lets get fishing effort totals by flag state

```{r}
effort_totals_flag <- effort_binned %>%
  group_by(new_flag) %>%
  summarize(fishing_KWh_lat_lon = sum(fishing_KWh_lat_lon, na.rm = T),
            fishing_hours_lat_lon = sum(fishing_hours_lat_lon, na.rm = T))
```

We then load our subsidy data, and calculate subsidy rates by flag for 2018.

```{r}
subsidy_dat_sumaila <- read_csv(subsidy_dat_sumaila_path) %>%
  group_by(iso3, category) %>%
  summarize(subs = sum(value, na.rm = T)) %>%
  spread(category, subs) %>%
  rename(A_subs = A,
         B_subs = B,
         C_subs = C)
```

```{r}
subsidy_rates_flag <- effort_totals_flag %>%
  left_join(subsidy_dat_sumaila, by = c("new_flag" = "iso3")) %>%
  mutate(A_subs_KWh = A_subs/fishing_KWh_lat_lon,
         B_subs_KWh = B_subs/fishing_KWh_lat_lon,
         C_subs_KWh = C_subs/fishing_KWh_lat_lon,
         tot_subs_KWh = (A_subs+B_subs+C_subs)/fishing_KWh_lat_lon) %>%
  dplyr::select(new_flag, contains("subs_KWh"))

```

Now we go back to our effort data, and apply our subsidy rates and calculate the median subsidy intensity for each lat/lon bin

```{r}
effort_binned_med_sub_intensity <- effort_binned %>%
  left_join(subsidy_rates_flag, by = "new_flag") %>%
  group_by(year, lat_bin_center, lon_bin_center, fao_region) %>%
  summarize(med_A_subs_KWh = median(A_subs_KWh, na.rm = T),
            med_B_subs_KWh = median(B_subs_KWh, na.rm = T),
            med_C_subs_KWh = median(C_subs_KWh, na.rm = T),
            med_tot_subs_KWh = median(tot_subs_KWh, na.rm = T))

effort_binned_mean_sub_intensity <- effort_binned %>%
  left_join(subsidy_rates_flag, by = "new_flag") %>%
  group_by(year, lat_bin_center, lon_bin_center, fao_region) %>%
  summarize(mean_A_subs_KWh = mean(A_subs_KWh, na.rm = T),
            mean_B_subs_KWh = mean(B_subs_KWh, na.rm = T),
            mean_C_subs_KWh = mean(C_subs_KWh, na.rm = T),
            mean_tot_subs_KWh = mean(tot_subs_KWh, na.rm = T))
```

And plot...

```{r}
# Make land
world_land <- st_as_sf(rworldmap::countriesLow) ## data(countriesLow) is from the rworldmap package

median_subsidy_intensity_B_map <- effort_binned_med_sub_intensity %>%
  na.omit() %>%
  ggplot()+
  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = med_B_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Median Subsidy Intensity ($/KWh)", limits = c(0,2), na.value = "#000000") +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  theme(panel.background = element_rect(fill ="black"),
        plot.background = element_rect(fill = "black"),
        legend.background=element_rect(fill="black"),
        legend.text = element_text(color = "white", size = 16),
        legend.title = element_text(color = "white", size = 16),
        legend.title.align = 1,
        legend.direction="horizontal",
        legend.position = "bottom",
        legend.justification = "center",
        axis.text = element_text(color = "white", size = rel(1)),
        panel.grid.major = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
 guides(fill=guide_legend(
                 keywidth=0.25,
                 keyheight=0.25,
                 default.unit="inch"))

ggsave(paste0(results_dir, "median_subsidy_intensity_B_map.png"), dpi = 200, width = 7, height = 5)

mean_subsidy_intensity_B_map <- effort_binned_mean_sub_intensity %>%
  na.omit() %>%
  ggplot()+
  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = mean_B_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Median Subsidy Intensity ($/KWh)", limits = c(0,2), na.value = "#000000") +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  theme(panel.background = element_rect(fill ="black"),
        plot.background = element_rect(fill = "black"),
        legend.background=element_rect(fill="black"),
        legend.text = element_text(color = "white", size = 16),
        legend.title = element_text(color = "white", size = 16),
        legend.title.align = 1,
        legend.direction="horizontal",
        legend.position = "bottom",
        legend.justification = "center",
        axis.text = element_text(color = "white", size = rel(1)),
        panel.grid.major = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) +
 guides(fill=guide_legend(
                 keywidth=0.25,
                 keyheight=0.25,
                 default.unit="inch"))

ggsave(paste0(results_dir, "mean_subsidy_intensity_B_map.png"), dpi = 200, width = 7, height = 5)
```

Now we load the upsides database to get a measure of

### 2020-03-15 scripts/02_vessel_list.Rmd
good start on figure paper redo

--- 2020-03-10 scripts/01_vessel_list.Rmd
@@
 
-title: "SubsidyExplorer - Step 1: Create Vessel List"
+title: "SubsidyExplorer - Step 2: Create Vessel List"
 author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
@@
 
+It also creates a 5x5 degree version for use in making the figures for the paper, but this version is kept on BigQuery.
+
 ```{r}
@@
 # Path to cleaned subsidies data file
-subsidy_dat_path <- here::here("data", "edited", "sumaila-subsidies-2018-tidy.csv")
+subsidy_dat_sumaila_path <- here::here("data", "edited", "sumaila_et_al_2019_subsidies_tidy.csv")
 
 # Path to cleaned landings data file
-catch_dat_path <- here::here("data", "edited", "fisheries-area-2000-2017-tidy.csv")
+#catch_dat_path <- here::here("data", "edited", "fisheries-area-2000-2017-tidy.csv")
 
 # Bigquery project
-bq_project <-  "ucsb-gfw"
+bq_project <-  "emlab-gcp"
 
-# Do you want to make summary figures?
-make_figures <- F
 ```
@@
 # Directories for the output files generated by this script
-results_dir <- here::here("results", "1-vessel-list/")
+results_dir <- here::here("results", "01-vessel-list/")
 if (dir.exists(results_dir) == F) {
@@
 
+## By 5x5 degree latititude/longitude
+
+We first extract the number of hours spent fishing by each of our good fishing vessels in each 5x5 degree latitude/longitude bin from the raw fishing effort table (`world-fishing-827.gfw_research.pipe_v20190502_fishing`).
+
+To identify valid fishing effort here, we apply the following filters: 
+- The fishing activity must have occured during a valid segment as identified by GFW.
+- The fishing activity must have occured during a segment with more than 10 positions that was not concurrently overlapping with another, longer, segment for the same MMSI.  
+- The vessel performing the fishing activity must appear on the list of good fishing vessels created above
+
+We then extract a vessel table with the the following attributes: 
+- year (int): Year. Matches our data year specified above.
+- lat_bin (int): 5 degree latitude bin, coordinates refer to the center of the bin
+- lon_bin (int): 5 degree longitude bin, coordinates refer to the center of the bin
+- fao_region (int): Major FAO statistical region
+- fishing_hours_lat_lon: Total annual fishing hours in the specified lat/lon bin by a single vessel
+- ssvid (chr): Unique vessel identification number given by GFW (MMSI number for most vessels)
+- flag (chr): Best flag state of the vessel.
+
+```{r}
+sql2 <- '
+WITH
+  # This subquery identifies good segments
+  good_segments AS (
+  SELECT
+    seg_id
+  FROM
+    `world-fishing-827.gfw_research.pipe_v20190502_segs`
+  WHERE
+    good_seg
+    AND positions > 10
+    AND NOT overlapping_and_short),
+
+  # This subquery identifies good fishing vessels from our previous query
+  good_vessels AS (
+  SELECT
+    *
+  FROM
+    `emlab-gcp.SubsidyExplorer.all_good_fishing_vessels`),
+
+  # This subquery identifies vessel information that we want to keep
+  vessel_info AS (
+  SELECT
+    ssvid,
+    year,
+    best.best_flag as flag,
+    best.best_engine_power_kw as engine_power_kw
+  FROM
+    `world-fishing-827.gfw_research.vi_ssvid_byyear_v20190430`
+  WHERE
+    year = 2018),
+
+  # This subquery gets all fishing effort by ssvid, eez, and fao region in 2018 cooresponding to good segments and good vessels
+  fishing_by_lat_lon AS (
+    SELECT
+      EXTRACT(year FROM date) AS year,
+      ssvid,
+      FLOOR(lat*0.5)/0.5 + 2.5 lat_bin_center,
+      FLOOR(lon*0.5)/0.5 + 2.5 lon_bin_center, 
+      if(ARRAY_LENGTH(regions.major_fao)=0, "0", regions.major_fao[ordinal(1)]) AS fao_region,
+      sum(hours) AS fishing_hours_lat_lon
+    FROM
+      `world-fishing-827.gfw_research.pipe_v20190502_fishing`
+    WHERE
+      date > timestamp("2018-01-01")
+      AND date < timestamp("2018-12-31")
+      AND ARRAY_LENGTH(regions.major_fao) > 0 # removes fishing inland
+      AND nnet_score2 > .5
+      AND seg_id IN (
+        SELECT
+          seg_id
+        FROM
+          good_segments)
+      AND ssvid IN (
+        SELECT
+          ssvid
+        FROM
+          good_vessels
+        WHERE
+          year = 2018)
+    GROUP BY
+      year,
+      ssvid,
+      lat_bin_center,
+      lon_bin_center,
+      fao_region
+    ORDER BY
+      year,
+      ssvid,
+      fishing_hours_lat_lon DESC)
+
+SELECT
+  *,
+  fishing_hours_lat_lon*engine_power_kw as fishing_KWh_lat_lon
+FROM
+  fishing_by_lat_lon
+LEFT JOIN
+  vessel_info
+USING
+  (ssvid,
+  year)
+'
+
+binned_effort_table <- bq_table(project = bq_project, 
+                                table = "effort_5deg_good_fishing_vessels_2018_raw",
+                                dataset = "SubsidyExplorer")
+
+if(bq_table_exists(binned_effort_table)){
+
+  bq_table_delete(binned_effort_table)
+  effort_binned_good_fishing_vessels_2018 <- 
+    bq_project_query(bq_project, 
+                    sql2, 
+                    destination_table = binned_effort_table, 
+                    use_legacy_sql = FALSE, 
+                    allowLargeResults = TRUE) %>%
+    bq_table_download()
+
+}else {
+  bq_table_create(binned_effort_table)
+  effort_binned_good_fishing_vessels_2018 <- 
+    bq_project_query(bq_project, 
+                   query = sql2, 
+                   destination_table = binned_effort_table,
+                   use_legacy_sql = FALSE, 
+                   allowLargeResults = TRUE) %>%
+    bq_table_download()
+}
+
+# Save
+write_csv(effort_binned_good_fishing_vessels_2018, paste0(results_dir, "effort_binned_good_fishing_vessels_2018_raw.csv"))
+```
+
+## By EEZ and/or FAO region
+
 We then extract the number of hours spent fishing by each of our good fishing vessels in different EEZs and/or FAO regions from the raw fishing effort table (`world-fishing-827.gfw_research.pipe_v20190502_fishing`).
@@
 ```{r}
-sql2 <- '
+sql3 <- '
 WITH
@@
     bq_project_query(bq_project, 
-                    sql2, 
+                    sql3, 
                     destination_table = effort_table, 
@@
     bq_project_query("world-fishing-827", 
-                   query = sql2, 
+                   query = sql3, 
                    destination_table = effort_table,
@@
 write_csv(effort_good_fishing_vessels_2018, paste0(results_dir, "effort_good_fishing_vessels_2018_raw.csv"))
-
-# If BigQuery connection isn't working, or you don't have access, impuort from local file
-effort_good_fishing_vessels_2018 <- read_csv(paste0(results_dir, "effort_good_fishing_vessels_2018_raw.csv"), col_types = "nnnnnccnnnccnccccccn")
 ```

### 2020-03-16 papers/paper-1/paper_1_figures.Rmd
finishing first version of new paper figures

---
output:
  html_document: default

title: "Paper # 1 - Figures"
author: "Kat Millage"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
---

# Description

```{r setup, include=FALSE}
# Load packages
library(knitr) 
library(countrycode) # country name matching
library(sf)
library(rworldmap)
library(rmapshaper)
library(tidyverse)

# Path to cleaned subsidies data file
subsidy_dat_sumaila_path <- here::here("data", "edited", "sumaila_et_al_2019_subsidies_tidy.csv")

# Path to binned effort data file
effort_dat_binned_path <- here::here("results", "02-vessel-list", "effort_binned_good_fishing_vessels_2018_raw.csv")

# Path to upsides data file 
upsides_dat_path <- here::here("data", "edited", "costello_et_al_2016_upsides_tidy.csv")

# Chunk options
knitr::opts_chunk$set(echo = TRUE, message = F, warning = F, prompt = F, error = F)

# Directories for the output files generated by this script
results_dir <- here::here("papers", "paper-1/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}
```

```{r}
# Plot themes and shapefiles
map_theme <- theme(panel.background = element_rect(fill ="black"),
        plot.background = element_rect(fill = "black"),
        legend.background=element_rect(fill="black"),
        legend.text = element_text(color = "white", size = 16),
        legend.title = element_text(color = "white", size = 16),
        legend.title.align = 1,
        legend.direction="horizontal",
        legend.position = "bottom",
        legend.justification = "center",
        axis.text = element_text(color = "white", size = rel(1)),
        panel.grid.major = element_blank(),
        axis.title.x = element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

plot_theme <- theme_bw()

# Land shapefile
world_land <- st_as_sf(rworldmap::countriesLow) ## data(countriesLow) is from the rworldmap package

# FAO regions
fao_regions <- read_sf(here::here("data", "shapefiles", "fao"), layer = "World_Fao_Zones") %>%
  rename(fao_region = zone) %>%
  rmapshaper::ms_simplify(keep = 0.05)
```

# Version 1: Binned effort and median F/Fmsy by FAO region

```{r}
effort_binned_good_fishing_vessels_2018 <- read_csv(effort_dat_binned_path)
```

# Correct outdated flag codes and Identify EU and USA dependent vessels

Before allocating catches and subsidies across vessels, we need to identify vessels flagged to states that are overseas dependencies of the EU or USA. We assume that these vessels recieve subsidies from their sovereign states and therefore their fishing efforts should be included in the totals.

```{r}
# Load country dependencies helper file
country_dependencies <- read_csv(here::here("data", "lookup-tables", "country_dependencies.csv"))

# EU countries
eu_countries <- country_dependencies$iso3[country_dependencies$is_EU]

# EU overseas territories
eu_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 %in% eu_countries]

# US overseas territories:  American Samoa, Guam, Northern Marianas Islands, Puerto Rico, US Virgin Islands
us_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "USA"]
```

We apply these to our binned fishing effort

```{r}
effort_binned <- effort_binned_good_fishing_vessels_2018 %>%
  mutate(is_eu = case_when(flag %in% c(eu_countries, eu_territories) ~ TRUE,
                           TRUE ~ FALSE),
         is_usa = case_when(flag %in% c(us_territories, "USA") ~ TRUE,
                            TRUE ~ FALSE),
         new_flag = case_when(is_eu ~ "EU", 
                              is_usa ~ "USA", 
                              TRUE ~ flag))

effort_binned$new_flag[effort_binned$new_flag == "GCA"] <- "GTM"
effort_binned$new_flag[effort_binned$new_flag == "ROM"] <- "ROU"
effort_binned$new_flag[effort_binned$new_flag == "UNK"] <- NA
```

### Subsidy intensities

Now lets get fishing effort totals by flag state

```{r}
effort_totals_flag <- effort_binned %>%
  group_by(new_flag) %>%
  summarize(fishing_KWh_lat_lon = sum(fishing_KWh_lat_lon, na.rm = T),
            fishing_hours_lat_lon = sum(fishing_hours_lat_lon, na.rm = T))
```

We then load our subsidy data, and calculate subsidy rates by flag for 2018. Subsidy rates are then applied to our binned effort data by flag.

```{r}
subsidy_dat_sumaila <- read_csv(subsidy_dat_sumaila_path) %>%
  group_by(iso3, category) %>%
  summarize(subs = sum(value, na.rm = T)) %>%
  spread(category, subs) %>%
  rename(A_subs = A,
         B_subs = B,
         C_subs = C)
```

```{r}
# Calculate subsidy rates by flag
subsidy_rates_flag <- effort_totals_flag %>%
  left_join(subsidy_dat_sumaila, by = c("new_flag" = "iso3")) %>%
  mutate(A_subs_KWh = A_subs/fishing_KWh_lat_lon,
         B_subs_KWh = B_subs/fishing_KWh_lat_lon,
         C_subs_KWh = C_subs/fishing_KWh_lat_lon,
         tot_subs_KWh = (A_subs+B_subs+C_subs)/fishing_KWh_lat_lon) %>%
  dplyr::select(new_flag, contains("subs_KWh"))

# Apply subsidy rates to binned effort
effort_binned_sub_intensity <- effort_binned %>%
  left_join(subsidy_rates_flag, by = "new_flag")
```

Now we go back to our effort data, and apply our subsidy rates.

Now let's calculate and plot the median bad subsidy intensities by lat/lon bin and FAO region.

```{r}
median_breaks <- seq(0,6, by = 1)
median_limits <- c(0,6)
median_labels <- c("0", "1", "2", "3", "4", "5", paste0("\u2265","6"))

median_subsidy_intensity_B_grid_map <- effort_binned_sub_intensity %>%
  group_by(year, lat_bin_center, lon_bin_center) %>%
  summarize(med_B_subs_KWh = median(B_subs_KWh, na.rm = T)) %>%
  ggplot()+
  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = med_B_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Median Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = median_limits, 
                       breaks = median_breaks,
                       labels = median_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

median_subsidy_intensity_B_grid_map

ggsave(paste0(results_dir, "median_subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 5)

```

```{r}
region_median_breaks <- seq(0,2, by = 0.5)
region_median_limits <- c(0,2)
region_median_labels <- c("0", "0.5", "1", "1.5", paste0("\u2265","2"))

median_subsidy_intensity_B_region_map <- effort_binned_sub_intensity %>%
  group_by(year, fao_region) %>%
  summarize(med_B_subs_KWh = median(B_subs_KWh, na.rm = T)) %>%
  right_join(fao_regions, by = "fao_region") %>%
  ggplot()+
  geom_sf(aes(geometry = geometry, fill = med_B_subs_KWh), color = "#000000") +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Median Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = region_median_limits, 
                       breaks = region_median_breaks,
                       labels = region_median_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

median_subsidy_intensity_B_region_map

ggsave(paste0(results_dir, "median_subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 5)

```

Do means too.

```{r}
mean_breaks <- seq(0,6, by = 1)
mean_limits <- c(0,6)
mean_labels <- c("0", "1", "2", "3", "4", "5", paste0("\u2265","6"))

mean_subsidy_intensity_B_grid_map <- effort_binned_sub_intensity %>%
  group_by(year, lat_bin_center, lon_bin_center) %>%
  summarize(mean_B_subs_KWh = mean(B_subs_KWh, na.rm = T)) %>%
  ggplot()+
  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = mean_B_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Mean Subsidy Intensity \n($/KWh)", 
                     na.value = "#000000", 
                     limits = mean_limits, 
                     breaks = mean_breaks,
                     labels = mean_labels,
                     oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

mean_subsidy_intensity_B_grid_map

ggsave(paste0(results_dir, "mean_subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 5)
```

```{r}
mean_subsidy_intensity_B_region_map <- effort_binned_sub_intensity %>%
  group_by(year, fao_region) %>%
  summarize(mean_B_subs_KWh = mean(B_subs_KWh, na.rm = T)) %>%
  right_join(fao_regions, by = "fao_region") %>%
  ggplot()+
  geom_sf(aes(geometry = geometry, fill = mean_B_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Mean Subsidy Intensity ($/KWh)", 
                       na.value = "#000000", 
                       limits = mean_limits, 
                       breaks = mean_breaks,
                       labels = mean_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

mean_subsidy_intensity_B_region_map

ggsave(paste0(results_dir, "mean_subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 5)
```

Let's make ones for the weighted means too using fishing KWh as the weights.

```{r}
weighted_mean_breaks <- seq(0,6, by = 1)
weighted_mean_limits <- c(0,6)
weighted_mean_labels <- c("0", "1", "2", "3", "4", "5", paste0("\u2265","6"))

weighted_mean_subsidy_intensity_B_grid_map <- effort_binned_sub_intensity %>%
  group_by(year, lat_bin_center, lon_bin_center) %>%
  summarize(weighted_mean_B_subs_KWh = weighted.mean(B_subs_KWh, w = fishing_KWh_lat_lon)) %>%
  ggplot()+
  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = weighted_mean_B_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Weighted Mean Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = weighted_mean_limits, 
                       breaks = weighted_mean_breaks,
                       labels = weighted_mean_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

weighted_mean_subsidy_intensity_B_grid_map

ggsave(paste0(results_dir, "weighted_mean_subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 5)
```

```{r}
region_weighted_mean_breaks <- seq(0,4, by = 1)
region_weighted_mean_limits <- c(0,4)
region_weighted_mean_labels <- c("0", "1", "2", "3", paste0("\u2265","4"))

weighted_mean_subsidy_intensity_B_region_map <- effort_binned_sub_intensity %>%
  group_by(year, fao_region) %>%
  summarize(weighted_mean_B_subs_KWh = weighted.mean(B_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T)) %>%
  right_join(fao_regions, by = "fao_region") %>%
  ggplot()+
  geom_sf(aes(geometry = geometry, fill = weighted_mean_B_subs_KWh)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  scale_fill_viridis_c(name="Weighted Mean Subsidy Intensity \n($/KWh)", 
                       na.value = "#000000", 
                       limits = region_weighted_mean_limits, 
                       breaks = region_weighted_mean_breaks,
                       labels = region_weighted_mean_labels,
                       oob = scales::squish) +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_colorbar(
   title.position = "left",
   title.hjust = 0.5,
   frame.colour = "white",
   barwidth=4,
   barheight=0.25,
   default.unit="inch"))

weighted_mean_subsidy_intensity_B_region_map

ggsave(paste0(results_dir, "weighted_mean_subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 5)
```

### Stock status

Now we load the upsides database, calculate mean and median F/Fmsy by FAO region, and plot.

```{r}
upsides_dat <- read_csv(upsides_dat_path)

upsides_regional_averages <- upsides_dat %>%
  group_by(region_fao_split) %>%
  summarize(mean_f_v_fmsy = mean(fv_fmsy),
            mean_weighted_f_v_fmsy = weighted.mean(fv_fmsy, w = msy),
            median_f_v_fmsy = median(fv_fmsy),
            mean_b_v_bmsy = mean(bv_bmsy),
            mean_weighted_b_v_bmsy = weighted.mean(bv_bmsy, w = msy),
            median_b_v_bmsy = median(bv_bmsy))

```

```{r}

upsides_regional_averages_spatial <- fao_regions %>%
  right_join(upsides_regional_averages, by = c("fao_region" = "region_fao_split"))

```

Mean F/Fmsy by region.

```{r}
mean_f_v_fmsy_regional_map <- ggplot()+
  geom_sf(data=upsides_regional_averages_spatial, color = "black", aes(fill = mean_f_v_fmsy)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Mean F/Fmsy", na.value = "#000000") +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
 guides(fill=guide_legend(
                 keywidth=0.25,
                 keyheight=0.25,
                 default.unit="inch"))

mean_f_v_fmsy_regional_map

ggsave(paste0(results_dir, "mean_f_v_fmsy_regional_map.png"), dpi = 200, width = 7, height = 5)
```

Weighted mean F/Fmsy by region (weighted by MSY of each stock).

```{r}
weighted_mean_f_v_fmsy_regional_map <- ggplot()+
  geom_sf(data=upsides_regional_averages_spatial, color = "black", aes(fill = mean_weighted_f_v_fmsy)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Weighted Mean F/Fmsy", na.value = "#000000") +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme + 
  guides(fill=guide_legend(
                 keywidth=0.25,
                 keyheight=0.25,
                 default.unit="inch"))

weighted_mean_f_v_fmsy_regional_map

ggsave(paste0(results_dir, "weighted_mean_f_v_fmsy_regional_map.png"), dpi = 200, width = 7, height = 5)
```

Median F/Fmsy by region.

```{r}
median_f_v_fmsy_regional_map <- ggplot()+
  geom_sf(data=upsides_regional_averages_spatial, color = "black", aes(fill = median_f_v_fmsy)) +
  geom_sf(data=world_land, color = NA, fill="grey30") +
  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
  scale_fill_viridis_c(name="Median F/Fmsy", na.value = "#000000") +
  scale_x_continuous(expand = c(0,0))+
  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
  xlab("") +
  ylab("") +
  map_theme +
 guides(fill=guide_legend(
                 keywidth=0.25,
                 keyheight=0.25,
                 default.unit="inch"))

median_f_v_fmsy_regional_map

ggsave(paste0(results_dir, "median_f_v_fmsy_regional_map.png"), dpi = 200, width = 7, height = 5)
```

### 2020-03-16 scripts/01_data_wrangling.Rmd
finishing first version of new paper figures

@@
 us_territory_names <- sort(countrycode(us_territories, "iso3c", "country.name"))
+
+# Norwegian overseas territories: 
+nor_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "NOR"]
+nor_territory_names <- sort(countrycode(nor_territories, "iso3c", "country.name"))
 ```
@@
 
-Outside of the EU, the only other dependencies we need to worry about are those that relate to the United States.
+Outside of the EU, the other dependencies we need to worry about are those that relate to the United States and Norway.
 The following overseas dependencies are considered to be a part of the United States for the purpose of aggregating data in this analysis: `r paste(us_territory_names, collapse = ", ")`.
+The following overseas dependencies are considered to be a part of Norway for the purpose of aggregating data in this analysis: `r paste(norway_territory_names, collapse = ", ")`.
 
@@
 ## Fisheries landings for 2000-2017 from the FAO Global Capture Production database (2019)
+
+## Estimated landed price
+
+## Stock status database
+```{r}
+# Load data
+costello_upsides_dat <- read_csv(costello_upsides_path) %>%
+  clean_names(case = "snake")
+
+# We need to split the entries that span multiple FAO regions...  
+costello_upsides_dat_edit <- costello_upsides_dat %>%
+  mutate(region_fao_chr = as.character(region_fao),
+         n_regions = nchar(region_fao_chr)/2,
+         region_fao_split = str_split(gsub("(.{2})", "\\1 ", region_fao_chr), " ")) %>%
+  unnest(cols = c(region_fao_split)) %>%
+  mutate(region_fao_split = as.numeric(region_fao_split)) %>%
+  dplyr::filter(region_fao_split != "") %>%
+  mutate(iso3 = case_when(country == "Channel Islands" ~ "JEY",
+                          country == "Micronesia" ~ "FSM",
+                          country == "Zanzibar" ~ "TZA",
+                          TRUE ~ countrycode(country, "country.name", "iso3c")))
+
+# Save clean
+write_csv(costello_upsides_dat_edit, paste0(data_dir, "costello_et_al_2016_upsides_tidy.csv"))
+
+```
+
+# Melnychuk FMI
+```{r}
+# Load data and wrangle
+melnychuk_fmi_dat <- read_csv(melnychuk_fmi_path) %>%
+  clean_names(case = "snake") %>%
+  mutate(iso3 = countrycode(country, "country.name", "iso3c")) %>%
+  dplyr::select(-country) %>%
+  gather(variable, value, -iso3)
+
+# Create a mean aggregate for the EU
+melnychuk_fmi_dat_eu <- melnychuk_fmi_dat  %>%
+  dplyr::filter(iso3 %in% c(eu_countries, eu_territories)) %>%
+  mutate(entity = "EU") %>%
+  group_by(entity, variable) %>%
+  summarize(value = mean(value, na.rm = T)) %>%
+  rename(iso3 = entity)
+
+# Add EU back in
+melnychuk_fmi_dat_edit <- melnychuk_fmi_dat %>%
+  bind_rows(melnychuk_fmi_dat_eu)
+
+# Export clean
+write_csv(melnychuk_fmi_dat_edit, paste0(data_dir, "melnychuk_et_al_2017_fmi_tidy.csv"))
+
+```

### 2020-03-16 scripts/02_vessel_list.Rmd
finishing first version of new paper figures

@@
 It requires access to the raw Global Fishing Watch (GFW) data stored on BigQuery (not-publically available), as well as a valid Google Cloud Console billing account.
-It outputs a single data file to `r here::here("results", "01-vessel-list")`:
+It outputs a single data file to `r here::here("results", "02-vessel-list")`:
 
@@
 
-It also creates a 5x5 degree version for use in making the figures for the paper, but this version is kept on BigQuery.
+It also creates a 1x1 degree version for use in making higher resolution figures. This is output to
 
@@
 # Directories for the output files generated by this script
-results_dir <- here::here("results", "01-vessel-list/")
+results_dir <- here::here("results", "02-vessel-list/")
 if (dir.exists(results_dir) == F) {
@@
 
-## By 5x5 degree latititude/longitude
+## By 1x1 degree latititude/longitude
 
@@
 - year (int): Year. Matches our data year specified above.
-- lat_bin (int): 5 degree latitude bin, coordinates refer to the center of the bin
-- lon_bin (int): 5 degree longitude bin, coordinates refer to the center of the bin
+- lat_bin_center (int): 1 degree latitude bin, coordinates refer to the center of the bin
+- lon_bin_center (int): 1 degree longitude bin, coordinates refer to the center of the bin
 - fao_region (int): Major FAO statistical region
@@
 - ssvid (chr): Unique vessel identification number given by GFW (MMSI number for most vessels)
-- flag (chr): Best flag state of the vessel.
+- flag (chr): Best flag state of the vessel
+- engine_power_kw (int): Best engine power of the vessel
 
@@
       ssvid,
-      FLOOR(lat*0.5)/0.5 + 2.5 lat_bin_center,
-      FLOOR(lon*0.5)/0.5 + 2.5 lon_bin_center, 
+      FLOOR(lat/1)*1 + 0.5 lat_bin_center,
+      FLOOR(lon/1)*1 + 0.5 lon_bin_center, 
       if(ARRAY_LENGTH(regions.major_fao)=0, "0", regions.major_fao[ordinal(1)]) AS fao_region,
@@
   *,
-  fishing_hours_lat_lon*engine_power_kw as fishing_KWh_lat_lon
+  CASE
+    WHEN engine_power_kw IS NULL THEN fishing_hours_lat_lon
+    ELSE fishing_hours_lat_lon*engine_power_kw
+  END AS fishing_KWh_lat_lon
 FROM

### 2020-03-16 scripts/03_management.Rmd
finishing first version of new paper figures

---
output:
  html_document: default

title: "SubsidyExplorer - Step 3: Classify vessels into management regimes"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
bibliography: "../pew-subsidies.bib"

---

# Introduction

The purpose of this script is to classify all of our vessels into three different management regimes: 
- Managed
- Intermediate
- Open access

This script outputs a single data file to `r here::here("results", "03-management")`: 
- vessel-list-2018-management.csv

In addition to the vessel list created in the previous script, the following data sources are used to classify management regimes:

```{r}
# General
library(knitr) 
library(countrycode) # country name matching
library(janitor)
library(tidyverse)

# Path to vessel list
vessel_list_path <- here::here("results", "1-vessel-list", "vessel-list-2018-raw.csv")

# Path to Management data
melnychuk_2017_mgmt_dat_path <- here::here("data", "raw", "management", "Melnychuk_2017", "fmi_values_country.csv" )

# Make figures?
make_plots <- T

# Few more packages if you're making figures
if(make_plots){
  library(ggridges)
  library(ggrepel)
  library(scales)
}
```

```{r}
# Code options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, message = FALSE, warning = F)

# Directories for the output files generated by this script
results_dir <- here::here("results", "2-management/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}

```

# Assign regions to vessels

```{r}
# Load vessel list
vessel_list_raw <- read.csv(vessel_list_path, stringsAsFactors = F)

```

# Match fishing areas to management indices

```{r setup, include=FALSE}
# Load management indicies by state
melnychuk_2017_mgmt_dat <- read_csv(melnychuk_2017_mgmt_dat_path) %>%
  clean_names(case = "snake") %>%
  mutate(iso3 = countrycode(country, "country.name", "iso3c")) %>%
  dplyr::select(iso3, fmi_weighted)

# Get eez codes and matching territories
eez_info <- vessel_list_raw %>%
  group_by(eez_id) %>%
  distinct(territory1_iso3, territory2_iso3, territory3_iso3, sovereign1_iso3, sovereign2_iso3, sovereign3_iso3)

# Tidy eez data
eez_info_tidy <- eez_info %>%
  mutate(states = case_when((is.na(territory2_iso3) & is.na(territory3_iso3)) ~ 1,
                            (!is.na(territory2_iso3) & is.na(territory3_iso3)) ~ 2,
                            TRUE ~ 3)) %>%
  mutate(territory_iso = case_when(states == 1 ~ c(territory1_iso3),
                                   states == 2 ~ paste(territory1_iso3, territory2_iso3, sep = " "),
                                   states == 3 ~ paste(territory1_iso3, territory2_iso3, territory3_iso3, sep = " ")),
         sovereign_iso = case_when(states == 1 ~ c(sovereign1_iso3),
                                   states == 2 ~ paste(sovereign1_iso3, sovereign2_iso3, sep = " "),
                                   states == 3 ~ paste(sovereign1_iso3, sovereign2_iso3, sovereign3_iso3, sep = " "))) %>%
  dplyr::select(eez_id, territory_iso, sovereign_iso) %>%
  mutate(territory_split = map(territory_iso, ~ str_split(.x, " ")[[1]]),
         sovereign_split = map(sovereign_iso, ~ str_split(.x, " ")[[1]])) %>%
  unnest(cols = c(territory_split, sovereign_split)) %>%
  dplyr::select(eez_id, territory_iso3 = territory_split, sovereign_iso3 = sovereign_split)

eez_info_tidy$sovereign_iso3[eez_info_tidy$eez_id == 49003] <- "CHN"
```

```{r}
# EU countries
#Belgium, Bulgaria, Croatia, Cyprus, Denmark, Estonia, Finland, France, Germany, Greece, Ireland, Italy, Latvia, Lithuania, Malta, Netherlands, Poland, Portugal, Romania, Slovenia, Spain, Sweden, United Kingdom
eu_countries <- c("BEL", "BGR", "HRV", "CYP", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "IRL", "ITA", "LVA", "LTU", "MLT", "NLD", "POL", "PRT", "ROU", "SVN", "ESP", "SWE", "GBR")

# Dutch overseas territories: Aruba, Bonaire/St. Eustatius/Saba, Curacao, Sint Maarten
dutch_territories <- c("ABW", "BES", "CUW", "SXM")

# French overseas territories: French Guiana, French Polynesia, French Southern and Antarctic Territories, Guadeloupe, Martinique, Mayotte, New Caledonia, Reunion, Saint Barthelemy, Saint Martin, St. Pierre and Miquelon, Wallis and Futuna Islands
french_territories <- c("GUF", "PYF", "ATF", "GLP", "MTQ", "MYT", "NCL", "REU", "BLM", "MAF", "SPM", "WLF")

# Danish overseas territories: Faroe Islands, Greenland
danish_territories <- c("FRO", "GRL")

# British overseas territories: Anguilla, Ascension island, Bermuda, Cayman Islands, Falkland Islands, Guernsey, Gibraltar, British Indian Ocean Territories, Jersey, Monserratt, Pitcairn Island, South Georgia and the South Sandwich Islands, Saint Helena/Ascension/Tristan da Cunha, Tristan da Cunha, Turks and Caicos Islands, British Virgin Islands
uk_territories <- c("AIA","ASC","BMU","CYM","FLK","GGY","GIB","IOT","JEY","MSR","PCN","SGS","SHN","TAA","TCA","VGB")

eu_territories <- c(dutch_territories, french_territories, danish_territories, uk_territories)

# Norwegian overseas territories: Bouvet Islands, Svalbard and Jan Mayen Islands
norwegian_territories <- c("BVT", "SJM")

# US overseas territories:  American Samoa, Guam, Northern Marianas Islands, Puerto Rico, US Virgin Islands
us_territories <- c("ASM", "GUM", "MNP", "PRI", "VIR")
```

```{r}
# Get mean management indices for the EU, as well as by region 
regional_management_indices <- melnychuk_2017_mgmt_dat %>%
  mutate(region = countrycode(iso3, "iso3c", "region")) %>%
  group_by(region) %>%
  summarize(fmi_weighted_region = mean(fmi_weighted))

# Get EU avg management index
eu_management_index <- melnychuk_2017_mgmt_dat %>%
  dplyr::filter(iso3 %in% c(eu_countries, eu_territories)) %>%
  summarize(fmi_weighted_eu = mean(fmi_weighted))

eu_df <- tibble(iso3 = c(eu_countries, eu_territories), fmi_weighted_eu = eu_management_index$fmi_weighted_eu)

# Get continent averages 
continent_management_indices <- melnychuk_2017_mgmt_dat %>%
  mutate(continent = countrycode(iso3, "iso3c", "continent")) %>%
  group_by(continent) %>%
  summarize(fmi_weighted_continent = mean(fmi_weighted))

# Assign management indices to each EEZ
eez_management_indices <- eez_info_tidy %>%
  mutate(territory_region = countrycode(territory_iso3, "iso3c", "region"),
         sovereign_region = countrycode(sovereign_iso3, "iso3c", "region"),
         continent = countrycode(territory_iso3, "iso3c", "continent")) %>%
  left_join(melnychuk_2017_mgmt_dat, by = c("sovereign_iso3" = "iso3")) %>%
  left_join(eu_df, by = c("territory_iso3" = "iso3")) %>%
  left_join(regional_management_indices, by = c("territory_region" = "region")) %>%
  rename(fmi_weighted_region_territory = fmi_weighted_region) %>%
  left_join(regional_management_indices, by = c("sovereign_region" = "region")) %>%
  rename(fmi_weighted_region_sovereign = fmi_weighted_region) %>%
  left_join(continent_management_indices, by = c("continent")) %>%
  mutate(fmi_best = case_when(!is.na(fmi_weighted) ~ fmi_weighted,
                              !is.na(fmi_weighted_eu) ~ fmi_weighted_eu,
                              !is.na(fmi_weighted_region_territory) ~ fmi_weighted_region_territory,
                              !is.na(fmi_weighted_region_sovereign) ~ fmi_weighted_region_sovereign,
                              !is.na(fmi_weighted_continent) ~ fmi_weighted_continent,
                              TRUE ~ min(melnychuk_2017_mgmt_dat$fmi_weighted))) %>%
  group_by(eez_id) %>%
  summarize(fmi_best = mean(fmi_best)) %>%
  ungroup()

# Plot distribution by region curiousity
# ggplot(eez_management_indices, aes(x = fmi_best, y = territory_region, group = territory_region)) +
#   geom_density_ridges2()
# 
# ggplot(eez_management_indices, aes(x = fmi_best, y = continent, group = continent)) +
#   geom_density_ridges2()
```

# Apply management indices to vessels

```{r}
vessel_list_manage <- vessel_list_raw %>%
  left_join((eez_management_indices %>% dplyr::select(eez_id, fmi_best)), by = c("eez_id"))

management_quantile <- quantile(vessel_list_manage$fmi_best)
managed <- management_quantile["75%"]
openaccess <- management_quantile["25%"]

write_csv(vessel_list_manage, paste0(results_dir, "vessel-list-2018-management.csv"))
```

# Summary plots

## Average FMI by flag/fao region compared to total subsidy provision

```{r}
# FMI by flag from vessel list
fmi_flag_fao <- vessel_list_manage %>%
  group_by(flag) %>%
  mutate(tot_bad_subs = sum(bad_subs),
         tot_fuel_subs = sum(B7_subs)) %>%
  ungroup() %>%
  group_by(flag, fao_region) %>%
  summarize(fmi_weighted_avg = weighted.mean(fmi_best, catch),
            tot_bad_subs = unique(tot_bad_subs),
            tot_fuel_subs = unique(tot_fuel_subs))

ggplot(fmi_flag_fao)+
  aes(x = tot_bad_subs, y = fmi_weighted_avg)+
  geom_point()+
  theme_linedraw()+
  labs(x = "Total capacity-enhancing subsidies (2018 $US)",
       y = "Mean Weighted FMI")+
  scale_y_continuous(limits = c(0,1))+
  scale_x_continuous(labels = comma)
```

```{r}
# FMI by flag from vessel list
fmi_flag <- vessel_list_manage %>%
  group_by(flag) %>%
  mutate(tot_bad_subs = sum(bad_subs),
         tot_fuel_subs = sum(B7_subs)) %>%
  ungroup() %>%
  group_by(flag) %>%
  summarize(fmi_weighted_avg = weighted.mean(fmi_best, catch),
            tot_bad_subs = unique(tot_bad_subs),
            tot_fuel_subs = unique(tot_fuel_subs))

ggplot(fmi_flag)+
  aes(x = tot_bad_subs, y = fmi_weighted_avg)+
  geom_point()+
  theme_linedraw()+
  labs(x = "Total capacity-enhancing subsidies (2018 $US)",
       y = "Mean Weighted FMI")+
  scale_y_continuous(limits = c(0,1))+
  scale_x_continuous(labels = comma)
```

```{r}
countries_to_highlight <- c("CHN", "USA", "IDN", "JPN", "ISL", "THA")

# FMI by just from Melnychuk et al
fmi_flag_melnychuk_only <- vessel_list_manage %>%
  group_by(flag) %>%
  summarize(tot_bad_subs = sum(bad_subs),
         tot_fuel_subs = sum(B7_subs),
         tot_landings = sum(catch)) %>%
  right_join(melnychuk_2017_mgmt_dat, by = c("flag" = "iso3")) %>%
  mutate(display_name = case_when(flag %in% countries_to_highlight ~ countrycode(flag, "iso3c", "country.name")))

# plot
ggplot(fmi_flag_melnychuk_only)+
  aes(x = tot_bad_subs/1e6, y = fmi_weighted, size = tot_landings/1e6, color = display_name)+
  geom_point()+
  geom_text_repel(aes(label = display_name), size = 4, force = 100, point.padding = 0.25, box.padding = 1)+
  theme_linedraw()+
  labs(x = "Total capacity-enhancing subsidies (million 2018 $US)",
       y = "Weighted FMI")+
  scale_y_continuous(limits = c(0,1))+
  scale_x_continuous(labels = comma)+
  scale_size(range = c(2,8), breaks = c(5,10,15), limits = c(0,15), name = "Marine Capture Production (million mt, 2017)")+
  theme(legend.position = "top")+
  scale_color_discrete(guide = "none")

ggsave(paste0(results_dir, "fmi_flag_melnychuk_allbad.png"), width = 7, height = 4.5, units = "in")
```

```{r}
# Plot fuel subsidies only 
ggplot(fmi_flag_melnychuk_only)+
  aes(x = tot_fuel_subs/1e6, y = fmi_weighted, size = tot_landings/1e6, color = display_name)+
  geom_point()+
  geom_text_repel(aes(label = display_name), size = 4, force = 100, point.padding = 0.25, box.padding = 1)+
  theme_linedraw()+
  labs(x = "Total fuel subsidies (million 2018 $US)",
       y = "Weighted FMI")+
  scale_y_continuous(limits = c(0,1))+
  scale_x_continuous(labels = comma)+
  scale_size(range = c(2,8), breaks = c(5,10,15), limits = c(0,15), name = "Marine Capture Production (million mt, 2017)")+
  theme(legend.position = "top")+
  scale_color_discrete(guide = "none")

ggsave(paste0(results_dir, "fmi_flag_melnychuk_fuel.png"), width = 7, height = 4.5, units = "in")
```

```{r}
# For later use, get fraction of catch in each region from catch share fisheries, vs. not
# costello_catch_share_frac <- costello_2016_dat_edit %>%
#   group_by(region, catch_share) %>%
#   summarize(landings = sum(catch_new, na.rm = T)) %>%
#   ungroup() %>%
#   group_by(region) %>%
#   mutate(tot_landings = sum(landings, na.rm = T)) %>%
#   ungroup() %>%
#   mutate(frac_landings = landings/tot_landings) %>%
#   arrange(region)
```

### 2020-03-16 papers/paper-1/paper_1_figures.Rmd
v1 of the paper done

@@
 
-plot_theme <- theme_bw()
+plot_theme <- theme_bw()+
+  theme(legend.text = element_text(color = "black", size = 16),
+        legend.title = element_text(color = "black", size = 16),
+        legend.title.align = 1,
+        legend.direction = "horizontal",
+        legend.position = "bottom",
+        legend.justification = "center",
+        axis.text = element_text(color = "black", size = rel(1)))
 
@@
 
-# EU countries
-eu_countries <- country_dependencies$iso3[country_dependencies$is_EU]
+# Netherlands overseas territories
+nld_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "NLD"]
 
-# EU overseas territories
-eu_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 %in% eu_countries]
+# France overseas territories
+fra_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "FRA"]
+
+# Denmark overseas territories
+dnk_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "DNK"]
+
+# British overseas territories
+gbr_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "GBR"]
+
+# Norway overseas territories
+nor_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "NOR"]
 
 # US overseas territories:  American Samoa, Guam, Northern Marianas Islands, Puerto Rico, US Virgin Islands
-us_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "USA"]
+usa_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "USA"]
+
+# Australian overseas territories: Christmas Island
+aus_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "AUS"]
 ```
@@
 effort_binned <- effort_binned_good_fishing_vessels_2018 %>%
-  mutate(is_eu = case_when(flag %in% c(eu_countries, eu_territories) ~ TRUE,
-                           TRUE ~ FALSE),
-         is_usa = case_when(flag %in% c(us_territories, "USA") ~ TRUE,
-                            TRUE ~ FALSE),
-         new_flag = case_when(is_eu ~ "EU", 
-                              is_usa ~ "USA", 
+  mutate(new_flag = case_when(flag %in% nld_territories ~ "NLD",
+                              flag %in% fra_territories ~ "FRA",
+                              flag %in% dnk_territories ~ "DNK",
+                              flag %in% gbr_territories ~ "GBR",
+                              flag %in% nor_territories ~ "NOR",
+                              flag %in% usa_territories ~ "USA",
+                              flag %in% aus_territories ~ "AUS",
+                              flag == "COK" ~ "NZL", # for now assign cook islands to new zealand
                               TRUE ~ flag))
@@
          B_subs = B,
-         C_subs = C)
+         C_subs = C) %>%
+  mutate(BC_subs = B_subs + C_subs,
+         tot_subs = A_subs + B_subs + C_subs)
 ```
@@
          C_subs_KWh = C_subs/fishing_KWh_lat_lon,
-         tot_subs_KWh = (A_subs+B_subs+C_subs)/fishing_KWh_lat_lon) %>%
+         BC_subs_KWh = BC_subs/fishing_KWh_lat_lon,
+         tot_subs_KWh = tot_subs/fishing_KWh_lat_lon) %>%
   dplyr::select(new_flag, contains("subs_KWh"))
@@
   left_join(subsidy_rates_flag, by = "new_flag")
+
+# Summarize by lat/lon
+subsidy_intensity_binned <- effort_binned_sub_intensity %>%
+  group_by(lat_bin_center, lon_bin_center) %>%
+  summarize(med_B_subs_KWh = median(B_subs_KWh, na.rm = T),
+            med_BC_subs_KWh = median(BC_subs_KWh, na.rm = T),
+            med_tot_subs_KWh = median(tot_subs_KWh, na.rm = T),
+            mean_B_subs_KWh = mean(B_subs_KWh, na.rm = T),
+            mean_BC_subs_KWh = mean(BC_subs_KWh, na.rm = T),
+            mean_tot_subs_KWh = mean(tot_subs_KWh, na.rm = T),
+            w_mean_B_subs_KWh = weighted.mean(B_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
+            w_mean_BC_subs_KWh = weighted.mean(BC_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
+            w_mean_tot_subs_KWh = weighted.mean(tot_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
+            tot_fishing_KWh = sum(fishing_KWh_lat_lon, na.rm = T))
+
+# Summarize by fao region
+subsidy_intensity_region <- effort_binned_sub_intensity %>%
+  group_by(fao_region) %>%
+  summarize(med_B_subs_KWh = median(B_subs_KWh, na.rm = T),
+            med_BC_subs_KWh = median(BC_subs_KWh, na.rm = T),
+            med_tot_subs_KWh = median(tot_subs_KWh, na.rm = T),
+            mean_B_subs_KWh = mean(B_subs_KWh, na.rm = T),
+            mean_BC_subs_KWh = mean(BC_subs_KWh, na.rm = T),
+            mean_tot_subs_KWh = mean(tot_subs_KWh, na.rm = T),
+            w_mean_B_subs_KWh = weighted.mean(B_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
+            w_mean_BC_subs_KWh = weighted.mean(BC_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
+            w_mean_tot_subs_KWh = weighted.mean(tot_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
+            tot_fishing_KWh = sum(fishing_KWh_lat_lon, na.rm = T))
 ```
@@
 ```{r}
-median_breaks <- seq(0,6, by = 1)
-median_limits <- c(0,6)
-median_labels <- c("0", "1", "2", "3", "4", "5", paste0("\u2265","6"))
+median_breaks <- seq(0,8, by = 2)
+median_limits <- c(0,8)
+median_labels <- c("0", "2", "4", "6", paste0("\u2265","8"))
 
-median_subsidy_intensity_B_grid_map <- effort_binned_sub_intensity %>%
-  group_by(year, lat_bin_center, lon_bin_center) %>%
-  summarize(med_B_subs_KWh = median(B_subs_KWh, na.rm = T)) %>%
+# Total subsidies
+median_subsidy_intensity_tot_grid_map <- subsidy_intensity_binned %>%
+  ggplot()+
+  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = med_tot_subs_KWh)) +
+  geom_sf(data=world_land, color = NA, fill="grey30") +
+  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
+  scale_fill_viridis_c(name="Median Subsidy Intensity \n($/KWh)", 
+                       na.value = "#000000", 
+                       limits = median_limits, 
+                       breaks = median_breaks,
+                       labels = median_labels,
+                       oob = scales::squish) +
+  scale_x_continuous(expand = c(0,0))+
+  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
+  xlab("") +
+  ylab("") +
+  map_theme + 
+  guides(fill=guide_colorbar(
+   title.position = "left",
+   title.hjust = 0.5,
+   frame.colour = "white",
+   barwidth=4,
+   barheight=0.25,
+   default.unit="inch"))
+
+median_subsidy_intensity_tot_grid_map
+
+ggsave(paste0(results_dir, "median_subsidy_intensity_tot_grid_map.png"), dpi = 200, width = 7, height = 5)
+
+# Bad subsidies only
+median_subsidy_intensity_B_grid_map <- subsidy_intensity_binned %>%
   ggplot()+
@@
 
+# Bad and ambiguous subsidies
+median_subsidy_intensity_BC_grid_map <- subsidy_intensity_binned %>%
+  ggplot()+
+  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = med_BC_subs_KWh)) +
+  geom_sf(data=world_land, color = NA, fill="grey30") +
+  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
+  scale_fill_viridis_c(name="Median Subsidy Intensity \n($/KWh)", 
+                       na.value = "#000000", 
+                       limits = median_limits, 
+                       breaks = median_breaks,
+                       labels = median_labels,
+                       oob = scales::squish) +
+  scale_x_continuous(expand = c(0,0))+
+  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
+  xlab("") +
+  ylab("") +
+  map_theme + 
+  guides(fill=guide_colorbar(
+   title.position = "left",
+   title.hjust = 0.5,
+   frame.colour = "white",
+   barwidth=4,
+   barheight=0.25,
+   default.unit="inch"))
+
+median_subsidy_intensity_BC_grid_map
+
+ggsave(paste0(results_dir, "median_subsidy_intensity_BC_grid_map.png"), dpi = 200, width = 7, height = 5)
+
 ```
@@
 
-median_subsidy_intensity_B_region_map <- effort_binned_sub_intensity %>%
-  group_by(year, fao_region) %>%
-  summarize(med_B_subs_KWh = median(B_subs_KWh, na.rm = T)) %>%
+# Total subsidies
+median_subsidy_intensity_tot_region_map <- subsidy_intensity_region %>%
+  right_join(fao_regions, by = "fao_region") %>%
+  ggplot()+
+  geom_sf(aes(geometry = geometry, fill = med_tot_subs_KWh), color = "#000000") +
+  geom_sf(data=world_land, color = NA, fill="grey30") +
+  scale_fill_viridis_c(name="Median Subsidy Intensity \n($/KWh)", 
+                       na.value = "#000000", 
+                       limits = region_median_limits, 
+                       breaks = region_median_breaks,
+                       labels = region_median_labels,
+                       oob = scales::squish) +
+  scale_x_continuous(expand = c(0,0))+
+  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
+  xlab("") +
+  ylab("") +
+  map_theme + 
+  guides(fill=guide_colorbar(
+   title.position = "left",
+   title.hjust = 0.5,
+   frame.colour = "white",
+   barwidth=4,
+   barheight=0.25,
+   default.unit="inch"))
+
+median_subsidy_intensity_tot_region_map
+
+ggsave(paste0(results_dir, "median_subsidy_intensity_tot_region_map.png"), dpi = 200, width = 7, height = 5)
+
+# Bad subsidies
+median_subsidy_intensity_B_region_map <- subsidy_intensity_region %>%
   right_join(fao_regions, by = "fao_region") %>%
@@
   geom_sf(data=world_land, color = NA, fill="grey30") +
-  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
   scale_fill_viridis_c(name="Median Subsidy Intensity \n($/KWh)", 
@@
 
+# Ambiguous and Bad subsidies
+median_subsidy_intensity_BC_region_map <- subsidy_intensity_region %>%
+  right_join(fao_regions, by = "fao_region") %>%
+  ggplot()+
+  geom_sf(aes(geometry = geometry, fill = med_BC_subs_KWh), color = "#000000") +
+  geom_sf(data=world_land, color = NA, fill="grey30") +
+  scale_fill_viridis_c(name="Median Subsidy Intensity \n($/KWh)", 
+                       na.value = "#000000", 
+                       limits = region_median_limits, 
+                       breaks = region_median_breaks,
+                       labels = region_median_labels,
+                       oob = scales::squish) +
+  scale_x_continuous(expand = c(0,0))+
+  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
+  xlab("") +
+  ylab("") +
+  map_theme + 
+  guides(fill=guide_colorbar(
+   title.position = "left",
+   title.hjust = 0.5,
+   frame.colour = "white",
+   barwidth=4,
+   barheight=0.25,
+   default.unit="inch"))
+
+median_subsidy_intensity_BC_region_map
+
+ggsave(paste0(results_dir, "median_subsidy_intensity_BC_region_map.png"), dpi = 200, width = 7, height = 5)
+
 ```
@@
 ```{r}
-mean_breaks <- seq(0,6, by = 1)
-mean_limits <- c(0,6)
-mean_labels <- c("0", "1", "2", "3", "4", "5", paste0("\u2265","6"))
+mean_breaks <- seq(0,8, by = 2)
+mean_limits <- c(0,8)
+mean_labels <- c("0", "2", "4", "6", paste0("\u2265","8"))
 
-mean_subsidy_intensity_B_grid_map <- effort_binned_sub_intensity %>%
-  group_by(year, lat_bin_center, lon_bin_center) %>%
-  summarize(mean_B_subs_KWh = mean(B_subs_KWh, na.rm = T)) %>%
+# Total subsidies 
+mean_subsidy_intensity_tot_grid_map <- subsidy_intensity_binned %>%
+  ggplot()+
+  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = mean_tot_subs_KWh)) +
+  geom_sf(data=world_land, color = NA, fill="grey30") +
+  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
+  scale_fill_viridis_c(name="Mean Subsidy Intensity \n($/KWh)", 
+                     na.value = "#000000", 
+                     limits = mean_limits, 
+                     breaks = mean_breaks,
+                     labels = mean_labels,
+                     oob = scales::squish) +
+  scale_x_continuous(expand = c(0,0))+
+  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
+  xlab("") +
+  ylab("") +
+  map_theme + 
+  guides(fill=guide_colorbar(
+   title.position = "left",
+   title.hjust = 0.5,
+   frame.colour = "white",
+   barwidth=4,
+   barheight=0.25,
+   default.unit="inch"))
+
+mean_subsidy_intensity_tot_grid_map
+
+ggsave(paste0(results_dir, "mean_subsidy_intensity_tot_grid_map.png"), dpi = 200, width = 7, height = 5)
+
+# Bad subsidies 
+mean_subsidy_intensity_B_grid_map <- subsidy_intensity_binned %>%
   ggplot()+
@@
 ggsave(paste0(results_dir, "mean_subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 5)
+
+# Bad and ambiguous subsidies 
+mean_subsidy_intensity_BC_grid_map <- subsidy_intensity_binned %>%
+  ggplot()+
+  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = mean_BC_subs_KWh)) +
+  geom_sf(data=world_land, color = NA, fill="grey30") +
+  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
+  scale_fill_viridis_c(name="Mean Subsidy Intensity \n($/KWh)", 
+                     na.value = "#000000", 
+                     limits = mean_limits, 
+                     breaks = mean_breaks,
+                     labels = mean_labels,
+                     oob = scales::squish) +
+  scale_x_continuous(expand = c(0,0))+
+  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
+  xlab("") +
+  ylab("") +
+  map_theme + 
+  guides(fill=guide_colorbar(
+   title.position = "left",
+   title.hjust = 0.5,
+   frame.colour = "white",
+   barwidth=4,
+   barheight=0.25,
+   default.unit="inch"))
+
+mean_subsidy_intensity_BC_grid_map
+
+ggsave(paste0(results_dir, "mean_subsidy_intensity_BC_grid_map.png"), dpi = 200, width = 7, height = 5)
 ```
@@
 ```{r}
-mean_subsidy_intensity_B_region_map <- effort_binned_sub_intensity %>%
-  group_by(year, fao_region) %>%
-  summarize(mean_B_subs_KWh = mean(B_subs_KWh, na.rm = T)) %>%
+# Tot subs
+mean_subsidy_intensity_tot_region_map <- subsidy_intensity_region %>%
+  right_join(fao_regions, by = "fao_region") %>%
+  ggplot()+
+  geom_sf(aes(geometry = geometry, fill = mean_tot_subs_KWh)) +
+  geom_sf(data=world_land, color = NA, fill="grey30") +
+  scale_fill_viridis_c(name="Mean Subsidy Intensity \n($/KWh)", 
+                       na.value = "#000000", 
+                       limits = mean_limits, 
+                       breaks = mean_breaks,
+                       labels = mean_labels,
+                       oob = scales::squish) +
+  scale_x_continuous(expand = c(0,0))+
+  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
+  xlab("") +
+  ylab("") +
+  map_theme + 
+  guides(fill=guide_colorbar(
+   title.position = "left",
+   title.hjust = 0.5,
+   frame.colour = "white",
+   barwidth=4,
+   barheight=0.25,
+   default.unit="inch"))
+
+mean_subsidy_intensity_tot_region_map
+
+ggsave(paste0(results_dir, "mean_subsidy_intensity_tot_region_map.png"), dpi = 200, width = 7, height = 5)
+
+# Bad subs
+mean_subsidy_intensity_B_region_map <- subsidy_intensity_region %>%
   right_join(fao_regions, by = "fao_region") %>%
@@
   geom_sf(data=world_land, color = NA, fill="grey30") +
-  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
-  scale_fill_viridis_c(name="Mean Subsidy Intensity ($/KWh)", 
+  scale_fill_viridis_c(name="Mean Subsidy Intensity \n($/KWh)", 
                        na.value = "#000000", 
@@
 ggsave(paste0(results_dir, "mean_subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 5)
+
+# Bad and ambiguous subs
+mean_subsidy_intensity_BC_region_map <- subsidy_intensity_region %>%
+  right_join(fao_regions, by = "fao_region") %>%
+  ggplot()+
+  geom_sf(aes(geometry = geometry, fill = mean_BC_subs_KWh)) +
+  geom_sf(data=world_land, color = NA, fill="grey30") +
+  scale_fill_viridis_c(name="Mean Subsidy Intensity \n($/KWh)", 
+                       na.value = "#000000", 
+                       limits = mean_limits, 
+                       breaks = mean_breaks,
+                       labels = mean_labels,
+                       oob = scales::squish) +
+  scale_x_continuous(expand = c(0,0))+
+  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
+  xlab("") +
+  ylab("") +
+  map_theme + 
+  guides(fill=guide_colorbar(
+   title.position = "left",
+   title.hjust = 0.5,
+   frame.colour = "white",
+   barwidth=4,
+   barheight=0.25,
+   default.unit="inch"))
+
+mean_subsidy_intensity_BC_region_map
+
+ggsave(paste0(results_dir, "mean_subsidy_intensity_BC_region_map.png"), dpi = 200, width = 7, height = 5)
 ```
@@
 
-weighted_mean_subsidy_intensity_B_grid_map <- effort_binned_sub_intensity %>%
-  group_by(year, lat_bin_center, lon_bin_center) %>%
-  summarize(weighted_mean_B_subs_KWh = weighted.mean(B_subs_KWh, w = fishing_KWh_lat_lon)) %>%
+# Tot subs
+w_mean_subsidy_intensity_tot_grid_map <- subsidy_intensity_binned %>%
   ggplot()+
-  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = weighted_mean_B_subs_KWh)) +
+  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = w_mean_tot_subs_KWh)) +
   geom_sf(data=world_land, color = NA, fill="grey30") +
@@
 
-weighted_mean_subsidy_intensity_B_grid_map
+w_mean_subsidy_intensity_tot_grid_map
 
-ggsave(paste0(results_dir, "weighted_mean_subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 5)
+ggsave(paste0(results_dir, "w_mean_subsidy_intensity_tot_grid_map.png"), dpi = 200, width = 7, height = 5)
+
+# Bad subs
+w_mean_subsidy_intensity_B_grid_map <- subsidy_intensity_binned %>%
+  ggplot()+
+  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = w_mean_B_subs_KWh)) +
+  geom_sf(data=world_land, color = NA, fill="grey30") +
+  scale_fill_viridis_c(name="Weighted Mean Subsidy Intensity \n($/KWh)", 
+                       na.value = "#000000", 
+                       limits = weighted_mean_limits, 
+                       breaks = weighted_mean_breaks,
+                       labels = weighted_mean_labels,
+                       oob = scales::squish) +
+  scale_x_continuous(expand = c(0,0))+
+  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
+  xlab("") +
+  ylab("") +
+  map_theme + 
+  guides(fill=guide_colorbar(
+   title.position = "left",
+   title.hjust = 0.5,
+   frame.colour = "white",
+   barwidth=4,
+   barheight=0.25,
+   default.unit="inch"))
+
+w_mean_subsidy_intensity_B_grid_map
+
+ggsave(paste0(results_dir, "w_mean_subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 5)
+
+# Bad and ambiguous subs
+w_mean_subsidy_intensity_BC_grid_map <- subsidy_intensity_binned %>%
+  ggplot()+
+  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = w_mean_BC_subs_KWh)) +
+  geom_sf(data=world_land, color = NA, fill="grey30") +
+  scale_fill_viridis_c(name="Weighted Mean Subsidy Intensity \n($/KWh)", 
+                       na.value = "#000000", 
+                       limits = weighted_mean_limits, 
+                       breaks = weighted_mean_breaks,
+                       labels = weighted_mean_labels,
+                       oob = scales::squish) +
+  scale_x_continuous(expand = c(0,0))+
+  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
+  xlab("") +
+  ylab("") +
+  map_theme + 
+  guides(fill=guide_colorbar(
+   title.position = "left",
+   title.hjust = 0.5,
+   frame.colour = "white",
+   barwidth=4,
+   barheight=0.25,
+   default.unit="inch"))
+
+w_mean_subsidy_intensity_BC_grid_map
+
+ggsave(paste0(results_dir, "w_mean_subsidy_intensity_BC_grid_map.png"), dpi = 200, width = 7, height = 5)
 ```
@@
 
-weighted_mean_subsidy_intensity_B_region_map <- effort_binned_sub_intensity %>%
-  group_by(year, fao_region) %>%
-  summarize(weighted_mean_B_subs_KWh = weighted.mean(B_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T)) %>%
+# Tot subs
+w_mean_subsidy_intensity_tot_region_map <- subsidy_intensity_region %>%
   right_join(fao_regions, by = "fao_region") %>%
   ggplot()+
-  geom_sf(aes(geometry = geometry, fill = weighted_mean_B_subs_KWh)) +
+  geom_sf(aes(geometry = geometry, fill = w_mean_tot_subs_KWh)) +
   geom_sf(data=world_land, color = NA, fill="grey30") +
@@
 
-weighted_mean_subsidy_intensity_B_region_map
+w_mean_subsidy_intensity_tot_region_map
 
-ggsave(paste0(results_dir, "weighted_mean_subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 5)
+ggsave(paste0(results_dir, "w_mean_subsidy_intensity_tot_region_map.png"), dpi = 200, width = 7, height = 5)
+
+# Bad subs
+w_mean_subsidy_intensity_B_region_map <- subsidy_intensity_region %>%
+  right_join(fao_regions, by = "fao_region") %>%
+  ggplot()+
+  geom_sf(aes(geometry = geometry, fill = w_mean_B_subs_KWh)) +
+  geom_sf(data=world_land, color = NA, fill="grey30") +
+  scale_fill_viridis_c(name="Weighted Mean Subsidy Intensity \n($/KWh)", 
+                       na.value = "#000000", 
+                       limits = region_weighted_mean_limits, 
+                       breaks = region_weighted_mean_breaks,
+                       labels = region_weighted_mean_labels,
+                       oob = scales::squish) +
+  scale_x_continuous(expand = c(0,0))+
+  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
+  xlab("") +
+  ylab("") +
+  map_theme + 
+  guides(fill=guide_colorbar(
+   title.position = "left",
+   title.hjust = 0.5,
+   frame.colour = "white",
+   barwidth=4,
+   barheight=0.25,
+   default.unit="inch"))
+
+w_mean_subsidy_intensity_B_region_map
+
+ggsave(paste0(results_dir, "w_mean_subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 5)
+
+# Bad and ambiguous subs
+w_mean_subsidy_intensity_BC_region_map <- subsidy_intensity_region %>%
+  right_join(fao_regions, by = "fao_region") %>%
+  ggplot()+
+  geom_sf(aes(geometry = geometry, fill = w_mean_BC_subs_KWh)) +
+  geom_sf(data=world_land, color = NA, fill="grey30") +
+  scale_fill_viridis_c(name="Weighted Mean Subsidy Intensity \n($/KWh)", 
+                       na.value = "#000000", 
+                       limits = region_weighted_mean_limits, 
+                       breaks = region_weighted_mean_breaks,
+                       labels = region_weighted_mean_labels,
+                       oob = scales::squish) +
+  scale_x_continuous(expand = c(0,0))+
+  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
+  xlab("") +
+  ylab("") +
+  map_theme + 
+  guides(fill=guide_colorbar(
+   title.position = "left",
+   title.hjust = 0.5,
+   frame.colour = "white",
+   barwidth=4,
+   barheight=0.25,
+   default.unit="inch"))
+
+w_mean_subsidy_intensity_BC_region_map
+
+ggsave(paste0(results_dir, "w_mean_subsidy_intensity_BC_region_map.png"), dpi = 200, width = 7, height = 5)
 ```
 
-### Stock status
+### Overfishing status
 
@@
 
-upsides_regional_averages <- upsides_dat %>%
+upsides_region <- upsides_dat %>%
   group_by(region_fao_split) %>%
-  summarize(mean_f_v_fmsy = mean(fv_fmsy),
-            mean_weighted_f_v_fmsy = weighted.mean(fv_fmsy, w = msy),
-            median_f_v_fmsy = median(fv_fmsy),
-            mean_b_v_bmsy = mean(bv_bmsy),
-            mean_weighted_b_v_bmsy = weighted.mean(bv_bmsy, w = msy),
-            median_b_v_bmsy = median(bv_bmsy))
-
-```
-
-```{r}
-
-upsides_regional_averages_spatial <- fao_regions %>%
-  right_join(upsides_regional_averages, by = c("fao_region" = "region_fao_split"))
+  summarize(mean_f_v_fmsy = mean(fv_fmsy, na.rm = T),
+            w_mean_f_v_fmsy = weighted.mean(fv_fmsy, w = msy, na.rm = T),
+            med_f_v_fmsy = median(fv_fmsy, na.rm = T),
+            mean_b_v_bmsy = mean(bv_bmsy, na.rm = T),
+            w_mean_b_v_bmsy = weighted.mean(bv_bmsy, w = msy, na.rm = T),
+            med_b_v_bmsy = median(bv_bmsy, na.rm = T),
+            tot_msy = sum(msy, na.rm = T)) %>%
+  rename(fao_region = region_fao_split) %>%
+  right_join(fao_regions, by = c("fao_region"))
 
@@
 ```{r}
-mean_f_v_fmsy_regional_map <- ggplot()+
-  geom_sf(data=upsides_regional_averages_spatial, color = "black", aes(fill = mean_f_v_fmsy)) +
+mean_f_v_fmsy_region_map <- ggplot()+
+  geom_sf(data=upsides_region, color = "black", aes(geometry = geometry, fill = mean_f_v_fmsy)) +
   geom_sf(data=world_land, color = NA, fill="grey30") +
   #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
-  scale_fill_viridis_c(name="Mean F/Fmsy", na.value = "#000000") +
+  scale_fill_viridis_c(name="Mean F/Fmsy", 
+                       na.value = "#000000") +
   scale_x_continuous(expand = c(0,0))+
@@
   map_theme + 
- guides(fill=guide_legend(
-                 keywidth=0.25,
-                 keyheight=0.25,
+  guides(fill=guide_colorbar(
+   title.position = "left",
+   title.hjust = 0.5,
+   frame.colour = "white",
+   barwidth=4,
+   barheight=0.25,
    default.unit="inch"))
 
-mean_f_v_fmsy_regional_map
+mean_f_v_fmsy_region_map
 
-ggsave(paste0(results_dir, "mean_f_v_fmsy_regional_map.png"), dpi = 200, width = 7, height = 5)
+ggsave(paste0(results_dir, "mean_f_v_fmsy_region_map.png"), dpi = 200, width = 7, height = 5)
 ```
@@
 ```{r}
-weighted_mean_f_v_fmsy_regional_map <- ggplot()+
-  geom_sf(data=upsides_regional_averages_spatial, color = "black", aes(fill = mean_weighted_f_v_fmsy)) +
+w_mean_f_v_fmsy_region_map <- ggplot()+
+  geom_sf(data=upsides_region, color = "black", aes(geometry = geometry, fill = w_mean_f_v_fmsy)) +
   geom_sf(data=world_land, color = NA, fill="grey30") +
@@
   map_theme + 
-  guides(fill=guide_legend(
-                 keywidth=0.25,
-                 keyheight=0.25,
+  guides(fill=guide_colorbar(
+   title.position = "left",
+   title.hjust = 0.5,
+   frame.colour = "white",
+   barwidth=4,
+   barheight=0.25,
    default.unit="inch"))
 
-weighted_mean_f_v_fmsy_regional_map
+w_mean_f_v_fmsy_region_map
 
-ggsave(paste0(results_dir, "weighted_mean_f_v_fmsy_regional_map.png"), dpi = 200, width = 7, height = 5)
+ggsave(paste0(results_dir, "w_mean_f_v_fmsy_region_map.png"), dpi = 200, width = 7, height = 5)
 ```
@@
 ```{r}
-median_f_v_fmsy_regional_map <- ggplot()+
-  geom_sf(data=upsides_regional_averages_spatial, color = "black", aes(fill = median_f_v_fmsy)) +
+median_f_v_fmsy_region_map <- ggplot()+
+  geom_sf(data=upsides_region, color = "black", aes(geometry = geometry, fill = med_f_v_fmsy)) +
   geom_sf(data=world_land, color = NA, fill="grey30") +
@@
   map_theme +
- guides(fill=guide_legend(
-                 keywidth=0.25,
-                 keyheight=0.25,
+  guides(fill=guide_colorbar(
+   title.position = "left",
+   title.hjust = 0.5,
+   frame.colour = "white",
+   barwidth=4,
+   barheight=0.25,
    default.unit="inch"))
 
-median_f_v_fmsy_regional_map
+median_f_v_fmsy_region_map
 
-ggsave(paste0(results_dir, "median_f_v_fmsy_regional_map.png"), dpi = 200, width = 7, height = 5)
+ggsave(paste0(results_dir, "median_f_v_fmsy_region_map.png"), dpi = 200, width = 7, height = 5)
 ```
+
+### Combine
+
+```{r}
+subsidy_intensity_upsides_region <- upsides_region %>%
+  left_join(subsidy_intensity_region, by = "fao_region")
+
+# Weighted mean of Bad + Ambig vs F/Fmsy
+w_mean_BC_vs_f_v_fmsy_plot <- ggplot(subsidy_intensity_upsides_region)+
+  aes(x = w_mean_BC_subs_KWh, y = w_mean_f_v_fmsy, size = tot_fishing_KWh, color = tot_fishing_KWh)+
+  geom_point()+
+  scale_color_viridis_c(name="Total Fishing Effort \n(KWh)", na.value = "#000000")+
+  scale_x_continuous(limits = c(0,2))+
+  scale_y_continuous(limits = c(0,2.5))+
+  xlab("Weighted Mean Subsidy Intensity ($/KWh)") +
+  ylab("Weighted Mean F/Fmsy") +
+  geom_hline(yintercept = 1, linetype = "dashed")+
+  geom_vline(xintercept = 1, linetype = "dashed")+
+  plot_theme+
+  guides(color=guide_colorbar(
+   title.position = "left",
+   title.hjust = 0.5,
+   frame.colour = "white",
+   barwidth=4,
+   barheight=0.25,
+   default.unit="inch"),
+   size = "none")
+
+w_mean_BC_vs_f_v_fmsy_plot
+
+ggsave(paste0(results_dir, "w_mean_BC_vs_f_v_fmsy_plot.png"), dpi = 200, width = 7, height = 7)
+```

### 2020-03-19 papers/paper-1/paper_1_figures.Rmd
remaking paper 1 figures

--- 2020-03-16 papers/paper-1/paper_1_figures.Rmd
@@
 library(rmapshaper)
+library(RColorBrewer)
+library(cowplot)
 library(tidyverse)
+
+source(here::here("functions", "MapMaker.R"))
 
@@
 ```{r}
-# Plot themes and shapefiles
-map_theme <- theme(panel.background = element_rect(fill ="black"),
-        plot.background = element_rect(fill = "black"),
-        legend.background=element_rect(fill="black"),
-        legend.text = element_text(color = "white", size = 16),
-        legend.title = element_text(color = "white", size = 16),
-        legend.title.align = 1,
-        legend.direction="horizontal",
-        legend.position = "bottom",
-        legend.justification = "center",
-        axis.text = element_text(color = "white", size = rel(1)),
-        panel.grid.major = element_blank(),
-        axis.title.x = element_blank(),
-        axis.text.x=element_blank(),
-        axis.ticks.x=element_blank(),
-        axis.title.y=element_blank(),
-        axis.text.y=element_blank(),
-        axis.ticks.y=element_blank())
-
-plot_theme <- theme_bw()
-
 # Land shapefile
@@
 effort_binned_sub_intensity <- effort_binned %>%
-  left_join(subsidy_rates_flag, by = "new_flag")
+  left_join(subsidy_rates_flag, by = "new_flag") %>%
+  mutate(B_subs = B_subs_KWh*fishing_KWh_lat_lon,
+         BC_subs = BC_subs_KWh*fishing_KWh_lat_lon,
+         C_subs = C_subs_KWh*fishing_KWh_lat_lon,
+         tot_subs = tot_subs_KWh*fishing_KWh_lat_lon)
+
+# Summarize by lat/lon
+subsidy_intensity_binned <- effort_binned_sub_intensity %>%
+  group_by(lat_bin_center, lon_bin_center) %>%
+  summarize(med_B_subs_KWh = median(B_subs_KWh, na.rm = T),
+            med_BC_subs_KWh = median(BC_subs_KWh, na.rm = T),
+            med_tot_subs_KWh = median(tot_subs_KWh, na.rm = T),
+            mean_B_subs_KWh = mean(B_subs_KWh, na.rm = T),
+            mean_BC_subs_KWh = mean(BC_subs_KWh, na.rm = T),
+            mean_tot_subs_KWh = mean(tot_subs_KWh, na.rm = T),
+            w_mean_B_subs_KWh = weighted.mean(B_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
+            w_mean_BC_subs_KWh = weighted.mean(BC_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
+            w_mean_tot_subs_KWh = weighted.mean(tot_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
+            B_subs = sum(B_subs, na.rm = T),
+            BC_subs = sum(BC_subs, na.rm = T),
+            C_subs = sum(C_subs, na.rm = T),
+            tot_subs = sum(tot_subs, na.rm = T),
+            tot_fishing_KWh = sum(fishing_KWh_lat_lon, na.rm = T))
+
+# Summarize by fao region
+subsidy_intensity_region <- effort_binned_sub_intensity %>%
+  group_by(fao_region) %>%
+  summarize(med_B_subs_KWh = median(B_subs_KWh, na.rm = T),
+            med_BC_subs_KWh = median(BC_subs_KWh, na.rm = T),
+            med_tot_subs_KWh = median(tot_subs_KWh, na.rm = T),
+            mean_B_subs_KWh = mean(B_subs_KWh, na.rm = T),
+            mean_BC_subs_KWh = mean(BC_subs_KWh, na.rm = T),
+            mean_tot_subs_KWh = mean(tot_subs_KWh, na.rm = T),
+            w_mean_B_subs_KWh = weighted.mean(B_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
+            w_mean_BC_subs_KWh = weighted.mean(BC_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
+            w_mean_tot_subs_KWh = weighted.mean(tot_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
+            B_subs = sum(B_subs, na.rm = T),
+            BC_subs = sum(BC_subs, na.rm = T),
+            C_subs = sum(C_subs, na.rm = T),
+            tot_subs = sum(tot_subs, na.rm = T),
+            tot_fishing_KWh = sum(fishing_KWh_lat_lon, na.rm = T))
 ```
@@
 
-Now let's calculate and plot the median bad subsidy intensities by lat/lon bin and FAO region.
+## Total Subsidies
+
+### Subsidy Intensities by Lat/Lon
 
 ```{r}
-median_breaks <- seq(0,6, by = 1)
-median_limits <- c(0,6)
-median_labels <- c("0", "1", "2", "3", "4", "5", paste0("\u2265","6"))
+# Median
+median_subsidy_intensity_tot_grid_map <- MapMaker(data = subsidy_intensity_binned,
+                                                  res = "grid",
+                                                  x = "lon_bin_center",
+                                                  y = "lat_bin_center",
+                                                  fill = "med_tot_subs_KWh",
+                                                  fill_name = "Subsidy Intensity \n($/KWh)",
+                                                  fill_breaks = seq(0,8, by = 2),
+                                                  fill_limits = c(0,8),
+                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                                  land_sf = world_land)
 
-median_subsidy_intensity_B_grid_map <- effort_binned_sub_intensity %>%
-  group_by(year, lat_bin_center, lon_bin_center) %>%
-  summarize(med_B_subs_KWh = median(B_subs_KWh, na.rm = T)) %>%
-  ggplot()+
-  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = med_B_subs_KWh)) +
-  geom_sf(data=world_land, color = NA, fill="grey30") +
-  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
-  scale_fill_viridis_c(name="Median Subsidy Intensity \n($/KWh)", 
-                       na.value = "#000000", 
-                       limits = median_limits, 
-                       breaks = median_breaks,
-                       labels = median_labels,
-                       oob = scales::squish) +
-  scale_x_continuous(expand = c(0,0))+
-  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
-  xlab("") +
-  ylab("") +
-  map_theme + 
-  guides(fill=guide_colorbar(
-   title.position = "left",
-   title.hjust = 0.5,
-   frame.colour = "white",
-   barwidth=4,
-   barheight=0.25,
-   default.unit="inch"))
+ggsave(paste0(results_dir, "median_subsidy_intensity_tot_grid_map.png"), dpi = 200, width = 7, height = 5)
 
-median_subsidy_intensity_B_grid_map
+# Mean
+mean_subsidy_intensity_tot_grid_map <- MapMaker(data = subsidy_intensity_binned,
+                                                  res = "grid",
+                                                  x = "lon_bin_center",
+                                                  y = "lat_bin_center",
+                                                  fill = "mean_tot_subs_KWh",
+                                                  fill_name = "Subsidy Intensity \n($/KWh)",
+                                                  fill_breaks = seq(0,8, by = 2),
+                                                  fill_limits = c(0,8),
+                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                                  land_sf = world_land)
+
+ggsave(paste0(results_dir, "mean_subsidy_intensity_tot_grid_map.png"), dpi = 200, width = 7, height = 5)
+
+# Weighted Mean
+w_mean_subsidy_intensity_tot_grid_map <- MapMaker(data = subsidy_intensity_binned,
+                                                  res = "grid",
+                                                  x = "lon_bin_center",
+                                                  y = "lat_bin_center",
+                                                  fill = "w_mean_tot_subs_KWh",
+                                                  fill_name = "Subsidy Intensity \n($/KWh)",
+                                                  fill_breaks = seq(0,8, by = 2),
+                                                  fill_limits = c(0,8),
+                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                                  land_sf = world_land)
+
+ggsave(paste0(results_dir, "w_mean_subsidy_intensity_tot_grid_map.png"), dpi = 200, width = 7, height = 5)
+
+# Combine into three panel
+intensity_tot_grid_legend <- get_legend(w_mean_subsidy_intensity_tot_grid_map)
+
+subsidy_intensity_tot_grid_map <- plot_grid(median_subsidy_intensity_tot_grid_map + theme(legend.position = "none"),
+                                            mean_subsidy_intensity_tot_grid_map + theme(legend.position = "none"),
+                                            w_mean_subsidy_intensity_tot_grid_map + theme(legend.position = "none"),
+                                            intensity_tot_grid_legend,
+                                            ncol = 1,
+                                            rel_heights = c(1,1,1,0.2),
+                                            labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
+                                            label_x = c(-0.04,-0.03,-0.1,0),
+                                            align = "v")
+
+subsidy_intensity_tot_grid_map
+ggsave(paste0(results_dir, "subsidy_intensity_tot_grid_map.png"), dpi = 200, width = 7, height = 12.5)
+
+```
+
+### Subsidy Intensities by Region
+
+```{r}
+# Median
+median_subsidy_intensity_tot_region_map <- MapMaker(data = subsidy_intensity_region,
+                                                  res = "region",
+                                                  fill = "med_tot_subs_KWh",
+                                                  fill_name = "Subsidy Intensity \n($/KWh)",
+                                                  fill_breaks = seq(0,8, by = 2),
+                                                  fill_limits = c(0,8),
+                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                                  land_sf = world_land,
+                                                  region_sf = fao_regions)
+
+ggsave(paste0(results_dir, "median_subsidy_intensity_tot_region_map.png"), dpi = 200, width = 7, height = 5)
+
+# Mean
+mean_subsidy_intensity_tot_region_map <- MapMaker(data = subsidy_intensity_region,
+                                                  res = "region",
+                                                  fill = "mean_tot_subs_KWh",
+                                                  fill_name = "Subsidy Intensity \n($/KWh)",
+                                                  fill_breaks = seq(0,8, by = 2),
+                                                  fill_limits = c(0,8),
+                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                                  land_sf = world_land,
+                                                  region_sf = fao_regions)
+
+ggsave(paste0(results_dir, "mean_subsidy_intensity_tot_region_map.png"), dpi = 200, width = 7, height = 5)
+
+# Weighted Mean
+w_mean_subsidy_intensity_tot_region_map <- MapMaker(data = subsidy_intensity_region,
+                                                  res = "region",
+                                                  fill = "w_mean_tot_subs_KWh",
+                                                  fill_name = "Subsidy Intensity \n($/KWh)",
+                                                  fill_breaks = seq(0,8, by = 2),
+                                                  fill_limits = c(0,8),
+                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                                  land_sf = world_land,
+                                                  region_sf = fao_regions)
+
+ggsave(paste0(results_dir, "w_mean_subsidy_intensity_tot_region_map.png"), dpi = 200, width = 7, height = 5)
+
+# Combine into three panel
+intensity_tot_region_legend <- get_legend(w_mean_subsidy_intensity_tot_region_map)
+
+subsidy_intensity_tot_region_map <- plot_grid(median_subsidy_intensity_tot_region_map + theme(legend.position = "none"),
+                                            mean_subsidy_intensity_tot_region_map + theme(legend.position = "none"),
+                                            w_mean_subsidy_intensity_tot_region_map + theme(legend.position = "none"),
+                                            intensity_tot_region_legend,
+                                            ncol = 1,
+                                            rel_heights = c(1,1,1,0.2),
+                                            labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
+                                            label_x = c(-0.04,-0.03,-0.1,0),
+                                            align = "v")
+
+subsidy_intensity_tot_region_map
+ggsave(paste0(results_dir, "subsidy_intensity_tot_region_map.png"), dpi = 200, width = 7, height = 12.5)
+
+```
+
+## Bad Subsidies
+
+### Subsidy Intensities by Lat/Lon
+
+```{r}
+# Median
+median_subsidy_intensity_B_grid_map <- MapMaker(data = subsidy_intensity_binned,
+                                                  res = "grid",
+                                                  x = "lon_bin_center",
+                                                  y = "lat_bin_center",
+                                                  fill = "med_B_subs_KWh",
+                                                  fill_name = "Subsidy Intensity \n($/KWh)",
+                                                  fill_breaks = seq(0,8, by = 2),
+                                                  fill_limits = c(0,8),
+                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                                  land_sf = world_land)
 
@@
 
+# Mean
+mean_subsidy_intensity_B_grid_map <- MapMaker(data = subsidy_intensity_binned,
+                                                  res = "grid",
+                                                  x = "lon_bin_center",
+                                                  y = "lat_bin_center",
+                                                  fill = "mean_B_subs_KWh",
+                                                  fill_name = "Subsidy Intensity \n($/KWh)",
+                                                  fill_breaks = seq(0,8, by = 2),
+                                                  fill_limits = c(0,8),
+                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                                  land_sf = world_land)
+
+ggsave(paste0(results_dir, "mean_subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 5)
+
+# Weighted Mean
+w_mean_subsidy_intensity_B_grid_map <- MapMaker(data = subsidy_intensity_binned,
+                                                  res = "grid",
+                                                  x = "lon_bin_center",
+                                                  y = "lat_bin_center",
+                                                  fill = "w_mean_B_subs_KWh",
+                                                  fill_name = "Subsidy Intensity \n($/KWh)",
+                                                  fill_breaks = seq(0,8, by = 2),
+                                                  fill_limits = c(0,8),
+                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                                  land_sf = world_land)
+
+ggsave(paste0(results_dir, "w_mean_subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 5)
+
+# Combine into three panel
+intensity_B_grid_legend <- get_legend(w_mean_subsidy_intensity_B_grid_map)
+
+subsidy_intensity_B_grid_map <- plot_grid(median_subsidy_intensity_B_grid_map + theme(legend.position = "none"),
+                                            mean_subsidy_intensity_B_grid_map + theme(legend.position = "none"),
+                                            w_mean_subsidy_intensity_B_grid_map + theme(legend.position = "none"),
+                                            intensity_B_grid_legend,
+                                            ncol = 1,
+                                            rel_heights = c(1,1,1,0.2),
+                                            labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
+                                            label_x = c(-0.04,-0.03,-0.1,0),
+                                            align = "v")
+
+subsidy_intensity_B_grid_map
+ggsave(paste0(results_dir, "subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 12.5)
+
 ```
 
+### Subsidy Intensities by Region
+
 ```{r}
-region_median_breaks <- seq(0,2, by = 0.5)
-region_median_limits <- c(0,2)
-region_median_labels <- c("0", "0.5", "1", "1.5", paste0("\u2265","2"))
-
-median_subsidy_intensity_B_region_map <- effort_binned_sub_intensity %>%
-  group_by(year, fao_region) %>%
-  summarize(med_B_subs_KWh = median(B_subs_KWh, na.rm = T)) %>%
-  right_join(fao_regions, by = "fao_region") %>%
-  ggplot()+
-  geom_sf(aes(geometry = geometry, fill = med_B_subs_KWh), color = "#000000") +
-  geom_sf(data=world_land, color = NA, fill="grey30") +
-  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
-  scale_fill_viridis_c(name="Median Subsidy Intensity \n($/KWh)", 
-                       na.value = "#000000", 
-                       limits = region_median_limits, 
-                       breaks = region_median_breaks,
-                       labels = region_median_labels,
-                       oob = scales::squish) +
-  scale_x_continuous(expand = c(0,0))+
-  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
-  xlab("") +
-  ylab("") +
-  map_theme + 
-  guides(fill=guide_colorbar(
-   title.position = "left",
-   title.hjust = 0.5,
-   frame.colour = "white",
-   barwidth=4,
-   barheight=0.25,
-   default.unit="inch"))
-
-median_subsidy_intensity_B_region_map
+# Median
+median_subsidy_intensity_B_region_map <- MapMaker(data = subsidy_intensity_region,
+                                                  res = "region",
+                                                  fill = "med_B_subs_KWh",
+                                                  fill_name = "Subsidy Intensity \n($/KWh)",
+                                                  fill_breaks = seq(0,8, by = 2),
+                                                  fill_limits = c(0,8),
+                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                                  land_sf = world_land,
+                                                  region_sf = fao_regions)
 
@@
 
+# Mean
+mean_subsidy_intensity_B_region_map <- MapMaker(data = subsidy_intensity_region,
+                                                  res = "region",
+                                                  fill = "mean_B_subs_KWh",
+                                                  fill_name = "Subsidy Intensity \n($/KWh)",
+                                                  fill_breaks = seq(0,8, by = 2),
+                                                  fill_limits = c(0,8),
+                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                                  land_sf = world_land,
+                                                  region_sf = fao_regions)
+
+ggsave(paste0(results_dir, "mean_subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 5)
+
+# Weighted Mean
+w_mean_subsidy_intensity_B_region_map <- MapMaker(data = subsidy_intensity_region,
+                                                  res = "region",
+                                                  fill = "w_mean_B_subs_KWh",
+                                                  fill_name = "Subsidy Intensity \n($/KWh)",
+                                                  fill_breaks = seq(0,8, by = 2),
+                                                  fill_limits = c(0,8),
+                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                                  land_sf = world_land,
+                                                  region_sf = fao_regions)
+
+ggsave(paste0(results_dir, "w_mean_subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 5)
+
+# Combine into three panel
+intensity_B_region_legend <- get_legend(w_mean_subsidy_intensity_B_region_map)
+
+subsidy_intensity_B_region_map <- plot_grid(median_subsidy_intensity_B_region_map + theme(legend.position = "none"),
+                                            mean_subsidy_intensity_B_region_map + theme(legend.position = "none"),
+                                            w_mean_subsidy_intensity_B_region_map + theme(legend.position = "none"),
+                                            intensity_B_region_legend,
+                                            ncol = 1,
+                                            rel_heights = c(1,1,1,0.2),
+                                            labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
+                                            label_x = c(-0.04,-0.03,-0.1,0),
+                                            align = "v")
+
+subsidy_intensity_B_region_map
+ggsave(paste0(results_dir, "subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 12.5)
+
 ```
 
-Do means too.
+## Bad + Ambiguous Subsidies
+
+### Subsidy Intensities by Lat/Lon
 
 ```{r}
-mean_breaks <- seq(0,6, by = 1)
-mean_limits <- c(0,6)
-mean_labels <- c("0", "1", "2", "3", "4", "5", paste0("\u2265","6"))
+# Median
+median_subsidy_intensity_BC_grid_map <- MapMaker(data = subsidy_intensity_binned,
+                                                  res = "grid",
+                                                  x = "lon_bin_center",
+                                                  y = "lat_bin_center",
+                                                  fill = "med_BC_subs_KWh",
+                                                  fill_name = "Subsidy Intensity \n($/KWh)",
+                                                  fill_breaks = seq(0,8, by = 2),
+                                                  fill_limits = c(0,8),
+                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                                  land_sf = world_land)
 
-mean_subsidy_intensity_B_grid_map <- effort_binned_sub_intensity %>%
-  group_by(year, lat_bin_center, lon_bin_center) %>%
-  summarize(mean_B_subs_KWh = mean(B_subs_KWh, na.rm = T)) %>%
-  ggplot()+
-  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = mean_B_subs_KWh)) +
-  geom_sf(data=world_land, color = NA, fill="grey30") +
-  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
-  scale_fill_viridis_c(name="Mean Subsidy Intensity \n($/KWh)", 
-                     na.value = "#000000", 
-                     limits = mean_limits, 
-                     breaks = mean_breaks,
-                     labels = mean_labels,
-                     oob = scales::squish) +
-  scale_x_continuous(expand = c(0,0))+
-  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
-  xlab("") +
-  ylab("") +
-  map_theme + 
-  guides(fill=guide_colorbar(
-   title.position = "left",
-   title.hjust = 0.5,
-   frame.colour = "white",
-   barwidth=4,
-   barheight=0.25,
-   default.unit="inch"))
+ggsave(paste0(results_dir, "median_subsidy_intensity_BC_grid_map.png"), dpi = 200, width = 7, height = 5)
 
-mean_subsidy_intensity_B_grid_map
+# Mean
+mean_subsidy_intensity_BC_grid_map <- MapMaker(data = subsidy_intensity_binned,
+                                                  res = "grid",
+                                                  x = "lon_bin_center",
+                                                  y = "lat_bin_center",
+                                                  fill = "mean_BC_subs_KWh",
+                                                  fill_name = "Subsidy Intensity \n($/KWh)",
+                                                  fill_breaks = seq(0,8, by = 2),
+                                                  fill_limits = c(0,8),
+                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                                  land_sf = world_land)
 
-ggsave(paste0(results_dir, "mean_subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 5)
+ggsave(paste0(results_dir, "mean_subsidy_intensity_BC_grid_map.png"), dpi = 200, width = 7, height = 5)
+
+# Weighted Mean
+w_mean_subsidy_intensity_BC_grid_map <- MapMaker(data = subsidy_intensity_binned,
+                                                  res = "grid",
+                                                  x = "lon_bin_center",
+                                                  y = "lat_bin_center",
+                                                  fill = "w_mean_BC_subs_KWh",
+                                                  fill_name = "Subsidy Intensity \n($/KWh)",
+                                                  fill_breaks = seq(0,8, by = 2),
+                                                  fill_limits = c(0,8),
+                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                                  land_sf = world_land)
+
+ggsave(paste0(results_dir, "w_mean_subsidy_intensity_BC_grid_map.png"), dpi = 200, width = 7, height = 5)
+
+# Combine into three panel
+intensity_BC_grid_legend <- get_legend(w_mean_subsidy_intensity_BC_grid_map)
+
+subsidy_intensity_BC_grid_map <- plot_grid(median_subsidy_intensity_BC_grid_map + theme(legend.position = "none"),
+                                            mean_subsidy_intensity_BC_grid_map + theme(legend.position = "none"),
+                                            w_mean_subsidy_intensity_BC_grid_map + theme(legend.position = "none"),
+                                            intensity_BC_grid_legend,
+                                            ncol = 1,
+                                            rel_heights = c(1,1,1,0.2),
+                                            labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
+                                            label_x = c(-0.04,-0.03,-0.1,0),
+                                            align = "v")
+
+subsidy_intensity_BC_grid_map
+ggsave(paste0(results_dir, "subsidy_intensity_BC_grid_map.png"), dpi = 200, width = 7, height = 12.5)
+
 ```
 
+### Subsidy Intensities by Region
+
 ```{r}
-mean_subsidy_intensity_B_region_map <- effort_binned_sub_intensity %>%
-  group_by(year, fao_region) %>%
-  summarize(mean_B_subs_KWh = mean(B_subs_KWh, na.rm = T)) %>%
-  right_join(fao_regions, by = "fao_region") %>%
-  ggplot()+
-  geom_sf(aes(geometry = geometry, fill = mean_B_subs_KWh)) +
-  geom_sf(data=world_land, color = NA, fill="grey30") +
-  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
-  scale_fill_viridis_c(name="Mean Subsidy Intensity ($/KWh)", 
-                       na.value = "#000000", 
-                       limits = mean_limits, 
-                       breaks = mean_breaks,
-                       labels = mean_labels,
-                       oob = scales::squish) +
-  scale_x_continuous(expand = c(0,0))+
-  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
-  xlab("") +
-  ylab("") +
-  map_theme + 
-  guides(fill=guide_colorbar(
-   title.position = "left",
-   title.hjust = 0.5,
-   frame.colour = "white",
-   barwidth=4,
-   barheight=0.25,
-   default.unit="inch"))
+# Median
+median_subsidy_intensity_BC_region_map <- MapMaker(data = subsidy_intensity_region,
+                                                  res = "region",
+                                                  fill = "med_BC_subs_KWh",
+                                                  fill_name = "Subsidy Intensity \n($/KWh)",
+                                                  fill_breaks = seq(0,8, by = 2),
+                                                  fill_limits = c(0,8),
+                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                                  land_sf = world_land,
+                                                  region_sf = fao_regions)
 
-mean_subsidy_intensity_B_region_map
+ggsave(paste0(results_dir, "median_subsidy_intensity_BC_region_map.png"), dpi = 200, width = 7, height = 5)
 
-ggsave(paste0(results_dir, "mean_subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 5)
+# Mean
+mean_subsidy_intensity_BC_region_map <- MapMaker(data = subsidy_intensity_region,
+                                                  res = "region",
+                                                  fill = "mean_BC_subs_KWh",
+                                                  fill_name = "Subsidy Intensity \n($/KWh)",
+                                                  fill_breaks = seq(0,8, by = 2),
+                                                  fill_limits = c(0,8),
+                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                                  land_sf = world_land,
+                                                  region_sf = fao_regions)
+
+ggsave(paste0(results_dir, "mean_subsidy_intensity_BC_region_map.png"), dpi = 200, width = 7, height = 5)
+
+# Weighted Mean
+w_mean_subsidy_intensity_BC_region_map <- MapMaker(data = subsidy_intensity_region,
+                                                  res = "region",
+                                                  fill = "w_mean_BC_subs_KWh",
+                                                  fill_name = "Subsidy Intensity \n($/KWh)",
+                                                  fill_breaks = seq(0,8, by = 2),
+                                                  fill_limits = c(0,8),
+                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                                  land_sf = world_land,
+                                                  region_sf = fao_regions)
+
+ggsave(paste0(results_dir, "w_mean_subsidy_intensity_BC_region_map.png"), dpi = 200, width = 7, height = 5)
+
+# Combine into three panel
+intensity_BC_region_legend <- get_legend(w_mean_subsidy_intensity_BC_region_map)
+
+subsidy_intensity_BC_region_map <- plot_grid(median_subsidy_intensity_BC_region_map + theme(legend.position = "none"),
+                                            mean_subsidy_intensity_BC_region_map + theme(legend.position = "none"),
+                                            w_mean_subsidy_intensity_BC_region_map + theme(legend.position = "none"),
+                                            intensity_BC_region_legend,
+                                            ncol = 1,
+                                            rel_heights = c(1,1,1,0.2),
+                                            labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
+                                            label_x = c(-0.04,-0.03,-0.1,0),
+                                            align = "v")
+
+subsidy_intensity_BC_region_map
+ggsave(paste0(results_dir, "subsidy_intensity_BC_region_map.png"), dpi = 200, width = 7, height = 12.5)
+
 ```
 
-Let's make ones for the weighted means too using fishing KWh as the weights.
-
-```{r}
-weighted_mean_breaks <- seq(0,6, by = 1)
-weighted_mean_limits <- c(0,6)
-weighted_mean_labels <- c("0", "1", "2", "3", "4", "5", paste0("\u2265","6"))
-
-weighted_mean_subsidy_intensity_B_grid_map <- effort_binned_sub_intensity %>%
-  group_by(year, lat_bin_center, lon_bin_center) %>%
-  summarize(weighted_mean_B_subs_KWh = weighted.mean(B_subs_KWh, w = fishing_KWh_lat_lon)) %>%
-  ggplot()+
-  geom_tile(aes(x = lon_bin_center, y=lat_bin_center, fill = weighted_mean_B_subs_KWh)) +
-  geom_sf(data=world_land, color = NA, fill="grey30") +
-  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
-  scale_fill_viridis_c(name="Weighted Mean Subsidy Intensity \n($/KWh)", 
-                       na.value = "#000000", 
-                       limits = weighted_mean_limits, 
-                       breaks = weighted_mean_breaks,
-                       labels = weighted_mean_labels,
-                       oob = scales::squish) +
-  scale_x_continuous(expand = c(0,0))+
-  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
-  xlab("") +
-  ylab("") +
-  map_theme + 
-  guides(fill=guide_colorbar(
-   title.position = "left",
-   title.hjust = 0.5,
-   frame.colour = "white",
-   barwidth=4,
-   barheight=0.25,
-   default.unit="inch"))
-
-weighted_mean_subsidy_intensity_B_grid_map
-
-ggsave(paste0(results_dir, "weighted_mean_subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 5)
-```
-
-```{r}
-region_weighted_mean_breaks <- seq(0,4, by = 1)
-region_weighted_mean_limits <- c(0,4)
-region_weighted_mean_labels <- c("0", "1", "2", "3", paste0("\u2265","4"))
-
-weighted_mean_subsidy_intensity_B_region_map <- effort_binned_sub_intensity %>%
-  group_by(year, fao_region) %>%
-  summarize(weighted_mean_B_subs_KWh = weighted.mean(B_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T)) %>%
-  right_join(fao_regions, by = "fao_region") %>%
-  ggplot()+
-  geom_sf(aes(geometry = geometry, fill = weighted_mean_B_subs_KWh)) +
-  geom_sf(data=world_land, color = NA, fill="grey30") +
-  scale_fill_viridis_c(name="Weighted Mean Subsidy Intensity \n($/KWh)", 
-                       na.value = "#000000", 
-                       limits = region_weighted_mean_limits, 
-                       breaks = region_weighted_mean_breaks,
-                       labels = region_weighted_mean_labels,
-                       oob = scales::squish) +
-  scale_x_continuous(expand = c(0,0))+
-  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
-  xlab("") +
-  ylab("") +
-  map_theme + 
-  guides(fill=guide_colorbar(
-   title.position = "left",
-   title.hjust = 0.5,
-   frame.colour = "white",
-   barwidth=4,
-   barheight=0.25,
-   default.unit="inch"))
-
-weighted_mean_subsidy_intensity_B_region_map
-
-ggsave(paste0(results_dir, "weighted_mean_subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 5)
-```
-
-### Stock status
+## Stock status
 
@@
 
-upsides_regional_averages <- upsides_dat %>%
+upsides_region <- upsides_dat %>%
   group_by(region_fao_split) %>%
-  summarize(mean_f_v_fmsy = mean(fv_fmsy),
-            mean_weighted_f_v_fmsy = weighted.mean(fv_fmsy, w = msy),
-            median_f_v_fmsy = median(fv_fmsy),
-            mean_b_v_bmsy = mean(bv_bmsy),
-            mean_weighted_b_v_bmsy = weighted.mean(bv_bmsy, w = msy),
-            median_b_v_bmsy = median(bv_bmsy))
+  summarize(mean_f_v_fmsy = mean(fv_fmsy, na.rm = T),
+            w_mean_f_v_fmsy = weighted.mean(fv_fmsy, w = msy, na.rm = T),
+            med_f_v_fmsy = median(fv_fmsy, na.rm = T),
+            mean_b_v_bmsy = mean(bv_bmsy, na.rm = T),
+            w_mean_b_v_bmsy = weighted.mean(bv_bmsy, w = msy, na.rm = T),
+            med_b_v_bmsy = median(bv_bmsy, na.rm = T),
+            tot_msy = sum(msy, na.rm = T)) %>%
+  rename(fao_region = region_fao_split)
 
@@
 
+### F/Fmsy by Region
+
 ```{r}
+# Median
+median_f_v_fmsy_region_map <- MapMaker(data = upsides_region, 
+                                     res = "region",
+                                     fill = "med_f_v_fmsy",
+                                     fill_name = "F/Fmsy",
+                                     fill_breaks = seq(0,4, by = 1),
+                                     fill_limits = c(0,4),
+                                     fill_labels = c("0", "1", "2", "3", "4"),
+                                     land_sf = world_land,
+                                     region_sf = fao_regions)
 
-upsides_regional_averages_spatial <- fao_regions %>%
-  right_join(upsides_regional_averages, by = c("fao_region" = "region_fao_split"))
+ggsave(paste0(results_dir, "median_f_v_fmsy_region_map.png"), dpi = 200, width = 7, height = 5)
+
+# Mean
+mean_f_v_fmsy_region_map <- MapMaker(data = upsides_region, 
+                                     res = "region",
+                                     fill = "mean_f_v_fmsy",
+                                     fill_name = "F/Fmsy",
+                                     fill_breaks = seq(0,4, by = 1),
+                                     fill_limits = c(0,4),
+                                     fill_labels = c("0", "1", "2", "3", "4"),
+                                     land_sf = world_land,
+                                     region_sf = fao_regions)
+
+ggsave(paste0(results_dir, "mean_f_v_fmsy_region_map.png"), dpi = 200, width = 7, height = 5)
+
+# Weighted Mean
+w_mean_f_v_fmsy_region_map <- MapMaker(data = upsides_region, 
+                                     res = "region",
+                                     fill = "w_mean_f_v_fmsy",
+                                     fill_name = "F/Fmsy",
+                                     fill_breaks = seq(0,4, by = 1),
+                                     fill_limits = c(0,4),
+                                     fill_labels = c("0", "1", "2", "3", "4"),
+                                     land_sf = world_land,
+                                     region_sf = fao_regions)
+
+ggsave(paste0(results_dir, "w_mean_f_v_fmsy_region_map.png"), dpi = 200, width = 7, height = 5)
+
+# Combine into three panel
+f_v_fmsy_region_legend <- get_legend(w_mean_f_v_fmsy_region_map)
+
+f_v_fmsy_region_map <- plot_grid(median_f_v_fmsy_region_map + theme(legend.position = "none"),
+                                 mean_f_v_fmsy_region_map + theme(legend.position = "none"),
+                                 w_mean_f_v_fmsy_region_map + theme(legend.position = "none"),
+                                 f_v_fmsy_region_legend,
+                                 ncol = 1,
+                                 rel_heights = c(1, 1, 1, 0.2),
+                                 labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
+                                 label_x = c(-0.04, -0.03, -0.1, 0),
+                                 align = "v")
+
+f_v_fmsy_region_map
+ggsave(paste0(results_dir, "f_v_fmsy_region_map.png"), dpi = 200, width = 7, height = 12.5)
+```
+
+## Coorelation Between Subsidies and Stock status
+
+```{r}
+subsidy_intensity_upsides_region <- upsides_region %>%
+  left_join(subsidy_intensity_region, by = "fao_region")
+
+# Weighted mean of Bad + Ambig vs Weighted mean F/Fmsy
+w_mean_BC_vs_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "w_mean_BC_subs_KWh",
+                                       x_name = "Weighted Mean Subsidy Intensity ($/KWh)",
+                                       x_limits = c(0,2),
+                                       y = "w_mean_f_v_fmsy",
+                                       y_name = "Weighted Mean F/Fmsy",
+                                       y_limits = c(0,2.5),
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = "Total Fishing Effort \n(KWh, billions)",
+                                       fill_limits = c(0,7.5e9),
+                                       fill_breaks = seq(0,7.5e9, length.out = 5),
+                                       fill_labels = format(seq(0,7.5e9, length.out = 5)/1e9, scientific = F, digits = 2))
+
+ggsave(paste0(results_dir, "w_mean_BC_vs_f_v_fmsy_plot.png"), dpi = 200, width = 7, height = 7)
+
+# mean of Bad + Ambig vs mean F/Fmsy
+w_mean_BC_vs_median_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "w_mean_BC_subs_KWh",
+                                       x_name = "Weighted Mean Subsidy Intensity ($/KWh)",
+                                       x_limits = c(0,4),
+                                       y = "med_f_v_fmsy",
+                                       y_name = "Median F/Fmsy",
+                                       y_limits = c(0,4),
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = "Total Fishing Effort \n(KWh, billions)",
+                                       fill_limits = c(0,7.5e9),
+                                       fill_breaks = seq(0,7.5e9, length.out = 5),
+                                       fill_labels = format(seq(0,7.5e9, length.out = 5)/1e9, scientific = F, digits = 2))
+
+ggsave(paste0(results_dir, "w_mean_BC_vs_median_f_v_fmsy_plot.png"), dpi = 200, width = 7, height = 7)
 
@@
 
-Mean F/Fmsy by region.
+## Figure 1
 
 ```{r}
-mean_f_v_fmsy_regional_map <- ggplot()+
-  geom_sf(data=upsides_regional_averages_spatial, color = "black", aes(fill = mean_f_v_fmsy)) +
-  geom_sf(data=world_land, color = NA, fill="grey30") +
-  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
-  scale_fill_viridis_c(name="Mean F/Fmsy", na.value = "#000000") +
-  scale_x_continuous(expand = c(0,0))+
-  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
-  xlab("") +
-  ylab("") +
-  map_theme + 
- guides(fill=guide_legend(
-                 keywidth=0.25,
-                 keyheight=0.25,
-                 default.unit="inch"))
+top_legend <- get_legend(w_mean_subsidy_intensity_BC_region_map)
 
-mean_f_v_fmsy_regional_map
+top_row <- plot_grid(
+  plot_grid(w_mean_subsidy_intensity_BC_grid_map + theme(legend.position = "none"),
+                     w_mean_subsidy_intensity_BC_region_map + theme(legend.position = "none"),
+                     nrow = 1,
+                     label_x = 0,
+                     labels = c("A) Subsidy Itensity (1x1 degree)",
+                                "B) Subsidy Intensity (FAO Region)")),
+  ncol = 1,
+  top_legend,
+  rel_heights = c(1,0.2))
 
-ggsave(paste0(results_dir, "mean_f_v_fmsy_regional_map.png"), dpi = 200, width = 7, height = 5)
+bottom_row <-  plot_grid(median_f_v_fmsy_region_map,
+                     w_mean_BC_vs_median_f_v_fmsy_plot,
+                     nrow = 1,
+                     label_x = 0,
+                     labels = c("C) F/Fmsy (FAO Region)",
+                                "D) Coorelation"))
+
+Figure1 <- plot_grid(top_row,
+                     bottom_row,
+                     nrow = 2)
+
+ggsave(paste0(results_dir, "Figure1.png"), dpi = 200, width = 14, height = 9.5)
 ```
-
-Weighted mean F/Fmsy by region (weighted by MSY of each stock).
-
-```{r}
-weighted_mean_f_v_fmsy_regional_map <- ggplot()+
-  geom_sf(data=upsides_regional_averages_spatial, color = "black", aes(fill = mean_weighted_f_v_fmsy)) +
-  geom_sf(data=world_land, color = NA, fill="grey30") +
-  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
-  scale_fill_viridis_c(name="Weighted Mean F/Fmsy", na.value = "#000000") +
-  scale_x_continuous(expand = c(0,0))+
-  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
-  xlab("") +
-  ylab("") +
-  map_theme + 
-  guides(fill=guide_legend(
-                 keywidth=0.25,
-                 keyheight=0.25,
-                 default.unit="inch"))
-
-weighted_mean_f_v_fmsy_regional_map
-
-ggsave(paste0(results_dir, "weighted_mean_f_v_fmsy_regional_map.png"), dpi = 200, width = 7, height = 5)
-```
-
-Median F/Fmsy by region.
-
-```{r}
-median_f_v_fmsy_regional_map <- ggplot()+
-  geom_sf(data=upsides_regional_averages_spatial, color = "black", aes(fill = median_f_v_fmsy)) +
-  geom_sf(data=world_land, color = NA, fill="grey30") +
-  #geom_sf(data=eez_boundaries, color="grey80", size=0.1, aes(group = mrgid_eez)) +
-  scale_fill_viridis_c(name="Median F/Fmsy", na.value = "#000000") +
-  scale_x_continuous(expand = c(0,0))+
-  scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
-  xlab("") +
-  ylab("") +
-  map_theme +
- guides(fill=guide_legend(
-                 keywidth=0.25,
-                 keyheight=0.25,
-                 default.unit="inch"))
-
-median_f_v_fmsy_regional_map
-
-ggsave(paste0(results_dir, "median_f_v_fmsy_regional_map.png"), dpi = 200, width = 7, height = 5)
-```

### 2020-03-20 scripts/02_vessel_list.Rmd

@@
   CASE
-    WHEN engine_power_kw IS NULL THEN fishing_hours_lat_lon
+    WHEN engine_power_kw IS NULL THEN fishing_hours_lat_lon*400
     ELSE fishing_hours_lat_lon*engine_power_kw

### 2020-03-20 scripts/01_data_wrangling.Rmd
fao landing plot back

@@
 # Paths to fisheries data files
-fao_production_path <- here::here("data", "raw", "FAO-2019-capture-production", "TS_FI_CAPTURE.csv")
+fao_production_path <- here::here("data", "raw", "FAO-2019-capture-production", "Capture_2019.1.0/")
 #fao_value_path
@@
 
+```{r}
+# FAO stores a lot of characteristics in lookup tables that come with the production dataset. We need to use these tables to match country names, species names, and source
+fao_country_lookup <- read_csv(paste0(fao_production_path, "CL_FI_COUNTRY_GROUPS.csv")) %>%
+  clean_names(case = "snake") %>%
+  dplyr::select(country = un_code,
+                iso3 = iso3_code,
+                name = name_en) %>%
+  mutate(iso3_new = case_when(name == "Belgium-Luxembourg" ~ "BEL",
+                              name %in% c("Canton and Enderbury Is", "Czechoslovakia", "Neutral Zone", "Pacific Islands Trust Tr", "Serbia and Montenegro", "Un.
+Sov.
+Soc.
+Rep.", "Yemen Arab Republic", "Yemen, Democratic", "Yugoslavia SFR") ~ "XXX",
+                              name %in% c("Channel Islands", "Sark") ~ "GGY",
+                              name == "Eswatini" ~ "SWZ",
+                              name == "European Union" ~ "EU",
+                              name %in% c("Johnston Island", "Midway Islands", "Wake Island", "US Minor Outlying Is.") ~ "UMI",
+                              name == "Netherlands Antilles" ~ "ANT",
+                              name == "Saint-Martin" ~ "MAF",
+                              name == "Zanzibar" ~ "TZA",
+                              name == "Other nei" ~ "UNK",
+                              is.na(name) ~ "UNK",
+                              TRUE ~ countrycode(name, "country.name", "iso3c"))) %>%
+  dplyr::filter(iso3_new != "XXX") %>% # remove entities that no longer exist today
+  dplyr::select(iso3 = iso3_new, country) %>%
+  mutate(country = as.integer(country))
+
+# FAO species lookup 
+fao_species_lookup <- read_csv(paste0(fao_production_path, "CL_FI_SPECIES_GROUPS.csv")) %>%
+  clean_names(case = "snake") %>%
+  dplyr::select(species = x3alpha_code,
+                asfis_species = name_en,
+                scientific_name,
+                yearbook_group,
+                isscaap_group)
+
+# FAO Symbol lookup
+fao_symbol_lookup <- read_csv(paste0(fao_production_path, "CL_FI_SYMBOL.csv"))
+
+# FAO Area lookup
+fao_area_lookup <- read_csv(paste0(fao_production_path, "CL_FI_WATERAREA_GROUPS.csv")) %>%
+  clean_names(case = "snake") %>%
+  mutate(keep = ifelse(is.na(fa_region_group), F, T)) %>%
+  dplyr::filter(keep) %>%
+  dplyr::select(area = code) %>%
+  mutate(area = as.integer(area))
+
+# Load data
+fao_production_dat <- read.csv(paste0(fao_production_path, "TS_FI_CAPTURE.csv")) %>%
+  clean_names(case = "snake") %>%
+  dplyr::filter(year >= 2000) %>%
+  dplyr::filter(unit == "t") %>% # remove catches measured in number of individuals
+  mutate(species = as.character(species)) %>%
+  left_join(fao_country_lookup, by = "country") %>%
+  inner_join(fao_area_lookup, by = c("fishing_area" = "area")) %>%
+  group_by(iso3, year, species, fishing_area) %>%
+  summarize(value = sum(quantity, na.rm = T)) %>%
+  ungroup() %>%
+  left_join(fao_species_lookup, by = "species")
+
+# Deal with the EU + territories
+fao_production_dat_eu <- fao_production_dat %>%
+  dplyr::filter(iso3 %in% c(eu_countries, eu_territories, "EU")) %>%
+  mutate(entity = "EU") %>%
+  group_by(entity, year, fishing_area, species, asfis_species, scientific_name, yearbook_group, isscaap_group) %>%
+  summarize(value = sum(value, na.rm = T)) %>%
+  rename(iso3 = entity)
+
+# Deal with the US + territories
+fao_production_dat_us <- fao_production_dat %>%
+  dplyr::filter(iso3 %in% c(us_territories, "USA")) %>%
+  mutate(entity = "USA-T") %>%
+  group_by(entity, year, fishing_area, species, asfis_species, scientific_name, yearbook_group, isscaap_group) %>%
+  summarize(value = sum(value, na.rm = T)) %>%
+  rename(iso3 = entity)
+
+# Put them back together
+fao_production_dat_edit <- fao_production_dat %>%
+  dplyr::filter(iso3 != "EU") %>%
+  bind_rows(fao_production_dat_eu) %>%
+  bind_rows(fao_production_dat_us)
+
+write_csv(fao_production_dat_edit, paste0(data_dir, "fao_2019_capture_production_tidy.csv"))
+
+# Aggregate by ISCCAP groups and export for time series plot
+fao_production_dat_edit_groups <- fao_production_dat_edit %>%
+  group_by(iso3, year, isscaap_group) %>%
+  summarize(value = sum(value, na.rm = T))
+
+write_csv(fao_production_dat_edit_groups, paste0(data_dir, "fao_2019_capture_production_isscaap_groups_tidy.csv"))
+write_csv(fao_production_dat_edit_groups, paste0(app_data_dir, "fao_2019_capture_production_isscaap_groups_tidy.csv"))
+```
+
 ## Estimated landed price

### 2020-03-20 app/00_initialize_app.R

@@ -165,6 +165,13 @@ demographic_dat <- demo_dat_world_bank %>%
 
 ### FISHERIES DATA -----------------------------------------------------------------------------------
 
+# 1) FAO Cature Production by ISSCAAP Group (2000-2017)
+
+capture_production_dat_fao <- read_csv("./data/fao_2019_capture_production_isscaap_groups_tidy.csv") %>%
+  group_by(iso3, year) %>%
+  mutate(prop_annual_total = value/sum(value)) %>%
+  ungroup()
+
 # # 2) Country profiles ---
 # profile_dat_raw <- read.csv("./data/country-profiles-tidy.csv", stringsAsFactors = F)
 # profile_dat_raw$subtype[profile_dat_raw$type == "B1"] <- "Boat construction and renovation"

### 2020-03-20 app/server.R

@@ -203,6 +203,7 @@ shinyServer(function(input, output, session) {
     # Filter data
     global_subsidies_map_dat <- subsidy_dat %>%
       dplyr::filter(variable == "subsidies_Sumaila") %>%
+      dplyr::filter(if(input$w_global_subsidies_category == "All") category_name %in% c("Beneficial", "Capacity-enhancing", "Ambiguous") else category_name == input$w_global_subsidies_category) %>%
       dplyr::filter(type %in% c(input$w_global_subsidies_types)) %>%
       dplyr::filter(!is.na(value) & value > 0) %>%
       group_by(iso3, display_name, category, category_name, type, type_name) %>%
@@ -371,7 +372,62 @@ shinyServer(function(input, output, session) {
   })
   
   ### Plotly figure: FAO Marine Capture Production ---------------------
-  #[NEED]
+  output$country_fishery_stats_production_plot <- renderPlotly({
+    
+    req(input$w_country_fishery_stats_selected_country)
+    
+    # Filter data
+    country_fishery_stats_production_plot_dat <- capture_production_dat_fao %>%
+      dplyr::filter(iso3 == input$w_country_fishery_stats_selected_country)
+    
+    req(nrow(country_fishery_stats_production_plot_dat) > 0)
+    
+    # Make plot
+    country_fishery_stats_production_plot <- country_fishery_stats_production_plot_dat %>%
+      ggplot()+
+      aes(x = year, y = value/1000, fill = isscaap_group)+
+      geom_area()+
+      geom_area(aes(text = paste0("<b>","Year: ","</b>", year,
+                                  "<br>",
+                                  "<b>", "ISSCAAP group: ", "</b>", isscaap_group,
+                                  "<br>",
+                                  "<b>", "Capture production (tonnes): ", "</b>", format(round(value, 0), big.mark = ","),
+                                  "<br>",
+                                  "<b>", "% of annual total: ", "</b>", round(prop_annual_total *100, 2))))+
+      scale_y_continuous(expand = c(0,0),
+                         name = "Capture production (tonnes, thousands)", 
+                         labels = function(x) format(x, big.mark = ",", decimal.mark = ".", scientific = FALSE))+
+      scale_x_continuous(expand = c(0,0))+
+      theme_bw()+
+      labs(x = "Year")+
+      theme(legend.title = element_blank(),
+            legend.position = "none")
+    
[…]

### 2020-03-20 app/ui_04b_country_fishery_stats.R

@@ -70,11 +70,9 @@ CountryFisheryStats = function(wto_members_and_observers)
            # Header and text
            includeHTML("./text/04b_country_fishery_stats_section2.html"),
            
-           # Capture fisheries production line plot (PLACEHOLDER - REPLACE WITH PLOTLY OBJECT)
-           #plotlyOutput("country_profile_landings_plot")
-           
-           # Temp image
-           img(src = "/sample-images/04b_capture_production_plot_image.png", width = "100%")
+           # Capture fisheries production plot
+           plotlyOutput("country_fishery_stats_production_plot")
+          
            
     ),
     

### 2020-03-20 app/ui_04c_compare_fishery_stats.R

@@ -134,6 +134,15 @@ CompareFisheryStats = function(wto_members_and_observers, subsidy_types_sorted_s
            
     ), # /column 12 - widgets
     
+    ### Bar plot 
+    column(12, style = "padding: 0 25px 15px;",
+           
+           # Bar chart
+           plotlyOutput("compare_fishery_stats_bar_plot", width = "100%")
+           
+           
+    ),
+    
     ### Bottom navigation buttons
     column(12,
            fluidRow(style = "padding: 5px 5px; background-color: #3c8dbc;",

### 2020-03-20 scripts/01_data_wrangling.Rmd
almost all data minus vessel list back in

@@
 
+**Other**
 IUU Consolidated vessel list
 > NEED
+
+Cap and Tier Data from the US Proposal
+> Citation for this?
 
@@
   bind_rows(fao_production_dat_eu) %>%
-  bind_rows(fao_production_dat_us)
+  bind_rows(fao_production_dat_us) %>%
+  mutate(variable = "capture_production",
+         units = "tonnes",
+         source = "FAO (2019)")
 
@@
 fao_production_dat_edit_groups <- fao_production_dat_edit %>%
-  group_by(iso3, year, isscaap_group) %>%
+  group_by(iso3, year, isscaap_group, variable, units, source) %>%
   summarize(value = sum(value, na.rm = T))
@@
 
-## Estimated landed price
+## Ex-vessel prices from Melnychuk et al. (2017)
+```{r}
+# Price data from Melynchuk et al. (2017)
+melnychuk_price_dat <- read_csv(melnychuk_price_path) %>%
+  clean_names(case = "snake") %>%
+  dplyr::select(-entry) %>%
+  dplyr::filter(year >= 2000 & year <= 2012) %>%
+  group_by(year, scientific_name, asfis_species, isscaap_group, group_for_pairing) %>%
+  summarize(exvessel = mean(exvessel, na.rm = T)) %>%
+  ungroup()
+
+# Pull data from 2012 to use for extrapolation to 2017
+melnychuk_price_dat_mry <- melnychuk_price_dat %>%
+  dplyr::filter(year == 2012) %>%
+  rename(exvessel_for_extrap = exvessel) %>%
+  dplyr::select(-year)
+
+# CPI for 2012 - 2018 to convert USD
+cpi_2012 <- 229.594
+cpi_2013 <- 232.957
+cpi_2014 <- 236.736
+cpi_2015 <- 237.017
+cpi_2016 <- 240.007
+cpi_2017 <- 245.120
+
+# Do extrapolation for missing years
+melnychuk_price_dat_extrapolation <- melnychuk_price_dat %>%
+  complete(nesting(scientific_name, asfis_species, isscaap_group, group_for_pairing), year = 2000:2017) %>%
+  left_join(melnychuk_price_dat_mry, by = c("scientific_name", "asfis_species", "isscaap_group", "group_for_pairing")) %>%
+  mutate(exvessel_adjusted = case_when(year <= 2012 ~ exvessel,
+                                       year == 2013 ~ exvessel_for_extrap * (cpi_2013/cpi_2012),
+                                       year == 2014 ~ exvessel_for_extrap * (cpi_2014/cpi_2012),
+                                       year == 2015 ~ exvessel_for_extrap * (cpi_2015/cpi_2012),
+                                       year == 2016 ~ exvessel_for_extrap * (cpi_2016/cpi_2012),
+                                       year == 2017 ~ exvessel_for_extrap * (cpi_2017/cpi_2012))) %>%
+  dplyr::select(-exvessel, -exvessel_for_extrap) %>%
+  rename(exvessel = exvessel_adjusted)
+
+# Get rid of NAs and save
+melnychuk_price_dat_extrapolation <- melnychuk_price_dat_extrapolation %>%
+  dplyr::filter(!is.nan(exvessel)) %>%
+  mutate(variable = "ex_vessel_price",
+         units = paste(year, "US$"),
+         source = "Melnychuk et al. (2017)")
+
+write_csv(melnychuk_price_dat_extrapolation, paste0(data_dir, "melnychuk_2017_price_tidy.csv"))
+
+# Create averages by pairing group for each year
+price_dat_group_year <- melnychuk_price_dat_extrapolation %>%
+  group_by(year, group_for_pairing) %>%
+  summarize(exvessel_group_avg = mean(exvessel, na.rm = T)) %>%
+  ungroup()
+
+# Create averages by pairing group (no year) 
+price_dat_group <- melnychuk_price_dat_extrapolation %>%
+  group_by(group_for_pairing) %>%
+  summarize(exvessel_group_avg_allyears = mean(exvessel, na.rm = T)) %>%
+  ungroup()
+```
+
+## Estimated landed value from FAO/Melnychuk et al. (2017)
+
+```{r}
+# Combine landings and price data
+combine_catch_price_dat <- fao_production_dat_edit %>%
+  left_join(melnychuk_price_dat_extrapolation %>% dplyr::select(-isscaap_group, -variable, -source, -units), by = c("year", "scientific_name", "asfis_species", "isscaap_group" = "group_for_pairing")) %>%
+  left_join(price_dat_group_year, by = c("year", "isscaap_group" = "group_for_pairing")) %>%
+  left_join(price_dat_group, by = c("isscaap_group" = "group_for_pairing")) %>%
+  mutate(exvessel_inclusive = case_when(!is.na(exvessel) ~ exvessel,
+                                        !is.na(exvessel_group_avg) ~ exvessel_group_avg,
+                                        !is.na(exvessel_group_avg_allyears) ~ exvessel_group_avg_allyears))
+
+# Look at NAs - 8498 entries
+combine_nas <- combine_catch_price_dat %>%
+  dplyr::filter(is.na(exvessel_inclusive))
+
+# Set price to 0 for those
+combine_catch_price_dat$exvessel_inclusive[is.na(combine_catch_price_dat$exvessel_inclusive)] <- 0
+
+# Calculate revenues and aggregate by ISSCAAP group
+landed_value_dat <- combine_catch_price_dat %>%
+  dplyr::select(-exvessel, -exvessel_group_avg, -exvessel_group_avg_allyears) %>%
+  rename(exvessel = exvessel_inclusive) %>%
+  mutate(landed_value = value*exvessel) %>%
+  group_by(iso3, year, isscaap_group) %>%
+  summarize(value = sum(landed_value, na.rm = T)) %>%
+  mutate(variable = "landed_value",
+         units = paste(year, "US$"),
+         source = "FAO (2019); Melnychuk et al. (2017)")
+
+write_csv(landed_value_dat, paste0(data_dir, "estimated_landed_value_isscaap_groups_tidy.csv"))
+write_csv(landed_value_dat, paste0(app_data_dir, "estimated_landed_value_isscaap_groups_tidy.csv"))
+```
 
@@
 ```
+
+# Section 4 - Other Data
+
+## Cap and Tier Data from the US Proposal
+```{r}
+cap_tier_dat <- read_csv(cap_tier_path) %>%
+  mutate(iso3 = case_when(country == "Eswatini" ~ "SWZ",
+                          country == "EU" ~ "EU",
+                          TRUE ~ countrycode(country, "country.name", "iso3c")))
+```

### 2020-03-20 app/00_initialize_app.R

@@ -172,33 +172,24 @@ capture_production_dat_fao <- read_csv("./data/fao_2019_capture_production_issca
   mutate(prop_annual_total = value/sum(value)) %>%
   ungroup()
 
-# # 2) Country profiles ---
-# profile_dat_raw <- read.csv("./data/country-profiles-tidy.csv", stringsAsFactors = F)
-# profile_dat_raw$subtype[profile_dat_raw$type == "B1"] <- "Boat construction and renovation"
-# 
-# # Get unique types so we can order them as factors
-# types <- unique(profile_dat_raw$type)
-# names(types) <- unique(profile_dat_raw$subtype)
-# types_sorted <- sort(types) 
-# 
-# # Now put them in the order we want
-# types_arranged <- c(types_sorted[26:38], types_sorted[39], types_sorted[1:25])
-# subtypes_arranged <- names(types_arranged)
-# categories_arranged <- c("Beneficial", "Capacity-enhancing", "Ambiguous", "Total", "Non Budgetary Transfers", "Budgetary Transfers", "General Service Support", "Cost Recovery Charges")
-# 
-# # Add back in to profile dat and order factors to aid with plotting throughout
-# profile_dat <- profile_dat_raw %>%
-#   mutate(type = factor(type, levels = types_arranged, ordered = T),
-#          category = factor(category, levels = categories_arranged, ordered = T),
-#          subtype = factor(subtype, levels = subtypes_arranged, ordered = T)) %>%
-#   mutate(country = case_when(iso3 == "EU" ~ "European Union",
-#                              iso3 == "TWN" ~ "Chinese Taipei",
-#                              TRUE ~ countrycode(iso3, "iso3c", "country.name")))
-# 
-# # 3) Vessel list ---
+capture_production_dat_tot <- capture_production_dat_fao %>%
+  group_by(iso3, year, variable, units, source) %>%
+  summarize(value = sum(value, na.rm = T))
+
+# 2) Landed value by ISSCAAP Group (2000-2017)
+landed_value_dat <- read_csv("./data/estimated_landed_value_isscaap_groups_tidy.csv") %>%
+  group_by(iso3, year) %>%
+  mutate(prop_annual_total = value/sum(value)) %>%
+  ungroup()
+
+landed_value_dat_tot <- landed_value_dat %>%
+  group_by(iso3, year, variable, units, source) %>%
[…]

### 2020-03-20 scripts/01_data_wrangling.Rmd
cap tier data

@@
 iuu_vessel_path <- here::here("data", "raw", "IUU-Vessel-List-2019", "IUUList-20190430.csv")
+cap_tier_path <- here::here("data", "raw", "USA-Cap-Tier-Proposal", "US_cap_tier_data.csv")
 ```
@@
                           country == "EU" ~ "EU",
-                          TRUE ~ countrycode(country, "country.name", "iso3c")))
+                          TRUE ~ countrycode(country, "country.name", "iso3c"))) %>%
+  dplyr::select(-country)
+
+write_csv(cap_tier_dat, paste0(data_dir, "USA_cap_tier_tidy.csv"))
+write_csv(cap_tier_dat, paste0(app_data_dir, "USA_cap_tier_tidy.csv"))
 ```

### 2020-03-20 app/00_initialize_app.R

@@ -215,12 +215,12 @@ bio_dat <- read.csv("./data/regional_model_parameters.csv")
 ### POLICY DATA -----------------------------------------------------------------------------------
 
 # 1) Cap/tier data (from US proposal) ---
-cap_tier_dat <- read_csv("./data/cap_tier_dat_tidy.csv") %>%
+cap_tier_dat <- read_csv("./data/USA_cap_tier_tidy.csv") %>%
   arrange(iso3)
 
 # 2) Proposal settings
-proposal_settings <- read.csv("./data/wto-proposal-settings.csv", stringsAsFactors = F)
-default_settings <- proposal_settings %>% dplyr::filter(proposal == "Default")
+# proposal_settings <- read.csv("./data/wto-proposal-settings.csv", stringsAsFactors = F)
+# default_settings <- proposal_settings %>% dplyr::filter(proposal == "Default")
 
 # # Proposal names
 # proposal_names <- proposal_settings %>%

### 2020-03-20 app/server.R

@@ -191,19 +191,19 @@ shinyServer(function(input, output, session) {
     req(input$w_global_subsidies_types)
     
     # Color palette to use based off selected input
-    global_subsidies_map_color <- switch(input$w_global_subsidies_category,
-                                         "All" = list("YlOrRd", 1, 10e9),
-                                         "Beneficial" = list("Blues", 1, 10e9),
-                                         "Capacity-enhancing" = list("Reds", 1, 10e9),
-                                         "Ambiguous" = list("Purples", 1, 10e9))
+    global_subsidies_map_switch <- switch(input$w_global_subsidies_category,
+                                         "All" = list("YlOrRd", 1, 10e9, subsidy_types_sorted_sumaila),
+                                         "Beneficial" = list("Blues", 1, 10e9, subsidy_types_sorted_sumaila[1:3]),
+                                         "Capacity-enhancing" = list("Reds", 1, 10e9, subsidy_types_sorted_sumaila[4:10]),
+                                         "Ambiguous" = list("Purples", 1, 10e9, subsidy_types_sorted_sumaila[11:13]))
     
-    global_subsidies_map_pal <- colorNumeric(palette = global_subsidies_map_color[[1]],
-                                             log10(c(global_subsidies_map_color[[2]], global_subsidies_map_color[[3]])))
+    global_subsidies_map_pal <- colorNumeric(palette = global_subsidies_map_switch[[1]],
+                                             log10(c(global_subsidies_map_switch[[2]], global_subsidies_map_switch[[3]])))
     
     # Filter data
     global_subsidies_map_dat <- subsidy_dat %>%
       dplyr::filter(variable == "subsidies_Sumaila") %>%
-      dplyr::filter(if(input$w_global_subsidies_category == "All") category_name %in% c("Beneficial", "Capacity-enhancing", "Ambiguous") else category_name == input$w_global_subsidies_category) %>%
+      dplyr::filter(type %in% global_subsidies_map_switch[[4]]) %>%
       dplyr::filter(type %in% c(input$w_global_subsidies_types)) %>%
       dplyr::filter(!is.na(value) & value > 0) %>%
       group_by(iso3, display_name, category, category_name, type, type_name) %>%
@@ -286,8 +286,8 @@ shinyServer(function(input, output, session) {
       setView(0,20, zoom = 2) %>%
       addLegend("bottomright", 
                 pal = global_subsidies_map_pal,
[…]

### 2020-03-24 papers/paper-1/paper_1_figures.Rmd
cleaning up

@@
                                                   fill_limits = c(0,8),
-                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                                  fill_labels = c("0", "2", "4", "6", "\u2265 8"),
                                                   land_sf = world_land)
@@
 
-subsidy_intensity_tot_grid_map
 ggsave(paste0(results_dir, "subsidy_intensity_tot_grid_map.png"), dpi = 200, width = 7, height = 12.5)
@@
                                                   fill_limits = c(0,8),
-                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                                  fill_labels = c("0", "2", "4", "6", "\u2265 8"),
                                                   land_sf = world_land,
@@
 
-subsidy_intensity_tot_region_map
 ggsave(paste0(results_dir, "subsidy_intensity_tot_region_map.png"), dpi = 200, width = 7, height = 12.5)
 
+```
+
+```{r, fig.width=14, fig.height=12.5}
+# Combine into six panel
+subsidy_intensity_tot_noleg <- plot_grid(median_subsidy_intensity_tot_grid_map + theme(legend.position = "none"),
+                                         median_subsidy_intensity_tot_region_map + theme(legend.position = "none"),
+                                         mean_subsidy_intensity_tot_grid_map + theme(legend.position = "none"),
+                                         mean_subsidy_intensity_tot_region_map + theme(legend.position = "none"),
+                                         w_mean_subsidy_intensity_tot_grid_map + theme(legend.position = "none"),
+                                         w_mean_subsidy_intensity_tot_region_map + theme(legend.position = "none"),
+                                         ncol = 2,
+                                         labels = c("A) Median", "", "B) Mean", "", "C) Weighted Mean", ""),
+                                         label_x = c(-0.04, 0, -0.03,0, -0.1, 0))
+
+subsidy_intensity_tot_map <- plot_grid(subsidy_intensity_tot_noleg,
+                                       intensity_tot_region_legend,
+                                       rel_heights = c(2,0.2),
+                                       ncol = 1)
+
+subsidy_intensity_tot_map
+ggsave(paste0(results_dir, "subsidy_intensity_tot_map.png"), dpi = 200, width = 14, height = 12.5)
 ```
@@
                                                   fill_name = "Subsidy Intensity \n($/KWh)",
-                                                  fill_breaks = seq(0,8, by = 2),
-                                                  fill_limits = c(0,8),
-                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                                  fill_breaks = seq(0,6, by = 2),
+                                                  fill_limits = c(0,6),
+                                                  fill_labels = c("0", "2", "4", "\u2265 6"),
                                                   land_sf = world_land)
@@
 
-subsidy_intensity_B_grid_map
 ggsave(paste0(results_dir, "subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 12.5)
@@
                                                   fill_name = "Subsidy Intensity \n($/KWh)",
-                                                  fill_breaks = seq(0,8, by = 2),
-                                                  fill_limits = c(0,8),
-                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                                  fill_breaks = seq(0,6, by = 2),
+                                                  fill_limits = c(0,6),
+                                                  fill_labels = c("0", "2", "4", "\u2265 >6"),
                                                   land_sf = world_land,
@@
                                                   fill_name = "Subsidy Intensity \n($/KWh)",
-                                                  fill_breaks = seq(0,8, by = 2),
-                                                  fill_limits = c(0,8),
-                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                                  fill_breaks = seq(0,6, by = 2),
+                                                  fill_limits = c(0,6),
+                                                  fill_labels = c("0", "2", "4", "\u2265 6"),
                                                   land_sf = world_land,
@@
 
-subsidy_intensity_B_region_map
 ggsave(paste0(results_dir, "subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 12.5)
 
+```
+
+```{r, fig.width=14, fig.height=12.5}
+# Combine into six panel
+subsidy_intensity_B_noleg <- plot_grid(median_subsidy_intensity_B_grid_map + theme(legend.position = "none"),
+                                       median_subsidy_intensity_B_region_map + theme(legend.position = "none"),
+                                       mean_subsidy_intensity_B_grid_map + theme(legend.position = "none"),
+                                       mean_subsidy_intensity_B_region_map + theme(legend.position = "none"),
+                                       w_mean_subsidy_intensity_B_grid_map + theme(legend.position = "none"),
+                                       w_mean_subsidy_intensity_B_region_map + theme(legend.position = "none"),
+                                       ncol = 2,
+                                       labels = c("A) Median", "", "B) Mean", "", "C) Weighted Mean", ""),
+                                       label_x = c(-0.04, 0, -0.03,0, -0.1, 0))
+
+subsidy_intensity_B_map <- plot_grid(subsidy_intensity_B_noleg,
+                                       intensity_B_region_legend,
+                                       rel_heights = c(2,0.2),
+                                       ncol = 1)
+
+subsidy_intensity_B_map
+
+ggsave(paste0(results_dir, "subsidy_intensity_B_map.png"), dpi = 200, width = 14, height = 12.5)
 ```
@@
 
-subsidy_intensity_BC_grid_map
 ggsave(paste0(results_dir, "subsidy_intensity_BC_grid_map.png"), dpi = 200, width = 7, height = 12.5)
@@
 
-subsidy_intensity_BC_region_map
 ggsave(paste0(results_dir, "subsidy_intensity_BC_region_map.png"), dpi = 200, width = 7, height = 12.5)
 
+```
+
+```{r, fig.width=14, fig.height=12.5}
+# Combine into six panel
+subsidy_intensity_BC_noleg <- plot_grid(median_subsidy_intensity_BC_grid_map + theme(legend.position = "none"),
+                                       median_subsidy_intensity_BC_region_map + theme(legend.position = "none"),
+                                       mean_subsidy_intensity_BC_grid_map + theme(legend.position = "none"),
+                                       mean_subsidy_intensity_BC_region_map + theme(legend.position = "none"),
+                                       w_mean_subsidy_intensity_BC_grid_map + theme(legend.position = "none"),
+                                       w_mean_subsidy_intensity_BC_region_map + theme(legend.position = "none"),
+                                       ncol = 2,
+                                       labels = c("A) Median", "", "B) Mean", "", "C) Weighted Mean", ""),
+                                       label_x = c(-0.04, 0, -0.03,0, -0.1, 0))
+
+subsidy_intensity_BC_map <- plot_grid(subsidy_intensity_BC_noleg,
+                                       intensity_BC_region_legend,
+                                       rel_heights = c(2,0.2),
+                                       ncol = 1)
+
+subsidy_intensity_BC_map
+
+ggsave(paste0(results_dir, "subsidy_intensity_BC_map.png"), dpi = 200, width = 14, height = 12.5)
 ```
@@
                                      fill_limits = c(0,4),
-                                     fill_labels = c("0", "1", "2", "3", "4"),
+                                     fill_labels = c("0", "1", "2", "3", "\u2265 4"),
                                      land_sf = world_land,
@@
 
+### B/Bmsy by Region
+
+```{r}
+# Median
+median_b_v_bmsy_region_map <- MapMaker(data = upsides_region, 
+                                     res = "region",
+                                     fill = "med_b_v_bmsy",
+                                     fill_name = "B/Bmsy",
+                                     fill_breaks = seq(0,2, by = 0.5),
+                                     fill_limits = c(0,2),
+                                     fill_labels = c("0", "0.5", "1", "1.5", "\u2265 2"),
+                                     land_sf = world_land,
+                                     region_sf = fao_regions)
+
+ggsave(paste0(results_dir, "median_b_v_bmsy_region_map.png"), dpi = 200, width = 7, height = 5)
+
+# Mean
+mean_b_v_bmsy_region_map <- MapMaker(data = upsides_region, 
+                                     res = "region",
+                                     fill = "mean_b_v_bmsy",
+                                     fill_name = "B/Bmsy",
+                                     fill_breaks = seq(0,2, by = 0.5),
+                                     fill_limits = c(0,2),
+                                     fill_labels = c("0", "0.5", "1", "1.5", "\u2265 2"),
+                                     land_sf = world_land,
+                                     region_sf = fao_regions)
+
+ggsave(paste0(results_dir, "mean_b_v_bmsy_region_map.png"), dpi = 200, width = 7, height = 5)
+
+# Weighted Mean
+w_mean_b_v_bmsy_region_map <- MapMaker(data = upsides_region, 
+                                     res = "region",
+                                     fill = "w_mean_b_v_bmsy",
+                                     fill_name = "B/Bmsy",
+                                     fill_breaks = seq(0,2, by = 0.5),
+                                     fill_limits = c(0,2),
+                                     fill_labels = c("0", "0.5", "1", "1.5", "\u2265 2"),
+                                     land_sf = world_land,
+                                     region_sf = fao_regions)
+
+ggsave(paste0(results_dir, "w_mean_b_v_bmsy_region_map.png"), dpi = 200, width = 7, height = 5)
+
+# Combine into three panel
+b_v_bmsy_region_legend <- get_legend(w_mean_b_v_bmsy_region_map)
+
+b_v_bmsy_region_map <- plot_grid(median_b_v_bmsy_region_map + theme(legend.position = "none"),
+                                 mean_b_v_bmsy_region_map + theme(legend.position = "none"),
+                                 w_mean_b_v_bmsy_region_map + theme(legend.position = "none"),
+                                 b_v_bmsy_region_legend,
+                                 ncol = 1,
+                                 rel_heights = c(1, 1, 1, 0.2),
+                                 labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
+                                 label_x = c(-0.04, -0.03, -0.1, 0),
+                                 align = "v")
+
+b_v_bmsy_region_map
+ggsave(paste0(results_dir, "b_v_bmsy_region_map.png"), dpi = 200, width = 7, height = 12.5)
+```
+
 ## Coorelation Between Subsidies and Stock status
@@
   left_join(subsidy_intensity_region, by = "fao_region")
-
-# Weighted mean of Bad + Ambig vs Weighted mean F/Fmsy
-w_mean_BC_vs_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+```
+
+```{r}
+# Set some plot scales
+subs_x <- c(0,2.5)
+f_y <- c(0,3)
+effort_fill_lim <- c(0,7.5e9)
+effort_fill_breaks <- seq(0,7.5e9, length.out = 5)
+effort_fill_labels <- format(seq(0,7.5e9, length.out = 5)/1e9, scientific = F, digits = 2)
+
+# Labels
+w_mean_subs_label <- "Weighted Mean Subsidy Intensity ($/KWh)"
+mean_subs_label <- "Mean Subsidy Intensity ($/KWh)"
+median_subs_label <- "Median Subsidy Intensity ($/KWh)"
+
+w_mean_f_label <- "Weighted Mean F/Fmsy"
+mean_f_label <- "Mean F/Fmsy"
+median_f_label <- "Median F/Fmsy"
+
+effort_label <- "Total Fishing Effort \n(KWh, billions)"
+```
+
+### Use Weighted Mean Subsidies
+
+#### Total Subsidies
+
+```{r}
+# Weighted Mean Total Subs vs Median F/Fmsy [LAST]
+w_mean_tot_vs_median_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "w_mean_tot_subs_KWh",
+                                       x_name = w_mean_subs_label,
+                                       x_limits = subs_x,
+                                       y = "med_f_v_fmsy",
+                                       y_name = median_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+# Weighted Mean Total Subs vs Mean F/Fmsy [BEST]
+w_mean_tot_vs_mean_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "w_mean_tot_subs_KWh",
+                                       x_name = w_mean_subs_label,
+                                       x_limits = subs_x,
+                                       y = "mean_f_v_fmsy",
+                                       y_name = mean_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+# Weighted Mean Total Subs vs Weighted Mean F/Fmsy [SECOND]
+w_mean_tot_vs_w_mean_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "w_mean_tot_subs_KWh",
+                                       x_name = w_mean_subs_label,
+                                       x_limits = subs_x,
+                                       y = "w_mean_f_v_fmsy",
+                                       y_name = w_mean_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+# Combine into three panel
+corr_legend <- get_legend(w_mean_tot_vs_w_mean_f_v_fmsy_plot)
+
+w_mean_tot_vs_f_v_fmsy_plot <- plot_grid(
+
+  plot_grid(w_mean_tot_vs_median_f_v_fmsy_plot + theme(legend.position = "none", axis.title.x = element_blank()),
+            w_mean_tot_vs_mean_f_v_fmsy_plot + theme(legend.position = "none", axis.title.x = element_blank()),
+            w_mean_tot_vs_w_mean_f_v_fmsy_plot + theme(legend.position = "none"),
+            ncol = 1,
+            align = "hv"),
+  corr_legend,
+  ncol = 1,
+  rel_heights = c(3, 0.2))
+
+w_mean_tot_vs_f_v_fmsy_plot
+ggsave(paste0(results_dir, "w_mean_tot_vs_f_v_fmsy_plot.png"), dpi = 200, width = 7, height = 12.5)
+```
+
+#### Bad Subsidies
+
+```{r}
+# Weighted Mean Bad Subs vs Median F/Fmsy [BEST!]
+w_mean_B_vs_median_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "w_mean_B_subs_KWh",
+                                       x_name = w_mean_subs_label,
+                                       x_limits = subs_x,
+                                       y = "med_f_v_fmsy",
+                                       y_name = median_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+# Weighted Mean Bad Subs vs Mean F/Fmsy [LAST]
+w_mean_B_vs_mean_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "w_mean_B_subs_KWh",
+                                       x_name = w_mean_subs_label,
+                                       x_limits = subs_x,
+                                       y = "mean_f_v_fmsy",
+                                       y_name = mean_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+# Weighted Mean Total Subs vs Weighted Mean F/Fmsy [SECOND]
+w_mean_B_vs_w_mean_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "w_mean_B_subs_KWh",
+                                       x_name = w_mean_subs_label,
+                                       x_limits = subs_x,
+                                       y = "w_mean_f_v_fmsy",
+                                       y_name = w_mean_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+# Combine into three panel
+w_mean_B_vs_f_v_fmsy_plot <- plot_grid(
+
+  plot_grid(w_mean_B_vs_median_f_v_fmsy_plot + theme(legend.position = "none", axis.title.x = element_blank()),
+            w_mean_B_vs_mean_f_v_fmsy_plot + theme(legend.position = "none", axis.title.x = element_blank()),
+            w_mean_B_vs_w_mean_f_v_fmsy_plot + theme(legend.position = "none"),
+            ncol = 1,
+            align = "hv"),
+  corr_legend,
+  ncol = 1,
+  rel_heights = c(3, 0.2))
+
+w_mean_B_vs_f_v_fmsy_plot
+ggsave(paste0(results_dir, "w_mean_B_vs_f_v_fmsy_plot.png"), dpi = 200, width = 7, height = 12.5)
+```
+
+#### Bad + Ambiguous Subsidies
+
+```{r}
+# Weighted Mean Bad + Ambiguous Subs vs Median F/Fmsy [BEST]
+w_mean_BC_vs_median_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
                                        res = "corr",
                                        x = "w_mean_BC_subs_KWh",
-                                       x_name = "Weighted Mean Subsidy Intensity ($/KWh)",
-                                       x_limits = c(0,2),
+                                       x_name = w_mean_subs_label,
+                                       x_limits = subs_x,
+                                       y = "med_f_v_fmsy",
+                                       y_name = median_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+# Weighted Mean Bad + Ambiguous Subs vs Mean F/Fmsy [LAST]
+w_mean_BC_vs_mean_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "w_mean_BC_subs_KWh",
+                                       x_name = w_mean_subs_label,
+                                       x_limits = subs_x,
+                                       y = "mean_f_v_fmsy",
+                                       y_name = mean_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+# Weighted Mean Total Subs vs Weighted Mean F/Fmsy [SECOND]
+w_mean_BC_vs_w_mean_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "w_mean_BC_subs_KWh",
+                                       x_name = w_mean_subs_label,
+                                       x_limits = subs_x,
                                        y = "w_mean_f_v_fmsy",
-                                       y_name = "Weighted Mean F/Fmsy",
-                                       y_limits = c(0,2.5),
-                                       fill = "tot_fishing_KWh",
-                                       fill_name = "Total Fishing Effort \n(KWh, billions)",
-                                       fill_limits = c(0,7.5e9),
-                                       fill_breaks = seq(0,7.5e9, length.out = 5),
-                                       fill_labels = format(seq(0,7.5e9, length.out = 5)/1e9, scientific = F, digits = 2))
-
-ggsave(paste0(results_dir, "w_mean_BC_vs_f_v_fmsy_plot.png"), dpi = 200, width = 7, height = 7)
-
-# mean of Bad + Ambig vs mean F/Fmsy
-w_mean_BC_vs_median_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
-                                       res = "corr",
-                                       x = "w_mean_BC_subs_KWh",
-                                       x_name = "Weighted Mean Subsidy Intensity ($/KWh)",
-                                       x_limits = c(0,4),
+                                       y_name = w_mean_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+# Combine into three panel
+w_mean_BC_vs_f_v_fmsy_plot <- plot_grid(
+
+  plot_grid(w_mean_BC_vs_median_f_v_fmsy_plot + theme(legend.position = "none", axis.title.x = element_blank()),
+            w_mean_BC_vs_mean_f_v_fmsy_plot + theme(legend.position = "none", axis.title.x = element_blank()),
+            w_mean_BC_vs_w_mean_f_v_fmsy_plot + theme(legend.position = "none"),
+            ncol = 1,
+            align = "hv"),
+  corr_legend,
+  ncol = 1,
+  rel_heights = c(3, 0.2))
+
+w_mean_BC_vs_f_v_fmsy_plot
+ggsave(paste0(results_dir, "w_mean_BC_vs_f_v_fmsy_plot.png"), dpi = 200, width = 7, height = 12.5)
+```
+
+### Use Mean Subsidies
+
+#### Total Subsidies
+
+```{r}
+# Mean Total Subs vs Median F/Fmsy [BEST]
+mean_tot_vs_median_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "mean_tot_subs_KWh",
+                                       x_name = mean_subs_label,
+                                       x_limits = subs_x,
                                        y = "med_f_v_fmsy",
-                                       y_name = "Median F/Fmsy",
-                                       y_limits = c(0,4),
-                                       fill = "tot_fishing_KWh",
-                                       fill_name = "Total Fishing Effort \n(KWh, billions)",
-                                       fill_limits = c(0,7.5e9),
-                                       fill_breaks = seq(0,7.5e9, length.out = 5),
-                                       fill_labels = format(seq(0,7.5e9, length.out = 5)/1e9, scientific = F, digits = 2))
-
-ggsave(paste0(results_dir, "w_mean_BC_vs_median_f_v_fmsy_plot.png"), dpi = 200, width = 7, height = 7)
+                                       y_name = median_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+ggsave(paste0(results_dir, "mean_tot_vs_median_f_v_fmsy_plot.png"), dpi = 200, width = 7, height = 7)
+
+# Mean Total Subs vs Mean F/Fmsy [LAST]
+mean_tot_vs_mean_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "mean_tot_subs_KWh",
+                                       x_name = mean_subs_label,
+                                       x_limits = subs_x,
+                                       y = "mean_f_v_fmsy",
+                                       y_name = mean_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+ggsave(paste0(results_dir, "mean_tot_vs_mean_f_v_fmsy_plot.png"), dpi = 200, width = 7, height = 7)
+
+# Mean Total Subs vs Weighted Mean F/Fmsy [SECOND]
+mean_tot_vs_w_mean_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "mean_tot_subs_KWh",
+                                       x_name = mean_subs_label,
+                                       x_limits = subs_x,
+                                       y = "w_mean_f_v_fmsy",
+                                       y_name = w_mean_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+ggsave(paste0(results_dir, "mean_tot_vs_w_mean_f_v_fmsy_plot.png"), dpi = 200, width = 7, height = 7)
+
+# Combine into three panel
+mean_tot_vs_f_v_fmsy_plot <- plot_grid(
+
+  plot_grid(mean_tot_vs_median_f_v_fmsy_plot + theme(legend.position = "none", axis.title.x = element_blank()),
+            mean_tot_vs_mean_f_v_fmsy_plot + theme(legend.position = "none", axis.title.x = element_blank()),
+            mean_tot_vs_w_mean_f_v_fmsy_plot + theme(legend.position = "none"),
+            ncol = 1,
+            align = "hv"),
+  corr_legend,
+  ncol = 1,
+  rel_heights = c(3, 0.2))
+
+mean_tot_vs_f_v_fmsy_plot
+ggsave(paste0(results_dir, "mean_tot_vs_f_v_fmsy_plot.png"), dpi = 200, width = 7, height = 12.5)
+```
+
+#### Bad Subsidies
+
+```{r}
+# Weighted Mean Bad Subs vs Median F/Fmsy [SECOND]
+mean_B_vs_median_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "mean_B_subs_KWh",
+                                       x_name = mean_subs_label,
+                                       x_limits = subs_x,
+                                       y = "med_f_v_fmsy",
+                                       y_name = median_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+# Weighted Mean Bad Subs vs Mean F/Fmsy [LAST]
+mean_B_vs_mean_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "mean_B_subs_KWh",
+                                       x_name = mean_subs_label,
+                                       x_limits = subs_x,
+                                       y = "mean_f_v_fmsy",
+                                       y_name = mean_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+# Weighted Mean Total Subs vs Weighted Mean F/Fmsy [BEST]
+mean_B_vs_w_mean_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "mean_B_subs_KWh",
+                                       x_name = mean_subs_label,
+                                       x_limits = subs_x,
+                                       y = "w_mean_f_v_fmsy",
+                                       y_name = w_mean_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+# Combine into three panel
+mean_B_vs_f_v_fmsy_plot <- plot_grid(
+
+  plot_grid(mean_B_vs_median_f_v_fmsy_plot + theme(legend.position = "none", axis.title.x = element_blank()),
+            mean_B_vs_mean_f_v_fmsy_plot + theme(legend.position = "none", axis.title.x = element_blank()),
+            mean_B_vs_w_mean_f_v_fmsy_plot + theme(legend.position = "none"),
+            ncol = 1,
+            align = "hv"),
+  corr_legend,
+  ncol = 1,
+  rel_heights = c(3, 0.2))
+
+mean_B_vs_f_v_fmsy_plot
+ggsave(paste0(results_dir, "mean_B_vs_f_v_fmsy_plot.png"), dpi = 200, width = 7, height = 12.5)
+```
+
+#### Bad + Ambiguous Subsidies
+
+```{r}
+# Mean Bad + Ambiguous Subs vs Median F/Fmsy [SECOND]
+mean_BC_vs_median_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "mean_BC_subs_KWh",
+                                       x_name = mean_subs_label,
+                                       x_limits = subs_x,
+                                       y = "med_f_v_fmsy",
+                                       y_name = median_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+# Mean Bad + Ambiguous Subs vs Mean F/Fmsy [LAST]
+mean_BC_vs_mean_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "mean_BC_subs_KWh",
+                                       x_name = mean_subs_label,
+                                       x_limits = subs_x,
+                                       y = "mean_f_v_fmsy",
+                                       y_name = mean_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+# Mean Total Subs vs Weighted Mean F/Fmsy [BEST]
+mean_BC_vs_w_mean_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "mean_BC_subs_KWh",
+                                       x_name = mean_subs_label,
+                                       x_limits = subs_x,
+                                       y = "w_mean_f_v_fmsy",
+                                       y_name = w_mean_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+# Combine into three panel
+mean_BC_vs_f_v_fmsy_plot <- plot_grid(
+
+  plot_grid(mean_BC_vs_median_f_v_fmsy_plot + theme(legend.position = "none", axis.title.x = element_blank()),
+            mean_BC_vs_mean_f_v_fmsy_plot + theme(legend.position = "none", axis.title.x = element_blank()),
+            mean_BC_vs_w_mean_f_v_fmsy_plot + theme(legend.position = "none"),
+            ncol = 1,
+            align = "hv"),
+  corr_legend,
+  ncol = 1,
+  rel_heights = c(3, 0.2))
+
+mean_BC_vs_f_v_fmsy_plot
+ggsave(paste0(results_dir, "mean_BC_vs_f_v_fmsy_plot.png"), dpi = 200, width = 7, height = 12.5)
+
+```
+
+### Use Median Subsidies
+
+#### Total Subsidies
+
+```{r}
+# Median Total Subs vs Median F/Fmsy [BAD]
+median_tot_vs_median_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "med_tot_subs_KWh",
+                                       x_name = median_subs_label,
+                                       x_limits = subs_x,
+                                       y = "med_f_v_fmsy",
+                                       y_name = median_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+# Median Total Subs vs Mean F/Fmsy [BAD]
+median_tot_vs_mean_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "med_tot_subs_KWh",
+                                       x_name = median_subs_label,
+                                       x_limits = subs_x,
+                                       y = "mean_f_v_fmsy",
+                                       y_name = mean_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+# Median Total Subs vs Weighted Mean F/Fmsy [BEST]
+median_tot_vs_w_mean_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "med_tot_subs_KWh",
+                                       x_name = median_subs_label,
+                                       x_limits = subs_x,
+                                       y = "w_mean_f_v_fmsy",
+                                       y_name = w_mean_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+# Combine into three panel
+median_tot_vs_f_v_fmsy_plot <- plot_grid(
+
+  plot_grid(median_tot_vs_median_f_v_fmsy_plot + theme(legend.position = "none", axis.title.x = element_blank()),
+            median_tot_vs_mean_f_v_fmsy_plot + theme(legend.position = "none", axis.title.x = element_blank()),
+            median_tot_vs_w_mean_f_v_fmsy_plot + theme(legend.position = "none"),
+            ncol = 1,
+            align = "hv"),
+  corr_legend,
+  ncol = 1,
+  rel_heights = c(3, 0.2))
+
+median_tot_vs_f_v_fmsy_plot
+ggsave(paste0(results_dir, "median_tot_vs_f_v_fmsy_plot.png"), dpi = 200, width = 7, height = 12.5)
+
+```
+
+#### Bad Subsidies
+
+```{r}
+# Median Bad Subs vs Median F/Fmsy [BAD]
+median_B_vs_median_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "med_B_subs_KWh",
+                                       x_name = median_subs_label,
+                                       x_limits = subs_x,
+                                       y = "med_f_v_fmsy",
+                                       y_name = median_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+# Median Bad Subs vs Mean F/Fmsy [BAD]
+median_B_vs_mean_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "med_B_subs_KWh",
+                                       x_name = median_subs_label,
+                                       x_limits = subs_x,
+                                       y = "mean_f_v_fmsy",
+                                       y_name = mean_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+# Median Total Subs vs Weighted Mean F/Fmsy [MEH]
+median_B_vs_w_mean_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "med_B_subs_KWh",
+                                       x_name = median_subs_label,
+                                       x_limits = subs_x,
+                                       y = "w_mean_f_v_fmsy",
+                                       y_name = w_mean_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+# Combine into three panel
+median_B_vs_f_v_fmsy_plot <- plot_grid(
+
+  plot_grid(median_B_vs_median_f_v_fmsy_plot + theme(legend.position = "none", axis.title.x = element_blank()),
+            median_B_vs_mean_f_v_fmsy_plot + theme(legend.position = "none", axis.title.x = element_blank()),
+            median_B_vs_w_mean_f_v_fmsy_plot + theme(legend.position = "none"),
+            ncol = 1,
+            align = "hv"),
+  corr_legend,
+  ncol = 1,
+  rel_heights = c(3, 0.2))
+
+median_B_vs_f_v_fmsy_plot
+ggsave(paste0(results_dir, "median_B_vs_f_v_fmsy_plot.png"), dpi = 200, width = 7, height = 12.5)
+```
+
+#### Bad + Ambiguous Subsidies
+
+```{r}
+# Median Bad + Ambiguous Subs vs Median F/Fmsy [BAD]
+median_BC_vs_median_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "med_BC_subs_KWh",
+                                       x_name = median_subs_label,
+                                       x_limits = subs_x,
+                                       y = "med_f_v_fmsy",
+                                       y_name = median_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+# Median Bad + Ambiguous Subs vs Mean F/Fmsy [MEH]
+median_BC_vs_mean_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "med_BC_subs_KWh",
+                                       x_name = median_subs_label,
+                                       x_limits = subs_x,
+                                       y = "mean_f_v_fmsy",
+                                       y_name = mean_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+# Median Total Subs vs Weighted Mean F/Fmsy [MEH]
+median_BC_vs_w_mean_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+                                       res = "corr",
+                                       x = "med_BC_subs_KWh",
+                                       x_name = median_subs_label,
+                                       x_limits = subs_x,
+                                       y = "w_mean_f_v_fmsy",
+                                       y_name = w_mean_f_label,
+                                       y_limits = f_y,
+                                       fill = "tot_fishing_KWh",
+                                       fill_name = effort_label,
+                                       fill_limits = effort_fill_lim,
+                                       fill_breaks = effort_fill_breaks,
+                                       fill_labels = effort_fill_labels)
+
+# Combine into three panel
+median_BC_vs_f_v_fmsy_plot <- plot_grid(
+
+  plot_grid(median_BC_vs_median_f_v_fmsy_plot + theme(legend.position = "none", axis.title.x = element_blank()),
+            median_BC_vs_mean_f_v_fmsy_plot + theme(legend.position = "none", axis.title.x = element_blank()),
+            median_BC_vs_w_mean_f_v_fmsy_plot + theme(legend.position = "none"),
+            ncol = 1,
+            align = "hv"),
+  corr_legend,
+  ncol = 1,
+  rel_heights = c(3, 0.2))
+
+median_BC_vs_f_v_fmsy_plot
+ggsave(paste0(results_dir, "median_BC_vs_f_v_fmsy_plot.png"), dpi = 200, width = 7, height = 12.5)
 

### 2020-03-24 scripts/01_data_wrangling.Rmd
cleaning up

@@
 ```
+
+# Section 5 - Relative Metrics
+
+This second is a bit of a relic from when we were doing "country profiles", but there are a couple of relative metrics we want to calculate from our data sources. This is done here.
+
+```{r}
+# GDP
+gdp_dat_mry <- wb_dat_edit %>%
+  dplyr::filter(variable == "gdp") %>%
+  group_by(iso3, variable) %>%
+  dplyr::filter(year == max(year[!is.na(value)])) %>%
+  ungroup() %>%
+  dplyr::select(-units) %>%
+  dplyr::select(iso3, gdp_year = year, gdp = value)
+
+# Population
+pop_dat_mry <- wb_dat_edit %>%
+  dplyr::filter(variable == "population") %>%
+  group_by(iso3, variable) %>%
+  dplyr::filter(year == max(year[!is.na(value)])) %>%
+  ungroup() %>%
+  dplyr::select(-units) %>%
+  dplyr::select(iso3, population_year = year, population = value)
+
+# Fishers
+fisher_dat_mry <- fao_fishers_dat_edit %>%
+  group_by(iso3, variable) %>%
+  dplyr::filter(year == max(year[!is.na(value)])) %>%
+  ungroup() %>%
+  dplyr::select(-units) %>%
+  dplyr::select(iso3, fishers_year = year, fishers = value)
+
+# FTE
+fte_dat_mry <- teh_fte_dat_edit %>%
+  dplyr::select(iso3, fte_year = year, fte = value)
+
+# Capture Production
+
+# Landed Value
+
+# Combine with subsidy data and calculate relative metrics
+relative_dat <- sumaila_2019_dat_edit %>%
+  dplyr::select(-data_type, -units, -source, -variable) %>%
+  rename(subs = value) %>%
+  left_join()
+```

### 2020-03-24 functions/MapMaker.R

@@ -106,16 +106,16 @@ MapMaker <- function(data,
     
   }else if(res == "corr"){
     
-    # This one isn't a map, but puttin it here for now
+    # This one isn't a map, but putting it here for now
     out <- data %>%
       ggplot()+
-      aes(x = get(x), y = get(y), size = get(fill))+
-      geom_point(color = "black")+
+      aes(x = get(x), y = get(y))+
+      geom_smooth(method = "lm", na.rm = T, se = F, color = "black")+
+      geom_point(aes(size = get(fill)), color = "black")+
       scale_size(name = fill_name,
                  limits = fill_limits,
                  breaks = fill_breaks,
                  labels = fill_labels)+
-      geom_smooth(method = "lm", na.rm = T, se = F, color = "black")+
       # scale_color_distiller(type = "seq", palette = "RdYlBu",
       #                      name = fill_name,
       #                      na.value = "#000000", 

### 2020-03-24 papers/paper-1/paper_1_figures.Rmd
v1 figures done for first paper

--- 2020-03-19 papers/paper-1/paper_1_figures.Rmd
@@
 
+# Version name
+version <- "v1"
+
 # Directories for the output files generated by this script
-results_dir <- here::here("papers", "paper-1/")
+results_dir <- paste0(here::here("papers", "paper-1/"), version, "/")
 if (dir.exists(results_dir) == F) {
@@
 subsidy_dat_sumaila <- read_csv(subsidy_dat_sumaila_path) %>%
-  group_by(iso3, category) %>%
-  summarize(subs = sum(value, na.rm = T)) %>%
-  spread(category, subs) %>%
-  rename(A_subs = A,
-         B_subs = B,
-         C_subs = C) %>%
-  mutate(BC_subs = B_subs + C_subs,
-         tot_subs = A_subs + B_subs + C_subs)
+  group_by(iso3, category, type) %>%
+  summarize(value = sum(value, na.rm = T)) %>%
+  group_by(iso3) %>%
+  summarize(A_subs = sum(value[category == "A"], na.rm = T),
+            B_subs = sum(value[category == "B"], na.rm = T),
+            C_subs = sum(value[category == "C"], na.rm = T),
+            BC_subs = sum(value[category %in% c("B", "C")], na.rm = T),
+            tot_subs = sum(value, na.rm = T),
+            fuel_subs = sum(value[type == "B7"], na.rm = T))
 ```
@@
   left_join(subsidy_dat_sumaila, by = c("new_flag" = "iso3")) %>%
-  mutate(A_subs_KWh = A_subs/fishing_KWh_lat_lon,
-         B_subs_KWh = B_subs/fishing_KWh_lat_lon,
-         C_subs_KWh = C_subs/fishing_KWh_lat_lon,
-         BC_subs_KWh = BC_subs/fishing_KWh_lat_lon,
-         tot_subs_KWh = tot_subs/fishing_KWh_lat_lon) %>%
+  mutate_at(vars(contains("subs")), list(KWh = ~./fishing_KWh_lat_lon)) %>%
   dplyr::select(new_flag, contains("subs_KWh"))
@@
 effort_binned_sub_intensity <- effort_binned %>%
-  left_join(subsidy_rates_flag, by = "new_flag") %>%
-  mutate(B_subs = B_subs_KWh*fishing_KWh_lat_lon,
-         BC_subs = BC_subs_KWh*fishing_KWh_lat_lon,
-         C_subs = C_subs_KWh*fishing_KWh_lat_lon,
-         tot_subs = tot_subs_KWh*fishing_KWh_lat_lon)
+  left_join(subsidy_rates_flag, by = "new_flag")
 
@@
   group_by(lat_bin_center, lon_bin_center) %>%
-  summarize(med_B_subs_KWh = median(B_subs_KWh, na.rm = T),
-            med_BC_subs_KWh = median(BC_subs_KWh, na.rm = T),
-            med_tot_subs_KWh = median(tot_subs_KWh, na.rm = T),
-            mean_B_subs_KWh = mean(B_subs_KWh, na.rm = T),
-            mean_BC_subs_KWh = mean(BC_subs_KWh, na.rm = T),
-            mean_tot_subs_KWh = mean(tot_subs_KWh, na.rm = T),
-            w_mean_B_subs_KWh = weighted.mean(B_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
-            w_mean_BC_subs_KWh = weighted.mean(BC_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
-            w_mean_tot_subs_KWh = weighted.mean(tot_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
-            B_subs = sum(B_subs, na.rm = T),
-            BC_subs = sum(BC_subs, na.rm = T),
-            C_subs = sum(C_subs, na.rm = T),
-            tot_subs = sum(tot_subs, na.rm = T),
-            tot_fishing_KWh = sum(fishing_KWh_lat_lon, na.rm = T))
+  summarize_at(vars(contains("subs_KWh"), "fishing_KWh_lat_lon"), 
+               list(median = ~median(., na.rm = T),
+                    mean = ~ mean(., na.rm = T),
+                    w_mean = ~weighted.mean(., w = fishing_KWh_lat_lon, na.rm = T),
+                    sum = ~sum(., na.rm = T))) %>%
+  dplyr::select(-c(contains("subs_KWh_sum"), "fishing_KWh_lat_lon_median", "fishing_KWh_lat_lon_mean", "fishing_KWh_lat_lon_w_mean"))
 
@@
   group_by(fao_region) %>%
-  summarize(med_B_subs_KWh = median(B_subs_KWh, na.rm = T),
-            med_BC_subs_KWh = median(BC_subs_KWh, na.rm = T),
-            med_tot_subs_KWh = median(tot_subs_KWh, na.rm = T),
-            mean_B_subs_KWh = mean(B_subs_KWh, na.rm = T),
-            mean_BC_subs_KWh = mean(BC_subs_KWh, na.rm = T),
-            mean_tot_subs_KWh = mean(tot_subs_KWh, na.rm = T),
-            w_mean_B_subs_KWh = weighted.mean(B_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
-            w_mean_BC_subs_KWh = weighted.mean(BC_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
-            w_mean_tot_subs_KWh = weighted.mean(tot_subs_KWh, w = fishing_KWh_lat_lon, na.rm = T),
-            B_subs = sum(B_subs, na.rm = T),
-            BC_subs = sum(BC_subs, na.rm = T),
-            C_subs = sum(C_subs, na.rm = T),
-            tot_subs = sum(tot_subs, na.rm = T),
-            tot_fishing_KWh = sum(fishing_KWh_lat_lon, na.rm = T))
+  summarize_at(vars(contains("subs_KWh"), "fishing_KWh_lat_lon"), 
+               list(median = ~median(., na.rm = T),
+                    mean = ~ mean(., na.rm = T),
+                    w_mean = ~weighted.mean(., w = fishing_KWh_lat_lon, na.rm = T),
+                    sum = ~sum(., na.rm = T))) %>%
+  dplyr::select(-c(contains("subs_KWh_sum"), "fishing_KWh_lat_lon_median", "fishing_KWh_lat_lon_mean", "fishing_KWh_lat_lon_w_mean"))
 ```
@@
 
+```{r}
+subs_fill_label <- "Subsidy Intensity \n($/KWh)"
+```
+
 ## Total Subsidies
 
-### Subsidy Intensities by Lat/Lon
+### Subsidy Intensity by 1x1 Degree
 
-```{r}
-# Median
-median_subsidy_intensity_tot_grid_map <- MapMaker(data = subsidy_intensity_binned,
+```{r, fig.width=4, fig.height=7}
+# Scales 
+tot_subs_fill_breaks <- seq(0,8, by = 2)
+tot_subs_fill_limits <- c(0,8)
+tot_subs_fill_labels <- c("0", "2", "4", "6", "\u2265 8")
+
+# Total subsidies (grid)
+subsidy_intensity_tot_grid_l <- MapMaker(data = subsidy_intensity_binned,
                                          res = "grid",
@@
                                          y = "lat_bin_center",
-                                                  fill = "med_tot_subs_KWh",
-                                                  fill_name = "Subsidy Intensity \n($/KWh)",
-                                                  fill_breaks = seq(0,8, by = 2),
-                                                  fill_limits = c(0,8),
-                                                  fill_labels = c("0", "2", "4", "6", "8"),
-                                                  land_sf = world_land)
+                                         fill = "tot_subs_KWh",
+                                         fill_name = subs_fill_label,
+                                         fill_breaks = tot_subs_fill_breaks,
+                                         fill_limits = tot_subs_fill_limits,
+                                         fill_labels = tot_subs_fill_labels,
+                                         land_sf = world_land,
+                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
+                                         file_name = "subsidy_intensity_tot_grid_map",
+                                         file_dir = results_dir)
 
-ggsave(paste0(results_dir, "median_subsidy_intensity_tot_grid_map.png"), dpi = 200, width = 7, height = 5)
-
-# Mean
-mean_subsidy_intensity_tot_grid_map <- MapMaker(data = subsidy_intensity_binned,
-                                                  res = "grid",
-                                                  x = "lon_bin_center",
-                                                  y = "lat_bin_center",
-                                                  fill = "mean_tot_subs_KWh",
-                                                  fill_name = "Subsidy Intensity \n($/KWh)",
-                                                  fill_breaks = seq(0,8, by = 2),
-                                                  fill_limits = c(0,8),
-                                                  fill_labels = c("0", "2", "4", "6", "8"),
-                                                  land_sf = world_land)
-
-ggsave(paste0(results_dir, "mean_subsidy_intensity_tot_grid_map.png"), dpi = 200, width = 7, height = 5)
-
-# Weighted Mean
-w_mean_subsidy_intensity_tot_grid_map <- MapMaker(data = subsidy_intensity_binned,
-                                                  res = "grid",
-                                                  x = "lon_bin_center",
-                                                  y = "lat_bin_center",
-                                                  fill = "w_mean_tot_subs_KWh",
-                                                  fill_name = "Subsidy Intensity \n($/KWh)",
-                                                  fill_breaks = seq(0,8, by = 2),
-                                                  fill_limits = c(0,8),
-                                                  fill_labels = c("0", "2", "4", "6", "8"),
-                                                  land_sf = world_land)
-
-ggsave(paste0(results_dir, "w_mean_subsidy_intensity_tot_grid_map.png"), dpi = 200, width = 7, height = 5)
-
-# Combine into three panel
-intensity_tot_grid_legend <- get_legend(w_mean_subsidy_intensity_tot_grid_map)
-
-subsidy_intensity_tot_grid_map <- plot_grid(median_subsidy_intensity_tot_grid_map + theme(legend.position = "none"),
-                                            mean_subsidy_intensity_tot_grid_map + theme(legend.position = "none"),
-                                            w_mean_subsidy_intensity_tot_grid_map + theme(legend.position = "none"),
-                                            intensity_tot_grid_legend,
-                                            ncol = 1,
-                                            rel_heights = c(1,1,1,0.2),
-                                            labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
-                                            label_x = c(-0.04,-0.03,-0.1,0),
-                                            align = "v")
-
-subsidy_intensity_tot_grid_map
-ggsave(paste0(results_dir, "subsidy_intensity_tot_grid_map.png"), dpi = 200, width = 7, height = 12.5)
+subsidy_intensity_tot_grid_l[["all"]]
 
@@
 
-```{r}
-# Median
-median_subsidy_intensity_tot_region_map <- MapMaker(data = subsidy_intensity_region,
+```{r, fig.width=4, fig.height=7}
+# Total subsidies (region)
+subsidy_intensity_tot_region_l <- MapMaker(data = subsidy_intensity_region,
                                          res = "region",
-                                                  fill = "med_tot_subs_KWh",
-                                                  fill_name = "Subsidy Intensity \n($/KWh)",
-                                                  fill_breaks = seq(0,8, by = 2),
-                                                  fill_limits = c(0,8),
-                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                         x = "lon_bin_center",
+                                         y = "lat_bin_center",
+                                         fill = "tot_subs_KWh",
+                                         fill_name = subs_fill_label,
+                                         fill_breaks = tot_subs_fill_breaks,
+                                         fill_limits = tot_subs_fill_limits,
+                                         fill_labels = tot_subs_fill_labels,
                                          land_sf = world_land,
-                                                  region_sf = fao_regions)
+                                         region_sf = fao_regions,
+                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
+                                         file_name = "subsidy_intensity_tot_region_map",
+                                         file_dir = results_dir)
 
-ggsave(paste0(results_dir, "median_subsidy_intensity_tot_region_map.png"), dpi = 200, width = 7, height = 5)
-
-# Mean
-mean_subsidy_intensity_tot_region_map <- MapMaker(data = subsidy_intensity_region,
-                                                  res = "region",
-                                                  fill = "mean_tot_subs_KWh",
-                                                  fill_name = "Subsidy Intensity \n($/KWh)",
-                                                  fill_breaks = seq(0,8, by = 2),
-                                                  fill_limits = c(0,8),
-                                                  fill_labels = c("0", "2", "4", "6", "8"),
-                                                  land_sf = world_land,
-                                                  region_sf = fao_regions)
-
-ggsave(paste0(results_dir, "mean_subsidy_intensity_tot_region_map.png"), dpi = 200, width = 7, height = 5)
-
-# Weighted Mean
-w_mean_subsidy_intensity_tot_region_map <- MapMaker(data = subsidy_intensity_region,
-                                                  res = "region",
-                                                  fill = "w_mean_tot_subs_KWh",
-                                                  fill_name = "Subsidy Intensity \n($/KWh)",
-                                                  fill_breaks = seq(0,8, by = 2),
-                                                  fill_limits = c(0,8),
-                                                  fill_labels = c("0", "2", "4", "6", "8"),
-                                                  land_sf = world_land,
-                                                  region_sf = fao_regions)
-
-ggsave(paste0(results_dir, "w_mean_subsidy_intensity_tot_region_map.png"), dpi = 200, width = 7, height = 5)
-
-# Combine into three panel
-intensity_tot_region_legend <- get_legend(w_mean_subsidy_intensity_tot_region_map)
-
-subsidy_intensity_tot_region_map <- plot_grid(median_subsidy_intensity_tot_region_map + theme(legend.position = "none"),
-                                            mean_subsidy_intensity_tot_region_map + theme(legend.position = "none"),
-                                            w_mean_subsidy_intensity_tot_region_map + theme(legend.position = "none"),
-                                            intensity_tot_region_legend,
-                                            ncol = 1,
-                                            rel_heights = c(1,1,1,0.2),
-                                            labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
-                                            label_x = c(-0.04,-0.03,-0.1,0),
-                                            align = "v")
-
-subsidy_intensity_tot_region_map
-ggsave(paste0(results_dir, "subsidy_intensity_tot_region_map.png"), dpi = 200, width = 7, height = 12.5)
-
+subsidy_intensity_tot_region_l[["all"]]
 ```
 
-## Bad Subsidies
+```{r, fig.width=8, fig.height=7}
+# Combine into six panel
+subsidy_intensity_tot_map <- plot_grid(
 
-### Subsidy Intensities by Lat/Lon
+  plot_grid(subsidy_intensity_tot_grid_l[["median"]] + theme(legend.position = "none"),
+            subsidy_intensity_tot_region_l[["median"]] + theme(legend.position = "none"),
+            subsidy_intensity_tot_grid_l[["mean"]] + theme(legend.position = "none"),
+            subsidy_intensity_tot_region_l[["mean"]] + theme(legend.position = "none"),
+            subsidy_intensity_tot_grid_l[["w_mean"]] + theme(legend.position = "none"),
+            subsidy_intensity_tot_region_l[["w_mean"]] + theme(legend.position = "none"),
+            ncol = 2,
+            labels = c("A) Median", "", "B) Mean", "", "C) Weighted Mean"),
+            align = "hv"),
 
-```{r}
-# Median
-median_subsidy_intensity_B_grid_map <- MapMaker(data = subsidy_intensity_binned,
+  get_legend(subsidy_intensity_tot_region_l[["w_mean"]]),
+  rel_heights = c(2,0.2),
+  ncol = 1)
+
+subsidy_intensity_tot_map
+ggsave(paste0(results_dir, "subsidy_intensity_tot_map.png"), dpi = 200, width = 14, height = 12.5)
+```
+
+## Bad Subsidies Only
+
+### Subsidy Intensity by 1x1 Degree
+
+```{r, fig.width=4, fig.height=7}
+# Scales 
+B_subs_fill_breaks <- seq(0,5, by = 1)
+B_subs_fill_limits <- c(0,5)
+B_subs_fill_labels <- c("0","1", "2", "3", "4", "\u2265 5")
+
+# Total subsidies (grid)
+subsidy_intensity_B_grid_l <- MapMaker(data = subsidy_intensity_binned,
                                          res = "grid",
@@
                                          y = "lat_bin_center",
-                                                  fill = "med_B_subs_KWh",
-                                                  fill_name = "Subsidy Intensity \n($/KWh)",
-                                                  fill_breaks = seq(0,8, by = 2),
-                                                  fill_limits = c(0,8),
-                                                  fill_labels = c("0", "2", "4", "6", "8"),
-                                                  land_sf = world_land)
+                                         fill = "B_subs_KWh",
+                                         fill_name = subs_fill_label,
+                                         fill_breaks = B_subs_fill_breaks,
+                                         fill_limits = B_subs_fill_limits,
+                                         fill_labels = B_subs_fill_labels,
+                                         land_sf = world_land,
+                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
+                                         file_name = "subsidy_intensity_B_grid_map",
+                                         file_dir = results_dir)
 
-ggsave(paste0(results_dir, "median_subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 5)
-
-# Mean
-mean_subsidy_intensity_B_grid_map <- MapMaker(data = subsidy_intensity_binned,
-                                                  res = "grid",
-                                                  x = "lon_bin_center",
-                                                  y = "lat_bin_center",
-                                                  fill = "mean_B_subs_KWh",
-                                                  fill_name = "Subsidy Intensity \n($/KWh)",
-                                                  fill_breaks = seq(0,8, by = 2),
-                                                  fill_limits = c(0,8),
-                                                  fill_labels = c("0", "2", "4", "6", "8"),
-                                                  land_sf = world_land)
-
-ggsave(paste0(results_dir, "mean_subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 5)
-
-# Weighted Mean
-w_mean_subsidy_intensity_B_grid_map <- MapMaker(data = subsidy_intensity_binned,
-                                                  res = "grid",
-                                                  x = "lon_bin_center",
-                                                  y = "lat_bin_center",
-                                                  fill = "w_mean_B_subs_KWh",
-                                                  fill_name = "Subsidy Intensity \n($/KWh)",
-                                                  fill_breaks = seq(0,8, by = 2),
-                                                  fill_limits = c(0,8),
-                                                  fill_labels = c("0", "2", "4", "6", "8"),
-                                                  land_sf = world_land)
-
-ggsave(paste0(results_dir, "w_mean_subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 5)
-
-# Combine into three panel
-intensity_B_grid_legend <- get_legend(w_mean_subsidy_intensity_B_grid_map)
-
-subsidy_intensity_B_grid_map <- plot_grid(median_subsidy_intensity_B_grid_map + theme(legend.position = "none"),
-                                            mean_subsidy_intensity_B_grid_map + theme(legend.position = "none"),
-                                            w_mean_subsidy_intensity_B_grid_map + theme(legend.position = "none"),
-                                            intensity_B_grid_legend,
-                                            ncol = 1,
-                                            rel_heights = c(1,1,1,0.2),
-                                            labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
-                                            label_x = c(-0.04,-0.03,-0.1,0),
-                                            align = "v")
-
-subsidy_intensity_B_grid_map
-ggsave(paste0(results_dir, "subsidy_intensity_B_grid_map.png"), dpi = 200, width = 7, height = 12.5)
+subsidy_intensity_B_grid_l[["all"]]
 
@@
 
-```{r}
-# Median
-median_subsidy_intensity_B_region_map <- MapMaker(data = subsidy_intensity_region,
+```{r, fig.width=4, fig.height=7}
+# Total subsidies (region)
+subsidy_intensity_B_region_l <- MapMaker(data = subsidy_intensity_region,
                                          res = "region",
-                                                  fill = "med_B_subs_KWh",
-                                                  fill_name = "Subsidy Intensity \n($/KWh)",
-                                                  fill_breaks = seq(0,8, by = 2),
-                                                  fill_limits = c(0,8),
-                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                         x = "lon_bin_center",
+                                         y = "lat_bin_center",
+                                         fill = "B_subs_KWh",
+                                         fill_name = subs_fill_label,
+                                         fill_breaks = B_subs_fill_breaks,
+                                         fill_limits = B_subs_fill_limits,
+                                         fill_labels = B_subs_fill_labels,
                                          land_sf = world_land,
-                                                  region_sf = fao_regions)
+                                         region_sf = fao_regions,
+                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
+                                         file_name = "subsidy_intensity_B_region_map",
+                                         file_dir = results_dir)
 
-ggsave(paste0(results_dir, "median_subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 5)
-
-# Mean
-mean_subsidy_intensity_B_region_map <- MapMaker(data = subsidy_intensity_region,
-                                                  res = "region",
-                                                  fill = "mean_B_subs_KWh",
-                                                  fill_name = "Subsidy Intensity \n($/KWh)",
-                                                  fill_breaks = seq(0,8, by = 2),
-                                                  fill_limits = c(0,8),
-                                                  fill_labels = c("0", "2", "4", "6", "8"),
-                                                  land_sf = world_land,
-                                                  region_sf = fao_regions)
-
-ggsave(paste0(results_dir, "mean_subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 5)
-
-# Weighted Mean
-w_mean_subsidy_intensity_B_region_map <- MapMaker(data = subsidy_intensity_region,
-                                                  res = "region",
-                                                  fill = "w_mean_B_subs_KWh",
-                                                  fill_name = "Subsidy Intensity \n($/KWh)",
-                                                  fill_breaks = seq(0,8, by = 2),
-                                                  fill_limits = c(0,8),
-                                                  fill_labels = c("0", "2", "4", "6", "8"),
-                                                  land_sf = world_land,
-                                                  region_sf = fao_regions)
-
-ggsave(paste0(results_dir, "w_mean_subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 5)
-
-# Combine into three panel
-intensity_B_region_legend <- get_legend(w_mean_subsidy_intensity_B_region_map)
-
-subsidy_intensity_B_region_map <- plot_grid(median_subsidy_intensity_B_region_map + theme(legend.position = "none"),
-                                            mean_subsidy_intensity_B_region_map + theme(legend.position = "none"),
-                                            w_mean_subsidy_intensity_B_region_map + theme(legend.position = "none"),
-                                            intensity_B_region_legend,
-                                            ncol = 1,
-                                            rel_heights = c(1,1,1,0.2),
-                                            labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
-                                            label_x = c(-0.04,-0.03,-0.1,0),
-                                            align = "v")
-
-subsidy_intensity_B_region_map
-ggsave(paste0(results_dir, "subsidy_intensity_B_region_map.png"), dpi = 200, width = 7, height = 12.5)
-
+subsidy_intensity_B_region_l[["all"]]
 ```
 
-## Bad + Ambiguous Subsidies
+```{r, fig.width=8, fig.height=7}
+# Combine into six panel
+subsidy_intensity_B_map <- plot_grid(
+
+  plot_grid(subsidy_intensity_B_grid_l[["median"]] + theme(legend.position = "none"),
+            subsidy_intensity_B_region_l[["median"]] + theme(legend.position = "none"),
+            subsidy_intensity_B_grid_l[["mean"]] + theme(legend.position = "none"),
+            subsidy_intensity_B_region_l[["mean"]] + theme(legend.position = "none"),
+            subsidy_intensity_B_grid_l[["w_mean"]] + theme(legend.position = "none"),
+            subsidy_intensity_B_region_l[["w_mean"]] + theme(legend.position = "none"),
+            ncol = 2,
+            labels = c("A) Median", "", "B) Mean", "", "C) Weighted Mean"),
+            align = "hv"),
+
+  get_legend(subsidy_intensity_B_region_l[["w_mean"]]),
+  rel_heights = c(2,0.2),
+  ncol = 1)
+
+subsidy_intensity_B_map
+ggsave(paste0(results_dir, "subsidy_intensity_B_map.png"), dpi = 200, width = 14, height = 12.5)
+```
+
+## Bad and Ambiguous Subsidies Only
 
@@
 
-```{r}
-# Median
-median_subsidy_intensity_BC_grid_map <- MapMaker(data = subsidy_intensity_binned,
+```{r, fig.width=4, fig.height=7}
+# Scales 
+BC_subs_fill_breaks <- seq(0,3, by = 0.75)
+BC_subs_fill_limits <- c(0,3)
+BC_subs_fill_labels <- c("0", "0.75", "1.5", "2.25", "\u2265 3")
+
+# Total subsidies (grid)
+subsidy_intensity_BC_grid_l <- MapMaker(data = subsidy_intensity_binned,
                                          res = "grid",
@@
                                          y = "lat_bin_center",
-                                                  fill = "med_BC_subs_KWh",
-                                                  fill_name = "Subsidy Intensity \n($/KWh)",
-                                                  fill_breaks = seq(0,8, by = 2),
-                                                  fill_limits = c(0,8),
-                                                  fill_labels = c("0", "2", "4", "6", "8"),
-                                                  land_sf = world_land)
+                                         fill = "BC_subs_KWh",
+                                         fill_name = subs_fill_label,
+                                         fill_breaks = BC_subs_fill_breaks,
+                                         fill_limits = BC_subs_fill_limits,
+                                         fill_labels = BC_subs_fill_labels,
+                                         land_sf = world_land,
+                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
+                                         file_name = "subsidy_intensity_BC_grid_map",
+                                         file_dir = results_dir)
 
-ggsave(paste0(results_dir, "median_subsidy_intensity_BC_grid_map.png"), dpi = 200, width = 7, height = 5)
-
-# Mean
-mean_subsidy_intensity_BC_grid_map <- MapMaker(data = subsidy_intensity_binned,
-                                                  res = "grid",
-                                                  x = "lon_bin_center",
-                                                  y = "lat_bin_center",
-                                                  fill = "mean_BC_subs_KWh",
-                                                  fill_name = "Subsidy Intensity \n($/KWh)",
-                                                  fill_breaks = seq(0,8, by = 2),
-                                                  fill_limits = c(0,8),
-                                                  fill_labels = c("0", "2", "4", "6", "8"),
-                                                  land_sf = world_land)
-
-ggsave(paste0(results_dir, "mean_subsidy_intensity_BC_grid_map.png"), dpi = 200, width = 7, height = 5)
-
-# Weighted Mean
-w_mean_subsidy_intensity_BC_grid_map <- MapMaker(data = subsidy_intensity_binned,
-                                                  res = "grid",
-                                                  x = "lon_bin_center",
-                                                  y = "lat_bin_center",
-                                                  fill = "w_mean_BC_subs_KWh",
-                                                  fill_name = "Subsidy Intensity \n($/KWh)",
-                                                  fill_breaks = seq(0,8, by = 2),
-                                                  fill_limits = c(0,8),
-                                                  fill_labels = c("0", "2", "4", "6", "8"),
-                                                  land_sf = world_land)
-
-ggsave(paste0(results_dir, "w_mean_subsidy_intensity_BC_grid_map.png"), dpi = 200, width = 7, height = 5)
-
-# Combine into three panel
-intensity_BC_grid_legend <- get_legend(w_mean_subsidy_intensity_BC_grid_map)
-
-subsidy_intensity_BC_grid_map <- plot_grid(median_subsidy_intensity_BC_grid_map + theme(legend.position = "none"),
-                                            mean_subsidy_intensity_BC_grid_map + theme(legend.position = "none"),
-                                            w_mean_subsidy_intensity_BC_grid_map + theme(legend.position = "none"),
-                                            intensity_BC_grid_legend,
-                                            ncol = 1,
-                                            rel_heights = c(1,1,1,0.2),
-                                            labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
-                                            label_x = c(-0.04,-0.03,-0.1,0),
-                                            align = "v")
-
-subsidy_intensity_BC_grid_map
-ggsave(paste0(results_dir, "subsidy_intensity_BC_grid_map.png"), dpi = 200, width = 7, height = 12.5)
+subsidy_intensity_BC_grid_l[["all"]]
 
@@
 
-```{r}
-# Median
-median_subsidy_intensity_BC_region_map <- MapMaker(data = subsidy_intensity_region,
+```{r, fig.width=4, fig.height=7}
+# Total subsidies (region)
+subsidy_intensity_BC_region_l <- MapMaker(data = subsidy_intensity_region,
                                          res = "region",
-                                                  fill = "med_BC_subs_KWh",
-                                                  fill_name = "Subsidy Intensity \n($/KWh)",
-                                                  fill_breaks = seq(0,8, by = 2),
-                                                  fill_limits = c(0,8),
-                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                         x = "lon_bin_center",
+                                         y = "lat_bin_center",
+                                         fill = "BC_subs_KWh",
+                                         fill_name = subs_fill_label,
+                                         fill_breaks = BC_subs_fill_breaks,
+                                         fill_limits = BC_subs_fill_limits,
+                                         fill_labels = BC_subs_fill_labels,
                                          land_sf = world_land,
-                                                  region_sf = fao_regions)
+                                         region_sf = fao_regions,
+                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
+                                         file_name = "subsidy_intensity_BC_region_map",
+                                         file_dir = results_dir)
 
-ggsave(paste0(results_dir, "median_subsidy_intensity_BC_region_map.png"), dpi = 200, width = 7, height = 5)
+subsidy_intensity_BC_region_l[["all"]]
+```
 
-# Mean
-mean_subsidy_intensity_BC_region_map <- MapMaker(data = subsidy_intensity_region,
+```{r, fig.width=8, fig.height=7}
+# Combine into six panel
+subsidy_intensity_BC_map <- plot_grid(
+
+  plot_grid(subsidy_intensity_BC_grid_l[["median"]] + theme(legend.position = "none"),
+            subsidy_intensity_BC_region_l[["median"]] + theme(legend.position = "none"),
+            subsidy_intensity_BC_grid_l[["mean"]] + theme(legend.position = "none"),
+            subsidy_intensity_BC_region_l[["mean"]] + theme(legend.position = "none"),
+            subsidy_intensity_BC_grid_l[["w_mean"]] + theme(legend.position = "none"),
+            subsidy_intensity_BC_region_l[["w_mean"]] + theme(legend.position = "none"),
+            ncol = 2,
+            labels = c("A) Median", "", "B) Mean", "", "C) Weighted Mean"),
+            align = "hv"),
+
+  get_legend(subsidy_intensity_BC_region_l[["w_mean"]]),
+  rel_heights = c(2,0.2),
+  ncol = 1)
+
+subsidy_intensity_BC_map
+ggsave(paste0(results_dir, "subsidy_intensity_BC_map.png"), dpi = 200, width = 14, height = 12.5)
+```
+
+## Fuel Subsidies Only
+
+### Subsidy Intensities by Lat/Lon
+
+```{r, fig.width=4, fig.height=7}
+# Scales 
+fuel_subs_fill_breaks <- seq(0,2, by = 0.5)
+fuel_subs_fill_limits <- c(0,2)
+fuel_subs_fill_labels <- c("0", "0.5", "1", "1.5", "\u2265 2")
+
+# Total subsidies (grid)
+subsidy_intensity_fuel_grid_l <- MapMaker(data = subsidy_intensity_binned,
+                                         res = "grid",
+                                         x = "lon_bin_center",
+                                         y = "lat_bin_center",
+                                         fill = "fuel_subs_KWh",
+                                         fill_name = subs_fill_label,
+                                         fill_breaks = fuel_subs_fill_breaks,
+                                         fill_limits = fuel_subs_fill_limits,
+                                         fill_labels = fuel_subs_fill_labels,
+                                         land_sf = world_land,
+                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
+                                         file_name = "subsidy_intensity_fuel_grid_map",
+                                         file_dir = results_dir)
+
+subsidy_intensity_fuel_grid_l[["all"]]
+
+```
+
+### Subsidy Intensities by Region
+
+```{r, fig.width=4, fig.height=7}
+# Total subsidies (region)
+subsidy_intensity_fuel_region_l <- MapMaker(data = subsidy_intensity_region,
                                          res = "region",
-                                                  fill = "mean_BC_subs_KWh",
-                                                  fill_name = "Subsidy Intensity \n($/KWh)",
-                                                  fill_breaks = seq(0,8, by = 2),
-                                                  fill_limits = c(0,8),
-                                                  fill_labels = c("0", "2", "4", "6", "8"),
+                                         x = "lon_bin_center",
+                                         y = "lat_bin_center",
+                                         fill = "fuel_subs_KWh",
+                                         fill_name = subs_fill_label,
+                                         fill_breaks = fuel_subs_fill_breaks,
+                                         fill_limits = fuel_subs_fill_limits,
+                                         fill_labels = fuel_subs_fill_labels,
                                          land_sf = world_land,
-                                                  region_sf = fao_regions)
+                                         region_sf = fao_regions,
+                                         plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
+                                         file_name = "subsidy_intensity_fuel_region_map",
+                                         file_dir = results_dir)
 
-ggsave(paste0(results_dir, "mean_subsidy_intensity_BC_region_map.png"), dpi = 200, width = 7, height = 5)
+subsidy_intensity_fuel_region_l[["all"]]
+```
 
-# Weighted Mean
-w_mean_subsidy_intensity_BC_region_map <- MapMaker(data = subsidy_intensity_region,
-                                                  res = "region",
-                                                  fill = "w_mean_BC_subs_KWh",
-                                                  fill_name = "Subsidy Intensity \n($/KWh)",
-                                                  fill_breaks = seq(0,8, by = 2),
-                                                  fill_limits = c(0,8),
-                                                  fill_labels = c("0", "2", "4", "6", "8"),
-                                                  land_sf = world_land,
-                                                  region_sf = fao_regions)
+```{r, fig.width=8, fig.height=7}
+# Combine into six panel
+subsidy_intensity_fuel_map <- plot_grid(
 
-ggsave(paste0(results_dir, "w_mean_subsidy_intensity_BC_region_map.png"), dpi = 200, width = 7, height = 5)
+  plot_grid(subsidy_intensity_fuel_grid_l[["median"]] + theme(legend.position = "none"),
+            subsidy_intensity_fuel_region_l[["median"]] + theme(legend.position = "none"),
+            subsidy_intensity_fuel_grid_l[["mean"]] + theme(legend.position = "none"),
+            subsidy_intensity_fuel_region_l[["mean"]] + theme(legend.position = "none"),
+            subsidy_intensity_fuel_grid_l[["w_mean"]] + theme(legend.position = "none"),
+            subsidy_intensity_fuel_region_l[["w_mean"]] + theme(legend.position = "none"),
+            ncol = 2,
+            labels = c("A) Median", "", "B) Mean", "", "C) Weighted Mean"),
+            align = "hv"),
 
-# Combine into three panel
-intensity_BC_region_legend <- get_legend(w_mean_subsidy_intensity_BC_region_map)
+  get_legend(subsidy_intensity_fuel_region_l[["w_mean"]]),
+  rel_heights = c(2,0.2),
+  ncol = 1)
 
-subsidy_intensity_BC_region_map <- plot_grid(median_subsidy_intensity_BC_region_map + theme(legend.position = "none"),
-                                            mean_subsidy_intensity_BC_region_map + theme(legend.position = "none"),
-                                            w_mean_subsidy_intensity_BC_region_map + theme(legend.position = "none"),
-                                            intensity_BC_region_legend,
-                                            ncol = 1,
-                                            rel_heights = c(1,1,1,0.2),
-                                            labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
-                                            label_x = c(-0.04,-0.03,-0.1,0),
-                                            align = "v")
-
-subsidy_intensity_BC_region_map
-ggsave(paste0(results_dir, "subsidy_intensity_BC_region_map.png"), dpi = 200, width = 7, height = 12.5)
-
+subsidy_intensity_fuel_map
+ggsave(paste0(results_dir, "subsidy_intensity_fuel_map.png"), dpi = 200, width = 14, height = 12.5)
 ```
@@
   group_by(region_fao_split) %>%
-  summarize(mean_f_v_fmsy = mean(fv_fmsy, na.rm = T),
-            w_mean_f_v_fmsy = weighted.mean(fv_fmsy, w = msy, na.rm = T),
-            med_f_v_fmsy = median(fv_fmsy, na.rm = T),
-            mean_b_v_bmsy = mean(bv_bmsy, na.rm = T),
-            w_mean_b_v_bmsy = weighted.mean(bv_bmsy, w = msy, na.rm = T),
-            med_b_v_bmsy = median(bv_bmsy, na.rm = T),
-            tot_msy = sum(msy, na.rm = T)) %>%
+  summarize_at(vars("fv_fmsy", "bv_bmsy", "msy"), list(median = ~median(., na.rm = T),
+                                                      mean = ~mean(., na.rm = T),
+                                                      w_mean = ~weighted.mean(., w = msy, na.rm = T),
+                                                      tot = ~sum(., na.rm = T))) %>%
+  dplyr::select(-c("fv_fmsy_tot", "bv_bmsy_tot", "msy_median", "msy_mean", "msy_w_mean")) %>%
   rename(fao_region = region_fao_split)
-
 ```
@@
 
-```{r}
-# Median
-median_f_v_fmsy_region_map <- MapMaker(data = upsides_region, 
+```{r, fig.width=4, fig.height=7}
+# Fmsy (region)
+F_Fmsy_region_l <- MapMaker(data = upsides_region,
                             res = "region",
-                                     fill = "med_f_v_fmsy",
+                            fill = "fv_fmsy",
                             fill_name = "F/Fmsy",
-                                     fill_breaks = seq(0,4, by = 1),
-                                     fill_limits = c(0,4),
-                                     fill_labels = c("0", "1", "2", "3", "4"),
+                            fill_breaks = seq(0,3, by = 0.75),
+                            fill_limits = c(0, 3),
+                            fill_labels = c("0", "0.75", "1.5", "2.25", "\u2265 3"),
                             land_sf = world_land,
-                                     region_sf = fao_regions)
+                            region_sf = fao_regions,
+                            plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
+                            file_name = "F_Fmsy_region_map",
+                            file_dir = results_dir)
 
-ggsave(paste0(results_dir, "median_f_v_fmsy_region_map.png"), dpi = 200, width = 7, height = 5)
-
-# Mean
-mean_f_v_fmsy_region_map <- MapMaker(data = upsides_region, 
-                                     res = "region",
-                                     fill = "mean_f_v_fmsy",
-                                     fill_name = "F/Fmsy",
-                                     fill_breaks = seq(0,4, by = 1),
-                                     fill_limits = c(0,4),
-                                     fill_labels = c("0", "1", "2", "3", "4"),
-                                     land_sf = world_land,
-                                     region_sf = fao_regions)
-
-ggsave(paste0(results_dir, "mean_f_v_fmsy_region_map.png"), dpi = 200, width = 7, height = 5)
-
-# Weighted Mean
-w_mean_f_v_fmsy_region_map <- MapMaker(data = upsides_region, 
-                                     res = "region",
-                                     fill = "w_mean_f_v_fmsy",
-                                     fill_name = "F/Fmsy",
-                                     fill_breaks = seq(0,4, by = 1),
-                                     fill_limits = c(0,4),
-                                     fill_labels = c("0", "1", "2", "3", "4"),
-                                     land_sf = world_land,
-                                     region_sf = fao_regions)
-
-ggsave(paste0(results_dir, "w_mean_f_v_fmsy_region_map.png"), dpi = 200, width = 7, height = 5)
-
-# Combine into three panel
-f_v_fmsy_region_legend <- get_legend(w_mean_f_v_fmsy_region_map)
-
-f_v_fmsy_region_map <- plot_grid(median_f_v_fmsy_region_map + theme(legend.position = "none"),
-                                 mean_f_v_fmsy_region_map + theme(legend.position = "none"),
-                                 w_mean_f_v_fmsy_region_map + theme(legend.position = "none"),
-                                 f_v_fmsy_region_legend,
-                                 ncol = 1,
-                                 rel_heights = c(1, 1, 1, 0.2),
-                                 labels = c("A) Median", "B) Mean", "C) Weighted Mean", ""),
-                                 label_x = c(-0.04, -0.03, -0.1, 0),
-                                 align = "v")
-
-f_v_fmsy_region_map
-ggsave(paste0(results_dir, "f_v_fmsy_region_map.png"), dpi = 200, width = 7, height = 12.5)
+F_Fmsy_region_l[["all"]]
 ```
 
-## Coorelation Between Subsidies and Stock status
+### B/Bmsy by Region
+
+```{r, fig.width=4, fig.height=7}
+# B/Bmsy (region)
+B_Bmsy_region_l <- MapMaker(data = upsides_region,
+                            res = "region",
+                            fill = "bv_bmsy",
+                            fill_name = "B/Bmsy",
+                            fill_breaks = seq(0,2, by = 0.5),
+                            fill_limits = c(0, 2),
+                            fill_labels = c("0", "0.5", "1", "1.5", "\u2265 2"),
+                            land_sf = world_land,
+                            region_sf = fao_regions,
+                            plot_labels = c("A) Median", "B) Mean", "C) Weighted Mean"),
+                            file_name = "B_Bmsy_region_map",
+                            file_dir = results_dir)
+
+B_Bmsy_region_l[["all"]]
+```
+
+## Coorelations Between Subsidy Intensity and Stock Status
 
@@
   left_join(subsidy_intensity_region, by = "fao_region")
+```
 
-# Weighted mean of Bad + Ambig vs Weighted mean F/Fmsy
-w_mean_BC_vs_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+```{r}
+# Set some plot scales
+subs_x <- c(0,2.5)
+f_y <- c(0,3)
+effort_fill_lim <- c(0,7.5e9)
+effort_fill_breaks <- seq(0,7.5e9, length.out = 5)
+effort_fill_labels <- format(seq(0,7.5e9, length.out = 5)/1e9, scientific = F, digits = 2)
+
+f_label <- "F/Fmsy"
+b_label <- "B/Bmsy"
+
+effort_label <- "Total Fishing Effort \n(KWh, billions)"
+```
+
+### Weighted Mean Subsidies vs F/Fmsy
+
+#### Total Subsidies
+
+```{r}
+w_mean_tot_subs_vs_F_Fmsy_l <- MapMaker(data = subsidy_intensity_upsides_region,
                                         res = "corr",
-                                       x = "w_mean_BC_subs_KWh",
-                                       x_name = "Weighted Mean Subsidy Intensity ($/KWh)",
-                                       x_limits = c(0,2),
-                                       y = "w_mean_f_v_fmsy",
-                                       y_name = "Weighted Mean F/Fmsy",
-                                       y_limits = c(0,2.5),
-                                       fill = "tot_fishing_KWh",
-                                       fill_name = "Total Fishing Effort \n(KWh, billions)",
-                                       fill_limits = c(0,7.5e9),
-                                       fill_breaks = seq(0,7.5e9, length.out = 5),
-                                       fill_labels = format(seq(0,7.5e9, length.out = 5)/1e9, scientific = F, digits = 2))
+                                        x = "tot_subs_KWh_w_mean",
+                                        x_name = paste0("Weighted Mean Subsidy Intensity ($/KWh)"),
+                                        x_limits = subs_x,
+                                        y = "fv_fmsy",
+                                        y_name = f_label,
+                                        y_limits = f_y,
+                                        fill = "fishing_KWh_lat_lon_sum",
+                                        fill_name = effort_label,
+                                        fill_limits = effort_fill_lim,
+                                        fill_breaks = effort_fill_breaks,
+                                        fill_labels = effort_fill_labels,
+                                        file_name = "w_mean_tot_subs_vs_F_Fmsy_plot",
+                                        file_dir = results_dir)
 
-ggsave(paste0(results_dir, "w_mean_BC_vs_f_v_fmsy_plot.png"), dpi = 200, width = 7, height = 7)
+w_mean_tot_subs_vs_F_Fmsy_l[["all"]]
+```
 
-# mean of Bad + Ambig vs mean F/Fmsy
-w_mean_BC_vs_median_f_v_fmsy_plot <- MapMaker(data = subsidy_intensity_upsides_region,
+#### Bad Subsidies Only
+
+```{r}
+w_mean_B_subs_vs_F_Fmsy_l <- MapMaker(data = subsidy_intensity_upsides_region,
                                         res = "corr",
-                                       x = "w_mean_BC_subs_KWh",
-                                       x_name = "Weighted Mean Subsidy Intensity ($/KWh)",
-                                       x_limits = c(0,4),
-                                       y = "med_f_v_fmsy",
-                                       y_name = "Median F/Fmsy",
-                                       y_limits = c(0,4),
-                                       fill = "tot_fishing_KWh",
-                                       fill_name = "Total Fishing Effort \n(KWh, billions)",
-                                       fill_limits = c(0,7.5e9),
-                                       fill_breaks = seq(0,7.5e9, length.out = 5),
-                                       fill_labels = format(seq(0,7.5e9, length.out = 5)/1e9, scientific = F, digits = 2))
+                                        x = "B_subs_KWh_w_mean",
+                                        x_name = paste0("Weighted Mean Subsidy Intensity ($/KWh)"),
+                                        x_limits = subs_x,
+                                        y = "fv_fmsy",
+                                        y_name = f_label,
+                                        y_limits = f_y,
+                                        fill = "fishing_KWh_lat_lon_sum",
+                                        fill_name = effort_label,
+                                        fill_limits = effort_fill_lim,
+                                        fill_breaks = effort_fill_breaks,
+                                        fill_labels = effort_fill_labels,
+                                        file_name = "w_mean_B_subs_vs_F_Fmsy_plot",
+                                        file_dir = results_dir)
 
-ggsave(paste0(results_dir, "w_mean_BC_vs_median_f_v_fmsy_plot.png"), dpi = 200, width = 7, height = 7)
+w_mean_B_subs_vs_F_Fmsy_l[["all"]]
+```
 
+#### Bad and Ambiguous Subsidies Only
+
+```{r}
+w_mean_BC_subs_vs_F_Fmsy_l <- MapMaker(data = subsidy_intensity_upsides_region,
+                                        res = "corr",
+                                        x = "BC_subs_KWh_w_mean",
+                                        x_name = paste0("Weighted Mean Subsidy Intensity ($/KWh)"),
+                                        x_limits = subs_x,
+                                        y = "fv_fmsy",
+                                        y_name = f_label,
+                                        y_limits = f_y,
+                                        fill = "fishing_KWh_lat_lon_sum",
+                                        fill_name = effort_label,
+                                        fill_limits = effort_fill_lim,
+                                        fill_breaks = effort_fill_breaks,
+                                        fill_labels = effort_fill_labels,
+                                        file_name = "w_mean_BC_subs_vs_F_Fmsy_plot",
+                                        file_dir = results_dir)
+
+w_mean_BC_subs_vs_F_Fmsy_l[["all"]]
+```
+
+#### Fuel Subsidies Only
+
+```{r}
+w_mean_fuel_subs_vs_F_Fmsy_l <- MapMaker(data = subsidy_intensity_upsides_region,
+                                        res = "corr",
+                                        x = "fuel_subs_KWh_w_mean",
+                                        x_name = paste0("Weighted Mean Subsidy Intensity ($/KWh)"),
+                                        x_limits = subs_x,
+                                        y = "fv_fmsy",
+                                        y_name = f_label,
+                                        y_limits = f_y,
+                                        fill = "fishing_KWh_lat_lon_sum",
+                                        fill_name = effort_label,
+                                        fill_limits = effort_fill_lim,
+                                        fill_breaks = effort_fill_breaks,
+                                        fill_labels = effort_fill_labels,
+                                        file_name = "w_mean_fuel_subs_vs_F_Fmsy_plot",
+                                        file_dir = results_dir)
+
+w_mean_fuel_subs_vs_F_Fmsy_l[["all"]]
+```
+
+### Mean Subsidies vs F/Fmsy
+
+#### Total Subsidies
+
+```{r}
+mean_tot_subs_vs_F_Fmsy_l <- MapMaker(data = subsidy_intensity_upsides_region,
+                                        res = "corr",
+                                        x = "tot_subs_KWh_mean",
+                                        x_name = paste0("Mean Subsidy Intensity ($/KWh)"),
+                                        x_limits = subs_x,
+                                        y = "fv_fmsy",
+                                        y_name = f_label,
+                                        y_limits = f_y,
+                                        fill = "fishing_KWh_lat_lon_sum",
+                                        fill_name = effort_label,
+                                        fill_limits = effort_fill_lim,
+                                        fill_breaks = effort_fill_breaks,
+                                        fill_labels = effort_fill_labels,
+                                        file_name = "mean_tot_subs_vs_F_Fmsy_plot",
+                                        file_dir = results_dir)
+
+mean_tot_subs_vs_F_Fmsy_l[["all"]]
+```
+
+#### Bad Subsidies Only
+
+```{r}
+mean_B_subs_vs_F_Fmsy_l <- MapMaker(data = subsidy_intensity_upsides_region,
+                                        res = "corr",
+                                        x = "B_subs_KWh_mean",
+                                        x_name = paste0("Mean Subsidy Intensity ($/KWh)"),
+                                        x_limits = subs_x,
+                                        y = "fv_fmsy",
+                                        y_name = f_label,
+                                        y_limits = f_y,
+                                        fill = "fishing_KWh_lat_lon_sum",
+                                        fill_name = effort_label,
+                                        fill_limits = effort_fill_lim,
+                                        fill_breaks = effort_fill_breaks,
+                                        fill_labels = effort_fill_labels,
+                                        file_name = "mean_B_subs_vs_F_Fmsy_plot",
+                                        file_dir = results_dir)
+
+mean_B_subs_vs_F_Fmsy_l[["all"]]
+```
+
+#### Bad and Ambiguous Subsidies Only
+
+```{r}
+mean_BC_subs_vs_F_Fmsy_l <- MapMaker(data = subsidy_intensity_upsides_region,
+                                        res = "corr",
+                                        x = "BC_subs_KWh_mean",
+                                        x_name = paste0("Mean Subsidy Intensity ($/KWh)"),
+                                        x_limits = subs_x,
+                                        y = "fv_fmsy",
+                                        y_name = f_label,
+                                        y_limits = f_y,
+                                        fill = "fishing_KWh_lat_lon_sum",
+                                        fill_name = effort_label,
+                                        fill_limits = effort_fill_lim,
+                                        fill_breaks = effort_fill_breaks,
+                                        fill_labels = effort_fill_labels,
+                                        file_name = "mean_BC_subs_vs_F_Fmsy_plot",
+                                        file_dir = results_dir)
+
+mean_BC_subs_vs_F_Fmsy_l[["all"]]
+```
+
+#### Fuel Subsidies Only
+
+```{r}
+mean_fuel_subs_vs_F_Fmsy_l <- MapMaker(data = subsidy_intensity_upsides_region,
+                                        res = "corr",
+                                        x = "fuel_subs_KWh_mean",
+                                        x_name = paste0("Mean Subsidy Intensity ($/KWh)"),
+                                        x_limits = subs_x,
+                                        y = "fv_fmsy",
+                                        y_name = f_label,
+                                        y_limits = f_y,
+                                        fill = "fishing_KWh_lat_lon_sum",
+                                        fill_name = effort_label,
+                                        fill_limits = effort_fill_lim,
+                                        fill_breaks = effort_fill_breaks,
+                                        fill_labels = effort_fill_labels,
+                                        file_name = "mean_fuel_subs_vs_F_Fmsy_plot",
+                                        file_dir = results_dir)
+
+mean_fuel_subs_vs_F_Fmsy_l[["all"]]
+```
+
+### Median Subsidies vs F/Fmsy
+
+#### Total Subsidies
+
+```{r}
+median_tot_subs_vs_F_Fmsy_l <- MapMaker(data = subsidy_intensity_upsides_region,
+                                        res = "corr",
+                                        x = "tot_subs_KWh_median",
+                                        x_name = paste0("Median Subsidy Intensity ($/KWh)"),
+                                        x_limits = subs_x,
+                                        y = "fv_fmsy",
+                                        y_name = f_label,
+                                        y_limits = f_y,
+                                        fill = "fishing_KWh_lat_lon_sum",
+                                        fill_name = effort_label,
+                                        fill_limits = effort_fill_lim,
+                                        fill_breaks = effort_fill_breaks,
+                                        fill_labels = effort_fill_labels,
+                                        file_name = "median_tot_subs_vs_F_Fmsy_plot",
+                                        file_dir = results_dir)
+
+median_tot_subs_vs_F_Fmsy_l[["all"]]
+```
+
+#### Bad Subsidies Only
+
+```{r}
+median_B_subs_vs_F_Fmsy_l <- MapMaker(data = subsidy_intensity_upsides_region,
+                                        res = "corr",
+                                        x = "B_subs_KWh_median",
+                                        x_name = paste0("Median Subsidy Intensity ($/KWh)"),
+                                        x_limits = subs_x,
+                                        y = "fv_fmsy",
+                                        y_name = f_label,
+                                        y_limits = f_y,
+                                        fill = "fishing_KWh_lat_lon_sum",
+                                        fill_name = effort_label,
+                                        fill_limits = effort_fill_lim,
+                                        fill_breaks = effort_fill_breaks,
+                                        fill_labels = effort_fill_labels,
+                                        file_name = "median_B_subs_vs_F_Fmsy_plot",
+                                        file_dir = results_dir)
+
+median_B_subs_vs_F_Fmsy_l[["all"]]
+```
+
+#### Bad and Ambiguous Subsidies Only
+
+```{r}
+median_BC_subs_vs_F_Fmsy_l <- MapMaker(data = subsidy_intensity_upsides_region,
+                                        res = "corr",
+                                        x = "BC_subs_KWh_median",
+                                        x_name = paste0("Median Subsidy Intensity ($/KWh)"),
+                                        x_limits = subs_x,
+                                        y = "fv_fmsy",
+                                        y_name = f_label,
+                                        y_limits = f_y,
+                                        fill = "fishing_KWh_lat_lon_sum",
+                                        fill_name = effort_label,
+                                        fill_limits = effort_fill_lim,
+                                        fill_breaks = effort_fill_breaks,
+                                        fill_labels = effort_fill_labels,
+                                        file_name = "median_BC_subs_vs_F_Fmsy_plot",
+                                        file_dir = results_dir)
+
+median_BC_subs_vs_F_Fmsy_l[["all"]]
+```
+
+#### Fuel Subsidies Only
+
+```{r}
+median_fuel_subs_vs_F_Fmsy_l <- MapMaker(data = subsidy_intensity_upsides_region,
+                                        res = "corr",
+                                        x = "fuel_subs_KWh_median",
+                                        x_name = paste0("Median Subsidy Intensity ($/KWh)"),
+                                        x_limits = subs_x,
+                                        y = "fv_fmsy",
+                                        y_name = f_label,
+                                        y_limits = f_y,
+                                        fill = "fishing_KWh_lat_lon_sum",
+                                        fill_name = effort_label,
+                                        fill_limits = effort_fill_lim,
+                                        fill_breaks = effort_fill_breaks,
+                                        fill_labels = effort_fill_labels,
+                                        file_name = "median_fuel_subs_vs_F_Fmsy_plot",
+                                        file_dir = results_dir)
+
+median_fuel_subs_vs_F_Fmsy_l[["all"]]
 ```
@@
 ```{r}
-top_legend <- get_legend(w_mean_subsidy_intensity_BC_region_map)
+top_row <- #plot_grid(
 
-top_row <- plot_grid(
-  plot_grid(w_mean_subsidy_intensity_BC_grid_map + theme(legend.position = "none"),
-                     w_mean_subsidy_intensity_BC_region_map + theme(legend.position = "none"),
+  #get_legend(subsidy_intensity_BC_grid_l[["w_mean"]]),
+
+  plot_grid(subsidy_intensity_BC_region_l[["w_mean"]],
+            F_Fmsy_region_l[["median"]],
             nrow = 1,
             label_x = 0,
-                     labels = c("A) Subsidy Itensity (1x1 degree)",
-                                "B) Subsidy Intensity (FAO Region)")),
-  ncol = 1,
-  top_legend,
-  rel_heights = c(1,0.2))
+            labels = c("A)", "B)"))
 
-bottom_row <-  plot_grid(median_f_v_fmsy_region_map,
-                     w_mean_BC_vs_median_f_v_fmsy_plot,
-                     nrow = 1,
-                     label_x = 0,
-                     labels = c("C) F/Fmsy (FAO Region)",
-                                "D) Coorelation"))
+  # ncol = 1,
+  # rel_heights = c(0.1, 1)
+
+#)
 
 Figure1 <- plot_grid(top_row,
-                     bottom_row,
-                     nrow = 2)
+                     w_mean_BC_subs_vs_F_Fmsy_l[["median"]],
+                     nrow = 2,
+                     labels = c("", "C)"),
+                     label_y = 1.05)
 

### 2020-03-24 functions/MapMaker.R

@@ -8,13 +8,17 @@ MapMaker <- function(data,
                      y_limits = NULL,
                      y_name = NULL,
                      fill,
+                     fill_var,
                      fill_name,
                      fill_breaks,
                      fill_limits,
                      fill_labels,
                      land_sf = NULL,
                      region_sf = NULL,
-                     eez_sf = NULL){
+                     eez_sf = NULL,
+                     file_name = "map",
+                     file_dir = here::here("results/"),
+                     plot_labels = NULL){
   
   ### Themes
   dark_theme <- theme(panel.background = element_rect(fill = "black"),
@@ -49,12 +53,12 @@ MapMaker <- function(data,
   
   if(res == "grid"){
     
-    out <- data %>%
+    median <- data %>%
       ggplot()+
-      geom_tile(aes(x = get(x), y = get(y), fill = get(fill))) +
+      geom_tile(aes(x = get(x), y = get(y), fill = get(paste0(fill, "_median")))) +
       land + 
       scale_fill_distiller(type = "seq", palette = "RdYlBu",
-                           name = fill_name,
+                           name = paste0(fill_name),
                            na.value = "#000000", 
                            limits = fill_limits,
                            breaks = fill_breaks,
@@ -73,14 +77,80 @@ MapMaker <- function(data,
         barheight=0.25,
         default.unit="inch"))
     
-    return(out)
+    mean <- data %>%
+      ggplot()+
+      geom_tile(aes(x = get(x), y = get(y), fill = get(paste0(fill, "_mean")))) +
+      land + 
+      scale_fill_distiller(type = "seq", palette = "RdYlBu",
+                           name = paste0(fill_name),
+                           na.value = "#000000", 
+                           limits = fill_limits,
+                           breaks = fill_breaks,
+                           labels = fill_labels,
+                           oob = scales::squish)+
+      scale_x_continuous(expand = c(0,0))+
+      scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
+      xlab("") +
+      ylab("") +
+      dark_theme + 
+      guides(fill=guide_colorbar(
+        title.position = "left",
+        title.hjust = 0.5,
+        frame.colour = "black",
+        barwidth=4,
+        barheight=0.25,
+        default.unit="inch"))
+    
+    w_mean <- data %>%
+      ggplot()+
[…]

### 2020-03-24 scripts/01_data_wrangling.Rmd
compare figure back up - missing landings/landed value

--- 2020-03-20 scripts/01_data_wrangling.Rmd
@@
 ```
+
+# Section 5 - Relative Metrics
+
+This second is a bit of a relic from when we were doing "country profiles", but there are a couple of relative metrics we want to calculate from our data sources. This is done here.
+
+```{r}
+# Sumaila dat for matching
+subs_dat_match <- sumaila_2019_dat_edit %>%
+  dplyr::select(-units, -variable) %>%
+  rename(subs = value, subs_year = year, subs_source = source)
+
+# GDP
+gdp_dat_mry <- wb_dat_edit %>%
+  dplyr::filter(variable == "gdp") %>%
+  group_by(iso3, variable) %>%
+  dplyr::filter(year == max(year[!is.na(value)])) %>%
+  ungroup() %>%
+  dplyr::select(iso3, gdp_year = year, gdp = value, gdp_source = source) %>%
+  right_join(subs_dat_match, by = c("iso3")) %>%
+  mutate(variable = "subsidies_per_gdp",
+         data_type = paste0(data_type),
+         source = paste0(subs_source, "; ", gdp_source),
+         value = subs/gdp,
+         units = paste0(subs_year, " US$/", gdp_year, " US$")) %>%
+  dplyr::select(iso3, category, category_name, type, type_name, variable, value, units, data_type, source) %>%
+  dplyr::filter(!is.na(value))
+
+# Population
+pop_dat_mry <- wb_dat_edit %>%
+  dplyr::filter(variable == "population") %>%
+  group_by(iso3, variable) %>%
+  dplyr::filter(year == max(year[!is.na(value)])) %>%
+  ungroup() %>%
+  dplyr::select(iso3, population_year = year, population = value, population_source = source) %>%
+  right_join(subs_dat_match, by = c("iso3")) %>%
+  mutate(variable = "subsidies_per_capita",
+         data_type = paste0(data_type),
+         source = paste0(subs_source, "; ", population_source),
+         value = subs/population,
+         units = paste0(subs_year, " US$/person (", population_year, ")")) %>%
+  dplyr::select(iso3, category, category_name, type, type_name, variable, value, units, data_type, source) %>%
+  dplyr::filter(!is.na(value))
+
+# Fishers
+fisher_dat_mry <- fao_fishers_dat_edit %>%
+  group_by(iso3, variable) %>%
+  dplyr::filter(year == max(year[!is.na(value)])) %>%
+  ungroup() %>%
+  dplyr::select(iso3, fishers_year = year, fishers = value, fishers_source = source) %>%
+  right_join(subs_dat_match, by = c("iso3")) %>%
+  mutate(variable = "subsidies_per_fisher",
+         data_type = paste0(data_type),
+         source = paste0(subs_source, "; ", fishers_source),
+         value = subs/fishers,
+         units = paste0(subs_year, " US$/fisher (", fishers_year, ")")) %>%
+  dplyr::select(iso3, category, category_name, type, type_name, variable, value, units, data_type, source) %>%
+  dplyr::filter(!is.na(value))
+
+# FTE
+fte_dat_mry <- teh_fte_dat_edit %>%
+  dplyr::select(iso3, fte_year = year, fte = value, fte_source = source) %>%
+  right_join(subs_dat_match, by = c("iso3")) %>%
+  mutate(variable = "subsidies_per_fte",
+         data_type = paste0(data_type),
+         source = paste0(subs_source, "; ", fte_source),
+         value = subs/fte,
+         units = paste0(subs_year, " US$/full-time-equivalent (", fte_year, ")")) %>%
+  dplyr::select(iso3, category, category_name, type, type_name, variable, value, units, data_type, source) %>%
+  dplyr::filter(!is.na(value))
+
+# Capture Production
+production_dat_mry <- fao_production_dat_edit_groups %>%
+  group_by(iso3, year, variable) %>%
+  summarize(value = sum(value, na.rm = T),
+            source = unique(source)) %>%
+  group_by(iso3, variable) %>%
+  dplyr::filter(year == max(year[!is.na(value)])) %>%
+  ungroup() %>%
+  dplyr::select(iso3, production_year = year, production = value, production_source = source) %>%
+  right_join(subs_dat_match, by = c("iso3")) %>%
+  mutate(variable = "subsidies_per_production",
+         data_type = paste0(data_type),
+         source = paste0(subs_source, "; ", production_source),
+         value = subs/production,
+         units = paste0(subs_year, " US$/tonne (", production_year, ")")) %>%
+  dplyr::select(iso3, category, category_name, type, type_name, variable, value, units, data_type, source) %>%
+  dplyr::filter(!is.na(value))
+
+# Landed Value
+landed_value_dat_mry <- landed_value_dat %>%
+  group_by(iso3, year, variable) %>%
+  summarize(value = sum(value, na.rm = T),
+            source = unique(source)) %>%
+  group_by(iso3, variable) %>%
+  dplyr::filter(year == max(year[!is.na(value)])) %>%
+  ungroup() %>%
+  dplyr::select(iso3, landed_value_year = year, landed_value = value, landed_value_source = source) %>%
+  right_join(subs_dat_match, by = c("iso3")) %>%
+  mutate(variable = "subsidies_per_landed_value",
+         data_type = paste0(data_type),
+         source = paste0(subs_source, "; ", landed_value_source),
+         value = subs/landed_value,
+         units = paste0(subs_year, " US$/", landed_value_year, " US$")) %>%
+  dplyr::select(iso3, category, category_name, type, type_name, variable, value, units, data_type, source) %>%
+  dplyr::filter(!is.na(value))
+
+# Combine with subsidy data and calculate relative metrics
+relative_dat <-  gdp_dat_mry %>%
+  bind_rows(pop_dat_mry) %>%
+  bind_rows(fisher_dat_mry) %>%
+  bind_rows(fte_dat_mry) %>%
+  bind_rows(production_dat_mry) %>%
+  bind_rows(landed_value_dat_mry)
+
+write_csv(relative_dat, paste0(data_dir, "relative_subsidy_metrics_tidy.csv"))
+write_csv(relative_dat, paste0(app_data_dir, "relative_subsidy_metrics_tidy.csv"))
+```

### 2020-03-24 app/00_initialize_app.R

@@ -148,14 +148,17 @@ names(categoryColors) <- names(subsidy_categories_sorted_sumaila)
 
 # 1) GDP and Population (World Bank WDI database 2020) ---
 demo_dat_world_bank <- read_csv("./data/world_bank_2020_wdi_tidy.csv") %>%
+  left_join(country_lookup %>% dplyr::select(iso3, display_name), by = "iso3") %>%
   arrange(iso3)
 
 # 2) Number of fishers (FAO Yearbook 2017) ---
 fisher_dat_fao <- read_csv("./data/fao_2017_yearbook_fishers_tidy.csv") %>%
+  left_join(country_lookup %>% dplyr::select(iso3, display_name), by = "iso3") %>%
   arrange(iso3)
 
 # 3) Full-time fisheries employment (Teh and Sumaila 2013) ---
 fisher_dat_teh_and_sumaila <- read_csv("./data/teh_and_sumaila_2013_fte_tidy.csv") %>%
+  left_join(country_lookup %>% dplyr::select(iso3, display_name), by = "iso3") %>%
   arrange(iso3)
 
 # Aggregate
@@ -170,23 +173,24 @@ demographic_dat <- demo_dat_world_bank %>%
 capture_production_dat_fao <- read_csv("./data/fao_2019_capture_production_isscaap_groups_tidy.csv") %>%
   group_by(iso3, year) %>%
   mutate(prop_annual_total = value/sum(value)) %>%
-  ungroup()
+  ungroup() %>%
+  left_join(country_lookup %>% dplyr::select(iso3, display_name), by = "iso3")
 
 capture_production_dat_tot <- capture_production_dat_fao %>%
-  group_by(iso3, year, variable, units, source) %>%
-  summarize(value = sum(value, na.rm = T))
+  group_by(iso3, year, variable, units, source, display_name) %>%
+  summarize(value = sum(value, na.rm = T)) 
 
 # 2) Landed value by ISSCAAP Group (2000-2017)
 landed_value_dat <- read_csv("./data/estimated_landed_value_isscaap_groups_tidy.csv") %>%
   group_by(iso3, year) %>%
   mutate(prop_annual_total = value/sum(value)) %>%
-  ungroup()
+  ungroup() %>%
+  left_join(country_lookup %>% dplyr::select(iso3, display_name), by = "iso3")
 
 landed_value_dat_tot <- landed_value_dat %>%
-  group_by(iso3, year, variable, units, source) %>%
+  group_by(iso3, year, variable, units, source, display_name) %>%
[…]

### 2020-03-24 app/server.R

@@ -715,77 +715,77 @@ shinyServer(function(input, output, session) {
     req(input$w_compare_fishery_stats_selected_country)
     req(input$w_compare_fishery_stats_plot_variable)
     req(input$w_compare_fishery_stats_method)
-    req(input$w_compare_fishery_stats_select_manual)
     req(input$w_compare_fishery_stats_subsidy_types)
     
     # Plot arguments: 1 = variable name, 2 = hover/x-axis caption, 3 = rounding digits, 4 = units prefix.
     compare_fishery_stats_bar_plot_args <- switch(
       input$w_compare_fishery_stats_plot_variable,
       "subsidies" = list("subsidies_Sumaila", "Est. fisheries subsidies (2018 US$)", 0, "$"),
-      "landings" = list("landings", "Capture production (mt, 2017)", 0, ""),
-      "revenue" = list("revenue", "Est. landed value (2017 US$)", 0, "$"),
-      "subsidies_per_landing" = list("subsidies_per_landing", "Fisheries subsidies per volume landed (2018 US$/mt)", 2, "$"),
-      "subsidies_per_revenue" = list("subsidies_per_revenue", "Ratio of fisheries subsidies to landed value", 2, ""), 
+      "landings" = list("capture_production", "Capture production (mt, 2017)", 0, ""),
+      "revenue" = list("landed_value", "Est. landed value (2017 US$)", 0, "$"),
+      "subsidies_per_landing" = list("subsidies_per_production", "Fisheries subsidies per tonne of capture production (2018 US$/tonne)", 2, "$"),
+      "subsidies_per_revenue" = list("subsidies_per_landed_value", "Ratio of fisheries subsidies to landed value", 2, ""), 
       "subsidies_per_capita" = list("subsidies_per_capita", "Fisheries subsidies per capita (2018 US$/person)", 2, "$"),
       "subsidies_per_gdp" = list("subsidies_per_gdp", "Ratio of fisheries subsidies to GDP", 4, ""),
-      "subsidies_per_fte" = list("subsidies_per_fte", "Fisheries subsidies per number of FTE persons employed in fisheries (2018 US$/person)", 2, "$"))
+      "subsidies_per_fte" = list("subsidies_per_fte", "Fisheries subsidies per full-time-equivalent fisheries jobs (2018 US$/FTE)", 2, "$"))
     
     # Filter data by selected variable and by selected subsidy type(s) [if applicable]
[…]

### 2020-03-26 scripts/02_vessel_list.Rmd
more vessel list work

@@
 
-# Introduction
-
-This script creates the global vessel list used in the SubsidyExplorer toolkit.
-It requires access to the raw Global Fishing Watch (GFW) data stored on BigQuery (not-publically available), as well as a valid Google Cloud Console billing account.
-It outputs a single data file to `r here::here("results", "02-vessel-list")`:
-
-- vessel_list_2018_raw.csv
-
-It also creates a 1x1 degree version for use in making higher resolution figures. This is output to
-
 ```{r}
@@
 
-# Path to cleaned landings data file
-#catch_dat_path <- here::here("data", "edited", "fisheries-area-2000-2017-tidy.csv")
+# Path to cleaned capture production data file
+catch_dat_path <- here::here("data", "edited", "fao_2019_capture_production_tidy.csv")
+
+# Path to cleaned landed value data file
+landed_value_dat_path <- here::here("data", "edited", "estimated_landed_value_isscaap_groups_tidy.csv")
 
@@
 
-```
-
-```{r}
 # Code options
@@
 }
+```
 
-```
+# Introduction
+
+This script creates the global vessel list used in the SubsidyExplorer toolkit.
+It requires access to the raw Global Fishing Watch (GFW) data stored on BigQuery (not-publically available), as well as a valid Google Cloud Console billing account.
+It creates and outputs the raw 2018 global vessel list (`r paste0(results_dir, "vessel_list_2018_raw.csv")`) with effort by vessel aggregated to the EEZ and/or FAO statistical region.
+
+It also creates a 1x1 degree version for use in making higher resolution figures (`r paste0(results_dir, "vessel_list_2018_1x1_binned.csv")`)
 
@@
 
-We first extract the number of hours spent fishing by each of our good fishing vessels in each 5x5 degree latitude/longitude bin from the raw fishing effort table (`world-fishing-827.gfw_research.pipe_v20190502_fishing`).
+We first extract the number of hours spent fishing by each of our good fishing vessels in each 1x1 degree latitude/longitude bin from the raw fishing effort table (`world-fishing-827.gfw_research.pipe_v20190502_fishing`).
 
@@
 - fao_region (int): Major FAO statistical region
-- fishing_hours_lat_lon: Total annual fishing hours in the specified lat/lon bin by a single vessel
 - ssvid (chr): Unique vessel identification number given by GFW (MMSI number for most vessels)
@@
 - engine_power_kw (int): Best engine power of the vessel
+- fishing_hours_lat_lon: Total annual fishing hours in the specified lat/lon bin by the vessel
+- fishing_KWh_lat_lon: Total annual fishing KWh in the specified lat/lon bin by the vessel
 
@@
 binned_effort_table <- bq_table(project = bq_project, 
-                                table = "effort_5deg_good_fishing_vessels_2018_raw",
+                                table = "effort_1x1_good_fishing_vessels_2018_raw",
                                 dataset = "SubsidyExplorer")
@@
   bq_table_delete(binned_effort_table)
-  effort_binned_good_fishing_vessels_2018 <- 
+  effort_1x1_good_fishing_vessels_2018 <- 
     bq_project_query(bq_project, 
@@
   bq_table_create(binned_effort_table)
-  effort_binned_good_fishing_vessels_2018 <- 
+  effort_1x1_good_fishing_vessels_2018 <- 
     bq_project_query(bq_project, 
@@
 # Save
-write_csv(effort_binned_good_fishing_vessels_2018, paste0(results_dir, "effort_binned_good_fishing_vessels_2018_raw.csv"))
+write_csv(effort_1x1_good_fishing_vessels_2018, paste0(results_dir, "effort_1x1_good_fishing_vessels_2018_raw.csv"))
 ```
@@
 - fao_region (int): Major FAO statistical region
-- fishing_hours_eez_fao: Total annual fishing hours in the specified eez and/or fao region by a single vessel
 - ssvid (chr): Unique vessel identification number given by GFW (MMSI number for most vessels)
@@
 - territory1_iso3 (chr) : Three letter code cooresponding to the administering territory of the EEZ
-- territory2_iso3 (chr) : Three letter code cooresponding to the second administering territory of the EEZ (disputed areas only)
-- territory3_iso3 (chr) : Three letter code cooresponding to the third administering territory of the EEZ (disputed areas only)
+- territory2_iso3 (chr) : Three letter code cooresponding to the second administering territory of the EEZ (disputed and/or joint regime areas only)
+- territory3_iso3 (chr) : Three letter code cooresponding to the third administering territory of the EEZ (disputed and/or joint regime areas only)
 - sovereign1_iso3 (chr) : Three letter code cooresponding to the sovereign state of the EEZ
-- sovereign2_iso3 (chr) : Three letter code cooresponding to the second sovereign state of the EEZ (disputed areas only)
-- sovereign3_iso3 (chr) : Three letter code cooresponding to the third sovereign state of the EEZ (disputed areas only)
+- sovereign2_iso3 (chr) : Three letter code cooresponding to the second sovereign state of the EEZ (disputed and/or joint regime areas only)
+- sovereign3_iso3 (chr) : Three letter code cooresponding to the third sovereign state of the EEZ (disputed and/or joint regime areas only)
+- fishing_hours_eez_fao: Total annual fishing hours in the specified eez and/or FAO statistical region by the vessel
+- fishing_KWh_eez_fao: Total annual fishing KWh hours in the specified eez and/or FAO statistical region by the vessel
 
@@
   FROM
-    `ucsb-gfw.SubsidyExplorer.all_good_fishing_vessels`),
+    `emlab-gcp.SubsidyExplorer.all_good_fishing_vessels`),
 
@@
   *,
-  fishing_hours_eez_fao*engine_power_kw as fishing_KWh_eez_fao
+  CASE
+    WHEN engine_power_kw IS NULL THEN fishing_hours_eez_fao*400
+    ELSE fishing_hours_eez_fao*engine_power_kw
+  END AS fishing_KWh_eez_fao
 FROM
@@
 effort_table <- bq_table(project = bq_project, 
-                     table = "effort_good_fishing_vessels_2018_raw",
+                     table = "effort_eez_fao_good_fishing_vessels_2018_raw",
                      dataset = "SubsidyExplorer")
@@
     bq_project_query(bq_project, 
-                    sql3, 
+                    query = sql3, 
                     destination_table = effort_table, 
@@
   effort_good_fishing_vessels_2018 <- 
-    bq_project_query("world-fishing-827", 
+    bq_project_query(bq_project, 
                    query = sql3, 
@@
 # Save
-write_csv(effort_good_fishing_vessels_2018, paste0(results_dir, "effort_good_fishing_vessels_2018_raw.csv"))
+write_csv(effort_good_fishing_vessels_2018, paste0(results_dir, "effort_eez_fao_good_fishing_vessels_2018_raw.csv"))
 ```
@@
 ```{r}
+# Load country dependencies helper file
+country_dependencies <- read_csv(here::here("data", "lookup-tables", "country_dependencies.csv"))
+
 # EU countries
-#Belgium, Bulgaria, Croatia, Cyprus, Denmark, Estonia, Finland, France, Germany, Greece, Ireland, Italy, Latvia, Lithuania, Malta, Netherlands, Poland, Portugal, Romania, Slovenia, Spain, Sweden, United Kingdom
-eu_countries <- c("BEL", "BGR", "HRV", "CYP", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "IRL", "ITA", "LVA", "LTU", "MLT", "NLD", "POL", "PRT", "ROU", "SVN", "ESP", "SWE", "GBR")
+eu_countries <- country_dependencies$iso3[country_dependencies$is_EU]
 
-# EU overseas territories: 
-# Dutch overseas territories: Aruba, Bonaire/St. Eustatius/Saba, Curacao, Sint Maarten
-dutch_territories <- c("ABW", "BES", "CUW", "SXM")
+# Dutch overseas territories 
+dutch_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "NLD"]
 
-# French overseas territories: French Guiana, French Polynesia, French Southern and Antarctic Territories, Guadeloupe, Martinique, Mayotte, New Caledonia, Reunion, Saint Barthelemy, Saint Martin, St.
-Pierre and Miquelon, Wallis and Futuna Islands
-french_territories <- c("GUF", "PYF", "ATF", "GLP", "MTQ", "MYT", "NCL", "REU", "BLM", "MAF", "SPM", "WLF")
+# French overseas territories 
+french_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "FRA"]
 
-# Danish overseas territories: Faroe Islands, Greenland
-danish_territories <- c("FRO", "GRL")
+# Danish overseas territories
+danish_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "DNK"]
 
-# British overseas territories: Anguilla, Ascension island, Bermuda, Cayman Islands, Falkland Islands, Guernsey, Gibraltar, British Indian Ocean Territories, Jersey, Monserratt, Pitcairn Island, South Georgia and the South Sandwich Islands, Saint Helena/Ascension/Tristan da Cunha, Tristan da Cunha, Turks and Caicos Islands, British Virgin Islands
-uk_territories <- c("AIA","ASC","BMU","CYM","FLK","GGY","GIB","IOT","JEY","MSR","PCN","SGS","SHN","TAA","TCA","VGB")
+# UK overseas territories
+uk_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "GBR"]
 
-# Combine
-eu_territories <- c(dutch_territories, french_territories, danish_territories, uk_territories)
-
-# Norwegian overseas territories: Bouvet Islands, Svalbard and Jan Mayen Islands
-norwegian_territories <- c("BVT", "SJM")
+# EU overseas territories
+eu_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 %in% eu_countries]
 
 # US overseas territories:  American Samoa, Guam, Northern Marianas Islands, Puerto Rico, US Virgin Islands
-us_territories <- c("ASM", "GUM", "MNP", "PRI", "VIR")
+us_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "USA"]
+
+# Norwegian overseas territories: 
+norwegian_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "NOR"]
 ```
@@
 ```{r}
-# Load catch and revenue data
+# Load catch data
 catch_flag_fao <- read_csv(catch_dat_path) %>%
@@
   dplyr::filter(!(iso3 %in% c("EU", "USA-T", "UNK"))) %>%
-  group_by(iso3, area, variable) %>%
+  group_by(iso3, fishing_area, variable) %>% 
   summarize(value = sum(value, na.rm = T)) %>%
   ungroup() %>%
-  spread(variable, value) %>%
-  dplyr::filter(landings > 0)
+  spread(variable, value)
 

### 2020-03-26 papers/paper-1/paper_1_figures.Rmd
and paper figures again

@@
 # Path to binned effort data file
-effort_dat_binned_path <- here::here("results", "02-vessel-list", "effort_binned_good_fishing_vessels_2018_raw.csv")
+effort_dat_binned_path <- here::here("results", "02-vessel-list", "effort_1x1_good_fishing_vessels_2018_raw.csv")
 
@@
                                          file_name = "subsidy_intensity_tot_grid_map",
-                                         file_dir = results_dir)
+                                         file_dir = results_dir,
+                                         fill_palette = "seq")
 
@@
                                          file_name = "subsidy_intensity_tot_region_map",
-                                         file_dir = results_dir)
+                                         file_dir = results_dir,
+                                         fill_palette = "seq")
 
@@
                                          file_name = "subsidy_intensity_B_grid_map",
-                                         file_dir = results_dir)
+                                         file_dir = results_dir,
+                                       fill_palette = "seq")
 
@@
                                          file_name = "subsidy_intensity_B_region_map",
-                                         file_dir = results_dir)
+                                         file_dir = results_dir,
+                                         fill_palette = "seq")
 
@@
                                          file_name = "subsidy_intensity_BC_grid_map",
-                                         file_dir = results_dir)
+                                         file_dir = results_dir,
+                                        fill_palette = "seq")
 
@@
                                          file_name = "subsidy_intensity_BC_region_map",
-                                         file_dir = results_dir)
+                                         file_dir = results_dir,
+                                         fill_palette = "seq")
 
@@
                             file_name = "F_Fmsy_region_map",
-                            file_dir = results_dir)
+                            file_dir = results_dir,
+                            fill_palette = "div",
+                            fill_low = "#001f9e",
+                            fill_high = "#EF3B2C",
+                            fill_mid = "#ffffff",
+                            fill_midpoint = 1)
 
@@
                             file_name = "B_Bmsy_region_map",
-                            file_dir = results_dir)
+                            file_dir = results_dir,
+                            fill_palette = "div",
+                            fill_low = "#0031f7",
+                            fill_high = "#EF3B2C",
+                            fill_mid = "#ffffff",
+                            fill_midpoint = 1)
 
@@
 # Set some plot scales
-subs_x <- c(0,2.5)
+subs_x <- c(0,4)
 f_y <- c(0,3)
@@
                                         x_name = paste0("Weighted Mean Subsidy Intensity ($/KWh)"),
-                                        x_limits = subs_x,
+                                        x_limits = c(0,1),
                                         y = "fv_fmsy",
@@
 
-## Figure 1
+## Figure 1 (Using Bad Subisides)
 
 ```{r}
-top_row <- #plot_grid(
+top_row <- plot_grid(
 
-  #get_legend(subsidy_intensity_BC_grid_l[["w_mean"]]),
-
-  plot_grid(subsidy_intensity_BC_region_l[["w_mean"]],
-            F_Fmsy_region_l[["median"]],
+  plot_grid(subsidy_intensity_B_grid_l[["w_mean"]] + theme(legend.position = "none"),
+            subsidy_intensity_B_region_l[["w_mean"]] + theme(legend.position = "none"),
             nrow = 1,
             label_x = 0,
-            labels = c("A)", "B)"))
+            labels = c("A)", "B)")),
 
-  # ncol = 1,
-  # rel_heights = c(0.1, 1)
+  get_legend(subsidy_intensity_B_grid_l[["w_mean"]]),
 
-#)
+  ncol = 1,
+  rel_heights = c(1, 0.2)
+
+)
+
+bottom_row <- plot_grid(
+  F_Fmsy_region_l[["median"]],
+  w_mean_B_subs_vs_F_Fmsy_l[["median"]] + theme(plot.margin = margin(1, 0, 1, 0, "cm")),
+  nrow = 1,
+  labels = c("C)", "D)")
+)
 
 Figure1 <- plot_grid(top_row,
-                     w_mean_BC_subs_vs_F_Fmsy_l[["median"]],
-                     nrow = 2,
-                     labels = c("", "C)"),
-                     label_y = 1.05)
+                     bottom_row,
+                     nrow = 2)
 

### 2020-03-26 scripts/01_data_wrangling.Rmd
and paper figures again

@@
 fao_production_dat_edit_groups <- fao_production_dat_edit %>%
-  group_by(iso3, year, isscaap_group, variable, units, source) %>%
+  group_by(iso3, year, fao_region = fishing_area, isscaap_group, variable, units, source) %>%
   summarize(value = sum(value, na.rm = T))

### 2020-03-26 functions/MapMaker.R

@@ -18,7 +18,12 @@ MapMaker <- function(data,
                      eez_sf = NULL,
                      file_name = "map",
                      file_dir = here::here("results/"),
-                     plot_labels = NULL){
+                     plot_labels = NULL,
+                     fill_palette = "seq",
+                     fill_low = "#FFF5F0",
+                     fill_high = "#CB181D",
+                     fill_mid = NULL,
+                     fill_midpoint = NULL){
   
   ### Themes
   dark_theme <- theme(panel.background = element_rect(fill = "black"),
@@ -51,19 +56,20 @@ MapMaker <- function(data,
   ### Make land layer
   land <- geom_sf(data=land_sf, color = "grey10", fill="grey30", size = 0.25)
   
-  if(res == "grid"){
+  if(res == "grid" & fill_palette == "seq"){
     
     median <- data %>%
       ggplot()+
       geom_tile(aes(x = get(x), y = get(y), fill = get(paste0(fill, "_median")))) +
       land + 
-      scale_fill_distiller(type = "seq", palette = "RdYlBu",
-                           name = paste0(fill_name),
-                           na.value = "#000000", 
-                           limits = fill_limits,
-                           breaks = fill_breaks,
-                           labels = fill_labels,
-                           oob = scales::squish)+
+      scale_fill_gradient(low = fill_low,
+                          high = fill_high,
+                          name = paste0(fill_name),
+                          na.value = "#ffffff",
+                          limits = fill_limits,
+                          breaks = fill_breaks,
+                          labels = fill_labels,
+                          oob = scales::squish) + 
       scale_x_continuous(expand = c(0,0))+
       scale_y_continuous(expand = c(0,0), limits = c(-80,90))+
       xlab("") +
@@ -81,13 +87,14 @@ MapMaker <- function(data,
       ggplot()+
       geom_tile(aes(x = get(x), y = get(y), fill = get(paste0(fill, "_mean")))) +
       land + 
-      scale_fill_distiller(type = "seq", palette = "RdYlBu",
-                           name = paste0(fill_name),
-                           na.value = "#000000", 
-                           limits = fill_limits,
-                           breaks = fill_breaks,
-                           labels = fill_labels,
-                           oob = scales::squish)+
+      scale_fill_gradient(low = "#FFF5F0",
+                          high = "#CB181D",
+                          name = paste0(fill_name),
+                          na.value = "#ffffff",
[…]

### 2020-03-30 scripts/01_data_wrangling.Rmd
back to vessel list

--- 2020-03-24 scripts/01_data_wrangling.Rmd
@@
 
-# Calculate revenues and aggregate by ISSCAAP group
+# Calculate revenues and export
 landed_value_dat <- combine_catch_price_dat %>%
@@
   mutate(landed_value = value*exvessel) %>%
-  group_by(iso3, year, isscaap_group) %>%
+  group_by(iso3, year, fishing_area, species, asfis_species, scientific_name, yearbook_group, isscaap_group) %>%
   summarize(value = sum(landed_value, na.rm = T)) %>%
@@
 
-write_csv(landed_value_dat, paste0(data_dir, "estimated_landed_value_isscaap_groups_tidy.csv"))
-write_csv(landed_value_dat, paste0(app_data_dir, "estimated_landed_value_isscaap_groups_tidy.csv"))
+write_csv(landed_value_dat, paste0(data_dir, "estimated_landed_value_tidy.csv"))
+
+# Calculate revenues and aggregate by ISSCAAP group
+landed_value_dat_groups <- landed_value_dat %>%
+  group_by(iso3, year, isscaap_group, variable, units, source) %>%
+  summarize(value = sum(value, na.rm = T))
+
+write_csv(landed_value_dat_groups, paste0(data_dir, "estimated_landed_value_isscaap_groups_tidy.csv"))
+write_csv(landed_value_dat_groups, paste0(app_data_dir, "estimated_landed_value_isscaap_groups_tidy.csv"))
 ```

### 2020-03-30 app/ui_02b_edit_policies_D_overcap.R

@@ -308,6 +308,8 @@ Overcap = function(wto_members_and_observers, subsidy_types_sorted_sumaila)
                   
                 ), # /fluidRow
                 
+                tags$hr(),
+                
                 ### ----------------
                 ### Cap/Tier section
                 ### ----------------

### 2020-04-02 scripts/01_data_wrangling.Rmd
updating RAM

@@
 eu_countries <- country_dependencies$iso3[country_dependencies$is_EU]
-eu_country_names <- sort(countrycode(eu_countries, "iso3c", "country.name"))
+eu_country_names <- country_dependencies$WTO_name[country_dependencies$iso3 %in% eu_countries]
 

### 2020-04-02 scripts/02_vessel_list.Rmd
updating RAM

@@
 
-# Path to cleaned subsidies data file
+# Path to cleaned subsidies data file (2018)
 subsidy_dat_sumaila_path <- here::here("data", "edited", "sumaila_et_al_2019_subsidies_tidy.csv")
@@
 catch_dat_path <- here::here("data", "edited", "fao_2019_capture_production_tidy.csv")
+catch_year <- 2017
 
 # Path to cleaned landed value data file
-landed_value_dat_path <- here::here("data", "edited", "estimated_landed_value_isscaap_groups_tidy.csv")
+landed_value_dat_path <- here::here("data", "edited", "estimated_landed_value_tidy.csv")
+landed_value_year <- 2017
 
@@
 bq_project <-  "emlab-gcp"
+vessel_year <- 2018
 
@@
       year,
-      best.best_vessel_class geartype,
-      best.best_flag flag
+      best.best_vessel_class vessel_class,
+      best.best_flag flag_iso3
     FROM
@@
 
-  # This subquery identifies MMSI that offsett a lot
+  # This subquery identifies MMSI that offset a lot
   nast_ssvid AS (
@@
   year,
-  geartype,
-  flag
+  vessel_class,
+  flag_iso3
 FROM
@@
 
-## By 1x1 degree latititude/longitude
+## By binned latititude/longitude
 
-We first extract the number of hours spent fishing by each of our good fishing vessels in each 1x1 degree latitude/longitude bin from the raw fishing effort table (`world-fishing-827.gfw_research.pipe_v20190502_fishing`).
+We first extract the number of hours spent fishing by each of our good fishing vessels in each latitude/longitude bin from the raw fishing effort table (`world-fishing-827.gfw_research.pipe_v20190502_fishing`).
 
@@
 - year (int): Year. Matches our data year specified above.
-- lat_bin_center (int): 1 degree latitude bin, coordinates refer to the center of the bin
-- lon_bin_center (int): 1 degree longitude bin, coordinates refer to the center of the bin
+- lat_bin_center (int): latitude bin, coordinates refer to the center of the bin
+- lon_bin_center (int): longitude bin, coordinates refer to the center of the bin
 - fao_region (int): Major FAO statistical region
@@
 ```{r}
-sql2 <- '
+bin_size <- 1
+
+sql2 <- paste0('
 WITH
@@
   WHERE
-    year = 2018),
+    year =', vessel_year, '),
 
@@
       ssvid,
-      FLOOR(lat/1)*1 + 0.5 lat_bin_center,
-      FLOOR(lon/1)*1 + 0.5 lon_bin_center, 
+      FLOOR(lat/', bin_size, ')*', bin_size,' + ', bin_size/2, ' lat_bin_center,
+      FLOOR(lon/', bin_size, ')*', bin_size, ' + ', bin_size/2, ' lon_bin_center, 
       if(ARRAY_LENGTH(regions.major_fao)=0, "0", regions.major_fao[ordinal(1)]) AS fao_region,
@@
     WHERE
-      date > timestamp("2018-01-01")
-      AND date < timestamp("2018-12-31")
+      date > timestamp("', vessel_year, '-01-01")
+      AND date < timestamp("', vessel_year, '-12-31")
       AND ARRAY_LENGTH(regions.major_fao) > 0 # removes fishing inland
@@
         WHERE
-          year = 2018)
+          year =', vessel_year, ')
     GROUP BY
@@
   (ssvid,
-  year)
-'
+  year)')
 
 binned_effort_table <- bq_table(project = bq_project, 
-                                table = "effort_1x1_good_fishing_vessels_2018_raw",
+                                table = paste0("effort_", bin_size, "x", bin_size, "_good_fishing_vessels_2018_raw"),
                                 dataset = "SubsidyExplorer")
@@
   bq_table_delete(binned_effort_table)
-  effort_1x1_good_fishing_vessels_2018 <- 
+  effort_binned_good_fishing_vessels <- 
     bq_project_query(bq_project, 
@@
   bq_table_create(binned_effort_table)
-  effort_1x1_good_fishing_vessels_2018 <- 
+  effort_binned_good_fishing_vessels <- 
     bq_project_query(bq_project, 
@@
 
-# Save
-write_csv(effort_1x1_good_fishing_vessels_2018, paste0(results_dir, "effort_1x1_good_fishing_vessels_2018_raw.csv"))
+# Save locally
+binned_effort_table_local <- paste0(results_dir, "effort_", bin_size, "x", bin_size, "_good_fishing_vessels_", vessel_year, "_raw.csv")
+
+if(file.exists(binned_effort_table_local)){
+  unlink(binned_effort_table_local)
+  write_csv(effort_binned_good_fishing_vessels, binned_effort_table_local)
+}else{
+  write_csv(effort_binned_good_fishing_vessels, binned_effort_table_local)
+}
 ```
@@
 - eez_id (chr): EEZ identifier. 
+- eez_territory1_iso3 (chr) : Three letter code cooresponding to the administering territory of the EEZ
+- eez_territory2_iso3 (chr) : Three letter code cooresponding to the second administering territory of the EEZ (disputed and/or joint regime areas only)
+- eez_territory3_iso3 (chr) : Three letter code cooresponding to the third administering territory of the EEZ (disputed and/or joint regime areas only)
+- eez_sovereign1_iso3 (chr) : Three letter code cooresponding to the sovereign state of the EEZ
+- eez_sovereign2_iso3 (chr) : Three letter code cooresponding to the second sovereign state of the EEZ (disputed and/or joint regime areas only)
+- eez_sovereign3_iso3 (chr) : Three letter code cooresponding to the third sovereign state of the EEZ (disputed and/or joint regime areas only)
+- is_territorial (bln): Did the fishing activity occur within 12nm of shore? (This is an approximation of a country's territorial waters)
 - fao_region (int): Major FAO statistical region
 - ssvid (chr): Unique vessel identification number given by GFW (MMSI number for most vessels)
-- flag (chr): Best flag state of the vessel. 
+- flag_iso3 (chr): Best flag state of the vessel. 
 - vessel_class (chr): Best vessel type. 
@@
 - broadcast_imo (chr): Most common imo number broadcast by the vessel.
-- territory1_iso3 (chr) : Three letter code cooresponding to the administering territory of the EEZ
-- territory2_iso3 (chr) : Three letter code cooresponding to the second administering territory of the EEZ (disputed and/or joint regime areas only)
-- territory3_iso3 (chr) : Three letter code cooresponding to the third administering territory of the EEZ (disputed and/or joint regime areas only)
-- sovereign1_iso3 (chr) : Three letter code cooresponding to the sovereign state of the EEZ
-- sovereign2_iso3 (chr) : Three letter code cooresponding to the second sovereign state of the EEZ (disputed and/or joint regime areas only)
-- sovereign3_iso3 (chr) : Three letter code cooresponding to the third sovereign state of the EEZ (disputed and/or joint regime areas only)
-- fishing_hours_eez_fao: Total annual fishing hours in the specified eez and/or FAO statistical region by the vessel
-- fishing_KWh_eez_fao: Total annual fishing KWh hours in the specified eez and/or FAO statistical region by the vessel
+- fishing_hours_eez_fao_ter: Total annual fishing hours in the specified eez and/or FAO statistical region and/or territorial seas by the vessel
+- fishing_KWh_eez_fao_ter: Total annual fishing KWh hours in the specified eez and/or FAO statistical region and/or territorial seas by the vessel
 
 ```{r}
-sql3 <- '
+sql3 <- paste0('
 WITH
@@
     year,
-    best.best_flag as flag,
+    best.best_flag as flag_iso3,
     best.best_vessel_class as vessel_class,
@@
     CAST(eez_id as string) as eez_id,
-    territory1_iso3,
-    territory2_iso3,
-    territory3_iso3,
-    sovereign1_iso3,
-    sovereign2_iso3,
-    sovereign3_iso3
+    territory1_iso3 as eez_territory1_iso3,
+    territory2_iso3 as eez_territory2_iso3,
+    territory3_iso3 as eez_territory3_iso3,
+    sovereign1_iso3 as eez_sovereign1_iso3,
+    sovereign2_iso3 as eez_sovereign2_iso3,
+    sovereign3_iso3 as eez_sovereign3_iso3
   FROM
@@
       if(ARRAY_LENGTH(regions.eez)=0, "0000", regions.eez[ordinal(1)]) AS eez_id,
+      if(distance_from_shore_m <= 22224, TRUE, FALSE) AS is_territorial,
       if(ARRAY_LENGTH(regions.major_fao)=0, "0", regions.major_fao[ordinal(1)]) AS fao_region,
-      sum(hours) AS fishing_hours_eez_fao
+      sum(hours) AS fishing_hours_eez_fao_ter
     FROM
@@
         WHERE
-          year = 2018)
+          year = ', vessel_year, ')
     GROUP BY
@@
       eez_id,
+      is_territorial,
       fao_region
@@
       ssvid,
-      fishing_hours_eez_fao DESC)
+      fishing_hours_eez_fao_ter DESC)
 
@@
   CASE
-    WHEN engine_power_kw IS NULL THEN fishing_hours_eez_fao*400
-    ELSE fishing_hours_eez_fao*engine_power_kw
-  END AS fishing_KWh_eez_fao
+    WHEN engine_power_kw IS NULL THEN fishing_hours_eez_fao_ter*400
+    ELSE fishing_hours_eez_fao_ter*engine_power_kw
+  END AS fishing_KWh_eez_fao_ter
 FROM
@@
 USING
-  (eez_id)
-'
+  (eez_id)')
 
-effort_table <- bq_table(project = bq_project, 
-                     table = "effort_eez_fao_good_fishing_vessels_2018_raw",
+eez_effort_table <- bq_table(project = bq_project, 
+                     table = paste0("effort_eez_fao_ter_good_fishing_vessels_", vessel_year, "_raw"),
                      dataset = "SubsidyExplorer")
 
-if(bq_table_exists(effort_table)){
+if(bq_table_exists(eez_effort_table)){
 
-  bq_table_delete(effort_table)
-  effort_good_fishing_vessels_2018 <- 
+  bq_table_delete(eez_effort_table)
+  effort_good_fishing_vessels_eez <- 
     bq_project_query(bq_project, 
                     query = sql3, 
-                    destination_table = effort_table, 
+                    destination_table = eez_effort_table, 
                     use_legacy_sql = FALSE, 
@@
 }else {
-  bq_table_create(effort_table)
-  effort_good_fishing_vessels_2018 <- 
+  bq_table_create(eez_effort_table)
+  effort_good_fishing_vessels_eez <- 
     bq_project_query(bq_project, 
                    query = sql3, 
-                   destination_table = effort_table,
+                   destination_table = eez_effort_table,
                    use_legacy_sql = FALSE, 
@@
 
-# Save
-write_csv(effort_good_fishing_vessels_2018, paste0(results_dir, "effort_eez_fao_good_fishing_vessels_2018_raw.csv"))
+# Save locally
+eez_effort_table_local <- paste0(results_dir, "effort_eez_fao_ter_good_fishing_vessels_", vessel_year, "_raw.csv")
+
+if(file.exists(eez_effort_table_local)){
+  unlink(eez_effort_table_local)
+  write_csv(effort_good_fishing_vessels_eez, eez_effort_table_local)
+}else{
+  write_csv(effort_good_fishing_vessels_eez, eez_effort_table_local)
+}
 ```
@@
 # Load country dependencies helper file
-country_dependencies <- read_csv(here::here("data", "lookup-tables", "country_dependencies.csv"))
+country_dependencies <- read_csv(here::here("data", "lookup-tables", "country_dependencies.csv")) %>%
+  dplyr::select(flag_iso3 = iso3, flag_sovereign_iso3 = sovereign_iso3, is_EU)
 
 # EU countries
-eu_countries <- country_dependencies$iso3[country_dependencies$is_EU]
+# eu_countries <- country_dependencies$iso3[country_dependencies$is_EU]
+# 
+# # Dutch overseas territories 
+# dutch_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "NLD"]
+# 
+# # French overseas territories 
+# french_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "FRA"]
+# 
+# # Danish overseas territories
+# danish_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "DNK"]
+# 
+# # UK overseas territories
+# uk_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "GBR"]
+# 
+# # EU overseas territories
+# eu_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 %in% eu_countries]
+# 
+# # US overseas territories:  American Samoa, Guam, Northern Marianas Islands, Puerto Rico, US Virgin Islands
+# us_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "USA"]
+# 
+# # Norwegian overseas territories: 
+# norwegian_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "NOR"]
 
-# Dutch overseas territories 
-dutch_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "NLD"]
-
-# French overseas territories 
-french_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "FRA"]
-
-# Danish overseas territories
-danish_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "DNK"]
-
-# UK overseas territories
-uk_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "GBR"]
-
-# EU overseas territories
-eu_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 %in% eu_countries]
-
-# US overseas territories:  American Samoa, Guam, Northern Marianas Islands, Puerto Rico, US Virgin Islands
-us_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "USA"]
-
-# Norwegian overseas territories: 
-norwegian_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "NOR"]
+# 
 ```
@@
 ```{r}
-# Get table of all flag states in the GFW data
-gfw_flags <- effort_good_fishing_vessels_2018 %>%
-  distinct(flag) %>%
-  mutate(flag_name = countrycode(flag, "iso3c", "country.name"))
+# Get table of all flag states in the data to check for weird flag codes
+gfw_flags <- effort_good_fishing_vessels_eez %>%
+  distinct(flag_iso3) %>%
+  mutate(flag_name = countrycode(flag_iso3, "iso3c", "country.name"))
 
+# Only three we need to fix: GCA (outdated code for Guatemala), ROM (outdated code for Romania), and UNK (unknown, for some reason not just NA)
+vessel_list <- effort_good_fishing_vessels_eez
+vessel_list$flag_iso3[vessel_list$flag_iso3 == "GCA"] <- "GTM"
+vessel_list$flag_iso3[vessel_list$flag_iso3 == "ROM"] <- "ROU"
+vessel_list$flag_iso3[vessel_list$flag_iso3 == "UNK"] <- NA
 ```
@@
 ```{r}
-# Only three we need to fix: GCA (outdated code for Guatemala), ROM (outdated code for Romania), and UNK (unknown, for some reason not just NA)
-vessel_list <- effort_good_fishing_vessels_2018
-vessel_list$flag[vessel_list$flag == "GCA"] <- "GTM"
-vessel_list$flag[vessel_list$flag == "ROM"] <- "ROU"
-vessel_list$flag[vessel_list$flag == "UNK"] <- NA
+# Now lets add sovereign flags
+vessel_list <- vessel_list %>%
+  left_join(country_dependencies, by = c("flag_iso3" = "flag_iso3"))
 ```
@@
 effort_flag_fao <- vessel_list %>%
-  group_by(flag, fao_region) %>%
-  summarize(fishing_KWh = sum(fishing_KWh_eez_fao, na.rm = T)) %>%
+  group_by(flag_iso3, fao_region) %>%
+  summarize(fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T)) %>%
   ungroup()
@@
 effort_flag <- effort_flag_fao %>%
-  group_by(flag) %>%
+  group_by(flag_iso3) %>%
   summarize(fishing_KWh = sum(fishing_KWh, na.rm = T)) %>%
@@
 catch_flag_fao <- read_csv(catch_dat_path) %>%
-  dplyr::filter(year == 2017) %>%
+  dplyr::filter(year == catch_year) %>%
   dplyr::filter(!(iso3 %in% c("EU", "USA-T", "UNK"))) %>%
@@
   ungroup() %>%
-  spread(variable, value)
+  spread(variable, value) %>%
+  rename(fao_region = fishing_area)
 
@@
   group_by(iso3) %>%
-  summarize(landings = sum(landings, na.rm = T),
-            revenue = sum(revenue, na.rm = T)) %>%
+  summarize(capture_production = sum(capture_production, na.rm = T)) %>%
   ungroup()
+
+# Load landed value estimates
+revenue_flag_fao <- read_csv(landed_value_dat_path) %>%
+  dplyr::filter(year == catch_year) %>%
+  dplyr::filter(!(iso3 %in% c("EU", "USA-T", "UNK"))) %>%
+  group_by(iso3, fishing_area, variable) %>% 
+  summarize(value = sum(value, na.rm = T)) %>%
+  ungroup() %>%
+  spread(variable, value) %>%
+  rename(fao_region = fishing_area)
+
+revenue_flag <- revenue_flag_fao %>%
+  group_by(iso3) %>%
+  summarize(landed_value = sum(capture_production, na.rm = T)) %>%
+  ungroup()
+
 ```

### 2020-04-09 scripts/01_data_wrangling.Rmd
finished redoing vessel list

@@
 
-title: "SubsidyExplorer - Step 0: Data Wrangling"
+title: "SubsidyExplorer - Step 1: Data Wrangling"
 author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
@@
 
-**Subsidy Data**
+**Fisheries (Subsidy) Data**
 Estimates of annual fisheries subsidies provision by state from Sumaila et al.
@@
 These data were last downloaded from the OECD iLibrary portal as a CSV file on March 10, 2019 and are stored as `r oecd_fse_path`.
-> OECD (2019), "Fisheries: Fisheries support estimates", OECD Agriculture Statistics (database), https://doi.org/10.1787/ade64fdc-en (accessed on 10 March 2019).
+> OECD. (2019). Fisheries: Fisheries support estimates. Fisheries and Aquaculture Statistics, OECD Agriculture Statistics (Database). https://doi.org/10.1787/ade64fdc-en
 
@@
 The code used to pull the data is below.
-> The World Bank (2019). "World Development Indicators", https://datacatalog.worldbank.org/dataset/world-development-indicators (accessed on 24 October 2019).
+> World Bank. (2020). World Development Indicators. https://data.worldbank.org/
 
@@
 
-**Fisheries Data**
+**Other Fisheries Data**
 Fisheries landings in 2017 from the FAO Global Capture Production database (2019) and estimates of landed value generated using the ex-vessel price database created by Melnychuk et al.
@@
 https://doi.org/10.1093/icesjms/fsw169
+
+RAM Stock assessment database
+> RAM Legacy Stock Assessment Database. (2018). Version 4.44-assessment-only. Released 2018-12-22. DOI:10.5281/zenodo.2542919
 
@@
 
-RAM Stock assessment database
-> RAM Legacy Stock Assessment Database. (2018). Version 4.44-assessment-only. Released 2018-12-22. DOI:10.5281/zenodo.2542919
-
-Fisheries performance indicators
-> Anderson, J.
-L., Anderson, C.
-M., Chu, J., Meredith, J., Asche, F., Sylvia, G., Smith, M.
-D., Anggraeni, D., Arthur, R., Guttormsen, A., McCluney, J.
-K., Ward, T., Akpalu, W., Eggert, H., Flores, J., Freeman, M.
-A., Holland, D.
-S., Knapp, G., Kobayashi, M., … Valderrama, D.
-(2015).
-The Fishery Performance Indicators: A Management Tool for Triple Bottom Line Outcomes.
-PLOS ONE, 10(5), e0122809.
-https://doi.org/10.1371/journal.pone.0122809
-
-**Other**
 IUU Consolidated vessel list
@@
 
-# Note: Political entities, dependencies, and naming
+# Note: Country naming, political entities, and dependencies
 
@@
   clean_names(case = "snake") %>%
-  mutate(keep = ifelse(is.na(fa_region_group), F, T)) %>%
-  dplyr::filter(keep) %>%
   dplyr::select(area = code) %>%
@@
 
-# Look at NAs - 8498 entries
+# Look at NAs - 9398 entries
 combine_nas <- combine_catch_price_dat %>%
@@
 
-This second is a bit of a relic from when we were doing "country profiles", but there are a couple of relative metrics we want to calculate from our data sources. This is done here.
+This section is a bit of a relic from when we were doing "country profiles", but there are a couple of relative metrics we want to calculate from our data sources. This is done here.
 

### 2020-04-09 scripts/02_vessel_list.Rmd
finished redoing vessel list

@@
 subsidy_dat_sumaila_path <- here::here("data", "edited", "sumaila_et_al_2019_subsidies_tidy.csv")
+subsidy_year <- 2018
 
@@
 }
+
+# Do you wnat to make figures? 
+make_figures <- FALSE
 ```
@@
 country_dependencies <- read_csv(here::here("data", "lookup-tables", "country_dependencies.csv")) %>%
-  dplyr::select(flag_iso3 = iso3, flag_sovereign_iso3 = sovereign_iso3, is_EU)
+  dplyr::select(flag_iso3 = iso3, flag_sovereign_iso3 = sovereign_iso3, is_EU, is_dependency = is_overseas_territory)
 
-# EU countries
-# eu_countries <- country_dependencies$iso3[country_dependencies$is_EU]
-# 
-# # Dutch overseas territories 
-# dutch_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "NLD"]
-# 
-# # French overseas territories 
-# french_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "FRA"]
-# 
-# # Danish overseas territories
-# danish_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "DNK"]
-# 
-# # UK overseas territories
-# uk_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "GBR"]
-# 
-# # EU overseas territories
-# eu_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 %in% eu_countries]
-# 
-# # US overseas territories:  American Samoa, Guam, Northern Marianas Islands, Puerto Rico, US Virgin Islands
-# us_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "USA"]
-# 
-# # Norwegian overseas territories: 
-# norwegian_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "NOR"]
-
-# 
 ```
@@
 
-```{r}
-# Now lets add sovereign flags
-vessel_list <- vessel_list %>%
-  left_join(country_dependencies, by = c("flag_iso3" = "flag_iso3"))
-```
-
 # Allocating Catches and Subsidies
@@
 Before we allocate catches and subsidies, we need to get total fishing kWh by flag and FAO region, as well as by flag. 
-
 ```{r}
@@
 
-catch_flag <- catch_flag_fao %>%
-  group_by(iso3) %>%
-  summarize(capture_production = sum(capture_production, na.rm = T)) %>%
-  ungroup()
-
 # Load landed value estimates
@@
 
-revenue_flag <- revenue_flag_fao %>%
+# Combine catches and revenues
+catch_revenue_flag_fao <- catch_flag_fao %>%
+  left_join(revenue_flag_fao, by = c("iso3", "fao_region")) %>%
+  mutate(fao_region = as.character(fao_region))
+
+catch_revenue_flag <- catch_revenue_flag_fao %>%
   group_by(iso3) %>%
-  summarize(landed_value = sum(capture_production, na.rm = T)) %>%
-  ungroup()
+  summarize(capture_production = sum(capture_production, na.rm = T),
+            landed_value = sum(landed_value, na.rm = T))
 
@@
 ```{r}
-# effort_flag
+# Fishing effort (flag) for which we don't have matching catch data - 2 states (Christmas Island and NA)
 effort_no_matching_catches <- effort_flag %>%
-  dplyr::filter(!(flag %in% catch_flag$iso3))
+  anti_join(catch_revenue_flag, by = c("flag_iso3" = "iso3"))
 
-# There are 3 flag states for which we don't have reported catch data at all: CXR (Christmas Island), LIE (Liechtenstein) and NA (no flag).
+catch_no_matching_effort <- catch_revenue_flag %>%
+  anti_join(effort_flag, by = c("iso3" = "flag_iso3"))
+
+# There are 2 flag states for which we don't have reported catch data at all: CXR (Christmas Island), LIE (Liechtenstein) and NA (no flag).
 We're going to try assigning them based on the EEZ in which they spend the most time fishing instead.
-vessels_new_flag <- vessel_list %>%
-  dplyr::filter(flag %in% effort_no_matching_catches$flag) %>% # 773 entries 
-  dplyr::filter(eez_id != 0) %>% # remove high seas entries
+vessels_no_catches <- vessel_list %>%
+  dplyr::filter(flag_iso3 %in% effort_no_matching_catches$flag_iso3) %>% # 1094 entries 
+  group_by(ssvid, eez_id, eez_territory1_iso3, eez_territory2_iso3, eez_territory3_iso3) %>%
+  summarize(fishing_KWh_eez_fao_ter = sum(fishing_KWh_eez_fao_ter, na.rm = T)) %>%
   group_by(ssvid) %>%
-  top_n(1, fishing_KWh_eez_fao) %>%
-  summarize(new_flag = unique(territory1_iso3))  #486 vessels
+  mutate(rank = dense_rank(desc(fishing_KWh_eez_fao_ter)),
+         max_rank_no_hs = min(rank[!is.na(eez_territory1_iso3)])) %>%
+  ungroup()
 
-# So  there are 75 vessels that have no flag and that only fish on the high seas... We'll be excluding those vessels
-vessel_info_new_flag <- vessel_list %>%
-  dplyr::filter(ssvid %in% vessels_new_flag$ssvid) %>%
+# Isolate vessels for which we can assign a new flag this way: 474 vessels. 
+vessels_new_flag <- vessels_no_catches %>%
+  dplyr::filter(max_rank_no_hs != Inf) %>%
+  group_by(ssvid) %>%
+  summarize(new_flag = eez_territory1_iso3[rank == max_rank_no_hs])
+
+# Vessels still missing flag: So there are 75 vessels that have no flag and that only fish on the high seas... We'll be excluding those vessels. 
+vessels_missing_flag <- vessels_no_catches %>%
+  dplyr::filter(max_rank_no_hs == Inf)
+
+# Assign new flags to those vessels and remove those missing a flag state.  
+vessel_list <- vessel_list %>%
+  dplyr::filter(!(ssvid %in% vessels_missing_flag$ssvid)) %>%
   left_join(vessels_new_flag, by = "ssvid") %>%
-  mutate(flag = new_flag) %>%
-  dplyr::select(-new_flag) # 688 entries
+  mutate(flag_iso3 = case_when(!is.na(new_flag) ~ new_flag,
+                          TRUE ~ flag_iso3)) %>%
+  dplyr::select(-new_flag)
 
-# Fix vessel list 
-vessel_list <- vessel_list %>%
-  dplyr::filter(!(flag %in% effort_no_matching_catches$flag)) %>%
-  bind_rows(vessel_info_new_flag) %>%
-  dplyr::filter(!is.na(flag))
-vessel_list$flag[vessel_list$flag == "ESH"] <- "MAR"
-vessel_list$flag[vessel_list$flag == "CPT"] <- "FRA"
 ```
 
-Turns out they all do!
+```{r}
+# Now lets add sovereign flags
+vessel_list <- vessel_list %>%
+  left_join(country_dependencies, by = c("flag_iso3" = "flag_iso3"))
+
+# And manually correct two - Clipperton Atoll and Western Sahara
+vessel_list$flag_iso3[vessel_list$flag_iso3 == "CPT"] <- "FRA"
+vessel_list$flag_iso3[vessel_list$flag_iso3 == "ESH"] <- "MAR"
+```
+
+Now they all do and we can assign catches.
 
@@
 effort_no_matching_catches <- effort_flag %>%
-  dplyr::filter(!(flag %in% catch_flag$iso3))
+  anti_join(catch_revenue_flag, by = c("flag_iso3" = "iso3"))
 ```
@@
 ```{r}
-# Let's get region specific catch rates we can use for when we don't have matching flag/fao pairs
-catch_region_no_match <- catch_flag_fao %>%
-  anti_join(effort_flag_fao, by = c("iso3" = "flag", "area" = "fao_region")) %>%
-  mutate(join_region = case_when(area == 88 ~ 58,
-                                      TRUE ~ area)) %>%
-  group_by(join_region) %>%
-  summarize(tot_landings = sum(landings, na.rm = T),
-            tot_revenue = sum(revenue, na.rm = T))
+# Get matching catch/effort flag and fao region pairings
+effort_catch_flag_region_matching <- effort_flag_fao %>%
+  left_join(catch_revenue_flag_fao, by = c("flag_iso3" = "iso3", "fao_region")) %>%
+  arrange(flag_iso3, fao_region) %>%
+  mutate(is_flag_region_match = ifelse(!is.na(fishing_KWh) & !is.na(capture_production), T, F))
 
-# Get matching catch/effort flag and fao region pairings
-match_effort_catch <- effort_flag_fao %>%
-  left_join(catch_flag_fao, by = c("flag" = "iso3", "fao_region" = "area")) %>%
-  arrange(flag, fao_region) %>%
-  mutate(is_match = ifelse(!is.na(fishing_KWh) & !is.na(landings), T, F))
+# Matches
+flag_region_matches <- effort_catch_region_matching %>%
+  dplyr::filter(is_flag_region_match)
 
-# # Extract those flag/fao pairings for which we have matching entries to calculate catch rates
-match <- match_effort_catch %>%
-  dplyr::filter(is_match) %>%
-  mutate(catch_per_fishing_KWh = landings/fishing_KWh,
-         revenue_per_fishing_KWh = revenue/fishing_KWh) %>%
-  dplyr::select(flag, fao_region, catch_per_fishing_KWh, revenue_per_fishing_KWh)
+# Calculate catch rates for those entries with matching catches and efforts by flag/fao region pairing
+rates_flag_region_matches <- flag_region_matches %>%
+  mutate(flag_region_catch_per_fishing_KWh = capture_production/fishing_KWh,
+         flag_region_revenue_per_fishing_KWh = landed_value/fishing_KWh) %>%
+  dplyr::select(flag_iso3, fao_region, flag_region_catch_per_fishing_KWh, flag_region_revenue_per_fishing_KWh)
 
-# # Extract those flag/fao pairings for which we have matching entries to calculate catch rates
-no_match <- match_effort_catch %>%
-  dplyr::filter(is_match == F)
+### -----------------------------------------------------------------
+# Get matching catch/effort flag pairings
+effort_catch_flag_matching <- effort_flag %>%
+  left_join(catch_revenue_flag, by = c("flag_iso3" = "iso3")) %>%
+  arrange(flag_iso3) %>%
+  mutate(is_flag_match = ifelse(!is.na(fishing_KWh) & !is.na(capture_production), T, F))
 
-# Get leftover rates
-rates_no_match <- no_match %>%
-  mutate(join_region = case_when(fao_region == 18 ~ 21,
-                                 fao_region == 67 ~ 77,
-                                 fao_region == 47 ~ 41,
-                                 TRUE ~ fao_region)) %>%
-  full_join(catch_region_no_match, by = c("join_region")) %>%
-  group_by(join_region) %>%
-  mutate(tot_fishing_KWh = sum(fishing_KWh, na.rm = T),
-         catch_per_fishing_KWh = tot_landings/tot_fishing_KWh,
-         revenue_per_fishing_KWh = tot_revenue/tot_fishing_KWh) %>%
-  ungroup() %>%
-  group_by(fao_region) %>%
-  summarize(catch_per_fishing_KWh = unique(catch_per_fishing_KWh),
-            revenue_per_fishing_KWh = unique(revenue_per_fishing_KWh))
+### Matches 
+flag_matches <- effort_catch_flag_matching %>%
+  dplyr::filter(is_flag_match)
 
-# Add back in to our flag/fao pairings
-no_match <- no_match %>%
-  left_join(rates_no_match, by = c("fao_region")) %>%
-  dplyr::select(flag, fao_region, catch_per_fishing_KWh, revenue_per_fishing_KWh)
+# Calculate catch rates for those entries with matching catches and efforts by flag/fao region pairing
+rates_flag_matches <- flag_matches %>%
+  mutate(flag_catch_per_fishing_KWh = capture_production/fishing_KWh,
+         flag_revenue_per_fishing_KWh = landed_value/fishing_KWh) %>%
+  dplyr::select(flag_iso3, flag_catch_per_fishing_KWh, flag_revenue_per_fishing_KWh)
 
-# Combine
-catch_rates_flag_fao_all <- match %>%
-  bind_rows(no_match)
+### -------------------
+comprehensive_catch_rates <- effort_catch_flag_region_matching %>%
+  left_join(rates_flag_region_matches, by = c("flag_iso3", "fao_region")) %>%
+  left_join(rates_flag_matches, by = c("flag_iso3")) %>%
+  mutate(catch_per_fishing_KWh = case_when(!is.na(flag_region_catch_per_fishing_KWh) ~ flag_region_catch_per_fishing_KWh,
+                                           TRUE ~ flag_catch_per_fishing_KWh),
+         revenue_per_fishing_KWh = case_when(!is.na(flag_region_revenue_per_fishing_KWh) ~ flag_region_revenue_per_fishing_KWh,
+                                           TRUE ~ flag_revenue_per_fishing_KWh)) %>%
+  dplyr::select(flag_iso3, fao_region, catch_per_fishing_KWh, revenue_per_fishing_KWh)
 ```
@@
 vessel_list <- vessel_list %>%
-  left_join(catch_rates_flag_fao_all, by = c("flag", "fao_region"))
+  left_join(comprehensive_catch_rates, by = c("flag_iso3", "fao_region"))
 ```
@@
 # Load subsidy data
-subsidies_dat <- read_csv(subsidy_dat_path) %>%
-  dplyr::filter(year == 2018)
+subsidies_dat <- read_csv(subsidy_dat_sumaila_path) %>%
+  dplyr::filter(year == subsidy_year)
 
@@
 # Resummarize effort including overseas territories with their sovereign
-effort_flag_revised <- effort_flag %>%
-  mutate(flag_for_matching = case_when(flag %in% c("USA", us_territories) ~ "USA",
-                              flag %in% c("FRA", french_territories) ~ "FRA",
-                              flag %in% c("GBR", uk_territories) ~ "GBR",
-                              flag %in% c("NOR", norwegian_territories) ~ "NOR",
-                              flag %in% c("DNK", danish_territories) ~ "DNK",
-                              flag %in% c("NLD", dutch_territories) ~ "NLD",
-                              TRUE ~ flag)) %>%
-  group_by(flag_for_matching) %>%
-  mutate(tot_fishing_KWh = sum(fishing_KWh, na.rm = T))
+effort_sovereign_flag <- vessel_list %>%
+  group_by(flag_sovereign_iso3) %>%
+  summarize(fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T)) %>%
+  ungroup()
 
 # Calculate subsidy rates by flag
-subsidy_rates_flag <- effort_flag_revised %>%
-  left_join(subsidies_flag, by = c("flag_for_matching" = "iso3")) %>%
-  group_by(flag) %>%
-  summarize_at(subsidy_types, list(per_fishing_KWh = ~./tot_fishing_KWh))
+subsidy_rates_flag <- effort_sovereign_flag %>%
+  inner_join(subsidies_flag, by = c("flag_sovereign_iso3" = "iso3")) %>%
+  group_by(flag_sovereign_iso3) %>%
+  summarize_at(subsidy_types, list(per_fishing_KWh = ~./fishing_KWh))
 subsidy_rates_flag[is.na(subsidy_rates_flag)] <- 0
@@
 vessel_list <- vessel_list %>%
-  left_join(subsidy_rates_flag, by = c("flag"))
+  left_join(subsidy_rates_flag, by = c("flag_sovereign_iso3"))
 
@@
 vessel_list <- vessel_list %>%
-  mutate(catch = fishing_KWh_eez_fao*catch_per_fishing_KWh,
-         revenue = fishing_KWh_eez_fao*revenue_per_fishing_KWh) %>%
-  mutate_at(paste0(subsidy_types, "_per_fishing_KWh"), list(subs = ~.*fishing_KWh_eez_fao)) %>%
+  mutate(catch = fishing_KWh_eez_fao_ter*catch_per_fishing_KWh,
+         revenue = fishing_KWh_eez_fao_ter*revenue_per_fishing_KWh) %>%
+  mutate_at(paste0(subsidy_types, "_per_fishing_KWh"), list(subs = ~.*fishing_KWh_eez_fao_ter)) %>%
   rename_at(paste0(subsidy_types, "_per_fishing_KWh_subs"), rename_me) %>%
@@
 
-write_csv(vessel_list, paste0(results_dir, "vessel-list-2018-raw.csv"))
+write_csv(vessel_list, paste0(results_dir, "vessel_list_2018_raw.csv"))
 ```

### 2020-04-09 scripts/03_management.Rmd
finished redoing vessel list

@@
 
-The purpose of this script is to classify all of our vessels into three different management regimes: 
+The purpose of this script is to assign management scores to all of our vessels, such that they can later be classified into three different management regimes: 
+- Well-managed
 - Managed
-- Intermediate
 - Open access
@@
 - vessel-list-2018-management.csv
-
-In addition to the vessel list created in the previous script, the following data sources are used to classify management regimes:
 
@@
 # Path to vessel list
-vessel_list_path <- here::here("results", "1-vessel-list", "vessel-list-2018-raw.csv")
+vessel_list_path <- here::here("results", "02-vessel-list", "vessel-list-2018-raw.csv")
 

### 2020-04-09 scripts/04_subsidy_reform_definitions.Rmd
finished redoing vessel list

---
output:
  html_document: default

title: "SubsidyExplorer - Step 4: Apply proposal 'definitions' to vessel list"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
bibliography: "../pew-subsidies.bib"

---

# Introduction

The purpose of this script is to apply "definitions" to our global vessel list in order to make it easier to identify which vessels would be likely to be affected by each of the subsidy reform policies under consideration by the WTO. Storing whether each vessel meets a certain "definition" (i.e. qualification) speeds up selection of affected vessels within the SubsidyExplorer toolkit.

```{r}
# Load packages
library(knitr) 
library(countrycode) # country name matching
library(janitor) # cleaning column names
library(tidyverse)

# Package to normalize vessel names in the same way GFW normalizes vessel names
#devtools::install_github("jcvdav/startR")
library(startR)

# Path to global vessel list
vessel_list_path <- here::here("results", "3-model-parameterization", "vessel-list-2018-regions.csv")

# Paths to other data files
iuu_dat_path <- here::here("data", "raw", "fisheries", "IUU_Vessel_List", "IUUList-20190430.csv")
costello_2016_path <- here::here("data", "raw", "fisheries", "Costello_2016", "ProjectionData_2012.csv")

```

```{r}
# Code options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, message = FALSE, warning = F)

# Directories for the output files generated by this script
results_dir <- here::here("results", "5-vessel-list-policy-definitions/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}

app_dir <- here::here("WTOtoolkit", "data/")
if (dir.exists(app_dir) == F) {
  dir.create(app_dir, recursive = T)
}

```

# Input vessel info table

Our global vessel info table was created in a previous script (`r here::here("scripts", "1-vessel-list.Rmd")`) and saved to `r vessel_list_path`.

```{r}
vessel_list <- read.csv(vessel_list_path, stringsAsFactors = F)
```

```{r}
# EU countries
#Belgium, Bulgaria, Croatia, Cyprus, Denmark, Estonia, Finland, France, Germany, Greece, Ireland, Italy, Latvia, Lithuania, Malta, Netherlands, Poland, Portugal, Romania, Slovenia, Spain, Sweden, United Kingdom
eu_countries <- c("BEL", "BGR", "HRV", "CYP", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "IRL", "ITA", "LVA", "LTU", "MLT", "NLD", "POL", "PRT", "ROU", "SVN", "ESP", "SWE", "GBR")

# Dutch overseas territories: Aruba, Bonaire/St. Eustatius/Saba, Curacao, Sint Maarten
dutch_territories <- c("ABW", "BES", "CUW", "SXM")

# French overseas territories: French Guiana, French Polynesia, French Southern and Antarctic Territories, Guadeloupe, Martinique, Mayotte, New Caledonia, Reunion, Saint Barthelemy, Saint Martin, St. Pierre and Miquelon, Wallis and Futuna Islands
french_territories <- c("GUF", "PYF", "ATF", "GLP", "MTQ", "MYT", "NCL", "REU", "BLM", "MAF", "SPM", "WLF")

# Danish overseas territories: Faroe Islands, Greenland
danish_territories <- c("FRO", "GRL")

# British overseas territories: Anguilla, Ascension island, Bermuda, Cayman Islands, Falkland Islands, Guernsey, Gibraltar, British Indian Ocean Territories, Jersey, Monserratt, Pitcairn Island, South Georgia and the South Sandwich Islands, Saint Helena/Ascension/Tristan da Cunha, Tristan da Cunha, Turks and Caicos Islands, British Virgin Islands
uk_territories <- c("AIA","ASC","BMU","CYM","FLK","GGY","GIB","IOT","JEY","MSR","PCN","SGS","SHN","TAA","TCA","VGB")

eu_territories <- c(dutch_territories, french_territories, danish_territories, uk_territories)

# Norwegian overseas territories: Bouvet Islands, Svalbard and Jan Mayen Islands
norwegian_territories <- c("BVT", "SJM")

# US overseas territories:  American Samoa, Guam, Northern Marianas Islands, Puerto Rico, US Virgin Islands
us_territories <- c("ASM", "GUM", "MNP", "PRI", "VIR")

eu_northern_agreement <- c("NOR", "ISL")
```

# Apply Definitions

## Country Development Status

We use the flag of the vessel to assign development status. If the flag of the vessel was not able to be determined, we assume the development status to be "Developing".

```{r}
# Read in country list with development status
country_list <- read_csv(here::here("data", "country-conversion-sheet-all.csv"))

country_development_status <- country_list %>%
  group_by(iso3) %>%
  summarize(development_status_full = unique(development_status)) %>%
  mutate(development_status = str_replace(development_status_full, ' \\(.*\\)', ""),
         development_status_notes = str_extract(development_status_full, '\\(.*\\)')) %>%
  dplyr::select(iso3, development_status)

country_development_status$development_status[country_development_status$iso3 == "ATF"] <- "Developed"
country_development_status$development_status[country_development_status$iso3 == "IOT"] <- "Developed"

# Add development status to the vessel list
temp_vessel_list <- vessel_list %>%
  left_join(country_development_status, by = c("flag" = "iso3"))

# Let's also add identifies of EU vessels and US territory vessels to the vessel list
temp_vessel_list <- temp_vessel_list %>%
  mutate(is_EU = case_when(flag %in% eu_countries ~ T,
                           TRUE ~ F),
         is_EU_territory = case_when(flag %in% eu_territories ~ T,
                                     TRUE ~ F),
         is_US_territory = case_when(flag %in% us_territories ~ T,
                                     TRUE ~ F))
```

## Distant water fishing

In order to determine whether a vessel is engaging in distant water fishing, we need to know something about the sovereign state of the vessel's flag state.

```{r}
# Get pairings of administering and sovereign states from the EEZ data
sovereign_pairings <- temp_vessel_list %>%
  distinct(territory1_iso3, sovereign1_iso3) %>%
  rename(flag = territory1_iso3, flag_sovereign = sovereign1_iso3)
sovereign_pairings$flag_sovereign[sovereign_pairings$flag == "CHN"] <- "CHN"

# Create a manual list of missing sovereign pairings
sovereign_pairings_manual <- tibble(flag = c("HKG", "KHM", "CUW", "BLZ", "CYM", "JOR", "PSE", "JAM", "AIA")) %>%
  mutate(flag_sovereign = case_when(flag == "HKG" ~ "CHN",
                                    flag == "CUW" ~ "NLD",
                                    flag == "CYM" ~ "GBR",
                                    flag == "PSE" ~ "ISR",
                                    flag == "AIA" ~ "GBR",
                                    TRUE ~ flag))

sovereign_pairings <- sovereign_pairings %>%
  bind_rows(sovereign_pairings_manual) %>%
  distinct(flag, flag_sovereign)

# Also fix that on the vessel list
temp_vessel_list$sovereign1_iso3[temp_vessel_list$territory1_iso3 == "CHN"] <- "CHN"

# We then match it back to our vessel list so each entry has an assigned sovereign flag
temp_vessel_list <- temp_vessel_list %>%
  left_join(sovereign_pairings, by = "flag")

# We fist exclude entries where the flag state of the vessel and the administering state of the EEZ in which it is fishing are the same
distant_water_fishing <- temp_vessel_list %>%
  mutate(territory1_match = case_when(!is.na(territory1_iso3) & flag == territory1_iso3 ~ T,
                                      TRUE ~ F),
         territory2_match = case_when(!is.na(territory2_iso3) & flag == territory2_iso3 ~ T,
                                      TRUE ~ F),
         territory3_match = case_when(!is.na(territory3_iso3) & flag == territory3_iso3 ~ T,
                                      TRUE ~ F)) %>%
  dplyr::filter(!territory1_match & !territory2_match & !territory3_match)
```

### "Intra-EU fishing".

Vessels flagged to EU member states have the right to fish in the EEZs of other EU member states, therefore we do not include these instances as "distant water fishing". In order to remove these from our dataset, we first need create a list of EU member states, as well as non-member states with with the EU has fishing agreements as part of the northern agreement (i.e. Norway and Iceland).

We define "intra-EU fishing" as fishing activity that meets one of the following criteria: 
1. The flag state of the vessel is a member state of the EU, Norway, Svalbard and Jan Mayen, or Iceland and the EEZ in which it is fishing is administered by a member state of the EU, Norway, Svalbard and Jan Mayen, or Iceland (e.g. a French-flagged vessel fishing in the EEZ of Spain);
2. The sovereign of the vessel's flag state is a member state of the EU, Norway, Svalbard and Jan Mayen, or Iceland and the EEZ in which it is fishing is administered by a member state of the EU, Norway, Svalbard and Jan Mayen, or Iceland (e.g. a XXX-flagged vessel fishing in the EEZ of Spain).

We do not consider the following to be "intra-EU fishing": 
1. The flag state of the vessel is a member state of the EU, Norway, Svalbard and Jan Mayen, or Iceland and the EEZ in which it is fishing belongs to a territory or distant region of an EU member state (e.g. a French-flagged vessel fishing in the EEZ of French Polynesia).

```{r}
# Exclude intra EU fishing
distant_water_fishing <- distant_water_fishing %>%
  mutate(is_intra_EU = case_when(flag %in% c(eu_countries, eu_northern_agreement, norwegian_territories) & territory1_iso3 %in% c(eu_countries, eu_northern_agreement, norwegian_territories) ~ T,
                                 flag_sovereign %in% c(eu_countries, eu_northern_agreement, norwegian_territories) & territory1_iso3 %in% c(eu_countries, eu_northern_agreement, norwegian_territories) ~ T,
                                 TRUE ~ F)) %>%
  dplyr::filter(!is_intra_EU) %>%
  mutate(distant_water = T) %>%
  dplyr::select(eez_id, ssvid, fao_region, distant_water)
```

### Sovereignity

If the sovereign flag state of a vessel is the same as the sovereign state of the EEZ in which it's fishing, this connection may still be considered to be distant water fishing (e.g. US vessel fishing in Palmyra Atoll), though this is generally not considered to be foreign distant water fishing.

We descibe "sovereign fishing" as fishing activity that meets one of the following criteria: 
1. The flag state of the vessel is the same as the sovereign of the administering territory of the EEZ in which it is fishing (e.g. a US flagged vessel fishing in the EEZ of Palmyra Atoll).
2. The sovereign of the flag state of the vessel is the same as the sovereign of the administering territory of the EEZ in which it is fishing (e.g. a Puerto-Rican flagged vessel fishing in the EEZ of Palmyra Atoll);

Sovereign fishing is included in our definition of distant water fishing

```{r}
temp_vessel_list <- temp_vessel_list %>%
  left_join(distant_water_fishing, by = c("eez_id", "ssvid", "fao_region"))
temp_vessel_list$distant_water[is.na(temp_vessel_list$distant_water)] <- F

```

## High seas fishing

In order to later be able to easily identify high seas fishing, we want to be able to easily identify the fraction of each vessel's total fishing effort spent on the high seas in a given year.

```{r}
# Get totals by vessel
vessel_totals_high_seas <- temp_vessel_list %>%
  dplyr::filter(eez_id == 0) %>%
  group_by(ssvid) %>%
  summarize(fishing_h_hs = sum(fishing_hours_eez_fao, na.rm = T),
            fishing_KWh_hs = sum(fishing_KWh_eez_fao, na.rm = T))

vessel_totals_prop_hs <- temp_vessel_list %>%
  group_by(ssvid) %>%
  summarize(fishing_h = sum(fishing_hours_eez_fao, na.rm = T),
            fishing_KWh = sum(fishing_KWh_eez_fao, na.rm = T)) %>%
  ungroup() %>%
  left_join(vessel_totals_high_seas, by = "ssvid") %>%
  mutate(prop_fishing_hours_HS = case_when(is.na(fishing_h_hs) ~ 0, 
                                           TRUE ~ fishing_h_hs/fishing_h),
         prop_fishing_KWh_HS = case_when(is.na(fishing_KWh_hs) ~ 0, 
                                         TRUE ~ fishing_KWh_hs/fishing_KWh)) %>%
  dplyr::select(ssvid, prop_fishing_hours_HS, prop_fishing_KWh_HS)

temp_vessel_list <- temp_vessel_list %>%
  left_join(vessel_totals_prop_hs, by = "ssvid")
```

## IUU

### IUU #1: RFMO IUU vessel lists

Using the combined list of IUU vessels (https://iuu-vessels.org/), we want to try to match as many vessels as possible to our vessel list.

```{r}
# Read in IUU list
iuu_list <- read_csv(iuu_dat_path) %>%
  clean_names(case = "snake")

# Extract only vessels currently listed, and create a new entry for each using the "name" field
iuu_clean_name <- iuu_list %>% 
   dplyr::filter(currently_listed) %>%
   mutate(name_new = str_split(name, ", "))%>%
   unnest(cols = c(name_new)) %>%
  dplyr::select(name, name_new, imo, gear_type, flag, ircs, ssvid, gt, length) %>%
  mutate(n_shipname = map_chr(name_new, normalize_shipname))

# Do the same thing, but for RFMO name since they differ
iuu_clean_rfmo_name <- iuu_list %>% 
   dplyr::filter(currently_listed) %>%
   mutate(name_new1 = str_split(rfmo_name, ", "),
          name_new2 = str_split(rfmo_name, "[()]"),
          name_new = case_when(name_new1 != rfmo_name ~ name_new1,
                               TRUE ~ name_new2)) %>%
   unnest(cols = c(name_new)) %>%
  dplyr::select(name, name_new, imo, gear_type, flag, ircs, ssvid, gt, length) %>%
  mutate(n_shipname = map_chr(name_new, normalize_shipname))

### Blank database for IUU vessels
iuu_matching_vessels <- tibble(ssvid = integer(0),
                               flag = character(0),
                               broadcast_shipname = character(0))

### Abbreviated vessel list for matching
vessels_for_matching <- temp_vessel_list %>%
  distinct(ssvid, flag, vessel_class, length_m, tonnage_gt, engine_power_kw, broadcast_shipname, broadcast_callsign, broadcast_imo)

iuu <- iuu_clean_name %>%
  dplyr::select(-name, -name_new) %>%
  rename(iuu_imo = imo, iuu_gear_type = gear_type, iuu_flag = flag, iuu_callsign = ircs, iuu_ssvid = ssvid, iuu_tonnage_gt = gt, iuu_length = length, iuu_shipname = n_shipname)

iuu2 <- iuu_clean_rfmo_name %>%
  dplyr::select(-name, -name_new) %>%
  rename(iuu_imo = imo, iuu_gear_type = gear_type, iuu_flag = flag, iuu_callsign = ircs, iuu_ssvid = ssvid, iuu_tonnage_gt = gt, iuu_length = length, iuu_shipname = n_shipname)

### Get matches by ssvid
# Join by id number - 4 matching vessels, all appear to be a match
iuu_by_ssvid <- vessels_for_matching %>%
    inner_join(iuu, by = c("ssvid"="iuu_ssvid"))

iuu_matching_vessels <- iuu_matching_vessels %>%
  bind_rows(iuu_by_ssvid %>% distinct(ssvid, flag, broadcast_shipname))

### Get matches by call sign - 3 matching vessels, only two appear to be a match
iuu_by_callsign <- vessels_for_matching %>%
    inner_join(iuu %>% dplyr::filter(!is.na(iuu_callsign)), by = c("broadcast_callsign"="iuu_callsign"))

iuu_matching_vessels <- iuu_matching_vessels %>%
  bind_rows(iuu_by_callsign %>% distinct(ssvid, flag, broadcast_shipname) %>% dplyr::filter(broadcast_shipname != "ROSE4"))

### Get matches by IMO - 3 matching vessels, all appear to be enough for a match
iuu_by_imo <- vessels_for_matching %>%
    inner_join(iuu %>% dplyr::filter(!is.na(iuu_imo)), by = c("broadcast_imo"="iuu_imo"))

iuu_matching_vessels <- iuu_matching_vessels %>%
  bind_rows(iuu_by_imo %>% distinct(ssvid, flag, broadcast_shipname))

### Match by normalized shipname  - 52 matching records, most are not a match. 
iuu_by_name1 <- vessels_for_matching %>%
    inner_join(iuu %>% dplyr::filter(!is.na(iuu_shipname)), by = c("broadcast_shipname"="iuu_shipname")) %>%
  arrange(broadcast_shipname)

iuu_by_name2 <- vessels_for_matching %>%
    inner_join(iuu2 %>% dplyr::filter(!is.na(iuu_shipname)), by = c("broadcast_shipname"="iuu_shipname")) %>%
  arrange(broadcast_shipname)

# Manually determined matches
name_matches1 <- iuu_by_name1 %>%
  dplyr::filter(broadcast_shipname %in% c("EPHRAEEM", "HUALI8", "SHUNCHANG3"))

name_matches2 <- iuu_by_name2 %>%
  dplyr::filter(broadcast_shipname %in% c("HAILUNG", "HUALI8", "MYSMARII"))

iuu_matching_vessels <- iuu_matching_vessels %>%
  bind_rows(name_matches1 %>% distinct(ssvid, flag, broadcast_shipname)) %>%
  bind_rows(name_matches2 %>% distinct(ssvid, flag, broadcast_shipname))

# Get all matches - 7 vessels
iuu_matches <- iuu_matching_vessels %>%
  distinct(ssvid)

# Apply to vessel list
temp_vessel_list <- temp_vessel_list %>%
  mutate(iuu1 = ifelse(ssvid %in% iuu_matches$ssvid, T, F))

```

## Overfished and Unassessed Stocks

### OA #1: Overfished as determined by the RAM legacy stock assessment database

```{r}
# Load costello data to get the fraction of catches by eez/fao region that are in RAM and are determined to be overfished
costello_2016_dat <- read_csv(costello_2016_path) %>%
  clean_names(case = "snake")

costello_2016_dat_clean <- costello_2016_dat %>%
  mutate(region_fao_chr = as.character(region_fao),
         n_regions = nchar(region_fao_chr)/2,
         region_fao_split = str_split(gsub("(.{2})", "\\1 ", region_fao_chr), " ")) %>%
  unnest(cols = c(region_fao_split)) %>%
  mutate(region_fao_split = as.numeric(region_fao_split)) %>%
  dplyr::filter(region_fao_split != "") %>%
  mutate(iso3 = case_when(country == "Channel Islands" ~ "JEY",
                          country == "Micronesia" ~ "FSM",
                          country == "Zanzibar" ~ "TZA",
                          TRUE ~ countrycode(country, "country.name", "iso3c")))

# Get EEZ regions for matching
eez_regions <- temp_vessel_list %>%
  distinct(eez_id, fao_region, territory1_iso3, territory2_iso3, territory3_iso3, sovereign1_iso3, sovereign2_iso3, sovereign3_iso3)

# Get RAM stocks only and summarize by iso3 and fao_region
ram_data <- costello_2016_dat_clean %>%
  dplyr::filter(dbase == "RAM") %>%
  group_by(iso3, region_fao_split) %>%
  summarize(n_stocks = n_distinct(id_orig),
            mean_bv_bmsy = mean(bv_bmsy),
            median_bv_bmsy = median(bv_bmsy)) %>%
  mutate(oa_mean = ifelse(mean_bv_bmsy >= 1, F, T),
         oa_med = ifelse(median_bv_bmsy >= 1, F, T),
         oa1 = ifelse(oa_mean & oa_med, T, F))

ram_by_eez_region <- eez_regions %>%
  left_join(ram_data, by = c("territory1_iso3" = "iso3", "fao_region" = "region_fao_split")) %>%
  arrange(eez_id, fao_region) %>%
  dplyr::select(eez_id, fao_region, oa1)
ram_by_eez_region$oa1[is.na(ram_by_eez_region$oa1)] <- F

# Join back to vessel list
temp_vessel_list <- temp_vessel_list %>%
  left_join(ram_by_eez_region, by = c("eez_id", "fao_region"))
```

### OA #2: Overfished as determined by Costello et al. (2016)

```{r}
# Include all stocks 
all_data <- costello_2016_dat_clean %>%
  group_by(iso3, region_fao_split) %>%
  summarize(n_stocks = n_distinct(id_orig),
            mean_bv_bmsy = mean(bv_bmsy),
            median_bv_bmsy = median(bv_bmsy)) %>%
  mutate(oa_mean = ifelse(mean_bv_bmsy >= 1, F, T),
         oa_med = ifelse(median_bv_bmsy >= 1, F, T),
         oa2 = ifelse(oa_mean & oa_med, T, F))

all_by_eez_region <- eez_regions %>%
  left_join(all_data, by = c("territory1_iso3" = "iso3", "fao_region" = "region_fao_split")) %>%
  arrange(eez_id, fao_region) %>%
  dplyr::select(eez_id, fao_region, oa2)
all_by_eez_region$oa2[is.na(all_by_eez_region$oa2)] <- F

# Join back to vessel list
temp_vessel_list <- temp_vessel_list %>%
  left_join(all_by_eez_region, by = c("eez_id", "fao_region"))
```

# Export final vessel list

```{r}
# Export final vessel list with definitions
write_csv(temp_vessel_list, paste0(results_dir, "vessel-list-2018-final.csv"))
write_csv(temp_vessel_list, paste0(app_dir, "vessel-list-2018-final.csv"))
```

### 2020-04-13 scripts/02_vessel_list.Rmd
still updating

@@
 
-We then need to get total catches and revenues per fishing KWh by flag and FAO region, as well as by flag.
+We then need to get total catches and revenues per fishing kWh by flag and FAO region, as well as by flag.
 We first will assign catch rates for FAO region/flag combinations that appear in both the GFW and FAO data.
-For FAO region/flag combinations that don't appear in the FAO data, we will allocate the remainder?
+For FAO region/flag combinations that don't appear in the FAO data, we will assign the overall rate by flag state.
 

### 2020-04-13 scripts/04_subsidy_reform_definitions.Rmd
still updating

@@
 # Directories for the output files generated by this script
-results_dir <- here::here("results", "5-vessel-list-policy-definitions/")
+results_dir <- here::here("results", "04_subsidy_reform_definitions/")
 if (dir.exists(results_dir) == F) {

### 2020-04-15 scripts/03_management.Rmd
management section updated

@@
 # Path to vessel list
-vessel_list_path <- here::here("results", "02-vessel-list", "vessel-list-2018-raw.csv")
+vessel_list_path <- here::here("results", "02-vessel-list", "vessel_list_2018_raw.csv")
 
-# Path to Management data
-melnychuk_2017_mgmt_dat_path <- here::here("data", "raw", "management", "Melnychuk_2017", "fmi_values_country.csv" )
+# Path to Melnychuk FMI data
+melnychuk_2017_mgmt_dat_path <- here::here("data", "edited", "melnychuk_et_al_2017_fmi_tidy.csv" )
+
+# Path to Costello upsides data
+costello_2016_upsides_dat_path <- here::here("data", "edited", "costello_et_al_2016_upsides_tidy.csv")
 
 # Make figures?
-make_plots <- T
+make_plots <- F
 
@@
 # Directories for the output files generated by this script
-results_dir <- here::here("results", "2-management/")
+results_dir <- here::here("results", "03-management/")
 if (dir.exists(results_dir) == F) {
@@
 
-# Assign regions to vessels
+# Get EEZ info from vessel list
 
@@
 
-# Match fishing areas to management indices
+```{r}
+# Get eez codes and cooresponding territories/sovereigns
+eez_info <- vessel_list_raw %>%
+  group_by(eez_id) %>%
+  distinct(eez_territory1_iso3, eez_territory2_iso3, eez_territory3_iso3, eez_sovereign1_iso3, eez_sovereign2_iso3, eez_sovereign3_iso3)
+
+# Tidy eez data
+eez_info_tidy <- eez_info %>%
+  mutate(n_states = case_when((is.na(eez_territory2_iso3) & is.na(eez_territory3_iso3)) ~ 1,
+                            (!is.na(eez_territory2_iso3) & is.na(eez_territory3_iso3)) ~ 2,
+                            TRUE ~ 3)) %>%
+  mutate(eez_territory_iso3 = case_when(n_states == 1 ~ c(eez_territory1_iso3),
+                                   n_states == 2 ~ paste(eez_territory1_iso3, eez_territory2_iso3, sep = " "),
+                                   n_states == 3 ~ paste(eez_territory1_iso3, eez_territory2_iso3, eez_territory3_iso3, sep = " ")),
+         eez_sovereign_iso3 = case_when(n_states == 1 ~ c(eez_sovereign1_iso3),
+                                   n_states == 2 ~ paste(eez_sovereign1_iso3, eez_sovereign2_iso3, sep = " "),
+                                   n_states == 3 ~ paste(eez_sovereign1_iso3, eez_sovereign2_iso3, eez_sovereign3_iso3, sep = " "))) %>%
+  dplyr::select(eez_id, eez_territory_iso3, eez_sovereign_iso3) %>%
+  mutate(territory_split = map(eez_territory_iso3, ~ str_split(.x, " ")[[1]]),
+         sovereign_split = map(eez_sovereign_iso3, ~ str_split(.x, " ")[[1]])) %>%
+  unnest(cols = c(territory_split, sovereign_split)) %>%
+  dplyr::select(eez_id, eez_territory_iso3 = territory_split, eez_sovereign_iso3 = sovereign_split)
+
+eez_info_tidy$eez_sovereign_iso3[eez_info_tidy$eez_id == 49003] <- "CHN"
+```
+
+# Management Scores from FMI indices
+
+## Assign FMI indicies to regions
 
@@
 melnychuk_2017_mgmt_dat <- read_csv(melnychuk_2017_mgmt_dat_path) %>%
-  clean_names(case = "snake") %>%
-  mutate(iso3 = countrycode(country, "country.name", "iso3c")) %>%
-  dplyr::select(iso3, fmi_weighted)
+  dplyr::filter(variable == "fmi_weighted")
 
-# Get eez codes and matching territories
-eez_info <- vessel_list_raw %>%
-  group_by(eez_id) %>%
-  distinct(territory1_iso3, territory2_iso3, territory3_iso3, sovereign1_iso3, sovereign2_iso3, sovereign3_iso3)
+# Load country lookup
+country_dependencies <- read_csv(here::here("data", "lookup-tables", "country_dependencies.csv"))
 
-# Tidy eez data
-eez_info_tidy <- eez_info %>%
-  mutate(states = case_when((is.na(territory2_iso3) & is.na(territory3_iso3)) ~ 1,
-                            (!is.na(territory2_iso3) & is.na(territory3_iso3)) ~ 2,
-                            TRUE ~ 3)) %>%
-  mutate(territory_iso = case_when(states == 1 ~ c(territory1_iso3),
-                                   states == 2 ~ paste(territory1_iso3, territory2_iso3, sep = " "),
-                                   states == 3 ~ paste(territory1_iso3, territory2_iso3, territory3_iso3, sep = " ")),
-         sovereign_iso = case_when(states == 1 ~ c(sovereign1_iso3),
-                                   states == 2 ~ paste(sovereign1_iso3, sovereign2_iso3, sep = " "),
-                                   states == 3 ~ paste(sovereign1_iso3, sovereign2_iso3, sovereign3_iso3, sep = " "))) %>%
-  dplyr::select(eez_id, territory_iso, sovereign_iso) %>%
-  mutate(territory_split = map(territory_iso, ~ str_split(.x, " ")[[1]]),
-         sovereign_split = map(sovereign_iso, ~ str_split(.x, " ")[[1]])) %>%
-  unnest(cols = c(territory_split, sovereign_split)) %>%
-  dplyr::select(eez_id, territory_iso3 = territory_split, sovereign_iso3 = sovereign_split)
-
-eez_info_tidy$sovereign_iso3[eez_info_tidy$eez_id == 49003] <- "CHN"
-```
-
-```{r}
 # EU countries
-#Belgium, Bulgaria, Croatia, Cyprus, Denmark, Estonia, Finland, France, Germany, Greece, Ireland, Italy, Latvia, Lithuania, Malta, Netherlands, Poland, Portugal, Romania, Slovenia, Spain, Sweden, United Kingdom
-eu_countries <- c("BEL", "BGR", "HRV", "CYP", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "IRL", "ITA", "LVA", "LTU", "MLT", "NLD", "POL", "PRT", "ROU", "SVN", "ESP", "SWE", "GBR")
-
-# Dutch overseas territories: Aruba, Bonaire/St. Eustatius/Saba, Curacao, Sint Maarten
-dutch_territories <- c("ABW", "BES", "CUW", "SXM")
-
-# French overseas territories: French Guiana, French Polynesia, French Southern and Antarctic Territories, Guadeloupe, Martinique, Mayotte, New Caledonia, Reunion, Saint Barthelemy, Saint Martin, St.
-Pierre and Miquelon, Wallis and Futuna Islands
-french_territories <- c("GUF", "PYF", "ATF", "GLP", "MTQ", "MYT", "NCL", "REU", "BLM", "MAF", "SPM", "WLF")
-
-# Danish overseas territories: Faroe Islands, Greenland
-danish_territories <- c("FRO", "GRL")
-
-# British overseas territories: Anguilla, Ascension island, Bermuda, Cayman Islands, Falkland Islands, Guernsey, Gibraltar, British Indian Ocean Territories, Jersey, Monserratt, Pitcairn Island, South Georgia and the South Sandwich Islands, Saint Helena/Ascension/Tristan da Cunha, Tristan da Cunha, Turks and Caicos Islands, British Virgin Islands
-uk_territories <- c("AIA","ASC","BMU","CYM","FLK","GGY","GIB","IOT","JEY","MSR","PCN","SGS","SHN","TAA","TCA","VGB")
-
-eu_territories <- c(dutch_territories, french_territories, danish_territories, uk_territories)
-
-# Norwegian overseas territories: Bouvet Islands, Svalbard and Jan Mayen Islands
-norwegian_territories <- c("BVT", "SJM")
-
-# US overseas territories:  American Samoa, Guam, Northern Marianas Islands, Puerto Rico, US Virgin Islands
-us_territories <- c("ASM", "GUM", "MNP", "PRI", "VIR")
+eu_countries <- country_dependencies$iso3[country_dependencies$is_EU]
+eu_territories <- country_dependencies$iso3[country_dependencies$sovereign_iso3 %in% eu_countries & country_dependencies$is_overseas_territory]
 ```
@@
   group_by(region) %>%
-  summarize(fmi_weighted_region = mean(fmi_weighted))
+  summarize(fmi_weighted_region = mean(value)) %>%
+  na.omit()
 
@@
 eu_management_index <- melnychuk_2017_mgmt_dat %>%
-  dplyr::filter(iso3 %in% c(eu_countries, eu_territories)) %>%
-  summarize(fmi_weighted_eu = mean(fmi_weighted))
+  dplyr::filter(iso3 == "EU")
 
-eu_df <- tibble(iso3 = c(eu_countries, eu_territories), fmi_weighted_eu = eu_management_index$fmi_weighted_eu)
+eu_df <- tibble(iso3 = c(eu_countries, eu_territories), fmi_weighted_eu = eu_management_index$value)
 
@@
   group_by(continent) %>%
-  summarize(fmi_weighted_continent = mean(fmi_weighted))
+  summarize(fmi_weighted_continent = mean(value)) %>%
+  na.omit()
 
@@
 eez_management_indices <- eez_info_tidy %>%
-  mutate(territory_region = countrycode(territory_iso3, "iso3c", "region"),
-         sovereign_region = countrycode(sovereign_iso3, "iso3c", "region"),
-         continent = countrycode(territory_iso3, "iso3c", "continent")) %>%
-  left_join(melnychuk_2017_mgmt_dat, by = c("sovereign_iso3" = "iso3")) %>%
-  left_join(eu_df, by = c("territory_iso3" = "iso3")) %>%
-  left_join(regional_management_indices, by = c("territory_region" = "region")) %>%
+  arrange(eez_sovereign_iso3) %>%
+  mutate(eez_territory_region = countrycode(eez_territory_iso3, "iso3c", "region"),
+         eez_sovereign_region = countrycode(eez_sovereign_iso3, "iso3c", "region"),
+         eez_continent = countrycode(eez_territory_iso3, "iso3c", "continent")) %>%
+  left_join(melnychuk_2017_mgmt_dat, by = c("eez_sovereign_iso3" = "iso3")) %>%
+  rename(fmi_weighted = value) %>%
+  dplyr::select(-variable) %>%
+  left_join(eu_df, by = c("eez_territory_iso3" = "iso3")) %>%
+  left_join(regional_management_indices, by = c("eez_territory_region" = "region")) %>%
   rename(fmi_weighted_region_territory = fmi_weighted_region) %>%
-  left_join(regional_management_indices, by = c("sovereign_region" = "region")) %>%
+  left_join(regional_management_indices, by = c("eez_sovereign_region" = "region")) %>%
   rename(fmi_weighted_region_sovereign = fmi_weighted_region) %>%
-  left_join(continent_management_indices, by = c("continent")) %>%
+  left_join(continent_management_indices, by = c("eez_continent" = "continent")) %>%
   mutate(fmi_best = case_when(!is.na(fmi_weighted) ~ fmi_weighted,
@@
                               !is.na(fmi_weighted_continent) ~ fmi_weighted_continent,
-                              TRUE ~ min(melnychuk_2017_mgmt_dat$fmi_weighted))) %>%
+                              TRUE ~ min(melnychuk_2017_mgmt_dat$value))) %>%
   group_by(eez_id) %>%
-  summarize(fmi_best = mean(fmi_best)) %>%
+  summarize(fmi_best = mean(fmi_best)) %>% # Necessary for disputed areas/joint regime areas
   ungroup()
 
-# Plot distribution by region curiousity
-# ggplot(eez_management_indices, aes(x = fmi_best, y = territory_region, group = territory_region)) +
-#   geom_density_ridges2()
-# 
-# ggplot(eez_management_indices, aes(x = fmi_best, y = continent, group = continent)) +
-#   geom_density_ridges2()
+```
+
+# Median fishing pressure by FAO region
+
+```{r}
+# Load costello stock status database
+costello_2016_upsides_dat <- read_csv(costello_2016_upsides_dat_path)
+
+# Median F/Fmsy by FAO region
+median_fvfmsy_fao <- costello_2016_upsides_dat %>%
+  group_by(region_fao_split) %>%
+  summarize(fvfmsy_med_region = median(fv_fmsy, na.rm = T),
+            fvfmsy_mean_region = mean(fv_fmsy, na.rm = T),
+            fvfmsy_w_mean_region = weighted.mean(fv_fmsy, w = msy, na.rm = T)) %>%
+  dplyr::select(fao_region = region_fao_split, fvfmsy_med_region)
+```
+
+# Median fishing pressure by FAO region and state
+
+```{r}
+# median_fvfmsy_fao_flag <- costello_2016_upsides_dat %>%
+#   group_by(iso3, region_fao_split) %>%
+#   summarize(fvfmsy_med_eez = median(fv_fmsy, na.rm = T),
+#             fvfmsy_mean_eez = mean(fv_fmsy, na.rm = T),
+#             fvfmsy_w_mean_eez = weighted.mean(fv_fmsy, w = msy, na.rm = T)) %>%
+#   dplyr::select(iso3, fao_region = region_fao_split, fvfmsy_med_eez)
+```
+
+# Proportion of formally assessed stocks by FAO region
+
+In order to include flag state, we would need to fix this one - How to treat "multinational" stocks. These should be attributed to all flag states that are fishing in those fisheries.
+
+```{r}
+prop_assessed_stocks <- costello_2016_upsides_dat %>%
+  group_by(region_fao_split) %>%
+  summarize(catch_ram = sum(catch[dbase == "RAM"]),
+            catch_other = sum(catch[dbase != "RAM"])) %>%
+  mutate(catch_prop_ram = catch_ram/(catch_ram + catch_other)) %>%
+  dplyr::select(fao_region = region_fao_split, catch_prop_ram)
+```
+
+# Proportion of catch share stocks by FAO region
+
+```{r}
+prop_catch_share_stocks <- costello_2016_upsides_dat %>%
+  group_by(region_fao_split) %>%
+  summarize(catch_share= sum(catch[catch_share == 1]),
+            catch_other = sum(catch[catch_share != 1])) %>%
+  mutate(catch_prop_cs= catch_share/(catch_share + catch_other)) %>%
+  dplyr::select(fao_region = region_fao_split, catch_prop_cs)
 ```
@@
 vessel_list_manage <- vessel_list_raw %>%
-  left_join((eez_management_indices %>% dplyr::select(eez_id, fmi_best)), by = c("eez_id"))
+  left_join(eez_management_indices, by = c("eez_id")) %>%
+  left_join(median_fvfmsy_fao, by = c("fao_region")) %>%
+  left_join(prop_assessed_stocks, by = c("fao_region")) %>%
+  left_join(prop_catch_share_stocks, by = c("fao_region"))
 
-management_quantile <- quantile(vessel_list_manage$fmi_best)
-managed <- management_quantile["75%"]
-openaccess <- management_quantile["25%"]
+# FAO region 18 is missing stock data, but has some effort
+vessel_list_manage$fvfmsy_med_region[is.na(vessel_list_manage$fvfmsy_med_region)] <- 1
+vessel_list_manage$catch_prop_ram[is.na(vessel_list_manage$catch_prop_ram)] <- 0
+vessel_list_manage$catch_prop_cs[is.na(vessel_list_manage$catch_prop_cs)] <- 0
 
-write_csv(vessel_list_manage, paste0(results_dir, "vessel-list-2018-management.csv"))
+write_csv(vessel_list_manage, paste0(results_dir, "vessel_list_2018_management.csv"))
+
+# Calculate management quantiles for each indicator
+fmi_quantile <- tibble("indicator" = "fmi") %>%
+  bind_cols(setNames(as.data.frame(matrix(quantile(vessel_list_manage$fmi_best), nrow = 1)), names(quantile(vessel_list_manage$fmi_best))))
+
+fvfmsy_quantile <- tibble("indicator" = "fvfmsy") %>%
+  bind_cols(setNames(as.data.frame(matrix(quantile(vessel_list_manage$fvfmsy_med_region), nrow = 1)), names(quantile(vessel_list_manage$fvfmsy_med_region))))
+
+catch_ram_quantile <- tibble("indicator" = "catch_prop_ram") %>%
+  bind_cols(setNames(as.data.frame(matrix(quantile(vessel_list_manage$catch_prop_ram), nrow = 1)), names(quantile(vessel_list_manage$catch_prop_ram))))
+
+catch_cs_quantile <- tibble("indicator" = "catch_prop_cs") %>%
+  bind_cols(setNames(as.data.frame(matrix(quantile(vessel_list_manage$catch_prop_cs), nrow = 1)), names(quantile(vessel_list_manage$catch_prop_cs))))
+
+indicator_quantiles <- fmi_quantile %>%
+  bind_rows(fvfmsy_quantile) %>%
+  bind_rows(catch_ram_quantile) %>%
+  bind_rows(catch_cs_quantile)
+
+write_csv(indicator_quantiles, paste0(results_dir, "management_indicator_quantiles.csv"))
 ```
@@
 
-## Average FMI by flag/fao region compared to total subsidy provision
+## Coorelation between average FMI by flag/fao region and subsidy provisioning
 
 ```{r}
-# FMI by flag from vessel list
+if(make_plots){
+
+# FMI by flag and FAO from vessel list
 fmi_flag_fao <- vessel_list_manage %>%
@@
   scale_x_continuous(labels = comma)
-```
 
-```{r}
 # FMI by flag from vessel list
@@
   scale_x_continuous(labels = comma)
-```
 
-```{r}
 countries_to_highlight <- c("CHN", "USA", "IDN", "JPN", "ISL", "THA")
@@
 ggsave(paste0(results_dir, "fmi_flag_melnychuk_allbad.png"), width = 7, height = 4.5, units = "in")
-```
 
-```{r}
 # Plot fuel subsidies only 
@@
 ggsave(paste0(results_dir, "fmi_flag_melnychuk_fuel.png"), width = 7, height = 4.5, units = "in")
+
+}
 ```

### 2020-04-16 scripts/04_model_parameterization.Rmd
pre-subdirectory attempt

---
output:
  html_document: default

title: "SubsidyExplorer - Step 3: Model Parameterization"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
bibliography: "../pew-subsidies.bib"

---

# Introduction

This script handles the preliminary data wrangling necessary to create the biological parameters for the bio-economic model underlying the SubsidyExplorer toolkit. It outputs two CSV files used by the SubsidyExplorer toolkit (located in `r here::here("WTOToolkit", "data")`): 
- model-parameters-global.csv
- model-parameters-regional.csv

```{r}
# Load packages
library(knitr) 
library(countrycode) # country name matching
library(janitor) # cleaning column names
library(readxl) # Load XLSX files
library(tidyverse)

# Path to Costello upsides data
costello_2016_upsides_dat_path <- here::here("data", "edited", "costello_et_al_2016_upsides_tidy.csv")

# Path to vessel list
vessel_list_path <- here::here("results", "03-management", "vessel_list_2018_management.csv")
```

In addition to the data sources described in the inital data wrangling script, we also draw on the folloing data sources:

- Bioeconomic model parameters from both of the World Bank's Sunken Billions Reports (2009 and 2017). 
> World Bank, & FAO. (2009). The Sunken Billions: The Economic Justification for Fisheries Reform. Retrieved from https://siteresources.worldbank.org/EXTARD/Resources/336681-1224775570533/SunkenBillionsFinal.pdf
> World Bank. (2017). The Sunken Billions Revisited: Progress and Challenges in Global Marine Fisheries. Retrieved from https://openknowledge.worldbank.org/handle/10986/24056

```{r setup, include=FALSE}
# Code options
knitr::opts_chunk$set(echo = FALSE, error = FALSE, message = FALSE, warning = F)

# Directories for the output files generated by this script
results_dir <- here::here("results", "3-model-parameterization/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}

app_dir <- here::here("app", "data/")
if (dir.exists(app_dir) == F) {
  dir.create(app_dir, recursive = T)
}

# Define regions 
region_names <- sort(c("atlantic", "indian", "pacific_e", "pacific_w"))

# Create a tidy df with the cooresponding fao regions
regions_tidy <- tibble(
  region = region_names,
  fao_region = list(c(21, 27, 37, 31, 34, 41, 47, 18, 48), c(51, 57, 58), c(67, 77, 87), c(61, 71, 81, 88))
) %>%
  unnest(cols = c(fao_region))

# Also create a blank tibble with regions as column names
regions_spread <- setNames(data.frame(matrix(ncol = length(region_names), nrow = 0)), region_names)

# Now make empty output tables for both our global parameters, and for our regional parameters
global_model_parameters <- tibble(parameter = character(0), value = numeric(0), source = character(0))

regional_model_parameters <- tibble(parameter = character(0), source = character(0)) %>%
  bind_cols(regions_spread)
```

```{r}
# Load data sets
# Load costello data
costello_2016_dat <- read_csv(costello_2016_path) %>%
  clean_names(case = "snake")

# Load vessel list
vessel_list_mgmt <- read.csv(vessel_list_path, stringsAsFactors = F)

# Create cutoffs determining which vessels are in which fleets
managed_cutoff <- quantile(vessel_list_mgmt$fmi_best, probs = seq(0,1,0.33))[3]

# Assign management criteria
vessel_list_out <- vessel_list_mgmt %>%
  mutate(fleet = case_when(fmi_best >= managed_cutoff ~ "managed",
                           TRUE ~ "open_access")) %>%
  left_join(regions_tidy, by = c("fao_region" = "fao_region"))

```

# Step 1: Biomass growth function

For our biomass growth function, $G(b)$, we use a form of the basic logistic surplus production model commonly referred to as the Pella-Tomlinson Model. With discrete units of time (hereafter years for the purposes of our model), biomass in the next year, $b_{t+1}$, is given by:

$$ b_{t+1} = b_{t} + \frac{\phi + 1}{\phi} r b_{t}\Bigg(1 - \bigg(\frac{b_{t}}{K}\bigg)^{\phi}\Bigg) - h_{t}$$
where $\phi$ is the Pella-Tomlinson parameter that allows for asymmetry in the production curve (centered on $phi = 1$), $r$ characterizes the intrinsic growth rate of the global stock, $K$ is the carrying capacity (maximum population size for growth to be positive), and $h_t$ is the total harvest in that year across all fleets.

Certain attributes of the Pella-Tomlinson biomass growth function relate its paramters to stock characteristics. For instance, $r$ can be calculated as

$$ r = \bigg(\frac{MSY}{K} \bigg) (\phi + 1)^{\frac{1}{\phi}} $$

where $MSY$ is the maximum sustinable yield of the stock, and $K$ is the carrying capacity of the stock.

We therefore need to estimate the following parameters for the biomass growth function: 
- $\phi$ : Pella-Tomlinson shape parameter (no units)
- $MSY$ : Global maximum sustainable yield (tons)
- $K$ : Global biomass carrying capacity (tons)
- $r$ : Global biomass intrinsic growth rate (no units)

The following parameters will be estimated prior to each model run:
- $b_0$ : Global biomass in the base year (tons)

<!-- ## Alternative form of the Pella-Tomlinson biomass growth function -->

<!-- The biomass growth function can also be written as: -->

<!-- $$ G(b) = \alpha b - \beta b^\phi $$ -->
<!-- where $\phi$ is the Pella-Tomlinson exponent dictating how skewed the growth curve is (centered on $\phi = 2$), $\alpha$ is the intrinsic growth rate, and $\beta$ is another parameter.  -->

<!-- In this case, $\alpha$ can be estimated as: -->

<!-- $$ \alpha = \bigg(\frac{MSY}{K}\bigg) \bigg(\frac{\phi^\frac{\phi}{\phi - 1}}{\phi - 1}\bigg) $$ -->

<!-- where $MSY$ is the maximum sustinable yield of the stock, and $K$ is the carrying capacity of the stock.  -->

<!-- Similarly, $\beta$ can be estimated as:  -->

<!-- $$ \beta = \bigg(\frac{MSY}{K^\phi}\bigg) \bigg(\frac{\phi^\frac{\phi}{\phi - 1}}{\phi - 1}\bigg) $$ -->

## Global biological parameters

We first parameterize our bio-economic model of fisheries subsidies reform globally.

We assume $\phi = 1.188$ based on literature for all (Thorson et al. 2012; World Bank 2017).

```{r}
# Phi
phi <- 0.188

# Add phi to parameter table
global_model_parameters <- global_model_parameters %>%
  bind_rows(tibble(parameter = "phi", value = phi, source = "Thorson et al. 2012"))
```

We then need to calculate $r$, for which we need both $MSY$ and $K$.

Many different estimates of the global marine $MSY$ exist, generally ranging between 80 and 115 million tons. Different sources have used different estimates: 
- The initial Sunken Billions report (World Bank and FAO 2009): 95 million tons
- Sumaila et al. 2012: 83 - 99 million tons
- Costello et al. 2012: 85 - 110 million tons
- The second Sunken Billions report (World Bank 2017): 102 million tons

For this analyis, we use the database of stock statuses for more than 4,000 fisheries (representing ~78% of global fisheries) created by Costello et al. (2016). MSY for our model is defined as the sum of the MSY of all stocks contained in this dataset, adjusted for the fraction of global biomass estimated to be represented by this data.

```{r}
# Calculate global MSY
global_msy <- sum(costello_2016_dat$msy)/0.78

# Add MSY to parameter table
global_model_parameters <- global_model_parameters %>%
  bind_rows(tibble(parameter = "MSY", value = global_msy, source = "Costello et al. 2016"))

```

We therefore assume that the global MSY is therefore equal to `r format(global_msy, big.mark = ",")` tons, which is comparable to the estimates used by other studies.

Very little is known about the global carrying capacity of fish stocks, though many studies have suggested that it is between 5 and 15 times the MSY for different species of fish. Again using the database of stock statuses created by Costello et al. (2016), we can obtain an estimate of global carrying capacity by summing the carrying capacities of all stocks contained in this dataset, adjusted for the fraction of global biomass estimated to be represented by this data.

```{r}
# One estimate of global carrying capacity
global_k <- sum(costello_2016_dat$k)/0.78
```

That yields a global carrying capacity equal to `r format(global_k, big.mark = ",")` tons, which is `r global_k/global_msy` times our estimate of global MSY. We not that this is  significantly higher than estimates of global carrying capacity used by other studies.

```{r}
# Add K to parameter table
global_model_parameters <- global_model_parameters %>%
  bind_rows(tibble(parameter = "K", value = global_k, source = "Costello et al. 2016"))
```

<!-- That yields a global carrying capacity equal to `r format(global_k, big.mark = ",")` tons, which is much closer to the estimate of 980 million tons used by the World Bank (2017) study.  -->

We can then use all three parameters to estimate the global intrinsic growth rate.

```{r}
# Calculate r
global_r <- (global_msy/global_k)*(phi+1)^(1/phi)

# Add r to parameter table
global_model_parameters <- global_model_parameters %>%
  bind_rows(tibble(parameter = "r", value = global_r, source = "Costello et al. 2016"))
```

```{r}
# # NEED TO FIX THIS
global_biomass <- global_k*0.306

# Add base year biomass to parameter table
# global_model_parameters <- global_model_parameters %>%
#   bind_rows(tibble(parameter = "B0", value = global_biomass, source = "Costello et al. 2016"))
```

## Regional biological parameters

We also apply our bio-economic model of fisheries subsidies reform on a regional basis. For this analysis, we have chosen to use five regions based loosly on the major ocean basins and using the FAO statistical regions as subdivisions as needed to further separate regions: Arctic (18), Atlantic and Mediterranean (21, 27, 31, 34, 37, 41, 47), Indian (51, 57), Eastern Pacific (67, 77, 87), Western Pacific (61, 71, 81), and Southern (48, 58, 88).

This regional breakdown was chosen with the goal of trying to reflect commonly used delimitations of the boundaries of the world's largest fish stocks. Regional characterizations used by other studies (see World Bank 2017) are often organized around continents and political boundaries, which is inherently problematic for fisheries as most of the world's major fish stocks straddle these boundaries. While our regional model has tried to overcome some of these problems by aggregating ocean areas with more similar physical characteristics, we aknowledge that our results by region are likely to be less dependable than our global results.

For the regional portion of our analysis, we needed to calculate all of the same model inputs used in the global model for each of our six regions.

First, we assume that $\phi$ remains constant across regions ($\phi = 1.188$, Thorson et al. 2012).

```{r}
# Apply phi regionally
regional_phi <- rep(phi, length = length(region_names))
names(regional_phi) <- region_names

# Add phi to the regional paramter table
regional_model_parameters <- regional_model_parameters %>%
  bind_rows(c("parameter" = "phi", "source" = "Thorson et al. 2012", regional_phi))
```

Then, regional values of MSY were estimated in the same way as for the global fishery. We summed the MSYs of all stocks in the FAO statistical areas comprising each region from Costello et al. 2016. In cases where stocks in this dataset were associated with multiple FAO statistical areas, we assume that the stock's MSY and carrying capacity is split evenly between areas.

```{r}
# Create new row for every FAO statistical region - For stocks spanning multiple fao statistical regions, we assume msy/carrying capacity is split equally between them. 
# In most cases this doesn't matter since we've defined our regions in a way where the entire stock is in the same region, even if it spans multiple fao statistical areas 
costello_2016_dat_edit <- costello_2016_dat %>%
  mutate(region_fao_chr = as.character(region_fao),
         n_regions = nchar(region_fao_chr)/2,
         region_fao_split = str_split(gsub("(.{2})", "\\1 ", region_fao_chr), " ")) %>%
  unnest(cols = c(region_fao_split)) %>%
  mutate(region_fao_split = as.numeric(region_fao_split)) %>%
  dplyr::filter(region_fao_split != "") %>%
  mutate(msy_new = msy/n_regions,
         k_new = k/n_regions,
         biomass_new = biomass/n_regions,
         catch_new = catch/n_regions) %>%
  left_join(regions_tidy, by = c("region_fao_split" = "fao_region"))

# Now aggregate by region
costello_regional_dat <- costello_2016_dat_edit %>%
  group_by(region) %>%
  summarize(msy = sum(msy_new, na.rm = T)/0.78,
            k = sum(k_new, na.rm = T)/0.78,
            price = median(price, na.rm = T),
            bv_bmsy = median(bv_bmsy, na.rm = T),
            biomass = sum(biomass_new, na.rm = T),
            catch = sum(catch_new, na.rm = T)) %>%
  arrange(region)

# Extract msy
regional_msy <- round(costello_regional_dat$msy)
names(regional_msy) <- region_names

# Add MSY to the regional paramter table
regional_model_parameters <- regional_model_parameters %>%
  bind_rows(c("parameter" = "MSY", "source" = "Costello et al. 2016", regional_msy))
```

We do the same for regional carrying capacities.

```{r}
# Extract carrying capacity
regional_k <- round(costello_regional_dat$k)
names(regional_k) <- region_names

# Add MSY to the regional paramter table
regional_model_parameters <- regional_model_parameters %>%
  bind_rows(c("parameter" = "K", "source" = "Costello et al. 2016", regional_k))
```

We then calculate regional growth rates using those values of MSY and K.

```{r}
# Calculate r regionally
regional_r <- (regional_msy/regional_k)*(regional_phi+1)^(1/regional_phi)

# Add r to parameter table
regional_model_parameters <- regional_model_parameters %>%
  bind_rows(c("parameter" = "r", "source" = "Costello et al. 2016", regional_r))
```

```{r}
# # NEED TO FIX THIS
regional_biomass <- regional_k * 0.306

# Add biomass to parameter table
# regional_model_parameters <- regional_model_parameters %>%
#   bind_rows(c("parameter" = "B0", "source" = "Costello et al. 2016", regional_biomass))
```

<!-- xxxxxxxxxxxxxxxxxxxx -->

# Step 2: Harvest function

Our harvest function, $Y(b,e)$, is really the sum of the individual harvest functions for our three fleet segments (managed, intermediate, and open-access). Harvest for each fleet in a given year, $h_{j,t}$, is represented by:

$$ h_{j,t} = q_{j} b_{t} e_{j,t} $$

where $q_j$ is a fleet specific catchability parameter, and $e_{j,t}$ is the fishing effort expended by that fleet that year. We estimate catchability directly for each fleet based on base year data by calculating $q_j$ as follows:

$$ q_{j} = \frac{h_{j,0}}{b_{0}*e_{j,0}} $$

The total harvest is therefore the sum of harvests across all fleets:

$$ h_{t} = \sum_{i=1}^{j} h_{j,t} $$

The following parameters are calculuated prior to every model run as they vary depending on the relative sizes of the fleet:
- $h_{j,0}$ : Base year harvest for each fleet (tons)
- $e_{j,0}$ : Base year effort for each fleet (kWh)
- $q_{j}$ : Catchability for each fleet (tons)

<!-- ## Global harvest parameters -->

<!-- We calculate base year harvest for each fleet based on total marine capture production (2017) from the FAO.  -->

```{r}
# Group by fleet and calculate base year harvest and effort for the global fleet
global_fleet <- vessel_list_out %>%
  group_by(fleet) %>%
  summarize(vessels = n_distinct(ssvid),
            fishing_KWh = sum(fishing_KWh_eez_fao, na.rm = T),
            catch = sum(catch, na.rm = T),
            revenue = sum(revenue, na.rm = T),
            bad_subs = sum(bad_subs, na.rm = T))

# Add base year harvest to parameter table
# global_model_parameters <- global_model_parameters %>%
#   bind_rows(tibble(parameter = "h0_managed", value = global_fleet$catch[global_fleet$fleet == "managed"], source = "FAO 2019"))
# global_model_parameters <- global_model_parameters %>%
#   bind_rows(tibble(parameter = "h0_oa", value = global_fleet$catch[global_fleet$fleet == "open_access"], source = "FAO 2019"))

```

Base gear effort for each fleet comes from GFW data (2018). Effort is given in units of kW hours, which is a combination of the hours spent engaged in fishing activity, and the engine capacity of the vessel in KW.

```{r}
# global_model_parameters <- global_model_parameters %>%
#   bind_rows(tibble(parameter = "e0_managed", value = global_fleet$fishing_KWh[global_fleet$fleet == "managed"], source = "GFW 2019"))
# global_model_parameters <- global_model_parameters %>%
#   bind_rows(tibble(parameter = "e0_oa", value = global_fleet$fishing_KWh[global_fleet$fleet == "open_access"], source = "GFW 2019"))
```

We then estimate catchability for both fleets using the equation listed above

```{r}
catchability_global <- global_fleet$catch/(global_biomass*global_fleet$fishing_KWh)

# global_model_parameters <- global_model_parameters %>%
#   bind_rows(tibble(parameter = "q_managed", value = catchability_global[1], source = "FAO 2019; GFW 2019"))
# global_model_parameters <- global_model_parameters %>%
#   bind_rows(tibble(parameter = "q_oa", value = catchability_global[2], source = "FAO 2019; GFW 2019"))
```

## Regional harvest paramters

We do the same process to calculate base year harvest and effort, but aggregate by fleet and region.

```{r}
# Assign regions
# vessel_list_out <- vessel_list_out %>%
#   left_join(regions_tidy, by = c("fao_region" = "fao_regions"))

# Group by fleet and calculate base year harvest and effort for the global fleet
regional_fleet <- vessel_list_out %>%
  group_by(region, fleet) %>%
  summarize(vessels = n_distinct(ssvid),
            fishing_KWh = sum(fishing_KWh_eez_fao, na.rm = T),
            catch = sum(catch, na.rm = T),
            revenue = sum(revenue, na.rm = T),
            bad_subs = sum(bad_subs, na.rm = T)) %>%
  arrange(region, fleet)

# Get harvest
regional_fleet_harvest <- regional_fleet %>%
  dplyr::select(region, fleet, catch) %>%
  spread(region, catch)

# Get effort
regional_fleet_effort <- regional_fleet %>%
  dplyr::select(region, fleet, fishing_KWh) %>%
  spread(region, fishing_KWh)

# Add base year harvest to parameter table
# regional_model_parameters <- regional_model_parameters %>%
#   bind_rows(c("parameter" = "h0_managed", "source" = "FAO 2019", unlist(regional_fleet_harvest[1,-1])))
# regional_model_parameters <- regional_model_parameters %>%
#   bind_rows(c("parameter" = "h0_oa", "source" = "FAO 2019", unlist(regional_fleet_harvest[2,-1])))
# 
# # Add base year effort to parameter table
# regional_model_parameters <- regional_model_parameters %>%
#   bind_rows(c("parameter" = "e0_managed", "source" = "GFW 2019", unlist(regional_fleet_effort[1,-1])))
# regional_model_parameters <- regional_model_parameters %>%
#   bind_rows(c("parameter" = "e0_oa", "source" = "GFW 2019", unlist(regional_fleet_effort[2,-1])))
```

Now we calculate catchability for each fleet regionally

```{r}
# Calculate catchability regionally
catchability_regional <- tibble(fleet = c("managed", "open_access"))

for(i in 2:ncol(regional_fleet_harvest)){

  out <- tibble(unlist(regional_fleet_harvest[,i])/(regional_biomass[i-1]*unlist(regional_fleet_effort[,i])))
  colnames(out) <- region_names[i-1]

  catchability_regional <- catchability_regional %>%
    bind_cols(out)

}
# Add catchability to parameter table
# regional_model_parameters <- regional_model_parameters %>%
#   bind_rows(c("parameter" = "q_managed", "source" = "FAO 2019; GFW 2019", unlist(catchability_regional[1,-1])))
# regional_model_parameters <- regional_model_parameters %>%
#   bind_rows(c("parameter" = "q_oa", "source" = "FAO 2019; GFW 2019", unlist(catchability_regional[2,-1])))

```

<!-- xxxxxxxxxxxxxxxxxxxx -->

# Step 3: Global fish demand

In order to allow the price of fish to change as a function of harvest, we introduce a demand function, $D(h)$, for fish, and we assume it is downward-sloping. Total harvest in a given year, $h_{t}$, gives rise to fish price, $p_t$, through the constant elasticity of demand function:

$$ p_{t} = \bigg(\frac{1}{\delta}\bigg)^{1/\epsilon} h_{t}^{1/\epsilon} $$

where $\epsilon$ is the constant elasticity of demand, and $\delta$ is a constant. We calculate the parameter $\delta$ using data from Costello et al. (2016) as follows:

$$ \delta = \frac{h_{2012}}{(p_{2012})^{\epsilon}}$$

We therefore need to estimate the following parameters for the demand function: 
- $\epsilon$ : price flexibility/constant elasticity of demand

The following parameters are calculated prior to each time step: 
- $\delta$ : price constant

## Global demand parameters

We assume that the price flexibility/elasticity ($\epsilon$) is equal to -1.15 based on Costello et al. (2016).

```{r}
# Global price flexibility
global_epsilon <- -1.15

# Add base year biomass to parameter table
global_model_parameters <- global_model_parameters %>%
  bind_rows(tibble(parameter = "epsilon", value = global_epsilon, source = "Costello et al. 2016"))
```

<!-- We can then calculate the price constant using 2012 data from Costello et al. (2016).  -->

```{r}
# Global price constant
global_price_wrangling <- costello_2016_dat %>%
  group_by(year) %>%
  summarize(price = median(price, na.rm = T),
            harvest = sum(catch, na.rm = T))

global_delta <- global_price_wrangling$harvest/(global_price_wrangling$price^global_epsilon)

# Add price constant to parameter table
# global_model_parameters <- global_model_parameters %>%
#   bind_rows(tibble(parameter = "delta", value = global_delta, source = "Costello et al. 2016"))
```

## Regional demand parameters

For the regional analysis, we assume that the price flexibility/elasticity ($\epsilon$) is equal to -1.15 for all regions based on Costello et al. (2016).

```{r}
# Regional price flexibility
regional_epsilon <- rep(-1.15, length = length(region_names))
names(regional_epsilon) <- region_names

# Add epsilon to parameter table
regional_model_parameters <- regional_model_parameters %>%
  bind_rows(c("parameter" = "epsilon", "source" = "Costello et al. 2016", regional_epsilon))
```

<!-- We then calculate the price constant for each region using 2012 data from Costello et al. (2016).  -->

```{r}
# Regional price constant
regional_delta <- costello_regional_dat$catch/(costello_regional_dat$price^regional_epsilon)

# Add price constant to parameter table
# regional_model_parameters <- regional_model_parameters %>%
#   bind_rows(c("parameter" = "delta", "source" = "Costello et al. 2016", regional_delta))
```

<!-- xxxxxxxxxxxxxxxxxxxx -->

# Step 4: Costs and Benefits

Our cost function, $C(e)$, assumes that each fleet's total costs ($c_{j,t}$) are a function of fishing effort in that time step ($e_{j,t}$) and a fleet-specific cost coefficient ($\alpha_{j}$):
$$ c_{j,t} = \alpha_{j}  e_{j,t}^{\beta}$$

where $\beta$ is a scalar cost parameter that determines the shape of the cost curve (i.e. how non-linear costs are). The cost coefficient $\alpha_{j}$ for each fleet is a function of how much each unit of effort is being subsidized for that fleet $s_{j,t}$. We estimate the costs for each fleet directly based on base year data by calculating $\alpha_{j}$ as follows: 
$$ \alpha_{j} = \frac{p_{0}h_{j,0} + s_{j,0} e_{j,0}}{(e_{j,0})^{\beta}}$$

Fisheries profits are then calculated as revenue less costs plus subsidies for each fleet, where revenue is the fish price $p_t$ times harvest $h_{j,t}$ and costs are calculated as above. Profits for each fleet in each year, $\pi_{j,t}$, are therefore equal to:

$$ \pi_{j,t} = p_{t} h_{j,t} - c_{j,t} + s_{j,t}e_{j,t} $$

where $s_{j,t}$ is the rate of subsidization (i.e. how much each unit of effort is being subsidized) for fleet $j$.

Effort in the next year, $e_{j,t+1}$, adjusts in response to profits differently for each of our two fleets:

1) For the managed fleet, we assume that effort is decoupled from costs, and therefore remains constant regardless of changes to profits:

$$ e_{M,t+1} = e_{M,t}$$

2) For the open-access fleet, we assume that effort is coupled to costs, and therefore adjusts in response to profits:

$$ e_{OA,t+1} = \eta \pi_{OA,t} + e_{OA,t}$$
where $\eta$ is a parameter that regulates the speed at which effort is able to enter and exit the fishery.

We therefore need to estimate the following parameters for the cost and profit functions:
- $\beta$ : scalar cost parameter
- $p_{0}$ : base year fish price ($/ton)
- $\eta$ : speed at which effort is able to enter/exis a fishery

The following parameters are estimated prior to the start of each model run as they depend on the relative sizes of the fleets:
- $s_{j,0}$ : base year rate of subsidization for each fleet ($/kWh)
- $\alpha_{j}$ : cost coefficient for each fleet

## Global cost parameters

For our global analysis, we assume that $\beta$ is equal to 1.3 (Costello et al. 2016).

```{r}
# Define global beta
global_beta <- 1.3

# Add to parameter table
global_model_parameters <- global_model_parameters %>%
  bind_rows(tibble(parameter = "beta", value = global_beta, source = "Costello et al. 2016"))
```

In order to calculate $\alpha$, we first need to determine fish price in the base year. We compare two alternatives - 1) using the median price from Costello et al. (2016) adjusted to 2018 US$, and 2) solving for price based on the observed base year harvest.

```{r}
# Calculate global base prices
global_base_price1 <- ((1/global_delta)^(1/global_epsilon))*(sum(global_fleet$catch)^(1/global_epsilon))

CPI_2012 <- 229.594  #BLS CPI All Items (Annual Ave), (BLS Series ID: CUUR0000SA0)
CPI_2018 <- 251.107  #BLS CPI All Items (Annual Ave), (BLS Series ID: CUUR0000SA0)

global_base_price2 <- global_price_wrangling$price * (CPI_2018/CPI_2012)
```

The second price looks a bit high (comparable global price estimates are in the range of $1200-1400 per ton), so we use the first.

```{r}
# Add to parameter table
global_model_parameters <- global_model_parameters %>%
  bind_rows(tibble(parameter = "p0", value = global_base_price1, source = "Costello et al. 2016"))
```

We then can calculate the rate of subsidization in the base year using the subsidy estimates from Sumaila et al.

```{r}
# Calculate global base subsidies
global_base_subsidies <- global_fleet$bad_subs/global_fleet$fishing_KWh

# Add to parameter table
# global_model_parameters <- global_model_parameters %>%
#   bind_rows(tibble(parameter = "s0_managed", value = global_base_subsidies[1], source = "Sumaila et al. 2019"))
# global_model_parameters <- global_model_parameters %>%
#   bind_rows(tibble(parameter = "s0_oa", value = global_base_subsidies[2], source = "Sumaila et al. 2019"))
```

And now we are able to estimate the cost coefficients for each fleet.

```{r}
# Calculate cost coefficients 
global_cost_coeff <- ((global_base_price1*global_fleet$catch) + (global_base_subsidies*global_fleet$fishing_KWh))/(global_fleet$fishing_KWh^global_beta)

# Add to parameter table
# global_model_parameters <- global_model_parameters %>%
#   bind_rows(tibble(parameter = "alpha_managed", value = global_cost_coeff[1], source = "Calculated"))
# global_model_parameters <- global_model_parameters %>%
#   bind_rows(tibble(parameter = "alpha_oa", value = global_cost_coeff[2], source = "Calculated"))
```

Finally, we assume that $\eta$ is equal to 0.1 based on literature (Costello et al. 2016).

```{r}
# Define global eta
global_eta <- 0.1

# Add to parameter table
global_model_parameters <- global_model_parameters %>%
  bind_rows(tibble(parameter = "eta", value = global_eta, source = "Calculated"))
```

## Regional cost parameters

As with the global analysis, we assume $\beta$ to be equal to 1.3 across all regions.

```{r}
# Define global beta
regional_beta <- rep(1.3, length = length(region_names))
names(regional_beta) <- region_names

# Add to parameter table
regional_model_parameters <- regional_model_parameters %>%
  bind_rows(c("parameter" = "beta", "source" = "Costello et al. 2016", regional_beta))
```

We then calculate price in the base year in the same way regionally

```{r}
# Calculate base price regionally
regional_catches_total <- regional_fleet_harvest %>%
  gather(region, catch, -1) %>%
  group_by(region) %>%
  summarize(catch = sum(catch)) %>%
  spread(region, catch)

regional_base_price1 <- ((1/regional_delta)^(1/regional_epsilon))*(unlist(regional_catches_total[1,])^(1/regional_epsilon))

# Add catchability to parameter table
regional_model_parameters <- regional_model_parameters %>%
  bind_rows(c("parameter" = "p0", "source" = "Calculated", regional_base_price1))

```

As well as the rate of subsidization by fleet and region in the base year

```{r}
# get subsidy rates regionally by fleet
# Get effort
regional_fleet_subs <- regional_fleet %>%
  dplyr::select(region, fleet, bad_subs) %>%
  spread(region, bad_subs)

subsidies_regional <- tibble(fleet = c("managed", "open_access"))

for(i in 2:ncol(regional_fleet_subs)){

  out <- tibble(unlist(regional_fleet_subs[,i])/unlist(regional_fleet_effort[,i]))
  colnames(out) <- region_names[i-1]

  subsidies_regional <- subsidies_regional %>%
    bind_cols(out)

}

# Add subsidy base to parameter table
# regional_model_parameters <- regional_model_parameters %>%
#   bind_rows(c("parameter" = "s0_managed", "source" = "Sumaila et al. 2019; GFW 2019", unlist(subsidies_regional[1,-1])))
# regional_model_parameters <- regional_model_parameters %>%
#   bind_rows(c("parameter" = "s0_oa", "source" = "Sumaila et al. 2019; GFW 2019", unlist(subsidies_regional[2,-1])))
```

So we estimate cost coefficients for each fleet

```{r}

cost_coeff_regional <- tibble(fleet = c("managed", "open_access"))

for(i in 2:ncol(regional_fleet_subs)){

  out <- tibble(
    ((regional_base_price1[i-1]*unlist(regional_fleet_harvest[,i])) + 
      (unlist(subsidies_regional[,i])*unlist(regional_fleet_effort[,i]))) /
      (unlist(regional_fleet_effort[,i])^regional_beta[i-1])
    )
  colnames(out) <- region_names[i-1]

  cost_coeff_regional <- cost_coeff_regional %>%
    bind_cols(out)

}

# Add subsidy base to parameter table
# regional_model_parameters <- regional_model_parameters %>%
#   bind_rows(c("parameter" = "alpha_managed", "source" = "Calculated", unlist(cost_coeff_regional[1,-1])))
# regional_model_parameters <- regional_model_parameters %>%
#   bind_rows(c("parameter" = "alpha_oa", "source" = "Calculated", unlist(cost_coeff_regional[2,-1])))

```

And we again assume $\eta$ to be equal to 0.1 across all regions

```{r}
regional_eta <- rep(0.1, length = length(region_names))
names(regional_eta) <- region_names

# Add subsidy base to parameter table
regional_model_parameters <- regional_model_parameters %>%
  bind_rows(c("parameter" = "eta", "source" = "Costello et al. 2016", regional_eta))
```

```{r}
# Save both parameter files
write_csv(global_model_parameters, paste0(results_dir, "global-model-parameters.csv"))
write_csv(global_model_parameters, paste0(app_dir, "global-model-parameters.csv"))

write_csv(regional_model_parameters, paste0(results_dir, "regional-model-parameters.csv"))
write_csv(regional_model_parameters, paste0(app_dir, "regional-model-parameters.csv"))

# Save vessel list
write_csv(vessel_list_out, paste0(results_dir, "vessel-list-2018-regions.csv"))
```

<!-- xxxxxxxxxxxxxxxxxxxx -->

### 2020-04-16 functions/MapMaker.R
adding effort data

@@ -1,565 +1,0 @@
-
-MapMaker <- function(data,
-                     res = "grid",
-                     x = NULL,
-                     x_limits = NULL,
-                     x_name = NULL,
-                     y = NULL,
-                     y_limits = NULL,
-                     y_name = NULL,
-                     fill,
-                     fill_var,
-                     fill_name,
-                     fill_breaks,
-                     fill_limits,
-                     fill_labels,
-                     land_sf = NULL,
-                     region_sf = NULL,
-                     eez_sf = NULL,
-                     file_name = "map",
-                     file_dir = here::here("results/"),
-                     plot_labels = NULL,
-                     fill_palette = "seq",
-                     fill_low = "#FFF5F0",
-                     fill_high = "#CB181D",
-                     fill_mid = NULL,
-                     fill_midpoint = NULL){
-  
-  ### Themes
-  dark_theme <- theme(panel.background = element_rect(fill = "black"),
-                     plot.background = element_rect(fill = "white"),
-                     legend.background=element_rect(fill="white"),
-                     legend.text = element_text(color = "black", size = 16),
-                     legend.title = element_text(color = "black", size = 16),
-                     legend.title.align = 1,
-                     legend.direction="horizontal",
-                     legend.position = "bottom",
-                     legend.justification = "center",
-                     axis.text = element_text(color = "white", size = rel(1)),
-                     panel.grid.major = element_blank(),
-                     axis.title.x = element_blank(),
-                     axis.text.x=element_blank(),
-                     axis.ticks.x=element_blank(),
-                     axis.title.y=element_blank(),
-                     axis.text.y=element_blank(),
-                     axis.ticks.y=element_blank())
-  
-  plot_theme <- theme_bw()+
-    theme(legend.text = element_text(color = "black", size = 16),
-          legend.title = element_text(color = "black", size = 16),
-          legend.title.align = 1,
-          legend.direction = "horizontal",
-          legend.position = "bottom",
-          legend.justification = "center",
-          axis.text = element_text(color = "black", size = rel(1)))
-  
-  ### Make land layer
-  land <- geom_sf(data=land_sf, color = "grey10", fill="grey30", size = 0.25)
-  
[…]

### 2020-04-24 scripts/04_model_parameterization.Rmd
gfw analysis updated

@@
 # Directories for the output files generated by this script
-results_dir <- here::here("results", "3-model-parameterization/")
+results_dir <- here::here("results", "04-model-parameterization/")
 if (dir.exists(results_dir) == F) {
@@
 # Define regions 
-region_names <- sort(c("atlantic", "indian", "pacific_e", "pacific_w"))
+region_names <- sort(c("atlantic_e", "atlantic_w", "indian", "pacific_e", "pacific_w", "polar"))
 
@@
   region = region_names,
-  fao_region = list(c(21, 27, 37, 31, 34, 41, 47, 18, 48), c(51, 57, 58), c(67, 77, 87), c(61, 71, 81, 88))
+  fao_region = list(c(27, 37, 34, 47), # atlantic east + med
+                    c(21, 31, 41), # atlantic west
+                    c(51, 57), # indian
+                    c(67, 77, 87), # pacific e
+                    c(61, 71, 81),# pacific w 
+                    c(18, 48, 58, 88)) # polar
 ) %>%
@@
 # Load costello data
-costello_2016_dat <- read_csv(costello_2016_path) %>%
-  clean_names(case = "snake")
+costello_2016_dat <- read_csv(costello_2016_upsides_dat_path)
 
@@
 
-# Create cutoffs determining which vessels are in which fleets
-managed_cutoff <- quantile(vessel_list_mgmt$fmi_best, probs = seq(0,1,0.33))[3]
-
-# Assign management criteria
+# Assign regions to vessels
 vessel_list_out <- vessel_list_mgmt %>%
-  mutate(fleet = case_when(fmi_best >= managed_cutoff ~ "managed",
-                           TRUE ~ "open_access")) %>%
   left_join(regions_tidy, by = c("fao_region" = "fao_region"))
 
+# Save updated vessel list
+write_csv(vessel_list_out, paste0(results_dir, "vessel_list_2018_regions.csv"))
 ```
@@
 
-For our biomass growth function, $G(b)$, we use a form of the basic logistic surplus production model commonly referred to as the Pella-Tomlinson Model.
-With discrete units of time (hereafter years for the purposes of our model), biomass in the next year, $b_{t+1}$, is given by:
+For our biomass growth function, $G(b)$, we use a form of the basic logistic surplus production model commonly referred to as the Pella-Tomlinson model.
+With discrete units of time (hereafter years for the purposes of our model), biomass in the next year, $b_{t+1}$, is described by:
 
-$$ b_{t+1} = b_{t} + \frac{\phi + 1}{\phi} r b_{t}\Bigg(1 - \bigg(\frac{b_{t}}{K}\bigg)^{\phi}\Bigg) - h_{t}$$
-where $\phi$ is the Pella-Tomlinson parameter that allows for asymmetry in the production curve (centered on $phi = 1$), $r$ characterizes the intrinsic growth rate of the global stock, $K$ is the carrying capacity (maximum population size for growth to be positive), and $h_t$ is the total harvest in that year across all fleets.
+$$ b_{t+1} = b_{t} + \frac{\phi + 1}{\phi} g b_{t}\Bigg(1 - \bigg(\frac{b_{t}}{K}\bigg)^{\phi}\Bigg) - h_{t}$$
+where $\phi$ is a scaling parameter, $g$ is the population growth rate, $K$ is the carrying capacity (maximum population size for growth to be positive), and $h_t$ is the total harvest in that year across all fleets.
 
-Certain attributes of the Pella-Tomlinson biomass growth function relate its paramters to stock characteristics. For instance, $r$ can be calculated as
+The intrinsic growth rate of the global stock ($r$) is given by: 
+$$r = \frac{\phi + 1}{\phi}g$$
 
-$$ r = \bigg(\frac{MSY}{K} \bigg) (\phi + 1)^{\frac{1}{\phi}} $$
+Certain attributes of the Pella-Tomlinson biomass growth function relate its parameters to stock characteristics. For instance, $g$ is equal to
 
+$$ g = \bigg(\frac{MSY}{K} \bigg) (\phi + 1)^{\frac{1}{\phi}} $$
 where $MSY$ is the maximum sustinable yield of the stock, and $K$ is the carrying capacity of the stock.
 
-We therefore need to estimate the following parameters for the biomass growth function: 
-- $\phi$ : Pella-Tomlinson shape parameter (no units)
+Maximum sustainable yield is therefore equal to: 
+$$MSY = \frac{gK}{(\phi + 1)^{\frac{1}{\phi}}} $$
+and the biomass cooresponding to MSY as: 
+$$B_{MSY} = \frac{K}{(\phi + 1)^{\frac{1}{\phi}}}$$
+
+$B_{MSY}/K$ is given by: 
+$$\frac{B_{MSY}}{K} = \frac{1}{(\phi + 1)^{\frac{1}{\phi}}}$$
+where a value of $\phi = 1$ makes this equation equal to the Schaefer model (production function is symmetrical).
+
+We therefore need to assign the following parameters for the biomass growth function: 
+- $\phi$ : Scaler parameter (no units)
 - $MSY$ : Global maximum sustainable yield (tons)
 - $K$ : Global biomass carrying capacity (tons)
-- $r$ : Global biomass intrinsic growth rate (no units)
-
-The following parameters will be estimated prior to each model run:
+- $r$ : Global biomass population growth rate (no units)
+- $h_0$: Total harvest in the base year (tons)
 - $b_0$ : Global biomass in the base year (tons)
 
-<!-- ## Alternative form of the Pella-Tomlinson biomass growth function -->
+### Alternate forms of the Pella-Tomlinson model
 
-<!-- The biomass growth function can also be written as: -->
+### Discrete
 
-<!-- $$ G(b) = \alpha b - \beta b^\phi $$ -->
-<!-- where $\phi$ is the Pella-Tomlinson exponent dictating how skewed the growth curve is (centered on $\phi = 2$), $\alpha$ is the intrinsic growth rate, and $\beta$ is another parameter.  -->
+The Sunken Billions reports also used a form of the Pella-Tomlinson model, though they defined it differently. The form of the model used there may be written as:
 
-<!-- In this case, $\alpha$ can be estimated as: -->
+$$ G(X) = r X - \beta X^{\gamma} $$
+where $X$ is biomass, $\gamma$ is the Pella-Tomlinson exponent that defines the skewness of the biomass growth function, $r$ is the intrinsic growth rate, and $\beta$ is a parameter.
 
-<!-- $$ \alpha = \bigg(\frac{MSY}{K}\bigg) \bigg(\frac{\phi^\frac{\phi}{\phi - 1}}{\phi - 1}\bigg) $$ -->
+In this form, values of $\gamma < 2$ skew the function to the left, values of $\gamma > 2$ skew the function to the right, and $\gamma = 2$ reproduces the Lotka-Volterra logistic function (Schaefer) model (symmetric).
+As $\gamma$ gets closer to 1, it converges on the Fox biomass growth function.
 
-<!-- where $MSY$ is the maximum sustinable yield of the stock, and $K$ is the carrying capacity of the stock.  -->
+$X_{MSY}/K \in [0.368,1]$ for $\gamma$ values ranging from unity to infinity.
+In general, there are biological reasons to expect this to occur at a value less than 0.5 cooreponding to a $\gamma < 2$.
+This ratio can be caclulated as:
 
-<!-- Similarly, $\beta$ can be estimated as:  -->
+$$\frac{X_{MSY}}{K} = \gamma^{\frac{1}{1-\gamma}}$$
 
-<!-- $$ \beta = \bigg(\frac{MSY}{K^\phi}\bigg) \bigg(\frac{\phi^\frac{\phi}{\phi - 1}}{\phi - 1}\bigg) $$ -->
+With this form of the model, carrying capacity ($K$) is given by:
+$$K = \bigg(\frac{r}{\beta}\bigg)^{\frac{1}{\gamma-1}} $$
+Maximum sustainable yield can then be calculated as:
+$$ MSY = r \bigg(\frac{\gamma-1}{\gamma}\bigg)\bigg(\frac{r}{\gamma\beta}\bigg)^{\frac{1}{\gamma-1}} $$
+and the biomass cooresponding to MSY as: 
+$$ X_{MSY} = \bigg(\frac{r}{\gamma\beta}\bigg)^{\frac{1}{\gamma-1}}$$
 
@@
 Very little is known about the global carrying capacity of fish stocks, though many studies have suggested that it is between 5 and 15 times the MSY for different species of fish.
-Again using the database of stock statuses created by Costello et al.
-(2016), we can obtain an estimate of global carrying capacity by summing the carrying capacities of all stocks contained in this dataset, adjusted for the fraction of global biomass estimated to be represented by this data.
+The estimate of global carrying capacity obtained by summing the respective carrying capacities all all stocks from Costello et al.
+(2016) is higher than this (22 times MSY).
+We therefore instead assume global carrying capacity to be equal to 9.1 times MSY as found in the second Sunken Billions report.
 
@@
 # One estimate of global carrying capacity
-global_k <- sum(costello_2016_dat$k)/0.78
+# global_k <- sum(costello_2016_dat$k)/0.78
+global_k <- global_msy*9.6
+
+# Add K to parameter table
+global_model_parameters <- global_model_parameters %>%
+  bind_rows(tibble(parameter = "K", value = global_k, source = "Costello et al. 2016; World Bank 2017"))
 ```
 
-That yields a global carrying capacity equal to `r format(global_k, big.mark = ",")` tons, which is `r global_k/global_msy` times our estimate of global MSY.
-We not that this is  significantly higher than estimates of global carrying capacity used by other studies.
-
-```{r}
-# Add K to parameter table
-global_model_parameters <- global_model_parameters %>%
-  bind_rows(tibble(parameter = "K", value = global_k, source = "Costello et al. 2016"))
-```
-
-<!-- That yields a global carrying capacity equal to `r format(global_k, big.mark = ",")` tons, which is much closer to the estimate of 980 million tons used by the World Bank (2017) study.  -->
-
-We can then use all three parameters to estimate the global intrinsic growth rate.
+We can then use all three parameters to estimate the global biomass intrinsic growth rate using the equation above.
 
@@
 
+A great deal of uncertainty exists about the total amount of biomass currently in our oceans.
+We therefore estimate total biomass in the base year (2018) by assuming an annual rate of biomass growth of 8 million mt/year (World Bank 2017).
+We then solve for the biomass in 2018 that would have yielded the observed harvest after accounting for the assummed rate of biomass growth ($\xi = 8000000$)  $b_{t+1} = b_t + \xi$
+
+$$ h_0+ \xi =\frac{\phi + 1}{\phi} r b_{0}\Bigg(1 - \bigg(\frac{b_{0}}{K}\bigg)^{\phi}\Bigg)$$
+
 ```{r}
-# # NEED TO FIX THIS
-global_biomass <- global_k*0.306
+# Calculate global total harvest
+global_h0 <- sum(vessel_list_out$catch, na.rm = T)
+
+# Add base year harvest to parameter table
+global_model_parameters <- global_model_parameters %>%
+  bind_rows(tibble(parameter = "h0", value = global_h0, source = "FAO 2019"))
+```
+
+```{r}
+# Estimation of starting biomass
+biomass_vec <- seq(0, 0.5*global_k, length.out = 2000)
+growth_approx <- (((phi+1)/phi)*global_r*biomass_vec*(1-((biomass_vec/global_k)^phi)))
+biomass_pos <- which.min(abs(growth_approx - (global_h0+8000000)))
+global_b0 <- biomass_vec[biomass_pos]
 
 # Add base year biomass to parameter table
-# global_model_parameters <- global_model_parameters %>%
-#   bind_rows(tibble(parameter = "B0", value = global_biomass, source = "Costello et al. 2016"))
+global_model_parameters <- global_model_parameters %>%
+  bind_rows(tibble(parameter = "B0", value = global_b0, source = "FAO 2019; World Bank 2017"))
 ```
@@
 We also apply our bio-economic model of fisheries subsidies reform on a regional basis.
-For this analysis, we have chosen to use five regions based loosly on the major ocean basins and using the FAO statistical regions as subdivisions as needed to further separate regions: Arctic (18), Atlantic and Mediterranean (21, 27, 31, 34, 37, 41, 47), Indian (51, 57), Eastern Pacific (67, 77, 87), Western Pacific (61, 71, 81), and Southern (48, 58, 88).
+For this analysis, we have chosen to use six regions based loosly on the major ocean basins and using the FAO statistical regions as subdivisions as needed to further separate regions: Atlantic Ocean (East) and Mediterranean [`r paste(regions_tidy$fao_region[regions_tidy$region == "atlantic_e"], collapse = ", ")`], Atlantic Ocean (West) [`r paste(regions_tidy$fao_region[regions_tidy$region == "atlantic_w"], collapse = ", ")`], Indian Ocean [`r paste(regions_tidy$fao_region[regions_tidy$region == "indian"], collapse = ", ")`], Pacific Ocean (East) [`r paste(regions_tidy$fao_region[regions_tidy$region == "pacific_e"], collapse = ", ")`], Pacific Ocean (West) [`r paste(regions_tidy$fao_region[regions_tidy$region == "pacific_w"], collapse = ", ")`], and Polar Oceans [`r paste(regions_tidy$fao_region[regions_tidy$region == "polar"], collapse = ", ")`].
 
@@
 ```{r}
-# Create new row for every FAO statistical region - For stocks spanning multiple fao statistical regions, we assume msy/carrying capacity is split equally between them. 
-# In most cases this doesn't matter since we've defined our regions in a way where the entire stock is in the same region, even if it spans multiple fao statistical areas 
-costello_2016_dat_edit <- costello_2016_dat %>%
-  mutate(region_fao_chr = as.character(region_fao),
-         n_regions = nchar(region_fao_chr)/2,
-         region_fao_split = str_split(gsub("(.{2})", "\\1 ", region_fao_chr), " ")) %>%
-  unnest(cols = c(region_fao_split)) %>%
-  mutate(region_fao_split = as.numeric(region_fao_split)) %>%
+# Calculate stats by region
+costello_2016_dat_regional <- costello_2016_dat %>%
   dplyr::filter(region_fao_split != "") %>%
-  mutate(msy_new = msy/n_regions,
-         k_new = k/n_regions,
-         biomass_new = biomass/n_regions,
-         catch_new = catch/n_regions) %>%
-  left_join(regions_tidy, by = c("region_fao_split" = "fao_region"))
-
-# Now aggregate by region
-costello_regional_dat <- costello_2016_dat_edit %>%
+  mutate(msy_new = (msy/0.78)/n_regions) %>%
+  left_join(regions_tidy, by = c("region_fao_split" = "fao_region")) %>%
   group_by(region) %>%
-  summarize(msy = sum(msy_new, na.rm = T)/0.78,
-            k = sum(k_new, na.rm = T)/0.78,
-            price = median(price, na.rm = T),
-            bv_bmsy = median(bv_bmsy, na.rm = T),
-            biomass = sum(biomass_new, na.rm = T),
-            catch = sum(catch_new, na.rm = T)) %>%
+  summarize(msy = sum(msy_new, na.rm = T),
+            price = median(price, na.rm = T)) %>%
   arrange(region)
@@
 # Extract msy
-regional_msy <- round(costello_regional_dat$msy)
+regional_msy <- round(costello_2016_dat_regional$msy)
 names(regional_msy) <- region_names
@@
 
-We do the same for regional carrying capacities.
+We estimate regional carrying capacities again by assuming K to be 9.6 times MSY.
 
@@
 # Extract carrying capacity
-regional_k <- round(costello_regional_dat$k)
-names(regional_k) <- region_names
+regional_k <- regional_msy*9.6
 
@@
 regional_model_parameters <- regional_model_parameters %>%
-  bind_rows(c("parameter" = "K", "source" = "Costello et al. 2016", regional_k))
+  bind_rows(c("parameter" = "K", "source" = "Costello et al. 2016; World Bank 2017", regional_k))
 ```
@@
 ```{r}
-# # NEED TO FIX THIS
-regional_biomass <- regional_k * 0.306
+# Calculate global total harvest
+regional_h0 <- (vessel_list_out %>%
+  group_by(region) %>%
+  summarize(catch = round(sum(catch, na.rm = T))))$catch
+names(regional_h0) <- region_names
 
-# Add biomass to parameter table
-# regional_model_parameters <- regional_model_parameters %>%
-#   bind_rows(c("parameter" = "B0", "source" = "Costello et al. 2016", regional_biomass))
+# Add base year harvest to parameter table
+regional_model_parameters <- regional_model_parameters %>%
+  bind_rows(c("parameter" = "h0", "source" = "FAO 2019", regional_h0))
+```
+
+```{r}
+#Estimate starting biomass
+regional_b0 <- numeric(length(region_names))
+regional_biomass_growth <- c(4.1e6, 8e6, -2e6, 2.3e6, 2.3e6, -2e6)
+
+for(i in 1:length(regional_h0)){
+  biomass_vec <- seq(0, regional_k[i], length.out = 10000)
+  growth_approx <- (((regional_phi[i]+1)/regional_phi[i])*regional_r[i]*biomass_vec*(1-((biomass_vec/regional_k[i])^regional_phi[i])))
+  biomass_pos <- which.min(abs(growth_approx - (regional_h0 + regional_biomass_growth[i])))
+  regional_b0[i] <- biomass_vec[biomass_pos] 
+}
+names(regional_b0) <- region_names
+
+# Add base year biomass to parameter table
+regional_model_parameters <- regional_model_parameters %>%
+  bind_rows(c("parameter" = "b0", "source" = "FAO 2019; World Bank 2017", regional_b0))
 ```
@@
 
-<!-- ## Global harvest parameters -->
+## Global harvest parameters
 
-<!-- We calculate base year harvest for each fleet based on total marine capture production (2017) from the FAO.  -->
+Though we don't calculate the fleet specific parameters here, we have already calculated total harvest in the base year, and can calculate total fishing effort.
+This data comes from GFW data (2018).
+Effort is given in units of kWh, which is the product of the hours spent engaged in fishing activity, and the engine capacity of the vessel in kW
 
@@
 # Group by fleet and calculate base year harvest and effort for the global fleet
-global_fleet <- vessel_list_out %>%
-  group_by(fleet) %>%
-  summarize(vessels = n_distinct(ssvid),
-            fishing_KWh = sum(fishing_KWh_eez_fao, na.rm = T),
-            catch = sum(catch, na.rm = T),
-            revenue = sum(revenue, na.rm = T),
-            bad_subs = sum(bad_subs, na.rm = T))
+global_e0 <- sum(vessel_list_out$fishing_KWh_eez_fao_ter, na.rm = T)
 
-# Add base year harvest to parameter table
-# global_model_parameters <- global_model_parameters %>%
-#   bind_rows(tibble(parameter = "h0_managed", value = global_fleet$catch[global_fleet$fleet == "managed"], source = "FAO 2019"))
-# global_model_parameters <- global_model_parameters %>%
-#   bind_rows(tibble(parameter = "h0_oa", value = global_fleet$catch[global_fleet$fleet == "open_access"], source = "FAO 2019"))
-
-```
-
-Base gear effort for each fleet comes from GFW data (2018).
-Effort is given in units of kW hours, which is a combination of the hours spent engaged in fishing activity, and the engine capacity of the vessel in KW.
-
-```{r}
-# global_model_parameters <- global_model_parameters %>%
-#   bind_rows(tibble(parameter = "e0_managed", value = global_fleet$fishing_KWh[global_fleet$fleet == "managed"], source = "GFW 2019"))
-# global_model_parameters <- global_model_parameters %>%
-#   bind_rows(tibble(parameter = "e0_oa", value = global_fleet$fishing_KWh[global_fleet$fleet == "open_access"], source = "GFW 2019"))
-```
-
-We then estimate catchability for both fleets using the equation listed above
-
-```{r}
-catchability_global <- global_fleet$catch/(global_biomass*global_fleet$fishing_KWh)
-
-# global_model_parameters <- global_model_parameters %>%
-#   bind_rows(tibble(parameter = "q_managed", value = catchability_global[1], source = "FAO 2019; GFW 2019"))
-# global_model_parameters <- global_model_parameters %>%
-#   bind_rows(tibble(parameter = "q_oa", value = catchability_global[2], source = "FAO 2019; GFW 2019"))
+# Add base year effort to parameter table
+global_model_parameters <- global_model_parameters %>%
+  bind_rows(tibble(parameter = "e0", value = global_e0, source = "GFW 2019"))
 ```
@@
 
-We do the same process to calculate base year harvest and effort, but aggregate by fleet and region.
+We do the same process to calculate base year total effort by region
 
 ```{r}
-# Assign regions
-# vessel_list_out <- vessel_list_out %>%
-#   left_join(regions_tidy, by = c("fao_region" = "fao_regions"))
-
 # Group by fleet and calculate base year harvest and effort for the global fleet
 regional_fleet <- vessel_list_out %>%
-  group_by(region, fleet) %>%
+  group_by(region) %>%
   summarize(vessels = n_distinct(ssvid),
-            fishing_KWh = sum(fishing_KWh_eez_fao, na.rm = T),
-            catch = sum(catch, na.rm = T),
-            revenue = sum(revenue, na.rm = T),
+            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
             bad_subs = sum(bad_subs, na.rm = T)) %>%
-  arrange(region, fleet)
-
-# Get harvest
-regional_fleet_harvest <- regional_fleet %>%
-  dplyr::select(region, fleet, catch) %>%
-  spread(region, catch)
+  arrange(region)
 
 # Get effort
-regional_fleet_effort <- regional_fleet %>%
-  dplyr::select(region, fleet, fishing_KWh) %>%
-  spread(region, fishing_KWh)
+regional_e0 <- regional_fleet$fishing_KWh
+names(regional_e0) <- region_names
 
-# Add base year harvest to parameter table
-# regional_model_parameters <- regional_model_parameters %>%
-#   bind_rows(c("parameter" = "h0_managed", "source" = "FAO 2019", unlist(regional_fleet_harvest[1,-1])))
-# regional_model_parameters <- regional_model_parameters %>%
-#   bind_rows(c("parameter" = "h0_oa", "source" = "FAO 2019", unlist(regional_fleet_harvest[2,-1])))
-# 
-# # Add base year effort to parameter table
-# regional_model_parameters <- regional_model_parameters %>%
-#   bind_rows(c("parameter" = "e0_managed", "source" = "GFW 2019", unlist(regional_fleet_effort[1,-1])))
-# regional_model_parameters <- regional_model_parameters %>%
-#   bind_rows(c("parameter" = "e0_oa", "source" = "GFW 2019", unlist(regional_fleet_effort[2,-1])))
-```
-
-Now we calculate catchability for each fleet regionally
-
-```{r}
-# Calculate catchability regionally
-catchability_regional <- tibble(fleet = c("managed", "open_access"))
-
-for(i in 2:ncol(regional_fleet_harvest)){
-
-  out <- tibble(unlist(regional_fleet_harvest[,i])/(regional_biomass[i-1]*unlist(regional_fleet_effort[,i])))
-  colnames(out) <- region_names[i-1]
-
-  catchability_regional <- catchability_regional %>%
-    bind_cols(out)
-
-}
-# Add catchability to parameter table
-# regional_model_parameters <- regional_model_parameters %>%
-#   bind_rows(c("parameter" = "q_managed", "source" = "FAO 2019; GFW 2019", unlist(catchability_regional[1,-1])))
-# regional_model_parameters <- regional_model_parameters %>%
-#   bind_rows(c("parameter" = "q_oa", "source" = "FAO 2019; GFW 2019", unlist(catchability_regional[2,-1])))
-
+# Add base year effort to parameter table
+regional_model_parameters <- regional_model_parameters %>%
+  bind_rows(c("parameter" = "e0", "source" = "GFW 2019", regional_e0))
 ```
@@
 
-where $\epsilon$ is the constant elasticity of demand, and $\delta$ is a constant. We calculate the parameter $\delta$ using data from Costello et al. (2016) as follows:
+where $\epsilon$ is the constant elasticity of demand, and $\delta$ is a constant. We calculate the parameter $\delta$ using data as follows:
 
-$$ \delta = \frac{h_{2012}}{(p_{2012})^{\epsilon}}$$
+$$ \delta = \frac{h_{0}}{(p_{0})^{\epsilon}}$$
 
@@
 - $\epsilon$ : price flexibility/constant elasticity of demand
-
-The following parameters are calculated prior to each time step: 
-- $\delta$ : price constant
+- $p_0$: global price in the base year (2018)
 

### 2020-04-24 scripts/other-analyses/supplementary-gfw-datasets/gfw_dataset_for_pew.Rmd
gfw analysis updated

---
title: "GFW Dataset - Fishing effort by year, EEZ/high seas region, and flag state (2016-2019)"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: html_document
---

## Introduction

This script creates the a dataset of Global Fishing Watch (GFW) derived fishing activity in all EEZs of the world and on the high seas. It requires access to the non-public GFW data stored on BigQuery, as well as a valid Google Cloud Console billing account.

```{r, echo=F, error=F, message=F, warning=F}
# Load packages
library(knitr) 
library(countrycode) # country name matching
library(connections) # happy database viewing
library(bigrquery) # access Bigquery from R
library(tidyverse) # data wrangling

# Bigquery project
bq_project <-  "emlab-gcp"

# Create connection to emlab gcp
emlab_gcp_connection <- connection_open(
  bigquery(),
  project = "emlab-gcp",          # project you want to connect to
  dataset = "pew_subsidies",      # dataset we're working on
  billing = "emlab-gcp",          # Who's paying for this?
  use_legacy_sql = FALSE,         # Just don't
  allowLargeResults = TRUE        # Give me all the data
  )

# Create connection to gfw gcp
gfw_gcp_connection <- connection_open(
  bigquery(),
  project = "world-fishing-827",  # project you want to connect to
  dataset = "gfw_research",       # dataset we're working on
  billing = "emlab-gcp",          # Who's paying for this?
  use_legacy_sql = FALSE,         # Just don't
  allowLargeResults = TRUE        # Give me all the data
  )
```

```{r, echo=F, error=F, message=F, warning=F}
# Directories for the output files generated by this script
results_dir <- here::here("results", "supplementary-gfw-datasets/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}
```

## Extract good fishing vessels from existing vessel info table

This section describes the process of linking to the most recent version of the GFW vessel information table, and pulling information on all likely fishing vessels represented in that dataset. This process was last performed on `r format(Sys.time(), '%B %d, %Y')`.

The vessel info table we're using (`world-fishing-827.gfw_research.vi_ssvid_byyear_v20200115`) has all sorts of stuff in it, so there are some basic filters we need to apply.

First, we remove all transmissions from objects that are likely fishing gear (buoys, nets, etc.), rather than vessels.

Second, we apply a number of filters to remove ids associated with non-fishing, inactive, and spoofing vessels:

- MMSI must be on the best fishing vessel list
- MMSI cannot be used by 2+ vessels with different names simultaneously
- MMSI cannot be used by multiple vessels simultaneously for more than 3 days
- MMSI has not been found to be offsetting its position
- MMSI vessel class can be inferred by the neural net (i.e. it is an active vessel)
- MMSI was active for at least 1 day and fished for at least 1 hour in a year
- MMSI is associated with fewer than five shipnames

Finally, GFW has manually compiled a list of vessel IDs that are bad, so we exclude those.

```{r, echo=T, error=F, message=F, warning=F}
sql <- "WITH
  # This query identifies fishing vessels that meet annual quality criteria
  # e.g. not spoofing/offsetting/too many identities/etc.
  good_fishing_vessels AS (
  SELECT
      ssvid,
      year,
      best.best_vessel_class geartype,
      best.best_flag flag
    FROM
      `world-fishing-827.gfw_research.vi_ssvid_byyear_v20200410`
    WHERE
      on_fishing_list_best # MMSI must be on best fishing list
      AND (activity.overlap_hours_multinames = 0 OR activity.overlap_hours_multinames IS NULL) # MMSI cannot be used by 2+ vessels with different names simultaneously
      AND activity.overlap_hours < 24*3 # MMSI cannot be used by multiple vessels simultaneously for more than 3 days
      AND activity.offsetting IS FALSE # MMSI not offsetting position
      AND inferred.inferred_vessel_class_byyear IS NOT NULL # MMSI vessel class can be inferred by the neural net (active)
      # MMSI active for at least 1 days and fished for at least 1 hours in the year.
      AND activity.fishing_hours > 1
      AND activity.active_hours > 24*1
      AND 5 >= ( # MMSI associated with fewer than five shipnames
        SELECT
          COUNT(*)
        FROM (
          SELECT
            value,
            SUM(count) AS count
          FROM
            UNNEST(ais_identity.n_shipname)
          WHERE
            value IS NOT NULL
          GROUP BY
            value)
        WHERE
          count >= 10)
      AND ssvid NOT IN (
        SELECT
          ssvid
        FROM
          `ucsb-gfw.SubsidyExplorer.likely_gear`)),

  # This subquery identifies MMSI that offsett a lot in 2016
  nast_ssvid AS (
  SELECT
    ssvid,
    EXTRACT(year FROM last_timestamp) AS year,
    SUM( positions) positions
  FROM `world-fishing-827.gfw_research.pipe_v20190502_segs`
  WHERE
    (dist_avg_pos_sat_vessel_km > 3000 AND sat_positions_known > 5)
    AND first_timestamp < timestamp('2019-12-31')
    AND last_timestamp > timestamp('2016-01-01')
  GROUP BY 
    ssvid,
    year),

    # Extract vessels not on GFW's list of bad vessels
    good_fishing_vessels_2 AS (
      SELECT
        ssvid,
        year,
        geartype,
        flag
      FROM
        good_fishing_vessels
      WHERE
        CAST(ssvid AS int64) NOT IN (
          SELECT
            ssvid
          FROM
            `world-fishing-827.gfw_research.bad_mmsi`
          CROSS JOIN
            UNNEST(ssvid) AS ssvid)
    )

# Filter those ofsetting a lot are excluded and return
SELECT
  good_fishing_vessels_2.ssvid,
  good_fishing_vessels_2.year,
  geartype,
  flag
FROM
  good_fishing_vessels_2
LEFT JOIN
  nast_ssvid ON (good_fishing_vessels_2.ssvid = nast_ssvid.ssvid) AND (good_fishing_vessels_2.year = nast_ssvid.year)
WHERE 
  nast_ssvid.ssvid IS NULL"
```

```{r, echo=F, error=F, message=F, warning=F}
fv_table <- bq_table(project = bq_project, 
                     table = "all_good_fishing_vessels",
                     dataset = "pew_subsidies")

if(bq_table_exists(fv_table)){

  bq_table_delete(fv_table)
  bq_table_create(fv_table)
  bq_project_query(bq_project, 
                   sql, 
                   destination_table = fv_table, 
                   use_legacy_sql = FALSE, 
                   allowLargeResults = TRUE)

}else {
  bq_table_create(fv_table)
  bq_project_query(bq_project, 
                   query = sql, 
                   destination_table = fv_table,
                   use_legacy_sql = FALSE, 
                   allowLargeResults = TRUE)
}

fv_table_r <- tbl(emlab_gcp_connection, "all_good_fishing_vessels")
head(fv_table_r)

test <- fv_table_r %>%
  distinct(year)
```

## Extract fishing effort for good fishing vessels

We then extract the number of hours spent fishing by each of our good fishing vessels in different EEZs and/or FAO regions from the raw fishing effort table (`world-fishing-827.gfw_research.pipe_v20190502_fishing`). For fishing effort within an EEZ, we separate fishing effort happening within 12nm of land ("territorial fishing") versus that which happened more than 12nm from land.

To identify valid fishing effort, we apply the following filters:

- The fishing activity must have occured during a valid segment as identified by GFW.
- The fishing activity must have occured during a segment with more than 10 positions that was not concurrently overlapping with another, longer, segment for the same MMSI.  
- The vessel performing the fishing activity must appear on the list of good fishing vessels created above

We then extract a vessel table with the the following attributes:

- year (int): Year. Matches our data year specified above.
- eez_id (chr): EEZ identifier. 
- territory1_iso3 (chr) : Three letter code cooresponding to the administering territory of the EEZ
- territory2_iso3 (chr) : Three letter code cooresponding to the second administering territory of the EEZ (disputed areas only)
- territory3_iso3 (chr) : Three letter code cooresponding to the third administering territory of the EEZ (disputed areas only)
- sovereign1_iso3 (chr) : Three letter code cooresponding to the sovereign state of the EEZ
- sovereign2_iso3 (chr) : Three letter code cooresponding to the second sovereign state of the EEZ (disputed areas only)
- sovereign3_iso3 (chr) : Three letter code cooresponding to the third sovereign state of the EEZ (disputed areas only)
- is_territorial (bln): Did the fishing activity occur within 12nm of shore? (This is an approximation of a country's territorial waters)
- fao_region (int): Major FAO statistical region
- fishing_hours_eez_fao_ter: Total annual fishing hours in the specified territorial waters, EEZ, and/or FAO region by a single vessel 
- ssvid (chr): Unique vessel identification number given by GFW (MMSI number for most vessels)
- flag (chr): Best flag state of the vessel. 
- vessel_class (chr): Best vessel type. 
- length_m (dbl): Best vessel length in meters (m).
- tonnage_gt (dbl): Best vessel tonnage in gross tons (GT). 
- engine_power_kw (dbl): Best engine power in killowatt (kW). 
- broadcast_shipname (chr): Most common ship name broadcast by the vessel.
- broadcast_callsign (chr): Most common ship callsign broadcast by the vessel.
- broadcast_imo (chr): Most common imo number broadcast by the vessel.

For the aforementioned attributes, "best" means that GFW has determined that value to be the most reliable estimate based on some or all of the following (if available):

- information from an official vessel registry (1st priority)
- information broadcast directly by the vessel (2nd priority)
- predictions from convolutional neural network model (3rd priority)

```{r, echo=T, error=F, message=F, warning=F}
sql2 <- '
WITH
  # This subquery identifies good segments
  good_segments AS (
  SELECT
    seg_id
  FROM
    `world-fishing-827.gfw_research.pipe_v20190502_segs`
  WHERE
    good_seg
    AND positions > 10
    AND NOT overlapping_and_short),

  # This subquery identifies good fishing vessels from our previous query
  good_vessels AS (
  SELECT
    year,
    ssvid
  FROM
    `emlab-gcp.pew_subsidies.all_good_fishing_vessels`
  WHERE
    year IN (2016, 2017, 2018, 2019)),

  # This subquery identifies vessel information that we want to keep
  vessel_info AS (
  SELECT
    ssvid,
    year,
    best.best_flag as flag,
    best.best_vessel_class as vessel_class,
    best.best_length_m as length_m,
    best.best_tonnage_gt as tonnage_gt,
    best.best_engine_power_kw as engine_power_kw,
    ais_identity.n_shipname_mostcommon.value as broadcast_shipname,
    ais_identity.n_callsign_mostcommon.value as broadcast_callsign,
    ais_identity.n_imo_mostcommon.value as broadcast_imo
  FROM
    `world-fishing-827.gfw_research.vi_ssvid_byyear_v20200115`
  WHERE
    year IN (2016, 2017, 2018, 2019)),

  # This subquery identifies eez information that we want to keep
  eez_info AS (
  SELECT
    CAST(eez_id as string) as eez_id,
    reporting_name,
    territory1_iso3,
    territory2_iso3,
    territory3_iso3,
    sovereign1_iso3,
    sovereign2_iso3,
    sovereign3_iso3
  FROM
    `world-fishing-827.gfw_research.eez_info`),

  # This subquery gets all fishing effort by ssvid, eez, and fao region cooresponding to good segments and good vessels
  fishing_by_eez_and_fao_ter AS (
    SELECT
      EXTRACT(year FROM date) AS year,
      ssvid,
      if(ARRAY_LENGTH(regions.eez)=0, "0000", regions.eez[ordinal(1)]) AS eez_id,
      if(distance_from_shore_m <= 22224, TRUE, FALSE) AS is_territorial,
      if(ARRAY_LENGTH(regions.major_fao)=0, "0", regions.major_fao[ordinal(1)]) AS fao_region,
      sum(hours) AS fishing_hours_eez_fao_ter
    FROM
      `world-fishing-827.gfw_research.pipe_v20190502_fishing`
    WHERE
      date > timestamp("2016-01-01")
      AND date < timestamp("2019-12-31")
      AND ARRAY_LENGTH(regions.major_fao) > 0 # removes fishing inland
      AND nnet_score2 > .5
      AND seg_id IN (
        SELECT
          seg_id
        FROM
          good_segments)
    GROUP BY
      year,
      ssvid,
      eez_id,
      is_territorial,
      fao_region
    ORDER BY
      year,
      ssvid,
      fishing_hours_eez_fao_ter DESC),

  # This subquery extracts fishing effort only for good fishing vessels
  fishing_by_eez_and_fao_ter_good AS (
    SELECT
      fishing_by_eez_and_fao_ter.year,
      fishing_by_eez_and_fao_ter.ssvid,
      eez_id,
      is_territorial,
      fao_region,
      fishing_hours_eez_fao_ter
    FROM
      fishing_by_eez_and_fao_ter
    INNER JOIN
      good_vessels ON (good_vessels.ssvid = fishing_by_eez_and_fao_ter.ssvid) AND (good_vessels.year = fishing_by_eez_and_fao_ter.year))

SELECT
  *,
  fishing_hours_eez_fao_ter*engine_power_kw as fishing_KWh_eez_fao_ter
FROM
  fishing_by_eez_and_fao_ter_good
LEFT JOIN
  vessel_info
USING
  (ssvid,
  year)
LEFT JOIN
  eez_info
USING
  (eez_id)'
```

```{r, echo=F, error=F, message=F, warning=F}
effort_table <- bq_table(project = bq_project, 
                     table = "effort_good_fishing_vessels_2016_2019_raw",
                     dataset = "pew_subsidies")

if(bq_table_exists(effort_table)){

  bq_table_delete(effort_table)
  bq_table_create(effort_table)
  effort_good_fishing_vessels <- 
    bq_project_query(bq_project, 
                    sql2, 
                    destination_table = effort_table, 
                    use_legacy_sql = FALSE, 
                    allowLargeResults = TRUE) %>%
     bq_table_download()

}else {
  bq_table_create(effort_table)
  effort_good_fishing_vessels <- 
    bq_project_query(bq_project, 
                   query = sql2, 
                   destination_table = effort_table,
                   use_legacy_sql = FALSE, 
                   allowLargeResults = TRUE) %>%
    bq_table_download()
}

# Save
write_csv(effort_good_fishing_vessels, paste0(results_dir, "effort_good_fishing_vessels_2016_2019_raw.csv"))

```

## Manually aggregate certain non-contiguous EEZs

Marine Regions has separated most non-contiguous EEZs, so before we aggregate our dataset, we want to consolidate these into single units so that we are not double counting vessels (this would have no effect on other metrics of fishing effort, just distinct vessels). In reality, many of these EEZs that we're integrating are uninhabited islands (often protected areas) that see very little fishing activity.

We consider the following EEZs to encompass the subsidiaries listed below.

Austrailan EEZ (8323):

- Macquarie (8311)
- Heard and McDonald (8388)
- Christmas Island (8309)
- Cocos (Keeling) Islands (8308)
- Norfolk Island (8310)

Brazillian EEZ (8464):

- Trindade (8381)

Chillean EEZ (8465):

- San Felix (22756)
- Easter Island (21787)

Colombian EEZ (8426):

- Quita (33183)
- Serrana Bank (33184)
- Serranilla Bank (48984)
- Bajo Nuevo Bank (48985)

Ecuadorian EEZ (8431):

- Galapagos (8403)

Indian EEZ (8480):

- Andaman and Nicobar (8333)

Kiribati EEZ:

- Gilbert Islands (8488)
- Phoenix Islands (8450)
- Line Islands (8441)

Svalvard and Jan Mayen EEZ:

- Svalvard (33181)
- Jan Mayen (8437)

Portuguese EEZ (5688):

- Azores (8361)
- Madeira (8363)

United States EEZ (8456):

- Hawaii (8453)
- Alaska (8463)

Spanish EEZ (5693):

- Canary Islands (8364)

South African EEZ (8396):

- Prince Edward Island (8384)

We also create 19 high seas regions encompassing the high-seas portions of the FAO Major Fishing areas.

```{r, echo=F, error=F, message=F, warning=F}
# Create output dataset 
out <- effort_good_fishing_vessels
out$flag[out$flag == "Unknown"] <- "UNK"
out$flag[out$flag == "UNKNOWN"] <- "UNK"

out <- out %>%
  mutate(new_eez_id = case_when(eez_id %in% c("8311", "8388", "8309", "8308", "8310") ~ "8323",
                                eez_id %in% c("8381") ~ "8464",
                                eez_id %in% c("22756", "21787") ~ "8465",
                                eez_id %in% c("33183", "33184", "48984", "48985") ~ "8426",
                                eez_id %in% c("8403") ~ "8431",
                                eez_id %in% c("8333") ~ "8480",
                                eez_id %in% c("8450", "8441") ~ "8488",
                                eez_id %in% c("33181") ~ "8437",
                                eez_id %in% c("8661", "8363") ~ "5688",
                                eez_id %in% c("8453", "8463") ~ "8456",
                                eez_id %in% c("8364") ~ "5693", 
                                eez_id %in% c("8384") ~ "8396",
                                eez_id == "0000" ~ paste0("HS-", fao_region),
                                TRUE ~ eez_id),
         new_eez_name = case_when(new_eez_id == "8323" ~ "Australian Exclusive Economic Zone",
                                  new_eez_id == "8464" ~ "Brazilian Exclusive Economic Zone",
                                  new_eez_id == "8465" ~ "Chilean Exclusive Economic Zone",
                                  new_eez_id == "8426" ~ "Colombian Exclusive Economic Zone",
                                  new_eez_id == "8431" ~ "Ecuadorian Exclusive Economic Zone",
                                  new_eez_id == "8480" ~ "Indian Exclusive Economic Zone",
                                  new_eez_id == "8488" ~ "Kiribati Exclusive Economic Zone",
                                  new_eez_id == "8437" ~ "Svalvard and Jan Mayen Exclusive Economic Zone",
                                  new_eez_id == "5688" ~ "Portuguese Exclusive Economic Zone",
                                  new_eez_id == "8456" ~ "United States Exclusive Economic Zone",
                                  new_eez_id == "5693" ~ "Spanish Exclusive Economic Zone",
                                  new_eez_id == "8396" ~ "South African Exclusive Economic Zone",
                                  eez_id == "0000" ~ paste0("High Seas - FAO Fishing Area ", fao_region),
                                  TRUE ~ reporting_name)) %>%
  dplyr::select(-eez_id, -reporting_name) %>%
  rename(loc_id = new_eez_id,
         loc_name = new_eez_name)
  #dplyr::filter(loc_id != "8489") # this cooreponds to antarctica... Probably want to keep this in there.

out$loc_name[out$loc_id == "8489"] <- "Antarctic 200NM zone beyond the coastline"

```

## Aggregate by flag state

It's best for us to get vessel totals by flag state. Once we start aggregating by territorial waters/EEZ/high seas region, we're going to start double counting vessels. This table should help with that.

- year (int): year
- flag_iso3 (chr): ISO3 character code of the flag state of the vessel - "UNK" for unknown flag state
- vessels_n (int): number of unique vessels from this flag state
- fishing_h (num): total number of fishing hours (h)
- fishing_kwh (num): total number of fishing kilowatt hours (kWh)
- length_m_mean (num): mean vessel length (m)
- length_m_min (num): mininum vessel length (m)
- length_m_max (num): maximum vessel length (m)
- tonnage_gt_mean (num): mean vessel tonnage (gt)
- tonnage_gt_min (num): mininum vessel tonnage (gt)
- tonnage_gt_max (num): maximum vessel tonnage (gt)
- engine_power_kw_mean (num): mean vessel engine power (kw)
- engine_power_kw_min (num): mean vessel engine power (kw)
- engine_power_kw_max (num): mean vessel engine power (kw)

```{r, echo=F, error=F, message=F, warning=F}
# Aggregate
flag <- out %>%
  group_by(year,
           flag_iso3 = flag) %>%
  summarize(vessels_n = n_distinct(ssvid, na.rm = T),
            fishing_h = sum(fishing_hours_eez_fao_ter, na.rm = T),
            fishing_kwh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
            length_m_mean = mean(length_m, na.rm = T),
            length_m_min = min(length_m, na.rm = T),
            length_m_max = max(length_m, na.rm = T),
            tonnage_gt_mean = mean(tonnage_gt, na.rm = T),
            tonnage_gt_min = min(tonnage_gt, na.rm = T),
            tonnage_gt_max = max(tonnage_gt, na.rm = T),
            engine_power_kw_mean = mean(engine_power_kw, na.rm = T),
            engine_power_kw_min = min(engine_power_kw, na.rm = T),
            engine_power_kw_max = max(engine_power_kw, na.rm = T)) %>%
  arrange(year, flag_iso3)

# save
write_csv(flag_state, paste0(results_dir, "gfw_for_pew_totals_by_year_flag.csv"))
```

## Aggregate by EEZ and flag state

Now let's aggregate by EEZ/fao region and flag state (no distinction between territorial waters and not) By year, EEZ/region and flag state pairing, we calculate summary statistics and save the output dataset with the following attributes:

- year (int): year
- loc_id (chr): unique identifier for each EEZ and/or high seas region defined above
- loc_name (chr): name of each location
- loc_ter1_iso3 (chr): ISO3 character code of the administering territory - NA for high seas regions
- loc_sov1_iso3 (chr): ISO3 character code of the sovereign state - NA for high seas regions
- loc_ter2_iso3 (chr): ISO3 character code of the second administering territory - only in cases of joint regime or disputed areas, NA otherwise
- loc_sov2_iso3 (chr): ISO3 character code of the second sovereign state - only in cases of joint regime or disputed areas, NA otherwise
- loc_ter3_iso3 (chr): ISO3 character code of the third administering territory - only in cases of joint regime or disputed areas, NA otherwise
- loc_sov3_iso3 (chr): ISO3 character code of the third sovereign state - only in cases of joint regime or disputed areas, NA otherwise
- flag_iso3 (chr): ISO3 character code of the flag state of the vessel - "UNK" for unknown flag state
- vessels_n (int): number of unique vessels that fished there
- fishing_h (num): total number of fishing hours (h)
- fishing_kwh (num): total number of fishing kilowatt hours (kWh)
- length_m_mean (num): mean vessel length (m)
- length_m_min (num): mininum vessel length (m)
- length_m_max (num): maximum vessel length (m)
- tonnage_gt_mean (num): mean vessel tonnage (gt)
- tonnage_gt_min (num): mininum vessel tonnage (gt)
- tonnage_gt_max (num): maximum vessel tonnage (gt)
- engine_power_kw_mean (num): mean vessel engine power (kw)
- engine_power_kw_min (num): mean vessel engine power (kw)
- engine_power_kw_max (num): mean vessel engine power (kw)

```{r, echo=F, error=F, message=F, warning=F}
# Aggregate
eez <- out %>%
  group_by(year,
           loc_id,
           loc_name,
           loc_ter1_iso3 = territory1_iso3,
           loc_sov1_iso3 = sovereign1_iso3,
           loc_ter2_iso3 = territory2_iso3,
           loc_sov2_iso3 = sovereign2_iso3,
           loc_ter3_iso3 = territory3_iso3,
           loc_sov3_iso3 = sovereign3_iso3,
           flag_iso3 = flag) %>%
  summarize(vessels_n = n_distinct(ssvid, na.rm = T),
            fishing_h = sum(fishing_hours_eez_fao_ter, na.rm = T),
            fishing_kwh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
            length_m_mean = mean(length_m, na.rm = T),
            length_m_min = min(length_m, na.rm = T),
            length_m_max = max(length_m, na.rm = T),
            tonnage_gt_mean = mean(tonnage_gt, na.rm = T),
            tonnage_gt_min = min(tonnage_gt, na.rm = T),
            tonnage_gt_max = max(tonnage_gt, na.rm = T),
            engine_power_kw_mean = mean(engine_power_kw, na.rm = T),
            engine_power_kw_min = min(engine_power_kw, na.rm = T),
            engine_power_kw_max = max(engine_power_kw, na.rm = T)) %>%
  arrange(year, loc_name, flag_iso3)

# save
write_csv(eez, paste0(results_dir, "gfw_for_pew_totals_by_year_flag_eez.csv"))
```

## Aggregate by EEZ, territorial waters, and flag state

Now let's aggregate by EEZ/fao region, and make the distinction between territorial waters and not. By year, for each territorial waters, EEZ/region, and flag state pairing, we calculate summary statistics and save the output dataset with the following attributes:

- year (int): year
- loc_id (chr): unique identifier for each EEZ and/or high seas region defined above
- loc_name (chr): name of each location
- is_territorial (bol): T/F did this activity happen within the territorial waters of this eez?
- loc_ter1_iso3 (chr): ISO3 character code of the administering territory - NA for high seas regions
- loc_sov1_iso3 (chr): ISO3 character code of the sovereign state - NA for high seas regions
- loc_ter2_iso3 (chr): ISO3 character code of the second administering territory - only in cases of joint regime or disputed areas, NA otherwise
- loc_sov2_iso3 (chr): ISO3 character code of the second sovereign state - only in cases of joint regime or disputed areas, NA otherwise
- loc_ter3_iso3 (chr): ISO3 character code of the third administering territory - only in cases of joint regime or disputed areas, NA otherwise
- loc_sov3_iso3 (chr): ISO3 character code of the third sovereign state - only in cases of joint regime or disputed areas, NA otherwise
- flag_iso3 (chr): ISO3 character code of the flag state of the vessel - "UNK" for unknown flag state
- vessels_n (int): number of unique vessels that fished there
- fishing_h (num): total number of fishing hours (h)
- fishing_kwh (num): total number of fishing kilowatt hours (kWh)
- length_m_mean (num): mean vessel length (m)
- length_m_min (num): mininum vessel length (m)
- length_m_max (num): maximum vessel length (m)
- tonnage_gt_mean (num): mean vessel tonnage (gt)
- tonnage_gt_min (num): mininum vessel tonnage (gt)
- tonnage_gt_max (num): maximum vessel tonnage (gt)
- engine_power_kw_mean (num): mean vessel engine power (kw)
- engine_power_kw_min (num): mean vessel engine power (kw)
- engine_power_kw_max (num): mean vessel engine power (kw)

```{r, echo=F, error=F, message=F, warning=F}
# Aggregate
terr <- out %>%
  group_by(year,
           loc_id,
           is_territorial,
           loc_name,
           loc_ter1_iso3 = territory1_iso3,
           loc_sov1_iso3 = sovereign1_iso3,
           loc_ter2_iso3 = territory2_iso3,
           loc_sov2_iso3 = sovereign2_iso3,
           loc_ter3_iso3 = territory3_iso3,
           loc_sov3_iso3 = sovereign3_iso3,
           flag_iso3 = flag) %>%
  summarize(vessels_n = n_distinct(ssvid, na.rm = T),
            fishing_h = sum(fishing_hours_eez_fao_ter, na.rm = T),
            fishing_kwh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
            length_m_mean = mean(length_m, na.rm = T),
            length_m_min = min(length_m, na.rm = T),
            length_m_max = max(length_m, na.rm = T),
            tonnage_gt_mean = mean(tonnage_gt, na.rm = T),
            tonnage_gt_min = min(tonnage_gt, na.rm = T),
            tonnage_gt_max = max(tonnage_gt, na.rm = T),
            engine_power_kw_mean = mean(engine_power_kw, na.rm = T),
            engine_power_kw_min = min(engine_power_kw, na.rm = T),
            engine_power_kw_max = max(engine_power_kw, na.rm = T)) %>%
  arrange(year, loc_name, is_territorial, flag_iso3)

# save
write_csv(area, paste0(results_dir, "gfw_for_pew_totals_by_year_flag_eez_territorial.csv"))
```

### 2020-04-24 app/scripts/BioEconModel.R

@@ -1,0 +1,470 @@
+### -------------------------------------------------------------------
+### SubsidyExplorer
+### An interactive toolkit to explore the tradeoffs across proposed fisheries subsidies disciplines
+### 
+### Creator(s): Kat Millage and Vienna Saccomanno
+### 
+### This script contains the bioeconomic model 
+### --------------------------------------------------------------------
+
+BioEconModel <- function(fleet,
+                         region = "global",
+                         bio_param,
+                         end_year = 2050,
+                         biomass_scalar = 1,
+                         return = "last"){
+
+  ### Time ----------------------------
+  year_range <- seq(2018, end_year, by = 1)
+  stop_time <- length(year_range) 
+
+  ### Fleets ----------------------------
+  nf <- length(fleet$fleet)
+  fleet_names <- fleet$fleet
+
+  # Get affected/managed, affected/open access, unaffected/managed, and unaffected/open access positions
+  aff_man <- which(fleet_names == "affected_managed")
+  aff_oa <- which(fleet_names == "affected_oa")
+  un_man <- which(fleet_names == "unaffected_managed")
+  un_oa <- which(fleet_names == "unaffected_oa")
+
+  ### Fixed biological parameters ----------------------------
+  B0 <- bio_param$value[bio_param$parameter == "b0"]
+  K <- bio_param$value[bio_param$parameter == "K"]
+  r <- bio_param$value[bio_param$parameter == "r"]
+  phi <- bio_param$value[bio_param$parameter == "phi"]
+  
+  ### Fixed harvest/fleet parameters ----------------------------
+  H0 <- bio_param$value[bio_param$parameter == "h0"]
+  E0 <- bio_param$value[bio_param$parameter == "e0"]
+  beta <- bio_param$value[bio_param$parameter == "beta"]
+  eta <- bio_param$value[bio_param$parameter == "eta"]
+  omega <- bio_param$value[bio_param$parameter == "omega"]
+
[…]

### 2020-04-24 scripts/other-analyses/supplementary-gfw-datasets/gfw_dataset_for_pew.Rmd
and read me

@@
 # save
-write_csv(flag_state, paste0(results_dir, "gfw_for_pew_totals_by_year_flag.csv"))
+write_csv(flag, paste0(results_dir, "gfw_for_pew_totals_by_year_flag.csv"))
 ```
@@
 # save
-write_csv(area, paste0(results_dir, "gfw_for_pew_totals_by_year_flag_eez_territorial.csv"))
+write_csv(terr, paste0(results_dir, "gfw_for_pew_totals_by_year_flag_eez_territorial.csv"))
 ```

### 2020-04-28 scripts/05_subsidy_reform_definitions.Rmd
pre-subdirectory attempt
high seas and development status

--- 2020-04-13 scripts/04_subsidy_reform_definitions.Rmd
@@
 # Path to global vessel list
-vessel_list_path <- here::here("results", "3-model-parameterization", "vessel-list-2018-regions.csv")
+vessel_list_path <- here::here("results", "04-model-parameterization", "vessel_list_2018_regions.csv")
 
 # Paths to other data files
-iuu_dat_path <- here::here("data", "raw", "fisheries", "IUU_Vessel_List", "IUUList-20190430.csv")
-costello_2016_path <- here::here("data", "raw", "fisheries", "Costello_2016", "ProjectionData_2012.csv")
+iuu_dat_path <- here::here("data", "raw", "IUU-Vessel-List-2019", "IUUList-20190430.csv")
+costello_2016_path <- here::here("data", "edited", "costello_et_al_2016_upsides_tidy.csv")
 
@@
 # Directories for the output files generated by this script
-results_dir <- here::here("results", "04_subsidy_reform_definitions/")
+results_dir <- here::here("results", "05-subsidy-reform-definitions/")
 if (dir.exists(results_dir) == F) {
@@
 
-app_dir <- here::here("WTOtoolkit", "data/")
+app_dir <- here::here("app", "data/")
 if (dir.exists(app_dir) == F) {
@@
 ```{r}
-# EU countries
-#Belgium, Bulgaria, Croatia, Cyprus, Denmark, Estonia, Finland, France, Germany, Greece, Ireland, Italy, Latvia, Lithuania, Malta, Netherlands, Poland, Portugal, Romania, Slovenia, Spain, Sweden, United Kingdom
-eu_countries <- c("BEL", "BGR", "HRV", "CYP", "DNK", "EST", "FIN", "FRA", "DEU", "GRC", "IRL", "ITA", "LVA", "LTU", "MLT", "NLD", "POL", "PRT", "ROU", "SVN", "ESP", "SWE", "GBR")
+# Country lookup table
+country_lookup <- read_csv(here::here("data", "lookup-tables", "country_dependencies.csv"))
 
-# Dutch overseas territories: Aruba, Bonaire/St. Eustatius/Saba, Curacao, Sint Maarten
-dutch_territories <- c("ABW", "BES", "CUW", "SXM")
-
-# French overseas territories: French Guiana, French Polynesia, French Southern and Antarctic Territories, Guadeloupe, Martinique, Mayotte, New Caledonia, Reunion, Saint Barthelemy, Saint Martin, St.
-Pierre and Miquelon, Wallis and Futuna Islands
-french_territories <- c("GUF", "PYF", "ATF", "GLP", "MTQ", "MYT", "NCL", "REU", "BLM", "MAF", "SPM", "WLF")
-
-# Danish overseas territories: Faroe Islands, Greenland
-danish_territories <- c("FRO", "GRL")
-
-# British overseas territories: Anguilla, Ascension island, Bermuda, Cayman Islands, Falkland Islands, Guernsey, Gibraltar, British Indian Ocean Territories, Jersey, Monserratt, Pitcairn Island, South Georgia and the South Sandwich Islands, Saint Helena/Ascension/Tristan da Cunha, Tristan da Cunha, Turks and Caicos Islands, British Virgin Islands
-uk_territories <- c("AIA","ASC","BMU","CYM","FLK","GGY","GIB","IOT","JEY","MSR","PCN","SGS","SHN","TAA","TCA","VGB")
-
-eu_territories <- c(dutch_territories, french_territories, danish_territories, uk_territories)
-
-# Norwegian overseas territories: Bouvet Islands, Svalbard and Jan Mayen Islands
-norwegian_territories <- c("BVT", "SJM")
-
-# US overseas territories:  American Samoa, Guam, Northern Marianas Islands, Puerto Rico, US Virgin Islands
-us_territories <- c("ASM", "GUM", "MNP", "PRI", "VIR")
-
+# Countries participating in the Northern Agreement for fishing
 eu_northern_agreement <- c("NOR", "ISL")
@@
 
-We use the flag of the vessel to assign development status. If the flag of the vessel was not able to be determined, we assume the development status to be "Developing".
+We use the flag of the vessel to assign development status.
 
 ```{r}
-# Read in country list with development status
-country_list <- read_csv(here::here("data", "country-conversion-sheet-all.csv"))
-
-country_development_status <- country_list %>%
+# Sovereign development statuses
+sov_country_development_status <- country_lookup %>%
+  dplyr::filter(!is_overseas_territory) %>%
   group_by(iso3) %>%
-  summarize(development_status_full = unique(development_status)) %>%
-  mutate(development_status = str_replace(development_status_full, ' \\(.*\\)', ""),
-         development_status_notes = str_extract(development_status_full, '\\(.*\\)')) %>%
+  summarize(development_status = case_when(!is.na(development_status) ~ development_status,
+                                                TRUE ~ "Developing"))
+# Get development status
+ter_development_status <- country_lookup %>%
+  dplyr::filter(is_overseas_territory) %>%
+  dplyr::select(-development_status) %>%
+  left_join(sov_country_development_status, by = c("sovereign_iso3" = "iso3")) %>%
   dplyr::select(iso3, development_status)
 
-country_development_status$development_status[country_development_status$iso3 == "ATF"] <- "Developed"
-country_development_status$development_status[country_development_status$iso3 == "IOT"] <- "Developed"
+# combine
+development_status <- sov_country_development_status %>%
+  bind_rows(ter_development_status)
 
@@
 temp_vessel_list <- vessel_list %>%
-  left_join(country_development_status, by = c("flag" = "iso3"))
+  left_join(development_status, by = c("flag_iso3" = "iso3"))
 
-# Let's also add identifies of EU vessels and US territory vessels to the vessel list
+```
+
+## High seas fishing
+
+In order to later be able to identify high seas fishing, we need to determine fraction of each vessel's total annual fishing effort spent on the high seas.
+
+```{r}
+# Get high seas totals by vessel
+vessel_totals_high_seas <- temp_vessel_list %>%
+  dplyr::filter(eez_id == 0) %>%
+  group_by(ssvid) %>%
+  summarize(fishing_h_hs = sum(fishing_hours_eez_fao_ter, na.rm = T),
+            fishing_KWh_hs = sum(fishing_KWh_eez_fao_ter, na.rm = T))
+
+# Now calculate high seas proportions
+vessel_totals_prop_hs <- temp_vessel_list %>%
+  group_by(ssvid) %>%
+  summarize(fishing_h = sum(fishing_hours_eez_fao_ter, na.rm = T),
+            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T)) %>%
+  ungroup() %>%
+  left_join(vessel_totals_high_seas, by = "ssvid") %>%
+  mutate(prop_fishing_hours_high_seas = case_when(is.na(fishing_h_hs) ~ 0, 
+                                           TRUE ~ fishing_h_hs/fishing_h),
+         prop_fishing_KWh_high_seas = case_when(is.na(fishing_KWh_hs) ~ 0, 
+                                         TRUE ~ fishing_KWh_hs/fishing_KWh)) %>%
+  dplyr::select(ssvid, prop_fishing_hours_high_seas, prop_fishing_KWh_high_seas)
+
+# Add back into vessel list
 temp_vessel_list <- temp_vessel_list %>%
-  mutate(is_EU = case_when(flag %in% eu_countries ~ T,
-                           TRUE ~ F),
-         is_EU_territory = case_when(flag %in% eu_territories ~ T,
-                                     TRUE ~ F),
-         is_US_territory = case_when(flag %in% us_territories ~ T,
-                                     TRUE ~ F))
+  left_join(vessel_totals_prop_hs, by = "ssvid")
 ```
@@
 
-```
-
-## High seas fishing
-
-In order to later be able to easily identify high seas fishing, we want to be able to easily identify the fraction of each vessel's total fishing effort spent on the high seas in a given year.
-
-```{r}
-# Get totals by vessel
-vessel_totals_high_seas <- temp_vessel_list %>%
-  dplyr::filter(eez_id == 0) %>%
-  group_by(ssvid) %>%
-  summarize(fishing_h_hs = sum(fishing_hours_eez_fao, na.rm = T),
-            fishing_KWh_hs = sum(fishing_KWh_eez_fao, na.rm = T))
-
-vessel_totals_prop_hs <- temp_vessel_list %>%
-  group_by(ssvid) %>%
-  summarize(fishing_h = sum(fishing_hours_eez_fao, na.rm = T),
-            fishing_KWh = sum(fishing_KWh_eez_fao, na.rm = T)) %>%
-  ungroup() %>%
-  left_join(vessel_totals_high_seas, by = "ssvid") %>%
-  mutate(prop_fishing_hours_HS = case_when(is.na(fishing_h_hs) ~ 0, 
-                                           TRUE ~ fishing_h_hs/fishing_h),
-         prop_fishing_KWh_HS = case_when(is.na(fishing_KWh_hs) ~ 0, 
-                                         TRUE ~ fishing_KWh_hs/fishing_KWh)) %>%
-  dplyr::select(ssvid, prop_fishing_hours_HS, prop_fishing_KWh_HS)
-
-temp_vessel_list <- temp_vessel_list %>%
-  left_join(vessel_totals_prop_hs, by = "ssvid")
 ```

### 2020-05-01 scripts/05_subsidy_reform_definitions.Rmd
final definitions

@@
 costello_2016_path <- here::here("data", "edited", "costello_et_al_2016_upsides_tidy.csv")
+eez_info_path <- here::here("data", "lookup-tables", "eez_info.csv")
 
@@
 # Countries participating in the Northern Agreement for fishing
-eu_northern_agreement <- c("NOR", "ISL")
+eu_countries <- country_lookup$iso3[country_lookup$is_EU]
+eu_northern_agreement <- c("NOR", "ISL", "SJM")
 ```
@@
 
-In order to determine whether a vessel is engaging in distant water fishing, we need to know something about the sovereign state of the vessel's flag state.
+In order to determine whether a vessel is engaging in distant water fishing, we need to know something about the sovereign state of the vessel's flag state. We have already assigned this.
 
 ```{r}
-# Get pairings of administering and sovereign states from the EEZ data
+# Get pairings of administering and sovereign states from the vessel data
 sovereign_pairings <- temp_vessel_list %>%
-  distinct(territory1_iso3, sovereign1_iso3) %>%
-  rename(flag = territory1_iso3, flag_sovereign = sovereign1_iso3)
-sovereign_pairings$flag_sovereign[sovereign_pairings$flag == "CHN"] <- "CHN"
+  distinct(flag_iso3, flag_sovereign_iso3) %>%
+  arrange(flag_iso3)
 
-# Create a manual list of missing sovereign pairings
-sovereign_pairings_manual <- tibble(flag = c("HKG", "KHM", "CUW", "BLZ", "CYM", "JOR", "PSE", "JAM", "AIA")) %>%
-  mutate(flag_sovereign = case_when(flag == "HKG" ~ "CHN",
-                                    flag == "CUW" ~ "NLD",
-                                    flag == "CYM" ~ "GBR",
-                                    flag == "PSE" ~ "ISR",
-                                    flag == "AIA" ~ "GBR",
-                                    TRUE ~ flag))
+```
 
-sovereign_pairings <- sovereign_pairings %>%
-  bind_rows(sovereign_pairings_manual) %>%
-  distinct(flag, flag_sovereign)
-
-# Also fix that on the vessel list
-temp_vessel_list$sovereign1_iso3[temp_vessel_list$territory1_iso3 == "CHN"] <- "CHN"
-
-# We then match it back to our vessel list so each entry has an assigned sovereign flag
-temp_vessel_list <- temp_vessel_list %>%
-  left_join(sovereign_pairings, by = "flag")
-
+```{r}
 # We fist exclude entries where the flag state of the vessel and the administering state of the EEZ in which it is fishing are the same
 distant_water_fishing <- temp_vessel_list %>%
-  mutate(territory1_match = case_when(!is.na(territory1_iso3) & flag == territory1_iso3 ~ T,
+  mutate(territory1_match = case_when(!is.na(eez_territory1_iso3) & flag_iso3 == eez_territory1_iso3 ~ T,
                                       TRUE ~ F),
-         territory2_match = case_when(!is.na(territory2_iso3) & flag == territory2_iso3 ~ T,
+         territory2_match = case_when(!is.na(eez_territory2_iso3) & flag_iso3 == eez_territory2_iso3 ~ T,
                                       TRUE ~ F),
-         territory3_match = case_when(!is.na(territory3_iso3) & flag == territory3_iso3 ~ T,
+         territory3_match = case_when(!is.na(eez_territory3_iso3) & flag_iso3 == eez_territory3_iso3 ~ T,
                                       TRUE ~ F)) %>%
@@
 
-We do not consider the following to be "intra-EU fishing": 
+We do not consider the following to be "intra-EU fishing" (and is therefore distante water fishing): 
 1.
@@
 distant_water_fishing <- distant_water_fishing %>%
-  mutate(is_intra_EU = case_when(flag %in% c(eu_countries, eu_northern_agreement, norwegian_territories) & territory1_iso3 %in% c(eu_countries, eu_northern_agreement, norwegian_territories) ~ T,
-                                 flag_sovereign %in% c(eu_countries, eu_northern_agreement, norwegian_territories) & territory1_iso3 %in% c(eu_countries, eu_northern_agreement, norwegian_territories) ~ T,
+  mutate(is_intra_EU = case_when(flag_iso3 %in% c(eu_countries, eu_northern_agreement) & eez_territory1_iso3 %in% c(eu_countries, eu_northern_agreement) ~ T,
+                                 flag_sovereign_iso3 %in% c(eu_countries, eu_northern_agreement) & eez_territory1_iso3 %in% c(eu_countries, eu_northern_agreement) ~ T,
                                  TRUE ~ F)) %>%
@@
 
-### Sovereignity
+#### A Note on Sovereignity
 
-If the sovereign flag state of a vessel is the same as the sovereign state of the EEZ in which it's fishing, this connection may still be considered to be distant water fishing (e.g.
-US vessel fishing in Palmyra Atoll), though this is generally not considered to be foreign distant water fishing.
+If the sovereign country of the flag state of a vessel is the same as the sovereign country of the EEZ in which it's fishing, this connection may still be considered to be distant water fishing, though this is generally not considered to be foreign distant water fishing.
 
@@
 
-Sovereign fishing is included in our definition of distant water fishing
+Though not foreign, we consider sovereign fishing to still be distant water fishing for the purposes of this analysis.
 
@@
 
-Using the combined list of IUU vessels (https://iuu-vessels.org/), we want to try to match as many vessels as possible to our vessel list.
+Using the combined list of IUU vessels (https://iuu-vessels.org/), we match as many vessels as possible to our vessel list.
+
+GFW uses a function called "normalize_shipname" from the `startR` package to normalize vessel names. We apply the same function to the IUU vessel list as one method of facilitating matching.
 
@@
 iuu_matching_vessels <- tibble(ssvid = integer(0),
-                               flag = character(0),
+                               flag_iso3 = character(0),
                                broadcast_shipname = character(0))
@@
 vessels_for_matching <- temp_vessel_list %>%
-  distinct(ssvid, flag, vessel_class, length_m, tonnage_gt, engine_power_kw, broadcast_shipname, broadcast_callsign, broadcast_imo)
+  distinct(ssvid, flag_iso3, vessel_class, length_m, tonnage_gt, engine_power_kw, broadcast_shipname, broadcast_callsign, broadcast_imo)
 
@@
 iuu_matching_vessels <- iuu_matching_vessels %>%
-  bind_rows(iuu_by_ssvid %>% distinct(ssvid, flag, broadcast_shipname))
+  bind_rows(iuu_by_ssvid %>% distinct(ssvid, flag_iso3, broadcast_shipname))
 
@@
 iuu_matching_vessels <- iuu_matching_vessels %>%
-  bind_rows(iuu_by_callsign %>% distinct(ssvid, flag, broadcast_shipname) %>% dplyr::filter(broadcast_shipname != "ROSE4"))
+  bind_rows(iuu_by_callsign %>% distinct(ssvid, flag_iso3, broadcast_shipname) %>% dplyr::filter(broadcast_shipname != "ROSE4"))
 
@@
 iuu_matching_vessels <- iuu_matching_vessels %>%
-  bind_rows(iuu_by_imo %>% distinct(ssvid, flag, broadcast_shipname))
+  bind_rows(iuu_by_imo %>% distinct(ssvid, flag_iso3, broadcast_shipname))
 
@@
 iuu_matching_vessels <- iuu_matching_vessels %>%
-  bind_rows(name_matches1 %>% distinct(ssvid, flag, broadcast_shipname)) %>%
-  bind_rows(name_matches2 %>% distinct(ssvid, flag, broadcast_shipname))
+  bind_rows(name_matches1 %>% distinct(ssvid, flag_iso3, broadcast_shipname)) %>%
+  bind_rows(name_matches2 %>% distinct(ssvid, flag_iso3, broadcast_shipname))
 
@@
 
+### Disputed areas
+
+We pull the version of marine regions used by GFW to characterize fishing activity.
+
+```{r}
+# EEZ info lookup table from GFW
+eez_info <- read_csv(eez_info_path)
+
+# Get disputed regions
+disputed_areas <- eez_info %>%
+  mutate(is_disputed = case_when(str_detect(reporting_name, "Disputed area") == T ~ T,
+                                 TRUE ~ F)) %>%
+  dplyr::filter(is_disputed)
+
+# apply to vessel list
+temp_vessel_list <- temp_vessel_list %>%
+  mutate(is_disputed = ifelse(eez_id %in% disputed_areas$eez_id, T, F))
+```
+
 ## Overfished and Unassessed Stocks
 
-### OA #1: Overfished as determined by the RAM legacy stock assessment database
+### OA #1/#2: B/Bmsy < 1/0.8 as determined by the RAM legacy stock assessment database
 
@@
 
-costello_2016_dat_clean <- costello_2016_dat %>%
-  mutate(region_fao_chr = as.character(region_fao),
-         n_regions = nchar(region_fao_chr)/2,
-         region_fao_split = str_split(gsub("(.{2})", "\\1 ", region_fao_chr), " ")) %>%
-  unnest(cols = c(region_fao_split)) %>%
-  mutate(region_fao_split = as.numeric(region_fao_split)) %>%
-  dplyr::filter(region_fao_split != "") %>%
-  mutate(iso3 = case_when(country == "Channel Islands" ~ "JEY",
-                          country == "Micronesia" ~ "FSM",
-                          country == "Zanzibar" ~ "TZA",
-                          TRUE ~ countrycode(country, "country.name", "iso3c")))
+# Separate RAM stocks 
+ram_stocks <- costello_2016_dat %>%
+  dplyr::filter(dbase == "RAM")
 
-# Get EEZ regions for matching
-eez_regions <- temp_vessel_list %>%
-  distinct(eez_id, fao_region, territory1_iso3, territory2_iso3, territory3_iso3, sovereign1_iso3, sovereign2_iso3, sovereign3_iso3)
+# Get statuses of multinational ram stocks by fao region
+multinational_ram_stocks <- ram_stocks %>%
+  dplyr::filter(is.na(iso3)) %>%
+  group_by(region_fao_split) %>%
+  summarize(n_stocks = n_distinct(id_orig),
+            mean_bv_bmsy = mean(bv_bmsy, na.rm = T),
+            median_bv_bmsy = mean(bv_bmsy, na.rm = T),
+            w_mean_bv_bmsy = weighted.mean(bv_bmsy, w = (msy/n_regions), na.rm = T)) %>%
+  mutate(oa1_median = ifelse(median_bv_bmsy >= 1, F, T),
+         oa1_w_mean = ifelse(w_mean_bv_bmsy >= 1, F, T),
+         oa2_median = ifelse(median_bv_bmsy >= 0.8, F, T),
+         oa2_w_mean = ifelse(w_mean_bv_bmsy >= 0.8, F, T)) %>%
+  dplyr::select(region_fao_split, oa1_median, oa1_w_mean, oa2_median, oa2_w_mean) %>%
+  mutate(eez_id = 0)
 
-# Get RAM stocks only and summarize by iso3 and fao_region
-ram_data <- costello_2016_dat_clean %>%
-  dplyr::filter(dbase == "RAM") %>%
-  group_by(iso3, region_fao_split) %>%
+# Get statuses of domestic stocks by flag state and fao region
+eez_ram_stocks <- ram_stocks %>%
+  dplyr::filter(!is.na(iso3))
+
+# Get eez ids from fishing effort
+eez_effort <- temp_vessel_list %>%
+  distinct(eez_id, fao_region, eez_territory1_iso3, eez_territory2_iso3, eez_territory3_iso3, eez_sovereign1_iso3, eez_sovereign2_iso3, eez_sovereign3_iso3)
+
+# Match
+eez_ram_stocks <- eez_ram_stocks %>%
+  left_join(eez_effort, by = c("iso3" = "eez_territory1_iso3", "region_fao_split" = "fao_region")) %>%
+  group_by(eez_id, region_fao_split) %>%
   summarize(n_stocks = n_distinct(id_orig),
-            mean_bv_bmsy = mean(bv_bmsy),
-            median_bv_bmsy = median(bv_bmsy)) %>%
-  mutate(oa_mean = ifelse(mean_bv_bmsy >= 1, F, T),
-         oa_med = ifelse(median_bv_bmsy >= 1, F, T),
-         oa1 = ifelse(oa_mean & oa_med, T, F))
+            mean_bv_bmsy = mean(bv_bmsy, na.rm = T),
+            median_bv_bmsy = mean(bv_bmsy, na.rm = T),
+            w_mean_bv_bmsy = weighted.mean(bv_bmsy, w = (msy/n_regions), na.rm = T)) %>%
+  mutate(oa1_median = ifelse(median_bv_bmsy >= 1, F, T),
+         oa1_w_mean = ifelse(w_mean_bv_bmsy >= 1, F, T),
+         oa2_median = ifelse(median_bv_bmsy >= 0.8, F, T),
+         oa2_w_mean = ifelse(w_mean_bv_bmsy >= 0.8, F, T)) %>%
+  dplyr::select(eez_id, region_fao_split, oa1_median, oa1_w_mean, oa2_median, oa2_w_mean)
 
-ram_by_eez_region <- eez_regions %>%
-  left_join(ram_data, by = c("territory1_iso3" = "iso3", "fao_region" = "region_fao_split")) %>%
-  arrange(eez_id, fao_region) %>%
-  dplyr::select(eez_id, fao_region, oa1)
-ram_by_eez_region$oa1[is.na(ram_by_eez_region$oa1)] <- F
+# Combine 
+oa_1_2 <- multinational_ram_stocks %>%
+  bind_rows(eez_ram_stocks)
 
@@
 temp_vessel_list <- temp_vessel_list %>%
-  left_join(ram_by_eez_region, by = c("eez_id", "fao_region"))
+  left_join(oa_1_2, by = c("eez_id" = "eez_id", "fao_region" = "region_fao_split"))
+
+temp_vessel_list$oa1_median[is.na(temp_vessel_list$oa1_median)] <- F
+temp_vessel_list$oa2_median[is.na(temp_vessel_list$oa2_median)] <- F
+temp_vessel_list$oa1_w_mean[is.na(temp_vessel_list$oa1_w_mean)] <- F
+temp_vessel_list$oa2_w_mean[is.na(temp_vessel_list$oa2_w_mean)] <- F
+
 ```
 
-### OA #2: Overfished as determined by Costello et al. (2016)
+### OA #3/4: Overfished as determined by Costello et al. (2016)
 
 ```{r}
-# Include all stocks 
-all_data <- costello_2016_dat_clean %>%
-  group_by(iso3, region_fao_split) %>%
+# Get statuses of multinational ram stocks by fao region
+multinational_stocks <- costello_2016_dat %>%
+  dplyr::filter(is.na(iso3)) %>%
+  group_by(region_fao_split) %>%
   summarize(n_stocks = n_distinct(id_orig),
-            mean_bv_bmsy = mean(bv_bmsy),
-            median_bv_bmsy = median(bv_bmsy)) %>%
-  mutate(oa_mean = ifelse(mean_bv_bmsy >= 1, F, T),
-         oa_med = ifelse(median_bv_bmsy >= 1, F, T),
-         oa2 = ifelse(oa_mean & oa_med, T, F))
+            mean_bv_bmsy = mean(bv_bmsy, na.rm = T),
+            median_bv_bmsy = mean(bv_bmsy, na.rm = T),
+            w_mean_bv_bmsy = weighted.mean(bv_bmsy, w = (msy/n_regions), na.rm = T)) %>%
+  mutate(oa3_median = ifelse(median_bv_bmsy >= 1, F, T),
+         oa3_w_mean = ifelse(w_mean_bv_bmsy >= 1, F, T),
+         oa4_median = ifelse(median_bv_bmsy >= 0.8, F, T),
+         oa4_w_mean = ifelse(w_mean_bv_bmsy >= 0.8, F, T)) %>%
+  dplyr::select(region_fao_split, oa3_median, oa3_w_mean, oa4_median, oa4_w_mean) %>%
+  mutate(eez_id = 0)
 
-all_by_eez_region <- eez_regions %>%
-  left_join(all_data, by = c("territory1_iso3" = "iso3", "fao_region" = "region_fao_split")) %>%
-  arrange(eez_id, fao_region) %>%
-  dplyr::select(eez_id, fao_region, oa2)
-all_by_eez_region$oa2[is.na(all_by_eez_region$oa2)] <- F
+# Get statuses of domestic stocks by flag state and fao region
+eez_stocks <- costello_2016_dat %>%
+  dplyr::filter(!is.na(iso3)) %>%
+  left_join(eez_effort, by = c("iso3" = "eez_territory1_iso3", "region_fao_split" = "fao_region")) %>%
+  group_by(eez_id, region_fao_split) %>%
+  summarize(n_stocks = n_distinct(id_orig),
+            mean_bv_bmsy = mean(bv_bmsy, na.rm = T),
+            median_bv_bmsy = mean(bv_bmsy, na.rm = T),
+            w_mean_bv_bmsy = weighted.mean(bv_bmsy, w = (msy/n_regions), na.rm = T)) %>%
+  mutate(oa3_median = ifelse(median_bv_bmsy >= 1, F, T),
+         oa3_w_mean = ifelse(w_mean_bv_bmsy >= 1, F, T),
+         oa4_median = ifelse(median_bv_bmsy >= 0.8, F, T),
+         oa4_w_mean = ifelse(w_mean_bv_bmsy >= 0.8, F, T)) %>%
+  dplyr::select(eez_id, region_fao_split, oa3_median, oa3_w_mean, oa4_median, oa4_w_mean)
+
+# Combine 
+oa_3_4 <- multinational_stocks %>%
+  bind_rows(eez_stocks)
 
@@
 temp_vessel_list <- temp_vessel_list %>%
-  left_join(all_by_eez_region, by = c("eez_id", "fao_region"))
+  left_join(oa_3_4, by = c("eez_id" = "eez_id", "fao_region" = "region_fao_split"))
+
+temp_vessel_list$oa3_median[is.na(temp_vessel_list$oa3_median)] <- F
+temp_vessel_list$oa4_median[is.na(temp_vessel_list$oa4_median)] <- F
+temp_vessel_list$oa3_w_mean[is.na(temp_vessel_list$oa3_w_mean)] <- F
+temp_vessel_list$oa4_w_mean[is.na(temp_vessel_list$oa4_w_mean)] <- F
 ```
@@
 # Export final vessel list with definitions
-write_csv(temp_vessel_list, paste0(results_dir, "vessel-list-2018-final.csv"))
-write_csv(temp_vessel_list, paste0(app_dir, "vessel-list-2018-final.csv"))
+write_csv(temp_vessel_list, paste0(results_dir, "vessel_list_2018_final.csv"))
+write_csv(temp_vessel_list, paste0(app_dir, "vessel_list_2018_final.csv"))
 ```

### 2020-06-29 scripts/04_model_parameterization.Rmd
updated model parameters

@@
 It outputs two CSV files used by the SubsidyExplorer toolkit (located in `r here::here("WTOToolkit", "data")`):
-- model-parameters-global.csv
-- model-parameters-regional.csv
+- model_parameters_global.csv
+- model_parameters_regional.csv
 
@@
 # One estimate of global carrying capacity
-# global_k <- sum(costello_2016_dat$k)/0.78
-global_k <- global_msy*9.6
+global_k <- sum(costello_2016_dat$k)/0.78
+#global_k <- global_msy*9.1
 
@@
 ```{r}
-# Calculate r
-global_r <- (global_msy/global_k)*(phi+1)^(1/phi)
+# Calculate population growth rate
+global_g <- (global_msy/global_k)*(phi+1)^(1/phi)
 
-# Add r to parameter table
+# Add g to parameter table
 global_model_parameters <- global_model_parameters %>%
-  bind_rows(tibble(parameter = "r", value = global_r, source = "Costello et al. 2016"))
+  bind_rows(tibble(parameter = "g", value = global_g, source = "Costello et al. 2016"))
+
+# Calculate intrinsic growth rate
+global_r <- ((phi+1)/phi)*global_g
+
+# Add g to parameter table
+global_model_parameters <- global_model_parameters %>%
+  bind_rows(tibble(parameter = "r", value = global_g, source = "Costello et al. 2016"))
 ```
@@
 # Estimation of starting biomass
-biomass_vec <- seq(0, 0.5*global_k, length.out = 2000)
-growth_approx <- (((phi+1)/phi)*global_r*biomass_vec*(1-((biomass_vec/global_k)^phi)))
+biomass_vec <- seq(0, 0.5*global_k, length.out = 10000)
+growth_approx <- (((phi+1)/phi)*global_g*biomass_vec*(1-((biomass_vec/global_k)^phi)))
 biomass_pos <- which.min(abs(growth_approx - (global_h0+8000000)))
@@
   dplyr::filter(region_fao_split != "") %>%
-  mutate(msy_new = (msy/0.78)/n_regions) %>%
+  mutate(msy_new = msy/n_regions,
+         k_new = k/n_regions,
+         catch_new = catch/n_regions) %>%
   left_join(regions_tidy, by = c("region_fao_split" = "fao_region")) %>%
@@
   summarize(msy = sum(msy_new, na.rm = T),
+            k = sum(k_new, na.rm = T),
+            catch = sum(catch_new, na.rm = T),
             price = median(price, na.rm = T)) %>%
@@
 # Extract msy
-regional_msy <- round(costello_2016_dat_regional$msy)
+regional_msy <- round(costello_2016_dat_regional$msy/0.78)
 names(regional_msy) <- region_names
@@
 
-We estimate regional carrying capacities again by assuming K to be 9.6 times MSY.
+We estimate regional carrying capacities again by assuming K to be 9.1 times MSY.
 
@@
 # Extract carrying capacity
-regional_k <- regional_msy*9.6
+#regional_k <- regional_msy*9.1
+regional_k <- round(costello_2016_dat_regional$k/0.78)
+names(regional_k) <- region_names
 
@@
 # Calculate r regionally
-regional_r <- (regional_msy/regional_k)*(regional_phi+1)^(1/regional_phi)
+regional_g <- (regional_msy/regional_k)*(regional_phi+1)^(1/regional_phi)
+
+# Add r to parameter table
+regional_model_parameters <- regional_model_parameters %>%
+  bind_rows(c("parameter" = "g", "source" = "Costello et al. 2016", regional_g))
+
+# Calculate r regionally
+regional_r <- ((regional_phi+1)/(regional_phi))*regional_g
 
@@
 #Estimate starting biomass
-regional_b0 <- numeric(length(region_names))
-regional_biomass_growth <- c(4.1e6, 8e6, -2e6, 2.3e6, 2.3e6, -2e6)
+#regional_b0 <- numeric(length(region_names))
+# regional_biomass_growth <- c(1.33e6, 1.33e6, 1.33e6, 1.33e6, 1.33e6, 1.33e6)
+# 
+# for(i in 1:length(regional_h0)){
+#   biomass_vec <- seq(0, regional_k[i], length.out = 10000)
+#   growth_approx <- (((regional_phi[i]+1)/regional_phi[i])*regional_r[i]*biomass_vec*(1-((biomass_vec/regional_k[i])^regional_phi[i])))
+#   biomass_pos <- which.min(abs(growth_approx - (regional_h0 + regional_biomass_growth[i])))
+#   regional_b0[i] <- biomass_vec[biomass_pos] 
+# }
 
-for(i in 1:length(regional_h0)){
-  biomass_vec <- seq(0, regional_k[i], length.out = 10000)
-  growth_approx <- (((regional_phi[i]+1)/regional_phi[i])*regional_r[i]*biomass_vec*(1-((biomass_vec/regional_k[i])^regional_phi[i])))
-  biomass_pos <- which.min(abs(growth_approx - (regional_h0 + regional_biomass_growth[i])))
-  regional_b0[i] <- biomass_vec[biomass_pos] 
-}
+regional_b0 <- regional_k*0.2
 names(regional_b0) <- region_names
@@
             fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
-            bad_subs = sum(bad_subs, na.rm = T)) %>%
+            bad_subs = sum(bad_subs, na.rm = T),
+            catch = sum(catch, na.rm = T)) %>%
   arrange(region)
@@
 # Add price constant to parameter table
-# global_model_parameters <- global_model_parameters %>%
-#   bind_rows(tibble(parameter = "delta", value = global_delta, source = "Costello et al. 2016"))
+global_model_parameters <- global_model_parameters %>%
+  bind_rows(tibble(parameter = "delta", value = global_delta, source = "Costello et al. 2016"))
 ```
@@
 # Regional price constant
-regional_delta <- costello_regional_dat$catch/(costello_regional_dat$price^regional_epsilon)
+regional_delta <- costello_2016_dat_regional$catch/(costello_2016_dat_regional$price^regional_epsilon)
 
 # Add price constant to parameter table
-# regional_model_parameters <- regional_model_parameters %>%
-#   bind_rows(c("parameter" = "delta", "source" = "Costello et al. 2016", regional_delta))
+regional_model_parameters <- regional_model_parameters %>%
+  bind_rows(c("parameter" = "delta", "source" = "Costello et al. 2016", regional_delta))
 ```
@@
 # Calculate global base prices
-global_base_price1 <- ((1/global_delta)^(1/global_epsilon))*(sum(global_fleet$catch)^(1/global_epsilon))
+global_base_price1 <- ((1/global_delta)^(1/global_epsilon))*(global_h0^(1/global_epsilon))
 
-CPI_2012 <- 229.594  #BLS CPI All Items (Annual Ave), (BLS Series ID: CUUR0000SA0)
-CPI_2018 <- 251.107  #BLS CPI All Items (Annual Ave), (BLS Series ID: CUUR0000SA0)
-
-global_base_price2 <- global_price_wrangling$price * (CPI_2018/CPI_2012)
+# CPI_2012 <- 229.594  #BLS CPI All Items (Annual Ave), (BLS Series ID: CUUR0000SA0)
+# CPI_2018 <- 251.107  #BLS CPI All Items (Annual Ave), (BLS Series ID: CUUR0000SA0)
+# 
+# global_base_price2 <- global_price_wrangling$price * (CPI_2018/CPI_2012)
 ```
@@
   bind_rows(tibble(parameter = "p0", value = global_base_price1, source = "Costello et al. 2016"))
-```
-
-We then can calculate the rate of subsidization in the base year using the subsidy estimates from Sumaila et al.
-
-```{r}
-# Calculate global base subsidies
-global_base_subsidies <- global_fleet$bad_subs/global_fleet$fishing_KWh
-
-# Add to parameter table
-# global_model_parameters <- global_model_parameters %>%
-#   bind_rows(tibble(parameter = "s0_managed", value = global_base_subsidies[1], source = "Sumaila et al. 2019"))
-# global_model_parameters <- global_model_parameters %>%
-#   bind_rows(tibble(parameter = "s0_oa", value = global_base_subsidies[2], source = "Sumaila et al. 2019"))
-```
-
-And now we are able to estimate the cost coefficients for each fleet.
-
-```{r}
-# Calculate cost coefficients 
-global_cost_coeff <- ((global_base_price1*global_fleet$catch) + (global_base_subsidies*global_fleet$fishing_KWh))/(global_fleet$fishing_KWh^global_beta)
-
-# Add to parameter table
-# global_model_parameters <- global_model_parameters %>%
-#   bind_rows(tibble(parameter = "alpha_managed", value = global_cost_coeff[1], source = "Calculated"))
-# global_model_parameters <- global_model_parameters %>%
-#   bind_rows(tibble(parameter = "alpha_oa", value = global_cost_coeff[2], source = "Calculated"))
 ```
@@
   bind_rows(tibble(parameter = "eta", value = global_eta, source = "Calculated"))
+
+```
+
+We also define an omega which is equal to 0.001.
+
+```{r}
+# Define global eta
+global_omega <- 0.001
+
+# Add to parameter table
+global_model_parameters <- global_model_parameters %>%
+  bind_rows(tibble(parameter = "omega", value = global_omega, source = "Calculated"))
+
 ```
@@
 As with the global analysis, we assume $\beta$ to be equal to 1.3 across all regions. 
-
 ```{r}
@@
 # Calculate base price regionally
-regional_catches_total <- regional_fleet_harvest %>%
-  gather(region, catch, -1) %>%
-  group_by(region) %>%
-  summarize(catch = sum(catch)) %>%
-  spread(region, catch)
-
-regional_base_price1 <- ((1/regional_delta)^(1/regional_epsilon))*(unlist(regional_catches_total[1,])^(1/regional_epsilon))
+regional_base_price1 <- ((1/regional_delta)^(1/regional_epsilon))*(regional_fleet$catch^(1/regional_epsilon))
 
@@
 
-As well as the rate of subsidization by fleet and region in the base year
-
-```{r}
-# get subsidy rates regionally by fleet
-# Get effort
-regional_fleet_subs <- regional_fleet %>%
-  dplyr::select(region, fleet, bad_subs) %>%
-  spread(region, bad_subs)
-
-subsidies_regional <- tibble(fleet = c("managed", "open_access"))
-
-for(i in 2:ncol(regional_fleet_subs)){
-
-  out <- tibble(unlist(regional_fleet_subs[,i])/unlist(regional_fleet_effort[,i]))
-  colnames(out) <- region_names[i-1]
-
-  subsidies_regional <- subsidies_regional %>%
-    bind_cols(out)
-
-}
-
-# Add subsidy base to parameter table
-# regional_model_parameters <- regional_model_parameters %>%
-#   bind_rows(c("parameter" = "s0_managed", "source" = "Sumaila et al. 2019; GFW 2019", unlist(subsidies_regional[1,-1])))
-# regional_model_parameters <- regional_model_parameters %>%
-#   bind_rows(c("parameter" = "s0_oa", "source" = "Sumaila et al. 2019; GFW 2019", unlist(subsidies_regional[2,-1])))
-```
-
-So we estimate cost coefficients for each fleet
-
-```{r}
-
-cost_coeff_regional <- tibble(fleet = c("managed", "open_access"))
-
-for(i in 2:ncol(regional_fleet_subs)){
-
-  out <- tibble(
-    ((regional_base_price1[i-1]*unlist(regional_fleet_harvest[,i])) + 
-      (unlist(subsidies_regional[,i])*unlist(regional_fleet_effort[,i]))) /
-      (unlist(regional_fleet_effort[,i])^regional_beta[i-1])
-    )
-  colnames(out) <- region_names[i-1]
-
-  cost_coeff_regional <- cost_coeff_regional %>%
-    bind_cols(out)
-
-}
-
-# Add subsidy base to parameter table
-# regional_model_parameters <- regional_model_parameters %>%
-#   bind_rows(c("parameter" = "alpha_managed", "source" = "Calculated", unlist(cost_coeff_regional[1,-1])))
-# regional_model_parameters <- regional_model_parameters %>%
-#   bind_rows(c("parameter" = "alpha_oa", "source" = "Calculated", unlist(cost_coeff_regional[2,-1])))
-
-```
-
-And we again assume $\eta$ to be equal to 0.1 across all regions
+And we again assume $\eta$ to be equal to 0.1 and $\omega$ to be equal to 0.001 across all regions
 
@@
 ```{r}
+regional_omega <- rep(0.0011, length = length(region_names))
+names(regional_omega) <- region_names
+
+# Add subsidy base to parameter table
+regional_model_parameters <- regional_model_parameters %>%
+  bind_rows(c("parameter" = "omega", "source" = "Costello et al. 2016", regional_omega))
+```
+
+```{r}
 # Save both parameter files
-write_csv(global_model_parameters, paste0(results_dir, "global-model-parameters.csv"))
-write_csv(global_model_parameters, paste0(app_dir, "global-model-parameters.csv"))
+write_csv(global_model_parameters, paste0(results_dir, "model_parameters_global.csv"))
+write_csv(global_model_parameters, paste0(app_dir, "model_parameters_global.csv"))
 
-write_csv(regional_model_parameters, paste0(results_dir, "regional-model-parameters.csv"))
-write_csv(regional_model_parameters, paste0(app_dir, "regional-model-parameters.csv"))
-
-# Save vessel list
-write_csv(vessel_list_out, paste0(results_dir, "vessel-list-2018-regions.csv"))
+write_csv(regional_model_parameters, paste0(results_dir, "model_parameters_regional.csv"))
+write_csv(regional_model_parameters, paste0(app_dir, "model_parameters_regional.csv"))
 ```

### 2020-06-29 scripts/06_run_model.Rmd
updated model parameters

---
output:
  html_document: default

title: "SubsidyExplorer - Step 5: Run Model"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
bibliography: "../pew-subsidies.bib"
---

```{r setup, include=FALSE}
# Load packages
library(knitr) 
library(tidyverse)

knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This script generates the most ambitous global and regional results obtained by removing all capacity enhancing subsidies from all WTO Members and Observers.

```{r}
# Source model script

```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2020-08-06 scripts/01_data_wrangling.Rmd
finalizing data sources

@@
 ```{r}
-# Paths to subsidies data files
-sumaila_subsidies_path <- here::here("data", "raw", "Sumaila-et-al-2019-subsidies", "Subsidies_PEW_Final.xlsx")
-oecd_fse_path <- here::here("data", "raw", "OECD-2019-fse", "FISH_FSE_10032020183349581.csv")
-
-# Paths to demographic data files
+### Paths to demographic data files
+# WDI data - no path, accessed through package
 fao_fishers_path <- here::here("data", "raw", "FAO-2019-yearbook", "fao_fishers_yearbook_070619.csv")
@@
 
-# Paths to fisheries data files
+### Paths to fisheries subsidies data files
+sumaila_subsidies_path <- here::here("data", "raw", "Sumaila-et-al-2019-subsidies", "Subsidies_PEW_Final.xlsx")
+oecd_fse_path <- here::here("data", "raw", "OECD-2019-fse", "FISH_FSE_10032020183349581.csv")
+schuhbauer_subsidies_ssf_path <- here::here("data", "raw", "Schuhbauer-et-al-2017-ssf-subsidies", "Subsidies_SSF_split_2018.csv")
+
+### Paths to other fisheries data files
 fao_production_path <- here::here("data", "raw", "FAO-2019-capture-production", "Capture_2019.1.0/")
@@
 melnychuk_price_path <- here::here("data", "raw", "Melnychuk-et-al-2013-price", "Melnychuk_Exvessel_Price_Database.csv")
-
-# Paths to fisheries mgmt files 
+ram_sadb_path <- here::here("data", "raw", "RAM-2018-stock-assessment-database", "RLSADB v4.40", "DB Files With Assessment Data", "RLSADB v4.40 (assessment data only).xlsx")
 costello_upsides_path <- here::here("data", "raw", "Costello-et-al-2016-upsides", "ProjectionData_2012.csv")
 melnychuk_fmi_path <- here::here("data", "raw", "Melnychuk-et-al-2017-fmi", "fmi_values_country.csv")
-ram_sadb_path <- here::here("data", "raw", "RAM-2018-stock-assessment-database", "RLSADB v4.40", "DB Files With Assessment Data", "RLSADB v4.40 (assessment data only).xlsx")
-anderson_fpi_path <- here::here("data", "raw", "Anderson-et-al-2015-fpi", "fpi_values_fishery.csv")
+iuu_vessel_path <- here::here("data", "raw", "IUU-Vessel-List-2019", "IUUList-20190430.csv")
 
-# Paths to other files
-iuu_vessel_path <- here::here("data", "raw", "IUU-Vessel-List-2019", "IUUList-20190430.csv")
+### Paths to other necessary files
 cap_tier_path <- here::here("data", "raw", "USA-Cap-Tier-Proposal", "US_cap_tier_data.csv")
+country_lookup_path <- here::here("data", "lookup-tables", "country_dependencies.csv")
+fao_regions_for_ram_lookup_path <- here::here("data", "lookup-tables", "fao_areas_for_ram_stocks_v4.491.csv")
 ```
@@
 The following data sources are included in this analysis:
-
-**Fisheries (Subsidy) Data**
-Estimates of annual fisheries subsidies provision by state from Sumaila et al.
-(2019) in 2018 US\$.
-These data were provided to us directly by the authors as a .xlsx file and are stored at `r sumaila_subsidies_path`.
-> Sumaila, U.
-R., Ebrahim, N., Schuhbauer, A., Skerritt, D., Li, Y., Kim, H.
-S., … Pauly, D.
-(2019).
-Updated estimates and analysis of global fisheries subsidies.
-Marine Policy, 109, 103695.
-https://doi.org/10.1016/j.marpol.2019.103695
-
-Estimates of fisheries support provision by state from the OECD (2008 - 2018).
-These data were last downloaded from the OECD iLibrary portal as a CSV file on March 10, 2019 and are stored as `r oecd_fse_path`.
-> OECD. (2019). Fisheries: Fisheries support estimates. Fisheries and Aquaculture Statistics, OECD Agriculture Statistics (Database). https://doi.org/10.1787/ade64fdc-en
 
@@
 These data were manually transcribed from PDF (`./data/raw/fleet_&_employment.pdf`) to CSV format on July 6, 2019 and are stored as `r fao_fishers_path`.
-> FAO (2019). FAO yearbook. Fishery and Aquaculture Statistics 2017, http://www.fao.org/fishery/statistics/global-fishers/en (accessed on 24 October 2019).
+> FAO. (2019). FAO Yearbook of Fishery and Aquaculture Statistics 2017 (p. 108).
 
-Estimated number of full-time jobs in fisheries from Teh and Sumaila (2013) in 2003. These data were provided to us directly by the authors as a .xlsx file and are stored as `r teh_fte_path`. 
+Estimated number of full-time jobs in fisheries from Teh and Sumaila (2013) in 2003. These data were provided to us directly by the authors and are stored as `r teh_fte_path`. 
 > Teh, L. C. L., & Sumaila, U. R. (2011). Contribution of marine fisheries to worldwide employment. Fish and Fisheries, 14(1), 77–88. https://doi.org/10.1111/j.1467-2979.2011.00450.x
 
+**Fisheries Subsidies Data**
+Estimates of annual fisheries subsidies provision by state from Sumaila et al. (2019) in 2018 US\$. These data were provided to us directly by the authors and are stored at `r sumaila_subsidies_path`.
+> Sumaila, U.
+R., Ebrahim, N., Schuhbauer, A., Skerritt, D., Li, Y., Kim, H.
+S., … Pauly, D.
+(2019).
+Updated estimates and analysis of global fisheries subsidies.
+Marine Policy, 109, 103695.
+https://doi.org/10.1016/j.marpol.2019.103695
+
+Estimates of fisheries support provision by state from the OECD (2008 - 2018). These data were last downloaded from the OECD iLibrary portal on March 10, 2019 and are stored as `r oecd_fse_path`.
+> OECD. (2019). Fisheries: Fisheries support estimates. Fisheries and Aquaculture Statistics, OECD Agriculture Statistics (Database). https://doi.org/10.1787/ade64fdc-en
+
+Estimates of annual fisheries subsidies provision to small scale fisheries by state in 2018 US\$.
+Data used in this analysis are unpublished updates (based on the Sumaila et al.
+(2019) data) from those reported in Schuhbauer et al.
+(2017) (which are in 2009 US\$).
+These data were provided to us directly by the authors and are stored at `r schuhbauer_subsidies_ssf_path`.
+> Schuhbauer, A., Chuenpagdee, R., Cheung, W.
+W.
+L., Greer, K., & Sumaila, U.
+R.
+(2017).
+How subsidies affect the economic viability of small-scale fisheries.
+Marine Policy, 82, 114–121.
+https://doi.org/10.1016/j.marpol.2017.05.013
+
 **Other Fisheries Data**
-Fisheries landings in 2017 from the FAO Global Capture Production database (2019) and estimates of landed value generated using the ex-vessel price database created by Melnychuk et al.
-(2017).
-These data were were wrangled in the previous script, and the edited data are stored as `r catch_dat_path`.
-> FAO (2019). FAO yearbook. Fishery and Aquaculture Statistics 2017, http://www.fao.org/fishery/statistics/global-capture-production/en (accessed on 24 October 2019).
+Fisheries landings in 2018 from the FAO Global Capture Production database (2020). These data were last downloaded from the FAO website on July 25, 2020 and are stored as `r fao_production_path`. 
+> FAO. (2020). Global Capture Production Dataset. http://www.fao.org/fishery/statistics/global-capture-production/en
 
-Estimated landed price 
+Estimates of ex-vessel prices created by Melnychuk et al. (2017). These data were provided to us directly by the authors and are stored as `r melnychuk_price_path`. 
 > Melnychuk, M.
@@
 
-RAM Stock assessment database
-> RAM Legacy Stock Assessment Database. (2018). Version 4.44-assessment-only. Released 2018-12-22. DOI:10.5281/zenodo.2542919
+The RAM Legacy Stock Assessment Database is a compolation of stock assessments for commercially exploited species from around the world.
+The latest version of this database (version 4.491) was downloaded directly from the RAM website on July 25, 2020 and are stored as `r ram_sadb_path`.
+> RAM Legacy Stock Assessment Database. (2020). Version 4.491-assessment only. Released 2020-02-20. https://doi.org/10.5281/zenodo.3676087
 
-Stock status database
+Estimates of stock status for comericlaly exploited species not included in the RAM Legacy Stock Assessment Database from Costello et al.
+(2016).
+These data were provided to us directly by the authors and are stored as `r costello_upsides_path`.
 > Costello, C., Ovando, D., Clavelle, T., Strauss, C.
@@
 
-Fisheries management indicators
+Fisheries management indicators for many of the top fishing nations from Melnychuk et al.
+(2017).
+These data were manually transcribed from Figure S2 in the supplementary information and are stored as `r melnychuk_fmi_path`.
 > Melnychuk, M.
@@
 
-IUU Consolidated vessel list
-> NEED
+The IUU Consolidated Vessel List created and maintained by Trygg Mat Tracking. These data were downloaded directly from the website on November 30, 2019 and are stored as `r iuu_vessel_path`. 
+> Trygg Mat Tracking. (2020). Combined IUU Fishing Vessel List. https://www.iuu-vessels.org/
 
-Cap and Tier Data from the US Proposal
-> Citation for this?
+We also use the following tables to aid in our analysis:
+
+- Proposed tier assignments for a cap-based approach to limiting subsidies as included in the proposal made to the WTO by the US Delegation on May 3, 2019 [TN/RL/GEN/197/Rev.1].
+
+- A manually compiled table of overseas dependencies of WTO Member and Observer countries
+
+- A manually compiled table of FAO statistical regions coorepsonding to the stocks contained in version 4.491 of the RAM Legacy Stock Assessment Database.
 
@@
 # Load country dependencies helper file
-country_dependencies <- read_csv(here::here("data", "lookup-tables", "country_dependencies.csv"))
+country_dependencies <- read_csv(country_lookup_path)
 

### 2020-08-06 data/raw/RAM-2018-stock-assessment-database/RAMLDB v4.491/DB Files With Assessment Data/R Data/loadDBdata[asmt][v4.491].r

@@ -1,114 +1,0 @@
-###################################################################################
-###################################################################################
-###################################################################################
-#
-# This will load database data from the file DBdata.RData. Put the data file in the
-# working directory, then run the line at the bottom of the file.
-#
-###################################################################################
-###################################################################################
-###################################################################################
-#
-# The following objects are tables from RAM (data frames):
-#
-# --- metadata
-#	Summarized metadata
-# --- stock
-#	General stock metadata
-# --- assessment
-#	General assessment metadata
-# --- taxonomy
-#	Taxonomic metadata
-# --- management
-#	Management authority metadata
-# --- assessor
-#	Stock assessor metadata
-# --- assessmethod
-#	Assessment method metadata
-# --- area
-#	Area metadata
-# --- biometrics
-#	Parameter data types with descriptions
-# --- tsmetrics
-#	Time series data types with descriptions
-# --- timeseries
-#	Full time series data listing
-# --- bioparams
-#	Full parameter data listing
-# --- timeseries_values_views
-#	Values by stock and year of common time series types
-# --- timeseries_units_views
-#	Units corresponding to values in timeseries_values_views
-# --- timeseries_ids_views
-#	Time series IDs corresponding to values in timeseries_values_views
-# --- timeseries_assessments_views
-#	Assessment IDs corresponding to values in timeseries_values_views
-# --- timeseries_notes_views
-#	Notes corresponding to values in timeseries_values_views
-# --- timeseries_sources_views
-#	Sources corresponding to values in timeseries_values_views
-# --- timeseries_years_views
-#	Year range corresponding to values in timeseries_values_views
-# --- bioparams_values_views
-#	Values by stock of common parameter types
-# --- bioparams_units_views
-#	Units corresponding to values in bioparams_values_views
-# --- bioparams_ids_views
-#	Parameter IDs corresponding to values in bioparams_values_views
-# --- bioparams_assessments_views
-#	Assessment IDs corresponding to values in bioparams_values_views
-# --- bioparams_sources_views
-#	Sources corresponding to values in bioparams_values_views
-# --- bioparams_notes_views
-#	Notes corresponding to values in bioparams_values_views
-#
[…]

### 2020-08-06 scripts/01_data_wrangling.Rmd
added new FAO data and RAM data

@@
 # Packages
-library(knitr) 
-library(countrycode) # country name matching
-library(here)
-library(WDI) # World Bank GDP and population numbers by country
-library(janitor) # cleaning column names
-library(tidyverse)
-library(readxl)
+library(knitr) # Necessary to convert file to .html
+library(countrycode) # Country name matching
+library(here) # File path handling
+library(WDI) # World Bank World Development Indicators data
+library(janitor) # Column name handling
+library(tidyverse) # General data wrangling
+library(readxl) # Load .xlsx files
 
@@
 
-# Source helper file
+# Source file with helper functions (used throughout analysis)
 source(here::here("scripts", "00_helpers.R"))
@@
 sumaila_subsidies_path <- here::here("data", "raw", "Sumaila-et-al-2019-subsidies", "Subsidies_PEW_Final.xlsx")
-oecd_fse_path <- here::here("data", "raw", "OECD-2019-fse", "FISH_FSE_10032020183349581.csv")
+oecd_fse_path <- here::here("data", "raw", "OECD-fisheries-support-estimates", "FISH_FSE_10032020183349581.csv")
 schuhbauer_subsidies_ssf_path <- here::here("data", "raw", "Schuhbauer-et-al-2017-ssf-subsidies", "Subsidies_SSF_split_2018.csv")
@@
 ### Paths to other fisheries data files
-fao_production_path <- here::here("data", "raw", "FAO-2019-capture-production", "Capture_2019.1.0/")
+fao_production_path <- here::here("data", "raw", "FAO-global-capture-production", "Capture_2020.1.0/")
 #fao_value_path
 melnychuk_price_path <- here::here("data", "raw", "Melnychuk-et-al-2013-price", "Melnychuk_Exvessel_Price_Database.csv")
-ram_sadb_path <- here::here("data", "raw", "RAM-2018-stock-assessment-database", "RLSADB v4.40", "DB Files With Assessment Data", "RLSADB v4.40 (assessment data only).xlsx")
+ram_sadb_path <- here::here("data", "raw", "RAM-legacy-stock-assessment-database", "RAMLDB v4.491", "DB Files With Assessment Data", "RAMCore/")
 costello_upsides_path <- here::here("data", "raw", "Costello-et-al-2016-upsides", "ProjectionData_2012.csv")
 melnychuk_fmi_path <- here::here("data", "raw", "Melnychuk-et-al-2017-fmi", "fmi_values_country.csv")
-iuu_vessel_path <- here::here("data", "raw", "IUU-Vessel-List-2019", "IUUList-20190430.csv")
+iuu_vessel_path <- here::here("data", "raw", "combined-IUU-vessel-list", "IUUList-20190430.csv")
 
 ### Paths to other necessary files
-cap_tier_path <- here::here("data", "raw", "USA-Cap-Tier-Proposal", "US_cap_tier_data.csv")
+cap_tier_path <- here::here("data", "raw", "USA-cap-tier-proposal", "US_cap_tier_data.csv")
 country_lookup_path <- here::here("data", "lookup-tables", "country_dependencies.csv")
 fao_regions_for_ram_lookup_path <- here::here("data", "lookup-tables", "fao_areas_for_ram_stocks_v4.491.csv")
+sumaila_lookup_path <- here::here("data", "lookup-tables", "sumaila_subsidies_classification_lookup_table.csv")
+schuhbauer_lookup_path <- here::here("data", "lookup-tables", "schuhbauer_subsidies_classification_lookup_table.csv")
+oecd_fse_lookup_path <- here::here("data", "lookup-tables", "oecd_fse_classification_lookup_table.csv")
 ```
@@
 
-- Proposed tier assignments for a cap-based approach to limiting subsidies as included in the proposal made to the WTO by the US Delegation on May 3, 2019 [TN/RL/GEN/197/Rev.1].
+- Proposed tier assignments for a cap-based approach to limiting subsidies as included in the proposal made to the WTO by the delegations of Austraila and the USA on May 3, 2019 [TN/RL/GEN/197/Rev.1].
 
 - A manually compiled table of overseas dependencies of WTO Member and Observer countries
+
+- All subsidy types used by Sumaila et al. (2019)
+
+- All subsidy types used by the OECD FSE database
 
@@
 
-## Updated estimates and analysis of global fisheries subsidies from Sumaila et al. (2019)
+## Estimates of global fisheries subsidies from Sumaila et al. (2019)
 
@@
 # Load lookup table for classification scheme
-sumaila_lookup <- read_csv(here::here("data", "lookup-tables", "sumaila_subsidies_classification_lookup_table.csv"))
+sumaila_lookup <- read_csv(sumaila_lookup_path)
 
@@
 # Load OECD lookup table
-oecd_fse_lookup <- read_csv(here::here("data", "lookup-tables", "oecd_fse_classification_lookup_table.csv")) %>%
+oecd_fse_lookup <- read_csv(oecd_fse_lookup_path) %>%
   distinct(category, category_name, type, type_code, type_name)
@@
 write_csv(oecd_fse_dat_edit, paste0(app_data_dir, "oecd_2019_fse_tidy.csv"))
+
+```
+
+## Updated estimates of small-scale fisheries subsides from Schuhbauer et al. (2017)
+
+Note: these data are unpublished updates (in 2018 US\$) of the data described in Schuhbauer et al. (2017).
+
+```{r}
+# Load and wrangle data (2018 US$)
+schuhbauer_subsidies_ssf_dat <- read_csv(schuhbauer_subsidies_ssf_path) %>%
+  clean_names(case = "snake") %>%
+  mutate(iso3 = case_when(country == "Dominican Rp" ~ "DOM",
+                          country == "Micronesia" ~ "FSM",
+                          country == "Untd Arab Em" ~ "ARE",
+                          TRUE ~ countrycode(country, "country.name", "iso3c"))) %>%
+  mutate(prop_ssf = ssf_usd/constant_2018_usd) %>%
+  dplyr::select(iso3, old_type_name = type, prop_ssf) %>%
+  mutate(source = "Schuhbauer et al. (2017)") %>%
+  arrange(iso3)
+schuhbauer_subsidies_ssf_dat$prop_ssf[is.nan(schuhbauer_subsidies_ssf_dat$prop_ssf)] <- 0 # handling dividing by 0
+
+# Load lookup table
+schuhbauer_lookup <- read_csv(schuhbauer_lookup_path)
+
+# Clean up the naming/spelling of the classification scheme as well as data type
+schuhbauer_subsidies_ssf_dat_edit <- schuhbauer_subsidies_ssf_dat %>%
+  left_join(schuhbauer_lookup, by = c("old_type_name")) %>%
+  dplyr::select(iso3, category, category_name, type, type_name, prop_ssf, source)
+
+# Deal with the EU
+schuhbauer_subsidies_ssf_dat_eu <- read_csv(schuhbauer_subsidies_ssf_path) %>%
+  clean_names(case = "snake") %>%
+  mutate(iso3 = case_when(country == "Dominican Rp" ~ "DOM",
+                          country == "Micronesia" ~ "FSM",
+                          country == "Untd Arab Em" ~ "ARE",
+                          TRUE ~ countrycode(country, "country.name", "iso3c"))) %>%
+  dplyr::filter(iso3 %in% c(eu_countries, eu_territories)) %>%
+  mutate(entity = "EU") %>%
+  group_by(entity, type) %>%
+  summarize(constant_2018_usd = sum(constant_2018_usd, na.rm = T),
+            ssf_usd = sum(ssf_usd, na.rm = T)) %>%
+  ungroup() %>%
+  mutate(prop_ssf = ssf_usd/constant_2018_usd) %>%
+  dplyr::select(iso3 = entity, old_type_name = type, prop_ssf) %>%
+  mutate(source = "Schuhbauer et al. (2017)") %>%
+  left_join(schuhbauer_lookup, by = c("old_type_name")) %>%
+  dplyr::select(iso3, category, category_name, type, type_name, prop_ssf, source)
+
+# Add the EU back in
+schuhbauer_subsidies_ssf_dat_edit <- schuhbauer_subsidies_ssf_dat_edit %>%
+  bind_rows(schuhbauer_subsidies_ssf_dat_eu)
+
+# Save
+write_csv(schuhbauer_subsidies_ssf_dat_edit, paste0(data_dir, "schuhbauer_ssf_subsidies_proportions.csv"))
+write_csv(schuhbauer_subsidies_ssf_dat_edit, paste0(app_data_dir, "schuhbauer_ssf_subsidies_proportions.csv"))
 
@@
          units = "tonnes",
-         source = "FAO (2019)")
+         source = "FAO (2020)")
 
-write_csv(fao_production_dat_edit, paste0(data_dir, "fao_2019_capture_production_tidy.csv"))
+write_csv(fao_production_dat_edit, paste0(data_dir, "fao_2020_capture_production_tidy.csv"))
 
@@
 
-write_csv(fao_production_dat_edit_groups, paste0(data_dir, "fao_2019_capture_production_isscaap_groups_tidy.csv"))
-write_csv(fao_production_dat_edit_groups, paste0(app_data_dir, "fao_2019_capture_production_isscaap_groups_tidy.csv"))
+write_csv(fao_production_dat_edit_groups, paste0(data_dir, "fao_2020_capture_production_isscaap_groups_tidy.csv"))
+write_csv(fao_production_dat_edit_groups, paste0(app_data_dir, "fao_2020_capture_production_isscaap_groups_tidy.csv"))
 ```
@@
 cpi_2017 <- 245.120
+cpi_2018 <- 251.107
 
@@
 melnychuk_price_dat_extrapolation <- melnychuk_price_dat %>%
-  complete(nesting(scientific_name, asfis_species, isscaap_group, group_for_pairing), year = 2000:2017) %>%
+  complete(nesting(scientific_name, asfis_species, isscaap_group, group_for_pairing), year = 2000:2018) %>%
   left_join(melnychuk_price_dat_mry, by = c("scientific_name", "asfis_species", "isscaap_group", "group_for_pairing")) %>%
@@
                                        year == 2016 ~ exvessel_for_extrap * (cpi_2016/cpi_2012),
-                                       year == 2017 ~ exvessel_for_extrap * (cpi_2017/cpi_2012))) %>%
+                                       year == 2017 ~ exvessel_for_extrap * (cpi_2017/cpi_2012),
+                                       year == 2018 ~ exvessel_for_extrap * (cpi_2018/cpi_2012))) %>%
   dplyr::select(-exvessel, -exvessel_for_extrap) %>%
@@
 
-# Look at NAs - 9398 entries
+# Look at NAs - 10,023 entries
 combine_nas <- combine_catch_price_dat %>%
@@
          units = paste(year, "US$"),
-         source = "FAO (2019); Melnychuk et al. (2017)")
+         source = "FAO (2020); Melnychuk et al. (2017)")
 
@@
 
-## Stock status database
+## RAM Legacy Stock Assessment database
+
+```{r}
+# Load B/Bmsy timeseries from the RAM legacy stock assessment database
+ram_dat_bv_bmsy <- read_csv(paste0(ram_sadb_path, "BvB.csv")) %>%
+  rename(year = X1) %>%
+  gather(stockid, bv_bmsy, -year) %>%
+  na.omit() %>%
+  group_by(stockid) %>%
+  mutate(year_max = max(year)) %>%
+  ungroup() %>%
+  dplyr::filter(year == year_max)
+
+# Load lookup table applying FAO regions to the RAM stocks
+ram_lookup <- read_csv(fao_regions_for_ram_lookup_path)
+
+# Apply to RAM data and create a new row for each FAO region
+ram_dat_bv_bmsy_edit <- ram_dat_bv_bmsy %>%
+  left_join(ram_lookup, by = "stockid") %>%
+  mutate(region_fao = fao_area) %>%
+  mutate(region_fao_split = str_split(region_fao, ";")) %>%
+  unnest(cols = c(region_fao_split)) %>%
+  group_by(stockid) %>%
+  mutate(n_regions = n_distinct(region_fao_split)) %>%
+  ungroup()
+
+# Save clean
+write_csv(ram_dat_bv_bmsy_edit, paste0(data_dir, "RAMLDB_v4.491_bvmsy_tidy.csv"))
+```
+
+## Estimates of global stock status from Costello et al. (2016)
+
 ```{r}
@@
 
-# We need to split the entries that span multiple FAO regions...  
+# We need to split the entries that span multiple FAO regions 
 costello_upsides_dat_edit <- costello_upsides_dat %>%
@@
 ```
-
-# Section 4 - Other Data
 

### 2020-08-06 app/00_initialize_app.R

@@ -170,7 +170,7 @@ demographic_dat <- demo_dat_world_bank %>%
 
 # 1) FAO Cature Production by ISSCAAP Group (2000-2017)
 
-capture_production_dat_fao <- read_csv("./data/fao_2019_capture_production_isscaap_groups_tidy.csv") %>%
+capture_production_dat_fao <- read_csv("./data/fao_2020_capture_production_isscaap_groups_tidy.csv") %>%
   group_by(iso3, year) %>%
   mutate(prop_annual_total = value/sum(value)) %>%
   ungroup() %>%

### 2020-08-06 scripts/02_vessel_list.Rmd
vessel list done

@@
 
+# Path to cleaned ssf subsidy data file (2018)
+ssf_subsidy_prop_dat_path <- here::here("data", "edited", "schuhbauer_ssf_subsidies_proportions.csv")
+
 # Path to cleaned capture production data file
-catch_dat_path <- here::here("data", "edited", "fao_2019_capture_production_tidy.csv")
-catch_year <- 2017
+catch_dat_path <- here::here("data", "edited", "fao_2020_capture_production_tidy.csv")
+catch_year <- 2018
 
@@
 landed_value_dat_path <- here::here("data", "edited", "estimated_landed_value_tidy.csv")
-landed_value_year <- 2017
+landed_value_year <- 2018
 
@@
 make_figures <- FALSE
+
+# Temporary solution to bigrquery error (August 5, 2020) - see https://github.com/r-dbi/bigrquery/issues/395 for details
+options(scipen = 20)
 ```
@@
   distinct(flag_iso3) %>%
-  mutate(flag_name = countrycode(flag_iso3, "iso3c", "country.name"))
+  mutate(flag_name = countrycode(flag_iso3, "iso3c", "country.name")) %>%
+  arrange(flag_iso3)
 
@@
             landed_value = sum(landed_value, na.rm = T))
-
 ```
@@
 
-catch_no_matching_effort <- catch_revenue_flag %>%
-  anti_join(effort_flag, by = c("iso3" = "flag_iso3"))
-
-# There are 2 flag states for which we don't have reported catch data at all: CXR (Christmas Island), LIE (Liechtenstein) and NA (no flag).
-We're going to try assigning them based on the EEZ in which they spend the most time fishing instead.
+# There are some vessels for which we don't have flags. We're going to try assigning them based on the EEZ in which they spend the most time fishing instead. 
 vessels_no_catches <- vessel_list %>%
@@
 
-Now they all do and we can assign catches.
+Now we can assign catches.
 
@@
 
-# effort_flag
+# Verify again 
 effort_no_matching_catches <- effort_flag %>%
@@
 
-# Matches
-flag_region_matches <- effort_catch_region_matching %>%
+# Flag state-fao region pairings for which we have matching catch and effort data
+flag_region_matches <- effort_catch_flag_region_matching %>%
   dplyr::filter(is_flag_region_match)
@@
 ### -------------------
+# Apply catch/revenue rates by flag state-fao region pairings where available, otherwise use flag state rates
 comprehensive_catch_rates <- effort_catch_flag_region_matching %>%
@@
 
-The process for allocating subsidies is slightly more straightforard as we only have data by flag
+The process for allocating subsidies is slightly more straightforard as we only have data by flag. However we
 
@@
 
+# Load proportions going to SSF, and remove
+subsidies_dat_lsf <- read_csv(ssf_subsidy_prop_dat_path) %>%
+  dplyr::select(-source) %>%
+  left_join(subsidies_dat, by = c("iso3", "category", "category_name", "type", "type_name")) %>%
+  mutate(value_lsf = value*(1-prop_ssf))
+
 # Summarize total subsidies by type and flag
-subsidies_flag <- subsidies_dat %>%
+subsidies_flag <- subsidies_dat_lsf %>%
   group_by(iso3, type) %>%
-  summarize(value = sum(value, na.rm = T)) %>%
+  summarize(value = sum(value_lsf, na.rm = T)) %>%
   spread(type, value)
@@
 
-vessel_list <- vessel_list %>%
+vessel_list_out <- vessel_list %>%
   mutate(catch = fishing_KWh_eez_fao_ter*catch_per_fishing_KWh,
@@
 
-write_csv(vessel_list, paste0(results_dir, "vessel_list_2018_raw.csv"))
+write_csv(vessel_list_out, paste0(results_dir, "vessel_list_2018_raw.csv"))
 ```
@@
 # Summary by gear type
-vessels_by_gear <- vessel_list %>%
+vessels_by_gear <- vessel_list_out %>%
   group_by(vessel_class) %>%
   summarize(count = n_distinct(ssvid),
-            flag_states = n_distinct(flag),
+            flag_states = n_distinct(flag_iso3),
             fao_regions = n_distinct(fao_region),
@@
             engine_power_avg = mean(engine_power_kw, na.rm = T),
-            fishing_hours = sum(fishing_hours_eez_fao, na.rm = T))
+            fishing_hours = sum(fishing_hours_eez_fao_ter, na.rm = T),
+            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T))
 
@@
 # Total number of vessels
+n_gear_type_plot <- vessels_by_gear %>%
+  mutate(vessel_class = fct_re)
 ggplot(vessels_by_gear)+
-  aes(x = "", y = count, fill = vessel_class)+
+  aes(x = vessel_class, y = count, fill = vessel_class)+
   geom_bar(stat = "identity", width = 1, color = "grey4", size = 0.2)+
-  coord_polar("y")+
+  #coord_polar("y")+
   #scale_fill_tableau(name = "Flag State", palette = "Tableau 20")+
-  pie_theme+
-  labs(title = paste0("Number of vessels by vessel class | Total vessels: ", format(sum(vessels_by_gear$count), big.mark = ",")))
+  normal_theme+
+  labs(title = paste0("Number of vessels by class | Total vessels: ", format(sum(vessels_by_gear$count), big.mark = ",")))+
+  labs(x = "Gear Type", y = "Number of Vessels")+
+  guides(fill = "none")+
+  coord_flip()+
+  scale_y_continuous(expand = c(0,0))
 

### 2020-08-07 scripts/02_vessel_list.Rmd
plots

@@
 
-pie_theme <- normal_theme +
-  theme(
-    axis.line = element_blank(),
-    axis.title.x = element_blank(),
-    axis.text = element_blank(),
-    axis.title.y = element_blank(),
-    panel.border = element_blank(),
-    axis.ticks = element_blank()  )
-
-# Total number of vessels
+# Total number of vessels by gear type
 n_gear_type_plot <- vessels_by_gear %>%
-  mutate(vessel_class = fct_re)
-ggplot(vessels_by_gear)+
+  mutate(vessel_class = fct_reorder(vessel_class, count)) %>%
+  ggplot()+
   aes(x = vessel_class, y = count, fill = vessel_class)+
@@
   normal_theme+
-  labs(title = paste0("Number of vessels by class | Total vessels: ", format(sum(vessels_by_gear$count), big.mark = ",")))+
+  labs(title = paste0("Number of vessels by gear type | Total vessels: ", format(sum(vessels_by_gear$count), big.mark = ",")))+
   labs(x = "Gear Type", y = "Number of Vessels")+
@@
 
-# Flags using each gear types
-ggplot(vessels_by_gear)+
-  aes(x = fct_reorder(vessel_class, flag_states, .desc = TRUE), y = flag_states, fill = vessel_class)+
+ggsave(paste0(results_dir, "n_vessels_gear_type_plot.png"), n_gear_type_plot, width = 7.5, height = 6, units = "in")
+
+# Total number of vessels by flag
+vessels_by_flag_gear <- vessel_list_out %>%
+  group_by(flag_iso3, vessel_class) %>%
+  summarize(count = n_distinct(ssvid),
+            fao_regions = n_distinct(fao_region),
+            length_avg = mean(length_m, na.rm = T),
+            tonnage_avg = mean(tonnage_gt, na.rm = T),
+            engine_power_avg = mean(engine_power_kw, na.rm = T),
+            fishing_hours = sum(fishing_hours_eez_fao_ter, na.rm = T),
+            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T)) %>%
+  mutate(tot_count = sum(count)) %>%
+  ungroup()
+
+n_flag_plot <- vessels_by_flag_gear %>%
+  mutate(flag = fct_reorder(countrycode(flag_iso3, "iso3c", "country.name"), tot_count)) %>%
+  ggplot()+
+  aes(x = flag, y = log(count), fill = vessel_class)+
   geom_bar(stat = "identity", width = 1, color = "grey4", size = 0.2)+
+  #coord_polar("y")+
+  #scale_fill_tableau(name = "Flag State", palette = "Tableau 20")+
+  normal_theme+
+  labs(title = paste0("Number of vessels by flag state and gear type | Total vessels: ", format(sum(vessels_by_gear$count), big.mark = ",")))+
+  labs(x = "Flag State", y = "log(Number of Vessels)", fill = "Gear Type")+
+  coord_flip()+
   scale_y_continuous(expand = c(0,0))+
-  scale_fill_discrete(guide = "none")+
-  normal_theme +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
-  labs(title = paste0("Number of flag states using each vessel class | Total vessels: ", format(sum(vessels_by_gear$count), big.mark = ",")),
-       x = "Vessel Class",
-       y = "Number of Flag States")
+  theme(axis.text.y = element_text(size = 4, angle = 20))
+
+ggsave(paste0(results_dir, "n_vessels_flag_gear_type_plot.png"), n_flag_plot, width = 7.5, height = 10, units = "in")
 }

### 2020-08-07 scripts/01_data_wrangling.Rmd

@@
 
-This script handles the preliminary data wrangling for the raw datasets underlying the SubsidyExplorer analysis.
-It outputs tidyed data files to `r data_dir`.
+This script handles the preliminary data wrangling for the raw data sets underlying the SubsidyExplorer analysis.
+It outputs tidied data files to `r data_dir`.
 Some of these tidied data files are used directly as input data by the SubsidyExplorer toolkit (saved to `r app_data_dir`).
@@
 
-The RAM Legacy Stock Assessment Database is a compolation of stock assessments for commercially exploited species from around the world.
+The RAM Legacy Stock Assessment Database is a compilation of stock assessments for commercially exploited species from around the world.
 The latest version of this database (version 4.491) was downloaded directly from the RAM website on July 25, 2020 and are stored as `r ram_sadb_path`.
@@
 
-Estimates of stock status for comericlaly exploited species not included in the RAM Legacy Stock Assessment Database from Costello et al.
+Estimates of stock status for commercially exploited species not included in the RAM Legacy Stock Assessment Database from Costello et al.
 (2016).
@@
 
-- Proposed tier assignments for a cap-based approach to limiting subsidies as included in the proposal made to the WTO by the delegations of Austraila and the USA on May 3, 2019 [TN/RL/GEN/197/Rev.1].
+- Proposed tier assignments for a cap-based approach to limiting subsidies as included in the proposal made to the WTO by the delegations of Australia and the USA on May 3, 2019 [TN/RL/GEN/197/Rev.1].
 
@@
 
-- A manually compiled table of FAO statistical regions coorepsonding to the stocks contained in version 4.491 of the RAM Legacy Stock Assessment Database.
+- A manually compiled table of FAO statistical regions corresponding to the stocks contained in version 4.491 of the RAM Legacy Stock Assessment Database.
 
@@
 
-The naming of flag and coastal states varies widely across our data sources and we recognize that this can be a politially sensitive matter.
+The naming of flag and coastal states varies widely across our data sources and we recognize that this can be a politically sensitive matter.
 For the purposes of merging multiple data sources, we therefore translate all state names from the raw data sources to ISO-3 character codes.

### 2020-08-07 scripts/02_vessel_list.Rmd

@@
 # Do you wnat to make figures? 
-make_figures <- FALSE
+make_plots <- FALSE
+
+# Few more packages if you're making figures
+if(make_plots){
+  library(forcats)
+}
 
@@
 
-Quick summary of our global vessel list by gear type:
-
 ```{r}
-if(make_figures){
+if(make_plots){
 # Summary by gear type

### 2020-08-07 scripts/03_management.Rmd

@@
 
-# Few more packages if you're making figures
+# Few more packages and dataif you're making figures
 if(make_plots){
+
   library(ggridges)
@@
   library(scales)
+  library(sf)
+
+  # 1) World map ---
+  world <- read_sf(here::here("app", "data", "shapefiles", "ne_50m_admin_SubsidyExplorer"), layer = "land_50m")
+
+  # 2) EEZs/FAO regions ---
+  eez_fao <- read_sf(dsn = here::here("app", "data", "shapefiles", "eez-v10-fao-combined-simple"), layer="eez_v10_fao_combined_simple") %>%
+    mutate(eez_hs_code = ifelse(!is.na(zone), paste0("HS-",zone), as.character(mrgid)))
+
 }
@@
 
+```
+
+```{r}
+if(make_plots){
+
+  # Summarize data
+    fmi_map_dat <- eez_fao %>%
+      left_join(eez_management_indices %>% mutate(eez_hs_code = as.character(eez_id)), by = c("eez_hs_code")) %>%
+      mutate(fmi_best = ifelse(is.na(fmi_best), 0.21, fmi_best))
+
+  fmi_map <- ggplot()+
+    geom_sf(data = world, fill = "black", color = "grey", size = 0.25)+
+    geom_sf(data = fmi_map_dat, aes(fill = fmi_best), color = "grey", size = 0.25)+
+    theme_bw()+
+    scale_fill_distiller(palette = "YlGn", 
+                         direction = 1,
+                         limits = c(0.2, 1))+
+    labs(fill = "FMI Score")
+
+  ggsave(paste0(results_dir, "fmi_score_map.png"), width = 7.5, units = "in")
+}
 ```

### 2020-08-07 scripts/04_model_parameterization.Rmd

@@
 global_model_parameters <- global_model_parameters %>%
-  bind_rows(tibble(parameter = "MSY", value = global_msy, source = "Costello et al. 2016"))
+  bind_rows(tibble(parameter = "msy", value = global_msy, source = "Costello et al. 2016"))
 
@@
 global_model_parameters <- global_model_parameters %>%
-  bind_rows(tibble(parameter = "K", value = global_k, source = "Costello et al. 2016; World Bank 2017"))
+  bind_rows(tibble(parameter = "k", value = global_k, source = "Costello et al. 2016; World Bank 2017"))
 ```
@@
 global_model_parameters <- global_model_parameters %>%
-  bind_rows(tibble(parameter = "r", value = global_g, source = "Costello et al. 2016"))
+  bind_rows(tibble(parameter = "r", value = global_r, source = "Costello et al. 2016"))
 ```
@@
 global_model_parameters <- global_model_parameters %>%
-  bind_rows(tibble(parameter = "B0", value = global_b0, source = "FAO 2019; World Bank 2017"))
+  bind_rows(tibble(parameter = "b0", value = global_b0, source = "FAO 2019; World Bank 2017"))
 ```
@@
 regional_model_parameters <- regional_model_parameters %>%
-  bind_rows(c("parameter" = "MSY", "source" = "Costello et al. 2016", regional_msy))
+  bind_rows(c("parameter" = "msy", "source" = "Costello et al. 2016", regional_msy))
 ```
@@
 regional_model_parameters <- regional_model_parameters %>%
-  bind_rows(c("parameter" = "K", "source" = "Costello et al. 2016; World Bank 2017", regional_k))
+  bind_rows(c("parameter" = "k", "source" = "Costello et al. 2016; World Bank 2017", regional_k))
 ```

### 2020-08-07 scripts/06_run_model.Rmd

@@
 # Source model script
+source(here::here("app", "scripts", "BioEconModel.R"))
+```
+
+```{r}
+# Load vessel list
+pro_rate_subsidies <- F
+
+vessel_dat <- read.csv(here::here("app", "data", "vessel_list_2018_final.csv"), stringsAsFactors = F)
+
+if(pro_rate_subsidies == T){
+
+  vessel_dat <- vessel_dat %>%
+    mutate(B1_subs = B1_subs * 0.54, # boat construction/renovation - matched to payments based on vessels
+           B2_subs = B2_subs * 1, # fishery development projects/support services - matched to payments based on variable use
+           B3_subs = B3_subs * 0.87, # port construction and renovation - matched to payments based on vessels
+           B4_subs = B4_subs * 0.87, # price/marketing support, processing infrastructure - matched to payments based on output
+           B5_subs = B5_subs * 0.76, # non-fuel tax exemptions - matched to payments based on fishers income
+           B6_subs = B6_subs * 0.56, # foreign access agreements - matched to payments based on fishers own capital
+           B7_subs = B7_subs * 0.84, # fuel - matched to payments based on fuel use
+           bad_subs = (B1_subs + B2_subs + B3_subs + B4_subs + B5_subs + B6_subs + B7_subs))
+
+}
+
+vessel_dat <- vessel_dat %>%
+  mutate(eez_hs_code = case_when(eez_id == 0 ~ paste0("HS-", fao_region),
+                                 TRUE ~ as.character(eez_id)))
+```
+
+```{r}
+# Load biological parameters for the model
+bio_dat_global <- read.csv(here::here("app", "data", "model_parameters_global.csv"))
+bio_dat_regional <- read.csv(here::here("app", "data", "model_parameters_regional.csv"))
+
+# Regional parameter list
+bio_dat_regional_list <- bio_dat_regional %>%
+  gather(region, value, -c(1:2)) %>%
+  group_by(region) %>%
+  group_split()
+```
+
+```{r}
+# Get WTO countries territories
+```
+
+```{r}
+# Threshold to be considered managed
+managed_cutoff <- 0.66
+```
+
+## Create global fleet
+
+```{r pressure, echo=FALSE}
+# Assign fleets to vessels
+global_fleet_vessels <- vessel_dat %>%
+  mutate(is_WTO = ifelse(flag_iso3 %in% c(cap_tier_dat$iso3, eu_countries, eu_territories, us_territories, norwegian_territories), T, F)) %>%
+  mutate(fleet = case_when(is_WTO & fmi_best >= managed_cutoff & bad_subs > 0 ~ "affected_managed",
+                           is_WTO & fmi_best < managed_cutoff & bad_subs > 0 ~ "affected_oa",
+                           (!is_WTO & fmi_best >= managed_cutoff) ~ "unaffected_managed",
+                           (!is_WTO & fmi_best < managed_cutoff) ~ "unaffected_oa",
+                           TRUE ~ "unaffected_oa"))
+
+# Create fleet (summary)
+global_fleet_summary <- global_fleet_vessels %>%
+  group_by(region, fleet) %>%
+  summarize(catch = sum(catch, na.rm = T),
+            bad_subs = sum(bad_subs, na.rm = T),
+            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
+            removed_subs = sum(bad_subs, na.rm = T))
+```
+
+## Run Model (Remove all bad subsidies)
+
+```{r}
 
 ```
-
-## Including Plots
-
-You can also embed plots, for example:
-
-```{r pressure, echo=FALSE}
-plot(pressure)
-```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2020-08-07 scripts/03_management.Rmd
management

@@
 
-The purpose of this script is to assign management scores to all of our vessels, such that they can later be classified into three different management regimes: 
-- Well-managed
-- Managed
-- Open access
+The purpose of this script is to assign management scores to all of our vessels, such that they can later be classified into different management regimes.
+The idea being that fisheries with effective management controls in place are less likely to see as large of changes in fishing effort resulting from subsidy reforms (e.g., Subsidies are likely to be less coupled with effort in well-managed fisheries; effort is instead likely dictated more by management).
 
@@
 # Make figures?
-make_plots <- F
+make_plots <- T
 
@@
     mutate(eez_hs_code = ifelse(!is.na(zone), paste0("HS-",zone), as.character(mrgid)))
+
+  # 3) Just FAO regions ---
+  fao_areas <- read_sf(here::here("data", "shapefiles", "fao"), layer = "World_Fao_Zones")
 
@@
 
-## Assign FMI indicies to regions
+## Assign FMI indices to regions
 
@@
 
+  # Map by EEZ/FAO area
   fmi_map <- ggplot()+
@@
                          limits = c(0.2, 1))+
-    labs(fill = "FMI Score")
+    labs(fill = "FMI Score")+
+    theme(plot.background = element_rect(color = NA),
+          panel.border = element_rect(color = NA))
 
-  ggsave(paste0(results_dir, "fmi_score_map.png"), width = 7.5, units = "in")
+  fmi_map
+
+  ggsave(paste0(results_dir, "fmi_score_map.png"), width = 7.5, height = 4, units = "in")
 }
@@
             fvfmsy_w_mean_region = weighted.mean(fv_fmsy, w = msy, na.rm = T)) %>%
-  dplyr::select(fao_region = region_fao_split, fvfmsy_med_region)
+  dplyr::select(fao_region = region_fao_split, fvfmsy_med_region, fvfmsy_mean_region, fvfmsy_w_mean_region)
 ```
 
-# Median fishing pressure by FAO region and state
+```{r}
+if(make_plots){
 
-```{r}
-# median_fvfmsy_fao_flag <- costello_2016_upsides_dat %>%
-#   group_by(iso3, region_fao_split) %>%
-#   summarize(fvfmsy_med_eez = median(fv_fmsy, na.rm = T),
-#             fvfmsy_mean_eez = mean(fv_fmsy, na.rm = T),
-#             fvfmsy_w_mean_eez = weighted.mean(fv_fmsy, w = msy, na.rm = T)) %>%
-#   dplyr::select(iso3, fao_region = region_fao_split, fvfmsy_med_eez)
+  # Summarize data
+    fvfmsy_map_dat <- fao_areas %>%
+      rename(fao_region = zone) %>%
+      left_join(median_fvfmsy_fao, by = "fao_region") %>%
+      gather(metric, value, 3:5) %>%
+      mutate(metric = str_replace(str_replace(metric, "fvfmsy_", ""), "_region", ""),
+             metric_display = case_when(metric == "med" ~ "Median",
+                                        metric == "w_mean" ~ "Weighted Mean",
+                                        metric == "mean" ~ "Mean"))
+
+  # Map by EEZ/FAO area
+  fvfmsy_map <- ggplot()+
+    geom_sf(data = world, fill = "black", color = "grey", size = 0.25)+
+    geom_sf(data = fvfmsy_map_dat, aes(fill = value), color = "grey", size = 0.25)+
+    theme_bw()+
+    scale_fill_gradient2(low = "blue",
+                         high = 'red',
+                         mid = "white",
+                         midpoint = 1,
+                         limits = c(0,5),
+                         oob = scales::squish)+
+    labs(fill = "F/Fmsy")+
+    theme(plot.background = element_rect(color = NA),
+          panel.border = element_rect(color = NA))+
+    facet_wrap(~metric_display, ncol = 1)
+
+  fvfmsy_map
+
+  ggsave(paste0(results_dir, "fvfmsy_map.png"), width = 7.5, height = 9.5, units = "in")
+}
 ```
@@
 
-In order to include flag state, we would need to fix this one - How to treat "multinational" stocks. These should be attributed to all flag states that are fishing in those fisheries.
-
-```{r}
-prop_assessed_stocks <- costello_2016_upsides_dat %>%
-  group_by(region_fao_split) %>%
-  summarize(catch_ram = sum(catch[dbase == "RAM"]),
-            catch_other = sum(catch[dbase != "RAM"])) %>%
-  mutate(catch_prop_ram = catch_ram/(catch_ram + catch_other)) %>%
-  dplyr::select(fao_region = region_fao_split, catch_prop_ram)
-```
+# ```{r}
+# prop_assessed_stocks <- costello_2016_upsides_dat %>%
+#   group_by(region_fao_split) %>%
+#   summarize(catch_ram = sum(catch[dbase == "RAM"]),
+#             catch_other = sum(catch[dbase != "RAM"])) %>%
+#   mutate(catch_prop_ram = catch_ram/(catch_ram + catch_other)) %>%
+#   dplyr::select(fao_region = region_fao_split, catch_prop_ram)
+# ```
 
@@
 
-```{r}
-prop_catch_share_stocks <- costello_2016_upsides_dat %>%
-  group_by(region_fao_split) %>%
-  summarize(catch_share= sum(catch[catch_share == 1]),
-            catch_other = sum(catch[catch_share != 1])) %>%
-  mutate(catch_prop_cs= catch_share/(catch_share + catch_other)) %>%
-  dplyr::select(fao_region = region_fao_split, catch_prop_cs)
-```
+# ```{r}
+# prop_catch_share_stocks <- costello_2016_upsides_dat %>%
+#   group_by(region_fao_split) %>%
+#   summarize(catch_share= sum(catch[catch_share == 1]),
+#             catch_other = sum(catch[catch_share != 1])) %>%
+#   mutate(catch_prop_cs= catch_share/(catch_share + catch_other)) %>%
+#   dplyr::select(fao_region = region_fao_split, catch_prop_cs)
+# ```
 
@@
   left_join(eez_management_indices, by = c("eez_id")) %>%
-  left_join(median_fvfmsy_fao, by = c("fao_region")) %>%
-  left_join(prop_assessed_stocks, by = c("fao_region")) %>%
-  left_join(prop_catch_share_stocks, by = c("fao_region"))
+  left_join(median_fvfmsy_fao, by = c("fao_region"))
+  # left_join(prop_assessed_stocks, by = c("fao_region")) %>%
+  # left_join(prop_catch_share_stocks, by = c("fao_region"))
 
@@
 vessel_list_manage$fvfmsy_med_region[is.na(vessel_list_manage$fvfmsy_med_region)] <- 1
-vessel_list_manage$catch_prop_ram[is.na(vessel_list_manage$catch_prop_ram)] <- 0
-vessel_list_manage$catch_prop_cs[is.na(vessel_list_manage$catch_prop_cs)] <- 0
+vessel_list_manage$fvfmsy_mean_region[is.na(vessel_list_manage$fvfmsy_mean_region)] <- 1
+vessel_list_manage$fvfmsy_w_mean_region[is.na(vessel_list_manage$fvfmsy_w_mean_region)] <- 1
 
@@
 
-fvfmsy_quantile <- tibble("indicator" = "fvfmsy") %>%
+fvfmsy_med_quantile <- tibble("indicator" = "fvfmsy_median") %>%
   bind_cols(setNames(as.data.frame(matrix(quantile(vessel_list_manage$fvfmsy_med_region), nrow = 1)), names(quantile(vessel_list_manage$fvfmsy_med_region))))
 
-catch_ram_quantile <- tibble("indicator" = "catch_prop_ram") %>%
-  bind_cols(setNames(as.data.frame(matrix(quantile(vessel_list_manage$catch_prop_ram), nrow = 1)), names(quantile(vessel_list_manage$catch_prop_ram))))
+fvfmsy_mean_quantile <- tibble("indicator" = "fvfmsy_mean") %>%
+  bind_cols(setNames(as.data.frame(matrix(quantile(vessel_list_manage$fvfmsy_mean_region), nrow = 1)), names(quantile(vessel_list_manage$fvfmsy_mean_region))))
 
-catch_cs_quantile <- tibble("indicator" = "catch_prop_cs") %>%
-  bind_cols(setNames(as.data.frame(matrix(quantile(vessel_list_manage$catch_prop_cs), nrow = 1)), names(quantile(vessel_list_manage$catch_prop_cs))))
+fvfmsy_w_mean_quantile <- tibble("indicator" = "fvfmsy_w_mean") %>%
+  bind_cols(setNames(as.data.frame(matrix(quantile(vessel_list_manage$fvfmsy_w_mean_region), nrow = 1)), names(quantile(vessel_list_manage$fvfmsy_w_mean_region))))
 
 indicator_quantiles <- fmi_quantile %>%
-  bind_rows(fvfmsy_quantile) %>%
-  bind_rows(catch_ram_quantile) %>%
-  bind_rows(catch_cs_quantile)
+  bind_rows(fvfmsy_med_quantile) %>%
+  bind_rows(fvfmsy_mean_quantile) %>%
+  bind_rows(fvfmsy_w_mean_quantile)
 
@@
 
-# Summary plots
-
-## Coorelation between average FMI by flag/fao region and subsidy provisioning
-
 ```{r}
-if(make_plots){
-
-# FMI by flag and FAO from vessel list
-fmi_flag_fao <- vessel_list_manage %>%
-  group_by(flag) %>%
-  mutate(tot_bad_subs = sum(bad_subs),
-         tot_fuel_subs = sum(B7_subs)) %>%
-  ungroup() %>%
-  group_by(flag, fao_region) %>%
-  summarize(fmi_weighted_avg = weighted.mean(fmi_best, catch),
-            tot_bad_subs = unique(tot_bad_subs),
-            tot_fuel_subs = unique(tot_fuel_subs))
-
-ggplot(fmi_flag_fao)+
-  aes(x = tot_bad_subs, y = fmi_weighted_avg)+
-  geom_point()+
-  theme_linedraw()+
-  labs(x = "Total capacity-enhancing subsidies (2018 $US)",
-       y = "Mean Weighted FMI")+
-  scale_y_continuous(limits = c(0,1))+
-  scale_x_continuous(labels = comma)
-
-# FMI by flag from vessel list
-fmi_flag <- vessel_list_manage %>%
-  group_by(flag) %>%
-  mutate(tot_bad_subs = sum(bad_subs),
-         tot_fuel_subs = sum(B7_subs)) %>%
-  ungroup() %>%
-  group_by(flag) %>%
-  summarize(fmi_weighted_avg = weighted.mean(fmi_best, catch),
-            tot_bad_subs = unique(tot_bad_subs),
-            tot_fuel_subs = unique(tot_fuel_subs))
-
-ggplot(fmi_flag)+
-  aes(x = tot_bad_subs, y = fmi_weighted_avg)+
-  geom_point()+
-  theme_linedraw()+
-  labs(x = "Total capacity-enhancing subsidies (2018 $US)",
-       y = "Mean Weighted FMI")+
-  scale_y_continuous(limits = c(0,1))+
-  scale_x_continuous(labels = comma)
-
-countries_to_highlight <- c("CHN", "USA", "IDN", "JPN", "ISL", "THA")
-
-# FMI by just from Melnychuk et al
-fmi_flag_melnychuk_only <- vessel_list_manage %>%
-  group_by(flag) %>%
-  summarize(tot_bad_subs = sum(bad_subs),
-         tot_fuel_subs = sum(B7_subs),
-         tot_landings = sum(catch)) %>%
-  right_join(melnychuk_2017_mgmt_dat, by = c("flag" = "iso3")) %>%
-  mutate(display_name = case_when(flag %in% countries_to_highlight ~ countrycode(flag, "iso3c", "country.name")))
-
-# plot
-ggplot(fmi_flag_melnychuk_only)+
-  aes(x = tot_bad_subs/1e6, y = fmi_weighted, size = tot_landings/1e6, color = display_name)+
-  geom_point()+
-  geom_text_repel(aes(label = display_name), size = 4, force = 100, point.padding = 0.25, box.padding = 1)+
-  theme_linedraw()+
-  labs(x = "Total capacity-enhancing subsidies (million 2018 $US)",
-       y = "Weighted FMI")+
-  scale_y_continuous(limits = c(0,1))+
-  scale_x_continuous(labels = comma)+
-  scale_size(range = c(2,8), breaks = c(5,10,15), limits = c(0,15), name = "Marine Capture Production (million mt, 2017)")+
-  theme(legend.position = "top")+
-  scale_color_discrete(guide = "none")
-
-ggsave(paste0(results_dir, "fmi_flag_melnychuk_allbad.png"), width = 7, height = 4.5, units = "in")
-
-# Plot fuel subsidies only 
-ggplot(fmi_flag_melnychuk_only)+
-  aes(x = tot_fuel_subs/1e6, y = fmi_weighted, size = tot_landings/1e6, color = display_name)+
-  geom_point()+
-  geom_text_repel(aes(label = display_name), size = 4, force = 100, point.padding = 0.25, box.padding = 1)+
-  theme_linedraw()+
-  labs(x = "Total fuel subsidies (million 2018 $US)",
-       y = "Weighted FMI")+
-  scale_y_continuous(limits = c(0,1))+
-  scale_x_continuous(labels = comma)+
-  scale_size(range = c(2,8), breaks = c(5,10,15), limits = c(0,15), name = "Marine Capture Production (million mt, 2017)")+
-  theme(legend.position = "top")+
-  scale_color_discrete(guide = "none")
-
-ggsave(paste0(results_dir, "fmi_flag_melnychuk_fuel.png"), width = 7, height = 4.5, units = "in")
-
-}
+# if(make_plots){
+#   
+#   # Summarize data
+#   density_dat <- vessel_list_manage %>%
+#     dplyr::select(fmi_best, fvfmsy_med_region, fvfmsy_mean_region, fvfmsy_w_mean_region)
+#   
+#   probs <- c(0, 1/3, 2/3, 1)
+#   
+#   # Make FMI density plot (across all vessels)
+#   fmi_density <- density(density_dat$fmi_best)
+#   
+#   fmi_density_plot_dat <- data.frame(name = "FMI Score", x = fmi_density$x, y = fmi_density$y)
+#  
+#   fmi_quantiles <- quantile(fmi_density_plot_dat$y, prob=probs)
+#   fmi_density_plot_dat$quant <- factor(findInterval(fmi_density_plot_dat$x, fmi_quantiles))
+#   
+#   fmi_density_plot <- ggplot(fmi_density_plot_dat, aes(x,y)) + 
+#     geom_line() + 
+#     geom_ribbon(aes(ymin=0, ymax=y, fill=quant)) + 
+#     scale_y_continuous(expand = c(0,0)) + 
+#     scale_fill_manual(labels = c("0-33%", "33-66%", "66-100%"), values = brewer.pal(3, "Blues"), name = "Quantile")+
+#     labs(x = "FMI Score", y = "Kernal Density")+
+#     theme_bw()
+# 
+#   # Make median F/Fmsy density plot (across all vessels)
+#   med_density <- density(density_dat$fvfmsy_med_region)
+# 
+#   med_density_plot_dat <- data.frame(name = "Median F/Fmsy", x = med_density$x, y = med_density$y)
+#   
+#   med_quantiles <- quantile(med_density_plot_dat$y, prob=probs)
+#   med_density_plot_dat$quant <- factor(findInterval(med_density_plot_dat$x, med_quantiles))
+#   
+#   med_density_plot <- ggplot(med_density_plot_dat, aes(x,y)) + 
+#     geom_line() + 
+#     geom_ribbon(aes(ymin=0, ymax=y, fill=quant)) + 
+#     scale_y_continuous(expand = c(0,0)) + 
+#     scale_fill_manual(labels = c("66-100%"), values = brewer.pal(3, "Blues")[3], name = "Quantile")+
+#     labs(x = "Median F/Fmsy", y = "Kernal Density")+
+#     theme_bw()
+#   
+#   # Make mean F/Fmsy density plot (across all vessels)
+#   mean_density <- density(density_dat$fvfmsy_mean_region)
+# 
+#   mean_density_plot_dat <- data.frame(name = "Mean F/Fmsy", x = mean_density$x, y = mean_density$y)
+#   
+#   mean_quantiles <- quantile(mean_density_plot_dat$y, prob=probs)
+#   mean_density_plot_dat$quant <- factor(findInterval(mean_density_plot_dat$x, mean_quantiles))
+#   
+#   mean_density_plot <- ggplot(mean_density_plot_dat, aes(x,y)) + 
+#     geom_line() + 
+#     geom_ribbon(aes(ymin=0, ymax=y, fill=quant)) + 
+#     scale_y_continuous(expand = c(0,0)) + 
+#     scale_fill_manual(labels = c("66-100%"), values = brewer.pal(3, "Blues")[3], name = "Quantile")+
+#     labs(x = "Mean F/Fmsy", y = "Kernal Density")+
+#     theme_bw()
+#   
+#   # Make weighted mean F/Fmsy density plot (across all vessels)
+#   w_mean_density <- density(density_dat$fvfmsy_w_mean_region)
+# 
+#   w_mean_density_plot_dat <- data.frame(name = "Weight. Mean F/Fmsy", x = w_mean_density$x, y = w_mean_density$y)
+#   
+#   w_mean_quantiles <- quantile(w_mean_density_plot_dat$y, prob=probs)
+#   w_mean_density_plot_dat$quant <- factor(findInterval(w_mean_density_plot_dat$x, w_mean_quantiles))
+#   
+#   w_mean_density_plot <- ggplot(w_mean_density_plot_dat, aes(x,y)) + 
+#     geom_line() + 
+#     geom_ribbon(aes(ymin=0, ymax=y, fill=quant)) + 
+#     scale_y_continuous(expand = c(0,0)) + 
+#     scale_fill_manual(labels = c("66-100%"), values = brewer.pal(3, "Blues")[3], name = "Quantile")+
+#     labs(x = "Weight. Mean F/Fmsy", y = "Kernal Density")+
+#     theme_bw()
+#     
+# }
 ```
@@
 ```{r}
-# For later use, get fraction of catch in each region from catch share fisheries, vs. not
-# costello_catch_share_frac <- costello_2016_dat_edit %>%
-#   group_by(region, catch_share) %>%
-#   summarize(landings = sum(catch_new, na.rm = T)) %>%
-#   ungroup() %>%
-#   group_by(region) %>%
-#   mutate(tot_landings = sum(landings, na.rm = T)) %>%
-#   ungroup() %>%
-#   mutate(frac_landings = landings/tot_landings) %>%
-#   arrange(region)
+
 ```

### 2020-08-07 scripts/04_model_parameterization.Rmd
model param updated

@@
 This script handles the preliminary data wrangling necessary to create the biological parameters for the bio-economic model underlying the SubsidyExplorer toolkit.
-It outputs two CSV files used by the SubsidyExplorer toolkit (located in `r here::here("WTOToolkit", "data")`):
-- model_parameters_global.csv
-- model_parameters_regional.csv
+It allows for specification of different regional configurations, though we have selected the one for which we believe the data is most supportive.
 
@@
 vessel_list_path <- here::here("results", "03-management", "vessel_list_2018_management.csv")
-```
 
-In addition to the data sources described in the inital data wrangling script, we also draw on the folloing data sources:
-
-- Bioeconomic model parameters from both of the World Bank's Sunken Billions Reports (2009 and 2017). 
-> World Bank, & FAO.
-(2009).
-The Sunken Billions: The Economic Justification for Fisheries Reform.
-Retrieved from https://siteresources.worldbank.org/EXTARD/Resources/336681-1224775570533/SunkenBillionsFinal.pdf
-> World Bank. (2017). The Sunken Billions Revisited: Progress and Challenges in Global Marine Fisheries. Retrieved from https://openknowledge.worldbank.org/handle/10986/24056
-
-```{r setup, include=FALSE}
 # Code options
@@
 
+# Select number of regions (choices are 3 or 6)
+n_regions <- 3
+
+```
+
+In addition to the data sources described in the inital data wrangling script, we also draw on the folloing sources:
+
+- Bioeconomic model parameters from both of the World Bank's Sunken Billions Reports (2009 and 2017). 
+> World Bank, & FAO.
+(2009).
+The Sunken Billions: The Economic Justification for Fisheries Reform.
+Retrieved from https://siteresources.worldbank.org/EXTARD/Resources/336681-1224775570533/SunkenBillionsFinal.pdf
+> World Bank. (2017). The Sunken Billions Revisited: Progress and Challenges in Global Marine Fisheries. Retrieved from https://openknowledge.worldbank.org/handle/10986/24056
+
+```{r}
+if(n_regions == 3){
+
   # Define regions 
-region_names <- sort(c("atlantic_e", "atlantic_w", "indian", "pacific_e", "pacific_w", "polar"))
+  region_names <- sort(c("atlantic", "indian", "pacific"))
+
+  # Create a tidy df with the cooresponding fao regions
+  regions_tidy <- tibble(
+    region = region_names,
+    fao_region = list(c(21, 27, 31, 37, 34, 41, 47, 48), # atlantic (and med)
+                      c(51, 57, 58), # indian
+                      c(18, 61, 67, 71, 77, 81, 87, 88)) # pacific 
+  ) %>%
+    unnest(cols = c(fao_region))
+
+  # Also create a blank tibble with regions as column names
+  regions_spread <- setNames(data.frame(matrix(ncol = length(region_names), nrow = 0)), as.character(region_names))
+
+  # Now make empty output tables for both our global parameters, and for our regional parameters
+  global_model_parameters <- tibble(parameter = character(0), value = numeric(0), source = character(0))
+
+  regional_model_parameters <- tibble(parameter = character(0), source = character(0)) %>%
+    bind_cols(regions_spread) %>%
+    mutate(atlantic = as.character(atlantic),
+           indian = as.character(indian),
+           pacific = as.character(pacific))
+}
+```
+
+```{r setup, include=FALSE}
+if(n_regions == 6){
+
+# Define regions 
+region_names <- sort(c("atlantic_e", "atlantic_w", "indian", "pacific_e", "pacific_w", "polar")) # ran into difficulties with the polar region. 6 regions needs more work
 
@@
   bind_cols(regions_spread)
+
+}
 ```
@@
 
-We assume $\phi = 1.188$ based on literature for all (Thorson et al. 2012; World Bank 2017).
+We assume $\phi = 1.188$ based on literature for all (Thorson et al. 2012; World Bank 2017; Costello et al. 2016).
 
@@
 # One estimate of global carrying capacity
-global_k <- sum(costello_2016_dat$k)/0.78
-#global_k <- global_msy*9.1
+global_k <- global_msy*9.1
 
@@
 global_model_parameters <- global_model_parameters %>%
-  bind_rows(tibble(parameter = "g", value = global_g, source = "Costello et al. 2016"))
+  bind_rows(tibble(parameter = "g", value = global_g, source = "Calculated"))
 
@@
 global_model_parameters <- global_model_parameters %>%
-  bind_rows(tibble(parameter = "r", value = global_r, source = "Costello et al. 2016"))
+  bind_rows(tibble(parameter = "r", value = global_r, source = "Calculated"))
 ```
@@
 
-$$ h_0+ \xi =\frac{\phi + 1}{\phi} r b_{0}\Bigg(1 - \bigg(\frac{b_{0}}{K}\bigg)^{\phi}\Bigg)$$
+$$ h_0+ \xi =\frac{\phi + 1}{\phi} g b_{0}\Bigg(1 - \bigg(\frac{b_{0}}{K}\bigg)^{\phi}\Bigg)$$
 
@@
 global_model_parameters <- global_model_parameters %>%
-  bind_rows(tibble(parameter = "h0", value = global_h0, source = "FAO 2019"))
+  bind_rows(tibble(parameter = "h0", value = global_h0, source = "FAO 2020"))
 ```
@@
 # Estimation of starting biomass
-biomass_vec <- seq(0, 0.5*global_k, length.out = 10000)
+biomass_vec <- seq(0, 0.75*global_k, length.out = 1000000)
 growth_approx <- (((phi+1)/phi)*global_g*biomass_vec*(1-((biomass_vec/global_k)^phi)))
@@
 We also apply our bio-economic model of fisheries subsidies reform on a regional basis.
-For this analysis, we have chosen to use six regions based loosly on the major ocean basins and using the FAO statistical regions as subdivisions as needed to further separate regions: Atlantic Ocean (East) and Mediterranean [`r paste(regions_tidy$fao_region[regions_tidy$region == "atlantic_e"], collapse = ", ")`], Atlantic Ocean (West) [`r paste(regions_tidy$fao_region[regions_tidy$region == "atlantic_w"], collapse = ", ")`], Indian Ocean [`r paste(regions_tidy$fao_region[regions_tidy$region == "indian"], collapse = ", ")`], Pacific Ocean (East) [`r paste(regions_tidy$fao_region[regions_tidy$region == "pacific_e"], collapse = ", ")`], Pacific Ocean (West) [`r paste(regions_tidy$fao_region[regions_tidy$region == "pacific_w"], collapse = ", ")`], and Polar Oceans [`r paste(regions_tidy$fao_region[regions_tidy$region == "polar"], collapse = ", ")`].
 
@@
 # Extract carrying capacity
-#regional_k <- regional_msy*9.1
-regional_k <- round(costello_2016_dat_regional$k/0.78)
-names(regional_k) <- region_names
+regional_k <- regional_msy*9.1
 
@@
 regional_model_parameters <- regional_model_parameters %>%
-  bind_rows(c("parameter" = "g", "source" = "Costello et al. 2016", regional_g))
+  bind_rows(c("parameter" = "g", "source" = "Calculated", regional_g))
 
@@
 regional_model_parameters <- regional_model_parameters %>%
-  bind_rows(c("parameter" = "r", "source" = "Costello et al. 2016", regional_r))
+  bind_rows(c("parameter" = "r", "source" = "Calculated", regional_r))
 ```
@@
 
+We assume biomass growth to be equally divided among regions.
+
 ```{r}
 #Estimate starting biomass
-#regional_b0 <- numeric(length(region_names))
-# regional_biomass_growth <- c(1.33e6, 1.33e6, 1.33e6, 1.33e6, 1.33e6, 1.33e6)
-# 
-# for(i in 1:length(regional_h0)){
-#   biomass_vec <- seq(0, regional_k[i], length.out = 10000)
-#   growth_approx <- (((regional_phi[i]+1)/regional_phi[i])*regional_r[i]*biomass_vec*(1-((biomass_vec/regional_k[i])^regional_phi[i])))
-#   biomass_pos <- which.min(abs(growth_approx - (regional_h0 + regional_biomass_growth[i])))
-#   regional_b0[i] <- biomass_vec[biomass_pos] 
-# }
+regional_b0 <- numeric(length(region_names))
+regional_biomass_growth <- c(2.66e6, 2.66e6, 2.66e6)
 
-regional_b0 <- regional_k*0.2
+for(i in 1:length(regional_h0)){
+  biomass_vec <- seq(0, 0.75*regional_k[i], length.out = 10000)
+  growth_approx <- (((regional_phi[i]+1)/regional_phi[i])*regional_g[i]*biomass_vec*(1-((biomass_vec/regional_k[i])^regional_phi[i])))
+  biomass_pos <- which.min(abs(growth_approx - (regional_h0 + regional_biomass_growth[i])))
+  regional_b0[i] <- biomass_vec[biomass_pos]
+}
+
 names(regional_b0) <- region_names
@@
 
-<!-- We can then calculate the price constant using 2012 data from Costello et al. (2016).  -->
-
-```{r}
-# Global price constant
-global_price_wrangling <- costello_2016_dat %>%
-  group_by(year) %>%
-  summarize(price = median(price, na.rm = T),
-            harvest = sum(catch, na.rm = T))
-
-global_delta <- global_price_wrangling$harvest/(global_price_wrangling$price^global_epsilon)
-
-# Add price constant to parameter table
-global_model_parameters <- global_model_parameters %>%
-  bind_rows(tibble(parameter = "delta", value = global_delta, source = "Costello et al. 2016"))
-```
-
 ## Regional demand parameters
@@
   bind_rows(c("parameter" = "epsilon", "source" = "Costello et al. 2016", regional_epsilon))
-```
-
-<!-- We then calculate the price constant for each region using 2012 data from Costello et al. (2016).  -->
-
-```{r}
-# Regional price constant
-regional_delta <- costello_2016_dat_regional$catch/(costello_2016_dat_regional$price^regional_epsilon)
-
-# Add price constant to parameter table
-regional_model_parameters <- regional_model_parameters %>%
-  bind_rows(c("parameter" = "delta", "source" = "Costello et al. 2016", regional_delta))
 ```
@@
 We compare two alternatives - 1) using the median price from Costello et al.
-(2016) adjusted to 2018 US$, and 2) solving for price based on the observed base year harvest.
+(2016) adjusted to 2018 US\$, and 2) using the global price from the latest Sunken Billions report adjusted to 2018 US\$.
+The first price looks a bit high (comparable global price estimates are in the range of $1200-1400 per ton), so we use the second
 
 ```{r}
-# Calculate global base prices
-global_base_price1 <- ((1/global_delta)^(1/global_epsilon))*(global_h0^(1/global_epsilon))
+CPI_2012 <- 229.594  #BLS CPI All Items (Annual Ave), (BLS Series ID: CUUR0000SA0)
+CPI_2018 <- 251.107  #BLS CPI All Items (Annual Ave), (BLS Series ID: CUUR0000SA0)
 
-# CPI_2012 <- 229.594  #BLS CPI All Items (Annual Ave), (BLS Series ID: CUUR0000SA0)
-# CPI_2018 <- 251.107  #BLS CPI All Items (Annual Ave), (BLS Series ID: CUUR0000SA0)
-# 
-# global_base_price2 <- global_price_wrangling$price * (CPI_2018/CPI_2012)
+# Global price constant
+global_price_wrangling <- costello_2016_dat %>%
+  group_by(year) %>%
+  summarize(price = median(price, na.rm = T))
+
+global_base_price1 <- global_price_wrangling$price*(CPI_2018/CPI_2012)
+global_base_price2 <- 1260*(CPI_2018/CPI_2012)
+
+# Add to parameter table
+global_model_parameters <- global_model_parameters %>%
+  bind_rows(tibble(parameter = "p0", value = global_base_price2, source = "World Bank 2017"))
 ```
 
-The second price looks a bit high (comparable global price estimates are in the range of $1200-1400 per ton), so we use the first.
+```{r}
+global_delta <- global_h0/(global_base_price2^global_epsilon)
 
-```{r}
-# Add to parameter table
+# Add price constant to parameter table
 global_model_parameters <- global_model_parameters %>%
-  bind_rows(tibble(parameter = "p0", value = global_base_price1, source = "Costello et al. 2016"))
+  bind_rows(tibble(parameter = "delta", value = global_delta, source = "Costello et al. 2016"))
 ```
@@
   bind_rows(tibble(parameter = "eta", value = global_eta, source = "Calculated"))
-
 ```
@@
 
-We then calculate price in the base year in the same way regionally
+For simplicity, we assume the starting price to be equal across all regions.
 
@@
 # Calculate base price regionally
-regional_base_price1 <- ((1/regional_delta)^(1/regional_epsilon))*(regional_fleet$catch^(1/regional_epsilon))
+regional_base_price <- rep(global_base_price2, length = length(region_names))
+names(regional_base_price) <- region_names
 
@@
 regional_model_parameters <- regional_model_parameters %>%
-  bind_rows(c("parameter" = "p0", "source" = "Calculated", regional_base_price1))
+  bind_rows(c("parameter" = "p0", "source" = "World Bank 2017", regional_base_price))
 
+```
+
+```{r}
+# Regional price constant
+regional_delta <- regional_h0/(regional_base_price^regional_epsilon)
+
+# Add price constant to parameter table
+regional_model_parameters <- regional_model_parameters %>%
+  bind_rows(c("parameter" = "delta", "source" = "Costello et al. 2016", regional_delta))
 ```
@@
 ```{r}
-regional_omega <- rep(0.0011, length = length(region_names))
+regional_omega <- rep(0.001, length = length(region_names))
 names(regional_omega) <- region_names
@@
 
-write_csv(regional_model_parameters, paste0(results_dir, "model_parameters_regional.csv"))
-write_csv(regional_model_parameters, paste0(app_dir, "model_parameters_regional.csv"))
+regional_name <- paste0("model_parameters_regional_", n_regions, "_regions.csv")
+
+write_csv(regional_model_parameters, paste0(results_dir, regional_name))
+write_csv(regional_model_parameters, paste0(app_dir, regional_name))
 ```

### 2020-08-11 scripts/06_run_model.Rmd
model results script back up

--- 2020-06-29 scripts/06_run_model.Rmd
@@
 
-title: "SubsidyExplorer - Step 5: Run Model"
+title: "SubsidyExplorer - Step 6: Run Model"
 author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
@@
 knitr::opts_chunk$set(echo = TRUE)
+
+make_plots <- T
+
+if(make_plots){
+  library(RColorBrewer)
+  library(scales)
+}
+
+# Directories for the output files generated by this script
+results_dir <- here::here("results", "06-run-model/")
+if (dir.exists(results_dir) == F) {
+  dir.create(results_dir, recursive = T)
+}
 ```
@@
 
-This script generates the most ambitous global and regional results obtained by removing all capacity enhancing subsidies from all WTO Members and Observers.
+This script generates the most ambitious global and regional results obtained by removing all capacity enhancing subsidies from all WTO Members and Observers.
 
@@
 # Source model script
+source(here::here("app", "scripts", "BioEconModel.R"))
+```
+
+```{r}
+# Load vessel list
+pro_rate_subsidies <- F
+
+vessel_dat <- read.csv(here::here("app", "data", "vessel_list_2018_final.csv"), stringsAsFactors = F)
+
+### Not applicable currently - old experimentation with pro-rating the dollar value of different subsidies
+# if(pro_rate_subsidies == T){
+# 
+#   vessel_dat <- vessel_dat %>%
+#     mutate(B1_subs = B1_subs * 0.54, # boat construction/renovation - matched to payments based on vessels
+#            B2_subs = B2_subs * 1, # fishery development projects/support services - matched to payments based on variable use
+#            B3_subs = B3_subs * 0.87, # port construction and renovation - matched to payments based on vessels
+#            B4_subs = B4_subs * 0.87, # price/marketing support, processing infrastructure - matched to payments based on output
+#            B5_subs = B5_subs * 0.76, # non-fuel tax exemptions - matched to payments based on fishers income
+#            B6_subs = B6_subs * 0.56, # foreign access agreements - matched to payments based on fishers own capital
+#            B7_subs = B7_subs * 0.84, # fuel - matched to payments based on fuel use
+#            bad_subs = (B1_subs + B2_subs + B3_subs + B4_subs + B5_subs + B6_subs + B7_subs))
+# 
+# }
+
+vessel_dat <- vessel_dat %>%
+  mutate(eez_hs_code = case_when(eez_id == 0 ~ paste0("HS-", fao_region),
+                                 TRUE ~ as.character(eez_id)))
+
+# Load country dependencies helper file
+country_dependencies <- read_csv(here::here("data", "lookup-tables", "country_dependencies.csv")) %>%
+  mutate(territory_is_WTO = case_when(WTO_status %in% c("Member", "Observer") ~ T,
+                            TRUE ~ F))
+
+sovereign_statuses <- country_dependencies %>%
+  distinct(sovereign_iso3, WTO_status) %>%
+  mutate(sovereign_is_WTO = case_when(WTO_status %in% c("Member", "Observer") ~ T,
+                            TRUE ~ F))
+
+wto_lookup <- country_dependencies %>%
+  left_join(sovereign_statuses, by = c("sovereign_iso3", "WTO_status")) %>%
+  mutate(is_WTO = case_when(territory_is_WTO ~ T,
+                            sovereign_is_WTO ~ T,
+                            TRUE ~ F)) %>%
+  dplyr::select(iso3, is_WTO)
+```
+
+```{r}
+# Load biological parameters for the model
+bio_dat_regional <- read.csv(here::here("app", "data", "model_parameters_regional_3_regions.csv"))
+
+# Regional parameter list
+bio_dat_regional_list <- bio_dat_regional %>%
+  gather(region, value, -c(1:2)) %>%
+  group_by(region) %>%
+  group_split()
+```
+
+```{r}
+# Threshold to be considered managed (using FMI scores)
+managed_cutoff <- 0.66
+```
+
+## Create global fleet
+
+```{r pressure, echo=FALSE}
+# Assign fleets to vessels
+global_fleet_vessels <- vessel_dat %>%
+  left_join(wto_lookup, by = c("flag_iso3" = "iso3")) %>%
+  mutate(fleet = case_when(is_WTO & fmi_best >= managed_cutoff & bad_subs > 0 ~ "affected_managed",
+                           is_WTO & fmi_best < managed_cutoff & bad_subs > 0 ~ "affected_oa",
+                           (!is_WTO & fmi_best >= managed_cutoff) ~ "unaffected_managed",
+                           (!is_WTO & fmi_best < managed_cutoff) ~ "unaffected_oa",
+                           TRUE ~ "unaffected_oa"))
+```
+
+## Run Model (Remove all bad subsidies)
+
+```{r}
+# Create model input for removing all bad subsidies
+global_all_bad_summary <- global_fleet_vessels %>%
+  group_by(region, fleet) %>%
+  summarize(catch = sum(catch, na.rm = T),
+            bad_subs = sum(bad_subs, na.rm = T),
+            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
+            removed_subs = sum(bad_subs, na.rm = T)) %>%
+  ungroup()
+
+# Turn into a list
+global_all_bad_list <- global_all_bad_summary %>%
+  group_by(region) %>%
+  group_split()
+names(global_all_bad_list) <- colnames(bio_dat_regional)[-c(1:2)]
+
+# Run model
+global_all_bad_results <- pmap_df(list(fleet = global_all_bad_list, 
+                                       region = names(global_all_bad_list),
+                                       bio_param = bio_dat_regional_list),
+                                  BioEconModel,
+                                  end_year = 2100,
+                                  return = "all")
+
+# Extract results timeseries
+global_all_bad_results_full <- global_all_bad_results %>%
+  dplyr::filter(Year > 2018) %>%
+  dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total")) %>%
+  group_by(Year, Variable, Fleet) %>%
+  mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU)/abs(BAU),
+                          TRUE ~ 0),
+         BAU_global = sum(BAU, na.rm = T),
+         Reform_global = sum(Reform, na.rm = T),
+         Diff_global = case_when(BAU_global != 0 ~ (Reform_global - BAU_global)/abs(BAU_global),
+                                 TRUE ~ 0)) %>%
+  ungroup() %>%
+  mutate(run_number = "A",
+         run_name = "Most ambitious scenario",
+         id = "A",
+         Description = "Complete removal of all capacity-enhancing subsidies (for comparison)")
+
+# Extract ending results (difference only)
+global_all_bad_results_last <- global_all_bad_results_full %>%
+  dplyr::filter(Year == 2100) %>%
+  group_by(Year, Variable) %>%
+  summarize(Value = unique(Diff_global)*100) %>%
+  ungroup() %>%
+  spread(Variable, Value) %>%
+  rename(Biomass = biomass,
+         Catches = catches_total,
+         Revenue = revenue_total) %>%
+  mutate(run_number = "A",
+         run_name = "Most ambitious scenario")
 
@@
 
-## Including Plots
+```{r}
+# Make plots
+if(make_plots){
 
-You can also embed plots, for example:
+  # 1) global (aggregated) timeseries plot
+  global_all_bad_plot <- global_all_bad_results_full %>%
+        group_by(run_number, run_name, id, Year, Variable, Fleet) %>%
+        summarize(BAU = unique(BAU_global),
+                  Reform = unique(Reform_global),
+                  Diff = unique(Diff_global)) %>%
+        ungroup() %>%
+        mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
+                                    Variable == "catches_total" ~ "Catches",
+                                    Variable == "revenue_total" ~ "Revenue")) %>%
+        mutate(Region = "Global") %>%
+        ggplot()+
+        aes(x = Year, y = Diff*100, color = Variable)+
+        geom_line(size = 1)+
+        theme_bw()+
+        geom_hline(yintercept = 0)+
+        scale_x_continuous(expand = c(0,0))+
+        labs(x = "Year", y = "Change relative to BAU (%)")+
+        theme(legend.position = "none")+
+        facet_wrap(~Variable, ncol = 1, scales = "free_y")
 
-```{r pressure, echo=FALSE}
-plot(pressure)
+  ggsave(paste0(results_dir, "global_all_bad_timeseries_plot.png"), global_all_bad_plot, width = 7.5, height = 6, units = "in")
+
+  # 2) regional timeseries plot
+  regional_all_bad_plot <- global_all_bad_results_full %>%
+        dplyr::select(run_number, run_name, id, Year, Variable, Fleet, Region, BAU, Reform, Diff) %>%
+        mutate(Region = case_when(Region == "atlantic" ~ "Atlantic Ocean",
+                                  Region == "indian" ~ "Indian Ocean",
+                                  Region == "pacific" ~ "Pacific Ocean")) %>%
+        mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
+                                    Variable == "catches_total" ~ "Catches",
+                                    Variable == "revenue_total" ~ "Revenue")) %>%
+        ggplot()+
+        aes(x = Year, y = Diff*100, color = Variable)+
+        geom_line(size = 1)+
+        theme_bw()+
+        geom_hline(yintercept = 0)+
+        scale_x_continuous(expand = c(0,0))+
+        labs(x = "Year", y = "Change relative to BAU (%)")+
+        theme(legend.position = "none")+
+        facet_wrap(Variable ~ Region, ncol = 3, scales = "free_y")
+
+  ggsave(paste0(results_dir, "regional_all_bad_timeseries_plot.png"), regional_all_bad_plot, width = 7.5, height = 6, units = "in")
+
+}
 ```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2020-08-11 app/00_initialize_app.R
pre-methods download

@@ -26,10 +26,12 @@ wid <- read_csv("./text/00_widget_values.csv") %>%
             max = unique(max), 
             value = unique(value),
             step = unique(step)) %>%
+  ungroup() %>%
   group_by(tab_num, tab_id, item_id) %>%
   mutate(choices = list(setNames(unlist(str_split(choices, ", ")),
                                  unlist(str_split(choice_names, ", ")))),
-         selected = list(unlist(str_split(selected, ", "))))
+         selected = list(unlist(str_split(selected, ", ")))) %>%
+  ungroup()
 
 ### ----------------------------------
 ### Country/Territory Naming ---------
@@ -178,7 +180,8 @@ capture_production_dat_fao <- read_csv("./data/fao_2020_capture_production_issca
 
 capture_production_dat_tot <- capture_production_dat_fao %>%
   group_by(iso3, year, variable, units, source, display_name) %>%
-  summarize(value = sum(value, na.rm = T)) 
+  summarize(value = sum(value, na.rm = T)) %>%
+  ungroup()
 
 # 2) Landed value by ISSCAAP Group (2000-2017)
 landed_value_dat <- read_csv("./data/estimated_landed_value_isscaap_groups_tidy.csv") %>%
@@ -189,33 +192,34 @@ landed_value_dat <- read_csv("./data/estimated_landed_value_isscaap_groups_tidy.
 
 landed_value_dat_tot <- landed_value_dat %>%
   group_by(iso3, year, variable, units, source, display_name) %>%
-  summarize(value = sum(value, na.rm = T))
+  summarize(value = sum(value, na.rm = T)) %>%
+  ungroup()
   
 # 3) GFW Vessel list (2018)
-pro_rate_subsidies <- F
+#pro_rate_subsidies <- F
 
 vessel_dat <- read.csv("./data/vessel_list_2018_final.csv", stringsAsFactors = F)
 
-if(pro_rate_subsidies == T){
-
-  vessel_dat <- vessel_dat %>%
-    mutate(B1_subs = B1_subs * 0.54, # boat construction/renovation - matched to payments based on vessels
-           B2_subs = B2_subs * 1, # fishery development projects/support services - matched to payments based on variable use
-           B3_subs = B3_subs * 0.87, # port construction and renovation - matched to payments based on vessels
[…]

### 2020-08-11 app/scripts/CreateFleets.R

@@ -496,7 +496,6 @@ CreateFleets <- function(vessel_list,
     }else if(oa$scope == "EX_TER"){
       
       # Select only vessels fishing outside of territorial waters
-      browser()
       # iuu_vessels_scope <- iuu_vessels_scope %>%
       #   dplyr::filter(!is_territorial)
       
@@ -698,7 +697,7 @@ CreateFleets <- function(vessel_list,
   ### Subsidies contributing to overcapacity and overfishing -------------------
   ### --------------------------------------------------------------------------
 
-  if(length(overcap$definitions) == 0 ){
+  if(length(overcap$definitions) == 0){
     
     # Shortcut output if no disciplines are selected from this category
     overcap_vessel_subset <- vessel_tracking_df
@@ -841,7 +840,6 @@ CreateFleets <- function(vessel_list,
     }else if(overcap$scope == "EX_TER"){
       
       # Select only vessels fishing outside of territorial waters
-      browser()
       # iuu_vessels_scope <- iuu_vessels_scope %>%
       #   dplyr::filter(!is_territorial)
       
@@ -1087,7 +1085,8 @@ overcap_vessels_out <- overcap_vessels_scope %>%
     
   ) %>%
     ungroup() %>%
-    dplyr::select(-flag1)
+    dplyr::select(-`flag...9`) %>%
+    rename(flag = `flag...1`)
   
   ### Section # 4 ---------------------------------------
   ### Cap and tier --------------------------------------

### 2020-08-11 app/server.R

@@ -412,12 +412,9 @@ shinyServer(function(input, output, session) {
       
       plot_dat <- dat %>%
         dplyr::select(run_number, run_name, id, Year, Variable, Fleet, Region, BAU, Reform, Diff) %>%
-        mutate(Region = case_when(Region == "atlantic_e" ~ "Atlantic Ocean (Eastern)",
-                                  Region == "atlantic_w" ~ "Atlantic Ocean (Western)",
+        mutate(Region = case_when(Region == "atlantic" ~ "Atlantic Ocean",
                                   Region == "indian" ~ "Indian Ocean",
-                                  Region == "pacific_e" ~ "Pacific Ocean (Eastern)",
-                                  Region == "pacific_w" ~ "Pacific Ocean (Western)",
-                                  Region == "polar" ~ "Polar Oceans"))
+                                  Region == "pacific" ~ "Pacific Ocean"))
       
     }
     

### 2020-08-11 app/ui.R

@@ -36,6 +36,9 @@ library(plotly) # interactive charts
 library(viridis) # colorblind color scales
 library(RColorBrewer) # other color scales
 
+# Silence new dplyr grouping messages
+options(dplyr.summarise.inform=F)
+
 # The content for each tab is stored in a separate file. Source all .R files in the current directory that start with "ui_":  
 sapply(list.files(
     pattern = "^ui_.*\\.R$",

### 2020-08-11 app/ui_02b_edit_policies.R

@@ -83,7 +83,7 @@ EditPolicies = function(wto_members_and_observers, subsidy_types_sorted_sumaila)
            #### Left column - tabBox with manual policy selection
            #### ----------------------------------------------------
            
-           column(9,
+           column(12,
     
                   ### tabBox container
                   column(12, style = "padding: 0px 25px 0px;",
@@ -139,44 +139,44 @@ EditPolicies = function(wto_members_and_observers, subsidy_types_sorted_sumaila)
                   
                   ) # /column 12 - tabBox container
            
-           ), # /column 9 - Left column
+           ) # /column 9 - Left column
     
            
            ####-----------------------------------------------------------------------------------------
            #### Right column - Menu of selected policies
            #### ----------------------------------------------------------------------------------------
-           column(3,
-                  style = "position: absolute;
-                  background-color: rgba(40, 97, 130, 0.8);
-                  color: #ffffff;
-                  padding: 0 10px;
-                  top:0;
-                  bottom:0;
-                  right:0;", 
-                  
-                  tags$h4(text$item_label[text$item_id == "selected-policy"]),
-                  
-                  # Reactive policy summary
-                  uiOutput("custom_policy"),
-                  
-                  # Run model button
-                  column(12, align = "center", style = "padding: 25px 0 0 0;",
-                         
-                         actionButton("ab_run_model_custom",
-                                      tags$b(text$item_label[text$item_id == "ab_run_model_custom"]),
-                                      style = "color: black;
-                                      background-color: rgba(255,255,255,0.7); 
-                                      border: 3px #3c8dbc solid; 
-                                      white-space: normal;"),
-                         
-                         
-                         # Warning about missing name
-                         uiOutput("custom_name_warning")
-                         
-                         
-                  )
-                  
-           ) # /column 3 - Right column
+           # column(3,
+           #        style = "position: absolute;
+           #        background-color: rgba(40, 97, 130, 0.8);
+           #        color: #ffffff;
+           #        padding: 0 10px;
+           #        top:0;
+           #        bottom:0;
+           #        right:0;", 
+           #        
+           #        tags$h4(text$item_label[text$item_id == "selected-policy"]),
+           #        
+           #        # Reactive policy summary
+           #        uiOutput("custom_policy"),
+           #        
+           #        # Run model button
+           #        column(12, align = "center", style = "padding: 25px 0 0 0;",
+           #               
+           #               actionButton("ab_run_model_custom",
[…]

### 2020-08-11 scripts/01_data_wrangling.Rmd
updating WTO status, overseas territory info, and fao data

@@
 library(here) # File path handling
+#remotes::install_github('vincentarelbundock/WDI')
 library(WDI) # World Bank World Development Indicators data
@@
 
+# Get all overseas dependencies that are relevant for the WTO - there are 49
+territories <- country_dependencies %>%
+  dplyr::filter(is_overseas_territory & is_WTO) %>%
+  distinct(iso3, sovereign_iso3)
+
+# Get all cooresponding sovereign states (we need to make sure any totals for these states include their dependencies) - there are 9
+# Australia, Denmark, France, United Kingdom, Morocco, Netherlands, Norway, New Zealand, and the United States
+sovereigns_with_territories <- territories %>%
+  distinct(sovereign_iso3)
+
 # EU countries
 eu_countries <- country_dependencies$iso3[country_dependencies$is_EU]
-eu_country_names <- country_dependencies$WTO_name[country_dependencies$iso3 %in% eu_countries]
 
@@
 eu_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 %in% eu_countries]
-eu_territory_names <- sort(c(countrycode(eu_territories, "iso3c", "country.name"), "Ascension Island", "Tristan da Cunha"))
-
-# US overseas territories:  American Samoa, Guam, Northern Marianas Islands, Puerto Rico, US Virgin Islands
-us_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "USA"]
-us_territory_names <- sort(countrycode(us_territories, "iso3c", "country.name"))
-
-# Norwegian overseas territories: 
-nor_territories <- country_dependencies$iso3[country_dependencies$is_overseas_territory & country_dependencies$sovereign_iso3 == "NOR"]
-nor_territory_names <- sort(countrycode(nor_territories, "iso3c", "country.name"))
 ```
@@
 We therefore need to create a profile for the European Union as a whole.
-The following `r length(eu_country_names)` states are considered to be part of the European Union for the purposes of this analysis: `r paste(eu_country_names, collapse = ", ")`.
+The following `r length(eu_country_names)` states are considered to be part of the European Union for the purposes of this analysis: `r paste(country_dependencies$WTO_name[country_dependencies$iso3 %in% eu_countries], collapse = ", ")`.
 
 The Netherlands, France, Denmark, and the United Kingdom also have overseas dependencies that should be considered to be a part of the European Union for statistical purposes.
-The following overseas dependencies are also considered to be a part of the European Union for the purpose of aggregating data in this analysis: `r paste(eu_territory_names, collapse = ", ")`.
 
-Outside of the EU, the other dependencies we need to worry about are those that relate to the United States and Norway.
-The following overseas dependencies are considered to be a part of the United States for the purpose of aggregating data in this analysis: `r paste(us_territory_names, collapse = ", ")`.
-The following overseas dependencies are considered to be a part of Norway for the purpose of aggregating data in this analysis: `r paste(norway_territory_names, collapse = ", ")`.
+Outside of the EU, the other dependencies we need to worry about are those that relate to the Austraila, Morocco, Norway, New Zealand, and the United States.
 
@@
   summarize(value = sum(value, na.rm = T)) %>%
+  ungroup() %>%
   rename(iso3 = entity)
@@
   mutate(variable = "subsidies_Sumaila")
+
+# Test to make sure there isn't data for any other dependencies - nope we're good
+sumaila_2019_dat_overseas_territory <- sumaila_2019_dat_edit %>%
+  dplyr::filter(iso3 %in% territories$iso3 & !(iso3 %in% eu_territories))
 
@@
   summarize(value = sum(value, na.rm = T)) %>%
+  ungroup() %>%
   rename(iso3 = entity) %>%
@@
   mutate(variable = "subsidies_OECD")
+
+# Test to make sure there isn't data for any other dependencies - nope we're good
+oecd_fse_dat_overseas_territory <- oecd_fse_dat_edit %>%
+  dplyr::filter(iso3 %in% territories$iso3 & !(iso3 %in% eu_territories))
 
@@
 
+# Test to make sure there isn't data for any other dependencies - nope we're good
+schuhbauer_subsidies_ssf_dat_overseas_territory <- schuhbauer_subsidies_ssf_dat_edit %>%
+  dplyr::filter(iso3 %in% territories$iso3 & !(iso3 %in% eu_territories))
+
 # Save
@@
 write_csv(schuhbauer_subsidies_ssf_dat_edit, paste0(app_data_dir, "schuhbauer_ssf_subsidies_proportions.csv"))
-
 ```
@@
 ```{r}
-# Load data using WDI package
-wb_demo_dat <- WDI(country = "all",
-                   indicator = c("gdp" = "NY.GDP.MKTP.CD",
-                                 "gdp_ffa" = "NV.AGR.TOTL.CD",
-                                 "population" = "SP.POP.TOTL"),
-                                  start = 2000,
-                                  end = 2018,
-                                  extra = TRUE) %>%
-  dplyr::filter(region != "Aggregates") %>%
-  dplyr::select(iso3 = iso3c,
-                year,
-                gdp,
-                gdp_ffa,
-                population) %>%
-  mutate(iso3 = as.character(iso3)) %>%
-  arrange(iso3, year) %>%
-  gather(variable, value, c("gdp", "gdp_ffa", "population")) %>%
-  dplyr::filter(!is.na(value)) %>%
-  mutate(units = case_when(variable == "population" ~ "individuals",
-                           TRUE ~ paste0(year, " US$")),
-         source = "World Bank WDI database")
+# Load data using WDI package'
+# wb_demo_dat <- WDI(country = "all",
+#                    indicator = c("gdp" = "NY.GDP.MKTP.CD",
+#                                  "gdp_ffa" = "NV.AGR.TOTL.CD",
+#                                  "population" = "SP.POP.TOTL"),
+#                                   start = 2000,
+#                                   end = 2018,
+#                                   extra = TRUE) %>%
+#   dplyr::filter(region != "Aggregates") %>%
+#   dplyr::select(iso3 = iso3c,
+#                 year,
+#                 gdp,
+#                 gdp_ffa,
+#                 population) %>%
+#   mutate(iso3 = as.character(iso3)) %>%
+#   arrange(iso3, year) %>%
+#   gather(variable, value, c("gdp", "gdp_ffa", "population")) %>%
+#   dplyr::filter(!is.na(value)) %>%
+#   mutate(units = case_when(variable == "population" ~ "individuals",
+#                            TRUE ~ paste0(year, " US$")),
+#          source = "World Bank WDI database")
+# 
+# # Deal with the EU + territories
+# wb_dat_eu <- wb_demo_dat %>%
+#   dplyr::filter(iso3 %in% c(eu_countries, eu_territories)) %>%
+#   mutate(entity = "EU") %>%
+#   group_by(entity, year, variable, units, source) %>%
+#   summarize(value = sum(value, na.rm = T)) %>%
+#   rename(iso3 = entity) %>%
+#   arrange(iso3, year, variable)
+# 
+# # Test to make sure there isn't data for any other dependencies - will need to add this once I can figure out why the WDI API isn't working
+# wb_dat_overseas_territory <- wb_demo_dat %>%
+#   dplyr::filter(iso3 %in% territories$iso3 & !(iso3 %in% eu_territories))
+# # Deal with the US + territories
+# wb_dat_us <- wb_demo_dat %>%
+#   dplyr::filter(iso3 %in% c(us_territories, "USA")) %>%
+#   mutate(entity = "USA") %>%
+#   group_by(entity, year, variable, units, source) %>%
+#   summarize(value = sum(value, na.rm = T)) %>%
+#   rename(iso3 = entity) %>%
+#   arrange(iso3, year, variable)
+# 
+# # Add back in
+# wb_dat_edit <- wb_demo_dat %>%
+#   dplyr::filter(iso3 != "USA") %>%
+#   bind_rows(wb_dat_eu) %>%
+#   bind_rows(wb_dat_us)
+# 
+# # Export clean
+# write_csv(wb_dat_edit, paste0(data_dir, "world_bank_2020_wdi_tidy.csv"))
+# write_csv(wb_dat_edit, paste0(app_data_dir, "world_bank_2020_wdi_tidy.csv"))
 
-# Deal with the EU + territories
-wb_dat_eu <- wb_demo_dat %>%
-  dplyr::filter(iso3 %in% c(eu_countries, eu_territories)) %>%
-  mutate(entity = "EU") %>%
-  group_by(entity, year, variable, units, source) %>%
-  summarize(value = sum(value, na.rm = T)) %>%
-  rename(iso3 = entity) %>%
-  arrange(iso3, year, variable)
-
-# Deal with the US + territories
-wb_dat_us <- wb_demo_dat %>%
-  dplyr::filter(iso3 %in% c(us_territories, "USA")) %>%
-  mutate(entity = "USA") %>%
-  group_by(entity, year, variable, units, source) %>%
-  summarize(value = sum(value, na.rm = T)) %>%
-  rename(iso3 = entity) %>%
-  arrange(iso3, year, variable)
-
-# Add back in
-wb_dat_edit <- wb_demo_dat %>%
-  dplyr::filter(iso3 != "USA") %>%
-  bind_rows(wb_dat_eu) %>%
-  bind_rows(wb_dat_us)
-
-# Export clean
-write_csv(wb_dat_edit, paste0(data_dir, "world_bank_2020_wdi_tidy.csv"))
-write_csv(wb_dat_edit, paste0(app_data_dir, "world_bank_2020_wdi_tidy.csv"))
+# Load in
+wb_dat_edit <- read_csv(paste0(data_dir, "world_bank_2020_wdi_tidy.csv"))
 ```
@@
   arrange(year, iso3)
+
+# # Test to make sure there isn't data for any other dependencies - nope we're good
+fao_fishers_dat_overseas_territory <- fao_fishers_dat %>%
+  dplyr::filter(iso3 %in% territories$iso3 & !(iso3 %in% eu_territories))
 
@@
   bind_rows(teh_fte_dat_eu)
+
+# # Test to make sure there isn't data for any other dependencies - nope we're good
+teh_fte_dat_overseas_territory <- teh_fte_dat_edit %>%
+  dplyr::filter(iso3 %in% territories$iso3 & !(iso3 %in% eu_territories))
 
@@
   summarize(value = sum(value, na.rm = T)) %>%
+  ungroup() %>%
   rename(iso3 = entity)
 
-# Deal with the US + territories
-fao_production_dat_us <- fao_production_dat %>%
-  dplyr::filter(iso3 %in% c(us_territories, "USA")) %>%
-  mutate(entity = "USA-T") %>%
+# Deal with all territories 
+fao_production_dat_overseas_territories <- fao_production_dat %>%
+  dplyr::filter(iso3 %in% territories$iso3 | iso3 %in% territories$sovereign_iso3) %>%
+  left_join(territories, by = c("iso3")) %>%
+  mutate(sovereign_iso3 = case_when(is.na(sovereign_iso3) ~ iso3,
+                                    TRUE ~ sovereign_iso3)) %>%
+  mutate(entity = paste0(sovereign_iso3, "-T")) %>%
   group_by(entity, year, fishing_area, species, asfis_species, scientific_name, yearbook_group, isscaap_group) %>%
   summarize(value = sum(value, na.rm = T)) %>%
+  ungroup() %>%
   rename(iso3 = entity)
@@
   bind_rows(fao_production_dat_eu) %>%
-  bind_rows(fao_production_dat_us) %>%
+  bind_rows(fao_production_dat_overseas_territories) %>%
   mutate(variable = "capture_production",
@@
   group_by(iso3, year, isscaap_group, variable, units, source) %>%
-  summarize(value = sum(value, na.rm = T))
+  summarize(value = sum(value, na.rm = T)) %>%
+  ungroup() %>%
+  spread(year, value) %>% # adding empty rows to make the plotting work better
+  gather(year, value, as.character(c(2000:2018))) %>% # second part of that process
+  mutate(year = as.numeric(year))
+fao_production_dat_edit_groups$value[is.na(fao_production_dat_edit_groups$value)] <- 0 # for plotting purposes - we don't get gaps on area plot this way
 
@@
 
-# Look at NAs - 10,023 entries
+# Look at NAs - 11,553 entries
 combine_nas <- combine_catch_price_dat %>%
   dplyr::filter(is.na(exvessel_inclusive))
+
+combine_nas_groups <- unique(combine_nas$isscaap_group)
 
@@
 landed_value_dat_groups <- landed_value_dat %>%
-  group_by(iso3, year, isscaap_group, variable, units, source) %>%
-  summarize(value = sum(value, na.rm = T))
+  group_by(iso3, year, isscaap_group, variable, source) %>%
+  summarize(value = sum(value, na.rm = T)) %>%
+  ungroup() %>%
+  spread(year, value) %>% # adding empty rows to make the plotting work better
+  gather(year, value, as.character(c(2000:2018))) %>% # second part of that process
+  mutate(year = as.numeric(year)) %>%
+  mutate(units = paste0(year, " US$"))
 
@@
 
-## Cap and Tier Data from the US Proposal
-```{r}
-cap_tier_dat <- read_csv(cap_tier_path) %>%
-  mutate(iso3 = case_when(country == "Eswatini" ~ "SWZ",
-                          country == "EU" ~ "EU",
-                          TRUE ~ countrycode(country, "country.name", "iso3c"))) %>%
-  dplyr::select(-country)
-
-write_csv(cap_tier_dat, paste0(data_dir, "USA_cap_tier_tidy.csv"))
-write_csv(cap_tier_dat, paste0(app_data_dir, "USA_cap_tier_tidy.csv"))
-```
-
 # Section 5 - Relative Metrics
 
-This section is a bit of a relic from when we were doing "country profiles", but there are a couple of relative metrics we want to calculate from our data sources. This is done here.
+This section is a bit of a relic from when we were doing "country profiles", but there are a couple of relative subsidy metrics we want to calculate from our data sources. This is done here.
 
@@
 ```
+
+# Section 6 - Cap/Tier Lookup Tables
+
+## Cap and Tier Data from the US Proposal
+```{r}
+cap_tier_dat <- read_csv(cap_tier_path) %>%
+  mutate(iso3 = case_when(country == "Eswatini" ~ "SWZ",
+                          country == "EU" ~ "EU",
+                          TRUE ~ countrycode(country, "country.name", "iso3c"))) %>%
+  dplyr::select(-country)
+
+write_csv(cap_tier_dat, paste0(data_dir, "USA_cap_tier_tidy.csv"))
+write_csv(cap_tier_dat, paste0(app_data_dir, "USA_cap_tier_tidy.csv"))
+```
+
+Many of the capping proposals utilize some metric to sort Members into tiers.
+This is often done based upon the average over some period.
+In order to allow this to be interactive later on, we need to craft a lookup table with all possible date ranges.
+
+```{r}
+# Capture production lookup
+capture_production_lookup <- fao_production_dat_edit_groups %>%
+  group_by(iso3, year) %>%
+  summarize(capture_production = sum(value, na.rm = T)) %>%
+  ungroup() %>%
+  spread(year, capture_production) %>%
+  mutate(variable = "capture_production") %>%
+  left_join(country_dependencies %>% dplyr::select(iso3, is_WTO), by = "iso3") %>%
+  mutate(is_WTO = case_when(!is.na(is_WTO) ~ is_WTO,
+                            iso3 %in% unique(paste0(territories$sovereign_iso3, "-T")) ~ TRUE,
+                            iso3 == "EU" ~ TRUE,
+                            TRUE ~ FALSE))
+
+# Landed value
+landed_value_lookup <- landed_value_dat_groups %>%
+  group_by(iso3, year) %>%
+  summarize(landed_value = sum(value, na.rm = T)) %>%
+  ungroup() %>%
+  spread(year, landed_value) %>%
+  mutate(variable = "landed_value") %>%
+  left_join(country_dependencies %>% dplyr::select(iso3, is_WTO), by = "iso3") %>%
+  mutate(is_WTO = case_when(!is.na(is_WTO) ~ is_WTO,
+                            iso3 %in% unique(paste0(territories$sovereign_iso3, "-T")) ~ TRUE,
+                            iso3 == "EU" ~ TRUE,
+                            TRUE ~ FALSE))
+
+# Combine 
+cap_tier_lookup <- capture_production_lookup %>%
+  bind_rows(landed_value_lookup)
+
+write_csv(cap_tier_lookup, paste0(data_dir, "cap_tier_lookup_table.csv"))
+write_csv(cap_tier_lookup, paste0(app_data_dir, "cap_tier_lookup_table.csv"))
+
+```

### 2020-08-11 scripts/06_run_model.Rmd
updating WTO status, overseas territory info, and fao data

@@
 # Load country dependencies helper file
-country_dependencies <- read_csv(here::here("data", "lookup-tables", "country_dependencies.csv")) %>%
-  mutate(territory_is_WTO = case_when(WTO_status %in% c("Member", "Observer") ~ T,
-                            TRUE ~ F))
-
-sovereign_statuses <- country_dependencies %>%
-  distinct(sovereign_iso3, WTO_status) %>%
-  mutate(sovereign_is_WTO = case_when(WTO_status %in% c("Member", "Observer") ~ T,
-                            TRUE ~ F))
-
-wto_lookup <- country_dependencies %>%
-  left_join(sovereign_statuses, by = c("sovereign_iso3", "WTO_status")) %>%
-  mutate(is_WTO = case_when(territory_is_WTO ~ T,
-                            sovereign_is_WTO ~ T,
-                            TRUE ~ F)) %>%
-  dplyr::select(iso3, is_WTO)
+country_dependencies <- read_csv(here::here("data", "lookup-tables", "country_dependencies.csv"))
 ```
@@
 global_fleet_vessels <- vessel_dat %>%
-  left_join(wto_lookup, by = c("flag_iso3" = "iso3")) %>%
+  left_join(country_dependencies %>% dplyr::select(iso3, is_WTO), by = c("flag_iso3" = "iso3")) %>%
   mutate(fleet = case_when(is_WTO & fmi_best >= managed_cutoff & bad_subs > 0 ~ "affected_managed",

### 2020-08-11 app/00_initialize_app.R

@@ -38,26 +38,37 @@ wid <- read_csv("./text/00_widget_values.csv") %>%
 ### ----------------------------------
 
 # Load list of WTO Member states and their dependencies with chosen display names
-country_lookup <- read_csv("./data/country_lookup.csv") %>%
+country_lookup <- read_csv("./data/country_dependencies.csv") %>%
   mutate(display_name = case_when(!is.na(WTO_name) ~ WTO_name,
+                                  iso3 == "ANT" ~ "Netherlands Antilles",
+                                  iso3 == "ASC" ~ "Ascension Island", 
+                                  iso3 == "CPT" ~ "Clipperton Island",
+                                  iso3 == "TAA" ~ "Tristan da Cunha",
                                   TRUE ~ countrycode(iso3, "iso3c", "country.name"))) %>%
   arrange(sovereign_iso3) 
 
-# Vector of all WTO Members and Observers for use in the app
-wto_members_and_observers <- country_lookup$iso3[country_lookup$WTO_member_status %in% c("Member", "Observer")]
-names(wto_members_and_observers) <- country_lookup$display_name[country_lookup$WTO_member_status %in% c("Member", "Observer")]
+# Vector of all WTO Members and Observers for use in the app [does not include the overseas territories associated with them]
+wto_members_and_observers <- country_lookup$iso3[country_lookup$is_WTO & !country_lookup$is_overseas_territory]
+names(wto_members_and_observers) <- country_lookup$display_name[country_lookup$iso3 %in% wto_members_and_observers]
 
 # EU states
-eu_countries <- country_lookup$iso3[country_lookup$iso3 != "EU" & country_lookup$is_EU]
+eu_countries <- country_lookup$iso3[country_lookup$is_EU]
+names(eu_countries) <- country_lookup$display_name[country_lookup$iso3 %in% eu_countries]
 
 # List of all EU overseas territories - vessels flagged here should be considered WTO Members
 eu_territories <- country_lookup$iso3[country_lookup$is_overseas_territory & country_lookup$sovereign_iso3 %in% eu_countries]
+names(eu_territories) <- country_lookup$display_name[country_lookup$iso3 %in% eu_territories]
 
-# List of all US overseas territories - vessels flagged here should be considered WTO Members
[…]

### 2020-08-15 scripts/05_subsidy_reform_definitions.Rmd

@@
 # Paths to other data files
-iuu_dat_path <- here::here("data", "raw", "IUU-Vessel-List-2019", "IUUList-20190430.csv")
+iuu_dat_path <- here::here("data", "raw", "combined-IUU-vessel-list", "IUUList-20190430.csv")
 costello_2016_path <- here::here("data", "edited", "costello_et_al_2016_upsides_tidy.csv")
+ram_dat_path <- here::here("data", "edited", "RAMLDB_v4.491_bvmsy_tidy.csv")
 eez_info_path <- here::here("data", "lookup-tables", "eez_info.csv")
@@
 # Extract only vessels currently listed, and create a new entry for each using the "name" field
+# We also normalize shipname using the same function GFW uses to normalize their shipnames (ignore roman numeral error - double checked this and it's working fine)
 iuu_clean_name <- iuu_list %>% 
@@
 ```{r}
-# Load costello data to get the fraction of catches by eez/fao region that are in RAM and are determined to be overfished
+# Load RAM data to get the status of stocks
 costello_2016_dat <- read_csv(costello_2016_path) %>%
@@
             w_mean_bv_bmsy = weighted.mean(bv_bmsy, w = (msy/n_regions), na.rm = T)) %>%
+  ungroup() %>%
   mutate(oa1_median = ifelse(median_bv_bmsy >= 1, F, T),
@@
             w_mean_bv_bmsy = weighted.mean(bv_bmsy, w = (msy/n_regions), na.rm = T)) %>%
+  ungroup() %>%
   mutate(oa3_median = ifelse(median_bv_bmsy >= 1, F, T),

### 2020-09-02 scripts/06_run_model.Rmd
sensitivity analysis

@@
 # Load vessel list
-pro_rate_subsidies <- F
-
 vessel_dat <- read.csv(here::here("app", "data", "vessel_list_2018_final.csv"), stringsAsFactors = F)
 
-### Not applicable currently - old experimentation with pro-rating the dollar value of different subsidies
-# if(pro_rate_subsidies == T){
-# 
-#   vessel_dat <- vessel_dat %>%
-#     mutate(B1_subs = B1_subs * 0.54, # boat construction/renovation - matched to payments based on vessels
-#            B2_subs = B2_subs * 1, # fishery development projects/support services - matched to payments based on variable use
-#            B3_subs = B3_subs * 0.87, # port construction and renovation - matched to payments based on vessels
-#            B4_subs = B4_subs * 0.87, # price/marketing support, processing infrastructure - matched to payments based on output
-#            B5_subs = B5_subs * 0.76, # non-fuel tax exemptions - matched to payments based on fishers income
-#            B6_subs = B6_subs * 0.56, # foreign access agreements - matched to payments based on fishers own capital
-#            B7_subs = B7_subs * 0.84, # fuel - matched to payments based on fuel use
-#            bad_subs = (B1_subs + B2_subs + B3_subs + B4_subs + B5_subs + B6_subs + B7_subs))
-# 
-# }
-
+# Create high seas code
 vessel_dat <- vessel_dat %>%

### 2020-09-02 scripts/07_sensitivity_analysis.Rmd
sensitivity analysis

---
output:
  html_document: default

title: "SubsidyExplorer - Step 7: Sensitivity Analysis"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
bibliography: "../pew-subsidies.bib"
---

```{r setup, include=FALSE}
# Load packages
library(knitr) 
library(tidyverse)

knitr::opts_chunk$set(echo = TRUE)

make_plots <- T

if(make_plots){
  library(RColorBrewer)
  library(scales)
}

# Directories for the output files generated by this script
results_dir <- here::here("results", "07-sensitivity-analysis/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}
```

```{r}
# Load vessel list
vessel_dat <- read.csv(here::here("app", "data", "vessel_list_2018_final.csv"), stringsAsFactors = F)

# Create high seas code
vessel_dat <- vessel_dat %>%
  mutate(eez_hs_code = case_when(eez_id == 0 ~ paste0("HS-", fao_region),
                                 TRUE ~ as.character(eez_id)))

# Load country dependencies helper file
country_dependencies <- read_csv(here::here("data", "lookup-tables", "country_dependencies.csv"))
```

## Relative subsidy effects

```{r}
# Vessel list with "effective" subsidies
### Not applicable currently - old experimentation with pro-rating the dollar value of different subsidies
# if(pro_rate_subsidies == T){
# 
#   vessel_dat <- vessel_dat %>%
#     mutate(B1_subs = B1_subs * 0.54, # boat construction/renovation - matched to payments based on vessels
#            B2_subs = B2_subs * 1, # fishery development projects/support services - matched to payments based on variable use
#            B3_subs = B3_subs * 0.87, # port construction and renovation - matched to payments based on vessels
#            B4_subs = B4_subs * 0.87, # price/marketing support, processing infrastructure - matched to payments based on output
#            B5_subs = B5_subs * 0.76, # non-fuel tax exemptions - matched to payments based on fishers income
#            B6_subs = B6_subs * 0.56, # foreign access agreements - matched to payments based on fishers own capital
#            B7_subs = B7_subs * 0.84, # fuel - matched to payments based on fuel use
#            bad_subs = (B1_subs + B2_subs + B3_subs + B4_subs + B5_subs + B6_subs + B7_subs))
# 
# }
```

## Bioeconomic model parameters

### 2020-09-02 scripts/06_main_results.Rmd
updating global results

---
output:
  html_document: default

title: "SubsidyExplorer - Step 6: Main Results"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
bibliography: "../pew-subsidies.bib"
---

# Introduction

This script generates the most ambitious global and regional results obtained by removing all capacity enhancing subsidies from all WTO Members and Observers.

```{r setup, include=FALSE}
# Load packages
library(knitr) 
library(tidyverse)

knitr::opts_chunk$set(echo = TRUE)

make_plots <- T

if(make_plots){
  library(RColorBrewer)
  library(scales)
}

# Directories for the output files generated by this script
results_dir <- here::here("results", "06-main-results/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}
```

```{r}
# Source model script
source(here::here("app", "scripts", "BioEconModel.R"))

# Source plotting script
source(here::here("scripts", "functions", "BioEconomicModelPlots.R"))
```

```{r}
# Load vessel list
vessel_dat <- read.csv(here::here("app", "data", "vessel_list_2018_final.csv"), stringsAsFactors = F)

# Create high seas code
vessel_dat <- vessel_dat %>%
  mutate(eez_hs_code = case_when(eez_id == 0 ~ paste0("HS-", fao_region),
                                 TRUE ~ as.character(eez_id)))

# Load country dependencies helper file
country_dependencies <- read_csv(here::here("data", "lookup-tables", "country_dependencies.csv"))
```

```{r}
# Load biological parameters for the model
bio_dat_regional <- read.csv(here::here("app", "data", "model_parameters_regional_3_regions.csv"))

# Regional parameter list
bio_dat_regional_list <- bio_dat_regional %>%
  gather(region, value, -c(1:2)) %>%
  group_by(region) %>%
  group_split()
```

```{r}
# Threshold to be considered managed (using FMI scores)
managed_cutoff <- 0.66
```

## Relative subsidy effects

```{r}
# Vessel list with "effective" subsidies
rel <- read_csv(here::here("data", "lookup-tables", "oecd_relative_effects_lookup_table.csv"))

bad_subsidy_types <- c("B1", "B2", "B3", "B4", "B5", "B6", "B7")
ugly_subsidy_types <- c("C1", "C2", "C3")

vessel_dat_relative <- vessel_dat %>%
   mutate(B1_subs = B1_subs * rel$rel_effect_effort[rel$type == "B1"], 
           B2_subs = B2_subs * rel$rel_effect_effort[rel$type == "B2"],
           B3_subs = B3_subs * rel$rel_effect_effort[rel$type == "B3"],
           B4_subs = B4_subs * rel$rel_effect_effort[rel$type == "B4"],
           B5_subs = B5_subs * rel$rel_effect_effort[rel$type == "B5"], 
           B6_subs = B6_subs * rel$rel_effect_effort[rel$type == "B6"],
           B7_subs = B7_subs * rel$rel_effect_effort[rel$type == "B7"], 
           C1_subs = C1_subs * rel$rel_effect_effort[rel$type == "C1"], 
           C2_subs = C2_subs * rel$rel_effect_effort[rel$type == "C2"],
           C3_subs = C3_subs * rel$rel_effect_effort[rel$type == "C3"], 
           bad_subs = rowSums(select(., one_of(paste0(bad_subsidy_types, "_subs")))),
           ugly_subs = rowSums(select(., one_of(paste0(ugly_subsidy_types, "_subs")))))
```

```{r pressure, echo=FALSE}
# Assign fleets to vessels
global_fleet_rel_vessels <- vessel_dat_relative %>%
  left_join(country_dependencies %>% dplyr::select(iso3, is_WTO), by = c("flag_iso3" = "iso3")) %>%
  mutate(fleet = case_when(is_WTO & fmi_best >= managed_cutoff & bad_subs > 0 ~ "affected_managed",
                           is_WTO & fmi_best < managed_cutoff & bad_subs > 0 ~ "affected_oa",
                           (!is_WTO & fmi_best >= managed_cutoff) ~ "unaffected_managed",
                           (!is_WTO & fmi_best < managed_cutoff) ~ "unaffected_oa",
                           TRUE ~ "unaffected_oa"))
```

```{r}
# Create model input for removing all bad subsidies
global_all_BC_rel_summary <- global_fleet_rel_vessels %>%
  group_by(region, fleet) %>%
  summarize(catch = sum(catch, na.rm = T),
            bad_subs = sum(bad_subs, na.rm = T) + sum(ugly_subs, na.rm = T),
            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
            removed_subs = sum(bad_subs, na.rm = T) + sum(ugly_subs, na.rm = T)) %>%
  ungroup()

# Turn into a list
global_all_BC_rel_list <- global_all_BC_rel_summary %>%
  group_by(region) %>%
  group_split()
names(global_all_BC_rel_list) <- colnames(bio_dat_regional)[-c(1:2)]

# Run model
global_all_BC_rel_results <- pmap_df(list(fleet = global_all_BC_rel_list, 
                                       region = names(global_all_BC_rel_list),
                                       bio_param = bio_dat_regional_list),
                                  BioEconModel,
                                  end_year = 2100,
                                  return = "all")

# Extract results timeseries
global_all_BC_rel_results_all <- global_all_BC_rel_results %>%
  dplyr::filter(Year > 2018) %>%
  group_by(Year, Variable, Fleet) %>%
  mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU)/abs(BAU),
                          TRUE ~ 0)) %>%
  ungroup() %>%
  mutate(run_id = "rel_subs_all_bad",
         run_name = "Complete removal of capacity-enhancing subisidies - relative subsidies")

write_csv(global_all_BC_rel_results_all, paste0(results_dir, "rel_subs_all_BC_ts.csv"))
```

```{r}
# Make plots
if(make_plots){

  # 1) global (aggregated) timeseries plot
  global_rel_all_BC_ts_plot <- BioEconomicModelPlots(dat = global_all_BC_rel_results_all,
                                                      spatial_res = "global",
                                                      temporal_res = "all",
                                                      start_year = 2018,
                                                      end_year = 2100,
                                                      plot_name = "global_rel_subs_all_BC_ts_plot",
                                                      plot_width = 8,
                                                      plot_height = 6.5,
                                                      results_dir = results_dir)

  # 2) global (aggregated) "kobe" final year plot
  global_rel_all_BC_end_plot <- BioEconomicModelPlots(dat = global_all_BC_rel_results_all,
                                                      spatial_res = "global",
                                                      temporal_res = "last",
                                                      end_year = 2100,
                                                      plot_name = "global_rel_subs_all_BC_end_plot",
                                                      plot_width = 8,
                                                      plot_height = 6.5,
                                                      results_dir = results_dir)

  # 3) regional timeseries plot
  regional_rel_all_BC_ts_plot <- BioEconomicModelPlots(dat = global_all_BC_rel_results_all,
                                                      spatial_res = "regional",
                                                      temporal_res = "all",
                                                      start_year = 2018,
                                                      end_year = 2100,
                                                      plot_name = "regional_rel_subs_all_BC_ts_plot",
                                                      plot_width = 8,
                                                      plot_height = 6.5,
                                                      results_dir = results_dir)

  # 4) regional "kobe" final year plot
  regional_rel_all_BC_end_plot <- BioEconomicModelPlots(dat = global_all_BC_rel_results_all,
                                                      spatial_res = "regional",
                                                      temporal_res = "last",
                                                      end_year = 2100,
                                                      plot_name = "regional_rel_subs_all_BC_end_plot",
                                                      plot_width = 8,
                                                      plot_height = 6.5,
                                                      results_dir = results_dir)
}
```

### 2020-09-02 scripts/06_run_model.Rmd
updating global results

@@
 ---
+# Introduction
+
+This script generates alternative global and regional results.
 
@@
 }
+
+bad_subsidy_types <- c("B1", "B2", "B3", "B4", "B5", "B6", "B7")
+ugly_subsidy_types <- c("C1", "C2", "C3")
 ```
-
-# Introduction
-
-This script generates the most ambitious global and regional results obtained by removing all capacity enhancing subsidies from all WTO Members and Observers.
 
@@
 source(here::here("app", "scripts", "BioEconModel.R"))
+
+# Source plotting script
+source(here::here("scripts", "functions", "BioEconomicModelPlots.R"))
 ```
@@
 
-## Create global fleet
-
 ```{r pressure, echo=FALSE}
 # Assign fleets to vessels
-global_fleet_vessels <- vessel_dat %>%
+fleet_vessels <- vessel_dat %>%
   left_join(country_dependencies %>% dplyr::select(iso3, is_WTO), by = c("flag_iso3" = "iso3")) %>%
@@
                            (!is_WTO & fmi_best < managed_cutoff) ~ "unaffected_oa",
-                           TRUE ~ "unaffected_oa"))
+                           TRUE ~ "unaffected_oa")) %>%
+    mutate(bad_ugly_subs = rowSums(select(., one_of(paste0(c(bad_subsidy_types, ugly_subsidy_types), "_subs")))))
 ```
 
-## Run Model (Remove all bad subsidies)
+# Section 1: Absolute subsidy values
+
+This first section presents results obtained by using absolute subsidy values.
+
+## Scenario 1: Remove all bad + ugly
 
@@
 # Create model input for removing all bad subsidies
-global_all_bad_summary <- global_fleet_vessels %>%
+abs_all_BC_fleet_summary <- fleet_vessels %>%
   group_by(region, fleet) %>%
   summarize(catch = sum(catch, na.rm = T),
-            bad_subs = sum(bad_subs, na.rm = T),
+            bad_subs = sum(bad_ugly_subs, na.rm = T),
             fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
-            removed_subs = sum(bad_subs, na.rm = T)) %>%
+            removed_subs = sum(bad_ugly_subs, na.rm = T)) %>%
   ungroup()
@@
 # Turn into a list
-global_all_bad_list <- global_all_bad_summary %>%
+abs_all_BC_list <- abs_all_BC_fleet_summary %>%
   group_by(region) %>%
   group_split()
-names(global_all_bad_list) <- colnames(bio_dat_regional)[-c(1:2)]
+names(abs_all_BC_list) <- colnames(bio_dat_regional)[-c(1:2)]
 
 # Run model
-global_all_bad_results <- pmap_df(list(fleet = global_all_bad_list, 
-                                       region = names(global_all_bad_list),
+abs_all_BC_results <- pmap_df(list(fleet = abs_all_BC_list, 
+                                       region = names(abs_all_BC_list),
                                        bio_param = bio_dat_regional_list),
@@
 # Extract results timeseries
-global_all_bad_results_full <- global_all_bad_results %>%
+abs_all_BC_results_all <- abs_all_BC_results %>%
   dplyr::filter(Year > 2018) %>%
-  dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total")) %>%
   group_by(Year, Variable, Fleet) %>%
   mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU)/abs(BAU),
-                          TRUE ~ 0),
-         BAU_global = sum(BAU, na.rm = T),
-         Reform_global = sum(Reform, na.rm = T),
-         Diff_global = case_when(BAU_global != 0 ~ (Reform_global - BAU_global)/abs(BAU_global),
                           TRUE ~ 0)) %>%
   ungroup() %>%
-  mutate(run_number = "A",
-         run_name = "Most ambitious scenario",
-         id = "A",
-         Description = "Complete removal of all capacity-enhancing subsidies (for comparison)")
+  mutate(run_id = "Absolute",
+         run_name = "All subsidies")
 
-# Extract ending results (difference only)
-global_all_bad_results_last <- global_all_bad_results_full %>%
-  dplyr::filter(Year == 2100) %>%
-  group_by(Year, Variable) %>%
-  summarize(Value = unique(Diff_global)*100) %>%
-  ungroup() %>%
-  spread(Variable, Value) %>%
-  rename(Biomass = biomass,
-         Catches = catches_total,
-         Revenue = revenue_total) %>%
-  mutate(run_number = "A",
-         run_name = "Most ambitious scenario")
-
+write_csv(abs_all_BC_results_all, paste0(results_dir, "abs_subs_all_BC_ts.csv"))
 ```
@@
   # 1) global (aggregated) timeseries plot
-  global_all_bad_plot <- global_all_bad_results_full %>%
-        group_by(run_number, run_name, id, Year, Variable, Fleet) %>%
-        summarize(BAU = unique(BAU_global),
-                  Reform = unique(Reform_global),
-                  Diff = unique(Diff_global)) %>%
-        ungroup() %>%
-        mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
-                                    Variable == "catches_total" ~ "Catches",
-                                    Variable == "revenue_total" ~ "Revenue")) %>%
-        mutate(Region = "Global") %>%
-        ggplot()+
-        aes(x = Year, y = Diff*100, color = Variable)+
-        geom_line(size = 1)+
-        theme_bw()+
-        geom_hline(yintercept = 0)+
-        scale_x_continuous(expand = c(0,0))+
-        labs(x = "Year", y = "Change relative to BAU (%)")+
-        theme(legend.position = "none")+
-        facet_wrap(~Variable, ncol = 1, scales = "free_y")
+  abs_all_BC_ts_plot <- BioEconomicModelPlots(dat = abs_all_BC_results_all,
+                                              spatial_res = "global",
+                                              temporal_res = "all",
+                                              start_year = 2018,
+                                              end_year = 2100,
+                                              plot_name = "abs_all_BC_ts_plot",
+                                              plot_width = 8,
+                                              plot_height = 6.5,
+                                              results_dir = results_dir)
 
-  ggsave(paste0(results_dir, "global_all_bad_timeseries_plot.png"), global_all_bad_plot, width = 7.5, height = 6, units = "in")
+  # 2) global (aggregated) "kobe" final year plot
+  abs_all_BC_end_plot <- BioEconomicModelPlots(dat = abs_all_BC_results_all,
+                                                      spatial_res = "global",
+                                                      temporal_res = "last",
+                                                      end_year = 2100,
+                                                      plot_name = "abs_all_BC_end_plot",
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
 
-  # 2) regional timeseries plot
-  regional_all_bad_plot <- global_all_bad_results_full %>%
-        dplyr::select(run_number, run_name, id, Year, Variable, Fleet, Region, BAU, Reform, Diff) %>%
-        mutate(Region = case_when(Region == "atlantic" ~ "Atlantic Ocean",
-                                  Region == "indian" ~ "Indian Ocean",
-                                  Region == "pacific" ~ "Pacific Ocean")) %>%
-        mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
-                                    Variable == "catches_total" ~ "Catches",
-                                    Variable == "revenue_total" ~ "Revenue")) %>%
-        ggplot()+
-        aes(x = Year, y = Diff*100, color = Variable)+
-        geom_line(size = 1)+
-        theme_bw()+
-        geom_hline(yintercept = 0)+
-        scale_x_continuous(expand = c(0,0))+
-        labs(x = "Year", y = "Change relative to BAU (%)")+
-        theme(legend.position = "none")+
-        facet_wrap(Variable ~ Region, ncol = 3, scales = "free_y")
+  # 3) regional timeseries plot
+  regional_abs_all_BC_ts_plot <- BioEconomicModelPlots(dat = abs_all_BC_results_all,
+                                                      spatial_res = "regional",
+                                                      temporal_res = "all",
+                                                      start_year = 2018,
+                                                      end_year = 2100,
+                                                      plot_name = "regional_abs_all_BC_ts_plot",
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
 
-  ggsave(paste0(results_dir, "regional_all_bad_timeseries_plot.png"), regional_all_bad_plot, width = 7.5, height = 6, units = "in")
-
+  # 4) regional "kobe" final year plot
+  regional_abs_all_BC_end_plot <- BioEconomicModelPlots(dat = abs_all_BC_results_all,
+                                                      spatial_res = "regional",
+                                                      temporal_res = "last",
+                                                      end_year = 2100,
+                                                      plot_name = "regional_abs_all_BC_end_plot",
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
 }
 ```
+
+## Scenario 2: Remove all bad
+
+```{r}
+# Create model input for removing all bad subsidies
+abs_all_B_fleet_summary <- fleet_vessels %>%
+  group_by(region, fleet) %>%
+  summarize(catch = sum(catch, na.rm = T),
+            bad_subs = sum(bad_ugly_subs, na.rm = T),
+            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
+            removed_subs = sum(bad_subs, na.rm = T)) %>%
+  ungroup()
+
+# Turn into a list
+abs_all_B_list <- abs_all_B_fleet_summary %>%
+  group_by(region) %>%
+  group_split()
+names(abs_all_B_list) <- colnames(bio_dat_regional)[-c(1:2)]
+
+# Run model
+abs_all_B_results <- pmap_df(list(fleet = abs_all_B_list, 
+                                       region = names(abs_all_B_list),
+                                       bio_param = bio_dat_regional_list),
+                                  BioEconModel,
+                                  end_year = 2100,
+                                  return = "all")
+
+# Extract results timeseries
+abs_all_B_results_all <- abs_all_B_results %>%
+  dplyr::filter(Year > 2018) %>%
+  group_by(Year, Variable, Fleet) %>%
+  mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU)/abs(BAU),
+                          TRUE ~ 0)) %>%
+  ungroup() %>%
+  mutate(run_id = "Absolute",
+         run_name = "Capacity-enhancing subsidies")
+
+write_csv(abs_all_B_results_all, paste0(results_dir, "abs_subs_all_B_ts.csv"))
+```
+
+```{r}
+# Make plots
+if(make_plots){
+
+  # 1) global (aggregated) timeseries plot
+  abs_all_B_ts_plot <- BioEconomicModelPlots(dat = abs_all_B_results_all,
+                                              spatial_res = "global",
+                                              temporal_res = "all",
+                                              start_year = 2018,
+                                              end_year = 2100,
+                                              plot_name = "abs_all_B_ts_plot",
+                                              plot_width = 8,
+                                              plot_height = 6.5,
+                                              results_dir = results_dir)
+
+  # 2) global (aggregated) "kobe" final year plot
+  abs_all_B_end_plot <- BioEconomicModelPlots(dat = abs_all_B_results_all,
+                                                      spatial_res = "global",
+                                                      temporal_res = "last",
+                                                      end_year = 2100,
+                                                      plot_name = "abs_all_B_end_plot",
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+
+  # 3) regional timeseries plot
+  regional_abs_all_B_ts_plot <- BioEconomicModelPlots(dat = abs_all_B_results_all,
+                                                      spatial_res = "regional",
+                                                      temporal_res = "all",
+                                                      start_year = 2018,
+                                                      end_year = 2100,
+                                                      plot_name = "regional_abs_all_B_ts_plot",
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+
+  # 4) regional "kobe" final year plot
+  regional_abs_all_B_end_plot <- BioEconomicModelPlots(dat = abs_all_B_results_all,
+                                                      spatial_res = "regional",
+                                                      temporal_res = "last",
+                                                      end_year = 2100,
+                                                      plot_name = "regional_abs_all_B_end_plot",
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+}
+```
+
+## Scenario 3: Remove fuel subsidies
+
+```{r}
+# Create model input for removing all bad subsidies
+abs_fuel_fleet_summary <- fleet_vessels %>%
+  group_by(region, fleet) %>%
+  summarize(catch = sum(catch, na.rm = T),
+            bad_subs = sum(bad_ugly_subs, na.rm = T),
+            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
+            removed_subs = sum(B7_subs, na.rm = T)) %>%
+  ungroup()
+
+# Turn into a list
+abs_fuel_list <- abs_fuel_fleet_summary %>%
+  group_by(region) %>%
+  group_split()
+names(abs_fuel_list) <- colnames(bio_dat_regional)[-c(1:2)]
+
+# Run model
+abs_fuel_results <- pmap_df(list(fleet = abs_fuel_list, 
+                                       region = names(abs_fuel_list),
+                                       bio_param = bio_dat_regional_list),
+                                  BioEconModel,
+                                  end_year = 2100,
+                                  return = "all")
+
+# Extract results timeseries
+abs_fuel_results_all <- abs_fuel_results %>%
+  dplyr::filter(Year > 2018) %>%
+  group_by(Year, Variable, Fleet) %>%
+  mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU)/abs(BAU),
+                          TRUE ~ 0)) %>%
+  ungroup() %>%
+  mutate(run_id = "Absolute",
+         run_name = "Fuel subsidies")
+
+write_csv(abs_fuel_results_all, paste0(results_dir, "abs_subs_fuel_ts.csv"))
+```
+
+```{r}
+# Make plots
+if(make_plots){
+
+  # 1) global (aggregated) timeseries plot
+  abs_fuel_ts_plot <- BioEconomicModelPlots(dat = abs_fuel_results_all,
+                                              spatial_res = "global",
+                                              temporal_res = "all",
+                                              start_year = 2018,
+                                              end_year = 2100,
+                                              plot_name = "abs_fuel_ts_plot",
+                                              plot_width = 8,
+                                              plot_height = 6.5,
+                                              results_dir = results_dir)
+
+  # 2) global (aggregated) "kobe" final year plot
+  abs_fuel_end_plot <- BioEconomicModelPlots(dat = abs_fuel_results_all,
+                                                      spatial_res = "global",
+                                                      temporal_res = "last",
+                                                      end_year = 2100,
+                                                      plot_name = "abs_fuel_end_plot",
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+
+  # 3) regional timeseries plot
+  regional_abs_fuel_ts_plot <- BioEconomicModelPlots(dat = abs_fuel_results_all,
+                                                      spatial_res = "regional",
+                                                      temporal_res = "all",
+                                                      start_year = 2018,
+                                                      end_year = 2100,
+                                                      plot_name = "regional_abs_fuel_ts_plot",
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+
+  # 4) regional "kobe" final year plot
+  regional_abs_fuel_end_plot <- BioEconomicModelPlots(dat = abs_fuel_results_all,
+                                                      spatial_res = "regional",
+                                                      temporal_res = "last",
+                                                      end_year = 2100,
+                                                      plot_name = "regional_abs_fuel_end_plot",
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+}
+```
+## Combine absolute subsidy results
+
+```{r}
+abs_results_all <- abs_all_BC_results_all %>%
+  bind_rows(abs_all_B_results_all) %>%
+  bind_rows(abs_fuel_results_all)
+```
+
+# Section 2: Effective subsidies
+
+This second section presents results obtained by using effective subsidy values - based on suggestions from Roger Martini at the OECD.
+
+```{r}
+rel <- read_csv(here::here("data", "lookup-tables", "oecd_relative_effects_lookup_table.csv"))
+
+rel_fleet_vessels <- fleet_vessels %>%
+   mutate(B1_subs = B1_subs * rel$rel_effect_effort[rel$type == "B1"], 
+           B2_subs = B2_subs * rel$rel_effect_effort[rel$type == "B2"],
+           B3_subs = B3_subs * rel$rel_effect_effort[rel$type == "B3"],
+           B4_subs = B4_subs * rel$rel_effect_effort[rel$type == "B4"],
+           B5_subs = B5_subs * rel$rel_effect_effort[rel$type == "B5"], 
+           B6_subs = B6_subs * rel$rel_effect_effort[rel$type == "B6"],
+           B7_subs = B7_subs * rel$rel_effect_effort[rel$type == "B7"], 
+           C1_subs = C1_subs * rel$rel_effect_effort[rel$type == "C1"], 
+           C2_subs = C2_subs * rel$rel_effect_effort[rel$type == "C2"],
+           C3_subs = C3_subs * rel$rel_effect_effort[rel$type == "C3"]) %>%
+  ungroup() %>%
+  mutate(bad_subs = rowSums(select(., one_of(paste0(bad_subsidy_types, "_subs")))),
+         ugly_subs = rowSums(select(., one_of(paste0(ugly_subsidy_types, "_subs")))),
+         bad_ugly_subs = rowSums(select(., one_of(paste0(c(bad_subsidy_types, ugly_subsidy_types), "_subs")))))
+```
+
+## Scenario 1: Remove all bad + ugly
+
+```{r}
+# Create model input for removing all bad subsidies
+rel_all_BC_fleet_summary <- rel_fleet_vessels %>%
+  group_by(region, fleet) %>%
+  summarize(catch = sum(catch, na.rm = T),
+            bad_subs = sum(bad_ugly_subs, na.rm = T),
+            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
+            removed_subs = sum(bad_ugly_subs, na.rm = T)) %>%
+  ungroup()
+
+# Turn into a list
+rel_all_BC_list <- rel_all_BC_fleet_summary %>%
+  group_by(region) %>%
+  group_split()
+names(rel_all_BC_list) <- colnames(bio_dat_regional)[-c(1:2)]
+
+# Run model
+rel_all_BC_results <- pmap_df(list(fleet = rel_all_BC_list, 
+                                       region = names(rel_all_BC_list),
+                                       bio_param = bio_dat_regional_list),
+                                  BioEconModel,
+                                  end_year = 2100,
+                                  return = "all")
+
+# Extract results timeseries
+rel_all_BC_results_all <- rel_all_BC_results %>%
+  dplyr::filter(Year > 2018) %>%
+  group_by(Year, Variable, Fleet) %>%
+  mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU)/abs(BAU),
+                          TRUE ~ 0)) %>%
+  ungroup() %>%
+  mutate(run_id = "Effective",
+         run_name = "All subsidies")
+
+write_csv(rel_all_BC_results_all, paste0(results_dir, "rel_subs_all_BC_ts.csv"))
+```
+
+```{r}
+# Make plots
+if(make_plots){
+
+  # 1) global (aggregated) timeseries plot
+  rel_all_BC_ts_plot <- BioEconomicModelPlots(dat = rel_all_BC_results_all,
+                                              spatial_res = "global",
+                                              temporal_res = "all",
+                                              start_year = 2018,
+                                              end_year = 2100,
+                                              plot_name = "rel_all_BC_ts_plot",
+                                              plot_width = 8,
+                                              plot_height = 6.5,
+                                              results_dir = results_dir)
+
+  # 2) global (aggregated) "kobe" final year plot
+  rel_all_BC_end_plot <- BioEconomicModelPlots(dat = rel_all_BC_results_all,
+                                                      spatial_res = "global",
+                                                      temporal_res = "last",
+                                                      end_year = 2100,
+                                                      plot_name = "rel_all_BC_end_plot",
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+
+  # 3) regional timeseries plot
+  regional_rel_all_BC_ts_plot <- BioEconomicModelPlots(dat = rel_all_BC_results_all,
+                                                      spatial_res = "regional",
+                                                      temporal_res = "all",
+                                                      start_year = 2018,
+                                                      end_year = 2100,
+                                                      plot_name = "regional_rel_all_BC_ts_plot",
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+
+  # 4) regional "kobe" final year plot
+  regional_rel_all_BC_end_plot <- BioEconomicModelPlots(dat = rel_all_BC_results_all,
+                                                      spatial_res = "regional",
+                                                      temporal_res = "last",
+                                                      end_year = 2100,
+                                                      plot_name = "regional_rel_all_BC_end_plot",
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+}
+```
+
+## Scenario 2: Remove all bad
+
+```{r}
+# Create model input for removing all bad subsidies
+rel_all_B_fleet_summary <- rel_fleet_vessels %>%
+  group_by(region, fleet) %>%
+  summarize(catch = sum(catch, na.rm = T),
+            bad_subs = sum(bad_ugly_subs, na.rm = T),
+            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
+            removed_subs = sum(bad_subs, na.rm = T)) %>%
+  ungroup()
+
+# Turn into a list
+rel_all_B_list <- rel_all_B_fleet_summary %>%
+  group_by(region) %>%
+  group_split()
+names(rel_all_B_list) <- colnames(bio_dat_regional)[-c(1:2)]
+
+# Run model
+rel_all_B_results <- pmap_df(list(fleet = rel_all_B_list, 
+                                       region = names(rel_all_B_list),
+                                       bio_param = bio_dat_regional_list),
+                                  BioEconModel,
+                                  end_year = 2100,
+                                  return = "all")
+
+# Extract results timeseries
+rel_all_B_results_all <- rel_all_B_results %>%
+  dplyr::filter(Year > 2018) %>%
+  group_by(Year, Variable, Fleet) %>%
+  mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU)/abs(BAU),
+                          TRUE ~ 0)) %>%
+  ungroup() %>%
+  mutate(run_id = "Effective",
+         run_name = "Capacity-enhancing subsidies")
+
+write_csv(rel_all_B_results_all, paste0(results_dir, "rel_subs_all_B_ts.csv"))
+```
+
+```{r}
+# Make plots
+if(make_plots){
+
+  # 1) global (aggregated) timeseries plot
+  rel_all_B_ts_plot <- BioEconomicModelPlots(dat = rel_all_B_results_all,
+                                              spatial_res = "global",
+                                              temporal_res = "all",
+                                              start_year = 2018,
+                                              end_year = 2100,
+                                              plot_name = "rel_all_B_ts_plot",
+                                              plot_width = 8,
+                                              plot_height = 6.5,
+                                              results_dir = results_dir)
+
+  # 2) global (aggregated) "kobe" final year plot
+  rel_all_B_end_plot <- BioEconomicModelPlots(dat = rel_all_B_results_all,
+                                                      spatial_res = "global",
+                                                      temporal_res = "last",
+                                                      end_year = 2100,
+                                                      plot_name = "rel_all_B_end_plot",
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+
+  # 3) regional timeseries plot
+  regional_rel_all_B_ts_plot <- BioEconomicModelPlots(dat = rel_all_B_results_all,
+                                                      spatial_res = "regional",
+                                                      temporal_res = "all",
+                                                      start_year = 2018,
+                                                      end_year = 2100,
+                                                      plot_name = "regional_rel_all_B_ts_plot",
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+
+  # 4) regional "kobe" final year plot
+  regional_rel_all_B_end_plot <- BioEconomicModelPlots(dat = rel_all_B_results_all,
+                                                      spatial_res = "regional",
+                                                      temporal_res = "last",
+                                                      end_year = 2100,
+                                                      plot_name = "regional_rel_all_B_end_plot",
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+}
+```
+
+## Scenario 3: Remove fuel subsidies
+
+```{r}
+# Create model input for removing all bad subsidies
+rel_fuel_fleet_summary <- rel_fleet_vessels %>%
+  group_by(region, fleet) %>%
+  summarize(catch = sum(catch, na.rm = T),
+            bad_subs = sum(bad_ugly_subs, na.rm = T),
+            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
+            removed_subs = sum(B7_subs, na.rm = T)) %>%
+  ungroup()
+
+# Turn into a list
+rel_fuel_list <- rel_fuel_fleet_summary %>%
+  group_by(region) %>%
+  group_split()
+names(rel_fuel_list) <- colnames(bio_dat_regional)[-c(1:2)]
+
+# Run model
+rel_fuel_results <- pmap_df(list(fleet = rel_fuel_list, 
+                                       region = names(rel_fuel_list),
+                                       bio_param = bio_dat_regional_list),
+                                  BioEconModel,
+                                  end_year = 2100,
+                                  return = "all")
+
+# Extract results timeseries
+rel_fuel_results_all <- rel_fuel_results %>%
+  dplyr::filter(Year > 2018) %>%
+  group_by(Year, Variable, Fleet) %>%
+  mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU)/abs(BAU),
+                          TRUE ~ 0)) %>%
+  ungroup() %>%
+  mutate(run_id = "Effective",
+         run_name = "Fuel subsidies")
+
+write_csv(rel_fuel_results_all, paste0(results_dir, "rel_subs_fuel_ts.csv"))
+```
+
+```{r}
+# Make plots
+if(make_plots){
+
+  # 1) global (aggregated) timeseries plot
+  rel_fuel_ts_plot <- BioEconomicModelPlots(dat = rel_fuel_results_all,
+                                              spatial_res = "global",
+                                              temporal_res = "all",
+                                              start_year = 2018,
+                                              end_year = 2100,
+                                              plot_name = "rel_fuel_ts_plot",
+                                              plot_width = 8,
+                                              plot_height = 6.5,
+                                              results_dir = results_dir)
+
+  # 2) global (aggregated) "kobe" final year plot
+  rel_fuel_end_plot <- BioEconomicModelPlots(dat = rel_fuel_results_all,
+                                                      spatial_res = "global",
+                                                      temporal_res = "last",
+                                                      end_year = 2100,
+                                                      plot_name = "rel_fuel_end_plot",
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+
+  # 3) regional timeseries plot
+  regional_fuel_BC_ts_plot <- BioEconomicModelPlots(dat = rel_fuel_results_all,
+                                                      spatial_res = "regional",
+                                                      temporal_res = "all",
+                                                      start_year = 2018,
+                                                      end_year = 2100,
+                                                      plot_name = "regional_rel_fuel_ts_plot",
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+
+  # 4) regional "kobe" final year plot
+  regional_rel_fuel_end_plot <- BioEconomicModelPlots(dat = rel_fuel_results_all,
+                                                      spatial_res = "regional",
+                                                      temporal_res = "last",
+                                                      end_year = 2100,
+                                                      plot_name = "regional_rel_fuel_end_plot",
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+}
+```
+
+## Combine absolute subsidy results
+
+```{r}
+rel_results_all <- rel_all_BC_results_all %>%
+  bind_rows(rel_all_B_results_all) %>%
+  bind_rows(rel_fuel_results_all)
+```
+
+# Compare
+
+```{r}
+results_all <- abs_results_all %>%
+  bind_rows(rel_results_all)
+
+# Make plots
+if(make_plots){
+
+  # 1) global (aggregated) timeseries plot
+  compare_ts_plot <- BioEconomicModelPlots(dat = results_all,
+                                           spatial_res = "global",
+                                           temporal_res = "all",
+                                           start_year = 2018,
+                                           end_year = 2100,
+                                           plot_name = "compare_ts_plot",
+                                           plot_width = 8,
+                                           plot_height = 6.5,
+                                           results_dir = results_dir,
+                                           compare = TRUE)
+
+  # 2) global (aggregated) "kobe" final year plot
+  compare_end_plot <- BioEconomicModelPlots(dat = results_all,
+                                            spatial_res = "global",
+                                            temporal_res = "last",
+                                            end_year = 2100,
+                                            plot_name = "compare_end_plot",
+                                            plot_width = 8,
+                                            plot_height = 6.5,
+                                            results_dir = results_dir,
+                                            compare = TRUE)
+
+  # 3) regional timeseries plot
+  regional_compare_ts_plot <- BioEconomicModelPlots(dat = results_all,
+                                                    spatial_res = "regional",
+                                                    temporal_res = "all",
+                                                    start_year = 2018,
+                                                    end_year = 2100,
+                                                    plot_name = "regional_compare_ts_plot",
+                                                    plot_width = 8,
+                                                    plot_height = 6.5,
+                                                    results_dir = results_dir,
+                                                    compare = TRUE)
+
+  # 4) regional "kobe" final year plot
+  regional_compare_end_plot <- BioEconomicModelPlots(dat = results_all,
+                                                     spatial_res = "regional",
+                                                     temporal_res = "last",
+                                                     end_year = 2100,
+                                                     plot_name = "regional_compare_end_plot",
+                                                     plot_width = 8,
+                                                     plot_height = 6.5,
+                                                     results_dir = results_dir,
+                                                     compare = TRUE)
+}
+```
+```

### 2020-09-02 scripts/07_alternate_results.Rmd
updating global results

---
output:
  html_document: default

title: "SubsidyExplorer - Step 7: Alternative Results"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
bibliography: "../pew-subsidies.bib"
---
# Introduction

This script generates alternative global and regional results.

```{r setup, include=FALSE}
# Load packages
library(knitr) 
library(tidyverse)

knitr::opts_chunk$set(echo = TRUE)

make_plots <- T

if(make_plots){
  library(RColorBrewer)
  library(scales)
}

# Directories for the output files generated by this script
results_dir <- here::here("results", "07-alternate-results/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}
```

```{r}
# Source model script
source(here::here("app", "scripts", "BioEconModel.R"))

# Source plotting script
source(here::here("scripts", "functions", "BioEconomicModelPlots.R"))
```

```{r}
# Load vessel list
vessel_dat <- read.csv(here::here("app", "data", "vessel_list_2018_final.csv"), stringsAsFactors = F)

# Create high seas code
vessel_dat <- vessel_dat %>%
  mutate(eez_hs_code = case_when(eez_id == 0 ~ paste0("HS-", fao_region),
                                 TRUE ~ as.character(eez_id)))

# Load country dependencies helper file
country_dependencies <- read_csv(here::here("data", "lookup-tables", "country_dependencies.csv"))
```

```{r}
# Load biological parameters for the model
bio_dat_regional <- read.csv(here::here("app", "data", "model_parameters_regional_3_regions.csv"))

# Regional parameter list
bio_dat_regional_list <- bio_dat_regional %>%
  gather(region, value, -c(1:2)) %>%
  group_by(region) %>%
  group_split()
```

```{r}
# Threshold to be considered managed (using FMI scores)
managed_cutoff <- 0.66
```

```{r pressure, echo=FALSE}
# Assign fleets to vessels
global_fleet_vessels <- vessel_dat %>%
  left_join(country_dependencies %>% dplyr::select(iso3, is_WTO), by = c("flag_iso3" = "iso3")) %>%
  mutate(fleet = case_when(is_WTO & fmi_best >= managed_cutoff & bad_subs > 0 ~ "affected_managed",
                           is_WTO & fmi_best < managed_cutoff & bad_subs > 0 ~ "affected_oa",
                           (!is_WTO & fmi_best >= managed_cutoff) ~ "unaffected_managed",
                           (!is_WTO & fmi_best < managed_cutoff) ~ "unaffected_oa",
                           TRUE ~ "unaffected_oa"))
```

# Category 1: Absolute subsidy values

```{r}
# Create model input for removing all bad subsidies
global_all_bad_summary <- global_fleet_vessels %>%
  group_by(region, fleet) %>%
  summarize(catch = sum(catch, na.rm = T),
            bad_subs = sum(bad_subs, na.rm = T),
            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
            removed_subs = sum(bad_subs, na.rm = T)) %>%
  ungroup()

# Turn into a list
global_all_bad_list <- global_all_bad_summary %>%
  group_by(region) %>%
  group_split()
names(global_all_bad_list) <- colnames(bio_dat_regional)[-c(1:2)]

# Run model
global_all_bad_results <- pmap_df(list(fleet = global_all_bad_list, 
                                       region = names(global_all_bad_list),
                                       bio_param = bio_dat_regional_list),
                                  BioEconModel,
                                  end_year = 2100,
                                  return = "all")

# Extract results timeseries
global_all_bad_results_full <- global_all_bad_results %>%
  dplyr::filter(Year > 2018) %>%
  dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total")) %>%
  group_by(Year, Variable, Fleet) %>%
  mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU)/abs(BAU),
                          TRUE ~ 0),
         BAU_global = sum(BAU, na.rm = T),
         Reform_global = sum(Reform, na.rm = T),
         Diff_global = case_when(BAU_global != 0 ~ (Reform_global - BAU_global)/abs(BAU_global),
                                 TRUE ~ 0)) %>%
  ungroup() %>%
  mutate(run_number = "A",
         run_name = "Most ambitious scenario",
         id = "A",
         Description = "Complete removal of all capacity-enhancing subsidies (for comparison)")

write_csv(global_all_bad_results_full, paste0(results_dir, "all_bad_ts.csv"))

# Extract ending results (difference only)
global_all_bad_results_last <- global_all_bad_results_full %>%
  dplyr::filter(Year == 2100) %>%
  group_by(Year, Variable) %>%
  summarize(Value = unique(Diff_global)*100) %>%
  ungroup() %>%
  spread(Variable, Value) %>%
  rename(Biomass = biomass,
         Catches = catches_total,
         Revenue = revenue_total) %>%
  mutate(run_number = "A",
         run_name = "Most ambitious scenario")

write_csv(global_all_bad_results_full, paste0(results_dir, "all_bad_ts.csv"))

```

```{r}
# Make plots
if(make_plots){

  # 1) global (aggregated) timeseries plot
  global_all_bad_plot <- global_all_bad_results_full %>%
        group_by(run_number, run_name, id, Year, Variable, Fleet) %>%
        summarize(BAU = unique(BAU_global),
                  Reform = unique(Reform_global),
                  Diff = unique(Diff_global)) %>%
        ungroup() %>%
        mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                                    Variable == "catches_total" ~ "Catches",
                                    Variable == "revenue_total" ~ "Revenue")) %>%
        mutate(Region = "Global") %>%
        ggplot()+
        aes(x = Year, y = Diff*100, color = Variable)+
        geom_line(size = 1)+
        theme_bw()+
        geom_hline(yintercept = 0)+
        scale_x_continuous(expand = c(0,0))+
        labs(x = "Year", y = "Change relative to BAU (%)")+
        theme(legend.position = "none")+
        facet_wrap(~Variable, ncol = 1, scales = "free_y")

  ggsave(paste0(results_dir, "global_all_bad_timeseries_plot.png"), global_all_bad_plot, width = 7.5, height = 6, units = "in")

  # 2) regional timeseries plot
  regional_all_bad_plot <- global_all_bad_results_full %>%
        dplyr::select(run_number, run_name, id, Year, Variable, Fleet, Region, BAU, Reform, Diff) %>%
        mutate(Region = case_when(Region == "atlantic" ~ "Atlantic Ocean",
                                  Region == "indian" ~ "Indian Ocean",
                                  Region == "pacific" ~ "Pacific Ocean")) %>%
        mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                                    Variable == "catches_total" ~ "Catches",
                                    Variable == "revenue_total" ~ "Revenue")) %>%
        ggplot()+
        aes(x = Year, y = Diff*100, color = Variable)+
        geom_line(size = 1)+
        theme_bw()+
        geom_hline(yintercept = 0)+
        scale_x_continuous(expand = c(0,0))+
        labs(x = "Year", y = "Change relative to BAU (%)")+
        theme(legend.position = "none")+
        facet_wrap(Variable ~ Region, ncol = 3, scales = "free_y")

  ggsave(paste0(results_dir, "regional_all_bad_timeseries_plot.png"), regional_all_bad_plot, width = 7.5, height = 6, units = "in")

}
```

### 2020-09-02 scripts/functions/BioEconomicModelPlots.R

@@ -1,0 +1,181 @@
+
+BioEconomicModelPlots <- function(dat,
+                                  spatial_res = "global", # or regional
+                                  temporal_res = "all", # or last
+                                  start_year = 2018,
+                                  end_year = 2100,
+                                  variables_keep = c("Biomass" = "biomass",
+                                                     "Catches" = "catches_total",
+                                                     "Revenue" = "revenue_total"),
+                                  fleets_keep = c("Total" = "Total"),
+                                  plot_name = "plot",
+                                  plot_width = 8,
+                                  plot_height = 6.5,
+                                  results_dir,
+                                  compare = FALSE){
+  
+  ### General theme
+  plot_theme <- theme_linedraw()+
+    theme(legend.position="right",
+          legend.box="vertical")
+    
+  ### Aggregate data
+  if(spatial_res == "global"){
+    
+  plot_dat <- dat %>%
+    dplyr::filter(Variable %in% variables_keep) %>%
+    dplyr::filter(Fleet %in% fleets_keep) %>%
+    group_by(Year, Variable, Fleet, run_id, run_name) %>%
+    summarize(BAU_tot = sum(BAU, na.rm = T),
+              Reform_tot = sum(Reform, na.rm = T),
+              Diff_tot = case_when(BAU_tot != 0 ~ (Reform_tot - BAU_tot)/abs(BAU_tot),
+                            TRUE ~ 0)) %>%
+    ungroup() %>%
+    mutate(Region = "Global") %>%
+    mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
+                                Variable == "catches_total" ~ "Catches",
+                                Variable == "revenue_total" ~ "Revenue"))
+    
+  }else if(spatial_res == "regional"){
+    
+    plot_dat <- dat %>%
+      dplyr::filter(Variable %in% variables_keep) %>%
+      dplyr::filter(Fleet %in% fleets_keep) %>%
+      group_by(Year, Variable, Fleet, Region, run_id, run_name) %>%
+      mutate(BAU_tot = sum(BAU, na.rm = T),
+             Reform_tot = sum(Reform, na.rm = T),
[…]

### 2020-09-03 scripts/07_proposals.Rmd
custom proposal page

---
output:
  html_document: default

title: "SubsidyExplorer - Step 6: Run Model"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
bibliography: "../pew-subsidies.bib"
---

# Introduction

This script generates the most ambitious global and regional results obtained by removing all capacity enhancing subsidies from all WTO Members and Observers.

```{r setup, include=FALSE}
# Load packages
library(knitr) 
library(tidyverse)

knitr::opts_chunk$set(echo = TRUE)

make_plots <- T

if(make_plots){
  library(RColorBrewer)
  library(scales)
}

# Directories for the output files generated by this script
results_dir <- here::here("results", "07-sensitivity-analysis/")
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}
```

```{r}
# Source model script
source(here::here("app", "scripts", "BioEconModel.R"))

# Source plotting script
source(here::here("scripts", "functions", "BioEconomicModelPlots.R"))
```

```{r}
# Load vessel list
vessel_dat <- read.csv(here::here("app", "data", "vessel_list_2018_final.csv"), stringsAsFactors = F)

# Create high seas code
vessel_dat <- vessel_dat %>%
  mutate(eez_hs_code = case_when(eez_id == 0 ~ paste0("HS-", fao_region),
                                 TRUE ~ as.character(eez_id)))

# Load country dependencies helper file
country_dependencies <- read_csv(here::here("data", "lookup-tables", "country_dependencies.csv"))

# Vector of all WTO Members and Observers for use in the app [does not include the overseas territories associated with them]
wto_members_and_observers <- country_dependencies$iso3[country_dependencies$is_WTO & !country_dependencies$is_overseas_territory]
```

```{r}
# Load biological parameters for the model
bio_dat_regional <- read.csv(here::here("app", "data", "model_parameters_regional_3_regions.csv"))

# Regional parameter list
bio_dat_regional_list <- bio_dat_regional %>%
  gather(region, value, -c(1:2)) %>%
  group_by(region) %>%
  group_split()
```

```{r}
# Threshold to be considered managed (using FMI scores)
managed_cutoff <- 0.66
```

```{r}
# Proposal settings
proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings.csv"), stringsAsFactors = F)

# Proposal names
included_proposals <- proposal_settings %>%
  dplyr::filter(include == "Yes") %>%
  mutate(display_name = case_when(proposal == "Default" ~ "None",
                                  TRUE ~ paste0(title_tool, " (", proposal, ")"))) %>%
  dplyr::select(category, proposal, display_name) %>%
  arrange(category)

proposal_choices <- included_proposals$proposal
names(proposal_choices) <- included_proposals$display_name
```
```{r}
# Combined fishery stats dat

```

## Model proposals

```{r}
proposal_results <- NULL
i <- 1
for(i in 1:length(proposal_choices)){

  # Choose proposal
  proposal <- proposal_choices[i]

  # Get all data for that proposal
  selected_proposal <- included_proposals %>%
      dplyr::filter(proposal == proposal)

  # Get all IUU conditions
  iuu <- 
    list("definitions" = unlist(str_split(selected_proposal$iuu_definitions, ", ")),
         "assumption" = selected_proposal$iuu_assumption,
         "percent" = selected_proposal$iuu_percent,
         "scope" = selected_proposal$iuu_scope,
         "scope_select" = unlist(str_split(selected_proposal$iuu_scope_select, ", ")),
         "scope_manual" = unlist(str_split(selected_proposal$iuu_scope_manual, ", ")),
         "allow_sdt" = selected_proposal$iuu_allow_sdt,
         "sdt_ldc" = selected_proposal$iuu_sdt_ldc,
         "sdt_what_ldc" = unlist(str_split(selected_proposal$iuu_sdt_what_ldc, ", ")),
         "sdt_time_delay_ldc" = selected_proposal$iuu_sdt_time_delay_ldc,
         "sdt_developing" = selected_proposal$iuu_sdt_developing,
         "sdt_what_developing" = unlist(str_split(selected_proposal$iuu_sdt_what_developing, ", ")),
         "sdt_time_delay_developing" = selected_proposal$iuu_sdt_time_delay_developing,
         "sdt_sve" = selected_proposal$iuu_sdt_sve,
         "sdt_what_sve" = unlist(str_split(selected_proposal$iuu_sdt_what_sve, ", ")),
         "sdt_time_delay_sve" = selected_proposal$iuu_sdt_time_delay_sve)

   # Get all OA conditions
   oa <- 
     list("definitions" = unlist(str_split(selected_proposal$oa_definitions, ", ")),
          "scope" = selected_proposal$oa_scope,
          "scope_select" = unlist(str_split(selected_proposal$oa_scope_select, ", ")),
          "scope_manual" = unlist(str_split(selected_proposal$oa_scope_manual, ", ")),
          "hs_cutoff" = selected_proposal$oa_hs_cutoff,
          "length_cutoff" = selected_proposal$oa_length_cutoff,
          "tonnage_cutoff" = selected_proposal$oa_tonnage_cutoff,
          "engine_cutoff" = selected_proposal$oa_engine_cutoff,
          "allow_sdt" = selected_proposal$oa_allow_sdt,
          "sdt_ldc" = selected_proposal$oa_sdt_ldc,
          "sdt_what_ldc" = unlist(str_split(selected_proposal$oa_sdt_what_ldc, ", ")),
          "sdt_hs_cutoff_ldc" = selected_proposal$oa_sdt_hs_cutoff_ldc,
          "sdt_time_delay_ldc" = selected_proposal$oa_sdt_time_delay_ldc,
          "sdt_developing" = selected_proposal$oa_sdt_developing,
          "sdt_what_developing" = unlist(str_split(selected_proposal$oa_sdt_what_developing, ", ")),
          "sdt_hs_cutoff_developing" = selected_proposal$oa_sdt_hs_cutoff_developing,
          "sdt_time_delay_developing" = selected_proposal$oa_sdt_time_delay_developing,
          "sdt_sve" = selected_proposal$oa_sdt_sve,
          "sdt_what_sve" = unlist(str_split(selected_proposal$oa_sdt_what_sve, ", ")),
          "sdt_hs_cutoff_sve" = selected_proposal$oa_sdt_hs_cutoff_sve,
          "sdt_time_delay_sve" = selected_proposal$oa_sdt_time_delay_sve)

   # Get all Overcap conditions
   overcap <- 
     list("definitions" = unlist(str_split(selected_proposal$overcap_definitions, ", ")),
          "scope" = selected_proposal$overcap_scope,
          "scope_select" = unlist(str_split(selected_proposal$overcap_scope_select, ", ")),
          "scope_manual" = unlist(str_split(selected_proposal$overcap_scope_manual, ", ")),
          "hs_cutoff" = selected_proposal$overcap_hs_cutoff,
          "length_cutoff" = selected_proposal$overcap_length_cutoff,
          "tonnage_cutoff" = selected_proposal$overcap_tonnage_cutoff,
          "engine_cutoff" = selected_proposal$overcap_engine_cutoff,
          "allow_sdt" = selected_proposal$overcap_allow_sdt,
          "sdt_ldc" = selected_proposal$overcap_sdt_ldc,
          "sdt_what_ldc" = unlist(str_split(selected_proposal$overcap_sdt_what_ldc, ", ")),
          "sdt_hs_cutoff_ldc" = selected_proposal$overcap_sdt_hs_cutoff_ldc,
          "sdt_time_delay_ldc" = selected_proposal$overcap_sdt_time_delay_ldc,
          "sdt_developing" = selected_proposal$overcap_sdt_developing,
          "sdt_what_developing" = unlist(str_split(selected_proposal$overcap_sdt_what_developing, ", ")),
          "sdt_hs_cutoff_developing" = selected_proposal$overcap_sdt_hs_cutoff_developing,
          "sdt_time_delay_developing" = selected_proposal$overcap_sdt_time_delay_developing,
          "sdt_sve" = selected_proposal$overcap_sdt_sve,
          "sdt_what_sve" = unlist(str_split(selected_proposal$overcap_sdt_what_sve, ", ")),
          "sdt_hs_cutoff_sve" = selected_proposal$overcap_sdt_hs_cutoff_sve,
          "sdt_time_delay_sve" = selected_proposal$overcap_sdt_time_delay_sve)

   # Get all Cap/Tier conditions
   cap_tier = 
     list("on_off" = selected_proposal$cap_on_off,
          "subsidy_types" = unlist(str_split(selected_proposal$cap_subsidy_types, ", ")),
          "tier_number" = selected_proposal$cap_tier_number,
          "tier_system" = selected_proposal$tier_system,
          "two_tier_cutoff" = selected_proposal$two_tier_cutoff,
          "three_tier_cutoff" = as.numeric(unlist(str_split(
          selected_proposal$three_tier_cutoff, ", "
          ))),
          "tier1_cap_rule" = selected_proposal$tier1_cap_rule,
          "tier2_cap_rule" = selected_proposal$tier2_cap_rule,
          "tier3_cap_rule" = selected_proposal$tier3_cap_rule,
          "tier1_cap_value" = selected_proposal$tier1_cap_value,
          "tier1_cap_fishers" = selected_proposal$tier1_cap_fishers,
          "tier1_cap_percent" = selected_proposal$tier1_cap_percent,
          "tier2_cap_value" = selected_proposal$tier2_cap_value,
          "tier2_cap_fishers" = selected_proposal$tier1_cap_fishers,
          "tier2_cap_percent" = selected_proposal$tier2_cap_percent,
          "tier3_cap_value" = selected_proposal$tier3_cap_value,
          "tier3_cap_fishers" = selected_proposal$tier3_cap_fishers,
          "tier3_cap_percent" = selected_proposal$tier3_cap_percent)

   ### Find fleets
    fleet <-  CreateFleets(
      vessel_list = vessel_dat,
      iuu = iuu,
      oa = oa,
      overcap = overcap,
      cap_tier = cap_tier,
      cap_tier_dat = cap_tier_dat,
      profile_dat = combined_fishery_stats_dat,
      managed_threshold = managed_cutoff,
      wto_members_and_observers = wto_members_and_observers,
      subsidy_types_all = subsidy_types_sorted_sumaila,
      flag_summary_dat = flag_summary)

    # Make list
    fleet_list <- fleet$summary %>%
      group_by(region) %>%
      group_split()
    names(fleet_list) <- colnames(bio_dat)[-c(1:2)]

}
```

### 2020-09-03 app/00_initialize_app.R

@@ -270,6 +270,9 @@ proposal_categories <- unique(included_proposals$category)[unique(included_propo
 # 3) Management cutoff 
 managed_cutoff <- 0.66
 
+# 4) Default end year 
+end_year <- 2060
+
 ### OTHER DATA -------------------------------------------------------------------------------------------
 
 # Relative subsidies data
@@ -308,40 +311,6 @@ remove_all_bad_fleet_summary <- remove_all_bad_fleet_vessels %>%
             removed_subs = sum(bad_subs, na.rm = T)) %>%
   ungroup()
 
-# Get affected fleet stats by flag
-# remove_all_bad_fleet_by_flag <- remove_all_bad_fleet_vessels %>%
-#   dplyr::filter(fleet %in% c("affected_managed", "affected_oa")) %>%
-#   group_by(flag) %>%
-#   summarize(n_vessels = n_distinct(ssvid),
-#             fishing_h = sum(fishing_hours_eez_fao, na.rm = T),
-#             fishing_KWh = sum(fishing_KWh_eez_fao, na.rm = T),
-#             catch = sum(catch, na.rm = T),
-#             removed_subs = round(sum(bad_subs, na.rm = T))) %>%
-#   left_join(total_effort_flag, by = c("flag")) %>%
-#   mutate(percent_vessels = (n_vessels/tot_vessels)*100,
-#          percent_fishing_h = (fishing_h/tot_fishing_h)*100,
-#          percent_fishing_KWh = (fishing_KWh/tot_fishing_KWh)*100,
-#          percent_subs_removed = (removed_subs/tot_bad_subs)*100,
-#          percent_catch = (catch/tot_catch)*100) %>%
-#   dplyr::select(-contains("tot_"))
-
-# Get affected fleet stats by fishing a rea
-# remove_all_bad_fleet_by_area <- remove_all_bad_fleet_vessels %>%
-#   dplyr::filter(fleet %in% c("affected_managed", "affected_oa")) %>%
-#   group_by(eez_hs_code) %>%
-#   summarize(n_vessels = n_distinct(ssvid),
-#             fishing_h = sum(fishing_hours_eez_fao, na.rm = T),
-#             fishing_KWh = sum(fishing_KWh_eez_fao, na.rm = T),
-#             catch = sum(catch, na.rm = T),
-#             removed_subs = round(sum(bad_subs, na.rm = T))) %>%
[…]

### 2020-09-03 app/scripts/OASummaryText.R

@@ -1,0 +1,142 @@
+###---------------------------------
+### OA reactive policy summary
+### --------------------------------
+
+OASummaryText <- function(oa,
+                          wid,
+                          text,
+                          country_choices){
+  
+  ### OA title
+  oa_header <- paste0("<b class = 'big'>", "Overfished", "</b>", "</br>")
+  
+  ### Nothing selected ---
+  if(length(oa$definitions) == 0){
+    
+    oa_pro <- "None selected."
+    oa_disciplines <- paste0("<small class = 'gray'>", "DISCIPLINES:  ", "</small>",
+                              "<small>", oa_pro, "</br></small>")
+    
+    oa_scope <- ""
+    
+    oa_sdt <- ""
+    
+    # Output for nothing selected
+    oa_out <- paste0(oa_header,
+                      oa_disciplines,
+                      oa_scope,
+                      oa_sdt)
+    
+  ### At least one definition selected ---
+  }else if(length(oa$definitions) >= 1){
+    
+    oa_pro_names <- unlist(wid$choices[wid$item_id == "w_oa_definitions"])
+    oa_pro_selected <- names(oa_pro_names[oa_pro_names %in% oa$definitions])
+    
+    oa_pro <- paste0("<small>",text$item_label[text$item_id == "w_oa_definitions"], 
+                      "<ul><li>", 
+                      paste0(oa_pro_selected, collapse = "</li><li>"), 
+                      "</li></ul></small>")
+    
+    oa_disciplines <- paste0("<small class = 'gray'>", "DISCIPLINES:  ", "</small>",
+                              oa_pro)
+    
+    ### Scope (at least one definition selected) ---
+    if(oa$scope == "ALL"){
+      
+      oa_scope <- paste0("<small class = 'gray'>", "SCOPE:  ", "</small>",
+                          "<small>", "Disciplines apply to all Members & vessels.", "</br></small>")
+      
+    }else if(oa$scope == "SELECT"){
+      
+      oa_scope_names <- unlist(wid$choices[wid$item_id == "w_oa_scope_select"])
+      
+      oa_scope <- paste0("<small class = 'gray'>", "SCOPE:  ", "</small>",
+                          "<small>", "Disciplines only apply to vessels: ", "<ul>")
+      
+      # MANUAL: Manual country selection
[…]

### 2020-09-03 app/scripts/OvercapSummaryText.R

@@ -1,0 +1,143 @@
+###---------------------------------
+### Overcap reactive policy summary
+### --------------------------------
+
+OvercapSummaryText <- function(overcap,
+                               cap_tier,
+                               wid,
+                               text,
+                               country_choices){
+  
+  ### Overcapacity title
+  overcap_header <- paste0("<b class = 'big'>", "Overfished", "</b>", "</br>")
+  
+  ### Nothing selected ---
+  if(length(overcap$definitions) == 0){
+    
+    overcap_pro <- "None selected."
+    overcap_disciplines <- paste0("<small class = 'gray'>", "DISCIPLINES:  ", "</small>",
+                              "<small>", overcap_pro, "</br></small>")
+    
+    overcap_scope <- ""
+    
+    overcap_sdt <- ""
+    
+    # Output for nothing selected
+    overcap_out <- paste0(overcap_header,
+                      overcap_disciplines,
+                      overcap_scope,
+                      overcap_sdt)
+    
+  ### At least one definition selected ---
+  }else if(length(overcap$definitions) >= 1){
+    
+    overcap_pro_names <- unlist(wid$choices[wid$item_id == "w_overcap_definitions"])
+    overcap_pro_selected <- names(overcap_pro_names[overcap_pro_names %in% overcap$definitions])
+    
+    overcap_pro <- paste0("<small>",text$item_label[text$item_id == "w_overcap_definitions"], 
+                      "<ul><li>", 
+                      paste0(overcap_pro_selected, collapse = "</li><li>"), 
+                      "</li></ul></small>")
+    
+    overcap_disciplines <- paste0("<small class = 'gray'>", "DISCIPLINES:  ", "</small>",
+                              overcap_pro)
+    
+    ### Scope (at least one definition selected) ---
+    if(overcap$scope == "ALL"){
+      
+      overcap_scope <- paste0("<small class = 'gray'>", "SCOPE:  ", "</small>",
+                          "<small>", "Disciplines apply to all Members & vessels.", "</br></small>")
+      
+    }else if(overcap$scope == "SELECT"){
+      
+      overcap_scope_names <- unlist(wid$choices[wid$item_id == "w_overcap_scope_select"])
+      
+      overcap_scope <- paste0("<small class = 'gray'>", "SCOPE:  ", "</small>",
[…]

### 2020-09-03 app/scripts/PolicySummaryText.R

@@ -1,343 +1,0 @@
-###---------------------------------
-### Overfished reactive policy summary
-### --------------------------------
-
-OASummaryText <- function(oa,
-                          oa_definitions,
-                          country_choices){
-  
-  # OA
-  if(length(oa$definitions) == 0){
-    
-    oa_sum <- "None selected."
-    
-  }else if(length(oa$definitions >= 1)){
-    
-    oa_prohib_names <- names(oa_definitions[oa_definitions %in% oa$definitions])
-    oa_pro <- paste0("Subsidies shall be prohibited to any Member-flagged vessel if the target fish stock... ", paste0(oa_prohib_names, collapse = "; "))
-    
-    # OA - scope
-    if(oa$scope == "SELECT"){
-      
-      oa_country_names <- names(country_choices[country_choices %in% oa$scope_manual])
-      oa_sco <- paste0("Selected disciplines only apply to the following Members: ", paste0(oa_country_names, collapse = ", "))
-      
-    }else if(oa$scope == "HS"){
-      
-      oa_sco <- paste0("Selected disciplines only apply to vessels spending at least ",oa$hs_cutoff, "% of their total fishing effort on the high seas")
-      
-    }else if(oa$scope == "DW"){
-      
-      oa_sco <- "Selected disciplines only apply to Member-flagged vessels fishing in EEZs belonging to other coastal states ('distant-water' vessels)"
-      
-    }else {
-      
-      oa_sco <- "Selected disciplines apply to all Members"
-      
-    }
-    
-    # # OA - S&DT
-    # if(oa$allow_sdt == "Yes"){
-    #   
-    #   oa_sdt_names <- names(sdt_who[sdt_who == oa$sdt_who])
-    #   oa_sdt_what <- names(sdt_what[sdt_what == oa$sdt_what])
-    #   
-    #   oa_sdt <- paste0("S&DT is allowed. The following S&DT applies to ", oa_sdt_names, ": ", oa_sdt_what) 
-    #   
-    # }else if(oa$allow_sdt == "No"){
-    #   
-    #   oa_sdt <- "S&DT is not allowed"
-    #   
-    # }
-    
-    oa_sum <- paste0(oa_pro, ". ", oa_sco, ". ")
-  
-  }
-}
-
-###---------------------------------
-### OCOF reactive policy summary
-### --------------------------------
-  
[…]

### 2020-09-03 app/server.R

@@ -146,7 +146,8 @@ shinyServer(function(input, output, session) {
   })
   
   
-  ### Background happenings: Populate reactive value containers keeping track of model results ------
+  ### Background happenings: Get results for selected proposal -----------------------
+  
   observeEvent(input$ab_run_model_proposal, {
     
     # Require policy selection
@@ -200,8 +201,6 @@ shinyServer(function(input, output, session) {
              "sdt_what_sve" = unlist(str_split(selected_proposal$iuu_sdt_what_sve, ", ")),
              "sdt_time_delay_sve" = selected_proposal$iuu_sdt_time_delay_sve)
     
-      # rv_selected_policy$iuu <- iuu
-      
       # OA
       oa <- 
         list("definitions" = unlist(str_split(selected_proposal$oa_definitions, ", ")),
@@ -226,8 +225,6 @@ shinyServer(function(input, output, session) {
              "sdt_hs_cutoff_sve" = selected_proposal$oa_sdt_hs_cutoff_sve,
              "sdt_time_delay_sve" = selected_proposal$oa_sdt_time_delay_sve)
     
-      # rv_selected_policy$oa <- oa
-      
       # Overcap
       overcap <- 
         list("definitions" = unlist(str_split(selected_proposal$overcap_definitions, ", ")),
@@ -252,8 +249,6 @@ shinyServer(function(input, output, session) {
              "sdt_hs_cutoff_sve" = selected_proposal$overcap_sdt_hs_cutoff_sve,
              "sdt_time_delay_sve" = selected_proposal$overcap_sdt_time_delay_sve)
     
-      # rv_selected_policy$overcap <- overcap
-      
       # Cap/Tier
       cap_tier = 
         list("on_off" = selected_proposal$cap_on_off,
@@ -275,78 +270,72 @@ shinyServer(function(input, output, session) {
            "tier3_cap_fishers" = selected_proposal$tier3_cap_fishers,
            "tier3_cap_percent" = selected_proposal$tier3_cap_percent)
       
-      # rv_selected_policy$cap_tier <- cap_tier
-      
       # Policy summary
       policy_summary <- paste0(
         "<b>", "Name: ", "</b>", selected_proposal$title, "</br>",
         "<b>", "Summary: ", "</b>", selected_proposal$summary, "</br>")
       
+      # Advance progress tracker
       incProgress(0.25)
     
-    ### Find fleets ---
[…]

### 2020-09-03 app/ui_02b_edit_policies_B_iuu.R

@@ -281,7 +281,7 @@ IUU = function(wto_members_and_observers)
          fluidRow(
            
            # Next tab
-           column(2, offset = 10, id = "spaced-div",
+           column(3, offset = 9, id = "spaced-div",
                   
                   tags$button(id = "ab_edit_policies_tabs_iuu_to_oa",
                               class = "btn action-button nav-button-c",

### 2020-09-03 app/ui_02b_edit_policies_C_oa.R

@@ -10,22 +10,17 @@ OA = function(wto_members_and_observers)
   # Column container for tab panel        
   column(12, id = "edit-policies-tab-panel",
                   
-         # # Introductory text about the OA disciplines
-         # column(12, style = "padding: 15px 25px 15px;",
-         #        
-         #        includeHTML("./text/02b_edit_policies_oa_intro.html")
-         #        
-         # ),
+         # Manual IUU discipline selection
+         column(12, id = "spaced-div", 
          
-         # Manual OA discipline selection
-         column(12, id = "spaced-div",
-                
+                ### ------------------------
+                ### Top Row: Disciplines
+                ### ------------------------
                 fluidRow( 
                   
-                  ### ------------------------
-                  ### Left column: Definitions
-                  ### ------------------------
-                  column(5, style = "padding: 0 10px;",
+                  tags$h4("DISCIPLINES: "),
+                  
+                  column(12, style = "padding-right: 10px;",
                          
                          # Input - Select OA discipline(s)
                          checkboxGroupInput("w_oa_definitions", 
@@ -36,29 +31,41 @@ OA = function(wto_members_and_observers)
                                               tags$button(id = "info_oa",
                                                           class = "btn action-button info-button",
                                                           icon("info"))
-                                              ), 
+                                            ), 
                                             choices = unlist(wid$choices[wid$item_id == "w_oa_definitions"]),
                                             selected = unlist(wid$selected[wid$item_id == "w_oa_definitions"]),
                                             width = "100%",
                                             inline = FALSE)
-
-                  ), # /column 5 - Left column 
-                  
-                  ### -------------------------------
-                  ### Middle column: scope/allow S&DT
-                  ### -------------------------------
-                  column(4, style = "padding: 0 10px;",
                          
-                         # Conditional panel - At least one OA discipline(s) selected
-                         conditionalPanel('input.w_oa_definitions.length > 0',
-                                          
+                         
+                  ) # /column 12
+                ), #/fluidRow - top Row
+                
+                ### ------------------------
+                ### Middle Row: Scope
+                ### ------------------------
+                fluidRow(
+                  
+                  # Conditional panel - At least one OA discipline(s) selected
+                  conditionalPanel('input.w_oa_definitions.length > 0',
+                                   
+                                   tags$hr(),
+                                   tags$h4("SCOPE: "),
+                                   
+                                   ### Left column
+                                   column(6, style = "padding-right: 10px;",
[…]

### 2020-09-03 app/scripts/OASummaryText.R
policy things

@@ -54,36 +54,103 @@ OASummaryText <- function(oa,
       oa_scope <- paste0("<small class = 'gray'>", "SCOPE:  ", "</small>",
                           "<small>", "Disciplines only apply to vessels: ", "<ul>")
       
-      # MANUAL: Manual country selection
-      if("MANUAL" %in% oa$scope_select & length(oa$scope_manual) >= 1){
+      if(length(oa$scope_select) >= 1){
         
-        oa_country_names <- names(country_choices[country_choices %in% oa$scope_manual])
-        oa_scope_manual <- paste0("<li>", names(oa_scope_names[oa_scope_names == "MANUAL"]),
-                                   " (", paste0(oa_country_names, collapse = ", "), ")", "</li>")
-      }else{
+        # SUB: Top 10 subsidizers
+        if("SUB" %in% oa$scope_select){
+          oa_scope_sub <- paste0("<li>", names(oa_scope_names[oa_scope_names == "SUB"]), "</li>")
+        }else{
+          oa_scope_sub <- ""
+        }
         
-        oa_scope_manual <- ""
-      }
-      
-      # EX_TER: Outside of territorial waters
-      if("EX_TER" %in% oa$scope_select){
+        # MANUAL: Manual country selection
+        if("MANUAL" %in% oa$scope_select){
+          oa_country_names <- names(country_choices[country_choices %in% oa$scope_manual])
+          oa_scope_manual <- paste0("<li>", names(oa_scope_names[oa_scope_names == "MANUAL"]),
+                                    " (", paste0(oa_country_names, collapse = ", "), ")", "</li>")
+        }else{
+          oa_scope_manual <- ""
+        }
         
-        oa_scope_ex_ter <- paste0("<li>", names(oa_scope_names[oa_scope_names == "EX_TER"]), "</li>")
+        # EX_TER: Outside of territorial waters
+        if("EX_TER" %in% oa$scope_select){
+          oa_scope_ex_ter <- paste0("<li>", names(oa_scope_names[oa_scope_names == "EX_TER"]), "</li>")
+        }else{
+          oa_scope_ex_ter <- ""
+        }
         
-      }else{
+        # HS: Fishing in ABNJ
+        if("HS" %in% oa$scope_select){
+          oa_scope_hs <- paste0("<li>", names(oa_scope_names[oa_scope_names == "HS"]), " (min. of ", oa$hs_cutoff, "% of annual effort)", "</li>")
+        }else{
+          oa_scope_hs <- ""
+        }
         
[…]

### 2020-09-03 app/ui_02b_edit_policies_C_oa.R

@@ -20,7 +20,7 @@ OA = function(wto_members_and_observers)
                   
                   tags$h4("DISCIPLINES: "),
                   
-                  column(12, style = "padding-right: 10px;",
+                  column(12,
                          
                          # Input - Select OA discipline(s)
                          checkboxGroupInput("w_oa_definitions", 
@@ -85,7 +85,7 @@ OA = function(wto_members_and_observers)
                                                                             selectizeInput("w_oa_scope_manual",
                                                                                            label = tags$b(text$item_label[text$item_id == "w_oa_scope_manual"]),
                                                                                            choices = wto_members_and_observers,
-                                                                                           selected = "",
+                                                                                           selected = NULL,
                                                                                            width = "100%",
                                                                                            options = list(placeholder = 'Select...'),
                                                                                            multiple = T)
@@ -114,7 +114,7 @@ OA = function(wto_members_and_observers)
                                                            ), # /conditionalPanel - High seas scope
                                                            
                                                            # Conditional panel - Length cutoff
-                                                           conditionalPanel("input.w_oa_scope_select.includes('LENGTH') || input.w_oa_scope_select_includes('LTE')",
+                                                           conditionalPanel("input.w_oa_scope_select.includes('LENGTH')",
                                                                             
                                                                             # Input: High seas cutoff
                                                                             sliderInput("w_oa_length_cutoff",
@@ -128,7 +128,7 @@ OA = function(wto_members_and_observers)
                                                            ), # /conditionalPanel - Length cutoff
                                                            
                                                            # Conditional panel - tonnage cutoff
-                                                           conditionalPanel("input.w_oa_scope_select.includes('TONNAGE') || input.w_oa_scope_select_includes('LTE')",
+                                                           conditionalPanel("input.w_oa_scope_select.includes('TONNAGE')",
                                                                             
                                                                             # Input: High seas cutoff
                                                                             sliderInput("w_oa_tonnage_cutoff",
@@ -142,7 +142,7 @@ OA = function(wto_members_and_observers)
                                                            ), # /conditionalPanel - tonnage cutoff
                                                            
                                                            # Conditional panel - engine power cutoff
-                                                           conditionalPanel("input.w_oa_scope_select.includes('ENGINE') || input.w_oa_scope_select_includes('LTE')",
+                                                           conditionalPanel("input.w_oa_scope_select.includes('ENGINE')",
[…]

### 2020-09-03 app/ui_02b_edit_policies_D_overcap.R

@@ -9,68 +9,75 @@ Overcap = function(wto_members_and_observers, subsidy_types_sorted_sumaila)
   
   # Column container for tab panel        
   column(12, id = "edit-policies-tab-panel",
-                  
-         # # Introductory text about the Overcapacity disciplines
-         # column(12, style = "padding: 15px 25px 15px;",
-         #        
-         #        includeHTML("./text/02b_edit_policies_overcap_intro.html")
-         #        
-         # ),
          
-         # Manual Overcapacity discipline selection
-         column(12, id = "spaced-div",
+         # Manual IUU discipline selection
+         column(12, id = "spaced-div", 
                 
+                ### ------------------------
+                ### Top Row: Disciplines
+                ### ------------------------
                 fluidRow( 
                   
-                  ### ------------------------
-                  ### Left column: Definitions
-                  ### ------------------------
-                  column(5, style = "padding: 0 10px;",
+                  tags$h4("DISCIPLINES: "),
+                  
+                  column(12,
                          
-                         # Input - Select Overcapacity discipline(s)
+                         # Input - Select OCOF discipline(s)
                          checkboxGroupInput("w_overcap_definitions", 
                                             
                                             label = tagList(
                                               tags$b(text$item_label[text$item_id == "w_overcap_definitions"]),
-                                              # Overcapacity definitions info button
+                                              # OA definitions info button
                                               tags$button(id = "info_overcap",
                                                           class = "btn action-button info-button",
                                                           icon("info"))
-                                              ), 
-                                            choices = subsidy_types_sorted_sumaila[4:10],
-                                            selected = "",
+                                            ), 
+                                            choices = subsidy_types_sorted_sumaila[4:13],
+                                            selected = NULL,
                                             width = "100%",
                                             inline = FALSE)
-
-                  ), # /column 5 - Left column 
-                  
-                  ### -------------------------------
-                  ### Middle column: scope/allow S&DT
-                  ### -------------------------------
-                  column(4, style = "padding: 0 10px;",
                          
-                         # Conditional panel - At least one Overcapacity discipline(s) selected
-                         conditionalPanel('input.w_overcap_definitions.length > 0',
-                                          
+                         
+                  ) # /column 12
+                ), #/fluidRow - top Row
+                
+                ### ------------------------
+                ### Middle Row: Scope
+                ### ------------------------
+                fluidRow(
+                  
+                  # Conditional panel - At least one OCOF discipline(s) selected
[…]

### 2020-09-04 scripts/01_data_wrangling.Rmd
cap fixes

@@
 ```{r}
-# Load data using WDI package'
-# wb_demo_dat <- WDI(country = "all",
-#                    indicator = c("gdp" = "NY.GDP.MKTP.CD",
-#                                  "gdp_ffa" = "NV.AGR.TOTL.CD",
-#                                  "population" = "SP.POP.TOTL"),
-#                                   start = 2000,
-#                                   end = 2018,
-#                                   extra = TRUE) %>%
-#   dplyr::filter(region != "Aggregates") %>%
-#   dplyr::select(iso3 = iso3c,
-#                 year,
-#                 gdp,
-#                 gdp_ffa,
-#                 population) %>%
-#   mutate(iso3 = as.character(iso3)) %>%
-#   arrange(iso3, year) %>%
-#   gather(variable, value, c("gdp", "gdp_ffa", "population")) %>%
-#   dplyr::filter(!is.na(value)) %>%
-#   mutate(units = case_when(variable == "population" ~ "individuals",
-#                            TRUE ~ paste0(year, " US$")),
-#          source = "World Bank WDI database")
-# 
+#Load data using WDI package
+wb_demo_dat <- WDI(country = "all",
+                   indicator = c("gdp" = "NY.GDP.MKTP.CD", # GDP (current US$)
+                                 "gdp_ffa" = "NV.AGR.TOTL.CD", # Added value coming from fisheries, forestry, and agriculture (current US$)
+                                 "population" = "SP.POP.TOTL", # Total population
+                                 "gni_per_capita" = "NY.GNP.PCAP.KD"), # GNI per capita (constant 2010 US$)
+                                  start = 2000,
+                                  end = 2018,
+                                  extra = TRUE) %>%
+  dplyr::filter(region != "Aggregates") %>%
+  dplyr::select(iso3 = iso3c,
+                year,
+                gdp,
+                gdp_ffa,
+                population,
+                gni_per_capita) %>%
+  mutate(iso3 = as.character(iso3)) %>%
+  arrange(iso3, year) %>%
+  gather(variable, value, c("gdp", "gdp_ffa", "population", "gni_per_capita")) %>%
+  dplyr::filter(!is.na(value)) %>%
+  mutate(units = case_when(variable == "population" ~ "individuals",
+                           variable == "gni_per_capita" ~ "constant 2010 US$",
+                           TRUE ~ paste0(year, " US$")),
+         source = "World Bank WDI database")
+
 # # Deal with the EU + territories
-# wb_dat_eu <- wb_demo_dat %>%
-#   dplyr::filter(iso3 %in% c(eu_countries, eu_territories)) %>%
-#   mutate(entity = "EU") %>%
-#   group_by(entity, year, variable, units, source) %>%
-#   summarize(value = sum(value, na.rm = T)) %>%
-#   rename(iso3 = entity) %>%
-#   arrange(iso3, year, variable)
-# 
-# # Test to make sure there isn't data for any other dependencies - will need to add this once I can figure out why the WDI API isn't working
-# wb_dat_overseas_territory <- wb_demo_dat %>%
-#   dplyr::filter(iso3 %in% territories$iso3 & !(iso3 %in% eu_territories))
-# # Deal with the US + territories
-# wb_dat_us <- wb_demo_dat %>%
-#   dplyr::filter(iso3 %in% c(us_territories, "USA")) %>%
-#   mutate(entity = "USA") %>%
-#   group_by(entity, year, variable, units, source) %>%
-#   summarize(value = sum(value, na.rm = T)) %>%
-#   rename(iso3 = entity) %>%
-#   arrange(iso3, year, variable)
-# 
-# # Add back in
-# wb_dat_edit <- wb_demo_dat %>%
-#   dplyr::filter(iso3 != "USA") %>%
-#   bind_rows(wb_dat_eu) %>%
-#   bind_rows(wb_dat_us)
-# 
-# # Export clean
-# write_csv(wb_dat_edit, paste0(data_dir, "world_bank_2020_wdi_tidy.csv"))
-# write_csv(wb_dat_edit, paste0(app_data_dir, "world_bank_2020_wdi_tidy.csv"))
-
-# Load in
-wb_dat_edit <- read_csv(paste0(data_dir, "world_bank_2020_wdi_tidy.csv"))
+wb_dat_eu <- wb_demo_dat %>%
+  dplyr::filter(iso3 %in% c(eu_countries, eu_territories)) %>%
+  mutate(entity = "EU") %>%
+  group_by(entity, year, variable, units, source) %>%
+  summarize(value = sum(value, na.rm = T)) %>%
+  rename(iso3 = entity) %>%
+  arrange(iso3, year, variable)
+
+# Deal with data for other dependencies
+wb_dat_overseas_territories <- wb_demo_dat %>%
+  dplyr::filter(iso3 %in% territories$iso3 | iso3 %in% territories$sovereign_iso3) %>%
+  left_join(territories, by = c("iso3")) %>%
+  mutate(sovereign_iso3 = case_when(is.na(sovereign_iso3) ~ iso3,
+                                    TRUE ~ sovereign_iso3)) %>%
+  mutate(entity = paste0(sovereign_iso3, "-T")) %>%
+  group_by(entity, year, variable, units, source) %>%
+  summarize(value = sum(value, na.rm = T)) %>%
+  rename(iso3 = entity) %>%
+  arrange(iso3, year, variable)
+
+# Add back in
+wb_dat_edit <- wb_demo_dat %>%
+  bind_rows(wb_dat_eu) %>%
+  bind_rows(wb_dat_overseas_territories)
+
+# Export clean
+write_csv(wb_dat_edit, paste0(data_dir, "world_bank_2020_wdi_tidy.csv"))
+write_csv(wb_dat_edit, paste0(app_data_dir, "world_bank_2020_wdi_tidy.csv"))
 ```
@@
 
+# Subsidy lookup 
+subsidy_totals <- sumaila_2019_dat_edit %>%
+  group_by(iso3, year) %>%
+  summarize(good_subs = sum(value[type %in% c("A1", "A2", "A3")], na.rm = T),
+            bad_subs = sum(value[type %in% c("B1", "B2", "B3", "B4", "B5", "B6", "B7")], na.rm = T),
+            ugly_subs = sum(value[type %in% c("C1", "C2", "C3")], na.rm = T)) %>%
+  ungroup() %>%
+  mutate(all_subs = rowSums(select(., one_of(c("good_subs", "bad_subs", "ugly_subs")))),
+         bad_ugly_subs = rowSums(select(., one_of(c("bad_subs", "ugly_subs"))))) %>%
+  gather(variable, value, -c("iso3", "year")) %>%
+  spread(year, value) %>%
+  left_join(country_dependencies %>% dplyr::select(iso3, is_WTO), by = "iso3") %>%
+  mutate(is_WTO = case_when(!is.na(is_WTO) ~ is_WTO,
+                            iso3 %in% unique(paste0(territories$sovereign_iso3, "-T")) ~ TRUE,
+                            iso3 == "EU" ~ TRUE,
+                            TRUE ~ FALSE))
+
+subsidy_lookup <- sumaila_2019_dat_edit %>%
+  dplyr::select(iso3, year, type, value) %>%
+  mutate(variable = paste0(type, "_subs")) %>%
+  dplyr::select(-type) %>%
+  group_by(iso3, year, variable) %>%
+  summarize(value = sum(value, na.rm = T)) %>%
+  spread(year, value) %>%
+  left_join(country_dependencies %>% dplyr::select(iso3, is_WTO), by = "iso3") %>%
+  mutate(is_WTO = case_when(!is.na(is_WTO) ~ is_WTO,
+                            iso3 %in% unique(paste0(territories$sovereign_iso3, "-T")) ~ TRUE,
+                            iso3 == "EU" ~ TRUE,
+                            TRUE ~ FALSE)) %>%
+  bind_rows(subsidy_totals)
+
+# Demographic lookup 
+demographic_lookup <- wb_dat_edit %>%
+  dplyr::select(-units, -source) %>%
+  spread(year, value) %>%
+  left_join(country_dependencies %>% dplyr::select(iso3, is_WTO), by = "iso3") %>%
+  mutate(is_WTO = case_when(!is.na(is_WTO) ~ is_WTO,
+                            iso3 %in% unique(paste0(territories$sovereign_iso3, "-T")) ~ TRUE,
+                            iso3 == "EU" ~ TRUE,
+                            TRUE ~ FALSE))
+
+# Fishers lookup
+fishers_lookup <- fao_fishers_dat_edit %>%
+  dplyr::select(-units, -source) %>%
+  spread(year, value) %>%
+  dplyr::select(-`1995`) %>%
+  left_join(country_dependencies %>% dplyr::select(iso3, is_WTO), by = "iso3") %>%
+  mutate(is_WTO = case_when(!is.na(is_WTO) ~ is_WTO,
+                            iso3 %in% unique(paste0(territories$sovereign_iso3, "-T")) ~ TRUE,
+                            iso3 == "EU" ~ TRUE,
+                            TRUE ~ FALSE))
+
 # Combine 
 cap_tier_lookup <- capture_production_lookup %>%
-  bind_rows(landed_value_lookup)
+  bind_rows(landed_value_lookup) %>%
+  bind_rows(subsidy_lookup) %>%
+  bind_rows(demographic_lookup) %>%
+  bind_rows(fishers_lookup)
 

### 2020-09-04 scripts/07_proposals.Rmd
cap fixes

@@
 ```
+
 ```{r}
-# Combined fishery stats dat
+# Cap/Tier Data
+cap_tier_dat <- read_csv(here::here("app", "data", "USA_cap_tier_tidy.csv")) %>%
+  arrange(iso3)
+
+# Data
+# 1) Subsidy estimates (Sumaila et al. 2019) ---
+subsidy_dat_sumaila_raw <- read_csv("./data/sumaila_et_al_2019_subsidies_tidy.csv") %>%
+  arrange(iso3)
+
+# Organize subsidy types as defined by Sumaila et al. (2019) for consistent plotting throughout
+subsidy_classification_sumaila <- subsidy_dat_sumaila_raw %>%
+  distinct(category, category_name, type, type_name) %>%
+  arrange(type)
+
+subsidy_types_sorted_sumaila <- subsidy_classification_sumaila$type
+names(subsidy_types_sorted_sumaila) <- subsidy_classification_sumaila$type_name
 

### 2020-09-04 app/scripts/CreateFleets.R

@@ -12,13 +12,10 @@ CreateFleets <- function(vessel_list,
                          oa,
                          overcap,
                          cap_tier,
-                         cap_tier_dat,
-                         profile_dat,
                          subsidy_types_all,
                          managed_threshold = 0.66,
-                         wto_members_and_observers,
-                         subsidy_types,
-                         flag_summary_dat){
+                         cap_tier_lookup,
+                         country_lookup){
   
   ### ---------------------------------
   ### SETUP ---------------------------
@@ -27,19 +24,46 @@ CreateFleets <- function(vessel_list,
   ### Since we don't have this as a selectable option - we define domestic vessels are those that spend less than 1% of their time fishing outside of their own EEZ
   domestic_vessel_cutoff <- 0.01
   
-  # Subsidy types removed if an IUU discipline is triggered
-  iuu_subtypes_removed <- c("B1", "B2", "B3", "B4", "B5", "B6", "B7")
-  
-  # Subsidy types removed if an Overfished discipline is triggered
-  oa_subtypes_removed <- c("B1", "B2", "B3", "B4", "B5", "B6", "B7")
-  
-  # SVE countries
-  sves <- c("ATG", "BRB", "BLZ", "BOL", "CUB", "DMA", "DOM", "SLV", "ECU", "FJI", "GRD", "GTM", "HND", "JAM", "MRT", "NIC", "PAN", "PNG", "KNA", "LCA", "VCT", "WSM", "SYC", "LKA", "TON", "TTO", "BHS")
-  
   # All subsidy types
   good_sub_types <- subsidy_types_all[1:3]
   bad_sub_types <- subsidy_types_all[4:10]
   ugly_sub_types <- subsidy_types_all[11:13]
+  
+  removed_sub_types <- c(bad_sub_types, ugly_sub_types)
+  
+  # Subsidy types removed if an IUU discipline is triggered
+  iuu_subtypes_removed <- c(bad_sub_types, ugly_sub_types)
+  
+  # Subsidy types removed if an Overfished discipline is triggered
+  oa_subtypes_removed <- c(bad_sub_types, ugly_sub_types)
+  
+  # WTO members and observers
+  wto_members_and_observers <- country_lookup$iso3[country_lookup$is_WTO & !country_lookup$is_overseas_territory]
+  names(wto_members_and_observers) <- country_lookup$display_name[country_lookup$iso3 %in% wto_members_and_observers] 
[…]

### 2020-09-04 app/server.R

@@ -43,6 +43,10 @@ shinyServer(function(input, output, session) {
     
   )
   
+  # Reactive object that keeps track of what policy we're on ----
+  rv_policy_id <- reactiveValues(id = character())
+  
+  
   # Add most ambitious results to our reactive results data frame
   observeEvent(input$ab_introduction_to_selected_results, {
     
@@ -64,6 +68,9 @@ shinyServer(function(input, output, session) {
     
     # Add to results reactive object
     isolate(rv_results$run <- rbind(rv_results$run, best_result))
+    
+    # Start our policy id tracker
+    rv_policy_id$id <- best_result$id
     
   })
   
@@ -171,7 +178,7 @@ shinyServer(function(input, output, session) {
     }else{
       
       # Create run id 
-      last_run_id <- which(LETTERS == rv_results$run$id[nrow(rv_results$run)])
+      last_run_id <- which(LETTERS == rv_policy_id$id)
       new_run_id <- LETTERS[last_run_id + 1]
       
       # Update selection tracker so new run is selected
@@ -285,12 +292,10 @@ shinyServer(function(input, output, session) {
         oa = oa,
         overcap = overcap,
         cap_tier = cap_tier,
-        cap_tier_dat = cap_tier_dat,
-        profile_dat = combined_fishery_stats_dat,
         managed_threshold = managed_cutoff,
-        wto_members_and_observers = wto_members_and_observers,
         subsidy_types_all = subsidy_types_sorted_sumaila,
-        flag_summary_dat = flag_summary)
+        cap_tier_lookup = cap_tier_lookup_table,
+        country_lookup = country_lookup)
     
       # Create list by region
       fleet_list <- fleet$summary %>%
@@ -352,6 +357,9 @@ shinyServer(function(input, output, session) {
     # Add to results reactive object
     isolate(rv_results$run <- rbind(rv_results$run, new_result))
     
+    # Update reactive policy id tracker
+    rv_policy_id$id <- new_run_id
+    
     # Update progress tracker
     incProgress(0.95)
     
@@ -362,7 +370,7 @@ shinyServer(function(input, output, session) {
   })
   
   ### Reactive text: Get description for selected proposal --------
-  output$selected_policy_description <- renderUI({
+  output$selected_results_selected_policy_description <- renderUI({
     
     # Make sure something is selected
     req(rv_selected_result$id != "0")
[…]

### 2020-09-04 app/ui_02b_selected_results.R

@@ -167,7 +167,7 @@ SelectedResults = function(proposal_choices)
              ### Selected Policy Description ---
              column(12, id = "tb-spaced-div",
                     
-                    uiOutput("selected_policy_description")
+                    uiOutput("selected_results_selected_policy_description")
                     
              )
              

### 2020-09-04 app/ui_02c_edit_policies_C_overcap.R

@@ -359,7 +359,7 @@ Overcap = function(wto_members_and_observers, subsidy_types_sorted_sumaila)
                                     inline = FALSE),
                        
                        # Conditional Panel - Cap is turned on
-                       conditionalPanel("input.w_cap_on_off == 'Yes'",
+                       conditionalPanel("input.w_cap_on_off == 'YES'",
                                         
                                         # Input - subsidy types to include in cap
                                         checkboxGroupInput("w_cap_subsidy_types",
@@ -374,7 +374,7 @@ Overcap = function(wto_members_and_observers, subsidy_types_sorted_sumaila)
                   ),
                 
                   # Conditional Panel - Cap is turned on and at least one subsidy type selected
-                  conditionalPanel("input.w_cap_on_off == 'Yes' && input.w_cap_subsidy_types.length > 0",
+                  conditionalPanel("input.w_cap_on_off == 'YES' && input.w_cap_subsidy_types.length > 0",
                                  
                                  ### Step 1 - Tier structure -------------------
                                  column(12, style = "padding: 5px;",

### 2020-09-04 app/00_initialize_app.R
relative subs

@@ -64,12 +64,6 @@ territories <- country_lookup %>%
   dplyr::filter(is_overseas_territory & is_WTO) %>%
   distinct(iso3, sovereign_iso3)
 
-# # List of all US overseas territories - vessels flagged here should be considered WTO Members
-# us_territories <- country_lookup$iso3[country_lookup$is_overseas_territory & country_lookup$sovereign_iso3 == "USA"]
-# 
-# # List of all Norwegian overseas territories - vessels flagged here should be considered WTO Members
-# norwegian_territories <- country_lookup$iso3[country_lookup$is_overseas_territory & country_lookup$sovereign_iso3 == "NOR"]
-
 # ### --------------------
 # ### Shapefiles ---------
 # ### --------------------
@@ -210,25 +204,32 @@ landed_value_dat_tot <- landed_value_dat %>%
   ungroup()
   
 # 3) GFW Vessel list (2018)
-#pro_rate_subsidies <- F
 
 vessel_dat <- read.csv("./data/vessel_list_2018_final.csv", stringsAsFactors = F) %>%
   left_join(country_lookup %>% dplyr::select(iso3, is_WTO), by = c("flag_iso3" = "iso3"))
 
-# if(pro_rate_subsidies == T){
-# 
-#   vessel_dat <- vessel_dat %>%
-#     mutate(B1_subs = B1_subs * 0.54, # boat construction/renovation - matched to payments based on vessels
-#            B2_subs = B2_subs * 1, # fishery development projects/support services - matched to payments based on variable use
-#            B3_subs = B3_subs * 0.87, # port construction and renovation - matched to payments based on vessels
-#            B4_subs = B4_subs * 0.87, # price/marketing support, processing infrastructure - matched to payments based on output
-#            B5_subs = B5_subs * 0.76, # non-fuel tax exemptions - matched to payments based on fishers income
-#            B6_subs = B6_subs * 0.56, # foreign access agreements - matched to payments based on fishers own capital
-#            B7_subs = B7_subs * 0.84, # fuel - matched to payments based on fuel use
-#            bad_subs = (B1_subs + B2_subs + B3_subs + B4_subs + B5_subs + B6_subs + B7_subs))
-# 
[…]

### 2020-09-04 app/scripts/CreateFleets.R

@@ -1710,7 +1710,6 @@ overcap_vessels_out <- overcap_vessels_scope %>%
     
     ### Calculate remainders, apply to vessel list and be done --------
       
-    browser()  
     # After caps are set, calculate remaining subs, accounting for already removed subs
      flag_remainders <- flag_caps_out %>%
        arrange(flag_iso3, type) %>%

### 2020-09-04 app/server.R

@@ -44,7 +44,7 @@ shinyServer(function(input, output, session) {
   )
   
   # Reactive object that keeps track of what policy we're on ----
-  rv_policy_id <- reactiveValues(id = character())
+  rv_policy_id <- reactiveValues(id = "A")
   
   
   # Add most ambitious results to our reactive results data frame
@@ -804,6 +804,7 @@ shinyServer(function(input, output, session) {
                      return = "all")
       
 
+      browser()
       # Store time series results both globally and regionally
       out_all <- out %>%
         dplyr::filter(Year > 2018) %>%

### 2020-09-04 scripts/07_proposals.Rmd
proposal results together working

--- 2020-09-03 scripts/07_proposals.Rmd
@@
 # Directories for the output files generated by this script
-results_dir <- here::here("results", "07-sensitivity-analysis/")
+results_dir <- here::here("results", "07-proposals/")
 if (dir.exists(results_dir) == F) {
@@
 }
+
+bad_subsidy_types <- c("B1", "B2", "B3", "B4", "B5", "B6", "B7")
+ugly_subsidy_types <- c("C1", "C2", "C3")
+good_subsidy_types <- c("A1", "A2", "A3")
+
+subsidy_types_sorted_sumaila <- c(good_subsidy_types, bad_subsidy_types, ugly_subsidy_types)
 ```
@@
 
+# Source create fleets script
+source(here::here("app", "scripts", "CreateFleets.R"))
+
 # Source plotting script
@@
 ```{r}
+# Load country dependencies helper file
+country_dependencies <- read_csv(here::here("app", "data", "country_dependencies.csv")) %>%
+   mutate(display_name = case_when(!is.na(WTO_name) ~ WTO_name,
+                                  iso3 == "ANT" ~ "Netherlands Antilles",
+                                  iso3 == "ASC" ~ "Ascension Island", 
+                                  iso3 == "CPT" ~ "Clipperton Island",
+                                  iso3 == "TAA" ~ "Tristan da Cunha",
+                                  TRUE ~ countrycode(iso3, "iso3c", "country.name"))) %>%
+  arrange(sovereign_iso3)
+
+# Vector of all WTO Members and Observers for use in the app [does not include the overseas territories associated with them]
+wto_members_and_observers <- country_dependencies$iso3[country_dependencies$is_WTO & !country_dependencies$is_overseas_territory]
+```
+
+```{r}
 # Load vessel list
-vessel_dat <- read.csv(here::here("app", "data", "vessel_list_2018_final.csv"), stringsAsFactors = F)
+vessel_dat <- read.csv(here::here("app", "data", "vessel_list_2018_final.csv"), stringsAsFactors = F) %>%
+  left_join(country_dependencies %>% dplyr::select(iso3, is_WTO), by = c("flag_iso3" = "iso3"))
+
+rel <- read_csv(here::here("data", "lookup-tables", "oecd_relative_effects_lookup_table.csv"))
+
+vessel_dat <- vessel_dat %>%
+   mutate(B1_subs = B1_subs * rel$rel_effect_effort[rel$type == "B1"], 
+           B2_subs = B2_subs * rel$rel_effect_effort[rel$type == "B2"],
+           B3_subs = B3_subs * rel$rel_effect_effort[rel$type == "B3"],
+           B4_subs = B4_subs * rel$rel_effect_effort[rel$type == "B4"],
+           B5_subs = B5_subs * rel$rel_effect_effort[rel$type == "B5"], 
+           B6_subs = B6_subs * rel$rel_effect_effort[rel$type == "B6"],
+           B7_subs = B7_subs * rel$rel_effect_effort[rel$type == "B7"], 
+           C1_subs = C1_subs * rel$rel_effect_effort[rel$type == "C1"], 
+           C2_subs = C2_subs * rel$rel_effect_effort[rel$type == "C2"],
+           C3_subs = C3_subs * rel$rel_effect_effort[rel$type == "C3"]) %>%
+  ungroup() %>%
+  mutate(bad_subs = rowSums(select(., one_of(paste0(bad_subsidy_types, "_subs")))),
+         ugly_subs = rowSums(select(., one_of(paste0(ugly_subsidy_types, "_subs")))),
+         good_subs = rowSums(select(., one_of(paste0(good_subsidy_types, "_subs")))),
+         bad_ugly_subs = rowSums(select(., one_of(paste0(c(bad_subsidy_types, ugly_subsidy_types), "_subs")))))
 
@@
                                  TRUE ~ as.character(eez_id)))
-
-# Load country dependencies helper file
-country_dependencies <- read_csv(here::here("data", "lookup-tables", "country_dependencies.csv"))
-
-# Vector of all WTO Members and Observers for use in the app [does not include the overseas territories associated with them]
-wto_members_and_observers <- country_dependencies$iso3[country_dependencies$is_WTO & !country_dependencies$is_overseas_territory]
 ```
@@
 ```
+
 ```{r}
-# Combined fishery stats dat
+# 1) Cap/tier lookup table
+cap_tier_lookup_table <- read_csv(here::here("app","data","cap_tier_lookup_table.csv"))
 
@@
 proposal_results <- NULL
-i <- 1
-for(i in 1:length(proposal_choices)){
+i <- 2
+for(i in 2:length(proposal_choices)){
 
   # Choose proposal
-  proposal <- proposal_choices[i]
+  proposal_name <- proposal_choices[i]
 
   # Get all data for that proposal
-  selected_proposal <- included_proposals %>%
-      dplyr::filter(proposal == proposal)
+  selected_proposal <- proposal_settings %>%
+      dplyr::filter(proposal == proposal_name)
 
@@
       cap_tier = cap_tier,
-      cap_tier_dat = cap_tier_dat,
-      profile_dat = combined_fishery_stats_dat,
       managed_threshold = managed_cutoff,
-      wto_members_and_observers = wto_members_and_observers,
       subsidy_types_all = subsidy_types_sorted_sumaila,
-      flag_summary_dat = flag_summary)
+      cap_tier_lookup = cap_tier_lookup,
+      country_lookup = country_dependencies)
 
@@
       group_split()
-    names(fleet_list) <- colnames(bio_dat)[-c(1:2)]
+    names(fleet_list) <- colnames(bio_dat_regional)[-c(1:2)]
+
+    # Run model
+    results <- pmap_df(list(fleet = fleet_list,
+                                   region = names(fleet_list),
+                                   bio_param = bio_dat_regional_list),
+                                  BioEconModel,
+                                  end_year = 2100,
+                                  return = "all")
+
+    # Extract results timeseries
+    results_all <- results %>%
+      dplyr::filter(Year > 2018) %>%
+      group_by(Year, Variable, Fleet) %>%
+      mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU) / abs(BAU),
+      TRUE ~ 0)) %>%
+      ungroup() %>%
+      mutate(run_id = proposal_name,
+             run_name = names(proposal_name))
+
+      write_csv(results_all, paste0(results_dir, "results_", str_replace_all(proposal_name, "/", "_"), ".csv"))
+
+    # Add to data frame
+      proposal_results <- proposal_results %>%
+        bind_rows(results_all)
 

### 2020-09-04 app/00_initialize_app.R

@@ -335,6 +335,7 @@ remove_all_bad_results_full <- remove_all_bad_results %>%
                           TRUE ~ 0),
          BAU_global = sum(BAU, na.rm = T),
          Reform_global = sum(Reform, na.rm = T),
+         Diff_value_global = (Reform_global - BAU_global),
          Diff_global = case_when(BAU_global != 0 ~ (Reform_global - BAU_global)/abs(BAU_global),
                                  TRUE ~ 0)) %>%
   ungroup() %>%
@@ -347,9 +348,19 @@ remove_all_bad_results_full <- remove_all_bad_results %>%
 remove_all_bad_results_last <- remove_all_bad_results_full %>%
   dplyr::filter(Year == end_year) %>%
   group_by(Year, Variable, Id, Name, Type, Description) %>%
-  summarize(Value = unique(Diff_global)*100) %>%
-  ungroup() %>%
-  spread(Variable, Value) %>%
+  summarize(Percent = unique(Diff_global)*100,
+            Value = unique(Diff_value_global)) %>%
+  ungroup() 
+
+
+biomass_end_percent <- round(remove_all_bad_results_last$Percent[remove_all_bad_results_last$Variable == "biomass"])
+biomass_end_value <- round(remove_all_bad_results_last$Value[remove_all_bad_results_last$Variable == "biomass"]/1e6)
+catch_end_percent <- round(remove_all_bad_results_last$Percent[remove_all_bad_results_last$Variable == "catches_total"])
+catch_end_value <- round(remove_all_bad_results_last$Value[remove_all_bad_results_last$Variable == "catches_total"]/1e6)
+
+
+remove_all_bad_results_last <- remove_all_bad_results_last%>%
+  spread(Variable, Percent) %>%
   rename(Biomass = biomass,
          Catches = catches_total,
          Revenue = revenue_total)

### 2020-09-04 app/ui_01_introduction.R

@@ -44,10 +44,10 @@ Introduction = function()
                                                 
                                                 tags$td(id = "introduction-table-cell-r",
                                                         
-                                                        tags$h4("An ambitious agreement on fisheries subsidies reform could result in increases of up to:"),
-                                                        tags$h3("+ 14% in global fish biomass"),
-                                                        tags$h3("+ 5% in global fish catch"),
-                                                        tags$p("More fish in the water and more catch opportunities")
+                                                        tags$h4("An ambitious agreement on fisheries subsidies reform could result in increases of up to"),
+                                                        tags$h3(paste0("+ ", biomass_end_percent, "% in global fish biomass")),
+                                                        tags$h3(paste0("+ ", catch_end_percent, "% in global fish catch")),
+                                                        tags$h4(paste0("Resulting in ", biomass_end_value, " million more tons of fish in the water, and ", catch_end_value, " million more tons of fish being caught."))
                                                 )
                                         )
                              )

### 2020-09-05 scripts/07_proposals.Rmd
individual proposal results

@@
 proposal_results <- NULL
-i <- 2
+
 for(i in 2:length(proposal_choices)){
@@
   proposal_name <- proposal_choices[i]
+
+  print(proposal_name)
 
@@
       subsidy_types_all = subsidy_types_sorted_sumaila,
-      cap_tier_lookup = cap_tier_lookup,
+      cap_tier_lookup = cap_tier_lookup_table,
       country_lookup = country_dependencies)
@@
       mutate(run_id = proposal_name,
-             run_name = names(proposal_name))
+             run_name = names(proposal_name),
+             run_group = unique(proposal_settings$category[proposal_settings$proposal == proposal_name]))
 
@@
 ```
+
+```{r}
+most_ambitious_results <- read_csv(paste0(here::here("results", "06-run-model/"), "rel_subs_all_B_ts.csv")) %>%
+  mutate(run_group = "Ambitious Reform")
+
+most_ambitious_results_global <- most_ambitious_results %>%
+  group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
+    summarize(BAU_tot = sum(BAU, na.rm = T),
+              Reform_tot = sum(Reform, na.rm = T),
+              Diff_tot = case_when(BAU_tot != 0 ~ (Reform_tot - BAU_tot)/abs(BAU_tot),
+                            TRUE ~ 0)) %>%
+    ungroup() %>%
+    mutate(Region = "Global") %>%
+    mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
+                                Variable == "catches_total" ~ "Catches",
+                                Variable == "revenue_total" ~ "Revenue")) %>%
+  dplyr::filter(Fleet == "Total") %>%
+  dplyr::filter(Variable %in% c("Biomass", "Catches", "Revenue"))
+
+plot_results <- proposal_results %>%
+  dplyr::filter(run_id != "RD/TN/RL/103") %>%
+  bind_rows(most_ambitious_results)
+
+# Make plots
+if(make_plots){
+
+  # 1) global (aggregated) timeseries plot
+  compare_ts_plot <- BioEconomicModelPlots(dat = plot_results,
+                                           spatial_res = "global",
+                                           temporal_res = "all",
+                                           start_year = 2018,
+                                           end_year = 2100,
+                                           plot_name = "all_proposals_ts_plot",
+                                           plot_width = 8,
+                                           plot_height = 6.5,
+                                           results_dir = results_dir,
+                                           compare = TRUE)
+
+  # 2) global (aggregated) "kobe" final year plot
+  compare_end_plot <- BioEconomicModelPlots(dat = plot_results,
+                                            spatial_res = "global",
+                                            temporal_res = "last",
+                                            end_year = 2100,
+                                            plot_name = "all_proposals_end_plot",
+                                            plot_width = 8,
+                                            plot_height = 6.5,
+                                            results_dir = results_dir,
+                                            compare = TRUE)
+
+  # 3) regional timeseries plot
+  regional_compare_ts_plot <- BioEconomicModelPlots(dat = plot_results,
+                                                    spatial_res = "regional",
+                                                    temporal_res = "all",
+                                                    start_year = 2018,
+                                                    end_year = 2100,
+                                                    plot_name = "regional_all_proposals_ts_plot",
+                                                    plot_width = 8,
+                                                    plot_height = 6.5,
+                                                    results_dir = results_dir,
+                                                    compare = TRUE)
+
+  # 4) regional "kobe" final year plot
+  regional_compare_end_plot <- BioEconomicModelPlots(dat = plot_results,
+                                                     spatial_res = "regional",
+                                                     temporal_res = "last",
+                                                     end_year = 2100,
+                                                     plot_name = "regional_all_proposals_end_plot",
+                                                     plot_width = 8,
+                                                     plot_height = 6.5,
+                                                     results_dir = results_dir,
+                                                     compare = TRUE)
+}
+```

### 2020-09-05 app/scripts/CreateFleets.R

@@ -1222,6 +1222,7 @@ overcap_vessels_out <- overcap_vessels_scope %>%
   
   if(cap_tier$on_off == "YES"){
   
+  browser()
   # Subsidy types to include in cap. 
   # Other bad subsidies could have either been completely prohibited in the overcapacity section, or are allowed.
   # We need to figure that out in this section

### 2020-09-05 scripts/functions/BioEconomicModelPlots.R

@@ -25,7 +25,7 @@ BioEconomicModelPlots <- function(dat,
   plot_dat <- dat %>%
     dplyr::filter(Variable %in% variables_keep) %>%
     dplyr::filter(Fleet %in% fleets_keep) %>%
-    group_by(Year, Variable, Fleet, run_id, run_name) %>%
+    group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
     summarize(BAU_tot = sum(BAU, na.rm = T),
               Reform_tot = sum(Reform, na.rm = T),
               Diff_tot = case_when(BAU_tot != 0 ~ (Reform_tot - BAU_tot)/abs(BAU_tot),
@@ -41,7 +41,7 @@ BioEconomicModelPlots <- function(dat,
     plot_dat <- dat %>%
       dplyr::filter(Variable %in% variables_keep) %>%
       dplyr::filter(Fleet %in% fleets_keep) %>%
-      group_by(Year, Variable, Fleet, Region, run_id, run_name) %>%
+      group_by(Year, Variable, Fleet, Region, run_id, run_name, run_group) %>%
       mutate(BAU_tot = sum(BAU, na.rm = T),
              Reform_tot = sum(Reform, na.rm = T),
              Diff_tot = case_when(BAU_tot != 0 ~ (Reform_tot - BAU_tot)/abs(BAU_tot),
@@ -119,7 +119,7 @@ BioEconomicModelPlots <- function(dat,
       plot <- plot_dat %>%
         dplyr::filter(Year >= start_year & Year <= end_year) %>%
         ggplot()+
-        aes(x = Year, y = Diff_tot*100, color = run_name, linetype = run_id)+
+        aes(x = Year, y = Diff_tot*100, color = run_group, linetype = run_group, group = run_id)+
         geom_line(size = 1, alpha = 0.6)+
         geom_hline(yintercept = 0)+
         scale_x_continuous(expand = c(0,0))+
@@ -132,21 +132,21 @@ BioEconomicModelPlots <- function(dat,
       
       plot_dat <- plot_dat %>%
         dplyr::filter(Year == end_year) %>%
-        group_by(Year, Variable, Fleet, Region, run_id, run_name) %>%
+        group_by(Year, Variable, Fleet, Region, run_id, run_name, run_group) %>%
         summarize(Value = unique(Diff_tot)) %>%
         ungroup() %>%
         spread(Variable, Value)
       
[…]

### 2020-09-11 app/ui_01_introduction.R
adding video

@@ -22,7 +22,11 @@ Introduction = function()
              # Child element 1: background image
              tags$div(class = "picture-wrapper",
                       
-                      tags$img(src = "intro-background.jpg")
+                      # tags$iframe(src = "https://www.youtube.com/embed/xYl4m0xFcCU?controls=0&amp;start=2",
+                      #             frameborder="0", 
+                      #             allow="autoplay; encrypted-media; gyroscope; picture-in-picture", allowfullscreen=NA)
+                      
+                      #tags$img(src = "intro-background.jpg")
              ),
                       
              # Child element 2: overlay

### 2020-09-11 scripts/04_model_parameterization.Rmd

@@
 
-We assume $\phi = 1.188$ based on literature for all (Thorson et al. 2012; World Bank 2017; Costello et al. 2016).
+We assume $\phi = 0.188$ based on literature for all (Thorson et al. 2012; World Bank 2017; Costello et al. 2016).
+
+> Thorson, J.
+T., Cope, J.
+M., Branch, T.
+A., & Jensen, O.
+P.
+(2012).
+Spawning biomass reference points for exploited marine fishes, incorporating taxonomic and body size information.
+Canadian Journal of Fisheries and Aquatic Sciences, 69(9), 1556–1568.
+https://doi.org/10.1139/f2012-077
 

### 2020-09-11 scripts/07_sensitivity_analysis.Rmd

@@
 
-title: "SubsidyExplorer - Step 7: Sensitivity Analysis"
+title: "SubsidyExplorer - Step 6: Run Model"
 author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
@@
 ---
+
+# Introduction
+
+This script generates the most ambitious global and regional results obtained by removing all capacity enhancing subsidies from all WTO Members and Observers.
 
@@
 ```{r}
+# Source model script
+source(here::here("app", "scripts", "BioEconModel.R"))
+
+# Source plotting script
+source(here::here("scripts", "functions", "BioEconomicModelPlots.R"))
+```
+
+```{r}
 # Load vessel list
@@
 
-## Relative subsidy effects
+```{r}
+# Load biological parameters for the model
+bio_dat_regional <- read.csv(here::here("app", "data", "model_parameters_regional_3_regions.csv"))
+
+# Regional parameter list
+bio_dat_regional_list <- bio_dat_regional %>%
+  gather(region, value, -c(1:2)) %>%
+  group_by(region) %>%
+  group_split()
+```
 
 ```{r}
-# Vessel list with "effective" subsidies
-### Not applicable currently - old experimentation with pro-rating the dollar value of different subsidies
-# if(pro_rate_subsidies == T){
-# 
-#   vessel_dat <- vessel_dat %>%
-#     mutate(B1_subs = B1_subs * 0.54, # boat construction/renovation - matched to payments based on vessels
-#            B2_subs = B2_subs * 1, # fishery development projects/support services - matched to payments based on variable use
-#            B3_subs = B3_subs * 0.87, # port construction and renovation - matched to payments based on vessels
-#            B4_subs = B4_subs * 0.87, # price/marketing support, processing infrastructure - matched to payments based on output
-#            B5_subs = B5_subs * 0.76, # non-fuel tax exemptions - matched to payments based on fishers income
-#            B6_subs = B6_subs * 0.56, # foreign access agreements - matched to payments based on fishers own capital
-#            B7_subs = B7_subs * 0.84, # fuel - matched to payments based on fuel use
-#            bad_subs = (B1_subs + B2_subs + B3_subs + B4_subs + B5_subs + B6_subs + B7_subs))
-# 
-# }
+# Threshold to be considered managed (using FMI scores)
+managed_cutoff <- 0.66
 ```
 
-## Bioeconomic model parameters
+## Alternative model parameters

### 2020-09-15 app/scripts/CreateFleets.R
policy navigation buttons

@@ -1222,6 +1222,7 @@ overcap_vessels_out <- overcap_vessels_scope %>%
   
   if(cap_tier$on_off == "YES"){
   
+    browser()
   # Subsidy types to include in cap. 
   # Other bad subsidies could have either been completely prohibited in the overcapacity section, or are allowed.
   # We need to figure that out in this section

### 2020-09-15 app/server.R

@@ -159,19 +159,28 @@ shinyServer(function(input, output, session) {
   })
   
   ### -------------------------
-  ### 02a. selected-results ---
+  ### 02a. explore-results ---
   ### -------------------------
   
   ### Navigation buttons ---------------------
   
-  # Navigation button from selected-results to edit-policies
-  observeEvent(input$ab_selected_results_to_edit_policies, {
+  # Navigation button from explore-results to selected-results
+  observeEvent(input$ab_explore_proposals, {
+    updateTabItems(session, "menu_items", "selected-results")
+  })
+  
+  # Navigation button from explore-results to edit-policies
+  observeEvent(input$ab_explore_results_design_custom_proposal, {
     updateTabItems(session, "menu_items", "edit-policies")
   })
   
-  # Navigation button from selected-results to introduction
-  observeEvent(input$ab_selected_results_to_introduction, {
-    updateTabItems(session, "menu_items", "introduction")
+  ### -------------------------
+  ### 02b. selected-results ---
+  ### -------------------------
+  
+  # Navigation button from selected-results to edit-policies
+  observeEvent(input$ab_selected_results_design_custom_proposal, {
+    updateTabItems(session, "menu_items", "edit-policies")
   })
   
   

### 2020-09-15 app/ui_02a_explore_results.R

@@ -92,9 +92,9 @@ ExploreResults = function(proposal_choices)
                     column(12, id = "tb-spaced-div",
                            
                            # Button
-                           tags$button(id = "ab_design_custom_proposal",
+                           tags$button(id = "ab_explore_results_design_custom_proposal",
                                        class = "btn action-button rounded-button",
-                                       tags$b(text$item_label[text$item_id == "ab_design_custom_proposal"], icon("caret-right")))
+                                       tags$b(text$item_label[text$item_id == "ab_explore_results_design_custom_proposal"], icon("caret-right")))
                     
                     )
              )

### 2020-09-15 app/ui_02b_selected_results.R

@@ -79,14 +79,28 @@ SelectedResults = function(proposal_choices)
                     
                     ),
              
-                    ### Section 2 ---
-                    column(12, align = "center", id = "tb-spaced-div",
+                    ### Third section - Design custom proposal ---
+                    column(12, id = "section-title",
+                           
+                           # Section Title
+                           tags$h5(text$item_label[text$item_id == "design-custom-proposal"])
+                           
+                    ),
                     
-                           # IUU definitions info button
-                           tags$button(id = "ab_selected_results_to_edit_policies",
+                    column(12,
+                           
+                           includeHTML("./text/02-results/explore-results/left_panel_design_proposal.html")
+                           
+                           
+                    ),
+                    
+                    column(12, id = "tb-spaced-div",
+                           
+                           # Button
+                           tags$button(id = "ab_selected_results_design_custom_proposal",
                                        class = "btn action-button rounded-button",
-                                       tags$b("Text"))
-                    
+                                       tags$b(text$item_label[text$item_id == "ab_selected_results_design_custom_proposal"], icon("caret-right")))
+                           
                     )
              )
                   

### 2020-09-15 scripts/05_subsidy_reform_definitions.Rmd
fixing normalize shipname

@@
 #devtools::install_github("jcvdav/startR")
-library(startR)
+#library(startR)
+# This used to live in the startR package, but now lives locally - the package developer is currently having some difficulties related to the update to R version 4.0
+source(here::here("scripts", "functions", "normalize.R"))
+devtools::install_github("rich-iannone/UnidecodeR")
+library(UnidecodeR)
 
@@
   mutate(distant_water = T) %>%
-  dplyr::select(eez_id, ssvid, fao_region, distant_water)
+  dplyr::select(eez_id, ssvid, fao_region, is_territorial, distant_water)
 ```
@@
 temp_vessel_list <- temp_vessel_list %>%
-  left_join(distant_water_fishing, by = c("eez_id", "ssvid", "fao_region"))
+  left_join(distant_water_fishing, by = c("eez_id", "ssvid", "fao_region", "is_territorial"))
 temp_vessel_list$distant_water[is.na(temp_vessel_list$distant_water)] <- F
-
 ```

### 2020-09-15 app/scripts/CreateFleets.R

@@ -21,7 +21,7 @@ CreateFleets <- function(vessel_list,
   ### SETUP ---------------------------
   ### ---------------------------------
   
-  ### Since we don't have this as a selectable option - we define domestic vessels are those that spend less than 1% of their time fishing outside of their own EEZ
+  ### Since we don't have this as a selectable option - domestic vessels are defined as those that spend less than 1% of their time fishing outside of their own EEZ
   domestic_vessel_cutoff <- 0.01
   
   # All subsidy types
@@ -73,8 +73,11 @@ CreateFleets <- function(vessel_list,
 
   ### Remove vessels with no bad subsidies or that do not below to a WTO Member or Observer state (they can't be affected) 
   vessel_subset <- vessel_list %>%
-    dplyr::filter((bad_subs > 0 | ugly_subs > 0) & is_WTO)
+    dplyr::filter((bad_subs > 0 | ugly_subs > 0) & is_WTO) %>%
+    mutate(id = case_when(is_territorial ~ paste0(ssvid, "_", region, "_", fao_region, "_", eez_hs_code, "_", flag_iso3, "_", "territorial"),
+                          !is_territorial ~ paste0(ssvid, "_", region, "_", fao_region, "_", eez_hs_code, "_", flag_iso3, "_", "non-territorial")))
   
+  browser()
   ### Create empty container to track existing/removed subsidies by subtype by affected vessel and region
   vessel_tracking_df <- tibble(ssvid = numeric(0),
                                region = character(0),

### 2020-09-15 scripts/functions/normalize.R

@@ -1,0 +1,211 @@
+#' Normalize shipname and callsign
+#'
+#' @description Performs a series of string normalizations to get a clean shipname or callsign.
+#' This was inspired by Jaeyoon Park's Python Module: \url{https://github.com/jaeyoonpark/shipdataprocess}.
+#'
+#' \code{normalize_shipname} will do the following:
+#' \itemize{
+#'   \item Make all letters into capital letters
+#'   \item Remove leading and trailing whitespaces
+#'   \item Remove linebreaks
+#'   \item Remove all references to vessel codes (\emph{i.e.} \code{MFV} stands for Marine Fishing Vessel)
+#'   \item Convert numbers expressed as letters to numbers (\emph{i.e.} \code{ONE} becomes \code{1})
+#'   \item Convert roman numerals to arabic numbers
+#'   \item Remove \code{NO.} when it references a number (\emph{i.e.} \code{BOAT NO.5} becomes \code{BOAT5})
+#'   \item Remove all special characters
+#' }
+#'
+#' \code{normalize_callsign} will:
+#' \itemize{
+#'   \item Make all letters into capital letters
+#'   \item Remove leading and trailing whitespaces
+#'   \item Remove linebreaks
+#'   \item Remove leading zeroes (\emph{i.e.} \code{007JAMESBOND} becomes \code{7JAMESBOND})
+#'   \item Remove all special characters
+#' }
+#'
+#' @param name A character string (or vector of strings) to be normalized
+#' @param callsign A character string (or vector of strings) to be normalized
+#' @param ... Any other arguments
+#'
+#' @return A normmalized shipname or callsign
+#'
+#' @importFrom UnidecodeR unidecode get_transliterations
+#' @importFrom stringr str_squish str_trim str_remove str_remove_all str_replace str_detect str_split str_extract
+#' @importFrom magrittr %>%
+#' @importFrom utils as.roman browseURL
+#'
+#' @aliases normalize_shipname normalize_callsign
+#' @examples
[…]

### 2020-09-15 app/ui_02c_edit_policies_C_overcap.R
adding new sliders for "best" cap option

@@ -376,105 +376,94 @@ Overcap = function(wto_members_and_observers, subsidy_types_sorted_sumaila)
                   # Conditional Panel - Cap is turned on and at least one subsidy type selected
                   conditionalPanel("input.w_cap_on_off == 'YES' && input.w_cap_subsidy_types.length > 0",
                                  
-                                 ### Step 1 - Tier structure -------------------
-                                 column(12, style = "padding: 5px;",
-                                                         
-                                        h4(class = "header-line-light", text$item_label[text$item_id == "tier-structure"]),
-                                        
-                                        # Row 1 - Number of tiers
-                                        fluidRow(
+                                   ### Step 1: Tier structure ------------------
+                                   column(12, id = "section-title-div-underline",
                                           
-                                          column(12, style = "padding: 0 10px;",
-                                                                  
-                                                 radioButtons("w_cap_tier_number",
-                                                              label = tags$b(text$item_label[text$item_id == "w_cap_tier_number"]),
-                                                              choices = unlist(wid$choices[wid$item_id == "w_cap_tier_number"]),
-                                                              selected = unlist(wid$selected[wid$item_id == "w_cap_tier_number"]),
-                                                              width = "100%",
-                                                              inline = FALSE)
-                                                 
-                                          ) # /column 12
-                                        ), # /row 1
-                                                         
-                                        # Row 2 - How should Members be sorted into tiers?
-                                        fluidRow(
+                                          # Section Title
+                                          tags$h5(text$item_label[text$item_id == "tier-structure"])
+                                          
+                                   ),
+                                   
+                                   # Number of tiers
+                                   column(12, id = "tb-spaced-div",
+                                          
+                                          radioButtons("w_cap_tier_number",
+                                                       label = tags$b(text$item_label[text$item_id == "w_cap_tier_number"]),
+                                                       choices = unlist(wid$choices[wid$item_id == "w_cap_tier_number"]),
+                                                       selected = unlist(wid$selected[wid$item_id == "w_cap_tier_number"]),
+                                                       width = "100%",
+                                                       inline = FALSE)
+                                          
+                                   ), # /column 12
+                                   
+                                   conditionalPanel('input.w_cap_tier_number != "ONE"',
+                                                    
+                                                    column(12, id = "div-topline",
                                                            
-                                          # Left Column
-                                          column(6, style = "padding: 0 10px;",
-                                                                  
-                                                 # Conditional Panel - Only one tier
-                                                 conditionalPanel('input.w_cap_tier_number == "ONE"',
[…]

### 2020-09-16 scripts/06_run_model.Rmd
updating static figures

--- 2020-09-02 scripts/06_run_model.Rmd
@@
 
+# End year for simulations
+end_year <- 2080
+
+# Threshold to be considered managed (using FMI scores)
+managed_cutoff <- 0.75
+
 # Directories for the output files generated by this script
-results_dir <- here::here("results", "06-run-model/")
+results_dir <- paste0(here::here("results", "06-run-model/"), "mgmt_threshold_", managed_cutoff, "/")
 if (dir.exists(results_dir) == F) {
@@
 
-```{r}
-# Threshold to be considered managed (using FMI scores)
-managed_cutoff <- 0.66
-```
-
-## Create global fleet
-
 ```{r pressure, echo=FALSE}
 # Assign fleets to vessels
-global_fleet_vessels <- vessel_dat %>%
+fleet_vessels <- vessel_dat %>%
   left_join(country_dependencies %>% dplyr::select(iso3, is_WTO), by = c("flag_iso3" = "iso3")) %>%
@@
 # Turn into a list
-global_all_bad_list <- global_all_bad_summary %>%
+abs_all_BC_list <- abs_all_BC_fleet_summary %>%
   group_by(region) %>%
   group_split()
-names(global_all_bad_list) <- colnames(bio_dat_regional)[-c(1:2)]
+names(abs_all_BC_list) <- colnames(bio_dat_regional)[-c(1:2)]
 
 # Run model
-global_all_bad_results <- pmap_df(list(fleet = global_all_bad_list, 
-                                       region = names(global_all_bad_list),
+abs_all_BC_results <- pmap_df(list(fleet = abs_all_BC_list, 
+                                       region = names(abs_all_BC_list),
                                        bio_param = bio_dat_regional_list),
                                   BioEconModel,
-                                  end_year = 2100,
+                                  end_year = end_year,
                                   return = "all")
@@
 # Extract results timeseries
-global_all_bad_results_full <- global_all_bad_results %>%
+abs_all_BC_results_all <- abs_all_BC_results %>%
   dplyr::filter(Year > 2018) %>%
-  dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total")) %>%
   group_by(Year, Variable, Fleet) %>%
   mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU)/abs(BAU),
-                          TRUE ~ 0),
-         BAU_global = sum(BAU, na.rm = T),
-         Reform_global = sum(Reform, na.rm = T),
-         Diff_global = case_when(BAU_global != 0 ~ (Reform_global - BAU_global)/abs(BAU_global),
                           TRUE ~ 0)) %>%
   ungroup() %>%
-  mutate(run_number = "A",
-         run_name = "Most ambitious scenario",
-         id = "A",
-         Description = "Complete removal of all capacity-enhancing subsidies (for comparison)")
+  mutate(run_id = "Absolute",
+         run_name = "All subsidies",
+         run_group = "Reference: All capacity-enhancing & \nambiguous subsidies (absolute $)")
 
-# Extract ending results (difference only)
-global_all_bad_results_last <- global_all_bad_results_full %>%
-  dplyr::filter(Year == 2100) %>%
-  group_by(Year, Variable) %>%
-  summarize(Value = unique(Diff_global)*100) %>%
-  ungroup() %>%
-  spread(Variable, Value) %>%
-  rename(Biomass = biomass,
-         Catches = catches_total,
-         Revenue = revenue_total) %>%
-  mutate(run_number = "A",
-         run_name = "Most ambitious scenario")
-
+write_csv(abs_all_BC_results_all, paste0(results_dir, "BC_abs_ts_data.csv"))
 ```
@@
   # 1) global (aggregated) timeseries plot
-  global_all_bad_plot <- global_all_bad_results_full %>%
-        group_by(run_number, run_name, id, Year, Variable, Fleet) %>%
-        summarize(BAU = unique(BAU_global),
-                  Reform = unique(Reform_global),
-                  Diff = unique(Diff_global)) %>%
-        ungroup() %>%
-        mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
-                                    Variable == "catches_total" ~ "Catches",
-                                    Variable == "revenue_total" ~ "Revenue")) %>%
-        mutate(Region = "Global") %>%
-        ggplot()+
-        aes(x = Year, y = Diff*100, color = Variable)+
-        geom_line(size = 1)+
-        theme_bw()+
-        geom_hline(yintercept = 0)+
-        scale_x_continuous(expand = c(0,0))+
-        labs(x = "Year", y = "Change relative to BAU (%)")+
-        theme(legend.position = "none")+
-        facet_wrap(~Variable, ncol = 1, scales = "free_y")
+  abs_all_BC_ts_plot <- BioEconomicModelPlots(dat = abs_all_BC_results_all,
+                                              spatial_res = "global",
+                                              temporal_res = "all",
+                                              start_year = 2018,
+                                              end_year = end_year,
+                                              plot_name = "BC_abs_global_ts_plot",
+                                              plot_width = 8,
+                                              plot_height = 6.5,
+                                              results_dir = results_dir)
 
-  ggsave(paste0(results_dir, "global_all_bad_timeseries_plot.png"), global_all_bad_plot, width = 7.5, height = 6, units = "in")
+  # 2) global (aggregated) "kobe" final year plot
+  abs_all_BC_end_plot <- BioEconomicModelPlots(dat = abs_all_BC_results_all,
+                                                      spatial_res = "global",
+                                                      temporal_res = "last",
+                                                      end_year = end_year,
+                                                      plot_name = paste0("BC_abs_global_", end_year, "_plot"),
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
 
-  # 2) regional timeseries plot
-  regional_all_bad_plot <- global_all_bad_results_full %>%
-        dplyr::select(run_number, run_name, id, Year, Variable, Fleet, Region, BAU, Reform, Diff) %>%
-        mutate(Region = case_when(Region == "atlantic" ~ "Atlantic Ocean",
-                                  Region == "indian" ~ "Indian Ocean",
-                                  Region == "pacific" ~ "Pacific Ocean")) %>%
-        mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
-                                    Variable == "catches_total" ~ "Catches",
-                                    Variable == "revenue_total" ~ "Revenue")) %>%
-        ggplot()+
-        aes(x = Year, y = Diff*100, color = Variable)+
-        geom_line(size = 1)+
-        theme_bw()+
-        geom_hline(yintercept = 0)+
-        scale_x_continuous(expand = c(0,0))+
-        labs(x = "Year", y = "Change relative to BAU (%)")+
-        theme(legend.position = "none")+
-        facet_wrap(Variable ~ Region, ncol = 3, scales = "free_y")
+  # 3) regional timeseries plot
+  regional_abs_all_BC_ts_plot <- BioEconomicModelPlots(dat = abs_all_BC_results_all,
+                                                      spatial_res = "regional",
+                                                      temporal_res = "all",
+                                                      start_year = 2018,
+                                                      end_year = end_year,
+                                                      plot_name = "BC_abs_regional_ts_plot",
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
 
-  ggsave(paste0(results_dir, "regional_all_bad_timeseries_plot.png"), regional_all_bad_plot, width = 7.5, height = 6, units = "in")
-
+  # 4) regional "kobe" final year plot
+  regional_abs_all_BC_end_plot <- BioEconomicModelPlots(dat = abs_all_BC_results_all,
+                                                      spatial_res = "regional",
+                                                      temporal_res = "last",
+                                                      end_year = end_year,
+                                                      plot_name = paste0("BC_abs_regional_", end_year, "_plot"),
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
 }
 ```
+
+## Scenario 2: Remove all bad
+
+```{r}
+# Create model input for removing all bad subsidies
+abs_all_B_fleet_summary <- fleet_vessels %>%
+  group_by(region, fleet) %>%
+  summarize(catch = sum(catch, na.rm = T),
+            bad_subs = sum(bad_ugly_subs, na.rm = T),
+            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
+            removed_subs = sum(bad_subs, na.rm = T)) %>%
+  ungroup()
+
+# Turn into a list
+abs_all_B_list <- abs_all_B_fleet_summary %>%
+  group_by(region) %>%
+  group_split()
+names(abs_all_B_list) <- colnames(bio_dat_regional)[-c(1:2)]
+
+# Run model
+abs_all_B_results <- pmap_df(list(fleet = abs_all_B_list, 
+                                       region = names(abs_all_B_list),
+                                       bio_param = bio_dat_regional_list),
+                                  BioEconModel,
+                                  end_year = end_year,
+                                  return = "all")
+
+# Extract results timeseries
+abs_all_B_results_all <- abs_all_B_results %>%
+  dplyr::filter(Year > 2018) %>%
+  group_by(Year, Variable, Fleet) %>%
+  mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU)/abs(BAU),
+                          TRUE ~ 0)) %>%
+  ungroup() %>%
+  mutate(run_id = "Absolute",
+         run_name = "Capacity-enhancing subsidies",
+         run_group = "Reference: All capacity-enhancing \nsubsidies (absolute $)")
+
+write_csv(abs_all_B_results_all, paste0(results_dir, "B_abs_ts_data.csv"))
+```
+
+```{r}
+# Make plots
+if(make_plots){
+
+  # 1) global (aggregated) timeseries plot
+  abs_all_B_ts_plot <- BioEconomicModelPlots(dat = abs_all_B_results_all,
+                                              spatial_res = "global",
+                                              temporal_res = "all",
+                                              start_year = 2018,
+                                              end_year = end_year,
+                                              plot_name = "B_abs_global_ts_plot",
+                                              plot_width = 8,
+                                              plot_height = 6.5,
+                                              results_dir = results_dir)
+
+  # 2) global (aggregated) "kobe" final year plot
+  abs_all_B_end_plot <- BioEconomicModelPlots(dat = abs_all_B_results_all,
+                                                      spatial_res = "global",
+                                                      temporal_res = "last",
+                                                      end_year = end_year,
+                                                      plot_name = paste0("B_abs_global_", end_year, "_plot"),
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+
+  # 3) regional timeseries plot
+  regional_abs_all_B_ts_plot <- BioEconomicModelPlots(dat = abs_all_B_results_all,
+                                                      spatial_res = "regional",
+                                                      temporal_res = "all",
+                                                      start_year = 2018,
+                                                      end_year = end_year,
+                                                      plot_name = "B_abs_regional_ts_plot",
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+
+  # 4) regional "kobe" final year plot
+  regional_abs_all_B_end_plot <- BioEconomicModelPlots(dat = abs_all_B_results_all,
+                                                      spatial_res = "regional",
+                                                      temporal_res = "last",
+                                                      end_year = end_year,
+                                                      plot_name = paste0("B_abs_regional_", end_year, "_plot"),
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+}
+```
+
+## Scenario 3: Remove fuel subsidies
+
+```{r}
+# Create model input for removing all bad subsidies
+abs_fuel_fleet_summary <- fleet_vessels %>%
+  group_by(region, fleet) %>%
+  summarize(catch = sum(catch, na.rm = T),
+            bad_subs = sum(bad_ugly_subs, na.rm = T),
+            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
+            removed_subs = sum(B7_subs, na.rm = T)) %>%
+  ungroup()
+
+# Turn into a list
+abs_fuel_list <- abs_fuel_fleet_summary %>%
+  group_by(region) %>%
+  group_split()
+names(abs_fuel_list) <- colnames(bio_dat_regional)[-c(1:2)]
+
+# Run model
+abs_fuel_results <- pmap_df(list(fleet = abs_fuel_list, 
+                                       region = names(abs_fuel_list),
+                                       bio_param = bio_dat_regional_list),
+                                  BioEconModel,
+                                  end_year = end_year,
+                                  return = "all")
+
+# Extract results timeseries
+abs_fuel_results_all <- abs_fuel_results %>%
+  dplyr::filter(Year > 2018) %>%
+  group_by(Year, Variable, Fleet) %>%
+  mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU)/abs(BAU),
+                          TRUE ~ 0)) %>%
+  ungroup() %>%
+  mutate(run_id = "Absolute",
+         run_name = "Fuel subsidies",
+         run_group = "Reference: All fuel \nsubsidies (absolute $)")
+
+write_csv(abs_fuel_results_all, paste0(results_dir, "fuel_abs_ts_data.csv"))
+```
+
+```{r}
+# Make plots
+if(make_plots){
+
+  # 1) global (aggregated) timeseries plot
+  abs_fuel_ts_plot <- BioEconomicModelPlots(dat = abs_fuel_results_all,
+                                              spatial_res = "global",
+                                              temporal_res = "all",
+                                              start_year = 2018,
+                                              end_year = end_year,
+                                              plot_name = "fuel_abs_global_ts_plot",
+                                              plot_width = 8,
+                                              plot_height = 6.5,
+                                              results_dir = results_dir)
+
+  # 2) global (aggregated) "kobe" final year plot
+  abs_fuel_end_plot <- BioEconomicModelPlots(dat = abs_fuel_results_all,
+                                                      spatial_res = "global",
+                                                      temporal_res = "last",
+                                                      end_year = end_year,
+                                                      plot_name = paste0("fuel_abs_global_", end_year, "_plot"),
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+
+  # 3) regional timeseries plot
+  regional_abs_fuel_ts_plot <- BioEconomicModelPlots(dat = abs_fuel_results_all,
+                                                      spatial_res = "regional",
+                                                      temporal_res = "all",
+                                                      start_year = 2018,
+                                                      end_year = end_year,
+                                                      plot_name = "fuel_abs_regional_ts_plot",
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+
+  # 4) regional "kobe" final year plot
+  regional_abs_fuel_end_plot <- BioEconomicModelPlots(dat = abs_fuel_results_all,
+                                                      spatial_res = "regional",
+                                                      temporal_res = "last",
+                                                      end_year = end_year,
+                                                      plot_name = paste0("fuel_abs_regional_", end_year, "_plot"),
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+}
+```
+
+## Combine absolute subsidy results
+
+```{r}
+abs_results_all <- abs_all_BC_results_all %>%
+  bind_rows(abs_all_B_results_all) %>%
+  bind_rows(abs_fuel_results_all)
+```
+
+# Section 2: Effective subsidies
+
+This second section presents results obtained by using effective subsidy values - based on suggestions from Roger Martini at the OECD.
+
+```{r}
+rel <- read_csv(here::here("data", "lookup-tables", "oecd_relative_effects_lookup_table.csv"))
+
+rel_fleet_vessels <- fleet_vessels %>%
+   mutate(B1_subs = B1_subs * rel$rel_effect_effort[rel$type == "B1"], 
+           B2_subs = B2_subs * rel$rel_effect_effort[rel$type == "B2"],
+           B3_subs = B3_subs * rel$rel_effect_effort[rel$type == "B3"],
+           B4_subs = B4_subs * rel$rel_effect_effort[rel$type == "B4"],
+           B5_subs = B5_subs * rel$rel_effect_effort[rel$type == "B5"], 
+           B6_subs = B6_subs * rel$rel_effect_effort[rel$type == "B6"],
+           B7_subs = B7_subs * rel$rel_effect_effort[rel$type == "B7"], 
+           C1_subs = C1_subs * rel$rel_effect_effort[rel$type == "C1"], 
+           C2_subs = C2_subs * rel$rel_effect_effort[rel$type == "C2"],
+           C3_subs = C3_subs * rel$rel_effect_effort[rel$type == "C3"]) %>%
+  ungroup() %>%
+  mutate(bad_subs = rowSums(select(., one_of(paste0(bad_subsidy_types, "_subs")))),
+         ugly_subs = rowSums(select(., one_of(paste0(ugly_subsidy_types, "_subs")))),
+         bad_ugly_subs = rowSums(select(., one_of(paste0(c(bad_subsidy_types, ugly_subsidy_types), "_subs")))))
+```
+
+## Scenario 1: Remove all bad + ugly
+
+```{r}
+# Create model input for removing all bad subsidies
+rel_all_BC_fleet_summary <- rel_fleet_vessels %>%
+  group_by(region, fleet) %>%
+  summarize(catch = sum(catch, na.rm = T),
+            bad_subs = sum(bad_ugly_subs, na.rm = T),
+            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
+            removed_subs = sum(bad_ugly_subs, na.rm = T)) %>%
+  ungroup()
+
+# Turn into a list
+rel_all_BC_list <- rel_all_BC_fleet_summary %>%
+  group_by(region) %>%
+  group_split()
+names(rel_all_BC_list) <- colnames(bio_dat_regional)[-c(1:2)]
+
+# Run model
+rel_all_BC_results <- pmap_df(list(fleet = rel_all_BC_list, 
+                                       region = names(rel_all_BC_list),
+                                       bio_param = bio_dat_regional_list),
+                                  BioEconModel,
+                                  end_year = end_year,
+                                  return = "all")
+
+# Extract results timeseries
+rel_all_BC_results_all <- rel_all_BC_results %>%
+  dplyr::filter(Year > 2018) %>%
+  group_by(Year, Variable, Fleet) %>%
+  mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU)/abs(BAU),
+                          TRUE ~ 0)) %>%
+  ungroup() %>%
+  mutate(run_id = "Effective",
+         run_name = "All subsidies",
+         run_group = "Reference: All capacity-enhancing \n& ambiguous subsidies (effective $)")
+
+write_csv(rel_all_BC_results_all, paste0(results_dir, "BC_rel_ts_data.csv"))
+```
+
+```{r}
+# Make plots
+if(make_plots){
+
+  # 1) global (aggregated) timeseries plot
+  rel_all_BC_ts_plot <- BioEconomicModelPlots(dat = rel_all_BC_results_all,
+                                              spatial_res = "global",
+                                              temporal_res = "all",
+                                              start_year = 2018,
+                                              end_year = end_year,
+                                              plot_name = "BC_rel_global_ts_plot",
+                                              plot_width = 8,
+                                              plot_height = 6.5,
+                                              results_dir = results_dir)
+
+  # 2) global (aggregated) "kobe" final year plot
+  rel_all_BC_end_plot <- BioEconomicModelPlots(dat = rel_all_BC_results_all,
+                                                      spatial_res = "global",
+                                                      temporal_res = "last",
+                                                      end_year = end_year,
+                                                      plot_name = paste0("BC_rel_global_", end_year, "_plot"),
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+
+  # 3) regional timeseries plot
+  regional_rel_all_BC_ts_plot <- BioEconomicModelPlots(dat = rel_all_BC_results_all,
+                                                      spatial_res = "regional",
+                                                      temporal_res = "all",
+                                                      start_year = 2018,
+                                                      end_year = end_year,
+                                                      plot_name = "BC_rel_regional_ts_plot",
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+
+  # 4) regional "kobe" final year plot
+  regional_rel_all_BC_end_plot <- BioEconomicModelPlots(dat = rel_all_BC_results_all,
+                                                      spatial_res = "regional",
+                                                      temporal_res = "last",
+                                                      end_year = end_year,
+                                                      plot_name = paste0("BC_rel_regional_", end_year, "_plot"),
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+}
+```
+
+## Scenario 2: Remove all bad
+
+```{r}
+# Create model input for removing all bad subsidies
+rel_all_B_fleet_summary <- rel_fleet_vessels %>%
+  group_by(region, fleet) %>%
+  summarize(catch = sum(catch, na.rm = T),
+            bad_subs = sum(bad_ugly_subs, na.rm = T),
+            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
+            removed_subs = sum(bad_subs, na.rm = T)) %>%
+  ungroup()
+
+# Turn into a list
+rel_all_B_list <- rel_all_B_fleet_summary %>%
+  group_by(region) %>%
+  group_split()
+names(rel_all_B_list) <- colnames(bio_dat_regional)[-c(1:2)]
+
+# Run model
+rel_all_B_results <- pmap_df(list(fleet = rel_all_B_list, 
+                                       region = names(rel_all_B_list),
+                                       bio_param = bio_dat_regional_list),
+                                  BioEconModel,
+                                  end_year = end_year,
+                                  return = "all")
+
+# Extract results timeseries
+rel_all_B_results_all <- rel_all_B_results %>%
+  dplyr::filter(Year > 2018) %>%
+  group_by(Year, Variable, Fleet) %>%
+  mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU)/abs(BAU),
+                          TRUE ~ 0)) %>%
+  ungroup() %>%
+  mutate(run_id = "Effective",
+         run_name = "Capacity-enhancing subsidies",
+         run_group = "Reference: All capacity-enhancing \nsubsidies (effective $)")
+
+write_csv(rel_all_B_results_all, paste0(results_dir, "B_rel_ts_data.csv"))
+```
+
+```{r}
+# Make plots
+if(make_plots){
+
+  # 1) global (aggregated) timeseries plot
+  rel_all_B_ts_plot <- BioEconomicModelPlots(dat = rel_all_B_results_all,
+                                              spatial_res = "global",
+                                              temporal_res = "all",
+                                              start_year = 2018,
+                                              end_year = end_year,
+                                              plot_name = "B_rel_global_ts_plot",
+                                              plot_width = 8,
+                                              plot_height = 6.5,
+                                              results_dir = results_dir)
+
+  # 2) global (aggregated) "kobe" final year plot
+  rel_all_B_end_plot <- BioEconomicModelPlots(dat = rel_all_B_results_all,
+                                                      spatial_res = "global",
+                                                      temporal_res = "last",
+                                                      end_year = end_year,
+                                                      plot_name = paste0("B_rel_global_", end_year, "_plot"),
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+
+  # 3) regional timeseries plot
+  regional_rel_all_B_ts_plot <- BioEconomicModelPlots(dat = rel_all_B_results_all,
+                                                      spatial_res = "regional",
+                                                      temporal_res = "all",
+                                                      start_year = 2018,
+                                                      end_year = end_year,
+                                                      plot_name = "B_rel_regional_ts_plot",
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+
+  # 4) regional "kobe" final year plot
+  regional_rel_all_B_end_plot <- BioEconomicModelPlots(dat = rel_all_B_results_all,
+                                                      spatial_res = "regional",
+                                                      temporal_res = "last",
+                                                      end_year = end_year,
+                                                      plot_name = paste0("B_rel_regional_", end_year, "_plot"),
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+}
+```
+
+## Scenario 3: Remove fuel subsidies
+
+```{r}
+# Create model input for removing all bad subsidies
+rel_fuel_fleet_summary <- rel_fleet_vessels %>%
+  group_by(region, fleet) %>%
+  summarize(catch = sum(catch, na.rm = T),
+            bad_subs = sum(bad_ugly_subs, na.rm = T),
+            fishing_KWh = sum(fishing_KWh_eez_fao_ter, na.rm = T),
+            removed_subs = sum(B7_subs, na.rm = T)) %>%
+  ungroup()
+
+# Turn into a list
+rel_fuel_list <- rel_fuel_fleet_summary %>%
+  group_by(region) %>%
+  group_split()
+names(rel_fuel_list) <- colnames(bio_dat_regional)[-c(1:2)]
+
+# Run model
+rel_fuel_results <- pmap_df(list(fleet = rel_fuel_list, 
+                                       region = names(rel_fuel_list),
+                                       bio_param = bio_dat_regional_list),
+                                  BioEconModel,
+                                  end_year = end_year,
+                                  return = "all")
+
+# Extract results timeseries
+rel_fuel_results_all <- rel_fuel_results %>%
+  dplyr::filter(Year > 2018) %>%
+  group_by(Year, Variable, Fleet) %>%
+  mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU)/abs(BAU),
+                          TRUE ~ 0)) %>%
+  ungroup() %>%
+  mutate(run_id = "Effective",
+         run_name = "Fuel subsidies",
+         run_group = "Reference: All fuel \nsubsidies (effective $)")
+
+write_csv(rel_fuel_results_all, paste0(results_dir, "fuel_rel_ts_data.csv"))
+```
+
+```{r}
+# Make plots
+if(make_plots){
+
+  # 1) global (aggregated) timeseries plot
+  rel_fuel_ts_plot <- BioEconomicModelPlots(dat = rel_fuel_results_all,
+                                              spatial_res = "global",
+                                              temporal_res = "all",
+                                              start_year = 2018,
+                                              end_year = end_year,
+                                              plot_name = "fuel_rel_global_ts_plot",
+                                              plot_width = 8,
+                                              plot_height = 6.5,
+                                              results_dir = results_dir)
+
+  # 2) global (aggregated) "kobe" final year plot
+  rel_fuel_end_plot <- BioEconomicModelPlots(dat = rel_fuel_results_all,
+                                                      spatial_res = "global",
+                                                      temporal_res = "last",
+                                                      end_year = end_year,
+                                                      plot_name = paste0("fuel_rel_global_", end_year, "_plot"),
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+
+  # 3) regional timeseries plot
+  regional_fuel_BC_ts_plot <- BioEconomicModelPlots(dat = rel_fuel_results_all,
+                                                      spatial_res = "regional",
+                                                      temporal_res = "all",
+                                                      start_year = 2018,
+                                                      end_year = end_year,
+                                                      plot_name = "fuel_rel_regional_ts_plot",
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+
+  # 4) regional "kobe" final year plot
+  regional_rel_fuel_end_plot <- BioEconomicModelPlots(dat = rel_fuel_results_all,
+                                                      spatial_res = "regional",
+                                                      temporal_res = "last",
+                                                      end_year = end_year,
+                                                      plot_name = paste0("fuel_rel_regional_", end_year, "_plot"),
+                                                      plot_width = 8,
+                                                      plot_height = 6.5,
+                                                      results_dir = results_dir)
+}
+```
+
+## Combine absolute subsidy results
+
+```{r}
+rel_results_all <- rel_all_BC_results_all %>%
+  bind_rows(rel_all_B_results_all) %>%
+  bind_rows(rel_fuel_results_all)
+```
+
+# Compare
+
+```{r}
+results_all <- abs_results_all %>%
+  bind_rows(rel_results_all)
+
+# Make plots
+if(make_plots){
+
+  # 1) global (aggregated) timeseries plot
+  compare_ts_plot <- BioEconomicModelPlots(dat = results_all,
+                                           spatial_res = "global",
+                                           temporal_res = "all",
+                                           start_year = 2018,
+                                           end_year = end_year,
+                                           plot_name = "compare_global_ts_plot",
+                                           plot_width = 8,
+                                           plot_height = 6.5,
+                                           results_dir = results_dir,
+                                           group_var = "run_group",
+                                           color_var = "run_group",
+                                           legend_pos_manual = "bottom",
+                                           legend_name = "Scenario")
+
+  # 2) global (aggregated) "kobe" final year plot
+  compare_end_plot <- BioEconomicModelPlots(dat = results_all,
+                                            spatial_res = "global",
+                                            temporal_res = "last",
+                                            end_year = end_year,
+                                            plot_name = paste0("compare_global_", end_year, "_plot"),
+                                            plot_width = 8,
+                                            plot_height = 6.5,
+                                            results_dir = results_dir,
+                                            group_var = "run_group",
+                                            color_var = "run_group",
+                                            legend_pos_manual = "bottom",
+                                            legend_name = "Scenario")
+
+  # 3) regional timeseries plot
+  regional_compare_ts_plot <- BioEconomicModelPlots(dat = results_all,
+                                                    spatial_res = "regional",
+                                                    temporal_res = "all",
+                                                    start_year = 2018,
+                                                    end_year = end_year,
+                                                    plot_name = "compare_regional_ts_plot",
+                                                    plot_width = 8,
+                                                    plot_height = 6.5,
+                                                    results_dir = results_dir,
+                                                    group_var = "run_group",
+                                                    color_var = "run_group",
+                                                    legend_pos_manual = "bottom",
+                                                    legend_name = "Scenario")
+
+  # 4) regional "kobe" final year plot
+  regional_compare_end_plot <- BioEconomicModelPlots(dat = results_all,
+                                                     spatial_res = "regional",
+                                                     temporal_res = "last",
+                                                     end_year = end_year,
+                                                     plot_name = paste0("compare_regional_", end_year, "_plot"),
+                                                     plot_width = 8,
+                                                     plot_height = 6.5,
+                                                     results_dir = results_dir,
+                                                     group_var = "run_group",
+                                                     color_var = "run_group",
+                                                     legend_pos_manual = "bottom",
+                                                     legend_name = "Scenario")
+}
+```
+```

### 2020-09-16 scripts/functions/BioEconomicModelPlots.R

@@ -12,7 +12,10 @@ BioEconomicModelPlots <- function(dat,
                                   plot_width = 8,
                                   plot_height = 6.5,
                                   results_dir,
-                                  compare = FALSE){
+                                  group_var = "run_group",
+                                  color_var = "Variable",
+                                  legend_pos_manual = "none",
+                                  legend_name = "Variable"){
   
   ### General theme
   plot_theme <- theme_linedraw()+
@@ -56,27 +59,28 @@ BioEconomicModelPlots <- function(dat,
     
   }
   
-  if(compare == FALSE){
-  ### Make plots
+  # if(compare == FALSE){
+  # ### Make plots
   if(temporal_res == "all"){
     
     plot <- plot_dat %>%
       dplyr::filter(Year >= start_year & Year <= end_year) %>%
       ggplot()+
-      aes(x = Year, y = Diff_tot*100, color = Variable)+
+      aes(x = Year, y = Diff_tot*100)+
+      aes_string(color = color_var, group = group_var)+
       geom_line(size = 1)+
       geom_hline(yintercept = 0)+
       scale_x_continuous(expand = c(0,0))+
-      labs(x = "Year", y = "Change relative to BAU (%)")+
+      labs(x = "Year", y = "Change relative to BAU (%)", color = legend_name)+
       plot_theme +
-      theme(legend.position = "none")+
+      theme(legend.position = legend_pos_manual)+
       facet_grid(Fleet+Variable~Region)
     
   }else if(temporal_res == "last"){
     
     plot_dat <- plot_dat %>%
       dplyr::filter(Year == end_year) %>%
-      group_by(Year, Variable, Fleet, Region) %>%
+      group_by(Year, Variable, Fleet, Region, run_id, run_name, run_group) %>%
       summarize(Value = unique(Diff_tot)) %>%
       ungroup() %>%
       spread(Variable, Value)
@@ -90,89 +94,93 @@ BioEconomicModelPlots <- function(dat,
     
     plot <- plot_dat %>%
       ggplot()+
-      aes(x = Biomass, y = Catches, size = Revenue, color = Revenue)+
-      geom_point()+
+      aes(x = Biomass, y = Catches, size = Revenue)+
+      aes_string(color = color_var, group = group_var)+
+      geom_point(alpha = 0.6)+
       scale_x_continuous(labels = percent, limits = x_limits)+
[…]

### 2020-09-16 scripts/functions/BioEconomicModelPlots.R
running another mgmt threshold for comparison

@@ -13,9 +13,9 @@ BioEconomicModelPlots <- function(dat,
                                   plot_height = 6.5,
                                   results_dir,
                                   group_var = "run_group",
-                                  color_var = "Variable",
+                                  color_var = "run_group",
                                   legend_pos_manual = "none",
-                                  legend_name = "Variable"){
+                                  legend_name = ""){
   
   ### General theme
   plot_theme <- theme_linedraw()+

### 2020-09-16 scripts/07_proposals.Rmd
running proposal results again

--- 2020-09-04 scripts/07_proposals.Rmd
@@
 
-# Directories for the output files generated by this script
-results_dir <- here::here("results", "07-proposals/")
-if (dir.exists(results_dir) == F) {
-  dir.create(results_dir, recursive = T)
-}
-
 bad_subsidy_types <- c("B1", "B2", "B3", "B4", "B5", "B6", "B7")
@@
 subsidy_types_sorted_sumaila <- c(good_subsidy_types, bad_subsidy_types, ugly_subsidy_types)
+
+# Threshold to be considered managed (using FMI scores)
+managed_cutoff <- 0.75
+
+end_year <- 2080
+
+# Directories for the output files generated by this script
+results_dir <- paste0(here::here("results", "07-proposals/"), "mgmt_threshold_", managed_cutoff, "/")
+if (dir.exists(results_dir) == F) {
+  dir.create(results_dir, recursive = T)
+}
 ```
@@
 ```{r}
-# Threshold to be considered managed (using FMI scores)
-managed_cutoff <- 0.66
-```
-
-```{r}
 # Proposal settings
@@
           "two_tier_cutoff" = selected_proposal$two_tier_cutoff,
-          "three_tier_cutoff" = as.numeric(unlist(str_split(
-          selected_proposal$three_tier_cutoff, ", "
-          ))),
+          "three_tier_cutoff" = as.numeric(unlist(str_split(selected_proposal$three_tier_cutoff, ", "))),
           "tier1_cap_rule" = selected_proposal$tier1_cap_rule,
@@
           "tier1_cap_value" = selected_proposal$tier1_cap_value,
-          "tier1_cap_fishers" = selected_proposal$tier1_cap_fishers,
           "tier1_cap_percent" = selected_proposal$tier1_cap_percent,
+          "tier1_cap_best_percent_subs" = selected_proposal$tier1_cap_best_percent_subs,
+          "tier1_cap_best_percent_landed_value" = selected_proposal$tier1_cap_best_percent_landed_value,
+          "tier1_cap_best_percent_fishers" = selected_proposal$tier1_cap_best_percent_fishers,
           "tier2_cap_value" = selected_proposal$tier2_cap_value,
-          "tier2_cap_fishers" = selected_proposal$tier1_cap_fishers,
           "tier2_cap_percent" = selected_proposal$tier2_cap_percent,
+          "tier2_cap_best_percent_subs" = selected_proposal$tier2_cap_best_percent_subs,
+          "tier2_cap_best_percent_landed_value" = selected_proposal$tier2_cap_best_percent_landed_value,
+          "tier2_cap_best_percent_fishers" = selected_proposal$tier2_cap_best_percent_fishers,
           "tier3_cap_value" = selected_proposal$tier3_cap_value,
-          "tier3_cap_fishers" = selected_proposal$tier3_cap_fishers,
-          "tier3_cap_percent" = selected_proposal$tier3_cap_percent)
+          "tier3_cap_percent" = selected_proposal$tier3_cap_percent,
+          "tier3_cap_best_percent_subs" = selected_proposal$tier3_cap_best_percent_subs,
+          "tier3_cap_best_percent_landed_value" = selected_proposal$tier3_cap_best_percent_landed_value,
+          "tier3_cap_best_percent_fishers" = selected_proposal$tier3_cap_best_percent_fishers)
 
@@
                                   BioEconModel,
-                                  end_year = 2100,
+                                  end_year = end_year,
                                   return = "all")
@@
       mutate(run_id = proposal_name,
-             run_name = names(proposal_name))
+             run_name = names(proposal_name),
+             run_group = unique(proposal_settings$category[proposal_settings$proposal == proposal_name]))
 
-      write_csv(results_all, paste0(results_dir, "results_", str_replace_all(proposal_name, "/", "_"), ".csv"))
+      write_csv(results_all, paste0(results_dir, str_replace_all(names(proposal_name), "/", "_"), ".csv"))
 
@@
 ```
+
+Make plots with all proposals and the most ambitious result
+
+```{r}
+# Load most ambitous results from previous script
+most_ambitious_results <- read_csv(paste0(here::here("results", "06-run-model/"), "mgmt_threshold_", managed_cutoff, "/", "BC_rel_ts_data.csv")) %>%
+  mutate(run_id = "Ambitious Reform",
+         run_group = "Ambitious Reform")
+
+plot_results <- proposal_results %>%
+  dplyr::filter(run_id != "RD/TN/RL/103") %>%
+  bind_rows(most_ambitious_results)
+
+# Make plots
+if(make_plots){
+
+  # 1) global (aggregated) timeseries plot
+  compare_ts_plot <- BioEconomicModelPlots(dat = plot_results,
+                                           spatial_res = "global",
+                                           temporal_res = "all",
+                                           start_year = 2018,
+                                           end_year = end_year,
+                                           plot_name = "all_proposals_ts_plot",
+                                           plot_width = 8,
+                                           plot_height = 10,
+                                           results_dir = results_dir,
+                                           group_var = "run_id",
+                                           color_var = "run_group",
+                                           legend_pos_manual = "bottom",
+                                           legend_name = "Scenario Type")
+
+  # 2) global (aggregated) "kobe" final year plot
+  compare_end_plot <- BioEconomicModelPlots(dat = plot_results,
+                                            spatial_res = "global",
+                                            temporal_res = "last",
+                                            end_year = end_year,
+                                            plot_name = "all_proposals_end_plot",
+                                            plot_width = 8,
+                                            plot_height = 8,
+                                            results_dir = results_dir,
+                                            group_var = "run_id",
+                                            color_var = "run_group",
+                                            legend_pos_manual = "bottom",
+                                            legend_name = "Scenario Type")
+
+  # 3) regional timeseries plot
+  regional_compare_ts_plot <- BioEconomicModelPlots(dat = plot_results,
+                                                    spatial_res = "regional",
+                                                    temporal_res = "all",
+                                                    start_year = 2018,
+                                                    end_year = end_year,
+                                                    plot_name = "regional_all_proposals_ts_plot",
+                                                    plot_width = 12,
+                                                    plot_height = 10,
+                                                    results_dir = results_dir,
+                                                    group_var = "run_id",
+                                                    color_var = "run_group",
+                                                    legend_pos_manual = "bottom",
+                                                    legend_name = "Scenario Type")
+
+  # 4) regional "kobe" final year plot
+  regional_compare_end_plot <- BioEconomicModelPlots(dat = plot_results,
+                                                     spatial_res = "regional",
+                                                     temporal_res = "last",
+                                                     end_year = end_year,
+                                                     plot_name = "regional_all_proposals_end_plot",
+                                                     plot_width = 12,
+                                                     plot_height = 8,
+                                                     results_dir = results_dir,
+                                                     group_var = "run_id",
+                                                     color_var = "run_group",
+                                                     legend_pos_manual = "bottom",
+                                                     legend_name = "Scenario Type")
+}
+```
+
+Make nice looking table showing most ambitious result values (global and regional)
+
+```{r}
+# most_ambitious_results_global <- most_ambitious_results %>%
+#   group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
+#     summarize(BAU_tot = sum(BAU, na.rm = T),
+#               Reform_tot = sum(Reform, na.rm = T),
+#               Diff_tot = case_when(BAU_tot != 0 ~ (Reform_tot - BAU_tot)/abs(BAU_tot),
+#                             TRUE ~ 0)) %>%
+#     ungroup() %>%
+#     mutate(Region = "Global") %>%
+#     # mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
+#     #                             Variable == "catches_total" ~ "Catches",
+#     #                             Variable == "revenue_total" ~ "Revenue",
+#     #                             Variable )) %>%
+#   dplyr::filter(Fleet == "Total") %>%
+#   dplyr::filter(Variable %in% c("Biomass", "Catches", "Revenue"))
+```

### 2020-09-16 app/scripts/BioEconModel.R

@@ -50,13 +50,16 @@ BioEconModel <- function(fleet,
   ### Step 1: BAU ----------------------------------------------------------------------
   ### ----------------------------------------------------------------------------------  
 
-  ## Set up storage bins to track important things for our BAU run
+  ### Set up storage bins to track important things for our BAU run
+  # Biomass
   biomass_bau <- matrix(0, nrow = stop_time, ncol = 1)
   rownames(biomass_bau) <- year_range
 
+  # Price
   price_bau <- matrix(0, nrow = stop_time, ncol = 1)
   rownames(price_bau) <- year_range
   
+  # Catches
   catches_fleet_bau <- matrix(0, nrow = stop_time, ncol = length(fleet_names))
   rownames(catches_fleet_bau) <- year_range
   colnames(catches_fleet_bau) <- fleet_names
@@ -64,6 +67,7 @@ BioEconModel <- function(fleet,
   catches_total_bau <- matrix(0, nrow = stop_time, ncol = 1)
   rownames(catches_total_bau) <- year_range
   
+  # Effort
   effort_fleet_bau <- matrix(0, nrow = stop_time, ncol = length(fleet_names))
   rownames(effort_fleet_bau) <- year_range
   colnames(effort_fleet_bau) <- fleet_names
@@ -71,6 +75,23 @@ BioEconModel <- function(fleet,
   effort_total_bau <- matrix(0, nrow = stop_time, ncol = 1)
   rownames(effort_total_bau) <- year_range
   
+  # Fishing mortality (continuous)
+  f_mort_fleet_bau <- matrix(0, nrow = stop_time, ncol = length(fleet_names))
+  rownames(f_mort_fleet_bau) <- year_range
+  colnames(f_mort_fleet_bau) <- fleet_names
+  
+  f_mort_total_bau <- matrix(0, nrow = stop_time, ncol = 1)
+  rownames(f_mort_total_bau) <- year_range
+  
+  # Fishing mortality (discrete)
+  u_mort_fleet_bau <- matrix(0, nrow = stop_time, ncol = length(fleet_names))
+  rownames(u_mort_fleet_bau) <- year_range
+  colnames(u_mort_fleet_bau) <- fleet_names
+  
[…]

### 2020-09-16 scripts/functions/BioEconomicModelPlots.R

@@ -6,7 +6,8 @@ BioEconomicModelPlots <- function(dat,
                                   end_year = 2100,
                                   variables_keep = c("Biomass" = "biomass",
                                                      "Catches" = "catches_total",
-                                                     "Revenue" = "revenue_total"),
+                                                     "Revenue" = "revenue_total",
+                                                     "Mortality" = "u_mort_total"),
                                   fleets_keep = c("Total" = "Total"),
                                   plot_name = "plot",
                                   plot_width = 8,
@@ -14,6 +15,7 @@ BioEconomicModelPlots <- function(dat,
                                   results_dir,
                                   group_var = "run_group",
                                   color_var = "run_group",
+                                  size_var = "Mortality",
                                   legend_pos_manual = "none",
                                   legend_name = ""){
   
@@ -37,7 +39,8 @@ BioEconomicModelPlots <- function(dat,
     mutate(Region = "Global") %>%
     mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                                 Variable == "catches_total" ~ "Catches",
-                                Variable == "revenue_total" ~ "Revenue"))
+                                Variable == "revenue_total" ~ "Revenue",
+                                Variable == "u_mort_total" ~ "Mortality"))
     
   }else if(spatial_res == "regional"){
     
@@ -55,12 +58,11 @@ BioEconomicModelPlots <- function(dat,
                                 Region == "pacific" ~ "Pacific Ocean")) %>%
       mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
                                   Variable == "catches_total" ~ "Catches",
-                                  Variable == "revenue_total" ~ "Revenue"))
+                                  Variable == "revenue_total" ~ "Revenue",
+                                  Variable == "u_mort_total" ~ "Mortality"))
     
   }
-  
-  # if(compare == FALSE){
-  # ### Make plots
+
   if(temporal_res == "all"){
     
     plot <- plot_dat %>%
[…]

### 2020-09-17 scripts/07_proposals.Rmd
static results update

@@
 library(tidyverse)
+library(countrycode)
 
@@
 
-Make nice looking table showing most ambitious result values (global and regional)
+## Extract 2060 and end year results for all proposals and save as nice tables
 
 ```{r}
-# most_ambitious_results_global <- most_ambitious_results %>%
-#   group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
-#     summarize(BAU_tot = sum(BAU, na.rm = T),
-#               Reform_tot = sum(Reform, na.rm = T),
-#               Diff_tot = case_when(BAU_tot != 0 ~ (Reform_tot - BAU_tot)/abs(BAU_tot),
-#                             TRUE ~ 0)) %>%
-#     ungroup() %>%
-#     mutate(Region = "Global") %>%
-#     # mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
-#     #                             Variable == "catches_total" ~ "Catches",
-#     #                             Variable == "revenue_total" ~ "Revenue",
-#     #                             Variable )) %>%
-#   dplyr::filter(Fleet == "Total") %>%
-#   dplyr::filter(Variable %in% c("Biomass", "Catches", "Revenue"))
+all_results_global_output_table <- plot_results %>%
+  dplyr::filter(Year %in% c(2060, end_year)) %>%
+  dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total", "u_mort_total")) %>%
+  group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
+  summarize(BAU_tot = sum(BAU, na.rm = T),
+            Reform_tot = sum(Reform, na.rm = T),
+            Diff_tot = case_when(BAU_tot != 0 ~ (Reform_tot - BAU_tot)/abs(BAU_tot),
+                            TRUE ~ 0)) %>%
+  ungroup() %>%
+  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
+                                Variable == "catches_total" ~ "Catches",
+                                Variable == "revenue_total" ~ "Revenue",
+                                Variable == "u_mort_total" ~ "Fishing Mortality")) %>%
+  dplyr::select(Id = run_id,
+                Name = run_name,
+                Category = run_group, 
+                Year,
+                Diff_tot,
+                Variable) %>%
+  spread(Variable, Diff_tot)
+
+write.csv(all_results_global_output_table, paste0(results_dir, "all_results_global_output_table.csv"))
+
+# Get rounded end values
+global_biomass_2060 <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == 2060 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
+global_biomass_end <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
+
+global_catches_2060 <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == 2060 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
+global_catches_end <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
+
+# Now do regional
+all_results_regional_output_table <- plot_results %>%
+  dplyr::filter(Year %in% c(2060, end_year)) %>%
+  dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total", "u_mort_total")) %>%
+  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
+                                Variable == "catches_total" ~ "Catches",
+                                Variable == "revenue_total" ~ "Revenue",
+                                Variable == "u_mort_total" ~ "Fishing Mortality")) %>%
+  dplyr::select(Id = run_id,
+                Name = run_name,
+                Category = run_group, 
+                Year,
+                Region,
+                Diff,
+                Variable) %>%
+  spread(Variable, Diff)
+
+write.csv(all_results_regional_output_table, paste0(results_dir, "all_results_regional_output_table.csv"))
 ```
+
+## Do the same with aboslute values
+
+```{r}
+# Weight of a mature dairy cow in mt
+cow_weight <- 0.6803886
+
+all_results_global_cow_equivalent_table <- plot_results %>%
+  dplyr::filter(Year %in% c(2060, end_year)) %>%
+  dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
+  group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
+  summarize(BAU_tot = sum(BAU, na.rm = T),
+            Reform_tot = sum(Reform, na.rm = T),
+            abs_Diff_tot = case_when(BAU_tot != 0 ~ Reform_tot-BAU_tot,
+                                     TRUE ~ 0),
+            cow_Diff = abs_Diff_tot*cow_weight) %>%
+  ungroup() %>%
+  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
+                              Variable == "catches_total" ~ "Catches")) %>%
+  dplyr::select(Id = run_id,
+                Name = run_name,
+                Category = run_group, 
+                Year,
+                cow_Diff,
+                Variable) %>%
+  spread(Variable, cow_Diff)
+
+write.csv(all_results_global_cow_equivalent_table, paste0(results_dir, "all_results_global_cow_equivalent_table.csv"))
+
+all_results_regional_cow_equivalent_table <- plot_results %>%
+  dplyr::filter(Year %in% c(2060, end_year)) %>%
+  dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
+  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
+                                Variable == "catches_total" ~ "Catches")) %>%
+  mutate(abs_Diff = case_when(BAU != 0 ~ Reform-BAU,
+                              TRUE ~ 0),
+         cow_Diff = abs_Diff*cow_weight) %>%
+  dplyr::select(Id = run_id,
+                Name = run_name,
+                Category = run_group, 
+                Year,
+                Region,
+                cow_Diff,
+                Variable) %>%
+  spread(Variable, cow_Diff)
+
+write.csv(all_results_regional_cow_equivalent_table, paste0(results_dir, "all_results_regional_cow_equivalent_table.csv"))
+
+```

### 2020-10-05 app/ui.R
rehost

@@ -41,8 +41,11 @@ library(leaflet) # interactive maps
 library(plotly) # interactive charts
 library(rnaturalearth)
 library(rnaturalearthdata)
-library(png)
-library(ggpubr) # plot arranging
+library(rgeos)
+library(cowplot)
+library(scales)
+#library(png)
+#library(ggpubr) # plot arranging
 library(gridExtra)
 library(grid)
 library(RColorBrewer) # other color scales

### 2020-10-05 scripts/07_proposals.Rmd

--- 2020-09-16 scripts/07_proposals.Rmd
@@
 included_proposals <- proposal_settings %>%
-  dplyr::filter(include == "Yes") %>%
+  dplyr::filter(include %in% c("Yes", "Alternate")) %>%
   mutate(display_name = case_when(proposal == "Default" ~ "None",
@@
   dplyr::select(category, proposal, display_name) %>%
-  arrange(category)
+  arrange(category) %>%
+  dplyr::filter(!(proposal %in% c("RD/TN/RL/126", "RD/TN/RL/119"))) # remove blank entries for tool
 
@@
 
+  # 2) global (aggregated) "kobe" final year plot
+  compare_2050_plot <- BioEconomicModelPlots(dat = plot_results,
+                                            spatial_res = "global",
+                                            temporal_res = "last",
+                                            end_year = 2050,
+                                            plot_name = "all_proposals_2050_plot",
+                                            plot_width = 8,
+                                            plot_height = 8,
+                                            results_dir = results_dir,
+                                            group_var = "run_id",
+                                            color_var = "run_group",
+                                            legend_pos_manual = "bottom",
+                                            legend_name = "Scenario Type")
+
   # 3) regional timeseries plot
@@
                                                      legend_name = "Scenario Type")
+
+  # 4) regional "kobe" final year plot
+  regional_compare_2050_plot <- BioEconomicModelPlots(dat = plot_results,
+                                                     spatial_res = "regional",
+                                                     temporal_res = "last",
+                                                     end_year = 2050,
+                                                     plot_name = "regional_all_proposals_2050_plot",
+                                                     plot_width = 12,
+                                                     plot_height = 8,
+                                                     results_dir = results_dir,
+                                                     group_var = "run_id",
+                                                     color_var = "run_group",
+                                                     legend_pos_manual = "bottom",
+                                                     legend_name = "Scenario Type")
 }
@@
 
-Make nice looking table showing most ambitious result values (global and regional)
+## Extract 2060 and end year results for all proposals and save as nice tables
 
 ```{r}
-# most_ambitious_results_global <- most_ambitious_results %>%
-#   group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
-#     summarize(BAU_tot = sum(BAU, na.rm = T),
-#               Reform_tot = sum(Reform, na.rm = T),
-#               Diff_tot = case_when(BAU_tot != 0 ~ (Reform_tot - BAU_tot)/abs(BAU_tot),
-#                             TRUE ~ 0)) %>%
-#     ungroup() %>%
-#     mutate(Region = "Global") %>%
-#     # mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
-#     #                             Variable == "catches_total" ~ "Catches",
-#     #                             Variable == "revenue_total" ~ "Revenue",
-#     #                             Variable )) %>%
-#   dplyr::filter(Fleet == "Total") %>%
-#   dplyr::filter(Variable %in% c("Biomass", "Catches", "Revenue"))
+all_results_global_output_table <- plot_results %>%
+  dplyr::filter(Year %in% c(2050, end_year)) %>%
+  dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total", "u_mort_total")) %>%
+  group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
+  summarize(BAU_tot = sum(BAU, na.rm = T),
+            Reform_tot = sum(Reform, na.rm = T),
+            Diff_tot = case_when(BAU_tot != 0 ~ (Reform_tot - BAU_tot)/abs(BAU_tot),
+                            TRUE ~ 0)) %>%
+  ungroup() %>%
+  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
+                                Variable == "catches_total" ~ "Catches",
+                                Variable == "revenue_total" ~ "Revenue",
+                                Variable == "u_mort_total" ~ "Fishing Mortality")) %>%
+  dplyr::select(Id = run_id,
+                Name = run_name,
+                Category = run_group, 
+                Year,
+                Diff_tot,
+                Variable) %>%
+  spread(Variable, Diff_tot)
+
+write.csv(all_results_global_output_table, paste0(results_dir, "all_results_global_output_table.csv"))
+
+# Get rounded end values
+global_biomass_2050 <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == 2050 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
+global_biomass_end <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
+
+global_catches_2050 <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == 2050 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
+global_catches_end <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
+
+# Now do regional
+all_results_regional_output_table <- plot_results %>%
+  dplyr::filter(Year %in% c(2050, end_year)) %>%
+  dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total", "u_mort_total")) %>%
+  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
+                                Variable == "catches_total" ~ "Catches",
+                                Variable == "revenue_total" ~ "Revenue",
+                                Variable == "u_mort_total" ~ "Fishing Mortality")) %>%
+  dplyr::select(Id = run_id,
+                Name = run_name,
+                Category = run_group, 
+                Year,
+                Region,
+                Diff,
+                Variable) %>%
+  spread(Variable, Diff)
+
+write.csv(all_results_regional_output_table, paste0(results_dir, "all_results_regional_output_table.csv"))
 ```
+
+## Do the same with aboslute values
+
+```{r}
+all_results_global_absolute_table <- plot_results %>%
+  dplyr::filter(Year %in% c(2050, end_year)) %>%
+  dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
+  group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
+  summarize(BAU_tot = sum(BAU, na.rm = T),
+            Reform_tot = sum(Reform, na.rm = T),
+            abs_Diff_tot = case_when(BAU_tot != 0 ~ Reform_tot-BAU_tot,
+                                     TRUE ~ 0),
+            cow_Diff = abs_Diff_tot*cow_weight) %>%
+  ungroup() %>%
+  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
+                              Variable == "catches_total" ~ "Catches")) %>%
+  dplyr::select(Id = run_id,
+                Name = run_name,
+                Category = run_group, 
+                Year,
+                abs_Diff_tot,
+                Variable) %>%
+  spread(Variable, abs_Diff_tot)
+
+write.csv(all_results_global_absolute_table, paste0(results_dir, "all_results_global_absolute_table.csv"))
+
+all_results_regional_absolute_table <- plot_results %>%
+  dplyr::filter(Year %in% c(2050, end_year)) %>%
+  dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
+  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
+                                Variable == "catches_total" ~ "Catches")) %>%
+  mutate(abs_Diff = case_when(BAU != 0 ~ Reform-BAU,
+                              TRUE ~ 0),
+         cow_Diff = abs_Diff*cow_weight) %>%
+  dplyr::select(Id = run_id,
+                Name = run_name,
+                Category = run_group, 
+                Year,
+                Region,
+                abs_Diff,
+                Variable) %>%
+  spread(Variable, abs_Diff)
+
+write.csv(all_results_regional_absolute_table, paste0(results_dir, "all_results_regional_absolute_table.csv"))
+```
+
+```{r}
+# Weight of a mature dairy cow in mt
+cow_weight <- 0.6803886
+
+all_results_global_cow_equivalent_table <- plot_results %>%
+  dplyr::filter(Year %in% c(2050, end_year)) %>%
+  dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
+  group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
+  summarize(BAU_tot = sum(BAU, na.rm = T),
+            Reform_tot = sum(Reform, na.rm = T),
+            abs_Diff_tot = case_when(BAU_tot != 0 ~ Reform_tot-BAU_tot,
+                                     TRUE ~ 0),
+            cow_Diff = abs_Diff_tot*cow_weight) %>%
+  ungroup() %>%
+  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
+                              Variable == "catches_total" ~ "Catches")) %>%
+  dplyr::select(Id = run_id,
+                Name = run_name,
+                Category = run_group, 
+                Year,
+                cow_Diff,
+                Variable) %>%
+  spread(Variable, cow_Diff)
+
+write.csv(all_results_global_cow_equivalent_table, paste0(results_dir, "all_results_global_cow_equivalent_table.csv"))
+
+all_results_regional_cow_equivalent_table <- plot_results %>%
+  dplyr::filter(Year %in% c(2050, end_year)) %>%
+  dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
+  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
+                                Variable == "catches_total" ~ "Catches")) %>%
+  mutate(abs_Diff = case_when(BAU != 0 ~ Reform-BAU,
+                              TRUE ~ 0),
+         cow_Diff = abs_Diff*cow_weight) %>%
+  dplyr::select(Id = run_id,
+                Name = run_name,
+                Category = run_group, 
+                Year,
+                Region,
+                cow_Diff,
+                Variable) %>%
+  spread(Variable, cow_Diff)
+
+write.csv(all_results_regional_cow_equivalent_table, paste0(results_dir, "all_results_regional_cow_equivalent_table.csv"))
+
+```

### 2020-10-14 app/00_initialize_app.R
friggen triple shapefile up

@@ -98,6 +98,10 @@ world_small_countries <- world  %>%
 # 2) EEZs/FAO regions ---
 eez_fao <- read_sf(dsn = "./data/shapefiles/eez-v10-fao-combined-simple", layer="eez_v10_fao_combined_simple") %>%
   mutate(eez_hs_code = ifelse(!is.na(zone), paste0("HS-",zone), as.character(mrgid)))
+
+eez_fao_triple <- read_sf(dsn = "./data/shapefiles/eez-fao-triplicate", layer="eez-fao-triplicate") %>%
+  rename(eez_hs_code = ez_hs_c) %>%
+  left_join(st_set_geometry(eez_fao, NULL), by = "eez_hs_code")
  
 # ### --------------------
 # ### Data ---------------

### 2020-10-14 app/data/duplicate_eez_fao_shapefile.R

@@ -1,0 +1,50 @@
+
+### The purpose of this script is to replicate the combined EEZ v10 and FAO region shapefile such that it is presented three times. 
+# New extent will be (-540, 540)
+
+library(sf)
+library(rmapshaper)
+library(mapview)
+library(tidyverse)
+
+eez_fao <- read_sf(dsn = "./app/data/shapefiles/eez-v10-fao-combined-simple", layer="eez_v10_fao_combined_simple") %>%
+  mutate(eez_hs_code = ifelse(!is.na(zone), paste0("HS-",zone), as.character(mrgid)))
+
+eez_fao_simple <- rmapshaper::ms_simplify(eez_fao, keep = 0.1, keep_shapes = T) %>%
+  st_set_crs(4326)
+
+# Make left duplicate (-540, -180)
+eez_fao_left <- (st_geometry(eez_fao_simple) - c(360, 0)) %>%
+  st_set_crs(4326)
+
+# Make right duplicate (180, 540)
+eez_fao_right <- (st_geometry(eez_fao_simple) + c(360, 0)) %>%
+  st_set_crs(4326)
+
+# Assign geometry
+eez_fao_left <- st_set_geometry(eez_fao_simple, eez_fao_left)
+eez_fao_right <- st_set_geometry(eez_fao_simple, eez_fao_right)
+
+# EEZ fao all <
+eez_fao_all <- eez_fao_simple %>%
+  rbind(eez_fao_left) %>% 
+  rbind(eez_fao_right) %>%
+  st_make_valid() %>%
+  group_by(eez_hs_code) %>%
+  summarize(a = 1) %>%
+  ungroup() %>%
+  dplyr::select(-a)
+
+# Keep only multipolygons
+eez_fao_polygon <- st_collection_extract(
+  eez_fao_all,
+  type = c("POLYGON"),
+  warn = FALSE
+)
+
+plot(eez_fao_polygon)
+
+st_write(eez_fao_polygon, paste0(here::here("app", "data", "shapefiles/"), "eez-fao-triplicate"),
+         layer = "eez-fao-triplicate",
+         driver = "ESRI Shapefile")
+

### 2020-10-14 app/data/shapefiles/duplicate_eez_fao_shapefile.R

@@ -1,0 +1,53 @@
+
+### The purpose of this script is to replicate the combined EEZ v10 and FAO region shapefile such that it is presented three times. 
+# New extent will be (-540, 540)
+
+library(sf)
+library(rmapshaper)
+library(mapview)
+library(tidyverse)
+
+eez_fao <- read_sf(dsn = "./app/data/shapefiles/eez-v10-fao-combined-simple", layer="eez_v10_fao_combined_simple") %>%
+  mutate(eez_hs_code = ifelse(!is.na(zone), paste0("HS-",zone), as.character(mrgid))) %>%
+  st_set_crs(4326)
+
+# eez_fao_simple <- rmapshaper::ms_simplify(eez_fao, keep = 0.1, keep_shapes = T) %>%
+#   st_set_crs(4326)
+#   
+
+# Make left duplicate (-540, -180)
+eez_fao_left <- (st_geometry(eez_fao) - c(360, 0)) %>%
+  st_set_crs(4326)
+
+# Make right duplicate (180, 540)
+eez_fao_right <- (st_geometry(eez_fao) + c(360, 0)) %>%
+  st_set_crs(4326)
+
+# Assign geometry
+eez_fao_left <- st_set_geometry(eez_fao, eez_fao_left)
+eez_fao_right <- st_set_geometry(eez_fao, eez_fao_right)
+
+# EEZ fao all <
+eez_fao_all <- eez_fao %>%
+  rbind(eez_fao_left) %>% 
+  rbind(eez_fao_right) %>%
+  st_make_valid() %>%
+  group_by(eez_hs_code) %>%
+  summarize(a = 1) %>%
+  ungroup() %>%
+  dplyr::select(-a)
+
+# Keep only multipolygons
+eez_fao_polygon <- st_collection_extract(
+  eez_fao_all,
+  type = c("POLYGON"),
+  warn = FALSE
+)
+
+#plot(eez_fao_polygon)
+
+st_write(eez_fao_polygon, paste0(here::here("app", "data", "shapefiles/"), "eez-fao-triplicate"),
+         layer = "eez-fao-triplicate",
+         overwrite = T,
+         driver = "ESRI Shapefile")
+

### 2020-10-14 app/server.R

@@ -2469,7 +2469,7 @@ shinyServer(function(input, output, session) {
     rv_global_fishing_footprint$data <- global_fishing_footprint_map_dat
     
     # Attach to polygons
-    global_fishing_footprint_map_dat_shp <- eez_fao %>%
+    global_fishing_footprint_map_dat_shp <- eez_fao_triple %>%
       left_join(global_fishing_footprint_map_dat, by = c("eez_hs_code" = "eez_hs_code")) %>%
       dplyr::filter(!is.na(fishing_KWh) & fishing_KWh > 0)
     

### 2020-10-14 scripts/07_proposals.Rmd
updating static result

@@
 # Threshold to be considered managed (using FMI scores)
-managed_cutoff <- 0.75
+managed_cutoff <- 0.5
 
@@
             abs_Diff_tot = case_when(BAU_tot != 0 ~ Reform_tot-BAU_tot,
-                                     TRUE ~ 0),
-            cow_Diff = abs_Diff_tot*cow_weight) %>%
+                                     TRUE ~ 0)) %>%
   ungroup() %>%
@@
   mutate(abs_Diff = case_when(BAU != 0 ~ Reform-BAU,
-                              TRUE ~ 0),
-         cow_Diff = abs_Diff*cow_weight) %>%
+                              TRUE ~ 0)) %>%
   dplyr::select(Id = run_id,

### 2020-10-14 app/server.R
fixing plot download

@@ -2476,6 +2476,14 @@ shinyServer(function(input, output, session) {
     # Update reactive data container
     rv_global_fishing_footprint$polygons <- global_fishing_footprint_map_dat_shp
     
+    # Make static version for the print map
+    global_fishing_footprint_map_dat_static_shp <- eez_fao %>%
+      left_join(global_fishing_footprint_map_dat, by = c("eez_hs_code" = "eez_hs_code")) %>%
+      dplyr::filter(!is.na(fishing_KWh) & fishing_KWh > 0)
+    
+    # Update reactive data container
+    rv_global_fishing_footprint$polygons_static <- global_fishing_footprint_map_dat_static_shp
+    
     # Create hover text
     global_fishing_footprint_map_text <- paste0(
       "<b>","Location: ","</b>", global_fishing_footprint_map_dat_shp$name,"</b>",
@@ -2556,7 +2564,7 @@ shinyServer(function(input, output, session) {
       world_mollweide <- st_transform(world, crs = "+proj=moll")
       
       # Reproject data
-      footprint_data_mollweide <- st_transform(rv_global_fishing_footprint$polygons, crs = "+proj=moll")
+      footprint_data_mollweide <- st_transform(rv_global_fishing_footprint$polygons_static, crs = "+proj=moll")
       
       # Get title, subtitle, and caption
       title <- paste0(text$item_label[text$item_id == "global-fishing-footprint"])
@@ -2567,7 +2575,7 @@ shinyServer(function(input, output, session) {
       global_fishing_footprint_map_static <- ggplot()+
         geom_sf(data = world_mollweide, fill = "white", color = "grey", size = 0.25)+
         geom_sf(data = footprint_data_mollweide, aes(fill = log10(fishing_KWh)), lwd = 0.3)+
-        scale_fill_gradientn(colors = brewer.pal(9, "YlOrRd"),
+        scale_fill_gradientn(colors = rev(brewer.pal(9, "RdYlBu")),
                              limits = limits,
                              breaks = breaks,
                              labels = scales::comma(labels))+

### 2020-10-15 scripts/01_data_wrangling.Rmd
formatting and country profile minor edits

@@
   inner_join(fao_area_lookup, by = c("fishing_area" = "area")) %>%
+  dplyr::filter(fishing_area > 10) %>% # remove inland fishing
   group_by(iso3, year, species, fishing_area) %>%

### 2020-10-15 app/server.R

@@ -68,6 +68,11 @@ shinyServer(function(input, output, session) {
   ### 01. Introduction/Sidebar ---
   ### ----------------------------
   
+  ### Navigation button on the top header
+  observeEvent(input$ab_subsidy_explorer, {
+    updateTabItems(session, "menu_items", "introduction")
+  })
+  
   ### Navigation buttons on the intro page ----
   
   # Navigation button from introduction to selected-results
@@ -293,9 +298,9 @@ shinyServer(function(input, output, session) {
       
       req(rv_selected_proposal$proposal != "Default")
       
-      paste0("<b class = 'big'>", "Formal Title: ", "</b>", selected_policy$title, "</br>",
-             "<b class = 'big'>", "Summary: ", "</b>", selected_policy$summary, "</br>",
-             "<b class = 'big'>", "Modeling Assumptions: ", "</b>", selected_policy$model_details_assumptions) %>%
+      paste0("<b class = 'big'>", "Formal Title ", "</b></br>", selected_policy$title, "</br></br>",
+             "<b class = 'big'>", "Summary ", "</b></br>", selected_policy$summary, "</br></br>",
+             "<b class = 'big'>", "Modeling Assumptions ", "</b></br>", selected_policy$model_details_assumptions) %>%
         lapply(htmltools::HTML)
       
     })
@@ -1697,6 +1702,8 @@ shinyServer(function(input, output, session) {
     # Update reactive container
     rv_country_fishery_stats$pop_data <- country_fishery_stats_pop_plot_dat
     
+    max_pop <- max(country_fishery_stats_pop_plot_dat$value)/1e6 + (max(country_fishery_stats_pop_plot_dat$value)*0.1)/1e6
+    
     # Make population plot
     country_fishery_stats_pop_plot <- ggplot(country_fishery_stats_pop_plot_dat)+
       aes(x = year, y = value/1e6)+
@@ -1706,7 +1713,8 @@ shinyServer(function(input, output, session) {
                                    "<b>", "Population: ", "</b>", format(round(value,0), big.mark = ",", scientific = F))),
                  alpha = 0, color = totColor)+
       scale_y_continuous(name = "Population (million persons)",
-                         labels = function(x) format(x, big.mark = ",", decimal.mark = ".", scientific = FALSE))+
+                         labels = function(x) format(x, big.mark = ",", decimal.mark = ".", scientific = FALSE),
+                         limits = c(0,max_pop))+
[…]

### 2020-10-15 app/ui.R

@@ -94,7 +94,10 @@ shinyUI(
             tags$li(
                 id = "custom-title-container",
                 class = "dropdown",
-                tags$h3(text$item_label[text$item_id == "app-title"]) # /h3
+                tags$button(id = "ab_subsidy_explorer",
+                            tags$h3(text$item_label[text$item_id == "app-title"],
+                                    style = "margin: 0;"),
+                            class = "btn action-button") # /h3
             ), # /tags$li
             
             # SFG logo

### 2020-10-15 app/ui_01_introduction.R

@@ -9,7 +9,7 @@ Introduction = function()
   fluidPage(
     
     # page style
-    style = "color: #ffffff; padding-bottom: 40px;",
+    style = "color: #ffffff; padding-bottom: 40px; background-color: var(--main-color);",
             
     # open links in new window
     tags$head(tags$base(target = "_blank")),

### 2021-10-19 scripts/05_subsidy_reform_definitions.Rmd
subs affected for Anthony

@@
 
-title: "SubsidyExplorer - Step 4: Apply proposal 'definitions' to vessel list"
+title: "SubsidyExplorer - Step 5: Apply proposal 'definitions' to vessel list"
 author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"

### 2021-10-19 scripts/06_run_model.Rmd
running another mgmt threshold for comparison
updating static result
subs affected for Anthony

@@
 
-This script generates alternative global and regional results.
+This script generates the most ambitious global and regional results obtained by removing all capacity enhancing subsidies from all WTO Members and Observers.
+This is effectively the reference case scenario for our model, which will be used later as a benchmark to which we can compare the results of specific proposals.
 

### 2021-10-19 scripts/07_proposals.Rmd
subs affected for Anthony

@@
 
-title: "SubsidyExplorer - Step 6: Run Model"
+title: "SubsidyExplorer - Step 7: Pre-Populated Proposals"
 author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"

### 2021-10-19 scripts/08_subs_affected.Rmd
subs affected for Anthony

---
output:
  html_document: default

title: "SubsidyExplorer - Step 8: Subsidies affected by discipline type"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
bibliography: "../pew-subsidies.bib"
---
# Introduction

This script outputs the amounts of subsidies affected by each discipline type (and/or definition) in SubsidyExplorer. This was requested by Anthony to aid in his analyses.

```{r setup, include=FALSE}
# Load packages
library(knitr) 
library(tidyverse)

knitr::opts_chunk$set(echo = TRUE)

make_plots <- T

if(make_plots){
  library(RColorBrewer)
  library(scales)
}

# Directories for the output files generated by this script
results_dir <- paste0(here::here("results", "08-subs-affected/"))
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}

good_subsidy_types <- c("A1", "A2", "A3")
bad_subsidy_types <- c("B1", "B2", "B3", "B4", "B5", "B6", "B7")
ugly_subsidy_types <- c("C1", "C2", "C3")
```

```{r}
# Load vessel list
vessel_dat <- read.csv(here::here("app", "data", "vessel_list_2018_final.csv"), stringsAsFactors = F)

# Create high seas code
vessel_dat <- vessel_dat %>%
  mutate(eez_hs_code = case_when(eez_id == 0 ~ paste0("HS-", fao_region),
                                 TRUE ~ as.character(eez_id)))

```

# IUU

We really only have data on one measure of IUU fishing - vessels identified as IUU from RFMO lists. We do also have subsidies going to vessels that have ever fished in a disputed area flagged.

```{r}
iuu_cols <- paste0(c(good_subsidy_types, bad_subsidy_types, ugly_subsidy_types), "_subs")

subs_affected_iuu <- vessel_dat %>%
  group_by(iuu1) %>%
  summarize(across(iuu_cols, ~ sum(.x, na.rm = T))) %>%
  mutate(description = "IUU - RFMO Lists") %>%
  relocate(description) %>%
  rename(affected = iuu1)

subs_affected_disputed <- vessel_dat %>%
  group_by(is_disputed) %>%
  summarize(across(iuu_cols, ~ sum(.x, na.rm = T))) %>%
  mutate(description = "IUU - Disputed Area") %>%
  relocate(description) %>%
  rename(affected = is_disputed)

subs_affected_iuu_out <- subs_affected_iuu %>%
  bind_rows(subs_affected_disputed)

write_csv(subs_affected_iuu_out, paste0(results_dir, "subs_affected_iuu_out.csv"))
```

# Overfished

Here we could consider multiple metrics... Let's stick with the four from the tool for now, but provide alternative methods (mean/median/weighted mean)

```{r}
oa_cols <- paste0(c(good_subsidy_types, bad_subsidy_types, ugly_subsidy_types), "_subs")

subs_affected_oa1_median <- vessel_dat %>%
  group_by(oa1_median) %>%
  summarize(across(oa_cols, ~ sum(.x, na.rm = T))) %>%
  mutate(description = "Overfished - Median BvBmsy < 1 (RAM stocks only)") %>%
  relocate(description) %>%
  rename(affected = oa1_median)

subs_affected_oa1_w_mean <- vessel_dat %>%
  group_by(oa1_w_mean) %>%
  summarize(across(oa_cols, ~ sum(.x, na.rm = T))) %>%
  mutate(description = "Overfished - Weighted Mean BvBmsy < 1 (RAM stocks only)") %>%
  relocate(description) %>%
  rename(affected = oa1_w_mean)

subs_affected_oa2_median <- vessel_dat %>%
  group_by(oa2_median) %>%
  summarize(across(oa_cols, ~ sum(.x, na.rm = T))) %>%
  mutate(description = "Overfished - Median BvBmsy < 0.8 (RAM stocks only)") %>%
  relocate(description) %>%
  rename(affected = oa2_median)

subs_affected_oa2_w_mean <- vessel_dat %>%
  group_by(oa2_w_mean) %>%
  summarize(across(oa_cols, ~ sum(.x, na.rm = T))) %>%
  mutate(description = "Overfished - Weighted Mean BvBmsy < 0.8 (RAM stocks only)") %>%
  relocate(description) %>%
  rename(affected = oa2_w_mean)

subs_affected_oa3_median <- vessel_dat %>%
  group_by(oa3_median) %>%
  summarize(across(oa_cols, ~ sum(.x, na.rm = T))) %>%
  mutate(description = "Overfished - Median BvBmsy < 1 (All Costello et al. 2016 stocks)") %>%
  relocate(description) %>%
  rename(affected = oa3_median)

subs_affected_oa3_w_mean <- vessel_dat %>%
  group_by(oa3_w_mean) %>%
  summarize(across(oa_cols, ~ sum(.x, na.rm = T))) %>%
  mutate(description = "Overfished - Weighted Mean BvBmsy < 1 (All Costello et al. 2016 stocks)") %>%
  relocate(description) %>%
  rename(affected = oa3_w_mean)

subs_affected_oa4_median <- vessel_dat %>%
  group_by(oa4_median) %>%
  summarize(across(oa_cols, ~ sum(.x, na.rm = T))) %>%
  mutate(description = "Overfished - Median BvBmsy < 0.8 (All Costello et al. 2016 stocks)") %>%
  relocate(description) %>%
  rename(affected = oa4_median)

subs_affected_oa4_w_mean <- vessel_dat %>%
  group_by(oa4_w_mean) %>%
  summarize(across(oa_cols, ~ sum(.x, na.rm = T))) %>%
  mutate(description = "Overfished - Weighted Mean BvBmsy < 0.8 (All Costello et al. 2016 stocks)") %>%
  relocate(description) %>%
  rename(affected = oa4_w_mean)

subs_affected_oa_out <- subs_affected_oa1_median %>%
  bind_rows(subs_affected_oa1_w_mean) %>%
  bind_rows(subs_affected_oa2_median) %>%
  bind_rows(subs_affected_oa2_w_mean) %>%
  bind_rows(subs_affected_oa3_median) %>%
  bind_rows(subs_affected_oa3_w_mean) %>%
  bind_rows(subs_affected_oa4_median) %>%
  bind_rows(subs_affected_oa4_w_mean)

write_csv(subs_affected_oa_out, paste0(results_dir, "subs_affected_overfished_out.csv"))
```

### 2021-10-21 scripts/08_subs_affected.Rmd
mgmt implications of chair's text

@@
 
-This script outputs the amounts of subsidies affected by each discipline type (and/or definition) in SubsidyExplorer. This was requested by Anthony to aid in his analyses.
+This script outputs the amounts of subsidies affected by each discipline type (and/or definition) in SubsidyExplorer. This was requested by Anthony Rogers to aid in his analyses for Pew.
 
@@
 write_csv(subs_affected_iuu_out, paste0(results_dir, "subs_affected_iuu_out.csv"))
+
+# Now do the same by country
+subs_affected_flag_iuu <- vessel_dat %>%
+  group_by(iuu1, flag_iso3) %>%
+  summarize(across(iuu_cols, ~ sum(.x, na.rm = T))) %>%
+  mutate(description = "IUU - RFMO Lists") %>%
+  relocate(description) %>%
+  rename(affected = iuu1) %>%
+  arrange(flag_iso3)
+
+subs_affected_flag_disputed <- vessel_dat %>%
+  group_by(is_disputed, flag_iso3) %>%
+  summarize(across(iuu_cols, ~ sum(.x, na.rm = T))) %>%
+  mutate(description = "IUU - Disputed Area") %>%
+  relocate(description) %>%
+  rename(affected = is_disputed) %>%
+  arrange(flag_iso3)
+
+subs_affected_flag_iuu_out <- subs_affected_flag_iuu %>%
+  bind_rows(subs_affected_flag_disputed)
+
+write_csv(subs_affected_flag_iuu_out, paste0(results_dir, "subs_affected_flag_iuu_out.csv"))
 ```
@@
 ```
+
+```{r}
+subs_affected_flag_oa1_median <- vessel_dat %>%
+  group_by(oa1_median, flag_iso3) %>%
+  summarize(across(oa_cols, ~ sum(.x, na.rm = T))) %>%
+  mutate(description = "Overfished - Median BvBmsy < 1 (RAM stocks only)") %>%
+  relocate(description) %>%
+  rename(affected = oa1_median) %>%
+  arrange(flag_iso3)
+
+subs_affected_flag_oa1_w_mean <- vessel_dat %>%
+  group_by(oa1_w_mean, flag_iso3) %>%
+  summarize(across(oa_cols, ~ sum(.x, na.rm = T))) %>%
+  mutate(description = "Overfished - Weighted Mean BvBmsy < 1 (RAM stocks only)") %>%
+  relocate(description) %>%
+  rename(affected = oa1_w_mean) %>%
+  arrange(flag_iso3)
+
+subs_affected_flag_oa2_median <- vessel_dat %>%
+  group_by(oa2_median, flag_iso3) %>%
+  summarize(across(oa_cols, ~ sum(.x, na.rm = T))) %>%
+  mutate(description = "Overfished - Median BvBmsy < 0.8 (RAM stocks only)") %>%
+  relocate(description) %>%
+  rename(affected = oa2_median) %>%
+  arrange(flag_iso3)
+
+subs_affected_flag_oa2_w_mean <- vessel_dat %>%
+  group_by(oa2_w_mean, flag_iso3) %>%
+  summarize(across(oa_cols, ~ sum(.x, na.rm = T))) %>%
+  mutate(description = "Overfished - Weighted Mean BvBmsy < 0.8 (RAM stocks only)") %>%
+  relocate(description) %>%
+  rename(affected = oa2_w_mean) %>%
+  arrange(flag_iso3)
+
+subs_affected_flag_oa3_median <- vessel_dat %>%
+  group_by(oa3_median, flag_iso3) %>%
+  summarize(across(oa_cols, ~ sum(.x, na.rm = T))) %>%
+  mutate(description = "Overfished - Median BvBmsy < 1 (All Costello et al. 2016 stocks)") %>%
+  relocate(description) %>%
+  rename(affected = oa3_median) %>%
+  arrange(flag_iso3)
+
+subs_affected_flag_oa3_w_mean <- vessel_dat %>%
+  group_by(oa3_w_mean, flag_iso3) %>%
+  summarize(across(oa_cols, ~ sum(.x, na.rm = T))) %>%
+  mutate(description = "Overfished - Weighted Mean BvBmsy < 1 (All Costello et al. 2016 stocks)") %>%
+  relocate(description) %>%
+  rename(affected = oa3_w_mean) %>%
+  arrange(flag_iso3)
+
+subs_affected_flag_oa4_median <- vessel_dat %>%
+  group_by(oa4_median, flag_iso3) %>%
+  summarize(across(oa_cols, ~ sum(.x, na.rm = T))) %>%
+  mutate(description = "Overfished - Median BvBmsy < 0.8 (All Costello et al. 2016 stocks)") %>%
+  relocate(description) %>%
+  rename(affected = oa4_median) %>%
+  arrange(flag_iso3)
+
+subs_affected_flag_oa4_w_mean <- vessel_dat %>%
+  group_by(oa4_w_mean, flag_iso3) %>%
+  summarize(across(oa_cols, ~ sum(.x, na.rm = T))) %>%
+  mutate(description = "Overfished - Weighted Mean BvBmsy < 0.8 (All Costello et al. 2016 stocks)") %>%
+  relocate(description) %>%
+  rename(affected = oa4_w_mean) %>%
+  arrange(flag_iso3)
+
+subs_affected_flag_oa_out <- subs_affected_flag_oa1_median %>%
+  bind_rows(subs_affected_flag_oa1_w_mean) %>%
+  bind_rows(subs_affected_flag_oa2_median) %>%
+  bind_rows(subs_affected_flag_oa2_w_mean) %>%
+  bind_rows(subs_affected_flag_oa3_median) %>%
+  bind_rows(subs_affected_flag_oa3_w_mean) %>%
+  bind_rows(subs_affected_flag_oa4_median) %>%
+  bind_rows(subs_affected_flag_oa4_w_mean)
+
+write_csv(subs_affected_flag_oa_out, paste0(results_dir, "subs_affected_flag_overfished_out.csv"))
+```

### 2021-10-21 scripts/09_chairs_text_mgmt.Rmd
mgmt implications of chair's text

--- 2020-10-14 scripts/07_proposals.Rmd
@@
 
-title: "SubsidyExplorer - Step 6: Run Model"
+title: "SubsidyExplorer - Step 9: New Chair's text - management assumptions"
 author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
@@
 
-This script generates the most ambitious global and regional results obtained by removing all capacity enhancing subsidies from all WTO Members and Observers.
+This script explores a couple of different assumptions regarding the exception in the newest Chair's text
 
@@
 
+# End year for projections
 end_year <- 2080
@@
 # Directories for the output files generated by this script
-results_dir <- paste0(here::here("results", "07-proposals/"), "mgmt_threshold_", managed_cutoff, "/")
+results_dir <- paste0(here::here("results", "09-chairs-text-mgmt/"), "mgmt_threshold_", managed_cutoff, "/")
 if (dir.exists(results_dir) == F) {
@@
 # Proposal settings
-proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings.csv"), stringsAsFactors = F)
+proposal_settings <- read.csv(here::here("data", "lookup-tables", "chairs_text_proposal_settings.csv"), stringsAsFactors = F)
 
@@
 proposal_results <- NULL
+affected_subs <- NULL
 
@@
 
-    # Make list
+    # # Summarize fleet breakdown by country and save
+    fleet_summary_country <- fleet$vessels %>%
+      group_by(flag_iso3, development_status) %>%
+      summarize(all_subs = sum(bad_ugly_subs, na.rm = T), removed_subs = sum(removed_subs, na.rm = T)) %>%
+      ungroup() %>%
+      mutate(percent_removed = round(case_when(all_subs == 0 ~ 0,
+                                      TRUE ~ (removed_subs/all_subs)*100), 2)) %>%
+      mutate(run_id = proposal_name,
+             run_name = names(proposal_name),
+             run_group = unique(proposal_settings$category[proposal_settings$proposal == proposal_name]))
+
+    # Make fleet list for model
     fleet_list <- fleet$summary %>%
@@
 
-    # Add to data frame
+    # Add to data frames
       proposal_results <- proposal_results %>%
         bind_rows(results_all)
+
+      affected_subs <- affected_subs %>%
+        bind_rows(fleet_summary_country)
 
@@
                 Variable) %>%
-  spread(Variable, Diff_tot)
+  spread(Variable, Diff_tot) %>%
+  arrange(Year)
 
@@
 
-# Get rounded end values
-global_biomass_2050 <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == 2050 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
-global_biomass_end <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
-
-global_catches_2050 <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == 2050 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
-global_catches_end <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
+# # Get rounded end values
+# global_biomass_2050 <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == 2050 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
+# global_biomass_end <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
+# 
+# global_catches_2050 <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == 2050 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
+# global_catches_end <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
 
@@
                 Variable) %>%
-  spread(Variable, Diff)
+  spread(Variable, Diff) %>%
+  arrange(Year, Region)
 
@@
 ```{r}
-all_results_global_absolute_table <- plot_results %>%
-  dplyr::filter(Year %in% c(2050, end_year)) %>%
-  dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
-  group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
-  summarize(BAU_tot = sum(BAU, na.rm = T),
-            Reform_tot = sum(Reform, na.rm = T),
-            abs_Diff_tot = case_when(BAU_tot != 0 ~ Reform_tot-BAU_tot,
-                                     TRUE ~ 0)) %>%
-  ungroup() %>%
-  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
-                              Variable == "catches_total" ~ "Catches")) %>%
-  dplyr::select(Id = run_id,
-                Name = run_name,
-                Category = run_group, 
-                Year,
-                abs_Diff_tot,
-                Variable) %>%
-  spread(Variable, abs_Diff_tot)
-
-write.csv(all_results_global_absolute_table, paste0(results_dir, "all_results_global_absolute_table.csv"))
-
-all_results_regional_absolute_table <- plot_results %>%
-  dplyr::filter(Year %in% c(2050, end_year)) %>%
-  dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
-  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
-                                Variable == "catches_total" ~ "Catches")) %>%
-  mutate(abs_Diff = case_when(BAU != 0 ~ Reform-BAU,
-                              TRUE ~ 0)) %>%
-  dplyr::select(Id = run_id,
-                Name = run_name,
-                Category = run_group, 
-                Year,
-                Region,
-                abs_Diff,
-                Variable) %>%
-  spread(Variable, abs_Diff)
-
-write.csv(all_results_regional_absolute_table, paste0(results_dir, "all_results_regional_absolute_table.csv"))
+# all_results_global_absolute_table <- plot_results %>%
+#   dplyr::filter(Year %in% c(2050, end_year)) %>%
+#   dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
+#   group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
+#   summarize(BAU_tot = sum(BAU, na.rm = T),
+#             Reform_tot = sum(Reform, na.rm = T),
+#             abs_Diff_tot = case_when(BAU_tot != 0 ~ Reform_tot-BAU_tot,
+#                                      TRUE ~ 0)) %>%
+#   ungroup() %>%
+#   mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
+#                               Variable == "catches_total" ~ "Catches")) %>%
+#   dplyr::select(Id = run_id,
+#                 Name = run_name,
+#                 Category = run_group, 
+#                 Year,
+#                 abs_Diff_tot,
+#                 Variable) %>%
+#   spread(Variable, abs_Diff_tot)
+# 
+# write.csv(all_results_global_absolute_table, paste0(results_dir, "all_results_global_absolute_table.csv"))
+# 
+# all_results_regional_absolute_table <- plot_results %>%
+#   dplyr::filter(Year %in% c(2050, end_year)) %>%
+#   dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
+#   mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
+#                                 Variable == "catches_total" ~ "Catches")) %>%
+#   mutate(abs_Diff = case_when(BAU != 0 ~ Reform-BAU,
+#                               TRUE ~ 0)) %>%
+#   dplyr::select(Id = run_id,
+#                 Name = run_name,
+#                 Category = run_group, 
+#                 Year,
+#                 Region,
+#                 abs_Diff,
+#                 Variable) %>%
+#   spread(Variable, abs_Diff)
+# 
+# write.csv(all_results_regional_absolute_table, paste0(results_dir, "all_results_regional_absolute_table.csv"))
 ```
@@
 # Weight of a mature dairy cow in mt
-cow_weight <- 0.6803886
-
-all_results_global_cow_equivalent_table <- plot_results %>%
-  dplyr::filter(Year %in% c(2050, end_year)) %>%
-  dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
-  group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
-  summarize(BAU_tot = sum(BAU, na.rm = T),
-            Reform_tot = sum(Reform, na.rm = T),
-            abs_Diff_tot = case_when(BAU_tot != 0 ~ Reform_tot-BAU_tot,
-                                     TRUE ~ 0),
-            cow_Diff = abs_Diff_tot*cow_weight) %>%
-  ungroup() %>%
-  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
-                              Variable == "catches_total" ~ "Catches")) %>%
-  dplyr::select(Id = run_id,
-                Name = run_name,
-                Category = run_group, 
-                Year,
-                cow_Diff,
-                Variable) %>%
-  spread(Variable, cow_Diff)
-
-write.csv(all_results_global_cow_equivalent_table, paste0(results_dir, "all_results_global_cow_equivalent_table.csv"))
-
-all_results_regional_cow_equivalent_table <- plot_results %>%
-  dplyr::filter(Year %in% c(2050, end_year)) %>%
-  dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
-  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
-                                Variable == "catches_total" ~ "Catches")) %>%
-  mutate(abs_Diff = case_when(BAU != 0 ~ Reform-BAU,
-                              TRUE ~ 0),
-         cow_Diff = abs_Diff*cow_weight) %>%
-  dplyr::select(Id = run_id,
-                Name = run_name,
-                Category = run_group, 
-                Year,
-                Region,
-                cow_Diff,
-                Variable) %>%
-  spread(Variable, cow_Diff)
-
-write.csv(all_results_regional_cow_equivalent_table, paste0(results_dir, "all_results_regional_cow_equivalent_table.csv"))
+# cow_weight <- 0.6803886
+# 
+# all_results_global_cow_equivalent_table <- plot_results %>%
+#   dplyr::filter(Year %in% c(2050, end_year)) %>%
+#   dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
+#   group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
+#   summarize(BAU_tot = sum(BAU, na.rm = T),
+#             Reform_tot = sum(Reform, na.rm = T),
+#             abs_Diff_tot = case_when(BAU_tot != 0 ~ Reform_tot-BAU_tot,
+#                                      TRUE ~ 0),
+#             cow_Diff = abs_Diff_tot*cow_weight) %>%
+#   ungroup() %>%
+#   mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
+#                               Variable == "catches_total" ~ "Catches")) %>%
+#   dplyr::select(Id = run_id,
+#                 Name = run_name,
+#                 Category = run_group, 
+#                 Year,
+#                 cow_Diff,
+#                 Variable) %>%
+#   spread(Variable, cow_Diff)
+# 
+# write.csv(all_results_global_cow_equivalent_table, paste0(results_dir, "all_results_global_cow_equivalent_table.csv"))
+# 
+# all_results_regional_cow_equivalent_table <- plot_results %>%
+#   dplyr::filter(Year %in% c(2050, end_year)) %>%
+#   dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
+#   mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
+#                                 Variable == "catches_total" ~ "Catches")) %>%
+#   mutate(abs_Diff = case_when(BAU != 0 ~ Reform-BAU,
+#                               TRUE ~ 0),
+#          cow_Diff = abs_Diff*cow_weight) %>%
+#   dplyr::select(Id = run_id,
+#                 Name = run_name,
+#                 Category = run_group, 
+#                 Year,
+#                 Region,
+#                 cow_Diff,
+#                 Variable) %>%
+#   spread(Variable, cow_Diff)
+# 
+# write.csv(all_results_regional_cow_equivalent_table, paste0(results_dir, "all_results_regional_cow_equivalent_table.csv"))
 
 ```
+
+## Save Percent Affected Subs by Country
+
+```{r}
+affected_subs <- affected_subs %>%
+  arrange(flag_iso3, run_id) %>%
+  dplyr::select(-all_subs, -removed_subs)
+
+write.csv(affected_subs, paste0(results_dir, "percent_subs_removed_by_country.csv"))
+```

### 2021-10-21 app/scripts/CreateFleets.R

@@ -896,7 +896,7 @@ CreateFleets <- function(vessel_list,
         overcap_vessels_scope <- overcap_vessels_scope %>%
           dplyr::filter(!is_territorial)
         
-        # 3) Only those coming from the top XX worst subsidizers are within scope  
+        # 3) Only those coming from the top 10 worst subsidizers are within scope  
       }else if("SUB" %in% overcap$scope_select){
         
         # Country ranking subsidies 
@@ -1080,7 +1080,14 @@ CreateFleets <- function(vessel_list,
         overcap_vessels_scope <- overcap_vessels_scope %>%
           dplyr::filter(engine_power_kw >= overcap$engine_cutoff)
         
-      }
+      # 11) Distant water fishing OR HIGH SEAS (for all vessels) plus all fishing by OA vessels    
+      }else if("OUT/OA" %in% overcap$scope_select & !is.na(overcap$hs_cutoff)){
+      
+        # Filter for high seas OR distant water fishing only
+        overcap_vessels_scope <- overcap_vessels_scope %>%
+          dplyr::filter(fmi_best < managed_threshold | distant_water | prop_fishing_KWh_high_seas >= (overcap$hs_cutoff/100))
+        
+    }
       
     } # /SELECT
     
@@ -1101,7 +1108,7 @@ CreateFleets <- function(vessel_list,
     ### Vessel list for S&DT
     overcap_vessels_sdt <- vessel_subset %>%
       right_join(overcap_vessels_scope, by = c("ssvid", "region", "fao_region", "eez_id", "is_territorial"))
-  
+    
   ### 1) LDC S&DT ---
   
   if(overcap$sdt_ldc == "YES"){
@@ -1132,12 +1139,6 @@ CreateFleets <- function(vessel_list,
       overcap_vessels_sdt_ldc <- overcap_vessels_sdt_ldc %>%
         dplyr::filter(prop_fishing_KWh_high_seas >= (overcap$sdt_hs_cutoff_ldc/100))
       
-    }else if("TIME" %in% overcap$sdt_what_ldc){
-      
-      #################
-      # XXX: NEED TO DO 
-      #################
-      
     }
     
   }else{
@@ -1167,7 +1168,7 @@ CreateFleets <- function(vessel_list,
     }else if("TER" %in% overcap$sdt_what_developing){
       
       # Exempt vessels fishing in territorial waters
-      overcap_vessels_sdt_ldc <- overcap_vessels_sdt_ldc %>%
[…]

### 2021-10-22 scripts/07_proposals.Rmd
rerun for all proposals. new fig 5 finalized

@@
 # Proposal settings
-proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings.csv"), stringsAsFactors = F)
+#proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings.csv"), stringsAsFactors = F)
+proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_v2.csv"), stringsAsFactors = F)
 
@@
   mutate(display_name = case_when(proposal == "Default" ~ "None",
-                                  TRUE ~ paste0(title_tool, " (", proposal, ")"))) %>%
+                                  TRUE ~ title_tool)) %>%
   dplyr::select(category, proposal, display_name) %>%
   arrange(category) %>%
-  dplyr::filter(!(proposal %in% c("RD/TN/RL/126", "RD/TN/RL/119"))) # remove blank entries for tool
+  dplyr::filter(!(proposal %in% c("RD/TN/RL/126/Rev.2", "RD/TN/RL/119/Rev.1"))) # remove blank entries for tool
 
@@
 plot_results <- proposal_results %>%
-  dplyr::filter(run_id != "RD/TN/RL/103") %>%
+  #dplyr::filter(run_id != "RD/TN/RL/103") %>%
   bind_rows(most_ambitious_results)
@@
                                             plot_width = 8,
-                                            plot_height = 8,
+                                            plot_height = 6,
                                             results_dir = results_dir,
@@
                                             plot_name = "all_proposals_2050_plot",
-                                            plot_width = 8,
-                                            plot_height = 8,
+                                            plot_width = 7.5,
+                                            plot_height = 4,
                                             results_dir = results_dir,
@@
 
-## Extract 2060 and end year results for all proposals and save as nice tables
+```{r}
+  # A) global (aggregated) "kobe" final year plot
+  box_2050_plot <- BioEconomicModelPlots(dat = plot_results,
+                                            spatial_res = "global",
+                                            temporal_res = "last",
+                                            end_year = 2050,
+                                            plot_name = "box_scenario_type_2050_plot",
+                                            plot_width = 7.5,
+                                            plot_height = 6,
+                                            results_dir = results_dir,
+                                            group_var = "run_group",
+                                            color_var = "run_group",
+                                            legend_pos_manual = "bottom",
+                                            legend_name = "Scenario Type",
+                                            plot_type = "box")
+
+figure_5 <- cowplot::plot_grid(box_2050_plot, compare_2050_plot, ncol = 1, rel_heights = c(1,0.75), axis = "lr", align = "v", labels = c("(A)", "(B)"), hjust = -1)
+ggsave(paste0(results_dir, "Fig5.tiff"), figure_5, width = 7.5, height = 8)
+
+```
+
+## Extract 2050 and end year results for all proposals and save as nice tables
 
@@
 write.csv(all_results_global_output_table, paste0(results_dir, "all_results_global_output_table.csv"))
+
+# Now make a pretty version for 2050 only
+all_results_global_output_table_2050_pretty <- all_results_global_output_table %>%
+  dplyr::filter(Year == 2050) %>%
+  ungroup() %>%
+  arrange(Category, desc(Biomass)) %>%
+  mutate(Biomass = round(Biomass*100, 3),
+         Catches = round(Catches*100, 3),
+         Revenue = round(Revenue*100, 3),
+         `Fishing Mortality` = round(`Fishing Mortality`*100, 3))
+
+write.csv(all_results_global_output_table_2050_pretty, paste0(results_dir, "all_results_global_output_table_2050_pretty.csv"))
 
@@
 write.csv(all_results_regional_output_table, paste0(results_dir, "all_results_regional_output_table.csv"))
+
+# Now make a pretty version for 2050 only
+all_results_regional_output_table_2050_pretty <- all_results_regional_output_table %>%
+  dplyr::filter(Year == 2050) %>%
+  ungroup() %>%
+  arrange(Region, Category, desc(Biomass)) %>%
+  mutate(Biomass = round(Biomass*100, 3),
+         Catches = round(Catches*100, 3),
+         Revenue = round(Revenue*100, 3),
+         `Fishing Mortality` = round(`Fishing Mortality`*100, 3))
+
+write.csv(all_results_regional_output_table_2050_pretty, paste0(results_dir, "all_results_regional_output_table_2050_pretty.csv"))
 ```

### 2021-10-22 scripts/functions/BioEconomicModelPlots.R

@@ -17,7 +17,8 @@ BioEconomicModelPlots <- function(dat,
                                   color_var = "run_group",
                                   size_var = "Mortality",
                                   legend_pos_manual = "none",
-                                  legend_name = ""){
+                                  legend_name = "",
+                                  plot_type = "point"){
   
   ### General theme
   plot_theme <- theme_linedraw()+
@@ -76,24 +77,23 @@ BioEconomicModelPlots <- function(dat,
       labs(x = "Year", y = "Change relative to BAU (%)", color = legend_name)+
       plot_theme +
       theme(legend.position = legend_pos_manual)+
-      facet_grid(Fleet+Variable~Region)
+      facet_grid(Variable~Region)
     
   }else if(temporal_res == "last"){
     
-    plot_dat <- plot_dat %>%
-      dplyr::filter(Year == end_year) %>%
-      group_by(Year, Variable, Fleet, Region, run_id, run_name, run_group) %>%
-      summarize(Value = unique(Diff_tot)) %>%
-      ungroup() %>%
-      spread(Variable, Value)
+    if(plot_type == "point"){
+      
+      plot_dat <- plot_dat %>%
+        dplyr::filter(Year == end_year) %>%
+        group_by(Year, Variable, Fleet, Region, run_id, run_name, run_group) %>%
+        summarize(Value = unique(Diff_tot)) %>%
+        ungroup() %>%
+        spread(Variable, Value)
     
     x_limits <- c(min(0,plyr::round_any(min(plot_dat$Biomass), 0.05, f = floor)), 
                   plyr::round_any(max(plot_dat$Biomass), 0.05, f = ceiling))
-    y_limits <- c(min(0,plyr::round_any(min(plot_dat$Catches), 0.05, f = floor)), 
+    y_limits <- c(min(0,plyr::round_any(min(plot_dat$Catches), 0.01, f = floor)), 
                   plyr::round_any(max(plot_dat$Catches), 0.05, f = ceiling))
-  
-    # size_limits <- c(min(0,plyr::round_any(min(plot_dat$`eRevenue`), 0.01, f = floor)), 
-    #                 plyr::round_any(max(plot_dat$Revenue), 0.01, f = ceiling))
     
     plot <- plot_dat %>%
       ggplot()+
@@ -115,7 +115,36 @@ BioEconomicModelPlots <- function(dat,
                  name = "Change in fishing mortality\nrelative to BAU (%)")+
[…]

### 2021-10-22 scripts/07_proposals.Rmd
prep for rehost and DOI

@@
 
+# Now make a min, max, and average for each proposal type
+summary_results_global_2050_pretty <- all_results_global_output_table_2050_pretty %>%
+  gather(Variable, Value, c("Biomass", "Catches", "Revenue", "Fishing Mortality")) %>%
+  group_by(Category, Year, Variable) %>%
+  summarize(Minimum = min(Value, na.rm = T),
+            Maximum = max(Value, na.rm = T),
+            Median = median(Value, na.rm = T),
+            Mean = mean(Value, na.rm = T)) %>%
+  arrange(Category)
+
+write.csv(summary_results_global_2050_pretty, paste0(results_dir, "summary_results_global_2050_pretty.csv"))
+
 # Get rounded end values
@@
 write.csv(all_results_regional_output_table_2050_pretty, paste0(results_dir, "all_results_regional_output_table_2050_pretty.csv"))
+
+# Now make a min, max, and average for each proposal type
+summary_results_regional_2050_pretty <- all_results_regional_output_table_2050_pretty %>%
+  gather(Variable, Value, c("Biomass", "Catches", "Revenue", "Fishing Mortality")) %>%
+  group_by(Region, Category, Year, Variable) %>%
+  summarize(Minimum = min(Value, na.rm = T),
+            Maximum = max(Value, na.rm = T),
+            Median = median(Value, na.rm = T),
+            Mean = mean(Value, na.rm = T)) %>%
+  arrange(Region, Category)
+
+write.csv(summary_results_regional_2050_pretty, paste0(results_dir, "summary_results_regional_2050_pretty.csv"))
 ```

### 2022-01-05 scripts/01b_sdt_data_wrangling.Rmd
final review of all proposals complete

--- 2020-08-11 scripts/01_data_wrangling.Rmd
@@
 
-title: "SubsidyExplorer - Step 1: Data Wrangling"
+title: "SubsidyExplorer - Additional data wrangling pertaining to proposal S&DT"
 author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
@@
 
-This script handles the preliminary data wrangling for the raw data sets underlying the SubsidyExplorer analysis.
+This script handles some additional data wrangling for the SubsidyExplorer analysis, specifically relating to proposed S&DT criteria from some of the proposals.
 It outputs tidied data files to `r data_dir`.
@@
 ```{r}
-### Paths to demographic data files
-# WDI data - no path, accessed through package
-fao_fishers_path <- here::here("data", "raw", "FAO-2019-yearbook", "fao_fishers_yearbook_070619.csv")
-teh_fte_path <- here::here("data", "raw", "Teh-and-Sumaila-2013-fte", "Fisher employment FTE.xlsx")
-
-### Paths to fisheries subsidies data files
-sumaila_subsidies_path <- here::here("data", "raw", "Sumaila-et-al-2019-subsidies", "Subsidies_PEW_Final.xlsx")
-oecd_fse_path <- here::here("data", "raw", "OECD-fisheries-support-estimates", "FISH_FSE_10032020183349581.csv")
-schuhbauer_subsidies_ssf_path <- here::here("data", "raw", "Schuhbauer-et-al-2017-ssf-subsidies", "Subsidies_SSF_split_2018.csv")
-
-### Paths to other fisheries data files
-fao_production_path <- here::here("data", "raw", "FAO-global-capture-production", "Capture_2020.1.0/")
-#fao_value_path
-melnychuk_price_path <- here::here("data", "raw", "Melnychuk-et-al-2013-price", "Melnychuk_Exvessel_Price_Database.csv")
-ram_sadb_path <- here::here("data", "raw", "RAM-legacy-stock-assessment-database", "RAMLDB v4.491", "DB Files With Assessment Data", "RAMCore/")
-costello_upsides_path <- here::here("data", "raw", "Costello-et-al-2016-upsides", "ProjectionData_2012.csv")
-melnychuk_fmi_path <- here::here("data", "raw", "Melnychuk-et-al-2017-fmi", "fmi_values_country.csv")
-iuu_vessel_path <- here::here("data", "raw", "combined-IUU-vessel-list", "IUUList-20190430.csv")
-
-### Paths to other necessary files
-cap_tier_path <- here::here("data", "raw", "USA-cap-tier-proposal", "US_cap_tier_data.csv")
 country_lookup_path <- here::here("data", "lookup-tables", "country_dependencies.csv")
-fao_regions_for_ram_lookup_path <- here::here("data", "lookup-tables", "fao_areas_for_ram_stocks_v4.491.csv")
-sumaila_lookup_path <- here::here("data", "lookup-tables", "sumaila_subsidies_classification_lookup_table.csv")
-schuhbauer_lookup_path <- here::here("data", "lookup-tables", "schuhbauer_subsidies_classification_lookup_table.csv")
-oecd_fse_lookup_path <- here::here("data", "lookup-tables", "oecd_fse_classification_lookup_table.csv")
 ```
 
-The following data sources are included in this analysis:
+The following data sources are used:
 
 **Demographic Data**
-Total GDP, GDP from fisheries, forestry, and agriculture, and population by state from the World Bank's World Development Indicators Database (2000 - 2018).
+GDP from fisheries, forestry, and agriculture, and GNI per capita from the World Bank's World Development Indicators Database (2000 - 2018).
 These data were accessed through the `WDI` package.
@@
 
-Total number of fishers by state from the FAO Yearbook of Fishery and Aquaculture Statistics (misc.
-years between 1995 and 2017).
-These data were manually transcribed from PDF (`./data/raw/fleet_&_employment.pdf`) to CSV format on July 6, 2019 and are stored as `r fao_fishers_path`.
-> FAO. (2019). FAO Yearbook of Fishery and Aquaculture Statistics 2017 (p. 108).
-
-Estimated number of full-time jobs in fisheries from Teh and Sumaila (2013) in 2003. These data were provided to us directly by the authors and are stored as `r teh_fte_path`. 
-> Teh, L. C. L., & Sumaila, U. R. (2011). Contribution of marine fisheries to worldwide employment. Fish and Fisheries, 14(1), 77–88. https://doi.org/10.1111/j.1467-2979.2011.00450.x
-
-**Fisheries Subsidies Data**
-Estimates of annual fisheries subsidies provision by state from Sumaila et al. (2019) in 2018 US\$. These data were provided to us directly by the authors and are stored at `r sumaila_subsidies_path`.
-> Sumaila, U.
-R., Ebrahim, N., Schuhbauer, A., Skerritt, D., Li, Y., Kim, H.
-S., … Pauly, D.
-(2019).
-Updated estimates and analysis of global fisheries subsidies.
-Marine Policy, 109, 103695.
-https://doi.org/10.1016/j.marpol.2019.103695
-
-Estimates of fisheries support provision by state from the OECD (2008 - 2018). These data were last downloaded from the OECD iLibrary portal on March 10, 2019 and are stored as `r oecd_fse_path`.
-> OECD. (2019). Fisheries: Fisheries support estimates. Fisheries and Aquaculture Statistics, OECD Agriculture Statistics (Database). https://doi.org/10.1787/ade64fdc-en
-
-Estimates of annual fisheries subsidies provision to small scale fisheries by state in 2018 US\$.
-Data used in this analysis are unpublished updates (based on the Sumaila et al.
-(2019) data) from those reported in Schuhbauer et al.
-(2017) (which are in 2009 US\$).
-These data were provided to us directly by the authors and are stored at `r schuhbauer_subsidies_ssf_path`.
-> Schuhbauer, A., Chuenpagdee, R., Cheung, W.
-W.
-L., Greer, K., & Sumaila, U.
-R.
-(2017).
-How subsidies affect the economic viability of small-scale fisheries.
-Marine Policy, 82, 114–121.
-https://doi.org/10.1016/j.marpol.2017.05.013
-
-**Other Fisheries Data**
-Fisheries landings in 2018 from the FAO Global Capture Production database (2020). These data were last downloaded from the FAO website on July 25, 2020 and are stored as `r fao_production_path`. 
-> FAO. (2020). Global Capture Production Dataset. http://www.fao.org/fishery/statistics/global-capture-production/en
-
-Estimates of ex-vessel prices created by Melnychuk et al. (2017). These data were provided to us directly by the authors and are stored as `r melnychuk_price_path`. 
-> Melnychuk, M.
-C., Clavelle, T., Owashi, B., & Strauss, K.
-(2017).
-Reconstruction of global ex-vessel prices of fished species.
-ICES Journal of Marine Science, 74(1), 121–133.
-https://doi.org/10.1093/icesjms/fsw169
-
-The RAM Legacy Stock Assessment Database is a compilation of stock assessments for commercially exploited species from around the world.
-The latest version of this database (version 4.491) was downloaded directly from the RAM website on July 25, 2020 and are stored as `r ram_sadb_path`.
-> RAM Legacy Stock Assessment Database. (2020). Version 4.491-assessment only. Released 2020-02-20. https://doi.org/10.5281/zenodo.3676087
-
-Estimates of stock status for commercially exploited species not included in the RAM Legacy Stock Assessment Database from Costello et al.
-(2016).
-These data were provided to us directly by the authors and are stored as `r costello_upsides_path`.
-> Costello, C., Ovando, D., Clavelle, T., Strauss, C.
-K., Hilborn, R., Melnychuk, M.
-C., Branch, T.
-A., Gaines, S.
-D., Szuwalski, C.
-S., Cabral, R.
-B., Rader, D.
-N., & Leland, A.
-(2016).
-Global fishery prospects under contrasting management regimes.
-Proceedings of the National Academy of Sciences, 113(18), 5125–5129.
-https://doi.org/10.1073/pnas.1520420113
-
-Fisheries management indicators for many of the top fishing nations from Melnychuk et al.
-(2017).
-These data were manually transcribed from Figure S2 in the supplementary information and are stored as `r melnychuk_fmi_path`.
-> Melnychuk, M.
-C., Peterson, E., Elliott, M., & Hilborn, R.
-(2017).
-Fisheries management impacts on target species status.
-Proceedings of the National Academy of Sciences, 114(1), 178–183.
-https://doi.org/10.1073/pnas.1609915114
-
-The IUU Consolidated Vessel List created and maintained by Trygg Mat Tracking. These data were downloaded directly from the website on November 30, 2019 and are stored as `r iuu_vessel_path`. 
-> Trygg Mat Tracking. (2020). Combined IUU Fishing Vessel List. https://www.iuu-vessels.org/
-
-We also use the following tables to aid in our analysis:
-
-- Proposed tier assignments for a cap-based approach to limiting subsidies as included in the proposal made to the WTO by the delegations of Australia and the USA on May 3, 2019 [TN/RL/GEN/197/Rev.1].
-
-- A manually compiled table of overseas dependencies of WTO Member and Observer countries
-
-- All subsidy types used by Sumaila et al. (2019)
-
-- All subsidy types used by the OECD FSE database
-
-- A manually compiled table of FAO statistical regions corresponding to the stocks contained in version 4.491 of the RAM Legacy Stock Assessment Database.
-
-# Note: Country naming, political entities, and dependencies
-
-The naming of flag and coastal states varies widely across our data sources and we recognize that this can be a politically sensitive matter.
-For the purposes of merging multiple data sources, we therefore translate all state names from the raw data sources to ISO-3 character codes.
-Country names are only used for display purposes, and the use of any particular name is not meant to convey any options regarding sovereignty on behalf of the authors.
+We also use our vessel list and definition of distant water fishing (described in other scripts) to identify countries fulfiling that criteria.
 
@@
 
-Additionally, it is important to note that the European Union as a political entity is a Member of the World Trade Organization, rather then the individual states that make up the European Union.
-We therefore need to create a profile for the European Union as a whole.
-The following `r length(eu_country_names)` states are considered to be part of the European Union for the purposes of this analysis: `r paste(country_dependencies$WTO_name[country_dependencies$iso3 %in% eu_countries], collapse = ", ")`.
+# S&DT Criteria
 
-The Netherlands, France, Denmark, and the United Kingdom also have overseas dependencies that should be considered to be a part of the European Union for statistical purposes.
-
-Outside of the EU, the other dependencies we need to worry about are those that relate to the Austraila, Morocco, Norway, New Zealand, and the United States.
-
-# Section 1 - Subsidies Data
-
-## Estimates of global fisheries subsidies from Sumaila et al. (2019)
+Some proposals advocate for allowing developing countries to provide certain types of subsidies unless they meet certain criteria for three consecutive years: 
+- GNI per capita is greater than \$5000 (constant 2015 US\$);
+- they engage in distant water fishing;
+- the contribution from Agriculture, Forestry and Fishing to their national GDP is greater than 10%.
 
 ```{r}
-### Data Wrangling
-# Load and wrangle 2019 data
-sumaila_2019_dat <- read_xlsx(sumaila_subsidies_path) %>%
-  clean_names(case = "snake") %>%
-  mutate(iso3 = case_when(country == "Dominican Rp" ~ "DOM",
-                          country == "Micronesia" ~ "FSM",
-                          country == "Untd Arab Em" ~ "ARE",
-                          TRUE ~ countrycode(country, "country.name", "iso3c"))) %>%
-  dplyr::select(iso3, type = class, data_type, value = constant_2018_usd) %>%
-  mutate(year = 2018,
-         units = "2018 US$",
-         source = "Sumaila et al. (2019)") %>%
-  arrange(iso3)
+#Load data using WDI package
+wb_sdt_dat <- WDI(country = "all",
+                   indicator = c("gdp_ffa_percent" = "NV.AGR.TOTL.ZS", # Added value coming from fisheries, forestry, and agriculture (%)
+                                 "gni_per_capita" = "NY.GNP.PCAP.KD"), # GNI per capita (constant 2015 US$)
+                                  start = 2016,
+                                  end = 2018,
+                                  extra = TRUE) %>%
+  dplyr::filter(region != "Aggregates") %>%
+  dplyr::select(iso3 = iso3c,
+                year,
+                gdp_ffa_percent,
+                gni_per_capita) %>%
+  mutate(iso3 = as.character(iso3)) %>%
+  arrange(iso3, year) %>%
+  group_by(iso3) %>%
+  mutate(n_exceeds_gdp_ffa = sum(gdp_ffa_percent > 10),
+         n_exceeds_gni_per_capita = sum(gni_per_capita > 5000)) %>%
+  ungroup()
 
-# Load lookup table for classification scheme
-sumaila_lookup <- read_csv(sumaila_lookup_path)
-
-# Clean up the naming/spelling of the classification scheme as well as data type
-sumaila_2019_dat_edit <- sumaila_2019_dat %>%
-  left_join(sumaila_lookup, by = "type") %>%
-  dplyr::select(iso3, year, category, category_name, type, type_name, value, data_type, units, source)
-
-sumaila_2019_dat_edit$data_type[sumaila_2019_dat_edit$data_type == "not found evidence of subsidy"] <- "Found no evidence of subsidy"
-
-# Deal with the EU
-sumaila_2019_dat_eu <- sumaila_2019_dat_edit %>%
-  dplyr::filter(iso3 %in% c(eu_countries, eu_territories)) %>%
-  mutate(entity = "EU",
-         data_type = "Aggregate") %>%
-  group_by(entity, year, category, category_name, type, type_name, data_type, units, source) %>%
-  summarize(value = sum(value, na.rm = T)) %>%
-  ungroup() %>%
-  rename(iso3 = entity)
-
-# Add the EU back in
-sumaila_2019_dat_edit <- sumaila_2019_dat_edit %>%
-  bind_rows(sumaila_2019_dat_eu) %>%
-  mutate(variable = "subsidies_Sumaila")
-
-# Test to make sure there isn't data for any other dependencies - nope we're good
-sumaila_2019_dat_overseas_territory <- sumaila_2019_dat_edit %>%
-  dplyr::filter(iso3 %in% territories$iso3 & !(iso3 %in% eu_territories))
-
-# Save
-write_csv(sumaila_2019_dat_edit, paste0(data_dir, "sumaila_et_al_2019_subsidies_tidy.csv"))
-write_csv(sumaila_2019_dat_edit, paste0(app_data_dir, "sumaila_et_al_2019_subsidies_tidy.csv"))
+wb_sdt_dat_out <- wb_sdt_dat %>%
+  distinct(iso3, n_exceeds_gdp_ffa, n_exceeds_gni_per_capita) %>%
+  mutate(exceeds_gdp_ffa = case_when(n_exceeds_gdp_ffa == 3 ~ T,
+                                     is.na(n_exceeds_gdp_ffa) ~ F,
+                                     TRUE ~ F),
+         exceeds_gni_per_capita = case_when(n_exceeds_gni_per_capita == 3 ~ T,
+                                            is.na(n_exceeds_gni_per_capita) ~ F,
+                                            TRUE ~ F)) %>%
+  dplyr::select(-n_exceeds_gdp_ffa, -n_exceeds_gni_per_capita)
 
@@
 
-## Estimates of fisheries support provision by state from the OECD (2008 - 2018)
+```{r}
+# Load vessel list
+vessel_dat <- read.csv(here::here("app", "data", "vessel_list_2018_final.csv"), stringsAsFactors = F)
+
+# Create high seas code
+vessel_dat <- vessel_dat %>%
+  mutate(eez_hs_code = case_when(eez_id == 0 ~ paste0("HS-", fao_region),
+                                 TRUE ~ as.character(eez_id)))
+
+# Get flag states that participate in distant water fishing
+vessel_dat_dw <- vessel_dat %>%
+  distinct(flag_iso3, distant_water) %>%
+  dplyr::filter(distant_water == T)
+```
 
 ```{r}
-# Load and wrangle OECD data (2009 - 2017)
-oecd_fse_dat <- read_csv(oecd_fse_path) %>%
-  clean_names(case = "snake") %>%
-  dplyr::filter(measure == "USD", # only pull estimates in USD for consistancy
-                country != "OECD") %>% # remove totals
-  dplyr::select(iso3 = country, code = variable, year, value)
+sdt_dat_out <- wb_sdt_dat_out %>%
+  left_join(vessel_dat_dw, by = c("iso3" = "flag_iso3")) %>%
+  mutate(distant_water = ifelse(is.na(distant_water), FALSE, distant_water)) %>%
+  mutate(meets_any_criteria = ifelse(exceeds_gdp_ffa | exceeds_gni_per_capita | distant_water, T, F))
 
-# Load OECD lookup table
-oecd_fse_lookup <- read_csv(oecd_fse_lookup_path) %>%
-  distinct(category, category_name, type, type_code, type_name)
-
-# Match based on type - that should be plenty for the figure on SubsidyExplorer
-oecd_fse_dat_edit <- oecd_fse_dat %>%
-  inner_join(oecd_fse_lookup, by = c("code" = "type_code")) %>%
-  mutate(data_type = "Reported",
-         units = paste0(year, " US$"),
-         source = "OECD FSE database") %>%
-  dplyr::select(iso3, year, category, category_name, type, type_name, data_type, units, source, value)
-
-# Deal with the EU
-oecd_fse_dat_eu <- oecd_fse_dat_edit %>%
-  dplyr::filter(iso3 %in% c(eu_countries, eu_territories)) %>%
-  mutate(entity = "EU",
-         data_type = "Aggregate") %>%
-  group_by(entity, year, category, category_name, type, type_name, data_type, units, source) %>%
-  summarize(value = sum(value, na.rm = T)) %>%
-  ungroup() %>%
-  rename(iso3 = entity) %>%
-  arrange(iso3, year, type)
-
-# Add EU back in 
-oecd_fse_dat_edit <- oecd_fse_dat_edit %>%
-  bind_rows(oecd_fse_dat_eu) %>%
-  mutate(variable = "subsidies_OECD")
-
-# Test to make sure there isn't data for any other dependencies - nope we're good
-oecd_fse_dat_overseas_territory <- oecd_fse_dat_edit %>%
-  dplyr::filter(iso3 %in% territories$iso3 & !(iso3 %in% eu_territories))
-
-# Save
-write_csv(oecd_fse_dat_edit, paste0(data_dir, "oecd_2019_fse_tidy.csv"))
-write_csv(oecd_fse_dat_edit, paste0(app_data_dir, "oecd_2019_fse_tidy.csv"))
-
+write_csv(sdt_dat_out, paste0(data_dir, "sdt_lookup_table.csv"))
+write_csv(sdt_dat_out, paste0(app_data_dir, "sdt_lookup_table.csv"))
 ```
-
-## Updated estimates of small-scale fisheries subsides from Schuhbauer et al. (2017)
-
-Note: these data are unpublished updates (in 2018 US\$) of the data described in Schuhbauer et al. (2017).
-
-```{r}
-# Load and wrangle data (2018 US$)
-schuhbauer_subsidies_ssf_dat <- read_csv(schuhbauer_subsidies_ssf_path) %>%
-  clean_names(case = "snake") %>%
-  mutate(iso3 = case_when(country == "Dominican Rp" ~ "DOM",
-                          country == "Micronesia" ~ "FSM",
-                          country == "Untd Arab Em" ~ "ARE",
-                          TRUE ~ countrycode(country, "country.name", "iso3c"))) %>%
-  mutate(prop_ssf = ssf_usd/constant_2018_usd) %>%
-  dplyr::select(iso3, old_type_name = type, prop_ssf) %>%
-  mutate(source = "Schuhbauer et al. (2017)") %>%
-  arrange(iso3)
-schuhbauer_subsidies_ssf_dat$prop_ssf[is.nan(schuhbauer_subsidies_ssf_dat$prop_ssf)] <- 0 # handling dividing by 0
-
-# Load lookup table
-schuhbauer_lookup <- read_csv(schuhbauer_lookup_path)
-
-# Clean up the naming/spelling of the classification scheme as well as data type
-schuhbauer_subsidies_ssf_dat_edit <- schuhbauer_subsidies_ssf_dat %>%
-  left_join(schuhbauer_lookup, by = c("old_type_name")) %>%
-  dplyr::select(iso3, category, category_name, type, type_name, prop_ssf, source)
-
-# Deal with the EU
-schuhbauer_subsidies_ssf_dat_eu <- read_csv(schuhbauer_subsidies_ssf_path) %>%
-  clean_names(case = "snake") %>%
-  mutate(iso3 = case_when(country == "Dominican Rp" ~ "DOM",
-                          country == "Micronesia" ~ "FSM",
-                          country == "Untd Arab Em" ~ "ARE",
-                          TRUE ~ countrycode(country, "country.name", "iso3c"))) %>%
-  dplyr::filter(iso3 %in% c(eu_countries, eu_territories)) %>%
-  mutate(entity = "EU") %>%
-  group_by(entity, type) %>%
-  summarize(constant_2018_usd = sum(constant_2018_usd, na.rm = T),
-            ssf_usd = sum(ssf_usd, na.rm = T)) %>%
-  ungroup() %>%
-  mutate(prop_ssf = ssf_usd/constant_2018_usd) %>%
-  dplyr::select(iso3 = entity, old_type_name = type, prop_ssf) %>%
-  mutate(source = "Schuhbauer et al. (2017)") %>%
-  left_join(schuhbauer_lookup, by = c("old_type_name")) %>%
-  dplyr::select(iso3, category, category_name, type, type_name, prop_ssf, source)
-
-# Add the EU back in
-schuhbauer_subsidies_ssf_dat_edit <- schuhbauer_subsidies_ssf_dat_edit %>%
-  bind_rows(schuhbauer_subsidies_ssf_dat_eu)
-
-# Test to make sure there isn't data for any other dependencies - nope we're good
-schuhbauer_subsidies_ssf_dat_overseas_territory <- schuhbauer_subsidies_ssf_dat_edit %>%
-  dplyr::filter(iso3 %in% territories$iso3 & !(iso3 %in% eu_territories))
-
-# Save
-write_csv(schuhbauer_subsidies_ssf_dat_edit, paste0(data_dir, "schuhbauer_ssf_subsidies_proportions.csv"))
-write_csv(schuhbauer_subsidies_ssf_dat_edit, paste0(app_data_dir, "schuhbauer_ssf_subsidies_proportions.csv"))
-```
-
-# Section 2 - Demographic Data
-
-## Demographic statistics by state from the World Bank's World Development Indicators Database (2000 - 2018)
-
-```{r}
-# Load data using WDI package'
-# wb_demo_dat <- WDI(country = "all",
-#                    indicator = c("gdp" = "NY.GDP.MKTP.CD",
-#                                  "gdp_ffa" = "NV.AGR.TOTL.CD",
-#                                  "population" = "SP.POP.TOTL"),
-#                                   start = 2000,
-#                                   end = 2018,
-#                                   extra = TRUE) %>%
-#   dplyr::filter(region != "Aggregates") %>%
-#   dplyr::select(iso3 = iso3c,
-#                 year,
-#                 gdp,
-#                 gdp_ffa,
-#                 population) %>%
-#   mutate(iso3 = as.character(iso3)) %>%
-#   arrange(iso3, year) %>%
-#   gather(variable, value, c("gdp", "gdp_ffa", "population")) %>%
-#   dplyr::filter(!is.na(value)) %>%
-#   mutate(units = case_when(variable == "population" ~ "individuals",
-#                            TRUE ~ paste0(year, " US$")),
-#          source = "World Bank WDI database")
-# 
-# # Deal with the EU + territories
-# wb_dat_eu <- wb_demo_dat %>%
-#   dplyr::filter(iso3 %in% c(eu_countries, eu_territories)) %>%
-#   mutate(entity = "EU") %>%
-#   group_by(entity, year, variable, units, source) %>%
-#   summarize(value = sum(value, na.rm = T)) %>%
-#   rename(iso3 = entity) %>%
-#   arrange(iso3, year, variable)
-# 
-# # Test to make sure there isn't data for any other dependencies - will need to add this once I can figure out why the WDI API isn't working
-# wb_dat_overseas_territory <- wb_demo_dat %>%
-#   dplyr::filter(iso3 %in% territories$iso3 & !(iso3 %in% eu_territories))
-# # Deal with the US + territories
-# wb_dat_us <- wb_demo_dat %>%
-#   dplyr::filter(iso3 %in% c(us_territories, "USA")) %>%
-#   mutate(entity = "USA") %>%
-#   group_by(entity, year, variable, units, source) %>%
-#   summarize(value = sum(value, na.rm = T)) %>%
-#   rename(iso3 = entity) %>%
-#   arrange(iso3, year, variable)
-# 
-# # Add back in
-# wb_dat_edit <- wb_demo_dat %>%
-#   dplyr::filter(iso3 != "USA") %>%
-#   bind_rows(wb_dat_eu) %>%
-#   bind_rows(wb_dat_us)
-# 
-# # Export clean
-# write_csv(wb_dat_edit, paste0(data_dir, "world_bank_2020_wdi_tidy.csv"))
-# write_csv(wb_dat_edit, paste0(app_data_dir, "world_bank_2020_wdi_tidy.csv"))
-
-# Load in
-wb_dat_edit <- read_csv(paste0(data_dir, "world_bank_2020_wdi_tidy.csv"))
-```
-
-## Total number of fishers by state from the FAO Yearbook of Fishery and Aquaculture Statistics (misc. years between 1995 and 2016)
-
-```{r}
-# Pull data and wrangle
-fao_fishers_dat <- read_csv(fao_fishers_path) %>%
-  mutate(iso3 = countrycode(country, "country.name", "iso3c")) %>%
-  dplyr::select(-country) %>%
-  gather(year, value, c('1995', '2000', '2005', '2010', '2011', '2012', '2013', '2014', '2015', '2016')) %>%
-  mutate(year = as.numeric(year)) %>%
-  dplyr::filter(!is.na(value)) %>%
-  mutate(variable = "fishers",
-         units = "individuals",
-         source = "FAO Yearbook of Fishery and Aquaculture Statistics (2017)")
-
-# Deal with EU
-fao_fishers_dat_eu <- fao_fishers_dat %>%
-  dplyr::filter(iso3 %in% c(eu_countries, eu_territories)) %>%
-  mutate(entity = "EU") %>%
-  group_by(entity, year, variable, units, source) %>%
-  summarize(value = sum(value, na.rm = T)) %>%
-  ungroup() %>%
-  rename(iso3 = entity) %>%
-  arrange(iso3, year, variable)
-
-# Add EU back in 
-fao_fishers_dat_edit <- fao_fishers_dat %>%
-  bind_rows(fao_fishers_dat_eu) %>%
-  arrange(year, iso3)
-
-# # Test to make sure there isn't data for any other dependencies - nope we're good
-fao_fishers_dat_overseas_territory <- fao_fishers_dat %>%
-  dplyr::filter(iso3 %in% territories$iso3 & !(iso3 %in% eu_territories))
-
-# Export clean
-write_csv(fao_fishers_dat_edit, paste0(data_dir, "fao_2017_yearbook_fishers_tidy.csv"))
-write_csv(fao_fishers_dat_edit, paste0(app_data_dir, "fao_2017_yearbook_fishers_tidy.csv"))
-```
-
-## Estimated number of full-time jobs in fisheries from Teh and Sumaila (2013) in 2003
-
-```{r}
-# Pull data and wrangle
-teh_fte_dat <- read_xlsx(teh_fte_path) %>%
-  clean_names(case = "snake") %>%
-  mutate(iso3 = case_when(country == "Dominican Rp" ~ "DOM",
-                          country == "Micronesia" ~ "FSM",
-                          country == "Untd Arab Em" ~ "ARE",
-                          TRUE ~ countrycode(country, "country.name", "iso3c"))) %>%
-  dplyr::select(-country) %>%
-  mutate(variable = "fishers_fte",
-         year = 2003,
-         units = "full-time equivalent jobs",
-         source = "Teh and Sumaila (2013)") %>%
-  dplyr::select(iso3, year, variable, value = total_fte, units, source)
-
-# Deal with EU
-teh_fte_dat_eu <- teh_fte_dat %>%
-  dplyr::filter(iso3 %in% c(eu_countries, eu_territories)) %>%
-  mutate(entity = "EU") %>%
-  group_by(entity, year, variable, units, source) %>%
-  summarize(value = sum(value, na.rm = T)) %>%
-  ungroup() %>%
-  rename(iso3 = entity) %>%
-  arrange(iso3, year, variable)
-
-# Add EU back in 
-teh_fte_dat_edit <- teh_fte_dat %>%
-  bind_rows(teh_fte_dat_eu)
-
-# # Test to make sure there isn't data for any other dependencies - nope we're good
-teh_fte_dat_overseas_territory <- teh_fte_dat_edit %>%
-  dplyr::filter(iso3 %in% territories$iso3 & !(iso3 %in% eu_territories))
-
-# Export clean
-write_csv(teh_fte_dat_edit, paste0(data_dir, "teh_and_sumaila_2013_fte_tidy.csv"))
-write_csv(teh_fte_dat_edit, paste0(app_data_dir, "teh_and_sumaila_2013_fte_tidy.csv"))
-```
-
-# Section 3 - Fisheries Data
-
-## Fisheries landings for 2000-2017 from the FAO Global Capture Production database (2019)
-
-```{r}
-# FAO stores a lot of characteristics in lookup tables that come with the production dataset. We need to use these tables to match country names, species names, and source
-fao_country_lookup <- read_csv(paste0(fao_production_path, "CL_FI_COUNTRY_GROUPS.csv")) %>%
-  clean_names(case = "snake") %>%
-  dplyr::select(country = un_code,
-                iso3 = iso3_code,
-                name = name_en) %>%
-  mutate(iso3_new = case_when(name == "Belgium-Luxembourg" ~ "BEL",
-                              name %in% c("Canton and Enderbury Is", "Czechoslovakia", "Neutral Zone", "Pacific Islands Trust Tr", "Serbia and Montenegro", "Un.
-Sov.
-Soc.
-Rep.", "Yemen Arab Republic", "Yemen, Democratic", "Yugoslavia SFR") ~ "XXX",
-                              name %in% c("Channel Islands", "Sark") ~ "GGY",
-                              name == "Eswatini" ~ "SWZ",
-                              name == "European Union" ~ "EU",
-                              name %in% c("Johnston Island", "Midway Islands", "Wake Island", "US Minor Outlying Is.") ~ "UMI",
-                              name == "Netherlands Antilles" ~ "ANT",
-                              name == "Saint-Martin" ~ "MAF",
-                              name == "Zanzibar" ~ "TZA",
-                              name == "Other nei" ~ "UNK",
-                              is.na(name) ~ "UNK",
-                              TRUE ~ countrycode(name, "country.name", "iso3c"))) %>%
-  dplyr::filter(iso3_new != "XXX") %>% # remove entities that no longer exist today
-  dplyr::select(iso3 = iso3_new, country) %>%
-  mutate(country = as.integer(country))
-
-# FAO species lookup 
-fao_species_lookup <- read_csv(paste0(fao_production_path, "CL_FI_SPECIES_GROUPS.csv")) %>%
-  clean_names(case = "snake") %>%
-  dplyr::select(species = x3alpha_code,
-                asfis_species = name_en,
-                scientific_name,
-                yearbook_group,
-                isscaap_group)
-
-# FAO Symbol lookup
-fao_symbol_lookup <- read_csv(paste0(fao_production_path, "CL_FI_SYMBOL.csv"))
-
-# FAO Area lookup
-fao_area_lookup <- read_csv(paste0(fao_production_path, "CL_FI_WATERAREA_GROUPS.csv")) %>%
-  clean_names(case = "snake") %>%
-  dplyr::select(area = code) %>%
-  mutate(area = as.integer(area))
-
-# Load data
-fao_production_dat <- read.csv(paste0(fao_production_path, "TS_FI_CAPTURE.csv")) %>%
-  clean_names(case = "snake") %>%
-  dplyr::filter(year >= 2000) %>%
-  dplyr::filter(unit == "t") %>% # remove catches measured in number of individuals
-  mutate(species = as.character(species)) %>%
-  left_join(fao_country_lookup, by = "country") %>%
-  inner_join(fao_area_lookup, by = c("fishing_area" = "area")) %>%
-  group_by(iso3, year, species, fishing_area) %>%
-  summarize(value = sum(quantity, na.rm = T)) %>%
-  ungroup() %>%
-  left_join(fao_species_lookup, by = "species")
-
-# Deal with the EU + territories
-fao_production_dat_eu <- fao_production_dat %>%
-  dplyr::filter(iso3 %in% c(eu_countries, eu_territories, "EU")) %>%
-  mutate(entity = "EU") %>%
-  group_by(entity, year, fishing_area, species, asfis_species, scientific_name, yearbook_group, isscaap_group) %>%
-  summarize(value = sum(value, na.rm = T)) %>%
-  ungroup() %>%
-  rename(iso3 = entity)
-
-# Deal with all territories 
-fao_production_dat_overseas_territories <- fao_production_dat %>%
-  dplyr::filter(iso3 %in% territories$iso3 | iso3 %in% territories$sovereign_iso3) %>%
-  left_join(territories, by = c("iso3")) %>%
-  mutate(sovereign_iso3 = case_when(is.na(sovereign_iso3) ~ iso3,
-                                    TRUE ~ sovereign_iso3)) %>%
-  mutate(entity = paste0(sovereign_iso3, "-T")) %>%
-  group_by(entity, year, fishing_area, species, asfis_species, scientific_name, yearbook_group, isscaap_group) %>%
-  summarize(value = sum(value, na.rm = T)) %>%
-  ungroup() %>%
-  rename(iso3 = entity)
-
-# Put them back together
-fao_production_dat_edit <- fao_production_dat %>%
-  dplyr::filter(iso3 != "EU") %>%
-  bind_rows(fao_production_dat_eu) %>%
-  bind_rows(fao_production_dat_overseas_territories) %>%
-  mutate(variable = "capture_production",
-         units = "tonnes",
-         source = "FAO (2020)")
-
-write_csv(fao_production_dat_edit, paste0(data_dir, "fao_2020_capture_production_tidy.csv"))
-
-# Aggregate by ISCCAP groups and export for time series plot
-fao_production_dat_edit_groups <- fao_production_dat_edit %>%
-  group_by(iso3, year, isscaap_group, variable, units, source) %>%
-  summarize(value = sum(value, na.rm = T)) %>%
-  ungroup() %>%
-  spread(year, value) %>% # adding empty rows to make the plotting work better
-  gather(year, value, as.character(c(2000:2018))) %>% # second part of that process
-  mutate(year = as.numeric(year))
-fao_production_dat_edit_groups$value[is.na(fao_production_dat_edit_groups$value)] <- 0 # for plotting purposes - we don't get gaps on area plot this way
-
-write_csv(fao_production_dat_edit_groups, paste0(data_dir, "fao_2020_capture_production_isscaap_groups_tidy.csv"))
-write_csv(fao_production_dat_edit_groups, paste0(app_data_dir, "fao_2020_capture_production_isscaap_groups_tidy.csv"))
-```
-
-## Ex-vessel prices from Melnychuk et al. (2017)
-```{r}
-# Price data from Melynchuk et al. (2017)
-melnychuk_price_dat <- read_csv(melnychuk_price_path) %>%
-  clean_names(case = "snake") %>%
-  dplyr::select(-entry) %>%
-  dplyr::filter(year >= 2000 & year <= 2012) %>%
-  group_by(year, scientific_name, asfis_species, isscaap_group, group_for_pairing) %>%
-  summarize(exvessel = mean(exvessel, na.rm = T)) %>%
-  ungroup()
-
-# Pull data from 2012 to use for extrapolation to 2017
-melnychuk_price_dat_mry <- melnychuk_price_dat %>%
-  dplyr::filter(year == 2012) %>%
-  rename(exvessel_for_extrap = exvessel) %>%
-  dplyr::select(-year)
-
-# CPI for 2012 - 2018 to convert USD
-cpi_2012 <- 229.594
-cpi_2013 <- 232.957
-cpi_2014 <- 236.736
-cpi_2015 <- 237.017
-cpi_2016 <- 240.007
-cpi_2017 <- 245.120
-cpi_2018 <- 251.107
-
-# Do extrapolation for missing years
-melnychuk_price_dat_extrapolation <- melnychuk_price_dat %>%
-  complete(nesting(scientific_name, asfis_species, isscaap_group, group_for_pairing), year = 2000:2018) %>%
-  left_join(melnychuk_price_dat_mry, by = c("scientific_name", "asfis_species", "isscaap_group", "group_for_pairing")) %>%
-  mutate(exvessel_adjusted = case_when(year <= 2012 ~ exvessel,
-                                       year == 2013 ~ exvessel_for_extrap * (cpi_2013/cpi_2012),
-                                       year == 2014 ~ exvessel_for_extrap * (cpi_2014/cpi_2012),
-                                       year == 2015 ~ exvessel_for_extrap * (cpi_2015/cpi_2012),
-                                       year == 2016 ~ exvessel_for_extrap * (cpi_2016/cpi_2012),
-                                       year == 2017 ~ exvessel_for_extrap * (cpi_2017/cpi_2012),
-                                       year == 2018 ~ exvessel_for_extrap * (cpi_2018/cpi_2012))) %>%
-  dplyr::select(-exvessel, -exvessel_for_extrap) %>%
-  rename(exvessel = exvessel_adjusted)
-
-# Get rid of NAs and save
-melnychuk_price_dat_extrapolation <- melnychuk_price_dat_extrapolation %>%
-  dplyr::filter(!is.nan(exvessel)) %>%
-  mutate(variable = "ex_vessel_price",
-         units = paste(year, "US$"),
-         source = "Melnychuk et al. (2017)")
-
-write_csv(melnychuk_price_dat_extrapolation, paste0(data_dir, "melnychuk_2017_price_tidy.csv"))
-
-# Create averages by pairing group for each year
-price_dat_group_year <- melnychuk_price_dat_extrapolation %>%
-  group_by(year, group_for_pairing) %>%
-  summarize(exvessel_group_avg = mean(exvessel, na.rm = T)) %>%
-  ungroup()
-
-# Create averages by pairing group (no year) 
-price_dat_group <- melnychuk_price_dat_extrapolation %>%
-  group_by(group_for_pairing) %>%
-  summarize(exvessel_group_avg_allyears = mean(exvessel, na.rm = T)) %>%
-  ungroup()
-```
-
-## Estimated landed value from FAO/Melnychuk et al. (2017)
-
-```{r}
-# Combine landings and price data
-combine_catch_price_dat <- fao_production_dat_edit %>%
-  left_join(melnychuk_price_dat_extrapolation %>% dplyr::select(-isscaap_group, -variable, -source, -units), by = c("year", "scientific_name", "asfis_species", "isscaap_group" = "group_for_pairing")) %>%
-  left_join(price_dat_group_year, by = c("year", "isscaap_group" = "group_for_pairing")) %>%
-  left_join(price_dat_group, by = c("isscaap_group" = "group_for_pairing")) %>%
-  mutate(exvessel_inclusive = case_when(!is.na(exvessel) ~ exvessel,
-                                        !is.na(exvessel_group_avg) ~ exvessel_group_avg,
-                                        !is.na(exvessel_group_avg_allyears) ~ exvessel_group_avg_allyears))
-
-# Look at NAs - 11,553 entries
-combine_nas <- combine_catch_price_dat %>%
-  dplyr::filter(is.na(exvessel_inclusive))
-
-combine_nas_groups <- unique(combine_nas$isscaap_group)
-
-# Set price to 0 for those
-combine_catch_price_dat$exvessel_inclusive[is.na(combine_catch_price_dat$exvessel_inclusive)] <- 0
-
-# Calculate revenues and export
-landed_value_dat <- combine_catch_price_dat %>%
-  dplyr::select(-exvessel, -exvessel_group_avg, -exvessel_group_avg_allyears) %>%
-  rename(exvessel = exvessel_inclusive) %>%
-  mutate(landed_value = value*exvessel) %>%
-  group_by(iso3, year, fishing_area, species, asfis_species, scientific_name, yearbook_group, isscaap_group) %>%
-  summarize(value = sum(landed_value, na.rm = T)) %>%
-  mutate(variable = "landed_value",
-         units = paste(year, "US$"),
-         source = "FAO (2020); Melnychuk et al. (2017)")
-
-write_csv(landed_value_dat, paste0(data_dir, "estimated_landed_value_tidy.csv"))
-
-# Calculate revenues and aggregate by ISSCAAP group
-landed_value_dat_groups <- landed_value_dat %>%
-  group_by(iso3, year, isscaap_group, variable, source) %>%
-  summarize(value = sum(value, na.rm = T)) %>%
-  ungroup() %>%
-  spread(year, value) %>% # adding empty rows to make the plotting work better
-  gather(year, value, as.character(c(2000:2018))) %>% # second part of that process
-  mutate(year = as.numeric(year)) %>%
-  mutate(units = paste0(year, " US$"))
-
-write_csv(landed_value_dat_groups, paste0(data_dir, "estimated_landed_value_isscaap_groups_tidy.csv"))
-write_csv(landed_value_dat_groups, paste0(app_data_dir, "estimated_landed_value_isscaap_groups_tidy.csv"))
-```
-
-## RAM Legacy Stock Assessment database
-
-```{r}
-# Load B/Bmsy timeseries from the RAM legacy stock assessment database
-ram_dat_bv_bmsy <- read_csv(paste0(ram_sadb_path, "BvB.csv")) %>%
-  rename(year = X1) %>%
-  gather(stockid, bv_bmsy, -year) %>%
-  na.omit() %>%
-  group_by(stockid) %>%
-  mutate(year_max = max(year)) %>%
-  ungroup() %>%
-  dplyr::filter(year == year_max)
-
-# Load lookup table applying FAO regions to the RAM stocks
-ram_lookup <- read_csv(fao_regions_for_ram_lookup_path)
-
-# Apply to RAM data and create a new row for each FAO region
-ram_dat_bv_bmsy_edit <- ram_dat_bv_bmsy %>%
-  left_join(ram_lookup, by = "stockid") %>%
-  mutate(region_fao = fao_area) %>%
-  mutate(region_fao_split = str_split(region_fao, ";")) %>%
-  unnest(cols = c(region_fao_split)) %>%
-  group_by(stockid) %>%
-  mutate(n_regions = n_distinct(region_fao_split)) %>%
-  ungroup()
-
-# Save clean
-write_csv(ram_dat_bv_bmsy_edit, paste0(data_dir, "RAMLDB_v4.491_bvmsy_tidy.csv"))
-```
-
-## Estimates of global stock status from Costello et al. (2016)
-
-```{r}
-# Load data
-costello_upsides_dat <- read_csv(costello_upsides_path) %>%
-  clean_names(case = "snake")
-
-# We need to split the entries that span multiple FAO regions 
-costello_upsides_dat_edit <- costello_upsides_dat %>%
-  mutate(region_fao_chr = as.character(region_fao),
-         n_regions = nchar(region_fao_chr)/2,
-         region_fao_split = str_split(gsub("(.{2})", "\\1 ", region_fao_chr), " ")) %>%
-  unnest(cols = c(region_fao_split)) %>%
-  mutate(region_fao_split = as.numeric(region_fao_split)) %>%
-  dplyr::filter(region_fao_split != "") %>%
-  mutate(iso3 = case_when(country == "Channel Islands" ~ "JEY",
-                          country == "Micronesia" ~ "FSM",
-                          country == "Zanzibar" ~ "TZA",
-                          TRUE ~ countrycode(country, "country.name", "iso3c")))
-
-# Save clean
-write_csv(costello_upsides_dat_edit, paste0(data_dir, "costello_et_al_2016_upsides_tidy.csv"))
-
-```
-
-# Melnychuk FMI
-```{r}
-# Load data and wrangle
-melnychuk_fmi_dat <- read_csv(melnychuk_fmi_path) %>%
-  clean_names(case = "snake") %>%
-  mutate(iso3 = countrycode(country, "country.name", "iso3c")) %>%
-  dplyr::select(-country) %>%
-  gather(variable, value, -iso3)
-
-# Create a mean aggregate for the EU
-melnychuk_fmi_dat_eu <- melnychuk_fmi_dat  %>%
-  dplyr::filter(iso3 %in% c(eu_countries, eu_territories)) %>%
-  mutate(entity = "EU") %>%
-  group_by(entity, variable) %>%
-  summarize(value = mean(value, na.rm = T)) %>%
-  rename(iso3 = entity)
-
-# Add EU back in
-melnychuk_fmi_dat_edit <- melnychuk_fmi_dat %>%
-  bind_rows(melnychuk_fmi_dat_eu)
-
-# Export clean
-write_csv(melnychuk_fmi_dat_edit, paste0(data_dir, "melnychuk_et_al_2017_fmi_tidy.csv"))
-
-```
-
-# Section 5 - Relative Metrics
-
-This section is a bit of a relic from when we were doing "country profiles", but there are a couple of relative subsidy metrics we want to calculate from our data sources. This is done here.
-
-```{r}
-# Sumaila dat for matching
-subs_dat_match <- sumaila_2019_dat_edit %>%
-  dplyr::select(-units, -variable) %>%
-  rename(subs = value, subs_year = year, subs_source = source)
-
-# GDP
-gdp_dat_mry <- wb_dat_edit %>%
-  dplyr::filter(variable == "gdp") %>%
-  group_by(iso3, variable) %>%
-  dplyr::filter(year == max(year[!is.na(value)])) %>%
-  ungroup() %>%
-  dplyr::select(iso3, gdp_year = year, gdp = value, gdp_source = source) %>%
-  right_join(subs_dat_match, by = c("iso3")) %>%
-  mutate(variable = "subsidies_per_gdp",
-         data_type = paste0(data_type),
-         source = paste0(subs_source, "; ", gdp_source),
-         value = subs/gdp,
-         units = paste0(subs_year, " US$/", gdp_year, " US$")) %>%
-  dplyr::select(iso3, category, category_name, type, type_name, variable, value, units, data_type, source) %>%
-  dplyr::filter(!is.na(value))
-
-# Population
-pop_dat_mry <- wb_dat_edit %>%
-  dplyr::filter(variable == "population") %>%
-  group_by(iso3, variable) %>%
-  dplyr::filter(year == max(year[!is.na(value)])) %>%
-  ungroup() %>%
-  dplyr::select(iso3, population_year = year, population = value, population_source = source) %>%
-  right_join(subs_dat_match, by = c("iso3")) %>%
-  mutate(variable = "subsidies_per_capita",
-         data_type = paste0(data_type),
-         source = paste0(subs_source, "; ", population_source),
-         value = subs/population,
-         units = paste0(subs_year, " US$/person (", population_year, ")")) %>%
-  dplyr::select(iso3, category, category_name, type, type_name, variable, value, units, data_type, source) %>%
-  dplyr::filter(!is.na(value))
-
-# Fishers
-fisher_dat_mry <- fao_fishers_dat_edit %>%
-  group_by(iso3, variable) %>%
-  dplyr::filter(year == max(year[!is.na(value)])) %>%
-  ungroup() %>%
-  dplyr::select(iso3, fishers_year = year, fishers = value, fishers_source = source) %>%
-  right_join(subs_dat_match, by = c("iso3")) %>%
-  mutate(variable = "subsidies_per_fisher",
-         data_type = paste0(data_type),
-         source = paste0(subs_source, "; ", fishers_source),
-         value = subs/fishers,
-         units = paste0(subs_year, " US$/fisher (", fishers_year, ")")) %>%
-  dplyr::select(iso3, category, category_name, type, type_name, variable, value, units, data_type, source) %>%
-  dplyr::filter(!is.na(value))
-
-# FTE
-fte_dat_mry <- teh_fte_dat_edit %>%
-  dplyr::select(iso3, fte_year = year, fte = value, fte_source = source) %>%
-  right_join(subs_dat_match, by = c("iso3")) %>%
-  mutate(variable = "subsidies_per_fte",
-         data_type = paste0(data_type),
-         source = paste0(subs_source, "; ", fte_source),
-         value = subs/fte,
-         units = paste0(subs_year, " US$/full-time-equivalent (", fte_year, ")")) %>%
-  dplyr::select(iso3, category, category_name, type, type_name, variable, value, units, data_type, source) %>%
-  dplyr::filter(!is.na(value))
-
-# Capture Production
-production_dat_mry <- fao_production_dat_edit_groups %>%
-  group_by(iso3, year, variable) %>%
-  summarize(value = sum(value, na.rm = T),
-            source = unique(source)) %>%
-  group_by(iso3, variable) %>%
-  dplyr::filter(year == max(year[!is.na(value)])) %>%
-  ungroup() %>%
-  dplyr::select(iso3, production_year = year, production = value, production_source = source) %>%
-  right_join(subs_dat_match, by = c("iso3")) %>%
-  mutate(variable = "subsidies_per_production",
-         data_type = paste0(data_type),
-         source = paste0(subs_source, "; ", production_source),
-         value = subs/production,
-         units = paste0(subs_year, " US$/tonne (", production_year, ")")) %>%
-  dplyr::select(iso3, category, category_name, type, type_name, variable, value, units, data_type, source) %>%
-  dplyr::filter(!is.na(value))
-
-# Landed Value
-landed_value_dat_mry <- landed_value_dat %>%
-  group_by(iso3, year, variable) %>%
-  summarize(value = sum(value, na.rm = T),
-            source = unique(source)) %>%
-  group_by(iso3, variable) %>%
-  dplyr::filter(year == max(year[!is.na(value)])) %>%
-  ungroup() %>%
-  dplyr::select(iso3, landed_value_year = year, landed_value = value, landed_value_source = source) %>%
-  right_join(subs_dat_match, by = c("iso3")) %>%
-  mutate(variable = "subsidies_per_landed_value",
-         data_type = paste0(data_type),
-         source = paste0(subs_source, "; ", landed_value_source),
-         value = subs/landed_value,
-         units = paste0(subs_year, " US$/", landed_value_year, " US$")) %>%
-  dplyr::select(iso3, category, category_name, type, type_name, variable, value, units, data_type, source) %>%
-  dplyr::filter(!is.na(value))
-
-# Combine with subsidy data and calculate relative metrics
-relative_dat <-  gdp_dat_mry %>%
-  bind_rows(pop_dat_mry) %>%
-  bind_rows(fisher_dat_mry) %>%
-  bind_rows(fte_dat_mry) %>%
-  bind_rows(production_dat_mry) %>%
-  bind_rows(landed_value_dat_mry)
-
-write_csv(relative_dat, paste0(data_dir, "relative_subsidy_metrics_tidy.csv"))
-write_csv(relative_dat, paste0(app_data_dir, "relative_subsidy_metrics_tidy.csv"))
-```
-
-# Section 6 - Cap/Tier Lookup Tables
-
-## Cap and Tier Data from the US Proposal
-```{r}
-cap_tier_dat <- read_csv(cap_tier_path) %>%
-  mutate(iso3 = case_when(country == "Eswatini" ~ "SWZ",
-                          country == "EU" ~ "EU",
-                          TRUE ~ countrycode(country, "country.name", "iso3c"))) %>%
-  dplyr::select(-country)
-
-write_csv(cap_tier_dat, paste0(data_dir, "USA_cap_tier_tidy.csv"))
-write_csv(cap_tier_dat, paste0(app_data_dir, "USA_cap_tier_tidy.csv"))
-```
-
-Many of the capping proposals utilize some metric to sort Members into tiers.
-This is often done based upon the average over some period.
-In order to allow this to be interactive later on, we need to craft a lookup table with all possible date ranges.
-
-```{r}
-# Capture production lookup
-capture_production_lookup <- fao_production_dat_edit_groups %>%
-  group_by(iso3, year) %>%
-  summarize(capture_production = sum(value, na.rm = T)) %>%
-  ungroup() %>%
-  spread(year, capture_production) %>%
-  mutate(variable = "capture_production") %>%
-  left_join(country_dependencies %>% dplyr::select(iso3, is_WTO), by = "iso3") %>%
-  mutate(is_WTO = case_when(!is.na(is_WTO) ~ is_WTO,
-                            iso3 %in% unique(paste0(territories$sovereign_iso3, "-T")) ~ TRUE,
-                            iso3 == "EU" ~ TRUE,
-                            TRUE ~ FALSE))
-
-# Landed value
-landed_value_lookup <- landed_value_dat_groups %>%
-  group_by(iso3, year) %>%
-  summarize(landed_value = sum(value, na.rm = T)) %>%
-  ungroup() %>%
-  spread(year, landed_value) %>%
-  mutate(variable = "landed_value") %>%
-  left_join(country_dependencies %>% dplyr::select(iso3, is_WTO), by = "iso3") %>%
-  mutate(is_WTO = case_when(!is.na(is_WTO) ~ is_WTO,
-                            iso3 %in% unique(paste0(territories$sovereign_iso3, "-T")) ~ TRUE,
-                            iso3 == "EU" ~ TRUE,
-                            TRUE ~ FALSE))
-
-# Combine 
-cap_tier_lookup <- capture_production_lookup %>%
-  bind_rows(landed_value_lookup)
-
-write_csv(cap_tier_lookup, paste0(data_dir, "cap_tier_lookup_table.csv"))
-write_csv(cap_tier_lookup, paste0(app_data_dir, "cap_tier_lookup_table.csv"))
-
-```

### 2022-01-05 app/00_initialize_app.R

@@ -272,9 +272,11 @@ bio_dat_list <- bio_dat %>%
 # 1) Cap/tier lookup table
 cap_tier_lookup_table <- read_csv("./data/cap_tier_lookup_table.csv")
 
+sdt_lookup_table <- read_csv("./data/sdt_lookup_table.csv")
+
 # 2) Proposal settings
 #proposal_settings <- read.csv("./data/wto_proposal_settings.csv", stringsAsFactors = F)
-proposal_settings <- read.csv("./data/wto_proposal_settings_v2.csv", stringsAsFactors = F)
+proposal_settings <- read.csv("./data/wto_proposal_settings_v3.csv", stringsAsFactors = F)
 
 # Proposal names
 included_proposals <- proposal_settings %>%

### 2022-01-05 app/scripts/CreateFleets.R

@@ -15,7 +15,8 @@ CreateFleets <- function(vessel_list,
                          subsidy_types_all,
                          managed_threshold = 0.66,
                          cap_tier_lookup,
-                         country_lookup){
+                         country_lookup,
+                         sdt_lookup){
   
   ### ---------------------------------
   ### SETUP ---------------------------
@@ -1083,7 +1084,7 @@ CreateFleets <- function(vessel_list,
       # 11) Distant water fishing OR HIGH SEAS (for all vessels) plus all fishing by OA vessels    
       }else if("OUT/OA" %in% overcap$scope_select & !is.na(overcap$hs_cutoff)){
       
-        # Filter for high seas OR distant water fishing only
+        # Filter for unmanaged OR high seas OR distant water fishing only
         overcap_vessels_scope <- overcap_vessels_scope %>%
           dplyr::filter(fmi_best < managed_threshold | distant_water | prop_fishing_KWh_high_seas >= (overcap$hs_cutoff/100))
         
@@ -1176,6 +1177,35 @@ CreateFleets <- function(vessel_list,
       # Exempt vessels fishing on the high seas
       overcap_vessels_sdt_developing <- overcap_vessels_sdt_developing %>%
         dplyr::filter(prop_fishing_KWh_high_seas >= (overcap$sdt_hs_cutoff_developing/100))
+      
+    }else if("TER/CRI3" %in% overcap$sdt_what_developing){
+      
+      # Exempt vessels fishing in territorial waters, and those fishing anywhere else whose flag state does not meet any of the three criteria: a) GNI per capita is greater than $5000 US$ (2016-2018), b) contribution to GDP from forestry, fisheries, and agriculture is greater than 10% (2016-2016), c) thye engage in distant water fishing (2018, GFW). 
+      
+      countries_to_exempt <- sdt_lookup$iso3[sdt_lookup$meets_any_criteria == F]
+
+      overcap_vessels_sdt_developing <- overcap_vessels_sdt_developing %>%
+        dplyr::filter(is_territorial | flag_iso3 %in% countries_to_exempt)
+      
+    }else if("TER/CAP07" %in% overcap$sdt_what_developing){
+      
+      # Exempt vessels fishing in territorial waters, and those fishing anywhere else whose flag state is not responsible for at least 07% of global capture production
+      
+      capture_years <- paste0("", seq(2016, 2018, by = 1), "")
+      
[…]

### 2022-01-05 app/server.R

@@ -474,7 +474,8 @@ shinyServer(function(input, output, session) {
           managed_threshold = managed_cutoff,
           subsidy_types_all = subsidy_types_sorted_sumaila,
           cap_tier_lookup = cap_tier_lookup_table,
-          country_lookup = country_lookup)
+          country_lookup = country_lookup,
+          sdt_lookup = sdt_lookup_table)
 
         # Create list by region
         fleet_list <- fleet$summary %>%
@@ -1096,7 +1097,8 @@ shinyServer(function(input, output, session) {
         managed_threshold = managed_cutoff,
         subsidy_types_all = subsidy_types_sorted_sumaila,
         cap_tier_lookup = cap_tier_lookup_table,
-        country_lookup = country_lookup)
+        country_lookup = country_lookup,
+        sdt_lookup = sdt_lookup_table)
       
       # Make list
       fleet_list <- fleet$summary %>%

### 2022-01-21 scripts/07_proposals.Rmd
comparing new vs. old proposals

@@
 # Directories for the output files generated by this script
-results_dir <- paste0(here::here("results", "07-proposals/"), "mgmt_threshold_", managed_cutoff, "/")
+results_dir <- paste0(here::here("results", "07-proposals/"), "mgmt_threshold_", managed_cutoff, "_2022/")
 if (dir.exists(results_dir) == F) {
@@
 #proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings.csv"), stringsAsFactors = F)
-proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_v2.csv"), stringsAsFactors = F)
+# proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_v2.csv"), stringsAsFactors = F)
+proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_v3.csv"), stringsAsFactors = F)
 
@@
 cap_tier_lookup_table <- read_csv(here::here("app","data","cap_tier_lookup_table.csv"))
+
+# S&DT lookup table
+sdt_lookup_table <- read_csv(here::here("app", "data", "sdt_lookup_table.csv"))
 
@@
       cap_tier_lookup = cap_tier_lookup_table,
-      country_lookup = country_dependencies)
+      country_lookup = country_dependencies,
+      sdt_lookup = sdt_lookup_table)
 

### 2022-02-22 scripts/07_proposals.Rmd
preparing for resubmission

@@
 # Directories for the output files generated by this script
-results_dir <- paste0(here::here("results", "07-proposals/"), "mgmt_threshold_", managed_cutoff, "_2022/")
+results_dir <- paste0(here::here("results", "07-proposals/"), "mgmt_threshold_", managed_cutoff, "_FINAL/")
 if (dir.exists(results_dir) == F) {
@@
 # proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_v2.csv"), stringsAsFactors = F)
-proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_v3.csv"), stringsAsFactors = F)
+proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_FINAL.csv"), stringsAsFactors = F) %>%
+  dplyr::filter(include != "Hide")
 
@@
 plot_results <- proposal_results %>%
-  #dplyr::filter(run_id != "RD/TN/RL/103") %>%
   bind_rows(most_ambitious_results)
@@
 ```{r}
+# We want these to be ordered by date within each category, so we need to go back to our list
+date_order <- proposal_settings %>%
+  dplyr::select(title_tool, date) %>%
+  rownames_to_column("order") %>%
+  mutate(order = as.numeric(order))
+
+# Collect global results
 all_results_global_output_table <- plot_results %>%
@@
                 Variable) %>%
-  spread(Variable, Diff_tot)
+  spread(Variable, Diff_tot) %>%
+  left_join(date_order %>% dplyr::select(Name = title_tool, order), by = "Name") %>%
+  mutate(Category = factor(Category, levels = c("Ambitious Reform", "IUU", "OFOC", "Overfished", "Other & Multiple"))) %>%
+  arrange(Category, order, Year) %>%
+  dplyr::select(-order)
 
@@
   ungroup() %>%
-  arrange(Category, desc(Biomass)) %>%
   mutate(Biomass = round(Biomass*100, 3),
@@
                 Variable) %>%
-  spread(Variable, Diff)
+  spread(Variable, Diff) %>%
+  left_join(date_order %>% dplyr::select(Name = title_tool, order), by = "Name") %>%
+  mutate(Category = factor(Category, levels = c("Ambitious Reform", "IUU", "OFOC", "Overfished", "Other & Multiple"))) %>%
+  arrange(Region, Category, order, Year) %>%
+  dplyr::select(-order)
 
@@
   ungroup() %>%
-  arrange(Region, Category, desc(Biomass)) %>%
   mutate(Biomass = round(Biomass*100, 3),
@@
 ```{r}
-# Weight of a mature dairy cow in mt
-cow_weight <- 0.6803886
-
-all_results_global_cow_equivalent_table <- plot_results %>%
-  dplyr::filter(Year %in% c(2050, end_year)) %>%
-  dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
-  group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
-  summarize(BAU_tot = sum(BAU, na.rm = T),
-            Reform_tot = sum(Reform, na.rm = T),
-            abs_Diff_tot = case_when(BAU_tot != 0 ~ Reform_tot-BAU_tot,
-                                     TRUE ~ 0),
-            cow_Diff = abs_Diff_tot*cow_weight) %>%
-  ungroup() %>%
-  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
-                              Variable == "catches_total" ~ "Catches")) %>%
-  dplyr::select(Id = run_id,
-                Name = run_name,
-                Category = run_group, 
-                Year,
-                cow_Diff,
-                Variable) %>%
-  spread(Variable, cow_Diff)
-
-write.csv(all_results_global_cow_equivalent_table, paste0(results_dir, "all_results_global_cow_equivalent_table.csv"))
-
-all_results_regional_cow_equivalent_table <- plot_results %>%
-  dplyr::filter(Year %in% c(2050, end_year)) %>%
-  dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
-  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
-                                Variable == "catches_total" ~ "Catches")) %>%
-  mutate(abs_Diff = case_when(BAU != 0 ~ Reform-BAU,
-                              TRUE ~ 0),
-         cow_Diff = abs_Diff*cow_weight) %>%
-  dplyr::select(Id = run_id,
-                Name = run_name,
-                Category = run_group, 
-                Year,
-                Region,
-                cow_Diff,
-                Variable) %>%
-  spread(Variable, cow_Diff)
-
-write.csv(all_results_regional_cow_equivalent_table, paste0(results_dir, "all_results_regional_cow_equivalent_table.csv"))
+# # Weight of a mature dairy cow in mt
+# cow_weight <- 0.6803886
+# 
+# all_results_global_cow_equivalent_table <- plot_results %>%
+#   dplyr::filter(Year %in% c(2050, end_year)) %>%
+#   dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
+#   group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
+#   summarize(BAU_tot = sum(BAU, na.rm = T),
+#             Reform_tot = sum(Reform, na.rm = T),
+#             abs_Diff_tot = case_when(BAU_tot != 0 ~ Reform_tot-BAU_tot,
+#                                      TRUE ~ 0),
+#             cow_Diff = abs_Diff_tot*cow_weight) %>%
+#   ungroup() %>%
+#   mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
+#                               Variable == "catches_total" ~ "Catches")) %>%
+#   dplyr::select(Id = run_id,
+#                 Name = run_name,
+#                 Category = run_group, 
+#                 Year,
+#                 cow_Diff,
+#                 Variable) %>%
+#   spread(Variable, cow_Diff)
+# 
+# write.csv(all_results_global_cow_equivalent_table, paste0(results_dir, "all_results_global_cow_equivalent_table.csv"))
+# 
+# all_results_regional_cow_equivalent_table <- plot_results %>%
+#   dplyr::filter(Year %in% c(2050, end_year)) %>%
+#   dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
+#   mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
+#                                 Variable == "catches_total" ~ "Catches")) %>%
+#   mutate(abs_Diff = case_when(BAU != 0 ~ Reform-BAU,
+#                               TRUE ~ 0),
+#          cow_Diff = abs_Diff*cow_weight) %>%
+#   dplyr::select(Id = run_id,
+#                 Name = run_name,
+#                 Category = run_group, 
+#                 Year,
+#                 Region,
+#                 cow_Diff,
+#                 Variable) %>%
+#   spread(Variable, cow_Diff)
+# 
+# write.csv(all_results_regional_cow_equivalent_table, paste0(results_dir, "all_results_regional_cow_equivalent_table.csv"))
 

### 2022-02-22 app/00_initialize_app.R

@@ -277,7 +277,8 @@ sdt_lookup_table <- read_csv("./data/sdt_lookup_table.csv")
 # 2) Proposal settings
 #proposal_settings <- read.csv("./data/wto_proposal_settings.csv", stringsAsFactors = F)
 #proposal_settings <- read.csv("./data/wto_proposal_settings_v3.csv", stringsAsFactors = F)
-proposal_settings <- read.csv("./data/wto_proposal_settings_FINAL.csv", stringsAsFactors = F)
+proposal_settings <- read.csv("./data/wto_proposal_settings_FINAL.csv", stringsAsFactors = F) %>%
+  dplyr::filter(include != "Hide") # remove bad proposals
 
 # Proposal names
 included_proposals <- proposal_settings %>%

### 2022-02-22 app/scripts/CreateFleets.R

@@ -1035,8 +1035,6 @@ CreateFleets <- function(vessel_list,
         overcap_vessels_scope <- overcap_vessels_scope %>%
           dplyr::filter(distant_water | prop_fishing_KWh_high_seas >= (overcap$hs_cutoff/100))
         
-        browser()
-        
         # 7) Disputed areas  
       }else if("DISPUTE" %in% overcap$scope_select){
         

### 2022-04-15 scripts/01b_sdt_data_wrangling.Rmd

@@
 
-We also use our vessel list and definition of distant water fishing (described in other scripts) to identify countries fulfiling that criteria.
+**Fisheries Data**
+We use 2018 data from the FAO Global Marine Capture Database to determine each country's contribution to the global total.
+
+**Other**
+We also use our vessel list and the definition of distant water fishing provided below to identify countries meeting this criteria.
 
@@
 - GNI per capita is greater than \$5000 (constant 2015 US\$);
+- percentage of FAO annual global marine capture production (2018) is greater than 2%; 
 - they engage in distant water fishing;
 - the contribution from Agriculture, Forestry and Fishing to their national GDP is greater than 10%.
+
+We can get at conditions 1, 2, and 4 using the World Bank WDI database (FAO data is shared here directly)
 
@@
                    indicator = c("gdp_ffa_percent" = "NV.AGR.TOTL.ZS", # Added value coming from fisheries, forestry, and agriculture (%)
-                                 "gni_per_capita" = "NY.GNP.PCAP.KD"), # GNI per capita (constant 2015 US$)
+                                 "gni_per_capita" = "NY.GNP.PCAP.KD", # GNI per capita (constant 2015 US$)
+                                 "cap_production" = "ER.FSH.CAPT.MT"), # Capture fisheries production from FAO (mt)
                                   start = 2016,
@@
                 gdp_ffa_percent,
-                gni_per_capita) %>%
+                gni_per_capita,
+                cap_production) %>%
   mutate(iso3 = as.character(iso3)) %>%
-  arrange(iso3, year) %>%
+  arrange(iso3, year)
+
+wb_sdt_dat_working <- wb_sdt_dat %>%
+  group_by(year) %>%
+  mutate(tot_cap_production = sum(cap_production, na.rm = T)) %>%
+  ungroup() %>%
+  mutate(cap_production_percent = (cap_production/tot_cap_production)*100) %>%
   group_by(iso3) %>%
   mutate(n_exceeds_gdp_ffa = sum(gdp_ffa_percent > 10),
-         n_exceeds_gni_per_capita = sum(gni_per_capita > 5000)) %>%
+         n_exceeds_gni_per_capita = sum(gni_per_capita > 5000),
+         cap_prod_percent_2018 = cap_production_percent[year == 2018]) %>%
   ungroup()
 
-wb_sdt_dat_out <- wb_sdt_dat %>%
-  distinct(iso3, n_exceeds_gdp_ffa, n_exceeds_gni_per_capita) %>%
+wb_sdt_dat_out <- wb_sdt_dat_working %>%
+  distinct(iso3, n_exceeds_gdp_ffa, n_exceeds_gni_per_capita, cap_prod_percent_2018) %>%
   mutate(exceeds_gdp_ffa = case_when(n_exceeds_gdp_ffa == 3 ~ T,
@@
                                             is.na(n_exceeds_gni_per_capita) ~ F,
+                                            TRUE ~ F),
+         exceeds_capture_production = case_when(cap_prod_percent_2018 > 2 ~ T,
                                                 TRUE ~ F)) %>%
-  dplyr::select(-n_exceeds_gdp_ffa, -n_exceeds_gni_per_capita)
+  dplyr::select(-n_exceeds_gdp_ffa, -n_exceeds_gni_per_capita, -cap_prod_percent_2018)
 
 ```
+
+For the second condition, the text stipulates that Members only fishing in areas beyond their national jurisdiction that are within the FAO Major Fishing Area(s) that is/are directly adjacent to their coastline shall not be considered to be engaging in distant water fishing.
+So we first need to get a list of FAO regions bordering each coastline/encompassing each EEZ.
 
@@
 
-# Get flag states that participate in distant water fishing
-vessel_dat_dw <- vessel_dat %>%
-  distinct(flag_iso3, distant_water) %>%
-  dplyr::filter(distant_water == T)
+# Create eez/fao region lookup
+eez_fao_lookup <- vessel_dat %>%
+  dplyr::filter(eez_id != 0) %>%
+  distinct(eez_territory1_iso3, eez_territory2_iso3, eez_territory3_iso3, fao_region) %>%
+  gather(rank, eez_territory_iso3, 2:4) %>%
+  dplyr::filter(!is.na(eez_territory_iso3)) %>%
+  distinct(eez_territory_iso3, fao_region) %>%
+  arrange(eez_territory_iso3)
+
+# Now we need to filter our vessel list for entries where the flag state is fishing in a non-adjacent FAO area 
+# NOTE - This could include both high seas fishing, and fishing in EEZs where the flag state and administering state of the EEZ are not the same. 
+dw_states <- vessel_dat %>%
+  anti_join(eez_fao_lookup, by = c("flag_iso3" = "eez_territory_iso3", "fao_region")) %>%
+  distinct(flag_iso3) %>%
+  arrange(flag_iso3) %>%
+  mutate(distant_water = T)
+
+dw_states_hs_only <- vessel_dat %>%
+  dplyr::filter(eez_id == 0) %>%
+  anti_join(eez_fao_lookup, by = c("flag_iso3" = "eez_territory_iso3", "fao_region")) %>%
+  distinct(flag_iso3) %>%
+  arrange(flag_iso3) %>%
+  mutate(distant_water = T)
+
+# After looking at the results from both, I think we should just use the high seas definition because of the issues with flagging/ownership in the GFW data. 
 ```
@@
 sdt_dat_out <- wb_sdt_dat_out %>%
-  left_join(vessel_dat_dw, by = c("iso3" = "flag_iso3")) %>%
+  left_join(dw_states_hs_only, by = c("iso3" = "flag_iso3")) %>%
   mutate(distant_water = ifelse(is.na(distant_water), FALSE, distant_water)) %>%
-  mutate(meets_any_criteria = ifelse(exceeds_gdp_ffa | exceeds_gni_per_capita | distant_water, T, F))
+  mutate(meets_any_criteria = ifelse(exceeds_gdp_ffa | exceeds_gni_per_capita | exceeds_capture_production | distant_water, T, F))
 

### 2022-04-29 scripts/03_management.Rmd
updating SI management plots in preparation for final submission

@@
 }
+
+# Save data files? 
+save_files <- F
 ```
@@
 ```{r}
-# Get eez codes and cooresponding territories/sovereigns
+# Get eez codes and corresponding territories/sovereigns
 eez_info <- vessel_list_raw %>%
@@
   ggsave(paste0(results_dir, "fmi_score_map.png"), width = 7.5, height = 4, units = "in")
+
+  # Map by EEZ with the high seas FAO areas removed for PLOS ONE
+  hs_color <- RColorBrewer::brewer.pal(9, "YlGn")[1]
+
+  fmi_map_no_hs <- ggplot()+
+    geom_sf(data = world, fill = "black", color = "grey", size = 0.25)+
+    geom_sf(data = fmi_map_dat %>% dplyr::filter(!is.na(mrgid)), aes(fill = fmi_best), color = "grey", size = 0.25)+
+    theme_bw()+
+    scale_fill_distiller(palette = "YlGn", 
+                         direction = 1,
+                         limits = c(0.2, 1))+
+    labs(fill = "FMI Score")+
+    theme(plot.background = element_rect(color = NA),
+          panel.border = element_rect(color = NA),
+          panel.background = element_rect(fill = hs_color),
+          axis.text = element_blank(),
+          axis.ticks = element_blank())+
+    coord_sf(expand = F)
+
+  fmi_map_no_hs
+
+  ggsave(paste0(results_dir, "fmi_scores_no_hs_map.png"), width = 7.5, height = 4, units = "in")
 }
@@
   ggsave(paste0(results_dir, "fvfmsy_map.png"), width = 7.5, height = 9.5, units = "in")
+
+  # Make PLOS ONE friendly version 
+  fao_region_names <- c("77" = "Eastern Central part of the Pacific Ocean", 
+                          "71" = "Western Central part of the Pacific Ocean",
+                          "51" = "Western part of the Indian Ocean",
+                          "61" = "Northwestern part of the Pacific Ocean",
+                          "87" = "Southeastern part of the Pacific Ocean",
+                          "41" = "Southwestern part of the Atlantic Ocean",
+                          "34" = "Eastern Central part of the Atlantic Ocean",
+                          "47" = "Southeastern part of the Atlantic Ocean",
+                          "27" = "Northeastern part of the Atlantic Ocean",
+                          "81" = "Southwestern part of the Pacific Ocean",
+                          "21" = "Northwestern part of the Atlantic Ocean",
+                          "57" = "Eastern part of the Indian Ocean",
+                          "31" = "Western part of the Atlantic Ocean",
+                          "67" = "Northeastern part of the Pacific Ocean",
+                          "48" = "Antarctic part of the Atlantic Ocean",
+                          "88" = "Antarctic part of the Pacific Ocean",
+                          "58" = "Antarctic and Southern parts of the Indian Ocean",
+                          "18" = "Arctic Ocean",
+                          "37" = "Mediterranean and Black Sea")
+
+    fao_region_names_df <- tibble(fao_region = as.integer(names(fao_region_names)),
+                                  name = fao_region_names)
+
+  fvfmsy_plot_dat <- fvfmsy_map_dat %>%
+    st_drop_geometry() %>%
+    left_join(fao_region_names_df, by = "fao_region") %>%
+    mutate(display_name = paste0("Area ", fao_region, ": ", name))
+
+  fvfmsy_plot <- ggplot()+
+    geom_hline(yintercept = 1)+
+    geom_point(data = fvfmsy_plot_dat, aes(x = as.factor(display_name), y = value, fill = value, shape = metric_display), size = 3)+
+    theme_bw()+
+    scale_x_discrete(limits=rev)+
+    coord_flip()+
+    scale_fill_gradient2(low = "blue",
+                         high = 'red',
+                         mid = "white",
+                         midpoint = 1,
+                         limits = c(0,5),
+                         oob = scales::squish)+
+    labs(fill = "F/Fmsy", shape = "Value", x = "", y = "F/Fmsy")+
+    guides(fill = "none")+
+    scale_shape_manual(values = c(21,22,23))+
+    theme(plot.background = element_rect(color = NA),
+          #panel.border = element_rect(color = NA),
+          panel.grid.major = element_blank(),
+          panel.grid.minor = element_blank(),
+          legend.position = "bottom")
+
+    ggsave(paste0(results_dir, "fvfmsy_plot.png"), width = 7.5, height = 5, units = "in")
+
 }
@@
 
-# Proportion of formally assessed stocks by FAO region
+<!-- # Proportion of formally assessed stocks by FAO region -->
 
-# ```{r}
-# prop_assessed_stocks <- costello_2016_upsides_dat %>%
-#   group_by(region_fao_split) %>%
-#   summarize(catch_ram = sum(catch[dbase == "RAM"]),
-#             catch_other = sum(catch[dbase != "RAM"])) %>%
-#   mutate(catch_prop_ram = catch_ram/(catch_ram + catch_other)) %>%
-#   dplyr::select(fao_region = region_fao_split, catch_prop_ram)
-# ```
+<!-- # ```{r} -->
+<!-- # prop_assessed_stocks <- costello_2016_upsides_dat %>% -->
+<!-- #   group_by(region_fao_split) %>% -->
+<!-- #   summarize(catch_ram = sum(catch[dbase == "RAM"]), -->
+<!-- #             catch_other = sum(catch[dbase != "RAM"])) %>% -->
+<!-- #   mutate(catch_prop_ram = catch_ram/(catch_ram + catch_other)) %>% -->
+<!-- #   dplyr::select(fao_region = region_fao_split, catch_prop_ram) -->
+<!-- # ``` -->
 
-# Proportion of catch share stocks by FAO region
+<!-- # Proportion of catch share stocks by FAO region -->
 
-# ```{r}
-# prop_catch_share_stocks <- costello_2016_upsides_dat %>%
-#   group_by(region_fao_split) %>%
-#   summarize(catch_share= sum(catch[catch_share == 1]),
-#             catch_other = sum(catch[catch_share != 1])) %>%
-#   mutate(catch_prop_cs= catch_share/(catch_share + catch_other)) %>%
-#   dplyr::select(fao_region = region_fao_split, catch_prop_cs)
-# ```
+<!-- # ```{r} -->
+<!-- # prop_catch_share_stocks <- costello_2016_upsides_dat %>% -->
+<!-- #   group_by(region_fao_split) %>% -->
+<!-- #   summarize(catch_share= sum(catch[catch_share == 1]), -->
+<!-- #             catch_other = sum(catch[catch_share != 1])) %>% -->
+<!-- #   mutate(catch_prop_cs= catch_share/(catch_share + catch_other)) %>% -->
+<!-- #   dplyr::select(fao_region = region_fao_split, catch_prop_cs) -->
+<!-- # ``` -->
 
@@
 ```{r}
+# Apply management scores to vessel list
 vessel_list_manage <- vessel_list_raw %>%
@@
   left_join(median_fvfmsy_fao, by = c("fao_region"))
-  # left_join(prop_assessed_stocks, by = c("fao_region")) %>%
-  # left_join(prop_catch_share_stocks, by = c("fao_region"))
 
@@
 
+if(save_files){
 write_csv(vessel_list_manage, paste0(results_dir, "vessel_list_2018_management.csv"))
+}
+```
 
+```{r}
 # Calculate management quantiles for each indicator
@@
 ```
-
-```{r}
-
-```

### 2022-08-15 scripts/07_proposals.Rmd
running all proposals including final agreement for summary figures and tables

@@
 managed_cutoff <- 0.5
-
 end_year <- 2080
+folder_name <- paste0("mgmt_threshold_", managed_cutoff, "_FINAL_AGREEMENT/")
 
 # Directories for the output files generated by this script
-results_dir <- paste0(here::here("results", "07-proposals/"), "mgmt_threshold_", managed_cutoff, "_FINAL/")
+results_dir <- paste0(here::here("results", "07-proposals/"), folder_name)
 if (dir.exists(results_dir) == F) {
@@
 # proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_v2.csv"), stringsAsFactors = F)
-proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_FINAL.csv"), stringsAsFactors = F) %>%
+# proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_FINAL.csv"), stringsAsFactors = F) %>%
+#   dplyr::filter(include != "Hide")
+proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_FINAL_AGREEMENT.csv"), stringsAsFactors = F) %>%
   dplyr::filter(include != "Hide")
@@
 ```{r}
+if(make_plots){
   # A) global (aggregated) "kobe" final year plot
@@
 ggsave(paste0(results_dir, "Fig5.tiff"), figure_5, width = 7.5, height = 8)
-
+}
 ```
-
 ## Extract 2050 and end year results for all proposals and save as nice tables
@@
   ungroup() %>%
-  mutate(Biomass = round(Biomass*100, 3),
-         Catches = round(Catches*100, 3),
-         Revenue = round(Revenue*100, 3),
-         `Fishing Mortality` = round(`Fishing Mortality`*100, 3))
+  mutate(Biomass = round(Biomass*100, 2),
+         Catches = round(Catches*100, 2),
+         Revenue = round(Revenue*100, 2),
+         `Fishing Mortality` = round(`Fishing Mortality`*100, 2))
 
@@
 
-# Get rounded end values
+# Get rounded end values for the most ambitious scenario
 global_biomass_2050 <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == 2050 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
@@
 global_catches_end <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
+```
 
+```{r}
 # Now do regional
@@
 
-## Do the same with aboslute values
+## Do the same with absolute values
 
 ```{r}
-# all_results_global_absolute_table <- plot_results %>%
-#   dplyr::filter(Year %in% c(2050, end_year)) %>%
-#   dplyr::filter(Variable %in% c("biomass", "catches_total")) %>%
-#   group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
-#   summarize(BAU_tot = sum(BAU, na.rm = T),
-#             Reform_tot = sum(Reform, na.rm = T),
-#             abs_Diff_tot = case_when(BAU_tot != 0 ~ Reform_tot-BAU_tot,
-#                                      TRUE ~ 0)) %>%
-#   ungroup() %>%
-#   mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
-#                               Variable == "catches_total" ~ "Catches")) %>%
-#   dplyr::select(Id = run_id,
-#                 Name = run_name,
-#                 Category = run_group, 
-#                 Year,
-#                 abs_Diff_tot,
-#                 Variable) %>%
-#   spread(Variable, abs_Diff_tot)
-# 
+# # We want these to be ordered by date within each category, so we need to go back to our list
+# date_order <- proposal_settings %>%
+#   dplyr::select(title_tool, date) %>%
+#   rownames_to_column("order") %>%
+#   mutate(order = as.numeric(order))
+
+# Collect global results
+all_results_global_output_table_absolute <- plot_results %>%
+  dplyr::filter(Year %in% c(2050, end_year)) %>%
+  dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total")) %>%
+  group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
+  summarize(BAU_tot = sum(BAU, na.rm = T),
+            Reform_tot = sum(Reform, na.rm = T),
+            Diff_tot = case_when(BAU_tot != 0 ~ Reform_tot - BAU_tot,
+                            TRUE ~ 0)) %>%
+  ungroup() %>%
+  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
+                                Variable == "catches_total" ~ "Catches",
+                                Variable == "revenue_total" ~ "Revenue")) %>%
+  dplyr::select(Id = run_id,
+                Name = run_name,
+                Category = run_group, 
+                Year,
+                Diff_tot_absolute = Diff_tot,
+                Variable) %>%
+  spread(Variable, Diff_tot_absolute) %>%
+  left_join(date_order %>% dplyr::select(Name = title_tool, order), by = "Name") %>%
+  mutate(Category = factor(Category, levels = c("Ambitious Reform", "IUU", "OFOC", "Overfished", "Other & Multiple"))) %>%
+  arrange(Category, order, Year) %>%
+  dplyr::select(-order)
+
+write.csv(all_results_global_output_table_absolute, paste0(results_dir, "all_results_global_output_table_absolute.csv"))
+
 # write.csv(all_results_global_absolute_table, paste0(results_dir, "all_results_global_absolute_table.csv"))

### 2022-09-20 scripts/10_final_proposal_database.Rmd
final database

--- 2022-08-15 scripts/07_proposals.Rmd
@@
 
-title: "SubsidyExplorer - Step 7: Pre-Populated Proposals"
+title: "SubsidyExplorer - Step 10: Final database of all pre-populated reform proposals"
 author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
@@
 
-This script generates the most ambitious global and regional results obtained by removing all capacity enhancing subsidies from all WTO Members and Observers.
+This script generates databases of results (global and regional) for all pre-populated proposals contained within the SubsidyExplorer tool.
+This includes the most ambitious global and regional results obtained by removing all capacity enhancing subsidies from all WTO Members and Observers.
 
@@
 end_year <- 2080
-folder_name <- paste0("mgmt_threshold_", managed_cutoff, "_FINAL_AGREEMENT/")
+folder_name <- paste0("mgmt_threshold_", managed_cutoff, "_ALL/")
 
 # Directories for the output files generated by this script
-results_dir <- paste0(here::here("results", "07-proposals/"), folder_name)
+results_dir <- paste0(here::here("results", "10-final-database/"), folder_name)
 if (dir.exists(results_dir) == F) {
@@
 # Load vessel list
-vessel_dat <- read.csv(here::here("app", "data", "vessel_list_2018_final.csv"), stringsAsFactors = F) %>%
+vessel_dat_raw <- read.csv(here::here("app", "data", "vessel_list_2018_final.csv"), stringsAsFactors = F) %>%
   left_join(country_dependencies %>% dplyr::select(iso3, is_WTO), by = c("flag_iso3" = "iso3"))
@@
 
-vessel_dat <- vessel_dat %>%
+vessel_dat <- vessel_dat_raw %>%
    mutate(B1_subs = B1_subs * rel$rel_effect_effort[rel$type == "B1"], 
@@
 ```{r}
-# Proposal settings
-#proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings.csv"), stringsAsFactors = F)
-# proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_v2.csv"), stringsAsFactors = F)
-# proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_FINAL.csv"), stringsAsFactors = F) %>%
-#   dplyr::filter(include != "Hide")
+# Load proposal settings
 proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_FINAL_AGREEMENT.csv"), stringsAsFactors = F) %>%
@@
 
-# Proposal names
+# Filter to final list of proposals to be included in database
 included_proposals <- proposal_settings %>%
@@
   arrange(category) %>%
-  dplyr::filter(!(proposal %in% c("RD/TN/RL/126/Rev.2", "RD/TN/RL/119/Rev.1"))) # remove blank entries for tool
+  dplyr::filter(!(proposal %in% c("RD/TN/RL/126/Rev.2", "RD/TN/RL/119/Rev.1"))) %>% # remove blank entries created for tool
+  dplyr::filter(proposal != "Default")
 
@@
 ```{r}
-# 1) Cap/tier lookup table
+# Load cap/tier lookup table
 cap_tier_lookup_table <- read_csv(here::here("app","data","cap_tier_lookup_table.csv"))
 
-# S&DT lookup table
+# Load S&DT lookup table
 sdt_lookup_table <- read_csv(here::here("app", "data", "sdt_lookup_table.csv"))
-
 ```
-
 ## Model proposals
@@
 proposal_results <- NULL
+affected_subs <- NULL
 
-for(i in 2:length(proposal_choices)){
+for(i in 1:length(proposal_choices)){
 
@@
 
-   ### Find fleets
+   # Find fleets
     fleet <-  CreateFleets(
@@
 
-    # Make list
+    # Make list of fleets for bioeconomic model
     fleet_list <- fleet$summary %>%
@@
 
-    # Extract results timeseries
-    results_all <- results %>%
+    # Extract model timeseries results
+    results_ts <- results %>%
       dplyr::filter(Year > 2018) %>%
@@
 
-      write_csv(results_all, paste0(results_dir, str_replace_all(names(proposal_name), "/", "_"), ".csv"))
+      write_csv(results_ts, paste0(results_dir, str_replace_all(names(proposal_name), "/", "_"), ".csv"))
 
@@
       proposal_results <- proposal_results %>%
-        bind_rows(results_all)
+        bind_rows(results_ts)
+
+    # Extract affected/unaffected subsidies amounts and convert back to absolute dollars
+      affected_subs_raw <- fleet$vessels %>%
+        group_by(region) %>%
+        summarize_at(vars(A1_subs:C3_subs, A1_subs_removed:C3_subs_removed), sum, na.rm = T) %>%
+        gather("type", "value", -region) %>%
+        mutate(category = ifelse(grepl("removed", type), "removed", "base")) %>%
+        mutate(type = str_replace(type, "_subs_removed", "")) %>%
+        mutate(type = str_replace(type, "_subs", "")) %>%
+        left_join(rel, by = "type") %>%
+        mutate(rel_effect_effort = ifelse(is.na(rel_effect_effort), 1, rel_effect_effort)) %>%
+        mutate(value_real = value/rel_effect_effort) %>%
+        group_by(region, category) %>%
+        summarize(value_real = sum(value_real, na.rm = T)) %>%
+        ungroup() %>%
+        group_by(region) %>%
+        summarize(subs_base = value_real[category == "base"],
+                  subs_affected = value_real[category == "removed"],
+                  percent_subs_affected = (value_real[category == "removed"]/value_real[category == "base"])*100)
+
+      affected_subs_out <- data_frame(run_id = rep(proposal_name, length.out = 3),
+                                      run_name = rep(names(proposal_name), length.out = 3),
+                                      run_group = rep(unique(proposal_settings$category[proposal_settings$proposal == proposal_name]), length.out = 3),
+                                      region = c("atlantic", "indian", "pacific")) %>%
+        left_join(affected_subs_raw, by = "region")
+
+      # Add to data frame
+      affected_subs <- affected_subs %>%
+        bind_rows(affected_subs_out)
 
@@
 
-Make plots with all proposals and the most ambitious result
+Add in most ambitious result and combine into single dataset
 
@@
 
-plot_results <- proposal_results %>%
+# Combine with ts data
+all_ts_results <- proposal_results %>%
   bind_rows(most_ambitious_results)
 
-# Make plots
-if(make_plots){
+# Get subsidies affected for most ambitious scenario
+most_ambitious_subs_affected <- vessel_dat_raw %>%
+  mutate(subs_base = bad_subs + good_subs + ugly_subs,
+         subs_affected = bad_subs + ugly_subs) %>%
+  group_by(region) %>%
+  summarize(subs_base = sum(subs_base, na.rm = T),
+            subs_affected = sum(subs_affected, na.rm = T)) %>%
+  mutate(percent_subs_affected = (subs_affected/subs_base)*100)
 
-  # 1) global (aggregated) timeseries plot
-  compare_ts_plot <- BioEconomicModelPlots(dat = plot_results,
-                                           spatial_res = "global",
-                                           temporal_res = "all",
-                                           start_year = 2018,
-                                           end_year = end_year,
-                                           plot_name = "all_proposals_ts_plot",
-                                           plot_width = 8,
-                                           plot_height = 10,
-                                           results_dir = results_dir,
-                                           group_var = "run_id",
-                                           color_var = "run_group",
-                                           legend_pos_manual = "bottom",
-                                           legend_name = "Scenario Type")
-
-  # 2) global (aggregated) "kobe" final year plot
-  compare_end_plot <- BioEconomicModelPlots(dat = plot_results,
-                                            spatial_res = "global",
-                                            temporal_res = "last",
-                                            end_year = end_year,
-                                            plot_name = "all_proposals_end_plot",
-                                            plot_width = 8,
-                                            plot_height = 6,
-                                            results_dir = results_dir,
-                                            group_var = "run_id",
-                                            color_var = "run_group",
-                                            legend_pos_manual = "bottom",
-                                            legend_name = "Scenario Type")
-
-  # 2) global (aggregated) "kobe" final year plot
-  compare_2050_plot <- BioEconomicModelPlots(dat = plot_results,
-                                            spatial_res = "global",
-                                            temporal_res = "last",
-                                            end_year = 2050,
-                                            plot_name = "all_proposals_2050_plot",
-                                            plot_width = 7.5,
-                                            plot_height = 4,
-                                            results_dir = results_dir,
-                                            group_var = "run_id",
-                                            color_var = "run_group",
-                                            legend_pos_manual = "bottom",
-                                            legend_name = "Scenario Type")
-
-  # 3) regional timeseries plot
-  regional_compare_ts_plot <- BioEconomicModelPlots(dat = plot_results,
-                                                    spatial_res = "regional",
-                                                    temporal_res = "all",
-                                                    start_year = 2018,
-                                                    end_year = end_year,
-                                                    plot_name = "regional_all_proposals_ts_plot",
-                                                    plot_width = 12,
-                                                    plot_height = 10,
-                                                    results_dir = results_dir,
-                                                    group_var = "run_id",
-                                                    color_var = "run_group",
-                                                    legend_pos_manual = "bottom",
-                                                    legend_name = "Scenario Type")
-
-  # 4) regional "kobe" final year plot
-  regional_compare_end_plot <- BioEconomicModelPlots(dat = plot_results,
-                                                     spatial_res = "regional",
-                                                     temporal_res = "last",
-                                                     end_year = end_year,
-                                                     plot_name = "regional_all_proposals_end_plot",
-                                                     plot_width = 12,
-                                                     plot_height = 8,
-                                                     results_dir = results_dir,
-                                                     group_var = "run_id",
-                                                     color_var = "run_group",
-                                                     legend_pos_manual = "bottom",
-                                                     legend_name = "Scenario Type")
-
-  # 4) regional "kobe" final year plot
-  regional_compare_2050_plot <- BioEconomicModelPlots(dat = plot_results,
-                                                     spatial_res = "regional",
-                                                     temporal_res = "last",
-                                                     end_year = 2050,
-                                                     plot_name = "regional_all_proposals_2050_plot",
-                                                     plot_width = 12,
-                                                     plot_height = 8,
-                                                     results_dir = results_dir,
-                                                     group_var = "run_id",
-                                                     color_var = "run_group",
-                                                     legend_pos_manual = "bottom",
-                                                     legend_name = "Scenario Type")
-}
+# Combine with subs affected data
+all_subs_affected <- data_frame(run_id = rep("Ambitious Reform", 3),
+                                run_name = rep("All bad and ugly subsidies", 3),
+                                run_group = rep("Ambitious Reform", 3)) %>%
+  bind_cols(most_ambitious_subs_affected) %>%
+  bind_rows(affected_subs)
 ```
 
-```{r}
-if(make_plots){
-  # A) global (aggregated) "kobe" final year plot
-  box_2050_plot <- BioEconomicModelPlots(dat = plot_results,
-                                            spatial_res = "global",
-                                            temporal_res = "last",
-                                            end_year = 2050,
-                                            plot_name = "box_scenario_type_2050_plot",
-                                            plot_width = 7.5,
-                                            plot_height = 6,
-                                            results_dir = results_dir,
-                                            group_var = "run_group",
-                                            color_var = "run_group",
-                                            legend_pos_manual = "bottom",
-                                            legend_name = "Scenario Type",
-                                            plot_type = "box")
-
-figure_5 <- cowplot::plot_grid(box_2050_plot, compare_2050_plot, ncol = 1, rel_heights = c(1,0.75), axis = "lr", align = "v", labels = c("(A)", "(B)"), hjust = -1)
-ggsave(paste0(results_dir, "Fig5.tiff"), figure_5, width = 7.5, height = 8)
-}
-```
-## Extract 2050 and end year results for all proposals and save as nice tables
+## Make nice databases (global and regional)
 
@@
 # Collect global results
-all_results_global_output_table <- plot_results %>%
+all_results_global_output_table <- all_ts_results %>%
   dplyr::filter(Year %in% c(2050, end_year)) %>%
@@
          Revenue = round(Revenue*100, 2),
-         `Fishing Mortality` = round(`Fishing Mortality`*100, 2))
+         `Fishing Mortality` = round(`Fishing Mortality`*100, 2)) %>%
+  rename(`Change in biomass (%, 2050)` = Biomass,
+         `Change in catch (%, 2050)` = Catches,
+         `Change in revenue (%, 2050)` = Revenue,
+         `Change in fishing mortality (%, 2050)` = `Fishing Mortality`) %>%
+  dplyr::select(-Year)
 
@@
 
-# Now make a min, max, and average for each proposal type
-summary_results_global_2050_pretty <- all_results_global_output_table_2050_pretty %>%
-  gather(Variable, Value, c("Biomass", "Catches", "Revenue", "Fishing Mortality")) %>%
-  group_by(Category, Year, Variable) %>%
-  summarize(Minimum = min(Value, na.rm = T),
-            Maximum = max(Value, na.rm = T),
-            Median = median(Value, na.rm = T),
-            Mean = mean(Value, na.rm = T)) %>%
-  arrange(Category)
+# Now make a pretty version for 2080 only
+all_results_global_output_table_2080_pretty <- all_results_global_output_table %>%
+  dplyr::filter(Year == 2080) %>%
+  ungroup() %>%
+  mutate(Biomass = round(Biomass*100, 2),
+         Catches = round(Catches*100, 2),
+         Revenue = round(Revenue*100, 2),
+         `Fishing Mortality` = round(`Fishing Mortality`*100, 2)) %>%
+  rename(`Change in biomass (%, 2080)` = Biomass,
+         `Change in catch (%, 2080)` = Catches,
+         `Change in revenue (%, 2080)` = Revenue,
+         `Change in fishing mortality (%, 2080)` = `Fishing Mortality`) %>%
+  dplyr::select(-Year)
 
-write.csv(summary_results_global_2050_pretty, paste0(results_dir, "summary_results_global_2050_pretty.csv"))
+write.csv(all_results_global_output_table_2080_pretty, paste0(results_dir, "all_results_global_output_table_2080_pretty.csv"))
 
-# Get rounded end values for the most ambitious scenario
-global_biomass_2050 <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == 2050 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
-global_biomass_end <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
+# Combine
+all_results_global_output_table_pretty <- all_results_global_output_table_2050_pretty %>%
+  left_join(all_results_global_output_table_2080_pretty %>% dplyr::select(-Name, -Category))
 
-global_catches_2050 <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == 2050 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
-global_catches_end <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
+write.csv(all_results_global_output_table_pretty, paste0(results_dir, "all_results_global_output_table_pretty.csv"))
+
+# Now let's get affected subs globally
+all_subs_affected_global <- all_subs_affected %>%
+  group_by(run_id, run_name, run_group) %>%
+  summarize(subs_base = sum(subs_base),
+            subs_affected = sum(subs_affected)) %>%
+  ungroup() %>%
+  mutate(percent_subs_affected = round((subs_affected/subs_base)*100, 2))
+
+# And add to table
+global_database <- all_results_global_output_table_pretty %>%
+  left_join(all_subs_affected_global %>% dplyr::select(Id = run_id, subs_affected, percent_subs_affected)) %>%
+  rename(`Subsidies affected ($)` = subs_affected,
+         `Subsidies affected (%)` = percent_subs_affected)
+
+write.csv(global_database, paste0(results_dir, "SubsidyExplorer_proposal_results_global.csv"))
 ```
@@
 # Now do regional
-all_results_regional_output_table <- plot_results %>%
+all_results_regional_output_table <- all_ts_results %>%
   dplyr::filter(Year %in% c(2050, end_year)) %>%
@@
          Revenue = round(Revenue*100, 2),
-         `Fishing Mortality` = round(`Fishing Mortality`*100, 2))
+         `Fishing Mortality` = round(`Fishing Mortality`*100, 2)) %>%
+  rename(`Change in biomass (%, 2050)` = Biomass,
+         `Change in catch (%, 2050)` = Catches,
+         `Change in revenue (%, 2050)` = Revenue,
+         `Change in fishing mortality (%, 2050)` = `Fishing Mortality`) %>%
+  dplyr::select(-Year) %>%
+  mutate(Region = case_when(Region == "atlantic" ~ "Atlantic Ocean",
+                            Region == "indian" ~ "Indian Ocean",
+                            Region == "pacific" ~ "Pacific Ocean"))
 
@@
 
-# Now make a min, max, and average for each proposal type
-summary_results_regional_2050_pretty <- all_results_regional_output_table_2050_pretty %>%
-  gather(Variable, Value, c("Biomass", "Catches", "Revenue", "Fishing Mortality")) %>%
-  group_by(Region, Category, Year, Variable) %>%
-  summarize(Minimum = min(Value, na.rm = T),
-            Maximum = max(Value, na.rm = T),
-            Median = median(Value, na.rm = T),
-            Mean = mean(Value, na.rm = T)) %>%
-  arrange(Region, Category)
+# Now make a pretty version for 2080 only
+all_results_regional_output_table_2080_pretty <- all_results_regional_output_table %>%
+  dplyr::filter(Year == 2080) %>%
+  ungroup() %>%
+  mutate(Biomass = round(Biomass*100, 2),
+         Catches = round(Catches*100, 2),
+         Revenue = round(Revenue*100, 2),
+         `Fishing Mortality` = round(`Fishing Mortality`*100, 2)) %>%
+  rename(`Change in biomass (%, 2080)` = Biomass,
+         `Change in catch (%, 2080)` = Catches,
+         `Change in revenue (%, 2080)` = Revenue,
+         `Change in fishing mortality (%, 2080)` = `Fishing Mortality`) %>%
+  dplyr::select(-Year) %>%
+  mutate(Region = case_when(Region == "atlantic" ~ "Atlantic Ocean",
+                            Region == "indian" ~ "Indian Ocean",
+                            Region == "pacific" ~ "Pacific Ocean"))
 
-write.csv(summary_results_regional_2050_pretty, paste0(results_dir, "summary_results_regional_2050_pretty.csv"))
+write.csv(all_results_regional_output_table_2080_pretty, paste0(results_dir, "all_results_regional_output_table_2080_pretty.csv"))
+
+# Combine
+all_results_regional_output_table_pretty <- all_results_regional_output_table_2050_pretty %>%
+  left_join(all_results_regional_output_table_2080_pretty %>% dplyr::select(-Name, -Category))
+
+write.csv(all_results_regional_output_table_pretty, paste0(results_dir, "all_results_regional_output_table_pretty.csv"))
+
+# And add affected subsidies to table
+regional_database <- all_results_regional_output_table_pretty %>%
+  left_join(all_subs_affected %>%
+              mutate(region = case_when(region == "atlantic" ~ "Atlantic Ocean",
+                                        region == "indian" ~ "Indian Ocean",
+                                        region == "pacific" ~ "Pacific Ocean")) %>%
+              mutate(percent_subs_affected = round(percent_subs_affected, 2)) %>%
+              dplyr::select(Id = run_id, Region = region, subs_affected, percent_subs_affected)) %>%
+  rename(`Subsidies affected ($)` = subs_affected,
+         `Subsidies affected (%)` = percent_subs_affected)
+
+write.csv(regional_database, paste0(results_dir, "SubsidyExplorer_proposal_results_regional.csv"))
+```
+
+```{r}
+# # Now make a min, max, and average for each proposal type
+# summary_results_global_2050_pretty <- all_results_global_output_table_2050_pretty %>%
+#   gather(Variable, Value, c("Biomass", "Catches", "Revenue", "Fishing Mortality")) %>%
+#   group_by(Category, Year, Variable) %>%
+#   summarize(Minimum = min(Value, na.rm = T),
+#             Maximum = max(Value, na.rm = T),
+#             Median = median(Value, na.rm = T),
+#             Mean = mean(Value, na.rm = T)) %>%
+#   arrange(Category)
+# 
+# write.csv(summary_results_global_2050_pretty, paste0(results_dir, "summary_results_global_2050_pretty.csv"))
+# 
+# # Get rounded end values for the most ambitious scenario
+# global_biomass_2050 <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == 2050 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
+# global_biomass_end <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
+# 
+# global_catches_2050 <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == 2050 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
+# global_catches_end <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2)
+
+# # Now make a min, max, and average for each proposal type
+# summary_results_regional_2050_pretty <- all_results_regional_output_table_2050_pretty %>%
+#   gather(Variable, Value, c("Biomass", "Catches", "Revenue", "Fishing Mortality")) %>%
+#   group_by(Region, Category, Year, Variable) %>%
+#   summarize(Minimum = min(Value, na.rm = T),
+#             Maximum = max(Value, na.rm = T),
+#             Median = median(Value, na.rm = T),
+#             Mean = mean(Value, na.rm = T)) %>%
+#   arrange(Region, Category)
+# 
+# write.csv(summary_results_regional_2050_pretty, paste0(results_dir, "summary_results_regional_2050_pretty.csv"))
+```
+
+## Plots
+
+```{r}
+if(make_plots){
+  # A) global (aggregated) "kobe" final year plot
+  box_2050_plot <- BioEconomicModelPlots(dat = all_ts_results,
+                                         spatial_res = "global",
+                                         temporal_res = "last",
+                                         end_year = 2050,
+                                         plot_name = "box_scenario_type_2050_plot",
+                                         plot_width = 7.5,
+                                         plot_height = 6,
+                                         results_dir = results_dir,
+                                         group_var = "run_group",
+                                         color_var = "run_group",
+                                         legend_pos_manual = "bottom",
+                                         legend_name = "Scenario Type",
+                                         plot_type = "box")
+
+ggsave(paste0(results_dir, "proposal_effects_2050_boxplot.tiff"), box_2050_plot, width = 7.5, height = 6)
+}
 ```
@@
 #   mutate(order = as.numeric(order))
-
-# Collect global results
-all_results_global_output_table_absolute <- plot_results %>%
-  dplyr::filter(Year %in% c(2050, end_year)) %>%
-  dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total")) %>%
-  group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
-  summarize(BAU_tot = sum(BAU, na.rm = T),
-            Reform_tot = sum(Reform, na.rm = T),
-            Diff_tot = case_when(BAU_tot != 0 ~ Reform_tot - BAU_tot,
-                            TRUE ~ 0)) %>%
-  ungroup() %>%
-  mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
-                                Variable == "catches_total" ~ "Catches",
-                                Variable == "revenue_total" ~ "Revenue")) %>%
-  dplyr::select(Id = run_id,
-                Name = run_name,
-                Category = run_group, 
-                Year,
-                Diff_tot_absolute = Diff_tot,
-                Variable) %>%
-  spread(Variable, Diff_tot_absolute) %>%
-  left_join(date_order %>% dplyr::select(Name = title_tool, order), by = "Name") %>%
-  mutate(Category = factor(Category, levels = c("Ambitious Reform", "IUU", "OFOC", "Overfished", "Other & Multiple"))) %>%
-  arrange(Category, order, Year) %>%
-  dplyr::select(-order)
-
-write.csv(all_results_global_output_table_absolute, paste0(results_dir, "all_results_global_output_table_absolute.csv"))
+# 
+# # Collect global results
+# all_results_global_output_table_absolute <- plot_results %>%
+#   dplyr::filter(Year %in% c(2050, end_year)) %>%
+#   dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total")) %>%
+#   group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>%
+#   summarize(BAU_tot = sum(BAU, na.rm = T),
+#             Reform_tot = sum(Reform, na.rm = T),
+#             Diff_tot = case_when(BAU_tot != 0 ~ Reform_tot - BAU_tot,
+#                             TRUE ~ 0)) %>%
+#   ungroup() %>%
+#   mutate(Variable = case_when(Variable == "biomass" ~ "Biomass",
+#                                 Variable == "catches_total" ~ "Catches",
+#                                 Variable == "revenue_total" ~ "Revenue")) %>%
+#   dplyr::select(Id = run_id,
+#                 Name = run_name,
+#                 Category = run_group, 
+#                 Year,
+#                 Diff_tot_absolute = Diff_tot,
+#                 Variable) %>%
+#   spread(Variable, Diff_tot_absolute) %>%
+#   left_join(date_order %>% dplyr::select(Name = title_tool, order), by = "Name") %>%
+#   mutate(Category = factor(Category, levels = c("Ambitious Reform", "IUU", "OFOC", "Overfished", "Other & Multiple"))) %>%
+#   arrange(Category, order, Year) %>%
+#   dplyr::select(-order)
+# 
+# write.csv(all_results_global_output_table_absolute, paste0(results_dir, "all_results_global_output_table_absolute.csv"))
 

### 2022-09-20 scripts/11_final_proposal_database.Rmd
renaming

--- 2022-09-20 scripts/10_final_proposal_database.Rmd
@@
 
-title: "SubsidyExplorer - Step 10: Final database of all pre-populated reform proposals"
+title: "SubsidyExplorer - Step 11: Final database of all pre-populated reform proposals"
 author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
@@
 # Directories for the output files generated by this script
-results_dir <- paste0(here::here("results", "10-final-database/"), folder_name)
+results_dir <- paste0(here::here("results", "11-final-database/"), folder_name)
 if (dir.exists(results_dir) == F) {

### 2022-09-21 scripts/10_high_seas_vessel_breakdown.Rmd
high seas vessel characteristics

---
output:
  html_document: default

title: "SubsidyExplorer - Step 10: Exploring high seas vessels"
author: "Kat Millage, Vienna Saccomanno, Laura Lea Rubino, Christopher Costello"
date: "`r format(Sys.time(), '%B %d, %Y')`"
fontsize: 11pt
bibliography: "../pew-subsidies.bib"
---

# Introduction

This script explores a couple of different ways of differentiating between high seas vessels in order to explore possible ways of refining the high seas assumption for the final agreement. The following breakdowns are considered: 
- Gear type
- Size class
- GT class
- Engine power class

```{r setup, include=FALSE}
# Load packages
library(knitr) 
library(tidyverse)
library(countrycode)

knitr::opts_chunk$set(echo = TRUE)

make_plots <- T

if(make_plots){
  library(RColorBrewer)
  library(scales)
}

bad_subsidy_types <- c("B1", "B2", "B3", "B4", "B5", "B6", "B7")
ugly_subsidy_types <- c("C1", "C2", "C3")
good_subsidy_types <- c("A1", "A2", "A3")

subsidy_types_sorted_sumaila <- c(good_subsidy_types, bad_subsidy_types, ugly_subsidy_types)

# # Threshold to be considered managed (using FMI scores)
# managed_cutoff <- 0.5
# end_year <- 2080
# folder_name <- paste0("mgmt_threshold_", managed_cutoff, "_ALL/")

# Directories for the output files generated by this script
results_dir <- paste0(here::here("results", "10-high-seas-vessel-breakdowns/"))
if (dir.exists(results_dir) == F) {
  dir.create(results_dir, recursive = T)
}
```

```{r}
# # Source model script
# source(here::here("app", "scripts", "BioEconModel.R"))
# 
# # Source create fleets script
# source(here::here("app", "scripts", "CreateFleets.R"))
# 
# # Source plotting script
# source(here::here("scripts", "functions", "BioEconomicModelPlots.R"))
```

```{r}
# # Load country dependencies helper file
# country_dependencies <- read_csv(here::here("app", "data", "country_dependencies.csv")) %>%
#    mutate(display_name = case_when(!is.na(WTO_name) ~ WTO_name,
#                                   iso3 == "ANT" ~ "Netherlands Antilles",
#                                   iso3 == "ASC" ~ "Ascension Island", 
#                                   iso3 == "CPT" ~ "Clipperton Island",
#                                   iso3 == "TAA" ~ "Tristan da Cunha",
#                                   TRUE ~ countrycode(iso3, "iso3c", "country.name"))) %>%
#   arrange(sovereign_iso3) 
# 
# # Vector of all WTO Members and Observers for use in the app [does not include the overseas territories associated with them]
# wto_members_and_observers <- country_dependencies$iso3[country_dependencies$is_WTO & !country_dependencies$is_overseas_territory]
```

```{r}
# Load vessel list
vessel_dat_raw <- read.csv(here::here("app", "data", "vessel_list_2018_final.csv"), stringsAsFactors = F) %>%
  left_join(country_dependencies %>% dplyr::select(iso3, is_WTO), by = c("flag_iso3" = "iso3"))

rel <- read_csv(here::here("data", "lookup-tables", "oecd_relative_effects_lookup_table.csv"))

vessel_dat <- vessel_dat_raw %>%
   mutate(B1_subs = B1_subs * rel$rel_effect_effort[rel$type == "B1"], 
           B2_subs = B2_subs * rel$rel_effect_effort[rel$type == "B2"],
           B3_subs = B3_subs * rel$rel_effect_effort[rel$type == "B3"],
           B4_subs = B4_subs * rel$rel_effect_effort[rel$type == "B4"],
           B5_subs = B5_subs * rel$rel_effect_effort[rel$type == "B5"], 
           B6_subs = B6_subs * rel$rel_effect_effort[rel$type == "B6"],
           B7_subs = B7_subs * rel$rel_effect_effort[rel$type == "B7"], 
           C1_subs = C1_subs * rel$rel_effect_effort[rel$type == "C1"], 
           C2_subs = C2_subs * rel$rel_effect_effort[rel$type == "C2"],
           C3_subs = C3_subs * rel$rel_effect_effort[rel$type == "C3"]) %>%
  ungroup() %>%
  mutate(bad_subs = rowSums(select(., one_of(paste0(bad_subsidy_types, "_subs")))),
         ugly_subs = rowSums(select(., one_of(paste0(ugly_subsidy_types, "_subs")))),
         good_subs = rowSums(select(., one_of(paste0(good_subsidy_types, "_subs")))),
         bad_ugly_subs = rowSums(select(., one_of(paste0(c(bad_subsidy_types, ugly_subsidy_types), "_subs")))))

# Create high seas code
vessel_dat <- vessel_dat %>%
  mutate(eez_hs_code = case_when(eez_id == 0 ~ paste0("HS-", fao_region),
                                 TRUE ~ as.character(eez_id)))
```

## Get high seas vessels (at least 5% of annual effort on the high seas)

```{r}
hs_vessel_dat <- vessel_dat_raw %>%
  dplyr::filter(prop_fishing_KWh_high_seas >= 0.05)

```

## Gear type breakdown

```{r}
gear_type_breakdown <- hs_vessel_dat %>%
  group_by(vessel_class) %>%
  summarize(bad_subs = sum(bad_subs, na.rm = T))

gear_type_breakdown_plot <- gear_type_breakdown %>%
  ggplot()+
  aes(x = vessel_class, y = bad_subs/1e9)+
  geom_bar(stat = "identity")+
  theme_linedraw()+
  coord_flip()+
  labs(x = "Gear type",
       y = "Capacity-enhancing subsidies ($, billions)")

ggsave(paste0(results_dir, "hs_gear_type_breakdown.png"), gear_type_breakdown_plot, width = 7.5, height = 6)
```

## Length breakdown

```{r}
length_breakdown <- hs_vessel_dat %>%
  mutate(bin = cut(length_m, seq(min(length_m), max(length_m) + 10, 10))) %>%
  group_by(bin) %>%
  summarize(bad_subs = sum(bad_subs, na.rm = T))

length_breakdown_plot <- length_breakdown %>%
  ggplot()+
  aes(x = bin, y = bad_subs/1e9)+
  geom_bar(stat = "identity")+
  theme_linedraw()+
  coord_flip()+
  labs(x = "Total length (m)",
       y = "Capacity-enhancing subsidies ($, billions)")

ggsave(paste0(results_dir, "hs_length_breakdown.png"), length_breakdown_plot, width = 7.5, height = 6)
```
## Tonnage breakdown

```{r}
tonnage_breakdown <- hs_vessel_dat %>%
  mutate(bin = cut(tonnage_gt, seq(min(tonnage_gt), max(tonnage_gt) + 100, 100))) %>%
  group_by(bin) %>%
  summarize(bad_subs = sum(bad_subs, na.rm = T))

tonnage_breakdown_plot <- tonnage_breakdown %>%
  ggplot()+
  aes(x = bin, y = bad_subs/1e9)+
  geom_bar(stat = "identity")+
  theme_linedraw()+
  coord_flip()+
  labs(x = "Tonnage (gt)",
       y = "Capacity-enhancing subsidies ($, billions)")

ggsave(paste0(results_dir, "hs_tonnage_breakdown.png"), tonnage_breakdown_plot, width = 7.5, height = 8)
```

## Engine power breakdown

```{r}
engine_power_breakdown <- hs_vessel_dat %>%
  mutate(bin = cut(engine_power_kw, seq(min(engine_power_kw), max(engine_power_kw) + 100, 100))) %>%
  group_by(bin) %>%
  summarize(bad_subs = sum(bad_subs, na.rm = T))

engine_power_breakdown_plot <- engine_power_breakdown %>%
  ggplot()+
  aes(x = bin, y = bad_subs/1e9)+
  geom_bar(stat = "identity")+
  theme_linedraw()+
  coord_flip()+
  labs(x = "Engine power (kW)",
       y = "Capacity-enhancing subsidies ($, billions)")

ggsave(paste0(results_dir, "hs_engine_power_breakdown.png"), engine_power_breakdown_plot, width = 7.5, height = 8)
```

<!-- ```{r} -->
<!-- # Load biological parameters for the model -->
<!-- bio_dat_regional <- read.csv(here::here("app", "data", "model_parameters_regional_3_regions.csv")) -->

<!-- # Regional parameter list -->
<!-- bio_dat_regional_list <- bio_dat_regional %>% -->
<!--   gather(region, value, -c(1:2)) %>% -->
<!--   group_by(region) %>% -->
<!--   group_split() -->
<!-- ``` -->

<!-- ```{r} -->
<!-- # Load proposal settings -->
<!-- proposal_settings <- read.csv(here::here("app", "data", "wto_proposal_settings_FINAL_AGREEMENT.csv"), stringsAsFactors = F) %>% -->
<!--   dplyr::filter(include != "Hide") -->

<!-- # Filter to final list of proposals to be included in database -->
<!-- included_proposals <- proposal_settings %>% -->
<!--   dplyr::filter(include %in% c("Yes", "Alternate")) %>% -->
<!--   mutate(display_name = case_when(proposal == "Default" ~ "None", -->
<!--                                   TRUE ~ title_tool)) %>% -->
<!--   dplyr::select(category, proposal, display_name) %>% -->
<!--   arrange(category) %>% -->
<!--   dplyr::filter(!(proposal %in% c("RD/TN/RL/126/Rev.2", "RD/TN/RL/119/Rev.1"))) %>% # remove blank entries created for tool -->
<!--   dplyr::filter(proposal != "Default") -->

<!-- proposal_choices <- included_proposals$proposal -->
<!-- names(proposal_choices) <- included_proposals$display_name -->
<!-- ``` -->

<!-- ```{r} -->
<!-- # Load cap/tier lookup table -->
<!-- cap_tier_lookup_table <- read_csv(here::here("app","data","cap_tier_lookup_table.csv")) -->

<!-- # Load S&DT lookup table -->
<!-- sdt_lookup_table <- read_csv(here::here("app", "data", "sdt_lookup_table.csv")) -->
<!-- ``` -->
<!-- ## Model proposals -->

<!-- ```{r} -->
<!-- proposal_results <- NULL -->
<!-- affected_subs <- NULL -->

<!-- for(i in 1:length(proposal_choices)){ -->

<!--   # Choose proposal -->
<!--   proposal_name <- proposal_choices[i] -->

<!--   print(proposal_name) -->

<!--   # Get all data for that proposal -->
<!--   selected_proposal <- proposal_settings %>% -->
<!--       dplyr::filter(proposal == proposal_name) -->

<!--   # Get all IUU conditions -->
<!--   iuu <-  -->
<!--     list("definitions" = unlist(str_split(selected_proposal$iuu_definitions, ", ")), -->
<!--          "assumption" = selected_proposal$iuu_assumption, -->
<!--          "percent" = selected_proposal$iuu_percent, -->
<!--          "scope" = selected_proposal$iuu_scope, -->
<!--          "scope_select" = unlist(str_split(selected_proposal$iuu_scope_select, ", ")), -->
<!--          "scope_manual" = unlist(str_split(selected_proposal$iuu_scope_manual, ", ")), -->
<!--          "allow_sdt" = selected_proposal$iuu_allow_sdt, -->
<!--          "sdt_ldc" = selected_proposal$iuu_sdt_ldc, -->
<!--          "sdt_what_ldc" = unlist(str_split(selected_proposal$iuu_sdt_what_ldc, ", ")), -->
<!--          "sdt_time_delay_ldc" = selected_proposal$iuu_sdt_time_delay_ldc, -->
<!--          "sdt_developing" = selected_proposal$iuu_sdt_developing, -->
<!--          "sdt_what_developing" = unlist(str_split(selected_proposal$iuu_sdt_what_developing, ", ")), -->
<!--          "sdt_time_delay_developing" = selected_proposal$iuu_sdt_time_delay_developing, -->
<!--          "sdt_sve" = selected_proposal$iuu_sdt_sve, -->
<!--          "sdt_what_sve" = unlist(str_split(selected_proposal$iuu_sdt_what_sve, ", ")), -->
<!--          "sdt_time_delay_sve" = selected_proposal$iuu_sdt_time_delay_sve) -->

<!--    # Get all OA conditions -->
<!--    oa <-  -->
<!--      list("definitions" = unlist(str_split(selected_proposal$oa_definitions, ", ")), -->
<!--           "scope" = selected_proposal$oa_scope, -->
<!--           "scope_select" = unlist(str_split(selected_proposal$oa_scope_select, ", ")), -->
<!--           "scope_manual" = unlist(str_split(selected_proposal$oa_scope_manual, ", ")), -->
<!--           "hs_cutoff" = selected_proposal$oa_hs_cutoff, -->
<!--           "length_cutoff" = selected_proposal$oa_length_cutoff, -->
<!--           "tonnage_cutoff" = selected_proposal$oa_tonnage_cutoff, -->
<!--           "engine_cutoff" = selected_proposal$oa_engine_cutoff, -->
<!--           "allow_sdt" = selected_proposal$oa_allow_sdt, -->
<!--           "sdt_ldc" = selected_proposal$oa_sdt_ldc, -->
<!--           "sdt_what_ldc" = unlist(str_split(selected_proposal$oa_sdt_what_ldc, ", ")), -->
<!--           "sdt_hs_cutoff_ldc" = selected_proposal$oa_sdt_hs_cutoff_ldc, -->
<!--           "sdt_time_delay_ldc" = selected_proposal$oa_sdt_time_delay_ldc, -->
<!--           "sdt_developing" = selected_proposal$oa_sdt_developing, -->
<!--           "sdt_what_developing" = unlist(str_split(selected_proposal$oa_sdt_what_developing, ", ")), -->
<!--           "sdt_hs_cutoff_developing" = selected_proposal$oa_sdt_hs_cutoff_developing, -->
<!--           "sdt_time_delay_developing" = selected_proposal$oa_sdt_time_delay_developing, -->
<!--           "sdt_sve" = selected_proposal$oa_sdt_sve, -->
<!--           "sdt_what_sve" = unlist(str_split(selected_proposal$oa_sdt_what_sve, ", ")), -->
<!--           "sdt_hs_cutoff_sve" = selected_proposal$oa_sdt_hs_cutoff_sve, -->
<!--           "sdt_time_delay_sve" = selected_proposal$oa_sdt_time_delay_sve) -->

<!--    # Get all Overcap conditions -->
<!--    overcap <-  -->
<!--      list("definitions" = unlist(str_split(selected_proposal$overcap_definitions, ", ")), -->
<!--           "scope" = selected_proposal$overcap_scope, -->
<!--           "scope_select" = unlist(str_split(selected_proposal$overcap_scope_select, ", ")), -->
<!--           "scope_manual" = unlist(str_split(selected_proposal$overcap_scope_manual, ", ")), -->
<!--           "hs_cutoff" = selected_proposal$overcap_hs_cutoff, -->
<!--           "length_cutoff" = selected_proposal$overcap_length_cutoff, -->
<!--           "tonnage_cutoff" = selected_proposal$overcap_tonnage_cutoff, -->
<!--           "engine_cutoff" = selected_proposal$overcap_engine_cutoff, -->
<!--           "allow_sdt" = selected_proposal$overcap_allow_sdt, -->
<!--           "sdt_ldc" = selected_proposal$overcap_sdt_ldc, -->
<!--           "sdt_what_ldc" = unlist(str_split(selected_proposal$overcap_sdt_what_ldc, ", ")), -->
<!--           "sdt_hs_cutoff_ldc" = selected_proposal$overcap_sdt_hs_cutoff_ldc, -->
<!--           "sdt_time_delay_ldc" = selected_proposal$overcap_sdt_time_delay_ldc, -->
<!--           "sdt_developing" = selected_proposal$overcap_sdt_developing, -->
<!--           "sdt_what_developing" = unlist(str_split(selected_proposal$overcap_sdt_what_developing, ", ")), -->
<!--           "sdt_hs_cutoff_developing" = selected_proposal$overcap_sdt_hs_cutoff_developing, -->
<!--           "sdt_time_delay_developing" = selected_proposal$overcap_sdt_time_delay_developing, -->
<!--           "sdt_sve" = selected_proposal$overcap_sdt_sve, -->
<!--           "sdt_what_sve" = unlist(str_split(selected_proposal$overcap_sdt_what_sve, ", ")), -->
<!--           "sdt_hs_cutoff_sve" = selected_proposal$overcap_sdt_hs_cutoff_sve, -->
<!--           "sdt_time_delay_sve" = selected_proposal$overcap_sdt_time_delay_sve) -->

<!--    # Get all Cap/Tier conditions -->
<!--    cap_tier =  -->
<!--      list("on_off" = selected_proposal$cap_on_off, -->
<!--           "subsidy_types" = unlist(str_split(selected_proposal$cap_subsidy_types, ", ")), -->
<!--           "tier_number" = selected_proposal$cap_tier_number, -->
<!--           "tier_system" = selected_proposal$tier_system, -->
<!--           "two_tier_cutoff" = selected_proposal$two_tier_cutoff, -->
<!--           "three_tier_cutoff" = as.numeric(unlist(str_split(selected_proposal$three_tier_cutoff, ", "))), -->
<!--           "tier1_cap_rule" = selected_proposal$tier1_cap_rule, -->
<!--           "tier2_cap_rule" = selected_proposal$tier2_cap_rule, -->
<!--           "tier3_cap_rule" = selected_proposal$tier3_cap_rule, -->
<!--           "tier1_cap_value" = selected_proposal$tier1_cap_value, -->
<!--           "tier1_cap_percent" = selected_proposal$tier1_cap_percent, -->
<!--           "tier1_cap_best_percent_subs" = selected_proposal$tier1_cap_best_percent_subs, -->
<!--           "tier1_cap_best_percent_landed_value" = selected_proposal$tier1_cap_best_percent_landed_value, -->
<!--           "tier1_cap_best_percent_fishers" = selected_proposal$tier1_cap_best_percent_fishers, -->
<!--           "tier2_cap_value" = selected_proposal$tier2_cap_value, -->
<!--           "tier2_cap_percent" = selected_proposal$tier2_cap_percent, -->
<!--           "tier2_cap_best_percent_subs" = selected_proposal$tier2_cap_best_percent_subs, -->
<!--           "tier2_cap_best_percent_landed_value" = selected_proposal$tier2_cap_best_percent_landed_value, -->
<!--           "tier2_cap_best_percent_fishers" = selected_proposal$tier2_cap_best_percent_fishers, -->
<!--           "tier3_cap_value" = selected_proposal$tier3_cap_value, -->
<!--           "tier3_cap_percent" = selected_proposal$tier3_cap_percent, -->
<!--           "tier3_cap_best_percent_subs" = selected_proposal$tier3_cap_best_percent_subs, -->
<!--           "tier3_cap_best_percent_landed_value" = selected_proposal$tier3_cap_best_percent_landed_value, -->
<!--           "tier3_cap_best_percent_fishers" = selected_proposal$tier3_cap_best_percent_fishers) -->

<!--    # Find fleets -->
<!--     fleet <-  CreateFleets( -->
<!--       vessel_list = vessel_dat, -->
<!--       iuu = iuu, -->
<!--       oa = oa, -->
<!--       overcap = overcap, -->
<!--       cap_tier = cap_tier, -->
<!--       managed_threshold = managed_cutoff, -->
<!--       subsidy_types_all = subsidy_types_sorted_sumaila, -->
<!--       cap_tier_lookup = cap_tier_lookup_table, -->
<!--       country_lookup = country_dependencies, -->
<!--       sdt_lookup = sdt_lookup_table) -->

<!--     # Make list of fleets for bioeconomic model -->
<!--     fleet_list <- fleet$summary %>% -->
<!--       group_by(region) %>% -->
<!--       group_split() -->
<!--     names(fleet_list) <- colnames(bio_dat_regional)[-c(1:2)] -->

<!--     # Run model -->
<!--     results <- pmap_df(list(fleet = fleet_list, -->
<!--                             region = names(fleet_list), -->
<!--                             bio_param = bio_dat_regional_list), -->
<!--                        BioEconModel, -->
<!--                        end_year = end_year, -->
<!--                        return = "all") -->

<!--     # Extract model timeseries results -->
<!--     results_ts <- results %>% -->
<!--       dplyr::filter(Year > 2018) %>% -->
<!--       group_by(Year, Variable, Fleet) %>% -->
<!--       mutate(Diff = case_when(BAU != 0 ~ (Reform - BAU) / abs(BAU), -->
<!--       TRUE ~ 0)) %>% -->
<!--       ungroup() %>% -->
<!--       mutate(run_id = proposal_name, -->
<!--              run_name = names(proposal_name), -->
<!--              run_group = unique(proposal_settings$category[proposal_settings$proposal == proposal_name])) -->

<!--       write_csv(results_ts, paste0(results_dir, str_replace_all(names(proposal_name), "/", "_"), ".csv")) -->

<!--     # Add to data frame -->
<!--       proposal_results <- proposal_results %>% -->
<!--         bind_rows(results_ts) -->

<!--     # Extract affected/unaffected subsidies amounts and convert back to absolute dollars -->
<!--       affected_subs_raw <- fleet$vessels %>% -->
<!--         group_by(region) %>% -->
<!--         summarize_at(vars(A1_subs:C3_subs, A1_subs_removed:C3_subs_removed), sum, na.rm = T) %>% -->
<!--         gather("type", "value", -region) %>% -->
<!--         mutate(category = ifelse(grepl("removed", type), "removed", "base")) %>% -->
<!--         mutate(type = str_replace(type, "_subs_removed", "")) %>% -->
<!--         mutate(type = str_replace(type, "_subs", "")) %>% -->
<!--         left_join(rel, by = "type") %>% -->
<!--         mutate(rel_effect_effort = ifelse(is.na(rel_effect_effort), 1, rel_effect_effort)) %>% -->
<!--         mutate(value_real = value/rel_effect_effort) %>% -->
<!--         group_by(region, category) %>% -->
<!--         summarize(value_real = sum(value_real, na.rm = T)) %>% -->
<!--         ungroup() %>% -->
<!--         group_by(region) %>% -->
<!--         summarize(subs_base = value_real[category == "base"], -->
<!--                   subs_affected = value_real[category == "removed"], -->
<!--                   percent_subs_affected = (value_real[category == "removed"]/value_real[category == "base"])*100) -->

<!--       affected_subs_out <- data_frame(run_id = rep(proposal_name, length.out = 3), -->
<!--                                       run_name = rep(names(proposal_name), length.out = 3), -->
<!--                                       run_group = rep(unique(proposal_settings$category[proposal_settings$proposal == proposal_name]), length.out = 3), -->
<!--                                       region = c("atlantic", "indian", "pacific")) %>% -->
<!--         left_join(affected_subs_raw, by = "region") -->

<!--       # Add to data frame -->
<!--       affected_subs <- affected_subs %>% -->
<!--         bind_rows(affected_subs_out) -->

<!-- } -->
<!-- ``` -->

<!-- Add in most ambitious result and combine into single dataset -->

<!-- ```{r} -->
<!-- # Load most ambitous results from previous script -->
<!-- most_ambitious_results <- read_csv(paste0(here::here("results", "06-run-model/"), "mgmt_threshold_", managed_cutoff, "/", "BC_rel_ts_data.csv")) %>% -->
<!--   mutate(run_id = "Ambitious Reform", -->
<!--          run_group = "Ambitious Reform") -->

<!-- # Combine with ts data -->
<!-- all_ts_results <- proposal_results %>% -->
<!--   bind_rows(most_ambitious_results) -->

<!-- # Get subsidies affected for most ambitious scenario -->
<!-- most_ambitious_subs_affected <- vessel_dat_raw %>% -->
<!--   mutate(subs_base = bad_subs + good_subs + ugly_subs, -->
<!--          subs_affected = bad_subs + ugly_subs) %>% -->
<!--   group_by(region) %>% -->
<!--   summarize(subs_base = sum(subs_base, na.rm = T), -->
<!--             subs_affected = sum(subs_affected, na.rm = T)) %>% -->
<!--   mutate(percent_subs_affected = (subs_affected/subs_base)*100) -->

<!-- # Combine with subs affected data -->
<!-- all_subs_affected <- data_frame(run_id = rep("Ambitious Reform", 3), -->
<!--                                 run_name = rep("All bad and ugly subsidies", 3), -->
<!--                                 run_group = rep("Ambitious Reform", 3)) %>% -->
<!--   bind_cols(most_ambitious_subs_affected) %>% -->
<!--   bind_rows(affected_subs) -->
<!-- ``` -->

<!-- ## Make nice databases (global and regional) -->

<!-- ```{r} -->
<!-- # We want these to be ordered by date within each category, so we need to go back to our list -->
<!-- date_order <- proposal_settings %>% -->
<!--   dplyr::select(title_tool, date) %>% -->
<!--   rownames_to_column("order") %>% -->
<!--   mutate(order = as.numeric(order)) -->

<!-- # Collect global results -->
<!-- all_results_global_output_table <- all_ts_results %>% -->
<!--   dplyr::filter(Year %in% c(2050, end_year)) %>% -->
<!--   dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total", "u_mort_total")) %>% -->
<!--   group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>% -->
<!--   summarize(BAU_tot = sum(BAU, na.rm = T), -->
<!--             Reform_tot = sum(Reform, na.rm = T), -->
<!--             Diff_tot = case_when(BAU_tot != 0 ~ (Reform_tot - BAU_tot)/abs(BAU_tot), -->
<!--                             TRUE ~ 0)) %>% -->
<!--   ungroup() %>% -->
<!--   mutate(Variable = case_when(Variable == "biomass" ~ "Biomass", -->
<!--                                 Variable == "catches_total" ~ "Catches", -->
<!--                                 Variable == "revenue_total" ~ "Revenue", -->
<!--                                 Variable == "u_mort_total" ~ "Fishing Mortality")) %>% -->
<!--   dplyr::select(Id = run_id, -->
<!--                 Name = run_name, -->
<!--                 Category = run_group,  -->
<!--                 Year, -->
<!--                 Diff_tot, -->
<!--                 Variable) %>% -->
<!--   spread(Variable, Diff_tot) %>% -->
<!--   left_join(date_order %>% dplyr::select(Name = title_tool, order), by = "Name") %>% -->
<!--   mutate(Category = factor(Category, levels = c("Ambitious Reform", "IUU", "OFOC", "Overfished", "Other & Multiple"))) %>% -->
<!--   arrange(Category, order, Year) %>% -->
<!--   dplyr::select(-order) -->

<!-- write.csv(all_results_global_output_table, paste0(results_dir, "all_results_global_output_table.csv")) -->

<!-- # Now make a pretty version for 2050 only -->
<!-- all_results_global_output_table_2050_pretty <- all_results_global_output_table %>% -->
<!--   dplyr::filter(Year == 2050) %>% -->
<!--   ungroup() %>% -->
<!--   mutate(Biomass = round(Biomass*100, 2), -->
<!--          Catches = round(Catches*100, 2), -->
<!--          Revenue = round(Revenue*100, 2), -->
<!--          `Fishing Mortality` = round(`Fishing Mortality`*100, 2)) %>% -->
<!--   rename(`Change in biomass (%, 2050)` = Biomass, -->
<!--          `Change in catch (%, 2050)` = Catches, -->
<!--          `Change in revenue (%, 2050)` = Revenue, -->
<!--          `Change in fishing mortality (%, 2050)` = `Fishing Mortality`) %>% -->
<!--   dplyr::select(-Year) -->

<!-- write.csv(all_results_global_output_table_2050_pretty, paste0(results_dir, "all_results_global_output_table_2050_pretty.csv")) -->

<!-- # Now make a pretty version for 2080 only -->
<!-- all_results_global_output_table_2080_pretty <- all_results_global_output_table %>% -->
<!--   dplyr::filter(Year == 2080) %>% -->
<!--   ungroup() %>% -->
<!--   mutate(Biomass = round(Biomass*100, 2), -->
<!--          Catches = round(Catches*100, 2), -->
<!--          Revenue = round(Revenue*100, 2), -->
<!--          `Fishing Mortality` = round(`Fishing Mortality`*100, 2)) %>% -->
<!--   rename(`Change in biomass (%, 2080)` = Biomass, -->
<!--          `Change in catch (%, 2080)` = Catches, -->
<!--          `Change in revenue (%, 2080)` = Revenue, -->
<!--          `Change in fishing mortality (%, 2080)` = `Fishing Mortality`) %>% -->
<!--   dplyr::select(-Year) -->

<!-- write.csv(all_results_global_output_table_2080_pretty, paste0(results_dir, "all_results_global_output_table_2080_pretty.csv")) -->

<!-- # Combine -->
<!-- all_results_global_output_table_pretty <- all_results_global_output_table_2050_pretty %>% -->
<!--   left_join(all_results_global_output_table_2080_pretty %>% dplyr::select(-Name, -Category)) -->

<!-- write.csv(all_results_global_output_table_pretty, paste0(results_dir, "all_results_global_output_table_pretty.csv")) -->

<!-- # Now let's get affected subs globally -->
<!-- all_subs_affected_global <- all_subs_affected %>% -->
<!--   group_by(run_id, run_name, run_group) %>% -->
<!--   summarize(subs_base = sum(subs_base), -->
<!--             subs_affected = sum(subs_affected)) %>% -->
<!--   ungroup() %>% -->
<!--   mutate(percent_subs_affected = round((subs_affected/subs_base)*100, 2)) -->

<!-- # And add to table -->
<!-- global_database <- all_results_global_output_table_pretty %>% -->
<!--   left_join(all_subs_affected_global %>% dplyr::select(Id = run_id, subs_affected, percent_subs_affected)) %>% -->
<!--   rename(`Subsidies affected ($)` = subs_affected, -->
<!--          `Subsidies affected (%)` = percent_subs_affected) -->

<!-- write.csv(global_database, paste0(results_dir, "SubsidyExplorer_proposal_results_global.csv")) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- # Now do regional -->
<!-- all_results_regional_output_table <- all_ts_results %>% -->
<!--   dplyr::filter(Year %in% c(2050, end_year)) %>% -->
<!--   dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total", "u_mort_total")) %>% -->
<!--   mutate(Variable = case_when(Variable == "biomass" ~ "Biomass", -->
<!--                                 Variable == "catches_total" ~ "Catches", -->
<!--                                 Variable == "revenue_total" ~ "Revenue", -->
<!--                                 Variable == "u_mort_total" ~ "Fishing Mortality")) %>% -->
<!--   dplyr::select(Id = run_id, -->
<!--                 Name = run_name, -->
<!--                 Category = run_group,  -->
<!--                 Year, -->
<!--                 Region, -->
<!--                 Diff, -->
<!--                 Variable) %>% -->
<!--   spread(Variable, Diff) %>% -->
<!--   left_join(date_order %>% dplyr::select(Name = title_tool, order), by = "Name") %>% -->
<!--   mutate(Category = factor(Category, levels = c("Ambitious Reform", "IUU", "OFOC", "Overfished", "Other & Multiple"))) %>% -->
<!--   arrange(Region, Category, order, Year) %>% -->
<!--   dplyr::select(-order) -->

<!-- write.csv(all_results_regional_output_table, paste0(results_dir, "all_results_regional_output_table.csv")) -->

<!-- # Now make a pretty version for 2050 only -->
<!-- all_results_regional_output_table_2050_pretty <- all_results_regional_output_table %>% -->
<!--   dplyr::filter(Year == 2050) %>% -->
<!--   ungroup() %>% -->
<!--   mutate(Biomass = round(Biomass*100, 2), -->
<!--          Catches = round(Catches*100, 2), -->
<!--          Revenue = round(Revenue*100, 2), -->
<!--          `Fishing Mortality` = round(`Fishing Mortality`*100, 2)) %>% -->
<!--   rename(`Change in biomass (%, 2050)` = Biomass, -->
<!--          `Change in catch (%, 2050)` = Catches, -->
<!--          `Change in revenue (%, 2050)` = Revenue, -->
<!--          `Change in fishing mortality (%, 2050)` = `Fishing Mortality`) %>% -->
<!--   dplyr::select(-Year) %>% -->
<!--   mutate(Region = case_when(Region == "atlantic" ~ "Atlantic Ocean", -->
<!--                             Region == "indian" ~ "Indian Ocean", -->
<!--                             Region == "pacific" ~ "Pacific Ocean")) -->

<!-- write.csv(all_results_regional_output_table_2050_pretty, paste0(results_dir, "all_results_regional_output_table_2050_pretty.csv")) -->

<!-- # Now make a pretty version for 2080 only -->
<!-- all_results_regional_output_table_2080_pretty <- all_results_regional_output_table %>% -->
<!--   dplyr::filter(Year == 2080) %>% -->
<!--   ungroup() %>% -->
<!--   mutate(Biomass = round(Biomass*100, 2), -->
<!--          Catches = round(Catches*100, 2), -->
<!--          Revenue = round(Revenue*100, 2), -->
<!--          `Fishing Mortality` = round(`Fishing Mortality`*100, 2)) %>% -->
<!--   rename(`Change in biomass (%, 2080)` = Biomass, -->
<!--          `Change in catch (%, 2080)` = Catches, -->
<!--          `Change in revenue (%, 2080)` = Revenue, -->
<!--          `Change in fishing mortality (%, 2080)` = `Fishing Mortality`) %>% -->
<!--   dplyr::select(-Year) %>% -->
<!--   mutate(Region = case_when(Region == "atlantic" ~ "Atlantic Ocean", -->
<!--                             Region == "indian" ~ "Indian Ocean", -->
<!--                             Region == "pacific" ~ "Pacific Ocean")) -->

<!-- write.csv(all_results_regional_output_table_2080_pretty, paste0(results_dir, "all_results_regional_output_table_2080_pretty.csv")) -->

<!-- # Combine -->
<!-- all_results_regional_output_table_pretty <- all_results_regional_output_table_2050_pretty %>% -->
<!--   left_join(all_results_regional_output_table_2080_pretty %>% dplyr::select(-Name, -Category)) -->

<!-- write.csv(all_results_regional_output_table_pretty, paste0(results_dir, "all_results_regional_output_table_pretty.csv")) -->

<!-- # And add affected subsidies to table -->
<!-- regional_database <- all_results_regional_output_table_pretty %>% -->
<!--   left_join(all_subs_affected %>% -->
<!--               mutate(region = case_when(region == "atlantic" ~ "Atlantic Ocean", -->
<!--                                         region == "indian" ~ "Indian Ocean", -->
<!--                                         region == "pacific" ~ "Pacific Ocean")) %>% -->
<!--               mutate(percent_subs_affected = round(percent_subs_affected, 2)) %>% -->
<!--               dplyr::select(Id = run_id, Region = region, subs_affected, percent_subs_affected)) %>% -->
<!--   rename(`Subsidies affected ($)` = subs_affected, -->
<!--          `Subsidies affected (%)` = percent_subs_affected) -->

<!-- write.csv(regional_database, paste0(results_dir, "SubsidyExplorer_proposal_results_regional.csv")) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- # # Now make a min, max, and average for each proposal type -->
<!-- # summary_results_global_2050_pretty <- all_results_global_output_table_2050_pretty %>% -->
<!-- #   gather(Variable, Value, c("Biomass", "Catches", "Revenue", "Fishing Mortality")) %>% -->
<!-- #   group_by(Category, Year, Variable) %>% -->
<!-- #   summarize(Minimum = min(Value, na.rm = T), -->
<!-- #             Maximum = max(Value, na.rm = T), -->
<!-- #             Median = median(Value, na.rm = T), -->
<!-- #             Mean = mean(Value, na.rm = T)) %>% -->
<!-- #   arrange(Category) -->
<!-- #  -->
<!-- # write.csv(summary_results_global_2050_pretty, paste0(results_dir, "summary_results_global_2050_pretty.csv")) -->
<!-- #  -->
<!-- # # Get rounded end values for the most ambitious scenario -->
<!-- # global_biomass_2050 <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == 2050 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2) -->
<!-- # global_biomass_end <- round(all_results_global_output_table$Biomass[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2) -->
<!-- #  -->
<!-- # global_catches_2050 <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == 2050 & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2) -->
<!-- # global_catches_end <- round(all_results_global_output_table$Catches[all_results_global_output_table$Year == end_year & all_results_global_output_table$Id == "Ambitious Reform"]*100, 2) -->

<!-- # # Now make a min, max, and average for each proposal type -->
<!-- # summary_results_regional_2050_pretty <- all_results_regional_output_table_2050_pretty %>% -->
<!-- #   gather(Variable, Value, c("Biomass", "Catches", "Revenue", "Fishing Mortality")) %>% -->
<!-- #   group_by(Region, Category, Year, Variable) %>% -->
<!-- #   summarize(Minimum = min(Value, na.rm = T), -->
<!-- #             Maximum = max(Value, na.rm = T), -->
<!-- #             Median = median(Value, na.rm = T), -->
<!-- #             Mean = mean(Value, na.rm = T)) %>% -->
<!-- #   arrange(Region, Category) -->
<!-- #  -->
<!-- # write.csv(summary_results_regional_2050_pretty, paste0(results_dir, "summary_results_regional_2050_pretty.csv")) -->
<!-- ``` -->

<!-- ## Plots -->

<!-- ```{r} -->
<!-- if(make_plots){ -->
<!--   # A) global (aggregated) "kobe" final year plot -->
<!--   box_2050_plot <- BioEconomicModelPlots(dat = all_ts_results, -->
<!--                                          spatial_res = "global", -->
<!--                                          temporal_res = "last", -->
<!--                                          end_year = 2050, -->
<!--                                          plot_name = "box_scenario_type_2050_plot", -->
<!--                                          plot_width = 7.5, -->
<!--                                          plot_height = 6, -->
<!--                                          results_dir = results_dir, -->
<!--                                          group_var = "run_group", -->
<!--                                          color_var = "run_group", -->
<!--                                          legend_pos_manual = "bottom", -->
<!--                                          legend_name = "Scenario Type", -->
<!--                                          plot_type = "box") -->

<!-- ggsave(paste0(results_dir, "proposal_effects_2050_boxplot.tiff"), box_2050_plot, width = 7.5, height = 6) -->
<!-- } -->
<!-- ``` -->

<!-- ## Do the same with absolute values -->

<!-- ```{r} -->
<!-- # # We want these to be ordered by date within each category, so we need to go back to our list -->
<!-- # date_order <- proposal_settings %>% -->
<!-- #   dplyr::select(title_tool, date) %>% -->
<!-- #   rownames_to_column("order") %>% -->
<!-- #   mutate(order = as.numeric(order)) -->
<!-- #  -->
<!-- # # Collect global results -->
<!-- # all_results_global_output_table_absolute <- plot_results %>% -->
<!-- #   dplyr::filter(Year %in% c(2050, end_year)) %>% -->
<!-- #   dplyr::filter(Variable %in% c("biomass", "catches_total", "revenue_total")) %>% -->
<!-- #   group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>% -->
<!-- #   summarize(BAU_tot = sum(BAU, na.rm = T), -->
<!-- #             Reform_tot = sum(Reform, na.rm = T), -->
<!-- #             Diff_tot = case_when(BAU_tot != 0 ~ Reform_tot - BAU_tot, -->
<!-- #                             TRUE ~ 0)) %>% -->
<!-- #   ungroup() %>% -->
<!-- #   mutate(Variable = case_when(Variable == "biomass" ~ "Biomass", -->
<!-- #                                 Variable == "catches_total" ~ "Catches", -->
<!-- #                                 Variable == "revenue_total" ~ "Revenue")) %>% -->
<!-- #   dplyr::select(Id = run_id, -->
<!-- #                 Name = run_name, -->
<!-- #                 Category = run_group,  -->
<!-- #                 Year, -->
<!-- #                 Diff_tot_absolute = Diff_tot, -->
<!-- #                 Variable) %>% -->
<!-- #   spread(Variable, Diff_tot_absolute) %>% -->
<!-- #   left_join(date_order %>% dplyr::select(Name = title_tool, order), by = "Name") %>% -->
<!-- #   mutate(Category = factor(Category, levels = c("Ambitious Reform", "IUU", "OFOC", "Overfished", "Other & Multiple"))) %>% -->
<!-- #   arrange(Category, order, Year) %>% -->
<!-- #   dplyr::select(-order) -->
<!-- #  -->
<!-- # write.csv(all_results_global_output_table_absolute, paste0(results_dir, "all_results_global_output_table_absolute.csv")) -->

<!-- # write.csv(all_results_global_absolute_table, paste0(results_dir, "all_results_global_absolute_table.csv")) -->
<!-- #  -->
<!-- # all_results_regional_absolute_table <- plot_results %>% -->
<!-- #   dplyr::filter(Year %in% c(2050, end_year)) %>% -->
<!-- #   dplyr::filter(Variable %in% c("biomass", "catches_total")) %>% -->
<!-- #   mutate(Variable = case_when(Variable == "biomass" ~ "Biomass", -->
<!-- #                                 Variable == "catches_total" ~ "Catches")) %>% -->
<!-- #   mutate(abs_Diff = case_when(BAU != 0 ~ Reform-BAU, -->
<!-- #                               TRUE ~ 0)) %>% -->
<!-- #   dplyr::select(Id = run_id, -->
<!-- #                 Name = run_name, -->
<!-- #                 Category = run_group,  -->
<!-- #                 Year, -->
<!-- #                 Region, -->
<!-- #                 abs_Diff, -->
<!-- #                 Variable) %>% -->
<!-- #   spread(Variable, abs_Diff) -->
<!-- #  -->
<!-- # write.csv(all_results_regional_absolute_table, paste0(results_dir, "all_results_regional_absolute_table.csv")) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- # # Weight of a mature dairy cow in mt -->
<!-- # cow_weight <- 0.6803886 -->
<!-- #  -->
<!-- # all_results_global_cow_equivalent_table <- plot_results %>% -->
<!-- #   dplyr::filter(Year %in% c(2050, end_year)) %>% -->
<!-- #   dplyr::filter(Variable %in% c("biomass", "catches_total")) %>% -->
<!-- #   group_by(Year, Variable, Fleet, run_id, run_name, run_group) %>% -->
<!-- #   summarize(BAU_tot = sum(BAU, na.rm = T), -->
<!-- #             Reform_tot = sum(Reform, na.rm = T), -->
<!-- #             abs_Diff_tot = case_when(BAU_tot != 0 ~ Reform_tot-BAU_tot, -->
<!-- #                                      TRUE ~ 0), -->
<!-- #             cow_Diff = abs_Diff_tot*cow_weight) %>% -->
<!-- #   ungroup() %>% -->
<!-- #   mutate(Variable = case_when(Variable == "biomass" ~ "Biomass", -->
<!-- #                               Variable == "catches_total" ~ "Catches")) %>% -->
<!-- #   dplyr::select(Id = run_id, -->
<!-- #                 Name = run_name, -->
<!-- #                 Category = run_group,  -->
<!-- #                 Year, -->
<!-- #                 cow_Diff, -->
<!-- #                 Variable) %>% -->
<!-- #   spread(Variable, cow_Diff) -->
<!-- #  -->
<!-- # write.csv(all_results_global_cow_equivalent_table, paste0(results_dir, "all_results_global_cow_equivalent_table.csv")) -->
<!-- #  -->
<!-- # all_results_regional_cow_equivalent_table <- plot_results %>% -->
<!-- #   dplyr::filter(Year %in% c(2050, end_year)) %>% -->
<!-- #   dplyr::filter(Variable %in% c("biomass", "catches_total")) %>% -->
<!-- #   mutate(Variable = case_when(Variable == "biomass" ~ "Biomass", -->
<!-- #                                 Variable == "catches_total" ~ "Catches")) %>% -->
<!-- #   mutate(abs_Diff = case_when(BAU != 0 ~ Reform-BAU, -->
<!-- #                               TRUE ~ 0), -->
<!-- #          cow_Diff = abs_Diff*cow_weight) %>% -->
<!-- #   dplyr::select(Id = run_id, -->
<!-- #                 Name = run_name, -->
<!-- #                 Category = run_group,  -->
<!-- #                 Year, -->
<!-- #                 Region, -->
<!-- #                 cow_Diff, -->
<!-- #                 Variable) %>% -->
<!-- #   spread(Variable, cow_Diff) -->
<!-- #  -->
<!-- # write.csv(all_results_regional_cow_equivalent_table, paste0(results_dir, "all_results_regional_cow_equivalent_table.csv")) -->

<!-- ``` -->

### 2022-09-30 scripts/10_high_seas_vessel_breakdown.Rmd
hs breakdowns, updated methodology, and database

@@
 ```{r}
-# # Load country dependencies helper file
-# country_dependencies <- read_csv(here::here("app", "data", "country_dependencies.csv")) %>%
-#    mutate(display_name = case_when(!is.na(WTO_name) ~ WTO_name,
-#                                   iso3 == "ANT" ~ "Netherlands Antilles",
-#                                   iso3 == "ASC" ~ "Ascension Island", 
-#                                   iso3 == "CPT" ~ "Clipperton Island",
-#                                   iso3 == "TAA" ~ "Tristan da Cunha",
-#                                   TRUE ~ countrycode(iso3, "iso3c", "country.name"))) %>%
-#   arrange(sovereign_iso3) 
-# 
-# # Vector of all WTO Members and Observers for use in the app [does not include the overseas territories associated with them]
-# wto_members_and_observers <- country_dependencies$iso3[country_dependencies$is_WTO & !country_dependencies$is_overseas_territory]
+# Load country dependencies helper file
+country_dependencies <- read_csv(here::here("app", "data", "country_dependencies.csv")) %>%
+   mutate(display_name = case_when(!is.na(WTO_name) ~ WTO_name,
+                                  iso3 == "ANT" ~ "Netherlands Antilles",
+                                  iso3 == "ASC" ~ "Ascension Island",
+                                  iso3 == "CPT" ~ "Clipperton Island",
+                                  iso3 == "TAA" ~ "Tristan da Cunha",
+                                  TRUE ~ countrycode(iso3, "iso3c", "country.name"))) %>%
+  arrange(sovereign_iso3)
+
+# Vector of all WTO Members and Observers for use in the app [does not include the overseas territories associated with them]
+wto_members_and_observers <- country_dependencies$iso3[country_dependencies$is_WTO & !country_dependencies$is_overseas_territory]
 ```
@@
   dplyr::filter(prop_fishing_KWh_high_seas >= 0.05)
-
 ```
@@
   group_by(vessel_class) %>%
-  summarize(bad_subs = sum(bad_subs, na.rm = T))
+  summarize(bad_subs = sum(bad_subs, na.rm = T),
+            n_vessels = n_distinct(ssvid))
 
@@
 
+write_csv(gear_type_breakdown, paste0(results_dir, "hs_gear_type_breakdown.csv"))
 ggsave(paste0(results_dir, "hs_gear_type_breakdown.png"), gear_type_breakdown_plot, width = 7.5, height = 6)
@@
   group_by(bin) %>%
-  summarize(bad_subs = sum(bad_subs, na.rm = T))
+  summarize(bad_subs = sum(bad_subs, na.rm = T),
+            n_vessels = n_distinct(ssvid))
 
@@
 
+write_csv(length_breakdown, paste0(results_dir, "hs_length_breakdown.csv"))
 ggsave(paste0(results_dir, "hs_length_breakdown.png"), length_breakdown_plot, width = 7.5, height = 6)
 ```
+
 ## Tonnage breakdown
@@
 
+write_csv(tonnage_breakdown, paste0(results_dir, "hs_tonnage_breakdown.csv"))
 ggsave(paste0(results_dir, "hs_tonnage_breakdown.png"), tonnage_breakdown_plot, width = 7.5, height = 8)
@@
 
+write_csv(engine_power_breakdown, paste0(results_dir, "hs_engine_power_breakdown.csv"))
 ggsave(paste0(results_dir, "hs_engine_power_breakdown.png"), engine_power_breakdown_plot, width = 7.5, height = 8)

### 2022-09-30 app/00_initialize_app.R

@@ -279,7 +279,7 @@ sdt_lookup_table <- read_csv("./data/sdt_lookup_table.csv")
 #proposal_settings <- read.csv("./data/wto_proposal_settings_v3.csv", stringsAsFactors = F)
 # proposal_settings <- read.csv("./data/wto_proposal_settings_FINAL.csv", stringsAsFactors = F) %>%
 #   dplyr::filter(include != "Hide") # remove bad proposals
-proposal_settings <- read.csv("./data/wto_proposal_settings_master_FINAL_AGREEMENT.csv", stringsAsFactors = F) %>%
+proposal_settings <- read.csv("./data/wto_proposal_settings_FINAL_AGREEMENT.csv", stringsAsFactors = F) %>%
   dplyr::filter(include != "Hide") # remove bad proposals
 
 # Proposal names

### 2022-09-30 app/server.R

@@ -1197,7 +1197,7 @@ shinyServer(function(input, output, session) {
   output$db_download_methods <- downloadHandler(
     filename = "SubsidyExplorer_methods.pdf",
     content = function(file) {
-      file.copy("www/SubsidyExplorer_methods.pdf", file)
+      file.copy("www/2022_09_28_SubsidyExplorer_methods.pdf", file)
     }
   )
   
